### 2017-11-03 paper.tex
First Cavalieri dump

\documentclass{article}
\usepackage{maa-monthly}

%% IF YOU HAVE FONTS INSTALLED
%\usepackage{mtpro2}
%\usepackage{mathtime}

\theoremstyle{theorem}
\newtheorem{theorem}{Theorem}

\theoremstyle{definition}
\newtheorem*{definition}{Definition}
\newtheorem*{remark}{Remark}

\begin{document}

\title{A 2D Geometric Interpretation of the Riemann-Stieltjes Integral}
\markright{Abbreviated Article Title}
\author{Woodrow Wilson and Herbert Hoover}

\maketitle

\begin{abstract}
It is desirable to have geometric interpretations for difficult mathematical ideas. In this paper we present an intiutive geometric interpretation of the Riemann-Stieltjes integral. It can be 
summarized as follows: the Riemann-Stieltjes integral can be inerpreted as an infinite sum of initesimally small non-rectangular 
integration strips. This interpretation is surprisingly similar to the geometric intrepretation of the ordinary Riemann integral. 
It is therefore likely that this geometric interpretaion would narrow the logical rift between the Riemann integral and the Riemann-Stieltjes integral (i.e. make the 
Riemann-Stieltjes integral less abstract).
\end{abstract}

\noindent
Providing a geometrical interpretation for a mathematical concept can greatly improve ones understanding of it. The Riemann-Stieltjes 
integral is no exception. Bullock proposed a three dimensional geometric framework with which one can interpret the Riemann-Stieltjes 
integral. Pol proposes to interpret the Riemann-Stieltjes integral as the real distance covered by a moving object, whose speed was 
correctly recorded but at incorrect times. In this paper we present an intiutive two dimensional geometric interpretation of the Riemann-Stieltjes integral.\\

\noindent
?? utilized the idea of using non-rectangular integration strips to perform integration
and in doing so developed the Cavalieri integral. The area of a non-rectangular integration strip is computed via 
Cavalieri's principle.  also showed that a Cavalieri integral can easily be converted to a Riemann-Stieltjes integral. The 
reverse operation was however not addressed therein. In this paper we address this shortcomming. An automatic consequence of being 
able to convert a Riemann-Stieltjes integral to a Cavalieri integral is that a geometric interpretation of the Riemann-Stieltjes
becomes evident. This geometric interpretation is: the Riemann-Stieltjes integral can be interpreted as an infinite sum of infinitesimally small
non-rectangular integration strips. Interestingly enough, this interpretation of the Riemann-Stieltjes integral is very similar 
to the geometric interpretation of the Riemann integral. The difference being: in the case of the Riemann integral we employ 
rectangular instead of non-rectangular integration strips. This geometric interpretation has been quite useful while 
theaching the ordinary Riemann integral to undergraduate students. It, therefore, seems likely that undergraduate students would find the non-rectangular geometric interpretation
of the Riemann-Stieltjes integral just as useful. It is also interesting to mention that it has been proposed to first 
teach other integral definitions (which are easier to grasp) before moving on to the Riemann integral. It therefore seems plausible that
students will find it useful to first understand the Cavaleri integral before the Riemann-Stieltjes integral is taught to them.

\section{Riemann-Stieltjes integral}
Let $f$ and $g$ denote real-valued functions defined on a closed interval $[a',b']$ of the real line. We shall suppose that 
both $f$ and $g$ are bounded on $[a',b']$.

\begin{definition}[Definition of integral]
Define a partition $\mathcal{P}$ of $[a',b']$ to be a set of points $x_0, x_1,\cdots,x_n$, 
where $a' = x_0 \leq x_1 \leq \cdots \leq x_n = b'$. For each partition 
$\mathcal{P}$ of $[a',b']$ write $\Delta g_k = g(x_k)-g(x_{k-1})$. Let 
$M_k = \max\{f(x),x_{k-1}\leq x \leq x_{k}\}$, $m_k = \max\{f(x),x_{k-1}\leq x \leq x_{k}\}$, and set 
\begin{equation}
\label{ref:S_up}
\mathcal{S}_U(\mathcal{P},f,g) = \sum_{k=1}^n M_k \Delta g_k, 
\end{equation}
and
\begin{equation}
\label{ref:S_low}
\mathcal{S}_L(\mathcal{P},f,g) = \sum_{k=1}^n m_k \Delta g_k. 
\end{equation}
The sums in Eq.~\eqref{ref:S_up} and Eq.~\eqref{ref:S_low} are respectively called the the upper and lower Riemann-Stieltjes sums.
If there is a unique number $I$ that satisfies the inequality $\mathcal{S}_L(\mathcal{P},f,g)\leq I \leq \mathcal{S}_U(\mathcal{P},f,g)$ for all 
partitions $P$ of $[a',b']$, then $f$ is Riemann integrable with respect to $g$ on $[a',b']$. Moreover, $I$ is called the Riemann-Stieltjes integral of $f$ from $a'$ to $b'$ and is denoted by
\begin{equation}
\int_{a'}^{b'} f(x) dg(x). 
\end{equation}
\end{definition}

\begin{theorem}
If the derivative $g'$ exists and is continuous on $[a',b']$ and if $f$ is integrable with respect to $g$ on $[a',b']$, then the following 
Riemann and Riemann-Stieltjes integrals are equivalent
\begin{equation}
\int_{a'}^{b'} f(x) dg(x) = \int_{a'}^{b'} f(x)g'(x)dx.
\end{equation}
\end{theorem}

%\begin{theorem}
%Assume $g(x)$ increases monotonically and $g'(x)$ is Riemann intergable on $[a,b]$. Let $f$ be a bounded, real, Riemann integrable 
%function on $[a,b]$. Then
%\begin{equation}
%\int_a^b f dg(x) = \int_a^b f(x) g'(x) dx. 
%\end{equation}
%\end{theorem}

\begin{theorem}
If $a'<s<b'$, $f$ is continuous at $s$, and 
\begin{equation}
g(x) = 
\begin{cases}
0 & \textrm{if}~x\leq s\\
1 & \textrm{if}~x > s
\end{cases}
\end{equation}
then $\int_a^b f dg(x) = f(s)$.
\end{theorem}

% #########################################################################################################
% Bartle definition of Riemann-Stieltjes integral
% #########################################################################################################

% \subsection{Bartle s. 29 p. 212}
% Let $f$ and $g$ denote real-valued functions defined on a closed interval $J=[a,b]$ of the real line. We shall suppose that 
% both $f$ and $g$ are bounded on $J$. A partition of $J$ is a finite collection  of non-overlapping intervals whose union is $J$. 
% Usually, we describe a partition $P$ by specifying a finite set of real numbers $(x_0,x_1,\cdots,x_n)$ such that 
% \begin{equation}
% a = x_0 \leq x_1 \leq \cdots \leq x_n = b
% \end{equation}
% and such that the subintervals occuring in the partition $P$ are the intervals $[x_{k-1},x_k]$, $k = 1,2,\cdots,n$. Hence we write 
% $P = (x_0,x_1,\cdots,x_n)$. If $P$ and $Q$ are partitions of $J$, we say $Q$ is a refinement of $P$ or that $Q$ is finer than $P$ in case every subinterval in $Q$ is contained in some subinterval in $P$.
% 
% \begin{definition}
% If $P$ is a partition of $J$, then a Riemann-Stieltjes sum of $f$ with respect to $g$ and corresponding to $P$ is a real number 
% $S(P,f,g)$ of the form 
% \begin{equation}
% S(P,f,g) = \sum_{k=1}^n f(\xi_{k})\{g(x_k)-g(x_{k-1})\}. 
% \end{equation}
% Here we have selected numbers $\xi_{k}$ satisfying 
% \begin{equation}
% x_{k-1} \leq \xi_{k} \leq x_{k}~\textrm{for}~k=1,2,\cdots,n.  
% \end{equation}
% \end{definition}
% 
% \begin{definition}
% We say that $f$ is integrable with respect to $g$ on $J$ if there exists a real number $I$ such that for every number $\epsilon>0$ there 
% is a partition $P_{\epsilon}$ of $J$ such that if $P$ is a refinement of $P_{\epsilon}$ and $S(P,f,g)$ is any Riemann-Stieltjes sum corresponding 
% to $P$, then 
% \begin{equation}
% |S(P,f,g)-I|<\epsilon. 
% \end{equation}
% In this case the number is uniquely determined and is denoted by
% \begin{equation}
% I = \int_a^b f(x) dg(x). 
% \end{equation}
% \end{definition}
% 
% \begin{theorem}
% If the derivative $g'$ exists and is continious on $J$ and if $f$ is integrable with respect to $g$, then the product $fg'$ is Riemann
% integrable and 
% \begin{equation}
% \int_a^b f(x) dg(x) = \int_a^b f(x)g'(x)dx.
% \end{equation}
% \end{theorem}

\section{3D Geometric Interpretation}
Bullock proposed one possible geometric interpretation of the Riemann-Stieltjes integral. 
The basic premise behind his approach is to represent $f(x)$ and $g(x)$ as three-dimensional sheets. 
The three dimensional coordinate system which Bullock proposes to realize this representation is depicted in 
Fig.~\ref{fig:bullock}. The $f$-sheet is constructed by simply extending the curve $f$ which resides in the $fx$-plane 
along the $g$-direction. The $g$-sheet is constructed similarly. Note that, since $f$ is independent of $g$, the $f$-sheet remains 
constant along the $g$-direction. Similarly, the $g$-sheet remains constant along the $f$-direction. 
A new sheet, known simply as the ``fence'', can be created by chopping off any part of the $g$-sheet that protrudes above the 
$f$-sheet and below the $gx$-plane. This sheet can now be projected onto the $fg$-plane. The area of the region that is formed 
via this projection can be interpreted as the value which is obtained when the Riemann-Stieltjes integral is evaluated.

\noindent
Let us now try to make the above ideas more concrete by applying them to an example. Let $f(x)=x^2$ and 
$g(x)=x$. The sheets associated with these two functions are depicted in Fig.~\ref{fig:bullock}. 
The $f$-sheet is depicted in blue, while the $g$-sheet is red. The ``fence'' is depicted in green. The region
obtained by projecting the ``fence'' on to the $fg$-plane is depicted in black.

\noindent
It is interesting to note that Bullock follows a similar route than we do in terms of developing his geometrical framework.
He starts of with quite strict requirements for $f$ ang $g$ and relaxes more and more of these requirements in latter 
examples.

\begin{figure}[htb]
\centering
\includegraphics[width=1.0\textwidth]{3D_final-crop.pdf}
\caption{An example of using Bullocks' geometric framework to interpret the Riemann-Stieltjes integral. In this example 
$f(x)$ is represented by the blue sheet, $g(x)$ is represented by the red sheet. Moreover, $f(x)=x^2$ and $g(x)=x$. The green sheet, simply known as the ``fence'', is formed 
by chopping of any part of the $g$-sheet which protrudes above the $f$-sheet and below the $gx$-plane. Projecting the ``fence''
onto the $fg$-plane produces the visible gray region in the $fg$-plane. The area of this gray region in the $fg$-plane is equal to the Riemann-Stieltjes integral:
$\int_{0}^{3} f(x) dg(x)$.}
\label{fig:bullock}
\end{figure}

\section{Cavalieri integral}
Let $a(y)$ be a translational function with respect to a function $f(x)$ on the interval $[a,b]$. Moreover, $b(y) := a(y) + (b-a)$. Furthermore, the functions $a(y)$ and $b(y)$ intersect $f(x)$ at $a'$ and $b'$ respectively.
These assertions are assumed to be true throughout the paper and will not be repeated again.

\begin{definition}
A continuous real-valued function $a(y)$ is called a translational function with respect to a continuous real-valued function $f(x)$ on the interval $[a,b]$ if 
$\{x\in\mathbb{R}|a\circ f(x) + z = x\}$ is a singleton, for every $z\in[0,b-a]$ and $a(0) = a$.
\end{definition}

\begin{definition}
The mapping $h : [a, b] \rightarrow [a',b']$, which maps $x_i^1 \in [a, b]$ to $x_i^2 \in [a',b']$, is defined as
$h(x_i^1) :=$ $\{x_i^2 \in [a' ,b'] | a\circ f(x_i^2) + [x_i^1 - a] = x_i^2$ , $a = a(0)\}$, which we will refer to
as the transformation function. 
\end{definition}

\noindent
It can easily be shown that $h(x)$ is a strictly monotone continuous function. It is therefore also bijective.

\begin{definition}
The mapping $g:[a′, b′] \rightarrow [a, b]$, which maps $x_i^2 \in [a' , b']$ to $x_i^1\in [a, b]$,
is defined as $g(x_i^2) := x_i^2 - a \circ f (x_i^2) + a$, which we will refer to as the inverse
transformation function. 
\end{definition}

\noindent
Note, that $g = h^{-1}$ per definition. Moreover $g$ is guaranteed to exists, since $h$ is bijective.

\begin{definition}
Define a partition $\mathcal{P}_1$ of $[a,b]$ to be a set of points $x_0, x_1,\cdots,x_n$, 
where $a = x_0^1 \leq x_1^1 \leq \cdots \leq x_n^1 = b$. For each partition 
$\mathcal{P}_1$ of $[a,b]$ write $\Delta x_k = x_k-x_{k-1}$. 
%Since both boundaries of any integration strip are necessarily
%translations of the translational function $a(y)$, we can apply the transformation
%function $h$ to the partition $\mathcal{P}_1$. 
If the transformation function $h$ is strictly increasing,
the application of $h$ to the partition $\mathcal{P}_1$ induces a new partition $\mathcal{P}_2 = \{x_0^2, x_1^2,\cdots, x_n^2\}$.
Otherwise, if $h$ is strictly decreasing, the application of $h$ induces a reversed partition $\mathcal{P}_2 = \{x_n^2, \cdots, x_1^2,x_0^2\}$. In the rest of this paper
we will assume that $h$ is strictly increasing, without any loss of generality.  Let 
$M_k = \sup \{f (x), h(x_{i-1}^1) = x_{i-1}^2 \leq x \leq x_i^2 = h(x_i^1)\}$, $m_k = \inf \{f (x), h(x_{i-1}^1) = x_{i-1}^2 \leq x \leq x_i^2 = h(x_i^1)\}$, and set 
\begin{equation}
\label{eq:c_up}
\mathcal{C}_U(\mathcal{P}_1,f,h) = \sum_{k=1}^n M_k \Delta x_k, 
\end{equation}
and
\begin{equation}
\label{eq:c_low}
\mathcal{C}_L(\mathcal{P}_1,f,h) = \sum_{k=1}^n m_k \Delta x_k. 
\end{equation}
The sums in Eq.~\eqref{eq:c_up} and Eq.~\eqref{eq:c_low} are respectively called the the upper and lower Cavalieri sums.
If there is a unique number $I$ that satisfies the inequality $\mathcal{C}_L(\mathcal{P}_1,f,h)\leq I \leq \mathcal{C}_U(\mathcal{P}_1,f,h)$ for all 
partitions $\mathcal{P}_1$ of $[a,b]$, then $I$ is called the Cavalieri integral of $f$ from $a(y)$ to $b(y)$ and is denoted by
\begin{equation}
\int_{a(y)}^{b(y)} f(x) dx.
\end{equation}
\end{definition}

\begin{theorem}
The following Cavalieri, Riemann and Riemann-Stieltjes integrals are equivalent
\begin{equation}
\int_{a(y)}^{b(y)} f(x) dx = \int_a^b f\circ h(x) dx = \int_{a'}^{b'} f(x)dg(x). 
\end{equation}
\end{theorem}

\begin{remark}
Note that the definition of the Cavalieri integral as presented above imposes much stricter requirements on $f$ and $g$ than the 
definition of the Riemann-Stieltjes integral does. To ensure consistency, we will assume, from here onwards and unless stated otherwise, that the stricter requirements imposed 
by the Cavalieri definition is now also binding on the Riemann-Stieltjes integral. Remember the main aim of the paper is to 
help students develop a geometric intuition for the Riemann-Stieltjes integral that will be valid for most of the 
Riemann-Stieltjes integral problems that students will encounter during their undergraduate studies and not to present a complete geometric framework 
that will remain valid for each and every possible Riemann-Stieltjes integral. This is not to say that the geometric interpretation presented here cannot be used to provide 
insight to a broad range of problems. In the example section we show that Cavalieri sums can provide meaningful insights even 
when we relax some of the strict restrictions imposed by the above definitions.
\end{remark}

\subsection{Clarifying Example}

Consider the region $R$ bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$. This region is shown in Fig.~\ref{fig:ex1}.\\
\begin{figure}[htb]
\centering
\includegraphics[width=0.36\textwidth]{fig12}
\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$.}
\label{fig:ex1}
\end{figure}

\noindent
Instead of trying to determine the area of $R$ using rectangular integration strips, it seems more natural 
to use integration strips whose sides are translations of $a(y)$. Cavalieri's principle tells us that the area of an 
arbitrary shaped integration strip is the product of its height and the length of its base. The area of $R$ 
can be approximated by summing together multiple non-rectangular integration strips that inscribe $R$. This concept is illustrated in Fig.~\eqref{fig:caval2}. 
More formally, consider a partition $(x_i^1)_{i=0}^{n}$, on the $x$-axis, such that $a = x_0^1 < x_1^1 < \cdots < x_n^1 = b$, and $\Delta x_i^1 = x_{i+1}^1 - x_i^1$.
%As Fig.~\ref{fig:caval2} illustrates, the partition points $x_i^1$ are chosen to coincide with the $x$-coordinates at which the sides of the 
%integration strips intersect the $x$-axis. Fig.~\ref{fig:caval2} also shows us that another partition $(x_i^2)_{i=0}^{n}$, on the $x$-axis, such that $a' = x_0^2 < x_1^2 < \cdots < x_n^2 = b'$
%is automatically created when we make use of non-rectangular integration strips. The partition points $x_i^2$ 
%coincide with the $x$-coordinates at which the sides of the 
%integration strips intersect $f(x)$. 
Let us now construct the following sum (i.e. a lower Cavalieri sum) with which we can approximate the area 
of $R$:
\begin{equation}
\label{eq:cav_sum}
\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1.
\end{equation}
The partition points $(x_i^2)_{i=0}^{n}$ are depicted in Fig.~\ref{fig:caval2}.
The above sum can be interpreted as summing together the areas associated with $n$ non-rectangular integration strips.
The left panel of Fig.~\ref{fig:caval2} depicts the scenario in which we made use of three integration strips.  
The right panel of Fig.~\ref{fig:caval2} illustrates that the larger $n$ becomes the better Eq.~\eqref{eq:cav_sum} approximates the area of $R$. In the limit Eq.~\eqref{eq:cav_sum} approaches the Cavalieri integral
\begin{equation}
\label{eq:caval1}
\int_{a(y)}^{b(y)}f(x)\, dx = \lim_{n\to \infty}\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1.
\end{equation}

\begin{figure}[htb]
\centering
\includegraphics[width=0.92\textwidth]{fig13}
\caption{Partition points $x_i^2$ as used in the Cavalieri sum.}
\label{fig:caval2}
\end{figure}

\noindent
It is however hard to evaluate Eq.~\eqref{eq:caval1} in its present form. Luckily we can transform the Cavalieri sum given in Eq.~\eqref{eq:caval1} into an ordinary Riemann sum
if we can determine an expression for $x_i^2$ in terms of the partition points $x_i^1$, for all $i=0,1,\ldots,n$. Consider the collection of functions $\{a(y) + [x_i^1-a] = x_i^2: i=0,1,\ldots,n\}$. To find the partition points $x_i^2$ in terms of $x_i^1$ we substitute the function $f(x_i^2)$ for $y$ to obtain:
\begin{align*}
a\circ f (x_i^2)+[x_i^1-1] &= x_i^2\\
x_i^2 &= \dfrac{x_i^1}{2},
\end{align*}
so that we have the general expression $x_i^2=h(x_i^1)$, with $h(x)=x/2$.\\

\noindent
The function $h$ allows us to rewrite the Cavalieri integral as an equivalent Riemann integral:
\begin{equation}
\label{eq:h_int}
\lim_{n\to \infty}\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1 =  \lim_{n\to \infty}\sum_{i=0}^{n-1} f \circ h (x_i^1)\Delta x_i^1 = \int_a^b f \circ h (x)\, dx.
\end{equation}

\noindent
It is now possible to compute the Cavalieri integral by evaluating its equivalent Riemann integral:
\begin{equation}
\int_{a(y)}^{b(y)}f(x)\, dx = \int_a^b f \circ h (x)\, dx = \dfrac{1}{2}\int_1^4x\, dx = 3.75.  
\end{equation}

\noindent
Interestingly, the function $g=h^{-1}$ allows us to rewrite the Cavalieri integral as an equivalent Riemann-Stieltjes integral:
\begin{equation}
\label{eq:g_int}
\lim_{n\to \infty}\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1 =  \lim_{n\to \infty} \sum_{i=0}^{n-1} f(x_i^2)[g(x_{i+1}^2)-g(x_{i}^2)] = \int_{a'}^{b'} f \, dg(x). 
\end{equation}

\noindent
We can therefore also compute the Cavalieri integral by evaluating its equivalent Riemann-Stieltjes integral:
\begin{equation}
\int_{a(y)}^{b(y)}f(x)\, dx = \int_{a'}^{b'} f \, dg(x) = \int_{\frac{1}{2}}^2x\, d2x = 3.75.  
\end{equation}

\noindent
We can quickly verify this to be correct by evaluating the area of $R$ with ordinary Riemann integration:
\begin{equation}
\int_0^2x\, dx+\int_2^44-x\, dx- \int_0^{\frac{1}{2}}x\, dx-\int_{\frac{1}{2}}^11-x\, dx = 3.75. 
\end{equation}

%Now consider the Riemann-Stieltjes integral: $\int_{a'}^{b'} f(x) dg(x)$. 
%In this figure $f(x) = x$, $g(x) = 2x$, $h(x) = \frac{1}{2}x$ and $a(y)=1-y$.

\section{2D Geometric Interpretation}
\begin{figure}[htb]
\centering
\includegraphics[width=1\textwidth]{fig13_change}
\caption{A sum-based 2D geometric interpretation of the Riemann-Stieltjes integral. Moreover, the figure depicts the region $R$ (also see Fig.~). The integrator $g$ maps points 
in $[a',b']$ (depicted in blue) to points in $[a,b]$ (depicted in green). The function $h$ performs the reverse operation. Moreover, $g$ maps the $x$-coordinates at which
translations of $a(y)$ (depicted in red) intersect with $f(x)$ to the $x$-intercepts of the translated functions. This observation enables us to interpret the Riemann-Stieltjes integral as an infinite sum of infinitesimally small non-rectangular integration 
strips.}
\label{fig:2d_geo}
\end{figure}
%\begin{equation}
%\label{eq:cal_def_2D}
%\int_{a(y)}^{b(y)}fdx =\lim_{n\to \infty}\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1,
%\end{equation}
%and that
%\begin{equation}
%\label{eq:rs_def_g}
%\int_{a'}^{b'} f \, dg(x) = \lim_{n\to \infty} \sum_{i=0}^{n-1} f(x_i^2)[g(x_{i+1}^2)-g(x_{i}^2)].
%\end{equation}
%Fig.~\ref{fig:2d_geo} depicts a region whose area can be determined by considering non-rectangular integration strips.
%. Note that the shape of the integration strips are determined by $a(y)$. 
%In Fig.~\ref{fig:2d_geo}, the function $a(y)$ is depicted in red. If we translate $a(y)$ along the $x$-axis we actually create two partitions on the $x$-axis, 
%i.e. $(x_i^1)_{i=0}^{n}$ and $(x_i^2)_{i=0}^{n}$ with $x_i^1\in[a,b]$ and $x_i^2\in[a',b']$.  To map partition points in $[a',b']$ to partition points 
%in $[a,b]$ we use the function $g$. The reverse is achieved through $h$. The functions $g$ and $h$ depend soly on $a(y)$ and are also 
%computed with it.
Consider the definition of the Riemann-Stieltjes integral and 
Eq.~\eqref{eq:g_int}. For the sake of continiuty we repeat Eq.~\eqref{eq:g_int} below:
\begin{equation}
\label{eq:g_int2}
\int_{a'}^{b'} f(x) dg(x) =  \lim_{n \rightarrow \infty}\sum_{i=0}^{n-1} f(x_i^2)[g(x_{i+1}^2)-g(x_{i}^2)]. 
\end{equation}
Eq.~\eqref{eq:g_int2} tells us that the function of the integrator $g$ is to map points in the interval $[a',b']$ to other 
locations on the $x$-axis. When, $g$ is monotone increasing it maps points in the interval $[a',b']$ to $[a,b]$,
with $a = g(a')$ and $b = g(b')$.\\

\noindent
To improve our understanding of $g$ lets explore a specific example of the Riemann-Stieltjes integral: 
\begin{equation}
\int_{\frac{1}{2}}^1 x~d2x. 
\end{equation}
In this example $g$ maps $[\frac{1}{2},2]$ to $[1,4]$. The mapping between these two intervals is graphically 
depicted in Fig.~\ref{fig:2d_geo}. Moreover, the interval $[\frac{1}{2},2]$ is depicted in blue,
while the interval $[1,4]$ is depicted in green.\\

\noindent
Furthermore, consider $a(y) = 1-y$ (depicted in red in Fig.~\ref{fig:2d_geo}). Interestingly, the integrator $g$ maps the $x$-coordinates where translations of $a(y)$ and $f(x)$ intersect to the $x$-intercepts of the translations of $a(y)$.
The implications of this observation is the following: 
\begin{itemize}
 \item $g(x_{i+1}^2)-g(x_{i}^2)$ represents the length of the base of a non-rectangular integration strip.
 \item $f(x_i^2)$ is the height of a non-rectangular integration strip.
 \item $f(x_i^2)[g(x_{i+1}^2)-g(x_{i}^2)]$ is the area of a non-rectangular integration strip (due to Cavalieri's principle).
 \item The Riemann-Stieltjes sum, i.e. $\sum_{i=0}^{n-1} f(x_i^2)[g(x_{i+1}^2)-g(x_{i}^2)]$, is equal to the area obtained by summing together the area of multiple 
 integration strips.
 \item In the limit the Riemann-Stieltjes sum approaches the area of $R$. 
\end{itemize}
The Riemann-Stieltjes integral, can therefore, be interpreted as the area which is obtained, by summing together the areas of an infinite number of infinitesimally small non-rectangular integration strips,
i.e. a Riemann-Stieltjes integral can be converted into an equivalent Cavalieri integral. Note, that the geometric interpretation presented
in Fig.~\ref{fig:2d_geo} is two dimensional.\\

%Consider Fig.~\ref{fig:2d_geo}, whilst keeping in mind the definition of the Riemann-Stieltjes integral presented in 
%Eq.~\eqref{eq:g_int}. For the sake of continiuty we repeat this definition below:
%\begin{equation}
%\label{eq:g_int2}
%\int_{a'}^{b'} f(x) dg(x) =  \lim_{n \rightarrow \infty}\sum_{i=0}^{n-1} f(x_i^2)[g(x_{i+1}^2)-g(x_{i}^2)]. 
%\end{equation}
%Fig.~\ref{fig:2d_geo} depicts the same region we used to explain the Cavalieri integral a bit better (see Fig.~{}).\\

%\noindent
%In light of the above equation and Fig.~\ref{fig:2d_geo}, how then should we interpret the Riemann-Stieltjes integral of $f$ 
%with respect to $g$ over the interval $[a',b]$? Eq.~\eqref{eq:g_int2} tells us that the function of the integrator $g$ is to map points in the interval $[a',b']$ to other 
%locations on the $x$-axis. When, $g$ is monotone increasing it maps points in the interval $[a',b']$ to $[a,b]$,
%with $a = g(a')$ and $b = g(b')$. For the specific example presented in Fig.~\ref{fig:2d_geo}, we can actually go one step 
%further. The integrator $g$ maps the $x$-coordinates where translations of $a(y)$ and $f(x)$ intersect to the $x$-intercepts of the translated functions intersect the $x$-axis.
%The implications of this assertion is the following: 
%\begin{itemize}
% \item $g(x_{i+1}^2)-g(x_{i}^2)$ represents the length of the base of a non-rectangular integration strip.
% \item $f(x_i^2)$ is the height of a non-rectangular integration strip.
% \item $f(x_i^2)[g(x_{i+1}^2)-g(x_{i}^2)]$ is the area of a non-rectangular integration strip (due to Cavalieri's principle).
% \item The Riemann-Stieltjes sum, i.e. $\sum_{i=0}^{n-1} f(x_i^2)[g(x_{i+1}^2)-g(x_{i}^2)]$, is equal to the area obtained by summing together the area of multiple 
% integration strips.
% \item In the limit the Riemann-Stieltjes sum approaches the area of $R$. 
%\end{itemize}
%The Riemann-Stieltjes integral, can therefore, be interpreted as the area which is obtained, by summing together the areas of an infinite number of infinitesimally small non-rectangular integration strips,
%i.e. a Riemann-Stieltjes integral can be converted into an equivalent Cavalieri integral.\\

\noindent
The geometric interpretation provided above was possible due to the fact that the function $a(y)$
was known to us a priori. In general $a(y)$ will be unknown. Below we discuss how $a(y)$ can be computed.\\

%the Riemann-Stieltjes sumthe Riemann-Stieltjes 
%In the original Cavalieri paper only the forward direction is discussed: given $a(y)$ how do we obtain $g(x)$. Being able to 
%go in the other direction is crucial if we wish to provide a geometric interpretation of the Riemann-Stieltjes integral using an infinite sum.
%Below we address this short-coming.\\

\noindent
For all $C \in \mathbb{R}$ we have that
\begin{equation}
\label{eq:rs_C}
\int_{a'}^{b'} f(x)dg(x) = \int_{a'}^{b'} f(x)d[\widetilde{g}(x)+C], 
\end{equation}
with $g(x) := \widetilde{g}(x)+C$. 
Moreover, 
\begin{equation}
\label{eq:g_x_start}
g(x) =  x - a\circ f(x) + a.
\end{equation}
It would seem that we are unable to calculate $a(y)$, since we do not know the value 
of $a$ nor $C$ a priori. However, we do know that 
\begin{equation}
g(a') = \widetilde{g}(a') + C = a \implies C = a - \widetilde{g}(a'). 
\end{equation}
If we substitute $C$ with $a - \widetilde{g}(a')$ in Eq.~\eqref{eq:g_x_start} we eliminate both $C$ and $a$ from it. This 
substitution results in
\begin{equation}
\widetilde{g}(x) - \widetilde{g}(a') =  x - a\circ f(x).
\end{equation}
The above equation can be rewritten as
\begin{equation}
a\circ f(x) = x - \widetilde{g}(x) + \widetilde{g}(a').   
\end{equation}
If we now substitute $x$ with $f^{-1}(y)$ we obtain an expression for $a(y)$
\begin{equation}
a(y) = f^{-1}(y) - \widetilde{g}\circ f^{-1}(y) + \widetilde{g}(a').   
\end{equation}

\noindent
Once we have an expression for $a(y)$ we can trivially compute the following values and expressions:
\begin{itemize}
 \item Compute $a = a(0)$.
 \item Compute $C = a - \widetilde{g}(a')$.
 \item Compute $b = g(b')$ and $b(y) = a(y) + (b-a)$.
 \item Compute $h(x) = g^{-1}(x)$. 
\end{itemize}
Note that the above procedure places an even stricter requirement of $f$, it now also needs to be invertable. Moreover the 
above derivation aslo requires that $a(0)$ exists.

%\noindent
%The above values and expressions enable us to convert Eq.~\ref{eq:rs_C} into a Cavalieri integral, i.e. 
%\begin{equation}
%\int_{a'}^{b'} f(x)dg(x) = \int_{a(y)}^{b(y)} f(x) dx. 
%\end{equation}
%\noindent
%The implication being, that the Riemann-Stieltjes integral can be interpreted as an infinite sum of infinitesimally small integration strips.
%The integration strips are however not rectangular as is the case for an ordinary Riemann integral, but have a shape which is determined by the function $a(y)$.

\section{Examples}
A couple of Riemann-Stieltjes integrals are given in Table~\ref{tab:table1}. The $a(y)$ functions associated 
with these Riemann-Stieltjes integrals are presented in the same table and were computed using the method 
described in the previous section. The Riemann-Stieltjes integrals were also evaluated using both $g$ and $h$ and the result
thereof is reported in Table~\ref{tab:table2}. The 2D sum-based geometric interpretations of the integrals in Table~\ref{tab:table1}, the $a(y)$ functions provide, are depicted in Figs.~\ref{fig:ex1_sec}--\ref{fig:ex4_sec}.\\

\noindent
In Fig.~\ref{fig:ex1_sec} we plot the geometric interpretation of $\int_{1}^3 (2x+8)^3 d[x^2-20]$. This same figure also 
provides a geometric interpretation of $\int_{1}^3 (2x+8)^3 dx^2$ albeit a less intuitive one. The $a(y)$ function need not 
produce a mapping $g$ from $[1,3]$ to $[-19,-11]$. It can also produce a mapping $\widetilde{g}$ from $[1,3]$ to $[1,9]$. In both cases the 
depiction remains valid, however, in the case of $\widetilde{g}$ the lengths of the bases of the depicted integration strips are not 
computed on the $x$-axis itself, but rather on the line $y=1000$. The fact that the 2D sum-based geometric framework remains useful even if $g(a')\neq a$ is true in general.\\

\noindent
In Fig.~\ref{fig:ex2_sec} we depict the geometric interpretation of $\int_1^2 \frac{1}{x} d[x^2+C]$. This example is a bit of a special case, since $a(0)$ does not exist. 
However, the 2D sum-based geometric framework does produce a meaningful result.\\

\noindent
One of the main limitations of the 2D geometric interpretation we present in this paper is that both $f$ and $g$ need to be invertible.
Being invertible is however not that big of a limitation if we take the following into account. We can always split a Riemann-Stieltjes
integral whose integrand and integrator are not invertable over its integratrion limits into multiple constittuent Riemann-Stieltjes integrals whose 
integrand and integrator are invertable over the integration limits of the consitutent integrals. For example, say 
$f$ and $g$ are not invertabal over the interval $[a',b']$, but are invertable over the inervals $[a',c']$ and 
$[c',b']$ then we may write:
\begin{equation}
\int_{a'}^{b'}f(x)dg(x) = \int_{a'}^{c'}f(x)dg(x) + \int_{c'}^{b'} f(x)dg(x).
\end{equation}
This allows us to to find a 2D sum-based geometric interpretation of $\int_{a'}^{c'}f(x)dg(x)$ and $\int_{c'}^{b'} f(x)dg(x)$
which we can combine to give a geometric interpretation of $\int_{a'}^{b'}f(x)dg(x)$.
In Fig.~\ref{fig:ex4_sec} we present just such a scenrio. In this example $g(x)$ is not invertible over the interval 
$[0,2]$. It is however invertible over the interval $[0,1]$ and $[1,2]$. The geometric interpretation whic we 
obtain by considering the intervals $[0,1]$ and $[1,2]$ seperately is depicted, respectively, in the 
right and left panel of Fig.~\ref{fig:ex4_sec}.

%Moreover, Fig to Fig. illustrates that $g:[a',b']\rightarrow[a,b]$ simply maps partition points 
%between $a'$ and $b'$ to partition points between $a$ and $b$, i.e. $\Delta g$ (differences between partition points between
%$a'$ and $b'$ after $g$ was applied) need not be interpreted as an arbitrary length, but can be interpreted as the base length of a non-rectangular integration strip.
%Since the Riemann-Stieltjes integral is evaluated between $a'$ and $b'$ we can interpret $f$ evaluated at 
%partition points between $a'$ and $b'$ as the height of non-rectangular integration strips. Multiplying The depicted Cavalieri sums, 
%are therefore, also Riemann-Stieltjes sums:

\begin{table}[h!]
\centering
\caption{Different Riemann-Stieltjes examples: $\int_{a'}^{b'}f(x)\widetilde{g}(x)$. The table also contains the $a(y)$ functions 
associated with these integrals. The 2D sum-based geometric interpretations of the integrals, the $a(y)$ functions provide, are depicted in Figs.~\ref{fig:ex1_sec}--\ref{fig:ex4_sec}.
The results of evaluaing these integrals are presented in Table~\ref{tab:table2}.
}
\label{tab:table1}
\begin{tabular}{|c|c|c|c|c||c|c|} 
 Number &$f(x)$ & $\widetilde{g}(x)$&$a'$&$b'$&$f^{-1}(y)$&$a(y)$\\
 \hline
 \hline
 Ex. 1 &$(2x+8)^3$&$x^2$&$1$&$3$&$\frac{\sqrt[3]{y} - 8}{2}$&$-\frac{1}{4}\sqrt[3]{y^2} + \frac{9}{2}\sqrt[3]{y} - 19$\\
 Ex. 2 &$\sin(x)$&$\cos(x)$&$\frac{-\pi}{2}$&$0$&$\sin^{-1}(y)$&$\sin^{-1}(y)-\sqrt{1-y^2}$\\ 
 Ex. 3 &$\frac{1}{x}$&$x^2$&$1$&$2$&$\frac{1}{y}$&$\frac{y^2+y-1}{y^2}$\\
 Ex. 4 &$x^2$&$x-\frac{1}{2}x^2$&$2$&$1$&$\sqrt{y}$&$\frac{1}{2}y$\\
 Ex. 5 &$x^2$&$x-\frac{1}{2}x^2$&$0$&$1$&$\sqrt{y}$&$\frac{1}{2}y$
 \end{tabular}
\end{table}

\begin{table}[h!]
\centering
\caption{The results of evaluating the Riemann-Stieltjes integrals in Table~\ref{tab:table1} are presented in the last column of this table. Both $g$ and $h$ were used to 
evaluate these integrals. The constants $a,b$ and $C$ associated with these integrals are also presented. Moreover, $h_1(x) = 2\sqrt{x+20}+8$, $h_2(x)=\sin(-\cos^{-1}(x+1))$, $h_3(x)=\sqrt{x-C}$, $h_4(x)=1+\sqrt{1-2x}$ and
$h_5(x)=1-\sqrt{1-2x}$.}
\label{tab:table2}
\begin{tabular}{|c|c||c|c|c||c|c|c|} 
 Number &$f(x)$&$a$&$b$&$C$&$g(x)$&$h(x)$&$\int$\\
 \hline
 \hline
 Ex. 1 &$(2x+8)^3$&$-19$&$-11$&$-20$&$x^2-20$&$h_1(x)$&$\frac{76832}{5}$\\
 Ex. 2 &$\sin(x)$&$-1$&$0$&$-1$&$\cos(x)-1$&$h_2(x)$&$\frac{-\pi}{4}$\\
 Ex. 3 &$\frac{1}{x}$&$-\infty$&$a+3$&$a-1$&$x^2+C$&$h_3(x)$&$2$\\
 Ex. 4 &$x^2$&$0$&$\frac{1}{2}$&$0$&$x-\frac{1}{2}x^2$&$h_4(x)$&$\frac{17}{12}$\\
 Ex. 5 &$x^2$&$0$&$\frac{1}{2}$&$0$&$x-\frac{1}{2}x^2$&$h_5(x)$&$\frac{1}{12}$\\
 \end{tabular}
\end{table}

 \begin{figure}[htb]
 \centering
 \includegraphics[width=1.0\textwidth]{EX1-crop.pdf}
 \caption{The sum-based 2D geometric interpretation of $\int_{1}^3 (2x+8)^3 d[x^2-20]$ (i.e this integral is equal to the 
 Cavalieri integral $\int_{a(y)}^{b(y)} (2x+8)^3 dx$).}
 \label{fig:ex1_sec}
 \end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=1.0\textwidth]{EX2-crop.pdf}
\caption{The sum-based 2D geometric interpretation of $\int_{\frac{-\pi}{2}}^0 \sin{x}~d[\cos{x}-1]$ (i.e this integral integral is equal to the 
 Cavalieri integral $\int_{a(y)}^{b(y)} \sin{x} dx$).}
\label{fig:ex2_sec}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=1.0\textwidth]{EX3-crop.pdf}
\caption{The sum-based 2D geometric interpretation of $\int_1^2 \frac{1}{x} d[x^2+C]$ (i.e this integral integral is equal to the 
 Cavalieri integral $\int_{a(y)}^{b(y)} \frac{1}{x} dx$).}
\label{fig:ex3_sec}
\end{figure}

\begin{figure}
\centering
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig20b.pdf}
  %\captionof{figure}{A figure}
  %\label{fig:test1}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig20c.pdf}
  %\captionof{figure}{Another figure}
  %\label{fig:test2}
\end{minipage}
\caption{In the left panel we have the area associated with the integral $\int_2^1 x^2~d[x-\frac{1}{2}x^2]$, while in the 
right panel we have the area associated with the integral $\int_0^1 x^2~d[x-\frac{1}{2}x^2]$. This example deomonstrates
that the geometric framework presented in this paper does provide a geometric interpretation for the Riemann-Stieltjes integral
even when $f$ and $g$ are only piece-wise invertable.}
\label{fig:ex4_sec}
\end{figure}

\section{Conclusion}
A two dimensional geometric interpretation of the Riemann-Stieltjes integral was presented in this paper. We can summarize this 
interpretation as follows: a Riemann-Stieltjes integral can be interpreted as an infinite sum of initesimally small non-rectangular 
integration strips. The hope is that this geometric interpretation will be usefull to instructors while teaching some of the more difficult concepts 
surrounding the Riemann-Stieltjes integral.

\noindent
The \textit{American Mathematical Monthly} style incorporates the following \LaTeX\ packages.  These styles should \textit{not} be included in the document header.
\begin{itemize}
\item times
\item pifont
\item graphicx
\item color
\item AMS styles: amsmath, amsthm, amsfonts, amssymb
\item url
\end{itemize}
Use of other \LaTeX\ packages should be minimized as much as possible. Math notation, like $c = \sqrt{a^2 +b^2}$, can be left in \TeX's default Computer Modern typefaces for manuscript preparation; or, if you have the appropriate fonts installed, the \texttt{mathtime} or \texttt{mtpro} packages may be used, which will better approximate the finished article.

Web links can be embedded using the \verb~\url{...}~ command, which will result in something like \url{http://www.maa.org}.  These links will be active and stylized in the online publication.

\section{First-level section heading.}

Section headings use an initial capital letter on the first word, with subsequent words lowercase.  In general, the style of the journal is to leave all section headings unnumbered.  Consult the journal editor if you wish to depart from this and other conventions.

\subsection{Second-level heading.}

The same goes for second-level headings.  It is not necessary to add font commands to make the math within heads bold and sans serif; this change will occur automatically when the production style is applied.

\section{Graphics.}

Figures for the \textsc{Monthly} can be submitted as either color or black \& white graphics.  Generally, color graphics will be used for the online publication, and converted to black \& white images for the print journal.  We recommend using whatever graphics program you are most comfortable with, so long as the submitted graphic is provided as a separate file using a standard file format.

For best results, please follow the following guidelines:
\begin{enumerate}
\item Bitmapped file formats---preferably TIFF or JPEG, but not BMP---are appropriate for photographs, using a resolution of at least 300 dpi at the final scaled size of the image.
\item Line art will reproduce best if provided in vector form, preferably EPS.
\item Alternatively, both photographs and line art can be provided as PDF files.  Note that creating a PDF does not affect whether the graphic is a bitmap or vector; saving a scanned piece of line art as PDF does not convert it to scalable line art.
\item If you generating graphics using a \TeX\ package, please be sure to provide a PDF of the manuscript.  In the production process, \TeX-generated graphics will eventually be converted to more conventional graphics so the \textsc{Monthly} can be delivered in e-reader formats.
\item For photos of contributing authors, we prefer photos that are not cropped tight to the author's profile, so that production staff can crop the head shot to an equal height and width.  If possible, avoid photographs that have excess shadows or glare.
\end{enumerate}

\section{Theorems, definitions, proofs, and all that.}

Following the defaults of the \texttt{amsthm} package, styling is provided for \texttt{theorem}, \texttt{definition}, and \texttt{remark} styles, although the latter two use the same styling.

\begin{theorem}[Pythagorean Theorem]
Theorems, lemmas, axioms, and the like are stylized using italicized text. These environments can be numbered or unnumbered, at the author's discretion.
\end{theorem}

\begin{proof}
Proofs set in roman (upright) text, and conclude with an ``end of proof'' (q.e.d.) symbol that is set automatically when you end the proof environment.  When the proof ends with an equation or other non-text element, you need to add \verb~\qedhere~ to the element to set the end of proof symbol; see the \texttt{amsthm} package documentation for more details.
\end{proof}

\begin{definition}[Secant Line]
Definitions, remarks, and notation are stylized as roman text.  They are typically unnumbered, but there are no hard-and-fast rules about numbering.
\end{definition}

\begin{remark}
Remarks stylize the same as definitions.
\end{remark}

\begin{acknowledgment}{Acknowledgment.}
The authors wish to thank the Greek polymath Anonymous, whose prolific works are an endless source of inspiration.
\end{acknowledgment}

\begin{thebibliography}{1}
\bibitem{parker13} Adam Parker, Who solved the Bernoulli equation and how did they do it? \textit{Coll. Math. J.} \textbf{44} (2013) 89--97.

\bibitem{hopkins} Brian Hopkins, ed., \textit{Resources for Teaching Discrete Mathematics}, Mathematical Association of America, Washington DC, 2009.
\end{thebibliography}

\begin{biog}
\item[Woodrow Wilson] received his Ph.D. in history and political science from Johns Hopkins University. He held visiting positions at Cornell and Wesleyan before joining the faculty at Princeton, where he was eventually appointed president of the university.  Among his proudest accomplishments was the abolition of eating clubs at Princeton on the grounds that they were elitist.
\begin{affil}
Office of the President, Princeton University, Princeton NJ 08544\\
twoodwilson@princeton.edu
\end{affil}

\item[Herbert Hoover] entered Stanford University in 1891, after failing all of the entrance exams except mathematics.  He received his B.S. degree in geology in 1895, spent time as a mining engineer, then was appointed by his co-author to the U.S. Food Administration and the Supreme Economic Council, where he orchestrated the greatest famine relief efforts of all time.
\begin{affil}
Hoover Institution, Stanford University, Stanford CA 94305\\
herbhoover@stanford.edu
\end{affil}
\end{biog}
\vfill\eject

\end{document}

### 2017-11-03 func_plotter.py

@@ -1,0 +1,85 @@
+import numpy as np
+import scipy as sp
+import pylab as plt
+
+def func_ex1(x):
+    y = (2*x+8)**3
+    return y
+
+def a_ex1(y):
+    x = -0.25*y**(2.0/3.0) + 9.0/2.0*y**(1.0/3.0) - 19
+    return x
+
+def a_ex2(y):
+    x = -0.25*y**(2.0/3.0) + 9.0/2.0*y**(1.0/3.0) - 11
+    return x
+
+
+
+if __name__ == "__main__":
+   import matplotlib
+   matplotlib.rcParams.update({'font.size': 16})
+   fig,ax = plt.subplots()
+   x = np.linspace(-19,9,1000)
+   y = func_ex1(x) 
+   ax.plot(x,y,'k')
+   y1 = np.linspace(0,3000,5000)
+   x1 = a_ex1(y1)
+   x2 = a_ex2(y1)
+   ax.plot(x1,y1,'k')
+   x1 = a_ex1(y1)
+   ax.plot(x2,y1,'k')
+   plt.title("$f(x) = (2x+8)^3$")
+
+   ax.annotate('$f(x)$',
+            xy=(0, 520), xycoords='data',
+            xytext=(-20,0), textcoords='offset points',
+            arrowprops=dict(arrowstyle="->",facecolor='black'),
+            horizontalalignment='right', verticalalignment='bottom') 
+
+   ax.annotate('$a(y)$',
+            xy=(-2, 2000), xycoords='data',
+            xytext=(-20,0), textcoords='offset points',
+            arrowprops=dict(arrowstyle="->",facecolor='black'),
+            horizontalalignment='right', verticalalignment='bottom') 
+
+   ax.annotate('$b(y)$',
+            xy=(6, 2000), xycoords='data',
+            xytext=(20,0), textcoords='offset points',
+            arrowprops=dict(arrowstyle="->",facecolor='black'),
+            horizontalalignment='left', verticalalignment='bottom') 
+
+   ax.annotate('$a$',
+            xy=(-19, 0), xycoords='data',
+            xytext=(0,20), textcoords='offset points',
+            arrowprops=dict(arrowstyle="->",facecolor='black'),
+            horizontalalignment='right', verticalalignment='bottom')
+
+   ax.annotate('$b$',
+            xy=(-11, 0), xycoords='data',
+            xytext=(0,20), textcoords='offset points',
+            arrowprops=dict(arrowstyle="->",facecolor='black'),
[…]

### 2017-11-03 func_plotter2.py

@@ -1,0 +1,88 @@
+import numpy as np
+import scipy as sp
+import pylab as plt
+
+def func_ex1(x):
+    y = 1/x
+    return y
+
+def a_ex1(y):
+    x = (y**2+y-1)/y**2
+    return x
+
+def a_ex2(y):
+    x = (y**2+y-1)/y**2 + 3
+    return x
+
+
+
+if __name__ == "__main__":
+   import matplotlib
+   matplotlib.rcParams.update({'font.size': 16})
+   fig,ax = plt.subplots()
+   x = np.linspace(0.25,4,1000)
+   y = func_ex1(x) 
+   ax.plot(x,y,'k')
+   y1 = np.linspace(0.4,4,5000)
+   y2 = np.linspace(0.4,4,5000)
+   x1 = a_ex1(y1)
+   x2 = a_ex2(y2)
+   ax.plot(x1,y1,'k')
+   x1 = a_ex1(y1)
+   ax.plot(x2,y1,'k')
+   plt.xlim([-2.5,4.5])
+   plt.title("$f(x) = 1/x$")
+
+   
+   ax.annotate('$f(x)$',
+            xy=(0.5, 1.98), xycoords='data',
+            xytext=(-20,0), textcoords='offset points',
+            arrowprops=dict(arrowstyle="->",facecolor='black'),
+            horizontalalignment='right', verticalalignment='bottom') 
+
+   ax.annotate('$a(y)$',
+            xy=(1.21, 3.25), xycoords='data',
+            xytext=(-20,0), textcoords='offset points',
+            arrowprops=dict(arrowstyle="->",facecolor='black'),
+            horizontalalignment='right', verticalalignment='bottom') 
+
+   ax.annotate('$b(y)$',
+            xy=(4.2, 3.33), xycoords='data',
+            xytext=(-20,0), textcoords='offset points',
+            arrowprops=dict(arrowstyle="->",facecolor='black'),
+            horizontalalignment='right', verticalalignment='bottom') 
+
+   #ax.annotate('$a$',
+   #         xy=(-19, 0), xycoords='data',
+   #         xytext=(0,15), textcoords='offset points',
+   #         arrowprops=dict(arrowstyle="->",facecolor='black'),
+   #         horizontalalignment='right', verticalalignment='bottom')
+
+   #ax.annotate('$b$',
+   #         xy=(-11, 0), xycoords='data',
+   #         xytext=(0,15), textcoords='offset points',
[…]

### 2017-11-03 func_plotter3.py

@@ -1,0 +1,87 @@
+import numpy as np
+import scipy as sp
+import pylab as plt
+
+def func_ex1(x):
+    y = np.sin(x)
+    return y
+
+def a_ex1(y):
+    x = np.arcsin(y) - np.sqrt(1-y**2)
+    return x
+
+def a_ex2(y):
+    x = np.arcsin(y) - np.sqrt(1-y**2) + 1
+    return x
+
+
+
+if __name__ == "__main__":
+   import matplotlib
+   matplotlib.rcParams.update({'font.size': 16})
+   fig,ax = plt.subplots()
+   x = np.linspace(-np.pi/2,0,1000)
+   y = func_ex1(x) 
+   ax.plot(x,y,'k')
+   y1 = np.linspace(-1,0,5000)
+   #y2 = np.linspace(0.4,4,5000)
+   x1 = a_ex1(y1)
+   x2 = a_ex2(y1)
+   ax.plot(x1,y1,'k')
+   x1 = a_ex1(y1)
+   ax.plot(x2,y1,'k')
+   plt.title("$f(x) = sin(x)$")
+
+   
+   ax.annotate('$f(x)$',
+            xy=(-0.90, -0.79), xycoords='data',
+            xytext=(25,-10), textcoords='offset points',
+            arrowprops=dict(arrowstyle="->",facecolor='black'),
+            horizontalalignment='left', verticalalignment='bottom') 
+
+   ax.annotate('$a(y)$',
+            xy=(-1.32, -0.39), xycoords='data',
+            xytext=(-25,0), textcoords='offset points',
+            arrowprops=dict(arrowstyle="->",facecolor='black'),
+            horizontalalignment='right', verticalalignment='bottom') 
+
+   ax.annotate('$b(y)$',
+            xy=(-0.52, -0.79), xycoords='data',
+            xytext=(25,0), textcoords='offset points',
+            arrowprops=dict(arrowstyle="->",facecolor='black'),
+            horizontalalignment='left', verticalalignment='bottom') 
+
+   ax.annotate('$a$',
+            xy=(-1, 0), xycoords='data',
+            xytext=(-30,0), textcoords='offset points',
+            arrowprops=dict(arrowstyle="->",facecolor='black'),
+            horizontalalignment='left', verticalalignment='bottom')
+
+   ax.annotate("$b',b$",
+            xy=(0, 0), xycoords='data',
+            xytext=(0,-30), textcoords='offset points',
[…]

### 2017-11-03 func_plotter4.py

@@ -1,0 +1,104 @@
+import numpy as np
+import scipy as sp
+import pylab as plt
+import scipy.special
+
+def func_ex1(x):
+    y = x
+    return y
+
+def func_g_y(y,mu,sig):
+    x = 0.5*(1+scipy.special.erf((y-mu)/sig))
+    return x
+
+def a_ex1(y,mu=0.0,sig=1.0,a_p=0.5):
+    x = y - func_g_y(y,mu,sig) + func_g_y(a_p,mu,sig) 
+    return x
+
+def a_ex2(y,c,mu=0.0,sig=1.0,a_p=0.5):
+    x = y - func_g_y(y,mu,sig) + func_g_y(a_p,mu,sig) + c 
+    return x
+
+#
+#def a_ex2(y):
+#    x = np.arcsin(y) - np.sqrt(1-y**2) + 1
+#    return x
+
+if __name__ == "__main__":
+   a_0 = a_ex1(0,mu=0.0,sig=1.0,a_p=0.5)
+   print "a_0 = ",a_0
+
+   c = func_g_y(1.0,0,1.0) - func_g_y(0.5,0,1.0) 
+   print "c = ",c
+
+   C = a_0 - func_g_y(0.5,0,1.0)
+   print "C = ",C
+
+   fig,ax = plt.subplots()
+   x = np.linspace(0,1.5,1000)
+   y = func_ex1(x) 
+   ax.plot(x,y,'k')
+   y1 = np.linspace(-0.5,1.5,5000)
+   #y2 = np.linspace(0.4,4,5000)
+   x1 = a_ex1(y1)
+   print "x1 = ",x1
+   x2 = a_ex2(y1,c)
+   ax.plot(x1,y1,'k')
+   #ax.plot(x1,y1,'k')
+   #x1 = a_ex1(y1)
+   ax.plot(x2,y1,'k')
+   #plt.title("$f(x) = sin(x)$")
+
+   '''
+   ax.annotate('$f(x)$',
+            xy=(0, 520), xycoords='data',
+            xytext=(-15,0), textcoords='offset points',
+            arrowprops=dict(arrowstyle="->",facecolor='black'),
+            horizontalalignment='right', verticalalignment='bottom') 
+
+   ax.annotate('$a(y)$',
+            xy=(-2, 2000), xycoords='data',
+            xytext=(-15,0), textcoords='offset points',
+            arrowprops=dict(arrowstyle="->",facecolor='black'),
[…]

### 2017-11-03 wire3d_demo.py

@@ -1,0 +1,102 @@
+import numpy as np
+from mpl_toolkits.mplot3d import Axes3D
+import matplotlib.pyplot as plt
+import random
+
+def f_x(x,y):
+    return x**2
+
+def g_x(x,z):
+  return x
+
+fig = plt.figure()
+
+x_max = 3.0
+d = 0.05
+y_max = g_x(x_max,0)
+z_max = f_x(x_max,0)
+
+#PLOT SURFACES
+#PLOT f_x
+ax = fig.add_subplot(111, projection='3d')
+x = np.arange(0, x_max, d)
+y = np.arange(0, y_max, d)
+X, Y = np.meshgrid(x, y)
+
+zs = np.array([f_x(x,y) for x,y in zip(np.ravel(X), np.ravel(Y))])
+Z = zs.reshape(X.shape)
+ax.plot_surface(X, Y, Z,alpha=0.2)
+
+#PLOT g_x
+x = np.arange(0, x_max, d)
+z = np.arange(0, z_max, d)
+X, Z = np.meshgrid(x, z)
+ys = np.array([g_x(x,z) for x,z in zip(np.ravel(X), np.ravel(Z))])
+Y = ys.reshape(X.shape)
+ax.plot_surface(X, Y, Z,color="red",alpha=0.2)
+
+#PLOT CURVES
+x = np.arange(0, x_max, d)
+#PLOT PROJECTION
+ax.plot(np.zeros(x.shape),g_x(x,0),f_x(x,0),color="black")
+
+#PLOT INTERSECTION
+ax.plot(x,g_x(x,0),f_x(x,0),color="black",linestyle='dashed',linewidth=1)
+
+import matplotlib 
+#matplotlib.rc('xtick', labelsize=20) 
+#matplotlib.rc('ytick', labelsize=20) 
+matplotlib.rcParams.update({'font.size': 60})
+#matplotlib.rc('xlabel', labelsize=20)
+#matplotlib.rc('ylabel', labelsize=20)
+#matplotlib.rc('zlabel', labelsize=20)
+
+ax.set_xlabel('$x$')
+ax.set_ylabel('$g(x)$')
+ax.set_zlabel('$f(x)$')
+
+ax.view_init(30,220)
+
+plt.show()
+
+'''
+def fun(x, y):
+  return x**2
+
+def fun2(x, z):
+  return x
+
+fig = plt.figure()
[…]

### 2017-11-08 paper.tex
cav intro update

@@
 
-\title{A 2D Geometric Interpretation of the Riemann-Stieltjes Integral}
+\title{An Alternative Geometric Interpretation of the Riemann-Stieltjes Integral}
 \markright{Abbreviated Article Title}
@@
 \begin{abstract}
-It is desirable to have geometric interpretations for difficult mathematical ideas. In this paper we present an intiutive geometric interpretation of the Riemann-Stieltjes integral. It can be 
-summarized as follows: the Riemann-Stieltjes integral can be inerpreted as an infinite sum of initesimally small non-rectangular 
-integration strips. This interpretation is surprisingly similar to the geometric intrepretation of the ordinary Riemann integral. 
-It is therefore likely that this geometric interpretaion would narrow the logical rift between the Riemann integral and the Riemann-Stieltjes integral (i.e. make the 
+It is desirable to have geometric interpretations for difficult mathematical ideas. In this paper we present an intuitive geometric interpretation of the Riemann-Stieltjes integral. It can be 
+summarized as follows: the Riemann-Stieltjes integral can be inerpreted as an infinite sum of infinitesimally small non-rectangular 
+integration strips. This interpretation is surprisingly similar to the geometric interpretation of the ordinary Riemann integral. 
+It is therefore likely that this geometric interpretation would reduce the large jump 
+students experience when they first encounter the Riemann-Stieltjes integral (i.e. make the 
 Riemann-Stieltjes integral less abstract).
@@
 Providing a geometrical interpretation for a mathematical concept can greatly improve ones understanding of it. The Riemann-Stieltjes 
-integral is no exception. Bullock proposed a three dimensional geometric framework with which one can interpret the Riemann-Stieltjes 
-integral. Pol proposes to interpret the Riemann-Stieltjes integral as the real distance covered by a moving object, whose speed was 
-correctly recorded but at incorrect times. In this paper we present an intiutive two dimensional geometric interpretation of the Riemann-Stieltjes integral.\\
+integral is no exception. G.~Bullock proposed a projection-based geometric framework with which one can interpret the Riemann-Stieltjes 
+integral \cite{bullock1988}. Furthermore, I.~Podlubny proposed to interpret the Riemann-Stieltjes integral as the real distance covered by a moving object, whose speed was 
+correctly recorded but at incorrect times \cite{podlubny2002}. In this paper we present an alternative, more initiative, geometric interpretation of the Riemann-Stieltjes integral.\\
 
 \noindent
-?? utilized the idea of using non-rectangular integration strips to perform integration
-and in doing so developed the Cavalieri integral. The area of a non-rectangular integration strip is computed via 
-Cavalieri's principle.  also showed that a Cavalieri integral can easily be converted to a Riemann-Stieltjes integral. The 
-reverse operation was however not addressed therein. In this paper we address this shortcomming. An automatic consequence of being 
-able to convert a Riemann-Stieltjes integral to a Cavalieri integral is that a geometric interpretation of the Riemann-Stieltjes
-becomes evident. This geometric interpretation is: the Riemann-Stieltjes integral can be interpreted as an infinite sum of infinitesimally small
+Ackermann et al. utilized the idea of using non-rectangular integration strips to perform integration
+and in doing so developed the Cavalieri integral \cite{ackermann2012}. The area of a non-rectangular integration strip is computed via 
+Cavalieri's principle \cite{andersen1985,eves1991, malik1984, wildberger2002, young1985}. They also showed that a Cavalieri integral can easily be converted to a Riemann-Stieltjes integral. The 
+reverse operation was however not described in \cite{ackermann2012}. In this paper we address this shortcoming. This 
+reverse operation actually allows us to contrive a novel geometric interpretation of the Riemann-Stieltjes integral.
+This geometric interpretation is: the Riemann-Stieltjes integral can be interpreted as an infinite sum of infinitesimally small
 non-rectangular integration strips. Interestingly enough, this interpretation of the Riemann-Stieltjes integral is very similar 
@@
 rectangular instead of non-rectangular integration strips. This geometric interpretation has been quite useful while 
-theaching the ordinary Riemann integral to undergraduate students. It, therefore, seems likely that undergraduate students would find the non-rectangular geometric interpretation
-of the Riemann-Stieltjes integral just as useful. It is also interesting to mention that it has been proposed to first 
-teach other integral definitions (which are easier to grasp) before moving on to the Riemann integral. It therefore seems plausible that
-students will find it useful to first understand the Cavaleri integral before the Riemann-Stieltjes integral is taught to them.
+teaching the ordinary Riemann integral to undergraduate students \cite{jones2015,sealey2014}.
+It, therefore, seems likely that undergraduate students would find the non-rectangular geometric interpretation
+of the Riemann-Stieltjes integral just as useful. It is also interesting to mention, that there is a few papers in literature that proposes to first 
+teach simpler integral definitions (which are easier to grasp) before introducing students to the Riemann integral \cite{czarnocha2001,prabhu2008,ruffa2002,zaskis2014}.
+It therefore seems plausible that
+students will find it useful to first understand the Cavalieri integral before the Riemann-Stieltjes integral is taught to them.
 
@@
 
-\begin{thebibliography}{1}
-\bibitem{parker13} Adam Parker, Who solved the Bernoulli equation and how did they do it? \textit{Coll. Math. J.} \textbf{44} (2013) 89--97.
+\begin{thebibliography}{10}
+\bibitem{ackermann2012} 
+E.~R.~Ackermann, T.~L.~Grobler, W.~Kleynhans, J.~C.~Olivier, B.~P.~Salmon, A.~J.~van Zyl, \emph{Quaest. Math.} \textbf{35} (2012) 265--296.
 
-\bibitem{hopkins} Brian Hopkins, ed., \textit{Resources for Teaching Discrete Mathematics}, Mathematical Association of America, Washington DC, 2009.
+\bibitem{andersen1985}
+K.~Andersen, Cavalieri's Method of Indivisibles, \emph{Arch. Hist. Exact Sci.} \textbf{31} (1985) 291--367.
+
+\bibitem{bartle1976}
+R.~G Bartle, \emph{The Elements of Real Analysis}, New York: Wiley, 1976
+
+\bibitem{bullock1988}
+G.~L.~Bullock, A Geometric Interpretation of the Riemann-Stieltjes Integral, \emph{Amer. Math. Monthly} \textbf{95} (1988) 448--455.
+
+\bibitem{czarnocha2001} B. Czarnocha, E. Dubinsky S. Loch, V. Prabhu, D. Vidakovic, Conceptions of Area: In Students and in History. \emph{College Math. J.} \textbf{32} (2001) 99--109.
+
+\bibitem{eves1991}
+H.~Eves, Two Surprising Theorems on Cavalieri Congruence, \emph{College Math. J.} \textbf{22} (1991) 118--124.
+
+\bibitem{jones2015}
+S.~R.~Jones, Areas, Anti-Derivatives, and Adding Up Pieces: Definite Integrals in Pure Mathematics and Applied Science Contexts, \emph{J. Math. Behav.}
+\textbf{38} (2015) 9--28.
+
+\bibitem{malik1984}
+H.~A~Malik, A Note on Cavalieri Integration, \emph{Math. Mag.} \textbf{57} (1984) 154--156.
+
+\bibitem{podlubny2002}
+I.~Podlubny, Geometric and Physical Interpretation of Fractional Integration and Fractional Differentiation, \emph{Fract. Calc. Appl. Anal.} 
+\textbf{5} (2002) 367--386.
+
+\bibitem{prabhu2008}
+V.~Prabhu, B. Czarnocha, Los Indivisibles en el C\'{a}lculo Contempor\'{a}neo, \emph{Ed. Mat.} \textbf{20} (2008) 53--88.
+
+\bibitem{ruffa2002}
+A.~A.~Ruffa, The Generalized Method of Exhaustion, \emph{Int. J. Math. Math. Sci.} \textbf{31} (2002) 345--351.
+
+\bibitem{sealey2014}
+V. Sealey, A framework for Characterizing Student Understanding of Riemann Sums and Definite Integrals, \emph{J. Math. Behav.}  \textbf{33} (2014) 230--245.
+
+\bibitem{wildberger2002}
+W.~N.~Wildeberger, A New Proof of Cavalieri's Quadrature Formula, \emph{Amer. Math. Monthly} \textbf{109} (2002) 843--845.
+
+\bibitem{william1917}
+E.~G.~William, Cavalieri's Theorem in his own Words, \emph{Amer. Math. Monthly} \textbf{95} (1917) 447--451.
+
+\bibitem{young1985}
+L. Lay-Young, S. Kangshen, The Chinese Concept of Cavalieri's Principle and Its Application, \emph{Hist. Math.}, \textbf{12} (1985) 219--228.
+
+\bibitem{zaskis2014}
+D.~Zaskis, C.~Rasmussen, S.~P.~Shen, A Mean-Based Approach for Teaching the Concept of Integration, \emph{Probl. Resour. Issues Math. Undergrad. Stud.} \textbf{24} (2014) 116--137.
 \end{thebibliography}

### 2017-11-14 paper.tex
added new changes to paper

@@
 \markright{Abbreviated Article Title}
-\author{Woodrow Wilson and Herbert Hoover}
+\author{Trienko Lups Grobler}
 
@@
 integration strips. This interpretation is surprisingly similar to the geometric interpretation of the ordinary Riemann integral. 
-It is therefore likely that this geometric interpretation would reduce the large jump 
-students experience when they first encounter the Riemann-Stieltjes integral (i.e. make the 
-Riemann-Stieltjes integral less abstract).
+It is therefore likely that students, who are encountering the Riemann-Stieltjes integral for the first time, would find this new alternative geometric interpretation useful for mastering it.
 \end{abstract}
@@
 to the geometric interpretation of the Riemann integral. The difference being: in the case of the Riemann integral we employ 
-rectangular instead of non-rectangular integration strips. This geometric interpretation has been quite useful while 
+rectangular instead of non-rectangular integration strips. This rectangular geometric interpretation has been quite useful while 
 teaching the ordinary Riemann integral to undergraduate students \cite{jones2015,sealey2014}.
 It, therefore, seems likely that undergraduate students would find the non-rectangular geometric interpretation
-of the Riemann-Stieltjes integral just as useful. It is also interesting to mention, that there is a few papers in literature that proposes to first 
+of the Riemann-Stieltjes integral just as useful. It is also interesting to mention, that there are a few papers in the literature that propose to first 
 teach simpler integral definitions (which are easier to grasp) before introducing students to the Riemann integral \cite{czarnocha2001,prabhu2008,ruffa2002,zaskis2014}.
-It therefore seems plausible that
-students will find it useful to first understand the Cavalieri integral before the Riemann-Stieltjes integral is taught to them.
+It therefore also seems plausible that
+students will find it useful to first understand the simpler Cavalieri integral before they are exposed to the more abstract Riemann-Stieltjes integral.\\
+
+\noindent
+We first present the formal definition of the Riemann-Stieltjes and Cavalieri integrals \cite{bartle1976,ackermann2012}.
+We then present the geometric interpretation proposed by G.~Bullock \cite{bullock1988}, which is followed by our alternative interpretation. We end 
+the paper with some examples which aim to help the reader grasp the new alternative interpretation.
 
@@
 
-\begin{definition}[Definition of integral]
+\begin{definition}
 Define a partition $\mathcal{P}$ of $[a',b']$ to be a set of points $x_0, x_1,\cdots,x_n$, 
@@
 
-\begin{theorem}
-If $a'<s<b'$, $f$ is continuous at $s$, and 
-\begin{equation}
-g(x) = 
-\begin{cases}
-0 & \textrm{if}~x\leq s\\
-1 & \textrm{if}~x > s
-\end{cases}
-\end{equation}
-then $\int_a^b f dg(x) = f(s)$.
-\end{theorem}
+%\begin{theorem}
+%If $a'<s<b'$, $f$ is continuous at $s$, and 
+%\begin{equation}
+%g(x) = 
+%\begin{cases}
+%0 & \textrm{if}~x\leq s\\
+%1 & \textrm{if}~x > s
+%\end{cases}
+%\end{equation}
+%then $\int_a^b f dg(x) = f(s)$.
+%\end{theorem}
 
@@
 
-\section{3D Geometric Interpretation}
-Bullock proposed one possible geometric interpretation of the Riemann-Stieltjes integral. 
-The basic premise behind his approach is to represent $f(x)$ and $g(x)$ as three-dimensional sheets. 
-The three dimensional coordinate system which Bullock proposes to realize this representation is depicted in 
-Fig.~\ref{fig:bullock}. The $f$-sheet is constructed by simply extending the curve $f$ which resides in the $fx$-plane 
-along the $g$-direction. The $g$-sheet is constructed similarly. Note that, since $f$ is independent of $g$, the $f$-sheet remains 
-constant along the $g$-direction. Similarly, the $g$-sheet remains constant along the $f$-direction. 
-A new sheet, known simply as the ``fence'', can be created by chopping off any part of the $g$-sheet that protrudes above the 
-$f$-sheet and below the $gx$-plane. This sheet can now be projected onto the $fg$-plane. The area of the region that is formed 
-via this projection can be interpreted as the value which is obtained when the Riemann-Stieltjes integral is evaluated.
-
-\noindent
-Let us now try to make the above ideas more concrete by applying them to an example. Let $f(x)=x^2$ and 
-$g(x)=x$. The sheets associated with these two functions are depicted in Fig.~\ref{fig:bullock}. 
-The $f$-sheet is depicted in blue, while the $g$-sheet is red. The ``fence'' is depicted in green. The region
-obtained by projecting the ``fence'' on to the $fg$-plane is depicted in black.
-
-\noindent
-It is interesting to note that Bullock follows a similar route than we do in terms of developing his geometrical framework.
-He starts of with quite strict requirements for $f$ ang $g$ and relaxes more and more of these requirements in latter 
-examples.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=1.0\textwidth]{3D_final-crop.pdf}
-\caption{An example of using Bullocks' geometric framework to interpret the Riemann-Stieltjes integral. In this example 
-$f(x)$ is represented by the blue sheet, $g(x)$ is represented by the red sheet. Moreover, $f(x)=x^2$ and $g(x)=x$. The green sheet, simply known as the ``fence'', is formed 
-by chopping of any part of the $g$-sheet which protrudes above the $f$-sheet and below the $gx$-plane. Projecting the ``fence''
-onto the $fg$-plane produces the visible gray region in the $fg$-plane. The area of this gray region in the $fg$-plane is equal to the Riemann-Stieltjes integral:
-$\int_{0}^{3} f(x) dg(x)$.}
-\label{fig:bullock}
-\end{figure}
-
 \section{Cavalieri integral}
@@
 
-\begin{definition}
+\begin{definition}[Translational Function]
 A continuous real-valued function $a(y)$ is called a translational function with respect to a continuous real-valued function $f(x)$ on the interval $[a,b]$ if 
@@
 
-\begin{definition}
+\begin{definition}[Transformation Function]
 The mapping $h : [a, b] \rightarrow [a',b']$, which maps $x_i^1 \in [a, b]$ to $x_i^2 \in [a',b']$, is defined as
-$h(x_i^1) :=$ $\{x_i^2 \in [a' ,b'] | a\circ f(x_i^2) + [x_i^1 - a] = x_i^2$ , $a = a(0)\}$, which we will refer to
-as the transformation function. 
+$h(x_i^1) :=$ $\{x_i^2 \in [a' ,b'] | a\circ f(x_i^2) + [x_i^1 - a] = x_i^2$ , $a = a(0)\}$
 \end{definition}
@@
 
-\begin{definition}
+\begin{definition}[Inverse Transformation Function]
 The mapping $g:[a′, b′] \rightarrow [a, b]$, which maps $x_i^2 \in [a' , b']$ to $x_i^1\in [a, b]$,
-is defined as $g(x_i^2) := x_i^2 - a \circ f (x_i^2) + a$, which we will refer to as the inverse
-transformation function. 
+is defined as $g(x_i^2) := x_i^2 - a \circ f (x_i^2) + a$.
 \end{definition}
@@
 the application of $h$ to the partition $\mathcal{P}_1$ induces a new partition $\mathcal{P}_2 = \{x_0^2, x_1^2,\cdots, x_n^2\}$.
-Otherwise, if $h$ is strictly decreasing, the application of $h$ induces a reversed partition $\mathcal{P}_2 = \{x_n^2, \cdots, x_1^2,x_0^2\}$. In the rest of this paper
-we will assume that $h$ is strictly increasing, without any loss of generality.  Let 
+Otherwise, if $h$ is strictly decreasing, the application of $h$ induces a reversed partition $\mathcal{P}_2 = \{x_n^2, \cdots, x_1^2,x_0^2\}$. It
+can be assumed that $h$ is strictly increasing, without any loss of generality.  Let 
 $M_k = \sup \{f (x), h(x_{i-1}^1) = x_{i-1}^2 \leq x \leq x_i^2 = h(x_i^1)\}$, $m_k = \inf \{f (x), h(x_{i-1}^1) = x_{i-1}^2 \leq x \leq x_i^2 = h(x_i^1)\}$, and set 
@@
 
-\subsection{Clarifying Example}
+\section{Cavalieri Integral: Example}
 
-Consider the region $R$ bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$. This region is shown in Fig.~\ref{fig:ex1}.\\
+Consider the region $R$ bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$ and $b(y)=4-y$. This region is shown in Fig.~\ref{fig:ex1}.\\
 \begin{figure}[htb]
@@
 The right panel of Fig.~\ref{fig:caval2} illustrates that the larger $n$ becomes the better Eq.~\eqref{eq:cav_sum} approximates the area of $R$.
-In the limit Eq.~\eqref{eq:cav_sum} approaches the Cavalieri integral
+In the limit Eq.~\eqref{eq:cav_sum} approaches the Cavalieri integral \cite{ackermann2012}:
 \begin{equation}
@@
 \noindent
-It is however hard to evaluate Eq.~\eqref{eq:caval1} in its present form. Luckily we can transform the Cavalieri sum given in Eq.~\eqref{eq:caval1} into an ordinary Riemann sum
+It is however hard to evaluate Eq.~\eqref{eq:caval1} in its present form. Fortuitously, we can transform the Cavalieri sum given in Eq.~\eqref{eq:caval1} into an ordinary Riemann sum
 if we can determine an expression for $x_i^2$ in terms of the partition points $x_i^1$, for all $i=0,1,\ldots,n$.
@@
 
-\section{2D Geometric Interpretation}
+\section{Existing Geometric Interpretation}
+G.~Bullock proposed one possible geometric interpretation of the Riemann-Stieltjes integral \cite{bullock1988}. 
+The basic premise behind his approach is to represent $f(x)$ and $g(x)$ as three-dimensional sheets. 
+The three dimensional coordinate system which G.~Bullock proposes to realize this representation is depicted in 
+Fig.~\ref{fig:bullock}. The $f$-sheet is constructed by simply extending the curve $f$ which resides in the $fx$-plane 
+along the $g$-direction. The $g$-sheet is constructed similarly. Note that, since $f$ is independent of $g$, the $f$-sheet remains 
+constant along the $g$-direction. Similarly, the $g$-sheet remains constant along the $f$-direction. 
+A new sheet, known simply as the ``fence'', can be created by chopping off any part of the $g$-sheet that protrudes above the 
+$f$-sheet and below the $gx$-plane. This sheet can now be projected onto the $fg$-plane. The area of the region that is formed 
+via this projection can be interpreted as the value which is obtained when the Riemann-Stieltjes integral is evaluated.\\
+
+\noindent
+Let us now try to make the above ideas more concrete by applying them to an example. Let $f(x)=x^2$ and 
+$g(x)=x$. The sheets associated with these two functions are depicted in Fig.~\ref{fig:bullock}. 
+The $f$-sheet is depicted in blue, while the $g$-sheet is red. The ``fence'' is depicted in green. The region
+obtained by projecting the ``fence'' on to the $fg$-plane is depicted in black.\\
+
+\noindent
+\begin{remark}
+It is interesting to note that G.~Bullock follows a similar route than we do in terms of developing his geometrical framework.
+He starts of with quite strict requirements for $f$ ang $g$ and relaxes more and more of these requirements in his latter 
+examples. 
+\end{remark}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=1.0\textwidth]{3D_final-crop.pdf}
+\caption{An example of using G.~Bullocks' geometric framework to interpret the Riemann-Stieltjes integral. In this example 
+$f(x)$ is represented by the blue sheet, $g(x)$ is represented by the red sheet. Moreover, $f(x)=x^2$ and $g(x)=x$. The green sheet, simply known as the ``fence'', is formed 
+by chopping of any part of the $g$-sheet which protrudes above the $f$-sheet and below the $gx$-plane. Projecting the ``fence''
+onto the $fg$-plane produces the visible gray region in the $fg$-plane. The area of this gray region in the $fg$-plane is equal to the Riemann-Stieltjes integral:
+$\int_{0}^{3} f(x) dg(x)$.}
+\label{fig:bullock}
+\end{figure}
+
+\section{Alternative Geometric Interpretation}
 \begin{figure}[htb]
@@
 \includegraphics[width=1\textwidth]{fig13_change}
-\caption{A sum-based 2D geometric interpretation of the Riemann-Stieltjes integral. Moreover, the figure depicts the region $R$ (also see Fig.~). The integrator $g$ maps points 
+\caption{A non-rectangular sum-based geometric interpretation of the Riemann-Stieltjes integral. Moreover, the figure depicts the region $R$ (also see Fig.~). The integrator $g$ maps points 
 in $[a',b']$ (depicted in blue) to points in $[a,b]$ (depicted in green). The function $h$ performs the reverse operation. Moreover, $g$ maps the $x$-coordinates at which
@@
 \label{eq:g_int2}
-\int_{a'}^{b'} f(x) dg(x) =  \lim_{n \rightarrow \infty}\sum_{i=0}^{n-1} f(x_i^2)[g(x_{i+1}^2)-g(x_{i}^2)]. 
+\int_{a'}^{b'} f(x) dg(x) =  \lim_{n \rightarrow \infty}\sum_{i=0}^{n-1} f(x_i^2)[g(x_{i+1}^2)-g(x_{i}^2)], 
 \end{equation}
+with $(x_i^2)_{i=0}^n$ being arbitrary partition points on the $x$-axis.
 Eq.~\eqref{eq:g_int2} tells us that the function of the integrator $g$ is to map points in the interval $[a',b']$ to other 
@@
 \noindent
-To improve our understanding of $g$ lets explore a specific example of the Riemann-Stieltjes integral: 
+To improve our understanding of $g$ lets investigate a specific example of the Riemann-Stieltjes integral in more depth: 
 \begin{equation}
-\int_{\frac{1}{2}}^1 x~d2x. 
+R = \int_{\frac{1}{2}}^1 x~d2x. 
 \end{equation}
-In this example $g$ maps $[\frac{1}{2},2]$ to $[1,4]$. The mapping between these two intervals is graphically 
+The reader is encouraged to, at this point, also inspect Fig.~\ref{fig:2d_geo} which graphically depicts $R$. 
+In this example $g$ maps $[\frac{1}{2},2]$ to $[1,4]$. The mapping between these two intervals is also 
 depicted in Fig.~\ref{fig:2d_geo}. Moreover, the interval $[\frac{1}{2},2]$ is depicted in blue,
@@
 \begin{itemize}
- \item $g(x_{i+1}^2)-g(x_{i}^2)$ represents the length of the base of a non-rectangular integration strip.
+ \item $g(x_{i+1}^2)-g(x_{i}^2)$ represents the length of the base of a non-rectangular integration strip. Note, the base lengths are all equal.
  \item $f(x_i^2)$ is the height of a non-rectangular integration strip.
@@
 The Riemann-Stieltjes integral, can therefore, be interpreted as the area which is obtained, by summing together the areas of an infinite number of infinitesimally small non-rectangular integration strips,
-i.e. a Riemann-Stieltjes integral can be converted into an equivalent Cavalieri integral. Note, that the geometric interpretation presented
-in Fig.~\ref{fig:2d_geo} is two dimensional.\\
+i.e. a Riemann-Stieltjes integral can be converted into an equivalent Cavalieri integral.\\
 
@@
 \end{itemize}
-Note that the above procedure places an even stricter requirement of $f$, it now also needs to be invertable. Moreover the 
-above derivation aslo requires that $a(0)$ exists.
+
+\begin{remark}
+Note that the above procedure places an even stricter limitation on $f$, it now also needs to be invertible. Moreover the 
+above derivation also requires that $a(0)$ exists.
+\end{remark}
 
@@
 thereof is reported in Table~\ref{tab:table2}.
-The 2D sum-based geometric interpretations of the integrals in Table~\ref{tab:table1}, the $a(y)$ functions provide, are depicted in Figs.~\ref{fig:ex1_sec}--\ref{fig:ex4_sec}.\\
+The non-rectangular sum-based geometric interpretations of the integrals in Table~\ref{tab:table1} are depicted in Figs.~\ref{fig:ex1_sec}--\ref{fig:ex4_sec}.\\
 
@@
 depiction remains valid, however, in the case of $\widetilde{g}$ the lengths of the bases of the depicted integration strips are not 
-computed on the $x$-axis itself, but rather on the line $y=1000$. The fact that the 2D sum-based geometric framework remains useful even if $g(a')\neq a$ is true in general.\\
+computed on the $x$-axis itself, but rather on the line $y=1000$. The fact that the non-rectangular sum-based geometric framework remains useful even if $g(a')\neq a$ is true in general.\\
 
@@
 In Fig.~\ref{fig:ex2_sec} we depict the geometric interpretation of $\int_1^2 \frac{1}{x} d[x^2+C]$. This example is a bit of a special case, since $a(0)$ does not exist. 
-However, the 2D sum-based geometric framework does produce a meaningful result.\\
+However, the non-rectangular sum-based geometric framework does still produce a meaningful result.\\
 
 \noindent
-One of the main limitations of the 2D geometric interpretation we present in this paper is that both $f$ and $g$ need to be invertible.
+One of the main limitations of the non-rectangular sum-based geometric interpretation we present in this paper is that both $f$ and $g$ need to be invertible.
 Being invertible is however not that big of a limitation if we take the following into account. We can always split a Riemann-Stieltjes
-integral whose integrand and integrator are not invertable over its integratrion limits into multiple constittuent Riemann-Stieltjes integrals whose 
-integrand and integrator are invertable over the integration limits of the consitutent integrals. For example, say 
-$f$ and $g$ are not invertabal over the interval $[a',b']$, but are invertable over the inervals $[a',c']$ and 
+integral whose integrand and integrator are not invertible over its integration limits into multiple constituent Riemann-Stieltjes integrals whose 
+integrand and integrator are invertible over the integration limits of the constituent integrals. For example, say 
+$f$ and $g$ are not invertible over the interval $[a',b']$, but are invertible over the intervals $[a',c']$ and 
 $[c',b']$ then we may write:
@@
 \end{equation}
-This allows us to to find a 2D sum-based geometric interpretation of $\int_{a'}^{c'}f(x)dg(x)$ and $\int_{c'}^{b'} f(x)dg(x)$
-which we can combine to give a geometric interpretation of $\int_{a'}^{b'}f(x)dg(x)$.
-In Fig.~\ref{fig:ex4_sec} we present just such a scenrio. In this example $g(x)$ is not invertible over the interval 
-$[0,2]$. It is however invertible over the interval $[0,1]$ and $[1,2]$. The geometric interpretation whic we 
-obtain by considering the intervals $[0,1]$ and $[1,2]$ seperately is depicted, respectively, in the 
+This allows us to to find a non-rectangular sum-based geometric interpretation of $\int_{a'}^{c'}f(x)dg(x)$ and $\int_{c'}^{b'} f(x)dg(x)$
+which we can then depict in one image to give a single geometric interpretation of $\int_{a'}^{b'}f(x)dg(x)$.
+In Fig.~\ref{fig:ex4_sec} we present just such a scenario. In this example $g(x)$ is not invertible over the interval 
+$[0,2]$. It is however invertible over the interval $[0,1]$ and $[1,2]$. The geometric interpretation which we 
+obtain by considering the intervals $[0,1]$ and $[1,2]$ separately is depicted, respectively, in the 
 right and left panel of Fig.~\ref{fig:ex4_sec}.
@@
 \caption{Different Riemann-Stieltjes examples: $\int_{a'}^{b'}f(x)\widetilde{g}(x)$. The table also contains the $a(y)$ functions 
-associated with these integrals. The 2D sum-based geometric interpretations of the integrals, the $a(y)$ functions provide, are depicted in Figs.~\ref{fig:ex1_sec}--\ref{fig:ex4_sec}.
-The results of evaluaing these integrals are presented in Table~\ref{tab:table2}.
+associated with these integrals. The non-rectangular sum-based geometric interpretations of the integrals are depicted in Figs.~\ref{fig:ex1_sec}--\ref{fig:ex4_sec}.
+The results of evaluating these integrals are presented in Table~\ref{tab:table2}.
 }
@@
 evaluate these integrals.
-The constants $a,b$ and $C$ associated with these integrals are also presented.
+The values of the constants $a,b$ and $C$ are also presented.
 Moreover, $h_1(x) = 2\sqrt{x+20}+8$, $h_2(x)=\sin(-\cos^{-1}(x+1))$, $h_3(x)=\sqrt{x-C}$, $h_4(x)=1+\sqrt{1-2x}$ and
@@
  \includegraphics[width=1.0\textwidth]{EX1-crop.pdf}
- \caption{The sum-based 2D geometric interpretation of $\int_{1}^3 (2x+8)^3 d[x^2-20]$ (i.e this integral is equal to the 
+ \caption{The non-rectangular sum-based geometric of interpretation of $\int_{1}^3 (2x+8)^3 d[x^2-20]$ (i.e this integral is equal to the 
  Cavalieri integral $\int_{a(y)}^{b(y)} (2x+8)^3 dx$).}
@@
 \includegraphics[width=1.0\textwidth]{EX2-crop.pdf}
-\caption{The sum-based 2D geometric interpretation of $\int_{\frac{-\pi}{2}}^0 \sin{x}~d[\cos{x}-1]$ (i.e this integral integral is equal to the 
+\caption{The non-rectangular sum-based geometric interpretation of $\int_{\frac{-\pi}{2}}^0 \sin{x}~d[\cos{x}-1]$ (i.e this integral integral is equal to the 
  Cavalieri integral $\int_{a(y)}^{b(y)} \sin{x} dx$).}
@@
 \includegraphics[width=1.0\textwidth]{EX3-crop.pdf}
-\caption{The sum-based 2D geometric interpretation of $\int_1^2 \frac{1}{x} d[x^2+C]$ (i.e this integral integral is equal to the 
+\caption{The non-rectangular sum-based geometric interpretation of $\int_1^2 \frac{1}{x} d[x^2+C]$ (i.e this integral integral is equal to the 
  Cavalieri integral $\int_{a(y)}^{b(y)} \frac{1}{x} dx$).}
@@
 \caption{In the left panel we have the area associated with the integral $\int_2^1 x^2~d[x-\frac{1}{2}x^2]$, while in the 
-right panel we have the area associated with the integral $\int_0^1 x^2~d[x-\frac{1}{2}x^2]$. This example deomonstrates
+right panel we have the area associated with the integral $\int_0^1 x^2~d[x-\frac{1}{2}x^2]$. This example demonstrates
 that the geometric framework presented in this paper does provide a geometric interpretation for the Riemann-Stieltjes integral
-even when $f$ and $g$ are only piece-wise invertable.}
+even when $f$ and $g$ are only piece-wise invertible.}
 \label{fig:ex4_sec}
@@
 \section{Conclusion}
-A two dimensional geometric interpretation of the Riemann-Stieltjes integral was presented in this paper. We can summarize this 
-interpretation as follows: a Riemann-Stieltjes integral can be interpreted as an infinite sum of initesimally small non-rectangular 
-integration strips. The hope is that this geometric interpretation will be usefull to instructors while teaching some of the more difficult concepts 
-surrounding the Riemann-Stieltjes integral.
+An alternative geometric interpretation of the Riemann-Stieltjes integral was presented in this paper. We can summarize this 
+interpretation as follows: a Riemann-Stieltjes integral can be interpreted as an infinite sum of infinitesimally small non-rectangular 
+integration strips. The hope is that this geometric interpretation will be useful to instructors that have to teach
+the Riemann-Stieltjes integral to undergraduate students.
 
-\noindent
-The \textit{American Mathematical Monthly} style incorporates the following \LaTeX\ packages.  These styles should \textit{not} be included in the document header.
-\begin{itemize}
-\item times
-\item pifont
-\item graphicx
-\item color
-\item AMS styles: amsmath, amsthm, amsfonts, amssymb
-\item url
-\end{itemize}
-Use of other \LaTeX\ packages should be minimized as much as possible.
+% \noindent
+% The \textit{American Mathematical Monthly} style incorporates the following \LaTeX\ packages.  These styles should \textit{not} be included in the document header.
+% \begin{itemize}
+% \item times
+% \item pifont
+% \item graphicx
+% \item color
+% \item AMS styles: amsmath, amsthm, amsfonts, amssymb
+% \item url
+% \end{itemize}
+% Use of other \LaTeX\ packages should be minimized as much as possible.
 Math notation, like $c = \sqrt{a^2 +b^2}$, can be left in \TeX's default Computer Modern typefaces for manuscript preparation; or, if you have the appropriate fonts installed, the \texttt{mathtime} or \texttt{mtpro} packages may be used, which will better approximate the finished article.
-
-Web links can be embedded using the \verb~\url{...}~ command, which will result in something like \url{http://www.maa.org}.  These links will be active and stylized in the online publication.
-
-\section{First-level section heading.}
-
-Section headings use an initial capital letter on the first word, with subsequent words lowercase.
+% 
+% Web links can be embedded using the \verb~\url{...}~ command, which will result in something like \url{http://www.maa.org}.  These links will be active and stylized in the online publication.
+% \section{First-level section heading.}
+% 
+% Section headings use an initial capital letter on the first word, with subsequent words lowercase.
 In general, the style of the journal is to leave all section headings unnumbered.
 Consult the journal editor if you wish to depart from this and other conventions.
-
-\subsection{Second-level heading.}
-
-The same goes for second-level headings.
+% 
+% \subsection{Second-level heading.}
+% 
+% The same goes for second-level headings.
 It is not necessary to add font commands to make the math within heads bold and sans serif; this change will occur automatically when the production style is applied.
-
-\section{Graphics.}
-
-Figures for the \textsc{Monthly} can be submitted as either color or black \& white graphics.
+% 
+% \section{Graphics.}
+% 
+% Figures for the \textsc{Monthly} can be submitted as either color or black \& white graphics.
 Generally, color graphics will be used for the online publication, and converted to black \& white images for the print journal.
 We recommend using whatever graphics program you are most comfortable with, so long as the submitted graphic is provided as a separate file using a standard file format.
+% 
+% For best results, please follow the following guidelines:
+% \begin{enumerate}
+% \item Bitmapped file formats---preferably TIFF or JPEG, but not BMP---are appropriate for photographs, using a resolution of at least 300 dpi at the final scaled size of the image.
+% \item Line art will reproduce best if provided in vector form, preferably EPS.
+% \item Alternatively, both photographs and line art can be provided as PDF files.
+Note that creating a PDF does not affect whether the graphic is a bitmap or vector; saving a scanned piece of line art as PDF does not convert it to scalable line art.
+% \item If you generating graphics using a \TeX\ package, please be sure to provide a PDF of the manuscript.
+In the production process, \TeX-generated graphics will eventually be converted to more conventional graphics so the \textsc{Monthly} can be delivered in e-reader formats.
+% \item For photos of contributing authors, we prefer photos that are not cropped tight to the author's profile, so that production staff can crop the head shot to an equal height and width.
+If possible, avoid photographs that have excess shadows or glare.
+% \end{enumerate}
+% 
+% \section{Theorems, definitions, proofs, and all that.}
+% 
+% Following the defaults of the \texttt{amsthm} package, styling is provided for \texttt{theorem}, \texttt{definition}, and \texttt{remark} styles, although the latter two use the same styling.
+% 
+% \begin{theorem}[Pythagorean Theorem]
+% Theorems, lemmas, axioms, and the like are stylized using italicized text. These environments can be numbered or unnumbered, at the author's discretion.
+% \end{theorem}
+% 
+% \begin{proof}
+% Proofs set in roman (upright) text, and conclude with an ``end of proof'' (q.e.d.) symbol that is set automatically when you end the proof environment.
+When the proof ends with an equation or other non-text element, you need to add \verb~\qedhere~ to the element to set the end of proof symbol; see the \texttt{amsthm} package documentation for more details.
+% \end{proof}
+% 
+% \begin{definition}[Secant Line]
+% Definitions, remarks, and notation are stylized as roman text.  They are typically unnumbered, but there are no hard-and-fast rules about numbering.
+% \end{definition}
+% 
+% \begin{remark}
+% Remarks stylize the same as definitions.
+% \end{remark}
 
-For best results, please follow the following guidelines:
-\begin{enumerate}
-\item Bitmapped file formats---preferably TIFF or JPEG, but not BMP---are appropriate for photographs, using a resolution of at least 300 dpi at the final scaled size of the image.
-\item Line art will reproduce best if provided in vector form, preferably EPS.
-\item Alternatively, both photographs and line art can be provided as PDF files.
-Note that creating a PDF does not affect whether the graphic is a bitmap or vector; saving a scanned piece of line art as PDF does not convert it to scalable line art.
-\item If you generating graphics using a \TeX\ package, please be sure to provide a PDF of the manuscript.
-In the production process, \TeX-generated graphics will eventually be converted to more conventional graphics so the \textsc{Monthly} can be delivered in e-reader formats.
-\item For photos of contributing authors, we prefer photos that are not cropped tight to the author's profile, so that production staff can crop the head shot to an equal height and width.
-If possible, avoid photographs that have excess shadows or glare.
-\end{enumerate}
-
-\section{Theorems, definitions, proofs, and all that.}
-
-Following the defaults of the \texttt{amsthm} package, styling is provided for \texttt{theorem}, \texttt{definition}, and \texttt{remark} styles, although the latter two use the same styling.
-
-\begin{theorem}[Pythagorean Theorem]
-Theorems, lemmas, axioms, and the like are stylized using italicized text. These environments can be numbered or unnumbered, at the author's discretion.
-\end{theorem}
-
-\begin{proof}
-Proofs set in roman (upright) text, and conclude with an ``end of proof'' (q.e.d.) symbol that is set automatically when you end the proof environment.
-When the proof ends with an equation or other non-text element, you need to add \verb~\qedhere~ to the element to set the end of proof symbol; see the \texttt{amsthm} package documentation for more details.
-\end{proof}
-
-\begin{definition}[Secant Line]
-Definitions, remarks, and notation are stylized as roman text.  They are typically unnumbered, but there are no hard-and-fast rules about numbering.
-\end{definition}
-
-\begin{remark}
-Remarks stylize the same as definitions.
-\end{remark}
-
-\begin{acknowledgment}{Acknowledgment.}
-The authors wish to thank the Greek polymath Anonymous, whose prolific works are an endless source of inspiration.
-\end{acknowledgment}
+% \begin{acknowledgment}{Acknowledgment.}
+% The authors wish to thank the Greek polymath Anonymous, whose prolific works are an endless source of inspiration.
+% \end{acknowledgment}
 

### 2017-11-14 paper.tex
added new changes to paper

@@
 It is desirable to have geometric interpretations for difficult mathematical ideas. In this paper we present an intuitive geometric interpretation of the Riemann-Stieltjes integral. It can be 
-summarized as follows: the Riemann-Stieltjes integral can be inerpreted as an infinite sum of infinitesimally small non-rectangular 
+summarized as follows: the Riemann-Stieltjes integral can be interpreted as an infinite sum of infinitesimally small non-rectangular 
 integration strips. This interpretation is surprisingly similar to the geometric interpretation of the ordinary Riemann integral. 
@@
 G.~Bullock proposed one possible geometric interpretation of the Riemann-Stieltjes integral \cite{bullock1988}. 
-The basic premise behind his approach is to represent $f(x)$ and $g(x)$ as three-dimensional sheets. 
+The basic idea behind his approach is to represent $f(x)$ and $g(x)$ as three-dimensional sheets. 
 The three dimensional coordinate system which G.~Bullock proposes to realize this representation is depicted in 
@@
 \centering
-\includegraphics[width=1.0\textwidth]{3D_final-crop.pdf}
+\includegraphics[width=1.0\textwidth]{3D_plot-crop.pdf}
 \caption{An example of using G.~Bullocks' geometric framework to interpret the Riemann-Stieltjes integral. In this example 

### 2017-11-14 paper.tex
latest cav version

@@
 integration strips. This interpretation is surprisingly similar to the geometric interpretation of the ordinary Riemann integral. 
-It is therefore likely that students, who are encountering the Riemann-Stieltjes integral for the first time, would find this new alternative geometric interpretation useful for mastering it.
+It is therefore likely that students, who are encountering the Riemann-Stieltjes integral for the first time, would find this new alternative geometric framework a useful visualization tool.
 \end{abstract}
@@
 \noindent
-We first present the formal definition of the Riemann-Stieltjes and Cavalieri integrals \cite{bartle1976,ackermann2012}.
-We then present the geometric interpretation proposed by G.~Bullock \cite{bullock1988}, which is followed by our alternative interpretation. We end 
-the paper with some examples which aim to help the reader grasp the new alternative interpretation.
+We first present the formal definitions of the Riemann-Stieltjes and Cavalieri integrals \cite{bartle1976,ackermann2012}.
+We then present the geometric interpretation proposed by G.~Bullock \cite{bullock1988}, which is followed up by the new alternative interpretation. We end 
+the paper with some examples which aim to help the reader better understand and visualize the new alternative interpretation.
 
@@
 The right panel of Fig.~\ref{fig:caval2} illustrates that the larger $n$ becomes the better Eq.~\eqref{eq:cav_sum} approximates the area of $R$.
-In the limit Eq.~\eqref{eq:cav_sum} approaches the Cavalieri integral \cite{ackermann2012}:
+In the limit Eq.~\eqref{eq:cav_sum} approaches the Cavalieri integral:
 \begin{equation}
@@
 \centering
-\includegraphics[width=1.0\textwidth]{3D_plot-crop.pdf}
+\includegraphics[width=1.0\textwidth]{3D_final-crop.pdf}
 \caption{An example of using G.~Bullocks' geometric framework to interpret the Riemann-Stieltjes integral. In this example 
@@
 \includegraphics[width=1\textwidth]{fig13_change}
-\caption{A non-rectangular sum-based geometric interpretation of the Riemann-Stieltjes integral. Moreover, the figure depicts the region $R$ (also see Fig.~). The integrator $g$ maps points 
+\caption{A non-rectangular sum-based geometric interpretation of the Riemann-Stieltjes integral.
+Moreover, the figure depicts the region $R$ (also see Fig.~\ref{fig:ex1}).
+The integrator $g$ maps points
 in $[a',b']$ (depicted in blue) to points in $[a,b]$ (depicted in green). The function $h$ performs the reverse operation. Moreover, $g$ maps the $x$-coordinates at which
@@
 \end{equation}
-The reader is encouraged to, at this point, also inspect Fig.~\ref{fig:2d_geo} which graphically depicts $R$. 
-In this example $g$ maps $[\frac{1}{2},2]$ to $[1,4]$. The mapping between these two intervals is also 
+$R$ is depicted in Fig.~\ref{fig:2d_geo}. In this example $g$ maps $[\frac{1}{2},2]$ to $[1,4]$. The mapping between these two intervals is also 
 depicted in Fig.~\ref{fig:2d_geo}. Moreover, the interval $[\frac{1}{2},2]$ is depicted in blue,
@@
 \begin{itemize}
- \item $g(x_{i+1}^2)-g(x_{i}^2)$ represents the length of the base of a non-rectangular integration strip. Note, the base lengths are all equal.
+ \item $g(x_{i+1}^2)-g(x_{i}^2)$ represents the length of the base of a non-rectangular integration strip. Note, the base lengths in Fig.~\ref{fig:2d_geo} are all equal.
  \item $f(x_i^2)$ is the height of a non-rectangular integration strip.
@@
  integration strips.
- \item In the limit the Riemann-Stieltjes sum approaches the area of $R$. 
+ \item In the limit the Riemann-Stieltjes sum approaches $R$. 
 \end{itemize}
@@
  \includegraphics[width=1.0\textwidth]{EX1-crop.pdf}
- \caption{The non-rectangular sum-based geometric of interpretation of $\int_{1}^3 (2x+8)^3 d[x^2-20]$ (i.e this integral is equal to the 
+ \caption{The non-rectangular sum-based geometric interpretation of $\int_{1}^3 (2x+8)^3 d[x^2-20]$ (i.e this integral is equal to the 
  Cavalieri integral $\int_{a(y)}^{b(y)} (2x+8)^3 dx$).}
@@
 \begin{biog}
-\item[Woodrow Wilson] received his Ph.D.
-in history and political science from Johns Hopkins University.
-He held visiting positions at Cornell and Wesleyan before joining the faculty at Princeton, where he was eventually appointed president of the university.
-Among his proudest accomplishments was the abolition of eating clubs at Princeton on the grounds that they were elitist.
+\item[Trienko Lups Grobler] received his Ph.D. in Engineering at the University of Pretoria in 2013. He was 
+a postdoctoral fellow at Rhodes University from 2013-2017. He is currently a lecturer in the Computer Science Division
+at Stellenbosch University.
 \begin{affil}
-Office of the President, Princeton University, Princeton NJ 08544\\
-twoodwilson@princeton.edu
+Dept of Mathematical Sciences, Computer Science Division, Stellenbosch University, Private Bag X1, 7602 Matieland, South Africa\\
+tlgrobler@sun.ac.za
 \end{affil}
 
-\item[Herbert Hoover] entered Stanford University in 1891, after failing all of the entrance exams except mathematics.
+%\item[Herbert Hoover] entered Stanford University in 1891, after failing all of the entrance exams except mathematics.
 He received his B.S.
@@
 Food Administration and the Supreme Economic Council, where he orchestrated the greatest famine relief efforts of all time.
-\begin{affil}
-Hoover Institution, Stanford University, Stanford CA 94305\\
-herbhoover@stanford.edu
-\end{affil}
+%\begin{affil}
+%Hoover Institution, Stanford University, Stanford CA 94305\\
+%herbhoover@stanford.edu
+%\end{affil}
 \end{biog}

### 2017-12-14 paper.tex
newest paper
added Jonathan's comments

@@
 \begin{abstract}
-It is desirable to have geometric interpretations for difficult mathematical ideas. In this paper we present an intuitive geometric interpretation of the Riemann-Stieltjes integral. It can be 
+It is desirable to have geometric interpretations of difficult mathematical concepts. In this paper we present an intuitive geometric interpretation of the Riemann-Stieltjes integral. It can be 
 summarized as follows: the Riemann-Stieltjes integral can be interpreted as an infinite sum of infinitesimally small non-rectangular 
 integration strips. This interpretation is surprisingly similar to the geometric interpretation of the ordinary Riemann integral. 
-It is therefore likely that students, who are encountering the Riemann-Stieltjes integral for the first time, would find this new alternative geometric framework a useful visualization tool.
+It is therefore likely that students, encountering the Riemann-Stieltjes integral for the first time, would find this new alternative geometric framework a useful visualization tool.
 \end{abstract}
@@
 \noindent
-Providing a geometrical interpretation for a mathematical concept can greatly improve ones understanding of it. The Riemann-Stieltjes 
+Providing a geometrical interpretation for a mathematical concept can greatly improve one's understanding of it. The Riemann-Stieltjes 
 integral is no exception. G.~Bullock proposed a projection-based geometric framework with which one can interpret the Riemann-Stieltjes 
@@
 and in doing so developed the Cavalieri integral \cite{ackermann2012}. The area of a non-rectangular integration strip is computed via 
-Cavalieri's principle \cite{andersen1985,eves1991, malik1984, wildberger2002, young1985}. They also showed that a Cavalieri integral can easily be converted to a Riemann-Stieltjes integral. The 
-reverse operation was however not described in \cite{ackermann2012}. In this paper we address this shortcoming. This 
+Cavalieri's principle \cite{andersen1985,eves1991, malik1984, wildberger2002, young1985}. They also showed that a Cavalieri integral can easily be converted to a Riemann-Stieltjes integral. 
+However, the reverse operation was not described in \cite{ackermann2012}. In this paper we address this shortcoming. This 
 reverse operation actually allows us to contrive a novel geometric interpretation of the Riemann-Stieltjes integral.
 This geometric interpretation is: the Riemann-Stieltjes integral can be interpreted as an infinite sum of infinitesimally small
-non-rectangular integration strips. Interestingly enough, this interpretation of the Riemann-Stieltjes integral is very similar 
-to the geometric interpretation of the Riemann integral. The difference being: in the case of the Riemann integral we employ 
-rectangular instead of non-rectangular integration strips. This rectangular geometric interpretation has been quite useful while 
+non-rectangular integration strips. Interestingly enough, this interpretation is very similar 
+to the geometric interpretation of the Riemann integral.
+The priciple difference between these interprations is the shape of the ingration strips; non-rectangular in the case of the Riemann-Stieltjies integral and rectangular in the case of the Rieman integral.
+This rectangular geometric interpretation has been quite useful when 
 teaching the ordinary Riemann integral to undergraduate students \cite{jones2015,sealey2014}.
-It, therefore, seems likely that undergraduate students would find the non-rectangular geometric interpretation
-of the Riemann-Stieltjes integral just as useful. It is also interesting to mention, that there are a few papers in the literature that propose to first 
-teach simpler integral definitions (which are easier to grasp) before introducing students to the Riemann integral \cite{czarnocha2001,prabhu2008,ruffa2002,zaskis2014}.
+Consquently, it seems likely that undergraduate students would find the non-rectangular geometric interpretation
+of the Riemann-Stieltjes integral just as useful.
+It is also interesting to mention that there are a few papers in the literature that propose teaching simpler integral definitions (which are easier to grasp) before introducing students to the Riemann integral \cite{czarnocha2001,prabhu2008,ruffa2002,zaskis2014}.
 It therefore also seems plausible that
@@
 $\mathcal{P}$ of $[a',b']$ write $\Delta g_k = g(x_k)-g(x_{k-1})$. Let 
-$M_k = \max\{f(x),x_{k-1}\leq x \leq x_{k}\}$, $m_k = \max\{f(x),x_{k-1}\leq x \leq x_{k}\}$, and set 
+$M_k = \sup\{f(x),x_{k-1}\leq x \leq x_{k}\}$, $m_k = \inf\{f(x),x_{k-1}\leq x \leq x_{k}\}$, and set 
 \begin{equation}
@@
 \begin{definition}[Inverse Transformation Function]
-The mapping $g:[a′, b′] \rightarrow [a, b]$, which maps $x_i^2 \in [a' , b']$ to $x_i^1\in [a, b]$,
+The mapping $g:[a', b'] \rightarrow [a, b]$, which maps $x_i^2 \in [a' , b']$ to $x_i^1\in [a, b]$,
 is defined as $g(x_i^2) := x_i^2 - a \circ f (x_i^2) + a$.
@@
 \noindent
-Note, that $g = h^{-1}$ per definition. Moreover $g$ is guaranteed to exists, since $h$ is bijective.
+Note, that $g = h^{-1}$ per definition. Moreover $g$ is guaranteed to exist, since $h$ is bijective.
 
@@
 definition of the Riemann-Stieltjes integral does. To ensure consistency, we will assume, from here onwards and unless stated otherwise, that the stricter requirements imposed 
-by the Cavalieri definition is now also binding on the Riemann-Stieltjes integral. Remember the main aim of the paper is to 
+by the Cavalieri definition are now also binding on the Riemann-Stieltjes integral. Recall that the main aim of the paper is to 
 help students develop a geometric intuition for the Riemann-Stieltjes integral that will be valid for most of the 
-Riemann-Stieltjes integral problems that students will encounter during their undergraduate studies and not to present a complete geometric framework 
-that will remain valid for each and every possible Riemann-Stieltjes integral. This is not to say that the geometric interpretation presented here cannot be used to provide 
+Riemann-Stieltjes integral problems that students will encounter during their undergraduate studies.
+While this does not imply that this interpretation cannot provide insight into a broad range of problems, it does mean that the interpretation may not remain valid for each and every Riemann-Stieltjes integral
+and not to present a complete geometric framework. This is not to say that the geometric interpretation presented here cannot be used to provide 
 insight to a broad range of problems. In the example section we show that Cavalieri sums can provide meaningful insights even 
@@
 Fig.~\ref{fig:bullock}. The $f$-sheet is constructed by simply extending the curve $f$ which resides in the $fx$-plane 
-along the $g$-direction. The $g$-sheet is constructed similarly. Note that, since $f$ is independent of $g$, the $f$-sheet remains 
+along the $g$-direction. The $g$-sheet is constructed similarly. Note that, as $f$ is independent of $g$, the $f$-sheet remains 
 constant along the $g$-direction. Similarly, the $g$-sheet remains constant along the $f$-direction. 
@@
 \begin{remark}
-It is interesting to note that G.~Bullock follows a similar route than we do in terms of developing his geometrical framework.
+It is interesting to note that G.~Bullock follows route similar to ours when developing his geometrical framework.
 He starts of with quite strict requirements for $f$ ang $g$ and relaxes more and more of these requirements in his latter 
@@
 \caption{An example of using G.~Bullocks' geometric framework to interpret the Riemann-Stieltjes integral. In this example 
-$f(x)$ is represented by the blue sheet, $g(x)$ is represented by the red sheet. Moreover, $f(x)=x^2$ and $g(x)=x$. The green sheet, simply known as the ``fence'', is formed 
-by chopping of any part of the $g$-sheet which protrudes above the $f$-sheet and below the $gx$-plane. Projecting the ``fence''
+$f(x)$ is represented by the blue sheet and $g(x)$ is represented by the red sheet. Moreover, $f(x)=x^2$ and $g(x)=x$. The green sheet, simply known as the ``fence'', is formed 
+by chopping off any part of the $g$-sheet which protrudes above the $f$-sheet and below the $gx$-plane. Projecting the ``fence''
 onto the $fg$-plane produces the visible gray region in the $fg$-plane. The area of this gray region in the $fg$-plane is equal to the Riemann-Stieltjes integral:
@@
 Interestingly, the integrator $g$ maps the $x$-coordinates where translations of $a(y)$ and $f(x)$ intersect to the $x$-intercepts of the translations of $a(y)$.
-The implications of this observation is the following: 
+The implications of this observation are the following: 
 \begin{itemize}
- \item $g(x_{i+1}^2)-g(x_{i}^2)$ represents the length of the base of a non-rectangular integration strip. Note, the base lengths in Fig.~\ref{fig:2d_geo} are all equal.
+ \item $g(x_{i+1}^2)-g(x_{i}^2)$ (i.e. $\Delta x_i^1$) represents the length of the base of a non-rectangular integration strip. Note, the base lengths in Fig.~\ref{fig:2d_geo} are all equal.
  \item $f(x_i^2)$ is the height of a non-rectangular integration strip.
@@
 \end{itemize}
-The Riemann-Stieltjes integral, can therefore, be interpreted as the area which is obtained, by summing together the areas of an infinite number of infinitesimally small non-rectangular integration strips,
+The Riemann-Stieltjes integral can therefore be interpreted as the area which is obtained by summing together the areas of an infinite number of infinitesimally small non-rectangular integration strips,
 i.e. a Riemann-Stieltjes integral can be converted into an equivalent Cavalieri integral.\\

### 2017-12-15 paper.tex
finished Jonathans comments

@@
 \begin{abstract}
-It is desirable to have geometric interpretations of difficult mathematical concepts. In this paper we present an intuitive geometric interpretation of the Riemann-Stieltjes integral. It can be 
+It is desirable to have geometric interpretations of difficult mathematical concepts.
+In this paper we present a new and more intuitive geometric interpretation of the Riemann-Stieltjes integral.
+It can be
 summarized as follows: the Riemann-Stieltjes integral can be interpreted as an infinite sum of infinitesimally small non-rectangular 
 integration strips. This interpretation is surprisingly similar to the geometric interpretation of the ordinary Riemann integral. 
-It is therefore likely that students, encountering the Riemann-Stieltjes integral for the first time, would find this new alternative geometric framework a useful visualization tool.
+It is therefore likely that students, when encountering the Riemann-Stieltjes integral for the first time, would find this new alternative geometric framework a useful visualization tool.
 \end{abstract}
@@
 to the geometric interpretation of the Riemann integral.
-The priciple difference between these interprations is the shape of the ingration strips; non-rectangular in the case of the Riemann-Stieltjies integral and rectangular in the case of the Rieman integral.
+The principle difference between these interprations is the shape of the ingration strips; non-rectangular in the case of the Riemann-Stieltjies integral and rectangular in the case of the Rieman integral.
 This rectangular geometric interpretation has been quite useful when 
@@
 definition of the Riemann-Stieltjes integral does. To ensure consistency, we will assume, from here onwards and unless stated otherwise, that the stricter requirements imposed 
-by the Cavalieri definition are now also binding on the Riemann-Stieltjes integral. Recall that the main aim of the paper is to 
-help students develop a geometric intuition for the Riemann-Stieltjes integral that will be valid for most of the 
-Riemann-Stieltjes integral problems that students will encounter during their undergraduate studies.
-While this does not imply that this interpretation cannot provide insight into a broad range of problems, it does mean that the interpretation may not remain valid for each and every Riemann-Stieltjes integral
-and not to present a complete geometric framework. This is not to say that the geometric interpretation presented here cannot be used to provide 
-insight to a broad range of problems. In the example section we show that Cavalieri sums can provide meaningful insights even 
+by the Cavalieri definition are now also binding on the Riemann-Stieltjes integral. 
+%Recall that the main aim of the paper is to 
+%help students develop a geometric intuition for the Riemann-Stieltjes integral that will be valid for most of the 
+%Riemann-Stieltjes integral problems that students will encounter during their undergraduate studies.
+While this does not imply that this interpretation cannot provide insight into a broad range of problems, it does mean that the interpretation may not remain valid for each and every conceivable Riemann-Stieltjes integral.
+In the example section we show that Cavalieri sums can provide meaningful insights even 
 when we relax some of the strict restrictions imposed by the above definitions.
@@
 \begin{remark}
-It is interesting to note that G.~Bullock follows route similar to ours when developing his geometrical framework.
+It is interesting to note that G.~Bullock follows a route similar to ours when developing his geometrical framework.
 He starts of with quite strict requirements for $f$ ang $g$ and relaxes more and more of these requirements in his latter 
@@
 \includegraphics[width=1\textwidth]{fig13_change}
-\caption{A non-rectangular sum-based geometric interpretation of the Riemann-Stieltjes integral.
-Moreover, the figure depicts the region $R$ (also see Fig.~\ref{fig:ex1}).
-The integrator $g$ maps points
+\caption{A non-rectangular sum-based geometric interpretation of the Riemann-Stieltjes integral. Moreover, the figure depicts the region $R$ (also see Fig.~\ref{fig:ex1}).
+Its area is denoted by the symbol $A$. The integrator $g$ maps points 
 in $[a',b']$ (depicted in blue) to points in $[a,b]$ (depicted in green). The function $h$ performs the reverse operation. Moreover, $g$ maps the $x$-coordinates at which
@@
 Consider the definition of the Riemann-Stieltjes integral and 
-Eq.~\eqref{eq:g_int}. For the sake of continiuty we repeat Eq.~\eqref{eq:g_int} below:
+Eq.~\eqref{eq:g_int}. For the sake of continuity we repeat Eq.~\eqref{eq:g_int} below:
 \begin{equation}
@@
 \noindent
-To improve our understanding of $g$ lets investigate a specific example of the Riemann-Stieltjes integral in more depth: 
+To further improve our understanding of $g$ lets investigate a specific example of the Riemann-Stieltjes integral in more depth: 
 \begin{equation}
-R = \int_{\frac{1}{2}}^1 x~d2x. 
+A =\int_{a'}^{b'} f(x) dg(x)=\int_{\frac{1}{2}}^1 x~d2x, 
 \end{equation}
-$R$ is depicted in Fig.~\ref{fig:2d_geo}. In this example $g$ maps $[\frac{1}{2},2]$ to $[1,4]$. The mapping between these two intervals is also 
+In this example $g$ maps $[\frac{1}{2},2]$ to $[1,4]$. The mapping between these two intervals is also 
 depicted in Fig.~\ref{fig:2d_geo}. Moreover, the interval $[\frac{1}{2},2]$ is depicted in blue,
@@
  integration strips.
- \item In the limit the Riemann-Stieltjes sum approaches $R$. 
+ \item In the limit the Riemann-Stieltjes sum approaches $A$, i.e. the area of the region $R$ (depicted in Fig.~\ref{fig:2d_geo}). 
 \end{itemize}
@@
 \begin{remark}
-Note that the above procedure places an even stricter limitation on $f$, it now also needs to be invertible. Moreover the 
+Note that the above procedure places an even stricter limitation on $f$ as it now also needs to be invertible. Moreover, the 
 above derivation also requires that $a(0)$ exists.
@@
 In Fig.~\ref{fig:ex1_sec} we plot the geometric interpretation of $\int_{1}^3 (2x+8)^3 d[x^2-20]$. This same figure also 
-provides a geometric interpretation of $\int_{1}^3 (2x+8)^3 dx^2$ albeit a less intuitive one. The $a(y)$ function need not 
+provides a geometric interpretation of $\int_{1}^3 (2x+8)^3 dx^2$, albeit a less intuitive one. The $a(y)$ function need not 
 produce a mapping $g$ from $[1,3]$ to $[-19,-11]$. It can also produce a mapping $\widetilde{g}$ from $[1,3]$ to $[1,9]$. In both cases the 
-depiction remains valid, however, in the case of $\widetilde{g}$ the lengths of the bases of the depicted integration strips are not 
+depiction remains valid. However, in the case of $\widetilde{g}$ the lengths of the bases of the depicted integration strips are not 
 computed on the $x$-axis itself, but rather on the line $y=1000$. The fact that the non-rectangular sum-based geometric framework remains useful even if $g(a')\neq a$ is true in general.\\
@@
 In Fig.~\ref{fig:ex2_sec} we depict the geometric interpretation of $\int_1^2 \frac{1}{x} d[x^2+C]$. This example is a bit of a special case, since $a(0)$ does not exist. 
-However, the non-rectangular sum-based geometric framework does still produce a meaningful result.\\
+However, the non-rectangular sum-based geometric framework still produces a meaningful result.\\
 
@@
 One of the main limitations of the non-rectangular sum-based geometric interpretation we present in this paper is that both $f$ and $g$ need to be invertible.
-Being invertible is however not that big of a limitation if we take the following into account. We can always split a Riemann-Stieltjes
+Being invertible is, however, not a severe limitation if we take the following into account. We can always split a Riemann-Stieltjes
 integral whose integrand and integrator are not invertible over its integration limits into multiple constituent Riemann-Stieltjes integrals whose 
-integrand and integrator are invertible over the integration limits of the constituent integrals. For example, say 
+integrand and integrator are invertible over their associated integration limits. For example, say 
 $f$ and $g$ are not invertible over the interval $[a',b']$, but are invertible over the intervals $[a',c']$ and 
@@
 $[0,2]$. It is however invertible over the interval $[0,1]$ and $[1,2]$. The geometric interpretation which we 
-obtain by considering the intervals $[0,1]$ and $[1,2]$ separately is depicted, respectively, in the 
-right and left panel of Fig.~\ref{fig:ex4_sec}.
+obtain by considering the intervals $[0,1]$ and $[1,2]$ separately is depicted in the 
+right and left panels of Fig.~\ref{fig:ex4_sec}.
 
@@
 \includegraphics[width=1.0\textwidth]{EX2-crop.pdf}
-\caption{The non-rectangular sum-based geometric interpretation of $\int_{\frac{-\pi}{2}}^0 \sin{x}~d[\cos{x}-1]$ (i.e this integral integral is equal to the 
+\caption{The non-rectangular sum-based geometric interpretation of $\int_{\frac{-\pi}{2}}^0 \sin{x}~d[\cos{x}-1]$ (i.e this integral is equal to the 
  Cavalieri integral $\int_{a(y)}^{b(y)} \sin{x} dx$).}
@@
 \includegraphics[width=1.0\textwidth]{EX3-crop.pdf}
-\caption{The non-rectangular sum-based geometric interpretation of $\int_1^2 \frac{1}{x} d[x^2+C]$ (i.e this integral integral is equal to the 
+\caption{The non-rectangular sum-based geometric interpretation of $\int_1^2 \frac{1}{x} d[x^2+C]$ (i.e this integral is equal to the 
  Cavalieri integral $\int_{a(y)}^{b(y)} \frac{1}{x} dx$).}

### 2019-03-04 fractional/CMJ style files/article-template.tex
started visualization of fractional integrals

\documentclass{article}
\usepackage{college-math-j}

%% IF YOU HAVE FONTS INSTALLED
%\usepackage{mtpro}
%\usepackage{mathtime}

\theoremstyle{theorem}
\newtheorem{theorem}{Theorem}

\theoremstyle{definition}
\newtheorem*{definition}{Definition}
\newtheorem*{remark}{Remark}

\begin{document}

\title{CMJ Article Title}
\author{Woodrow Wilson and Herbert Hoover} %%leave blank in initial submission to allow for double blind reviewing
%\author{ }

\maketitle

%Notes authors should leave bios out altogether.

\begin{biog} %comment out in initial submission to allow for double blind reviewing
\item[\biogpic{\includegraphics[width=84pt]{Woodrow_Wilson.pdf}}Woodrow Wilson] (twwilson@princeton.edu) received his PhD in history and political science from Johns Hopkins University. He held visiting positions at Cornell and Wesleyan before joining the faculty at Princeton, where he was eventually appointed president of the university.  Among his proudest accomplishments was the abolition of eating clubs at Princeton on the grounds that they were elitist.

\item[\biogpic{\includegraphics[width=84pt]{Herbert_Hoover.pdf}}Herbert Hoover] (hchoover@stanford.edu) entered Stanford University in 1891, after failing all of the entrance exams except mathematics.  He received his BS degree in geology in 1895, spent time as a mining engineer, then was appointed by his co-author to the U.S. Food Administration and the Supreme Economic Council, where he orchestrated the greatest famine relief efforts of all time.
\end{biog}

\noindent
The \textit{College Mathematics Journal} style incorporates the following \LaTeX\ packages.  These styles should \textit{not} be included in the document header.
\begin{itemize}
\item times
\item pifont
\item graphicx
\item color
\item AMS styles: amsmath, amsthm, amsfonts, amssymb
\item url
\end{itemize}
Use of other \LaTeX\ packages should be minimized as much as possible. Math notation, like $c = \sqrt{a^2 +b^2}$, can be left in \TeX's default Computer Modern typefaces for manuscript preparation; or, if you have the appropriate fonts installed, the \texttt{mathtime} or \texttt{mtpro} packages may be used, which will better approximate the finished article.

Web links can be embedded using the \verb~\url{...}~ command, which will result in something like \url{http://www.maa.org}.  These links will be active and stylized in the online publication.

\section{First-level section heading}

Section headings use an initial capital letter on the first word, with subsequent words lowercase.  In general, the style of the journal is to leave all section headings unnumbered.  Consult the journal editor if you wish to depart from this and other conventions.

\subsection{Second-level heading}

The same goes for second-level headings.  It is not necessary to add font commands to make the math within heads bold and sans serif; this change will occur automatically when the production style is applied.

\section{Graphics}

Figures for the \textsc{Journal} can be submitted as either color or black \& white graphics.  Generally, color graphics will be used for the online publication, and converted to black \& white images for the print journal.  We recommend using whatever graphics program you are most comfortable with, so long as the submitted graphic is provided as a separate file using a standard file format.

For best results, please follow the following guidelines:
\begin{enumerate}
\item Bitmapped file formats---preferably TIFF or JPEG, but not BMP---are appropriate for photographs, using a resolution of at least 300 dpi at the final scaled size of the image.
\item Line art will reproduce best if provided in vector form, preferably EPS.
\item Alternatively, both photographs and line art can alternatively be provided as PDF files.  Note that creating a PDF does not affect whether the graphic is a bitmap or vector; saving a scanned piece of line art as PDF does not convert it to scalable line art.
\item If you generating graphics using a \TeX\ package, please be sure to provide a PDF of the manuscript.  In the production process, \TeX-generated graphics will eventually be converted to more conventional graphics so the \textsc{Journal} can be delivered in e-reader formats.
\item For photos of contributing authors, we prefer photos that are not cropped tight to the author's profile, so that production staff can crop the head shot to an equal height and width.  If possible, avoid photographs that have excess shadows or glare.
\end{enumerate}

\section{Theorems, definitions, proofs, and all that}

Following the defaults of the \texttt{amsthm} package, styling is provided for \texttt{theorem}, \texttt{definition}, and \texttt{remark} styles, although the latter two use the same styling.

\begin{theorem}[Pythagorean Theorem]
Theorems, lemmas, axioms, and the like are stylized using italicized text. These environments can be numbered or unnumbered, at the author's discretion.
\end{theorem}

\begin{proof}
Proofs set in roman (upright) text, and conclude with an ``end of proof'' (q.e.d.) symbol that is set automatically when you end the proof environment.  When the proof ends with an equation or other non-text element, you need to add \verb~\qedhere~ to the element to set the end of proof symbol; see the \texttt{amsthm} package documentation for more details.
\end{proof}

\begin{definition}[Secant Line]
Definitions, remarks, and notation are stylized as roman text.  They are typically unnumbered, but there are no hard-and-fast rules about numbering.
\end{definition}

\begin{remark}
Remarks stylize the same as definitions.
\end{remark}

Note that the \textit{College Mathematics Journal\/} is meant to be accessible to a broad audience, so heavy use of theorem-like formalisms is generally discouraged.

\begin{acknowledgment}
The authors wish to thank the Greek polymath Anonymous, whose prolific works are an endless source of inspiration.
\end{acknowledgment}

\begin{abstract}
An abstract should not contain concrete mathematics, but rather should be discrete.  Be brief and avoid using mathematical notation except where absolutely necessary, since this brief synopsis will be used by search engines to identify your article!
\end{abstract}

\begin{thebibliography}{1}
\bibitem{parker13} Adam Parker, Who solved the Bernoulli equation and how did they do it? \textit{Coll. Math. J.} \textbf{44} (2013) 89--97.

\bibitem{hopkins} Brian Hopkins, ed., \textit{Resources for Teaching Discrete Mathematics}, Mathematical Association of America, Washington DC, 2009.
\end{thebibliography}
\vfill\eject

\end{document}

### 2019-03-04 fractional/func_plotter.py

@@ -1,0 +1,180 @@
+import numpy as np
+import scipy as sp
+import pylab as plt
+import math
+#from scipy.stats import gamma
+
+#def func_ex1(x):
+#    y = (2*x+8)**3
+#    return y
+
+#def a_ex1(y):
+#    x = -0.25*y**(2.0/3.0) + 9.0/2.0*y**(1.0/3.0) - 19
+#    return x
+
+#def a_ex2(y):
+#    x = -0.25*y**(2.0/3.0) + 9.0/2.0*y**(1.0/3.0) - 11
+#    return x
+
+def a1(y,alpha,t,b):
+    x = y - 1.0/math.gamma(alpha+1)*(t**alpha - (t-y)**alpha)
+    return x+b
+
+def g1(x,alpha,t):
+    return 1.0/math.gamma(alpha+1)*(t**alpha-(t-x)**alpha)
+
+
+def g_func(tau,alpha,t):
+    return (1.0/math.gamma(alpha+1))*(t**alpha-(t-tau)**alpha)
+
+def h_func(tau,alpha,t):
+    return t - (t**alpha-math.gamma(alpha+1)*tau)**(1.0/alpha)
+
+def a_func(y,alpha,t,f_inv):
+    return f_inv(y) - (1.0/math.gamma(alpha+1))*(t**alpha - (t-f_inv(y))**alpha)
+
+def f1(x):
+    return x
+
+def f1_inv(y):
+    return (y);
+
+def f2(x):
+    return np.sqrt(x)
+
+def f2_inv(y):
+    return y**2
+
+def plot_g_functions(t_vector,alpha_vector,tau_points):
+    fig, ax = plt.subplots(len(t_vector), len(alpha_vector), sharex='all', sharey='all')
+    for k in range(0,len(t_vector)):
+        for i in range(0,len(alpha_vector)):
+            tau = np.linspace(0,t_vector[k],tau_points)
+            ax[k,i].plot(tau,g_func(tau,alpha_vector[i],t_vector[k])) 
+            #ax[k,i].grid('on')
+            if k == len(t_vector)-1:
+               ax[k,i].set_xlabel(r"$\alpha$ = "+str(round(alpha_vector[i],2)))
+            if i == 0:
+              ax[k,i].set_ylabel("t = "+str(round(t_vector[k],1)))
+    plt.show() 
+
+def plot_h_functions(t_vector,alpha_vector,tau_points):
+    fig, ax = plt.subplots(len(t_vector), len(alpha_vector), sharex='all', sharey='all')
[…]

### 2019-03-04 fractional/CMJ style files/article-template.tex
added first equations --- needs to be fleshed out dramatically

@@
 
-\title{CMJ Article Title}
+\title{Visualization of Fractional Integrals}
 \author{Woodrow Wilson and Herbert Hoover} %%leave blank in initial submission to allow for double blind reviewing
@@
 Web links can be embedded using the \verb~\url{...}~ command, which will result in something like \url{http://www.maa.org}.  These links will be active and stylized in the online publication.
+
+\section{xxx}
+The fractional integral is defined as (need to be more explicit here). Need to add how it has come about... Start with a single integral, expand to the general case and then 
+to a general $\alpha$. 
+\begin{equation}
+\frac{1}{\Gamma(\alpha)}\int_{0}^{t}f(\tau)(t-\tau)^{\alpha-1}~d\tau
+\end{equation}
+
+Podlubny showed that the fractional integral can be rewritten as a Riemann-Stieltjes integral:
+\begin{equation}
+\label{eq:rs}
+\int_0^{\tau} f(\tau)~dg_t(\tau),
+\end{equation}
+with 
+\begin{equation}
+g_t^{\alpha}(\tau) = \frac{\left \{t^{\alpha} - (t-\tau)^{\alpha} \right \}}{\Gamma(\alpha+1)}. 
+\end{equation}
+
+We can now transform Equation~\ref{eq:rs} into an equivalent Cavalieri integral:
+\begin{equation}
+\label{eq:cav}
+\int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau, 
+\end{equation}
+with
+\begin{equation}
+a_t^{\alpha}(y) = f^{-1}(y) - \frac{t^{\alpha}-(t-f^{-1}(y))^{\alpha}}{\Gamma(\alpha+1)}
+\end{equation}
+
+Since Equation~\ref{eq:cav} is a Cavalieri integral, it has a clear geometric interpretation. The integral in eq xxx can be interpreted as the sum
 

### 2019-03-04 fractional/CMJ style files/article-template.tex
added the most basic mathematics to the tex file

@@
 \label{eq:rs}
-\int_0^{\tau} f(\tau)~dg_t(\tau),
+\int_0^{t} f(\tau)~dg_t(\tau),
 \end{equation}
@@
 
-Since Equation~\ref{eq:cav} is a Cavalieri integral, it has a clear geometric interpretation. The integral in eq xxx can be interpreted as the sum
+Since Equation~\ref{eq:cav} is a Cavalieri integral, it has a clear geometric interpretation. The integral in eq xxx can be interpreted as an infinite
+sum of infinitesimally small non–rectangular integration strips whose shape is determined by $\alpha$ and $t$. The shape of the integration 
+strip will change if either $\alpha$ or $t$ is changed. If $\alpha$ is equal to one, however, then the integral 
+reduces to a normal Riemann integral as the integration strips become rectangular for this particular choice of $\alpha$ (its shape is now also no longer affected by $t$).
 

### 2019-03-05 fractional/CMJ style files/article-template.tex
added new integral

@@
 
-\section{xxx}
+\section{Riemann-Liouville Fractional Integral}
+Let
+\begin{equation}
+If(x) := \int_0^x f(t) dt.
+\end{equation}
+If we apply the above operator in a repetative manner to $f$ we obtain the $n$th antiderivative of $f$ based at 0:
+\begin{equation}
+\label{eq:n_anti}
+I^nf(x) = \int_0^x\int_0^{x_1}\cdots \int_0^{x_{n-1}}f(x_n)~dx_n\cdots dx_2 dx_1.
+\end{equation}
+Applying Cauchy's formula for repetative integration to the above $n$th antiderivative of $f$ helps us express the above $n$th antiderivative as a single integral. 
+Applying Cauchy's formula to Equation~\ref{eq:n_anti} results in:
+\begin{equation}
+\label{eq:cauchy}
+I^nf(x) = \frac{1}{(n-1)!}\int_0^x (x-t)^{n-1}f(t)~dt.
+\end{equation}
+As an example if $f(x)=x$ and $n=2$ then Equation~\ref{eq:cauchy} reduces to:
+\begin{equation}
+I^3f(x) = \int_0^x (x-t)t~dt = \frac{t^2x}{2} - \frac{t^3}{3} \Bigg |_0^x = \frac{x^3}{3!}.
+\end{equation}
+The definition in Equation~\ref{eq:cauchy} can now be extended to an arbitrary fractional order by replacing $(n-1)!$ with the Gamma function:
+\begin{equation}
+\label{eq:frac_integral}
+I^{\alpha}f(x) = \frac{1}{\Gamma(\alpha)}\int_0^x (x-t)^{\alpha-1}f(t)~dt.
+\end{equation}
+Equation~\ref{eq:frac_integral} is known as the Riemann-Liouville fractional integral of order $\alpha$.
+\subsection{Examples}
+If $f(x)=x$ and $n=3$ then Equation~\ref{eq:frac_integral} reduces to:
+\begin{equation}
+I^3f(x) = \frac{1}{2!} \int_0^x (x-t)^2t~dt = \frac{1}{2}\left[\frac{t^4}{4} - \frac{2t^3}{3}+\frac{t^2x^2}{2}\right] \Bigg |_0^x = \frac{x^4}{4!} 
+\end{equation}
+
 The fractional integral is defined as (need to be more explicit here). Need to add how it has come about... Start with a single integral, expand to the general case and then 

### 2019-03-06 fractional/CMJ style files/article-template.tex
added new integral
started small section on Cavalieri

@@
 
+\section{Cavalieri Integral}
+Let the region $R$ be bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$ and $b(y)=4-y$. This region is shown in Fig.~\ref{fig:caval2}.\\
+%\begin{figure}[htb]
+%\centering
+%\includegraphics[width=0.3\textwidth]{fig12}
+%\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$. Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
+%\label{fig:ex1}
+%\end{figure}
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.75\textwidth]{fig13.eps}
+\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$.
+The figure also depicts the partition points $x_i^2$ as used in the Cavalieri sum (see Eq.~\ref{eq:cav_sum}).
+Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
+\label{fig:caval2}
+\end{figure}
+
+\noindent
+The area of $R$ can be determined as follows if we employ the classical notion of integration:
+\begin{equation}
+\int_0^2x\, dx+\int_2^44-x\, dx- \int_0^{\frac{1}{2}}x\, dx-\int_{\frac{1}{2}}^11-x\, dx = 3.75. 
+\end{equation}
+
+There, however, exists a more straightforward way do determine the area of $R$, i.e. we can sum together the area of non-rectangular integration strips inscribing $R$ instead of
+rectangular strips. Moreover, the shape of these non-rectangular integration strips should be determined by the function $a(y)$. We can express this notion more formally as 
+follows, let $(x_i^1)_{i=0}^{n}$ denote a partition on the $x$-axis, such that $a = x_0^1 < x_1^1 < \cdots < x_n^1 = b$, and $\Delta x_i^1 = x_{i+1}^1 - x_i^1$.
+We are now able to construct the following sum (the lower Cavalieri sum):
+\begin{equation}
+\label{eq:cav_sum}
+\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1.
+\end{equation}
+The partition points $(x_i^2)_{i=0}^{n}$ are depicted in Fig.~\ref{fig:caval2}. Note that Equation~\ref{eq:cav_sum} approximates the area of $R$. In the limit Equation~\ref{eq:cav_sum} approaches 
+the Cavalieri integral:
+\begin{equation}
+\label{eq:caval1}
+\int_{a(y)}^{b(y)}f(x)\, dx = \lim_{n\to \infty}\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1.
+\end{equation}
+It is, however, quite hard to evaluate the above integral directly. Fortunately, it is easy to convert a Cavalieri integral into an equivalent Riemann or Riemann-Stieltjes 
+integral using the transformation functions $h$ and $g$. Expressed mathematically:
+\begin{equation}
+ x
+\end{equation}
+
+\noindent
+Instead of trying to determine the area of $R$ using rectangular integration strips, it seems more natural 
+to use integration strips whose sides are translations of $a(y)$. Cavalieri's principle tells us that the area of an 
+arbitrary shaped integration strip is the product of its height and the length of its base. The area of $R$ 
+can be approximated by summing together multiple non--rectangular integration strips that inscribe $R$. This concept is illustrated in Fig.~\eqref{fig:caval2}. 
+More formally, consider a partition $(x_i^1)_{i=0}^{n}$ on the $x$-axis, such that $a = x_0^1 < x_1^1 < \cdots < x_n^1 = b$, and $\Delta x_i^1 = x_{i+1}^1 - x_i^1$.
+%As Fig.~\ref{fig:caval2} illustrates, the partition points $x_i^1$ are chosen to coincide with the $x$-coordinates at which the sides of the 
+%integration strips intersect the $x$-axis. Fig.~\ref{fig:caval2} also shows us that another partition $(x_i^2)_{i=0}^{n}$, on the $x$-axis, such that $a' = x_0^2 < x_1^2 < \cdots < x_n^2 = b'$
+%is automatically created when we make use of non--rectangular integration strips. The partition points $x_i^2$ 
+%coincide with the $x$-coordinates at which the sides of the 
+%integration strips intersect $f(x)$. 
+Let us now construct the following sum (i.e. a lower Cavalieri sum) with which we can approximate the area 
+of $R$:
+\begin{equation}
+\label{eq:cav_sum}
+\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1.
+\end{equation}
+The partition points $(x_i^2)_{i=0}^{n}$ are depicted in Fig.~\ref{fig:caval2}.
+The above sum can be interpreted as summing together the areas associated with $n$ non--rectangular integration strips.
+The left panel of Fig.~\ref{fig:caval2} depicts the scenario in which we made use of three integration strips.  
+The right panel of Fig.~\ref{fig:caval2} illustrates that the larger $n$ becomes the better Eq.~\eqref{eq:cav_sum} approximates the area of $R$.
+In the limit Eq.~\eqref{eq:cav_sum} approaches the Cavalieri integral:
+\begin{equation}
+\label{eq:caval1}
+\int_{a(y)}^{b(y)}f(x)\, dx = \lim_{n\to \infty}\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1.
+\end{equation}
+
+\noindent
+It is however hard to evaluate Eq.~\eqref{eq:caval1} in its present form. Fortuitously, we can transform the Cavalieri sum given in Eq.~\eqref{eq:caval1} into an ordinary Riemann sum
+if we can determine an expression for $x_i^2$ in terms of the partition points $x_i^1$, for all $i=0,1,\ldots,n$.
+Consider the collection of functions $\{a(y) + [x_i^1-a] = x_i^2: i=0,1,\ldots,n\}$.
+To find the partition points $x_i^2$ in terms of $x_i^1$ we substitute the function $f(x_i^2)$ for $y$ to obtain:
+\begin{align*}
+a\circ f (x_i^2)+[x_i^1-1] &= x_i^2\\
+x_i^2 &= \dfrac{x_i^1}{2},
+\end{align*}
+so that we have the general expression $x_i^2=h(x_i^1)$, with $h(x)=x/2$.\\
+
+\noindent
+The function $h$ allows us to rewrite the Cavalieri integral as an equivalent Riemann integral:
+\begin{equation}
+\label{eq:h_int}
+\lim_{n\to \infty}\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1 =  \lim_{n\to \infty}\sum_{i=0}^{n-1} f \circ h (x_i^1)\Delta x_i^1 = \int_a^b f \circ h (x)\, dx.
+\end{equation}
+
+\noindent
+It is now possible to compute the Cavalieri integral by evaluating its equivalent Riemann integral:
+\begin{equation}
+\int_{a(y)}^{b(y)}f(x)\, dx = \int_a^b f \circ h (x)\, dx = \dfrac{1}{2}\int_1^4x\, dx = 3.75.  
+\end{equation}
+
+\noindent
+Interestingly, the function $g=h^{-1}$ allows us to rewrite the Cavalieri integral as an equivalent Riemann--Stieltjes integral:
+\begin{equation}
+\label{eq:g_int}
+\lim_{n\to \infty}\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1 =  \lim_{n\to \infty} \sum_{i=0}^{n-1} f(x_i^2)[g(x_{i+1}^2)-g(x_{i}^2)] = \int_{a'}^{b'} f \, dg(x). 
+\end{equation}
+
+\noindent
+We can therefore also compute the Cavalieri integral by evaluating its equivalent Riemann--Stieltjes integral:
+\begin{equation}
+\int_{a(y)}^{b(y)}f(x)\, dx = \int_{a'}^{b'} f \, dg(x) = \int_{\frac{1}{2}}^2x\, d2x = 3.75.  
+\end{equation}
+
+\noindent
+We can quickly verify this to be correct by evaluating the area of $R$ with ordinary Riemann integration:
+\begin{equation}
+\int_0^2x\, dx+\int_2^44-x\, dx- \int_0^{\frac{1}{2}}x\, dx-\int_{\frac{1}{2}}^11-x\, dx = 3.75. 
+\end{equation}
+
 \section{Riemann-Liouville Fractional Integral}
@@
 \begin{equation}
-I^3f(x) = \int_0^x (x-t)t~dt = \frac{t^2x}{2} - \frac{t^3}{3} \Bigg |_0^x = \frac{x^3}{3!}.
+I^2f(x) = \int_0^x (x-t)t~dt = \frac{t^2x}{2} - \frac{t^3}{3} \Bigg |_0^x = \frac{x^3}{3!}.
 \end{equation}
@@
 \end{equation}
-Equation~\ref{eq:frac_integral} is known as the Riemann-Liouville fractional integral of order $\alpha$.
-\subsection{Examples}
-If $f(x)=x$ and $n=3$ then Equation~\ref{eq:frac_integral} reduces to:
+Equation~\ref{eq:frac_integral} is known as the Riemann-Liouville fractional integral of order $\alpha$. As an example if $f(x)=x$ and $\alpha=\frac{1}{2}$ then 
+Equation~\ref{eq:frac_integral} reduces to:
 \begin{equation}
-I^3f(x) = \frac{1}{2!} \int_0^x (x-t)^2t~dt = \frac{1}{2}\left[\frac{t^4}{4} - \frac{2t^3}{3}+\frac{t^2x^2}{2}\right] \Bigg |_0^x = \frac{x^4}{4!} 
+I^{\frac{1}{2}}f(x) = \frac{1}{\Gamma(\frac{1}{2})} \int_0^x \frac{t}{\sqrt{x-t}} dt = \frac{1}{\sqrt{\pi}}\left [ -\frac{2}{3}\sqrt{x-t}(t+2x)\right] \Bigg |_0^x=\frac{4}{3\sqrt{\pi}}x^{\frac{3}{2}}.
 \end{equation}
+Furthermore, it is straightforward to show that the $I$ operator satisfies:
+\begin{equation}
+I^{\alpha}I^{\beta}f(x) = I^{\alpha+\beta}f(x). 
+\end{equation}
+
+\section{Geometric Interpretation of Fractional Integrals}
 

### 2019-03-06 fractional/CMJ style files/article-template.tex
added an initial Cavalieri section to the paper

--- 2019-03-05 fractional/CMJ style files/article-template.tex
@@
 
+\section{Cavalieri Integral}
+Let the region $R$ be bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$ and $b(y)=4-y$. This region is shown in Fig.~\ref{fig:caval2}.\\
+%\begin{figure}[htb]
+%\centering
+%\includegraphics[width=0.3\textwidth]{fig12}
+%\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$. Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
+%\label{fig:ex1}
+%\end{figure}
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.75\textwidth]{fig13.eps}
+\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$.
+The figure also depicts the partition points $x_i^2$ as used in the Cavalieri sum (see Eq.~\ref{eq:cav_sum}).
+Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
+\label{fig:caval2}
+\end{figure}
+
+\noindent
+The area of $R$ can be determined as follows if we employ the classical notion of integration:
+\begin{equation}
+\int_0^2x\, dx+\int_2^44-x\, dx- \int_0^{\frac{1}{2}}x\, dx-\int_{\frac{1}{2}}^11-x\, dx = 3.75. 
+\end{equation}
+
+There, however, exists a more straightforward way do determine the area of $R$, i.e. we can sum together the area of non-rectangular integration strips inscribing $R$ instead of
+having to sum together the area of multiple rectangular integration strips.
+Moreover, the shape of the non-rectangular integration strips we should use is determined by the function $a(y)$.
+We can express this notion more formally as
+follows, let $(x_i^1)_{i=0}^{n}$ denote a partition on the $x$-axis, such that $a = x_0^1 < x_1^1 < \cdots < x_n^1 = b$, and $\Delta x_i^1 = x_{i+1}^1 - x_i^1$.
+We are now able to construct the following sum (the lower Cavalieri sum):
+\begin{equation}
+\label{eq:cav_sum}
+\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1.
+\end{equation}
+The partition points $(x_i^2)_{i=0}^{n}$ are depicted in Fig.~\ref{fig:caval2}. Note that Equation~\ref{eq:cav_sum} approximates the area of $R$. In the limit Equation~\ref{eq:cav_sum} approaches 
+the Cavalieri integral:
+\begin{equation}
+\label{eq:caval1}
+\int_{a(y)}^{b(y)}f(x)\, dx = \lim_{n\to \infty}\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1.
+\end{equation}
+It is, however, quite hard to evaluate the above integral directly. Fortunately, it is easy to convert a Cavalieri integral into an equivalent Riemann or Riemann-Stieltjes 
+integral by using the transformation functions $h$ and $g$. Expressed mathematically:
+\begin{equation}
+\int_{a(y)}^{b(y)}f(x)\,dx =\int_a^b f \circ h (x)\, dx = \int_{a'}^{b'} f(x) dg(x).
+\end{equation}
+We can calculate $g$ as follows:
+\begin{equation}
+g(x) = x - a\circ f(x) + a.
+\end{equation}
+Moreover, $h=g^{-1}$. We can now evaluate the Cavalieri integral by using its equivalent Riemann or Rieman-Stieltjes integral.
+If we use its Riemann equivalent we obtain:
+\begin{equation}
+\int_{a(y)}^{b(y)}f(x)\, dx = \int_a^b f \circ h (x)\, dx = \dfrac{1}{2}\int_1^4x\, dx = 3.75.  
+\end{equation}
+If we use its Riemann-Stieltjes equivalent we obtain:
+\begin{equation}
+\int_{a(y)}^{b(y)}f(x)\, dx = \int_{a'}^{b'} f \, dg(x) = \int_{\frac{1}{2}}^2x\, d2x = 3.75.  
+\end{equation}
+
+Conversely, if $g$ is known (and not $a(y)$) and $g(a') = a$ then we can calculate $a(y)$ using the following:
+\begin{equation}
+\label{eq:a_y}
+a(y) = f^{-1}(y) - g\circ f^{-1}(y) + g(a'). 
+\end{equation}
+Note the power of Equation~\ref{eq:a_y} it allows us to transform a Riemann-Stieltjes integral into a Cavalieri integral. 
+This transformation allows us to give a geometric interpretation of a Riemann-Stieltjes integral. The interpretation being,
+the sum of an infinite amount of non-rectangular infinitesimals whose shape is determined by $a(y)$.
+
 \section{Riemann-Liouville Fractional Integral}

### 2019-03-07 fractional/CMJ style files/article-template.tex
added an expression for h
added Riemann Stieltjes

@@
 Web links can be embedded using the \verb~\url{...}~ command, which will result in something like \url{http://www.maa.org}.  These links will be active and stylized in the online publication.
+
+\section{Riemann-Stieltjes Integral}
+Recall that the Riemann-Stieltjes integral is defined as follows:
+\begin{equation}
+\label{eq:g_int2}
+\int_{a'}^{b'} f(x) dg(x) =  \lim_{n \rightarrow \infty}\sum_{i=0}^{n-1} f(x_i^2)[g(x_{i+1}^2)-g(x_{i}^2)], 
+\end{equation}
+%Fig.~\ref{fig:2d_geo} depicts a region whose area can be determined by considering non--rectangular integration strips.
+%. Note that the shape of the integration strips are determined by $a(y)$. 
+%In Fig.~\ref{fig:2d_geo}, the function $a(y)$ is depicted in red. If we translate $a(y)$ along the $x$-axis we actually create two partitions on the $x$-axis, 
+%i.e. $(x_i^1)_{i=0}^{n}$ and $(x_i^2)_{i=0}^{n}$ with $x_i^1\in[a,b]$ and $x_i^2\in[a',b']$.  To map partition points in $[a',b']$ to partition points 
+%in $[a,b]$ we use the function $g$. The reverse is achieved through $h$. The functions $g$ and $h$ depend soly on $a(y)$ and are also 
+%computed with it.
+\noindent
+with $(x_i^2)_{i=0}^n$ being arbitrary partition points on the $x$-axis. Eq.~\eqref{eq:g_int2} shows us that the function of the integrator $g$ is to
+map points in the interval $[a',b']$ to other locations on the $x$-axis. When $g$ is monotone increasing, it maps points in the interval $[a',b']$ to $[a,b]$,
+with $a = g(a')$ and $b = g(b')$. The integral in Equation~\ref{eq:g_int2} is hard to evaluate in its present form. If $g$ is differentiable, however, then it becomes trivial to 
+evaluate a Riemann-Stieltjes integral due to the following identity:
+\begin{equation}
+\int_{a'}^{b'} f(x) dg(x) = \int_{a'}^{b'} f(x)g'(x)~dx.
+\end{equation}
+As an example:
+\begin{equation}
+\int_{\frac{1}{2}}^{2} f(x) dg(x)=\int_{\frac{1}{2}}^2 x~d2x = \int_{\frac{1}{2}}^2 2x~dx = 3.75. 
+\end{equation}
 
@@
 
+\begin{equation}
+h_t^{\alpha}(x) = t - \sqrt[\alpha]{t^{\alpha} - \Gamma(\alpha+1)x}
+\end{equation}
+
 \section{First-level section heading}

### 2019-03-07 fractional/CMJ style files/article-template.tex
started to add the gamma function

@@
 \noindent
-with $(x_i^2)_{i=0}^n$ being arbitrary partition points on the $x$-axis. Eq.~\eqref{eq:g_int2} shows us that the function of the integrator $g$ is to
+\textbf{NEED TO REWRITE SOME OF IT} with $(x_i^2)_{i=0}^n$ being arbitrary partition points on the $x$-axis. Eq.~\eqref{eq:g_int2} shows us that the function of the integrator $g$ is to
 map points in the interval $[a',b']$ to other locations on the $x$-axis. When $g$ is monotone increasing, it maps points in the interval $[a',b']$ to $[a,b]$,
@@
 the sum of an infinite amount of non-rectangular infinitesimals whose shape is determined by $a(y)$.
+
+\section{Gamma Function}
+The gamma function is defined for all real numbers except for the non-negative integers. Moreover, it is a natural extends the factorial of an integer 
+to any real number. The Gamma function is defined as:
+\begin{equation}
+\Gamma(x) = \int_0^{\infty} t^{x-1} e^{-t}\,dt
+\end{equation}
 

### 2019-03-11 fractional/func_plotter.py
added func_plotter

@@ -100,11 +100,47 @@ def plot_area(t_vector,alpha_vector,y_points,f_inv,f):
             if i == 0:
               ax[k,i].set_ylabel("t = "+str(round(t_vector[k],1)))
     plt.show() 
-           
 
+def plot_gamma(x):
+    y = np.zeros((len(x),))
+
+    for k in range(len(x)):
+        #print(k)
+        #print(x[k])
+        try:
+           # put the code you want to try here
+           y[k] = math.gamma(x[k])
+        except ValueError:
+           # what to do if we get a value error
+           y[k] = np.NaN
+    
+    plt.plot(x,y) 
+    plt.ylim([-5,5])      
+    plt.show()
+
+def plot_gamma2(x):
+    y = np.zeros((len(x),))
+
+    for k in range(len(x)):
+        #print(k)
+        #print(x[k])
+        try:
+           # put the code you want to try here
+           y[k] = math.gamma(x[k])
+        except ValueError:
+           # what to do if we get a value error
+           y[k] = np.NaN
+    
+    plt.plot(x,y) 
+    plt.ylim([-5,5])      
+    plt.show()
  
 
 if __name__ == "__main__":
+   x = np.linspace(-5,5,2000)
+   x = x[1:]
+   plot_gamma(x)
+   '''
    num_points = 5
    t_f = 10
    alpha_f = 2    
@@ -124,7 +160,7 @@ if __name__ == "__main__":
    plot_area(t_v,alpha_v,y_points,f1_inv,f1)
    plot_area(t_v,alpha_v,y_points,f2_inv,f2) 
    #plot_a_functions(t_v,alpha_v,y_points,f2_inv,f2)
-
+   '''
    '''
    fig, ax = plt.subplots(10, 10, sharex='all', sharey='all')
 

### 2019-03-11 fractional/func_plotter.py
improved the gamma plot

@@ -119,6 +119,9 @@ def plot_gamma(x):
     plt.show()
 
 def plot_gamma2(x):
+    
+    x = np.linspace(-5,-4,1000)
+    x = x[1:-2]
     y = np.zeros((len(x),))
 
     for k in range(len(x)):
@@ -131,7 +134,90 @@ def plot_gamma2(x):
            # what to do if we get a value error
            y[k] = np.NaN
     
-    plt.plot(x,y) 
+    plt.plot(x,y,"b")
+    plt.hold('on')
+    
+    x = np.linspace(-4,-3,1000)
+    x = x[1:-2]
+    y = np.zeros((len(x),))
+
+    for k in range(len(x)):
+        #print(k)
+        #print(x[k])
+        try:
+           # put the code you want to try here
+           y[k] = math.gamma(x[k])
+        except ValueError:
+           # what to do if we get a value error
+           y[k] = np.NaN
+    
+    plt.plot(x,y,"b")
+     
+    x = np.linspace(-3,-2,1000)
+    x = x[1:-2]
+    y = np.zeros((len(x),))
+
+    for k in range(len(x)):
+        #print(k)
+        #print(x[k])
+        try:
+           # put the code you want to try here
+           y[k] = math.gamma(x[k])
+        except ValueError:
+           # what to do if we get a value error
+           y[k] = np.NaN
+    
+    plt.plot(x,y,"b")
+    
+    x = np.linspace(-2,-1,1000)
+    x = x[1:-2]
+    y = np.zeros((len(x),))
+
+    for k in range(len(x)):
+        #print(k)
+        #print(x[k])
+        try:
+           # put the code you want to try here
+           y[k] = math.gamma(x[k])
+        except ValueError:
+           # what to do if we get a value error
+           y[k] = np.NaN
+    
+    plt.plot(x,y,"b")
+
+    x = np.linspace(-1,0,1000)
+    x = x[1:-2]
+    y = np.zeros((len(x),))
+
+    for k in range(len(x)):
+        #print(k)
+        #print(x[k])
+        try:
+           # put the code you want to try here
+           y[k] = math.gamma(x[k])
+        except ValueError:
+           # what to do if we get a value error
+           y[k] = np.NaN
+    
+    plt.plot(x,y,"b")
+
+    x = np.linspace(0,5,1000)
+    x = x[1:]
+    y = np.zeros((len(x),))
+
+    for k in range(len(x)):
[…]

### 2019-03-13 fractional/func_plotter.py
added a gamma plotting function

@@ -217,7 +217,15 @@ def plot_gamma2(x):
     
     plt.plot(x,y,"b")
     
-
+    plt.axvline(x=-4, color='r', linestyle='--')
+    plt.axvline(x=-3, color='r', linestyle='--')
+    plt.axvline(x=-2, color='r', linestyle='--')
+    plt.axvline(x=-1, color='r', linestyle='--')
+    plt.axvline(x=0, color='k')
+    plt.axhline(y=0, color='k')
+    plt.grid('on')
+    plt.xlabel(r"$x$")
+    plt.ylabel(r"$\Gamma(x)$")
     plt.ylim([-5,5])      
     plt.show()
  

### 2019-03-13 fractional/CMJ style files/article-template.tex
improved section on gamma function

@@
 \section{Gamma Function}
-The gamma function is defined for all real numbers except for the non-negative integers. Moreover, it is a natural extends the factorial of an integer 
-to any real number. The Gamma function is defined as:
+The gamma function was first devised by Euler.
+The gamma function is defined for all real numbers except for the non-negative integers.
+Moreover, it is a natural extension of the factorial function to the real numbers.
+The Gamma function is defined as:
 \begin{equation}
@@
 \end{equation}
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.75\textwidth]{gamma.pdf}
+\caption{A plot of $\Gamma(x)$. $\Gamma(x)$ is not defined for the non-negative integers.}
+\label{fig:gamma}
+\end{figure}
 

### 2019-03-25 fractional/CMJ style files/article-template.tex
started introduction

@@
 
-\title{Visualization of Fractional Integrals}
+\title{Visualization of [fulle name] Fractional Integrals}
 \author{Woodrow Wilson and Herbert Hoover} %%leave blank in initial submission to allow for double blind reviewing
@@
 
-\noindent
-The \textit{College Mathematics Journal} style incorporates the following \LaTeX\ packages.  These styles should \textit{not} be included in the document header.
-\begin{itemize}
-\item times
-\item pifont
-\item graphicx
-\item color
-\item AMS styles: amsmath, amsthm, amsfonts, amssymb
-\item url
-\end{itemize}
-Use of other \LaTeX\ packages should be minimized as much as possible.
-Math notation, like $c = \sqrt{a^2 +b^2}$, can be left in \TeX's default Computer Modern typefaces for manuscript preparation; or, if you have the appropriate fonts installed, the \texttt{mathtime} or \texttt{mtpro} packages may be used, which will better approximate the finished article.
+It can be argued that fractional calculus is as old as classical calculus itself. The father of calculus, Leibnis, mentiones the notion of a fractional 
+order derivative in a letter he sent to L'Hospital. In this letter he answers a question L'Hospital poses. Liouville and Riemann laid much of the groundwork which was 
+needed to define the Riemann-Liouville fractional integral [Laurent’].
 
-Web links can be embedded using the \verb~\url{...}~ command, which will result in something like \url{http://www.maa.org}.  These links will be active and stylized in the online publication.
+It was pointed out at the first international conference on fractional calculus in New Haven (USA) in 1974 that literature lacked an acceptable geometric and physical
+interpretation of the fractional integral []. Consequently the last few decades has seen a number of papers that attempt to rectify this. There now exists probabilistic interpretations, 
+geometric interpretations and ecenomic interpretations of the fractional integral.
+
+In this paper we present a novel geometric interpretation of the Riemann-Liouville fractional integral. The interpretation we present here is quite useful from 
+a pedigogical point of view as
 

### 2019-03-25 fractional/CMJ style files/article-template.tex
started fleshing out the introduction of the paper

@@
 
-It can be argued that fractional calculus is as old as classical calculus itself. The father of calculus, Leibnis, mentiones the notion of a fractional 
-order derivative in a letter he sent to L'Hospital. In this letter he answers a question L'Hospital poses. Liouville and Riemann laid much of the groundwork which was 
+It can be argued that fractional calculus is as old as classical calculus itself.
+Leibniz, who is regarded by many as the farther of calculs, invented the following notation: $\frac{d^n f(x)}{d^n x}$ Leibniz mentiones the notion of a fractional
+order derivative in a letter he sent to L'Hospital.
+In this letter he is responding to a question L'Hospital posed.
+L'Hospital asked the question: ``What if $n$ be a $\frac{1}{2}$?''.
+Liouville and Riemann laid much of the groundwork which was
 needed to define the Riemann-Liouville fractional integral [Laurent’].
@@
 It was pointed out at the first international conference on fractional calculus in New Haven (USA) in 1974 that literature lacked an acceptable geometric and physical
-interpretation of the fractional integral []. Consequently the last few decades has seen a number of papers that attempt to rectify this. There now exists probabilistic interpretations, 
+interpretation of the fractional integral and that this has been the case for more than 300 years [].
+Consequently the last few decades has seen a number of papers that attempt to rectify this.
+There now exists probabilistic interpretations,
 geometric interpretations and ecenomic interpretations of the fractional integral.
 
-In this paper we present a novel geometric interpretation of the Riemann-Liouville fractional integral. The interpretation we present here is quite useful from 
-a pedigogical point of view as
+In this paper we present a novel geometric interpretation of the Riemann-Liouville fractional integral. The interpretation we present here is especially useful from 
+a pedigogical point of view as it is similar in nature to the definition of classical integration. In ordinary integration we can interpret the integral 
+as an infinite sum of rectangular infinitesimals. In this paper, we demonstrate at the hand of examples that the Riemann-Liouville fractional integral can be interpreted 
+as an infinite sum of non-rectangular infinitesimals whose shape is determined by the order of integration $\alpha$ and the integration limit $x$.
 

### 2019-03-26 fractional/CMJ style files/article-template.tex
added a paragraph to introduction

@@
 
-\begin{biog} %comment out in initial submission to allow for double blind reviewing
-\item[\biogpic{\includegraphics[width=84pt]{Woodrow_Wilson.pdf}}Woodrow Wilson] (twwilson@princeton.edu) received his PhD in history and political science from Johns Hopkins University.
+%\begin{biog} %comment out in initial submission to allow for double blind reviewing
+%\item[\biogpic{\includegraphics[width=84pt]{Woodrow_Wilson.pdf}}Woodrow Wilson] (twwilson@princeton.edu) received his PhD in history and political science from Johns Hopkins University.
 He held visiting positions at Cornell and Wesleyan before joining the faculty at Princeton, where he was eventually appointed president of the university.
@@
 
-\item[\biogpic{\includegraphics[width=84pt]{Herbert_Hoover.pdf}}Herbert Hoover] (hchoover@stanford.edu) entered Stanford University in 1891, after failing all of the entrance exams except mathematics.
+%\item[\biogpic{\includegraphics[width=84pt]{Herbert_Hoover.pdf}}Herbert Hoover] (hchoover@stanford.edu) entered Stanford University in 1891, after failing all of the entrance exams except mathematics.
 He received his BS degree in geology in 1895, spent time as a mining engineer, then was appointed by his co-author to the U.S.
 Food Administration and the Supreme Economic Council, where he orchestrated the greatest famine relief efforts of all time.
-\end{biog}
+%\end{biog}
 
-It can be argued that fractional calculus is as old as classical calculus itself.
-Leibniz, who is regarded by many as the farther of calculs, invented the following notation: $\frac{d^n f(x)}{d^n x}$ Leibniz mentiones the notion of a fractional
+The idea of integer-order differentiation and integration is well known to most undergraduates.
+However, undergraduates are less familiar with the idea of an arbitrary order differential or integral (i.e.
+fractional-order calculus).
+Even though most undergraduates have a limited understanding of fractional-order calculus they generally are quite interested in the subject. This is quite 
+evident from perusing mathematical social media platforms and from surveying articles published in undergraduate journals []. The reason fractional calsulus is not generally 
+taught at the undegraduate level is partly due to the fact that the notion is quite abstract and it is therefore difficult to interpret geometrically. This paper 
+is specifically written for undergraduate lecturers and is very pedigogical in nature. The aim of the paper is to motivate and enable undergraduate 
+lectures to introduce undergraduate students to this fascinating mathematical discipline.
+
+This is not to say that there  This is partly, because there is no simplistic geometric interpretation for fractional calculus.
+
+It can be argued that fractional-order calculus is as old as classical calculus itself.
+Leibniz, who is regarded by many scholars as the farther of calculus, invented the following notation: $\frac{d^n y}{d x^n}$.
+Leibniz mentiones the notion of a fractional
 order derivative in a letter he sent to L'Hospital.
 In this letter he is responding to a question L'Hospital posed.
-L'Hospital asked the question: ``What if $n$ be a $\frac{1}{2}$?''.
-Liouville and Riemann laid much of the groundwork which was
-needed to define the Riemann-Liouville fractional integral [Laurent’].
+L'Hospital asked the question: ``\emph{What if $n$ be a $\frac{1}{2}$?}''.
+He responded, quite prophetically, ``\emph{This is an apparant paradox from which, one day, useful
+consequences will be drawn}.'' Liouville and Riemann laid much of the groundwork which was needed to define the Riemann-Liouville fractional integral [Laurent’].
 

### 2019-03-26 fractional/CMJ style files/article-template.tex
new sentences

@@
 taught at the undegraduate level is partly due to the fact that the notion is quite abstract and it is therefore difficult to interpret geometrically. This paper 
-is specifically written for undergraduate lecturers and is very pedigogical in nature. The aim of the paper is to motivate and enable undergraduate 
-lectures to introduce undergraduate students to this fascinating mathematical discipline.
+is specifically written for undergraduate lecturers and is very pedigogical in nature. In this paper we present a novel geometric interpretation of the 
+Riemann-Liouville fractional integral which is similar in nature to the classical interpretation of classical integration. Our hope is that this 
+geometric interpretation will encourage and enable undergraduate lectures to introduce undergraduates to this fascinating mathematical discipline.
 

### 2019-03-26 fractional/CMJ style files/article-template.tex
new sentences

@@
 %\end{biog}
+%This is not to say that there  This is partly, because there is no simplistic geometric interpretation for fractional calculus.  
+\noindent
+Fractional-order calculus can be summarized as the generalization of integer-order differentials and integrals to an arbitrary order. It can be argued that 
+fractional-order calculus is as old as classical calculus itself.
+Leibniz, who is regarded by many scholars as the farther of calculus, invented the following notation: $\frac{d^n y}{d x^n}$.
+Leibniz mentiones the notion of a fractional
+order derivative in a letter he sent to L'Hospital.
+In this letter he answers the following question posed by L'Hospital: ``\emph{What if $n$ be a $\frac{1}{2}$?}''.
+He responded, quite prophetically, ``\emph{This is an apparant paradox from which, one day, useful
+consequences will be drawn}.'' In this paper, we will mainly focus our attention on fractional-order integration and in particular investigate the Riemann-Liouville fractional 
+integral. It is Liouville and Riemann who laid much of the groundwork which was needed to define what is now known as the Riemann-Liouville fractional integral [Laurent’].
+
+It was pointed out at the first international conference on fractional calculus in New Haven (USA) in 1974 that literature lacked an acceptable geometric and physical
+interpretation of the fractional integral.
+In 1974, this had been the state of affairs for more than 300 years [].
+Subsequently, the last few decades has seen a number of papers that attempt to rectify this.
+There now exists probabilistic interpretations,
+geometric interpretations and ecenomic interpretations of the fractional integral.
 
@@
 Even though most undergraduates have a limited understanding of fractional-order calculus they generally are quite interested in the subject. This is quite 
-evident from perusing mathematical social media platforms and from surveying articles published in undergraduate journals []. The reason fractional calsulus is not generally 
-taught at the undegraduate level is partly due to the fact that the notion is quite abstract and it is therefore difficult to interpret geometrically. This paper 
-is specifically written for undergraduate lecturers and is very pedigogical in nature. In this paper we present a novel geometric interpretation of the 
-Riemann-Liouville fractional integral which is similar in nature to the classical interpretation of classical integration. Our hope is that this 
+evident from perusing mathematical social media platforms and from surveying articles published in undergraduate journals []. One of the reason fractional calculus is not generally 
+taught at the undegraduate level is due to the fact that the notion is quite abstract and it is therefore difficult to interpret geometrically. In this paper adress this shortcomming by presenting  
+a novel geometric interpretation of the Riemann-Liouville fractional integral which is similar in nature to the classical interpretation of classical integration. Our hope is that this 
 geometric interpretation will encourage and enable undergraduate lectures to introduce undergraduates to this fascinating mathematical discipline.
-
-This is not to say that there  This is partly, because there is no simplistic geometric interpretation for fractional calculus.
-
-It can be argued that fractional-order calculus is as old as classical calculus itself.
-Leibniz, who is regarded by many scholars as the farther of calculus, invented the following notation: $\frac{d^n y}{d x^n}$.
-Leibniz mentiones the notion of a fractional
-order derivative in a letter he sent to L'Hospital.
-In this letter he is responding to a question L'Hospital posed.
-L'Hospital asked the question: ``\emph{What if $n$ be a $\frac{1}{2}$?}''.
-He responded, quite prophetically, ``\emph{This is an apparant paradox from which, one day, useful
-consequences will be drawn}.'' Liouville and Riemann laid much of the groundwork which was needed to define the Riemann-Liouville fractional integral [Laurent’].
-
-It was pointed out at the first international conference on fractional calculus in New Haven (USA) in 1974 that literature lacked an acceptable geometric and physical
-interpretation of the fractional integral and that this has been the case for more than 300 years [].
-Consequently the last few decades has seen a number of papers that attempt to rectify this.
-There now exists probabilistic interpretations,
-geometric interpretations and ecenomic interpretations of the fractional integral.
 

### 2019-03-26 fractional/CMJ style files/article-template.tex
new sentences

@@
 \noindent
-Fractional-order calculus can be summarized as the generalization of integer-order differentials and integrals to an arbitrary order. It can be argued that 
-fractional-order calculus is as old as classical calculus itself.
+Fractional-order calculus can be summarized as the generalization of integer-order differentiation and integration to an arbitrary order.
 Leibniz, who is regarded by many scholars as the farther of calculus, invented the following notation: $\frac{d^n y}{d x^n}$.
@@
 He responded, quite prophetically, ``\emph{This is an apparant paradox from which, one day, useful
-consequences will be drawn}.'' In this paper, we will mainly focus our attention on fractional-order integration and in particular investigate the Riemann-Liouville fractional 
+consequences will be drawn}.'' It can, therefore, be argued that fractional-order calculus is as old as classical calculus itself.
+In this paper, we will mainly focus our attention on fractional-order integration and in particular investigate the Riemann-Liouville fractional
 integral. It is Liouville and Riemann who laid much of the groundwork which was needed to define what is now known as the Riemann-Liouville fractional integral [Laurent’].
@@
 interpretation of the fractional integral.
-In 1974, this had been the state of affairs for more than 300 years [].
+Interestingly in 1974, this had alreaady been the state of affairs for more than 300 years [].
 Subsequently, the last few decades has seen a number of papers that attempt to rectify this.
@@
 geometric interpretations and ecenomic interpretations of the fractional integral.
+
+In this paper we present a novel geometric interpretation of the Riemann-Liouville fractional integral. The interpretation we present here is especially useful from 
+a pedigogical point of view as it is similar in nature to the definition of classical integration. In ordinary integration we can interpret the integral 
+as an infinite sum of rectangular infinitesimals. In this paper, we demonstrate at the hand of examples that the Riemann-Liouville fractional integral can be interpreted 
+as an infinite sum of non-rectangular infinitesimals whose shape is determined by the order of integration $\alpha$ and the integration limit $x$.
 
@@
 geometric interpretation will encourage and enable undergraduate lectures to introduce undergraduates to this fascinating mathematical discipline.
-
-In this paper we present a novel geometric interpretation of the Riemann-Liouville fractional integral. The interpretation we present here is especially useful from 
-a pedigogical point of view as it is similar in nature to the definition of classical integration. In ordinary integration we can interpret the integral 
-as an infinite sum of rectangular infinitesimals. In this paper, we demonstrate at the hand of examples that the Riemann-Liouville fractional integral can be interpreted 
-as an infinite sum of non-rectangular infinitesimals whose shape is determined by the order of integration $\alpha$ and the integration limit $x$.
 

### 2019-03-26 fractional/CMJ style files/article-template.tex
edited introduction again

@@
 \noindent
-Fractional-order calculus can be summarized as the generalization of integer-order differentiation and integration to an arbitrary order.
-Leibniz, who is regarded by many scholars as the farther of calculus, invented the following notation: $\frac{d^n y}{d x^n}$.
-Leibniz mentiones the notion of a fractional
-order derivative in a letter he sent to L'Hospital.
-In this letter he answers the following question posed by L'Hospital: ``\emph{What if $n$ be a $\frac{1}{2}$?}''.
-He responded, quite prophetically, ``\emph{This is an apparant paradox from which, one day, useful
-consequences will be drawn}.'' It can, therefore, be argued that fractional-order calculus is as old as classical calculus itself.
+Leibniz, who is regarded by many scholars as the farther of calculus, is credited with inventing the following notation: $\frac{d^n y}{d x^n}$. 
+A natural question which arises when one inspects this notation is: Can $n$ be a non-integer value? L'Hospital phrased it differently: ``\emph{What if $n$ be a $\frac{1}{2}$?}''. 
+In a letter Leibniz sent to L'Hospital, he himself commented on this intriguing question: ``\emph{This is an apparant paradox from which, one day, useful 
+consequences will be drawn}.''
+
+It is, however, Liouville and Riemann who laid the theoretical groundwork which was needed to develop the field of fractional calculus. 
+Their contribution played a crucial part in defining what is now known as the Riemann-Lioville fractional integral. Fractional calculus can be 
+formally defined as the study of a an arbitrary order differentiation and integration operators.
+
+Fractional calculus can be summarized as the generalization of integer-order differentiation and integration to an arbitrary order.
+Fractional-order calculus is as old as classical calculus itself.
 In this paper, we will mainly focus our attention on fractional-order integration and in particular investigate the Riemann-Liouville fractional
@@
 interpretation of the fractional integral.
-Interestingly in 1974, this had alreaady been the state of affairs for more than 300 years [].
+Interestingly in 1974, this had already been the state of affairs for more than 300 years [].
 Subsequently, the last few decades has seen a number of papers that attempt to rectify this.
 There now exists probabilistic interpretations,
-geometric interpretations and ecenomic interpretations of the fractional integral.
+geometric interpretations, physical interpretations and ecenomic interpretations of the fractional integral.
 
 In this paper we present a novel geometric interpretation of the Riemann-Liouville fractional integral. The interpretation we present here is especially useful from 
-a pedigogical point of view as it is similar in nature to the definition of classical integration. In ordinary integration we can interpret the integral 
-as an infinite sum of rectangular infinitesimals. In this paper, we demonstrate at the hand of examples that the Riemann-Liouville fractional integral can be interpreted 
+a pedigogical point of view as it is similar in nature to the definition of classical integration.
+as an infinite sum of rectangular infinitesimals.
+In this paper, we demonstrate at the hand of examples that the Riemann-Liouville fractional integral can be interpreted
 as an infinite sum of non-rectangular infinitesimals whose shape is determined by the order of integration $\alpha$ and the integration limit $x$.
+Furthermore, please note that the intended audience of this
+paper is undergraduate students and lecturers and as such we do not present .  In ordinary integration we can interpret the integral
 

### 2019-03-26 fractional/CMJ style files/article-template.tex
changed introduction again

@@
 In a letter Leibniz sent to L'Hospital, he himself commented on this intriguing question: ``\emph{This is an apparant paradox from which, one day, useful 
-consequences will be drawn}.''
-
-It is, however, Liouville and Riemann who laid the theoretical groundwork which was needed to develop the field of fractional calculus. 
-Their contribution played a crucial part in defining what is now known as the Riemann-Lioville fractional integral. Fractional calculus can be 
-formally defined as the study of a an arbitrary order differentiation and integration operators.
-
-Fractional calculus can be summarized as the generalization of integer-order differentiation and integration to an arbitrary order.
-Fractional-order calculus is as old as classical calculus itself.
-In this paper, we will mainly focus our attention on fractional-order integration and in particular investigate the Riemann-Liouville fractional
-integral. It is Liouville and Riemann who laid much of the groundwork which was needed to define what is now known as the Riemann-Liouville fractional integral [Laurent’].
+consequences will be drawn}.'' The mathematical discipline in which we study the extension of derivatives and integrals to non-integer orders is known as 
+fractional calculus.
+Liouville and Riemann laid most of theoretical groundwork which was needed to develop the field of fractional calculus.
+In particular, their contribution played a crucial part in defining what is now known as the
+Riemann-Lioville fractional integral. In this paper we will not  fractional calculus to the Riemann-Lioville fractional integral.
 
 It was pointed out at the first international conference on fractional calculus in New Haven (USA) in 1974 that literature lacked an acceptable geometric and physical
-interpretation of the fractional integral.
+interpretation of fractional calculus (and therefore by implication the .
 Interestingly in 1974, this had already been the state of affairs for more than 300 years [].
@@
 paper is undergraduate students and lecturers and as such we do not present .  In ordinary integration we can interpret the integral
+
+%Fractional calculus can be summarized as the generalization of integer-order differentiation and integration to an arbitrary order.
+%Fractional-order calculus is as old as classical calculus itself.
+In this paper, we will mainly focus our attention on fractional-order integration and in particular investigate the Riemann-Liouville fractional
+%integral. It is Liouville and Riemann who laid much of the groundwork which was needed to define what is now known as the Riemann-Liouville fractional integral [Laurent’].
 

### 2019-03-27 fractional/CMJ style files/article-template.tex
significantly improved introduction

@@
 In a letter Leibniz sent to L'Hospital, he himself commented on this intriguing question: ``\emph{This is an apparant paradox from which, one day, useful 
-consequences will be drawn}.'' The mathematical discipline in which we study the extension of derivatives and integrals to non-integer orders is known as 
-fractional calculus.
-Liouville and Riemann laid most of theoretical groundwork which was needed to develop the field of fractional calculus.
+consequences will be drawn}.''
+
+The mathematical discipline in which we study the extension of derivatives and integrals to non-integer orders is known as fractional calculus. Liouville and Riemann laid most 
+of theoretical groundwork which was needed to develop the field of fractional calculus. Fractional calculus has now developed into a mature discipline. 
+However, there is one aspect of the discipline which only started to develop fairly recently: its physical and geometric interpretability.
+At the first international conference on fractional calculus in
+New Haven (USA) (which took place in 1974) it was pointed out that literature lacked an acceptable geometric and physical interpretation of fractional calculus.
+Subsequently, the last few decades has seen
+a number of papers that attempt to rectify this. There now exists probabilistic interpretations, geometric interpretations, physical interpretations and ecenomic 
+interpretations of fractional order integrals and differentials.
+
+In this article we specifically focus on the geometric interpretation of fractional integrals.
+To be more specific, we present a novel geometric interpretation of the Riemann-Liouville fractional integral.
+As we mentioned earlier, Riemann and Liouville played an important role in the development of fractional calculus. Their work was crucial in defining what is now know as 
+the Riemann-Lioville fractional integral. At this point in time the reader should be made aware of the fact that there exists many other accepted fractional integral definitions in the literature.
+We, however, do not discuss them any further in this article. Investigating whether one can apply the proposed framework to other fractional integral definitions will be adressed in a 
+future endeavour.
+
+Moreover, the geometric interpretation we present here is especially useful from a pedigogical point of view as it is similar in nature to the definition of classical integration.
+The Riemann integral
+can be interpreted as an infinite sum of rectangular infinitesimals. In this paper, we show that the Riemann-Liouville fractional integral can be interpreted 
+as an infinite sum of non-rectangular infinitesimals whose shape is determined by the order of integration $\alpha$ and the integration limit $x$.
+
+Due to the 
+Even though most undergraduates have a limited understanding of fractional-order calculus they generally are quite interested in the subject. This is quite 
+evident from perusing mathematical social media platforms and from surveying articles published in undergraduate journals []. One of the reason fractional calculus is not generally 
+taught at the undegraduate level is due to the fact that the notion is quite abstract and it is therefore difficult to interpret geometrically. In this paper adress this shortcomming by presenting  
+a novel geometric interpretation of the Riemann-Liouville fractional integral which is similar in nature to the classical interpretation of classical integration. Our hope is that this 
+geometric interpretation will encourage and enable undergraduate lectures to introduce undergraduates to this fascinating mathematical discipline.
+
+We specifically wrote this paper for people with a pedagogical interest, undergraduate students and for the layman who finds integration theory intriguing and 
+as such we will try to steer clear from using too many mathematical definitions and proofs. We will rather convey our ideas using as many examples as possible. From the 
+three groups mentioned we believe that the undergraduate student will find this article the most useful. Although undergraduate students have a limited understanding of 
+fractional calculus they generally are quite interested in the subject. This is quite evident from perusing mathematical social media platforms and from surveying 
+articles published in undergraduate journals []. One of the reasons undergraduates struggle to grasp fractional calculus is because it is such an abstract concept. We believe 
+that the geometric interpretation we present in this
+
+Our hope is that the geometric 
+interpretation we present here will encourage and enable undergraduate lectures to introduce undergraduates to this fascinating mathematical discipline.
+
+We therefore only present the min-
+imum number of mathematical definitions that are needed to convey the new geometric framework.
+
+This article is not an in depth study into the field of integral calculus, but should rather be viewed as an introductory text
+
+It is important to point out at this point that there exists numerous acccepted definitions of fractional integration and differentiation. For the sake of 
+simplicity we decided to focus on one In this paper we will focus 
+on the Riemann-Lioville fractional integral.
+
+There are many accepted definitions of fractional order differentiation and integration. In this paper we will only focus
+
 In particular, their contribution played a crucial part in defining what is now known as the 
-Riemann-Lioville fractional integral. In this paper we will not  fractional calculus to the Riemann-Lioville fractional integral.
+Riemann-Lioville fractional integral. In this paper, we present a novel geometric interpretation of the Riemann-Lioville fractional integral which is similar 
+in nature to the classical interpretation of an ordinary Riemann integral. An ordinary Riemann integral can be interpreted as an infinitesimal sum of rectangular 
+infinitesimals.
 
-It was pointed out at the first international conference on fractional calculus in New Haven (USA) in 1974 that literature lacked an acceptable geometric and physical
-interpretation of fractional calculus (and therefore by implication the .
-Interestingly in 1974, this had already been the state of affairs for more than 300 years [].
-Subsequently, the last few decades has seen a number of papers that attempt to rectify this.
-There now exists probabilistic interpretations,
-geometric interpretations, physical interpretations and ecenomic interpretations of the fractional integral.
-
-In this paper we present a novel geometric interpretation of the Riemann-Liouville fractional integral. The interpretation we present here is especially useful from 
+In this paper we present a novel geometric interpretation of the Riemann-Liouville fractional integral. There are in fact many accepted definitions of fractional integration 
+The interpretation we present here is especially useful from 
 a pedigogical point of view as it is similar in nature to the definition of classical integration.

### 2019-03-27 fractional/CMJ style files/article-template.tex
significantly improved introduction

@@
 fractional calculus they generally are quite interested in the subject. This is quite evident from perusing mathematical social media platforms and from surveying 
-articles published in undergraduate journals []. One of the reasons undergraduates struggle to grasp fractional calculus is because it is such an abstract concept. We believe 
-that the geometric interpretation we present in this
+articles published in undergraduate journals [].
+One of the reasons undergraduates struggle to grasp fractional calculus, apart from it not normally being taught as part of the undergraduate curricilum, is because,
+it is such an abstract concept.
+We believe that the geometric interpretation we present in this paper will provide undergraduates with the insight that they need to quickly grasp and understand the fundamental
+concepts that unerpin fractional calculus. We also hope that this paper will enable and encourage undergraduate lectures to introduce undergraduates to this fascinating mathematical discipline.
 

### 2019-03-27 fractional/CMJ style files/article-template.tex
introduction is looking much better

@@
 
-Due to the 
-Even though most undergraduates have a limited understanding of fractional-order calculus they generally are quite interested in the subject. This is quite 
-evident from perusing mathematical social media platforms and from surveying articles published in undergraduate journals []. One of the reason fractional calculus is not generally 
-taught at the undegraduate level is due to the fact that the notion is quite abstract and it is therefore difficult to interpret geometrically. In this paper adress this shortcomming by presenting  
-a novel geometric interpretation of the Riemann-Liouville fractional integral which is similar in nature to the classical interpretation of classical integration. Our hope is that this 
-geometric interpretation will encourage and enable undergraduate lectures to introduce undergraduates to this fascinating mathematical discipline.
+The geometric interpretation we present in this paper is an extension of the fractional geometric framework presented by Podlubny. Podlubny showed that a fractional Riemann-Liouville 
+integral can be converted to a Riemann-Stieltjes integral. Furthermore, Grobler showed that a Riemann-Stieltjes integral can be interpreted as an infiniesimal sum of 
+non-rectangular infinitesimels, i.e.
+a Riemann-Stieltjes integral can be converted into a Cavalieri integral.
+If we combine these two ideas together we obtain the geometric interpretaion contained in the
+previous paragraph.
 
@@
 We believe that the geometric interpretation we present in this paper will provide undergraduates with the insight that they need to quickly grasp and understand the fundamental
-concepts that unerpin fractional calculus. We also hope that this paper will enable and encourage undergraduate lectures to introduce undergraduates to this fascinating mathematical discipline.
+concepts that unerpin fractional calculus.
+We also hope that this paper will enable and encourage undergraduate lectures to already introduce students to this fascinating mathematical discipline as part of their
+undergraduate training.
 
-Our hope is that the geometric 
-interpretation we present here will encourage and enable undergraduate lectures to introduce undergraduates to this fascinating mathematical discipline.
+We start the paper by reviewing the definition of the Riemann-Stieltjes and Cavalieri integral. We then present the definition of the Riemann-Lioville fractional integral. 
+We end the paper by presenting our novel geometric interpretation and a conclusion.
 
-We therefore only present the min-
-imum number of mathematical definitions that are needed to convey the new geometric framework.
+%Due to the 
+%Even though most undergraduates have a limited understanding of fractional-order calculus they generally are quite interested in the subject. This is quite 
+%evident from perusing mathematical social media platforms and from surveying articles published in undergraduate journals []. One of the reason fractional calculus is not generally 
+%taught at the undegraduate level is due to the fact that the notion is quite abstract and it is therefore difficult to interpret geometrically. In this paper adress this shortcomming by presenting  
+%a novel geometric interpretation of the Riemann-Liouville fractional integral which is similar in nature to the classical interpretation of classical integration. Our hope is that this 
+%geometric interpretation will encourage and enable undergraduate lectures to introduce undergraduates to this fascinating mathematical discipline.
 
-This article is not an in depth study into the field of integral calculus, but should rather be viewed as an introductory text
+%Our hope is that the geometric 
+%interpretation we present here will encourage and enable undergraduate lectures to introduce undergraduates to this fascinating mathematical discipline.
 
-It is important to point out at this point that there exists numerous acccepted definitions of fractional integration and differentiation. For the sake of 
-simplicity we decided to focus on one In this paper we will focus 
-on the Riemann-Lioville fractional integral.
+%We therefore only present the min-
+%imum number of mathematical definitions that are needed to convey the new geometric framework.
 
-There are many accepted definitions of fractional order differentiation and integration. In this paper we will only focus
+%This article is not an in depth study into the field of integral calculus, but should rather be viewed as an introductory text
 
-In particular, their contribution played a crucial part in defining what is now known as the 
-Riemann-Lioville fractional integral. In this paper, we present a novel geometric interpretation of the Riemann-Lioville fractional integral which is similar 
-in nature to the classical interpretation of an ordinary Riemann integral. An ordinary Riemann integral can be interpreted as an infinitesimal sum of rectangular 
-infinitesimals.
+%It is important to point out at this point that there exists numerous acccepted definitions of fractional integration and differentiation. For the sake of 
+%simplicity we decided to focus on one In this paper we will focus 
+%on the Riemann-Lioville fractional integral.
 
-In this paper we present a novel geometric interpretation of the Riemann-Liouville fractional integral. There are in fact many accepted definitions of fractional integration 
-The interpretation we present here is especially useful from 
-a pedigogical point of view as it is similar in nature to the definition of classical integration.
+%There are many accepted definitions of fractional order differentiation and integration. In this paper we will only focus
+
+%In particular, their contribution played a crucial part in defining what is now known as the 
+%Riemann-Lioville fractional integral. In this paper, we present a novel geometric interpretation of the Riemann-Lioville fractional integral which is similar 
+%in nature to the classical interpretation of an ordinary Riemann integral. An ordinary Riemann integral can be interpreted as an infinitesimal sum of rectangular 
+%infinitesimals.
+
+%In this paper we present a novel geometric interpretation of the Riemann-Liouville fractional integral. There are in fact many accepted definitions of fractional integration 
+%The interpretation we present here is especially useful from 
+%a pedigogical point of view as it is similar in nature to the definition of classical integration.
 as an infinite sum of rectangular infinitesimals.
 In this paper, we demonstrate at the hand of examples that the Riemann-Liouville fractional integral can be interpreted
-as an infinite sum of non-rectangular infinitesimals whose shape is determined by the order of integration $\alpha$ and the integration limit $x$.
+%as an infinite sum of non-rectangular infinitesimals whose shape is determined by the order of integration $\alpha$ and the integration limit $x$.
 Furthermore, please note that the intended audience of this
-paper is undergraduate students and lecturers and as such we do not present .  In ordinary integration we can interpret the integral
+%paper is undergraduate students and lecturers and as such we do not present .  In ordinary integration we can interpret the integral
 
@@
 
-The idea of integer-order differentiation and integration is well known to most undergraduates.
+%The idea of integer-order differentiation and integration is well known to most undergraduates.
 However, undergraduates are less familiar with the idea of an arbitrary order differential or integral (i.e.
 fractional-order calculus).
-Even though most undergraduates have a limited understanding of fractional-order calculus they generally are quite interested in the subject. This is quite 
-evident from perusing mathematical social media platforms and from surveying articles published in undergraduate journals []. One of the reason fractional calculus is not generally 
-taught at the undegraduate level is due to the fact that the notion is quite abstract and it is therefore difficult to interpret geometrically. In this paper adress this shortcomming by presenting  
-a novel geometric interpretation of the Riemann-Liouville fractional integral which is similar in nature to the classical interpretation of classical integration. Our hope is that this 
-geometric interpretation will encourage and enable undergraduate lectures to introduce undergraduates to this fascinating mathematical discipline.
+%Even though most undergraduates have a limited understanding of fractional-order calculus they generally are quite interested in the subject. This is quite 
+%evident from perusing mathematical social media platforms and from surveying articles published in undergraduate journals []. One of the reason fractional calculus is not generally 
+%taught at the undegraduate level is due to the fact that the notion is quite abstract and it is therefore difficult to interpret geometrically. In this paper adress this shortcomming by presenting  
+%a novel geometric interpretation of the Riemann-Liouville fractional integral which is similar in nature to the classical interpretation of classical integration. Our hope is that this 
+%geometric interpretation will encourage and enable undergraduate lectures to introduce undergraduates to this fascinating mathematical discipline.
 

### 2019-03-29 fractional/func_plotter.py
added a gh plotting function

@@ -45,6 +45,22 @@ def f2(x):
 def f2_inv(y):
     return y**2
 
+def plt_gh_functions(alpha = np.array([0.25,0.5,0.75,1.0]),t=10,num=100):
+    tau = np.linspace(0,t,num)
+    
+
+    for k in range(len(alpha)):
+        tau2 = np.linspace(0,(t**alpha[k])/math.gamma(alpha+1),num)
+        y1 = g_func(tau,alpha[k],t)
+        y2 = h_func(tau2,alpha,t)
+
+        plt.plot(tau,y1)
+        plt.plot(tau2,y2)
+
+    plt.show()
+
+
+
 def plot_g_functions(t_vector,alpha_vector,tau_points):
     fig, ax = plt.subplots(len(t_vector), len(alpha_vector), sharex='all', sharey='all')
     for k in range(0,len(t_vector)):
@@ -228,12 +244,22 @@ def plot_gamma2(x):
     plt.ylabel(r"$\Gamma(x)$")
     plt.ylim([-5,5])      
     plt.show()
- 
 
+def plot_g(alpha, t, num):
+    tau = np.linspace(0,t,num)
+    plt.plot(tau,tau**alpha,"r")
+    plt.plot(tau,(-1*tau)**alpha,"b")
+    plt.plot(tau,(t-tau)**alpha,"m")
+    plt.plot(tau,-1*(t-tau)**alpha,"c")
+    plt.plot(tau,t**alpha-(t-tau)**alpha,"g")
+    plt.show()
+    
 if __name__ == "__main__":
-   x = np.linspace(-5,5,2000)
-   x = x[1:]
-   plot_gamma2(x)
+   plt_gh_functions()
+   #plot_g(1.5,10,1000)
+   #x = np.linspace(-5,5,2000)
+   #x = x[1:]
+   #plot_gamma2(x)
    '''
    num_points = 5
    t_f = 10

### 2019-03-29 fractional/func_plotter.py
added new plotting functionality

@@ -45,18 +45,23 @@ def f2(x):
 def f2_inv(y):
     return y**2
 
-def plt_gh_functions(alpha = np.array([0.25,0.5,0.75,1.0]),t=10,num=100):
+def plt_gh_functions(alpha = np.array([0.125,0.25,0.375,0.5,0.625,0.75,0.875,1.0]),t=10,num=1000):
     tau = np.linspace(0,t,num)
     
+    v = np.linspace(0,1.5,len(alpha))
 
     for k in range(len(alpha)):
-        tau2 = np.linspace(0,(t**alpha[k])/math.gamma(alpha+1),num)
+        tau2 = np.linspace(0,(t**alpha[k])/math.gamma(alpha[k]+1),num)
         y1 = g_func(tau,alpha[k],t)
-        y2 = h_func(tau2,alpha,t)
+        y2 = h_func(tau2,alpha[k],t)
+        col = [v[k]/2,v[k]/2,v[k]/2]    
+        plt.plot(tau,y1,color=col)
+        plt.plot(tau2,y2,color=col,ls = "--")
 
-        plt.plot(tau,y1)
-        plt.plot(tau2,y2)
-
+    plt.xlabel(r"$\tau$")
+    plt.ylabel(r"$y$")
+    plt.xlim([0,10])
+    plt.ylim([0,10])
     plt.show()
 
 
@@ -99,6 +104,41 @@ def plot_a_functions(t_vector,alpha_vector,y_points,f_inv,f):
             if i == 0:
               ax[k,i].set_ylabel("t = "+str(round(t_vector[k],1)))
     plt.show() 
+
+def plot_b_functions(t_vector=np.array([2,4,6,8,10]),alpha_vector=np.array([0.2,0.4,0.6,0.8]),y_points=1000,f_inv=f1_inv,f=f1):
+    #plt.grid('on')
+    fig,ax = plt.subplots(1,len(alpha_vector),sharex='all', sharey='all')
+    #plt.grid('on')
+    v = np.linspace(0,1.5,len(t_vector))
+
+    for i in range(len(alpha_vector)):
+        x = np.linspace(0,t_vector[-1],y_points)
+        
+        ax[i].plot(x,f(x),"k") 
+        if i == 0:
+           ax[i].set_xlabel(r"$\tau$")
+           ax[i].set_ylabel(r"$y$")
+        ax[i].set_title(r"$\alpha = $"+str(alpha_vector[i]))
+        for k in range(len(t_vector)):
[…]

### 2019-04-02 fractional/func_plotter.py
added a fractional result plot

@@ -45,9 +45,9 @@ def f2(x):
 def f2_inv(y):
     return y**2
 
-def plt_gh_functions(alpha = np.array([0.125,0.25,0.375,0.5,0.625,0.75,0.875,1.0]),t=10,num=1000):
+def plt_gh_functions(alpha = np.array([0.2,0.4,0.6,0.8,1.0]),t=10,num=1000):
     tau = np.linspace(0,t,num)
-    
+    #[0.125,0.25,0.375,0.5,0.625,0.75,0.875,1.0]
     v = np.linspace(0,1.5,len(alpha))
 
     for k in range(len(alpha)):
@@ -105,7 +105,7 @@ def plot_a_functions(t_vector,alpha_vector,y_points,f_inv,f):
               ax[k,i].set_ylabel("t = "+str(round(t_vector[k],1)))
     plt.show() 
 
-def plot_b_functions(t_vector=np.array([2,4,6,8,10]),alpha_vector=np.array([0.2,0.4,0.6,0.8]),y_points=1000,f_inv=f1_inv,f=f1):
+def plot_b_functions(t_vector=np.array([2,4,6,8,10]),alpha_vector=np.array([0.2,0.4,0.6,0.8]),y_points=50000,f_inv=f1_inv,f=f1):
     #plt.grid('on')
     fig,ax = plt.subplots(1,len(alpha_vector),sharex='all', sharey='all')
     #plt.grid('on')
@@ -122,9 +122,13 @@ def plot_b_functions(t_vector=np.array([2,4,6,8,10]),alpha_vector=np.array([0.2,
         for k in range(len(t_vector)):
             y = np.linspace(0,f(t_vector[k]),y_points)
             b = g_func(t_vector[k],alpha_vector[i],t_vector[k])
+            b_p = h_func(b,alpha_vector[i],t_vector[-1])
+            y2 = np.linspace(0,f(b_p),y_points)
             col = [v[k]/2,v[k]/2,v[k]/2]    
         
             ax[i].plot(a_func(y,alpha_vector[i],t_vector[k],f_inv)+b,y,color=col) 
+            if i == len(alpha_vector)-1:
[…]

### 2019-04-02 fractional/func_plotter.py
added a function plotter to the file

@@ -380,8 +380,50 @@ def plot_frac_int1():
     
     plt.show()
 
+def plot_frac_int2():
+    t = np.linspace(0,10,1000)
+    from matplotlib.pyplot import figure
+    from matplotlib.ticker import MaxNLocator
+    ax = figure().gca()
+    plt.plot(t,np.sqrt(t),"k",lw=2,label=r"$\alpha=0$")
+    y1 = (np.sqrt(np.pi)/(2*math.gamma(17.0/10.0)))*t**(7.0/10.0)
+    y2 = (np.sqrt(np.pi)/(2*math.gamma(19.0/10.0)))*t**(9.0/10.0)
+    y3 = (np.sqrt(np.pi)/(2*math.gamma(21.0/10.0)))*t**(11.0/10.0)
+    y4 = (np.sqrt(np.pi)/(2*math.gamma(23.0/10.0)))*t**(13.0/10.0)
+    ax.plot(t,y1,"k",dashes=[10, 5, 20, 5],label=r"$\alpha=0.2$")	
+    ax.plot(t,y2,"k",dashes=[4,10],label=r"$\alpha=0.4$")
+    ax.plot(t,y3,"k",ls=":",label=r"$\alpha=0.6$")
+    ax.plot(t,y4,"k",ls="-.",label=r"$\alpha=0.8$")
+    ax.plot(t,2.0/3.0*t**(3.0/2.0),"k",dashes=[5,1],lw=2,label=r"$\alpha=1.0$")
+
+    t_vector = np.array([2,4,6,8,10])
+
+    v = np.linspace(0,1.5,len(t_vector))
+    plt.legend()
+
+    for k in range(len(v)):
+    	y1 = (np.sqrt(np.pi)/(2*math.gamma(17.0/10.0)))*t_vector[k]**(7.0/10.0)
+    	y2 = (np.sqrt(np.pi)/(2*math.gamma(19.0/10.0)))*t_vector[k]**(9.0/10.0)
+    	y3 = (np.sqrt(np.pi)/(2*math.gamma(21.0/10.0)))*t_vector[k]**(11.0/10.0)
+    	y4 = (np.sqrt(np.pi)/(2*math.gamma(23.0/10.0)))*t_vector[k]**(13.0/10.0)
+    
+    	ax.plot(t_vector[k],y1,"o",color=[v[k]/2,v[k]/2,v[k]/2])
[…]

### 2019-04-11 fractional/CMJ style files/article-template.tex
added reason for why g is invertable
added a table of g and h
added a table frac integral
added h integral

@@
 
-\section{Geometric Interpretation of Fractional Integrals}
+\section{Geometric Interpretation of the Riemann-Liouville Fractional Integral}
 
@@
 \end{equation}
+
+Note that $g_t^{\alpha}(\tau)$ is always invertable, since $\frac{d g_t^{\alpha}}{d \tau} = \frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)}>0$ for $\tau\in[0,t]$.
 
@@
 \end{equation}
+
+By employing $h$ we can transform eq.~\ref{eq:cav} into the following Riemann integral:
+\begin{equation}
+\int_0^{\frac{t^{\alpha}}{\Gamma(\alpha+1)}} f\circ h_{\alpha}^t (\tau) d\tau.  
+\end{equation}
+
+\begin{table}[h!]
+\centering
+ \begin{tabular}{|c || c | c|} 
+ \hline
+ $\alpha$ & $g_{10}^{\alpha}(\tau)$ & $h_{10}^{\alpha}(\tau)$ \\ [0.5ex] 
+ \hline\hline
+ $0$ & 0 & $y=0$ \\ 
+ $0.2$ & $[\Gamma\left (\frac{6}{5} \right )]^{-1}\left(\sqrt[5]{10}-\sqrt[5]{10-\tau}\right)$ & $10 - \left ( \sqrt[5]{10} -  \Gamma\left (\frac{6}{5} \right ) \tau \right )^5$  \\
+ $0.4$ & $[\Gamma\left (\frac{7}{5} \right )]^{-1}\left(\sqrt[5]{10^2}-\sqrt[5]{(10-\tau)^2}\right)$ & $10 - \sqrt{\left ( \sqrt[5]{10} -  \Gamma\left (\frac{7}{5} \right ) \tau \right )^5}$ \\
+ $0.6$ & $[\Gamma\left (\frac{8}{5} \right )]^{-1}\left(\sqrt[5]{10^3}-\sqrt[5]{(10-\tau)^3}\right)$ & $10 - \sqrt[3]{\left ( \sqrt[5]{10} -  \Gamma\left (\frac{8}{5} \right ) \tau \right )^5}$ \\
+ $0.8$ & $[\Gamma\left (\frac{9}{5} \right )]^{-1}\left(\sqrt[5]{10^4}-\sqrt[5]{(10-\tau)^4}\right)$ & $10 - \sqrt[4]{\left ( \sqrt[5]{10} -  \Gamma\left (\frac{9}{5} \right ) \tau \right )^5}$ \\ [1ex]
+ $1$ & $\tau$ & $\tau$ \\ [1ex] 
+ \hline
+ \end{tabular}
+\end{table}
+
+\begin{table}[h!]
+\centering
+ \begin{tabular}{||c|| c| c||} 
+ \hline
+ $\alpha$ & $\frac{1}{\Gamma(\alpha)}\int_0^t \tau(t-\tau)^{\alpha-1}~d\tau$ & $\frac{1}{\Gamma(\alpha)}\int_0^t \sqrt{\tau}(t-\tau)^{\alpha-1}~d\tau$ \\[0.5ex]
+ \hline\hline
+ \rule{0pt}{2.5ex}
+ $0$ & $t$ & $\sqrt{t}$  \\  
+ \rule{0pt}{2.5ex}
+ $0.2$ & $\frac{25}{6\Gamma(\frac{1}{5})} t^{\frac{6}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{17}{10})} t^{\frac{7}{10}}$  \\ 
+ \rule{0pt}{2.5ex}
+ $0.4$ & $\frac{25}{14\Gamma(\frac{2}{5})} t^{\frac{7}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{19}{10})} t^{\frac{9}{10}}$  \\
+ \rule{0pt}{2.5ex}
+ $0.6$ & $\frac{25}{24\Gamma(\frac{3}{5})} t^{\frac{8}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{21}{10})} t^{\frac{11}{10}}$  \\ 
+ \rule{0pt}{2.5ex}
+ $0.8$ & $\frac{25}{36\Gamma(\frac{4}{5})} t^{\frac{9}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{23}{10})} t^{\frac{13}{10}}$  \\ 
+ \rule{0pt}{2.5ex}
+ $1$ & $\frac{1}{2}t^2$  & $\frac{2}{3}t^{\frac{3}{2}}$  \\ [1ex]
+ \hline
+ \end{tabular}
+\end{table}
+
+\section{Examples}
+We use the geometric framework we presented in the previous paragraph to provide 
+To make things clear we provide two fully worked examples below of how to geometrically interpret fractional integrals using conversion  presented in the previsous 
+section. The two fractional integrals we will visualize are:\\
+
+\noindent
+$\frac{1}{\Gamma(\alpha)}\int_0^t \tau(t-\tau)^{\alpha-1}~d\tau$ and $\frac{1}{\Gamma(\alpha)}\int_0^t \sqrt{\tau}(t-\tau)^{\alpha-1}~d\tau$.\\
+
+The steps to visualize the above two integral wer described in the previous paragraph. We first convert the integrals into Riemann-Stieltjes integrals. The 
+Riemann-Stieltjes integrals are then converted to Cavalieri integrals. The graphical
 

### 2019-04-11 fractional/CMJ style files/article-template.tex
added examples of (y)$

@@
 \centering
+ \begin{tabular}{|c || c | c|} 
+ \hline
+ & \multicolumn{2}{|c|}{$a_{10}^{\alpha}(\tau)$}\\
+ \hline
+ &$f(\tau) = \tau$ & $f(\tau)=\sqrt{\tau}$ \\ [0.5ex] 
+ \hline\hline
+ $0$ & 0 & $y=0$ \\ 
+ $0.2$ & $y-[\Gamma\left (\frac{6}{5} \right )]^{-1}\left(\sqrt[5]{10}-\sqrt[5]{10-y}\right)$ & $y^2-[\Gamma\left (\frac{6}{5} \right )]^{-1}\left(\sqrt[5]{10}-\sqrt[5]{10-y^2}\right)$  \\
+ $0.4$ & $y-[\Gamma\left (\frac{7}{5} \right )]^{-1}\left(\sqrt[5]{10^2}-\sqrt[5]{(10-y)^2}\right)$ & $y^2-[\Gamma\left (\frac{7}{5} \right )]^{-1}\left(\sqrt[5]{10^2}-\sqrt[5]{(10-y^2)^2}\right)$ \\
+ $0.6$ & $y-[\Gamma\left (\frac{8}{5} \right )]^{-1}\left(\sqrt[5]{10^3}-\sqrt[5]{(10-y)^3}\right)$ & $y^2-[\Gamma\left (\frac{8}{5} \right )]^{-1}\left(\sqrt[5]{10^3}-\sqrt[5]{(10-y^2)^3}\right)$ \\
+ $0.8$ & $y-[\Gamma\left (\frac{9}{5} \right )]^{-1}\left(\sqrt[5]{10^4}-\sqrt[5]{(10-y)^4}\right)$ & $y^2-[\Gamma\left (\frac{9}{5} \right )]^{-1}\left(\sqrt[5]{10^4}-\sqrt[5]{(10-y^2)^4}\right)$ \\ [1ex]
+ $1$ & $\tau$ & $\tau$ \\ [1ex] 
+ \hline
+ \end{tabular}
+\end{table}
+
+\begin{table}[h!]
+\centering
  \begin{tabular}{||c|| c| c||} 
@@
 \section{Examples}
-We use the geometric framework we presented in the previous paragraph to provide 
-To make things clear we provide two fully worked examples below of how to geometrically interpret fractional integrals using conversion  presented in the previsous 
-section. The two fractional integrals we will visualize are:\\
+In this section we will illustrate the usefulness of the proposed geometric framework at the hand of two examples.
+Consider the two fractional integrals:
+
+\begin{equation}
+\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \frac{1}{\Gamma(\alpha)}\int_0^t \tau(t-\tau)^{\alpha-1}~d\tau 
+\end{equation}
+
+and
+
+\begin{equation}
+\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \frac{1}{\Gamma(\alpha)}\int_0^t \sqrt{\tau}(t-\tau)^{\alpha-1}~d\tau.
+\end{equation}
 
@@
 
-The steps to visualize the above two integral wer described in the previous paragraph. We first convert the integrals into Riemann-Stieltjes integrals. The 
-Riemann-Stieltjes integrals are then converted to Cavalieri integrals. The graphical
+We can give
+
+The steps to visualize the above two integrals were described in the previous paragraph. We first convert the integrals into Riemann-Stieltjes integrals. The 
+Riemann-Stieltjes integrals are then converted to Cavalieri integrals. We can then simply depict the Cavalieri integrals and in doing so obtain a geometric interpretaion
+of the original fractional integrals. Importantly, for each value of $t$ we obtain a different
 

### 2019-04-11 fractional/CMJ style files/article-template.tex
added more text to example section

@@
 
-We can give
+We can assign a geometric interpretation to the above fractional integrals by converting them into Cavalieri integrals. This can be achieved by first 
+converting the above integrals into Riemann-Stieltjes integrals and then converting the resulting integrals into Cavalieri integrals. We can convert fractional 
+integral into Riemann-Stieltjes integrals by utilizing Eq.~\eqref{}. Riemann
+The inegrator $g_t^{\alpha}(\tau)$ of the aforementioned intermediate Riemann-Stieltjes integrals are equal and independent of the integrand $f(\tau)$.
+The set of functions $\{g_{10}^{\alpha}(\tau)|\alpha\in\{0,0.2,\cdots,0.8,1\}\}$ are presented in Table \textbf{??}.
+
+These steps 
+were discussed in more detail in the previous section.
 

### 2019-04-11 fractional/CMJ style files/article-template.tex
added more text to example section

@@
 We can assign a geometric interpretation to the above fractional integrals by converting them into Cavalieri integrals. This can be achieved by first 
-converting the above integrals into Riemann-Stieltjes integrals and then converting the resulting integrals into Cavalieri integrals. We can convert fractional 
-integral into Riemann-Stieltjes integrals by utilizing Eq.~\eqref{}. Riemann
+converting the above integrals into Riemann-Stieltjes integrals and then converting the resulting integrals into Cavalieri integrals. Exaclty how these conversion are 
+to be performed is discussed in the previous section.
 The inegrator $g_t^{\alpha}(\tau)$ of the aforementioned intermediate Riemann-Stieltjes integrals are equal and independent of the integrand $f(\tau)$.
-The set of functions $\{g_{10}^{\alpha}(\tau)|\alpha\in\{0,0.2,\cdots,0.8,1\}\}$ are presented in Table \textbf{??}.
+The set of functions $\{g_{10}^{\alpha}(\tau)|\alpha\in\{0,0.2,\cdots,0.8,1\}\}$ are presented in Table \textbf{??}. The integration limits of the aformentioned Cavalieri 
+integrals are functions and are determined by the integrand $f(\tau)$ and the integrator $g_t^{\alpha}(\tau)$. The shape of the infini
 

### 2019-04-11 fractional/CMJ style files/article-template.tex
added more text to example section

@@
 The set of functions $\{g_{10}^{\alpha}(\tau)|\alpha\in\{0,0.2,\cdots,0.8,1\}\}$ are presented in Table \textbf{??}. The integration limits of the aformentioned Cavalieri 
-integrals are functions and are determined by the integrand $f(\tau)$ and the integrator $g_t^{\alpha}(\tau)$. The shape of the infini
+integrals are functions and are determined by the integrand $f(\tau)$ and the integrator $g_t^{\alpha}(\tau)$. Recall that a Cavalieri integral can 
+be interpreted as an infinite sum of non-rectanguar infinitesimals whose shape is determined by its lower integration limit $a_t^{\alpha}(y)$. The list of functions 
+$\{a_{10}^{\alpha}(y)|\alpha\in\{0,0.2,\cdots,0.8,1\}\}$ that can be associated with the integrals in Eq~{??} and Eq~{??} are presented in Table~\textbf{??}. Note that 
+$a_t^{\alpha}(y)$ is not a static function it depends on the order of integration $\alpha$ and the integration limit $t$. The fact that $a_t^{\alpha}(y)$ is dependend 
+on $t$ implies that a fractional integral of a particular order cannot be converted to a single Cavalieri integral, but rather to an infinite set $\mathcal{C}$ of Cavalieri integrals.
+Each element of $\mathcal{C}$ can be associated with a particular choice of $t$.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=1\textwidth]{geo_int1.pdf}
+\caption{A plot of $\Gamma(x)$. $\Gamma(x)$ is not defined for the non-negative integers.}
+\label{fig:geo1}
+\end{figure}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=1\textwidth]{geo_int2.pdf}
+\caption{A plot of $\Gamma(x)$. $\Gamma(x)$ is not defined for the non-negative integers.}
+\label{fig:geo2}
+\end{figure}
 

### 2019-04-12 fractional/CMJ style files/article-template.tex
added extra text to article

--- 2019-04-11 fractional/CMJ style files/article-template.tex
@@
 The inegrator $g_t^{\alpha}(\tau)$ of the aforementioned intermediate Riemann-Stieltjes integrals are equal and independent of the integrand $f(\tau)$.
-The set of functions $\{g_{10}^{\alpha}(\tau)|\alpha\in\{0,0.2,\cdots,0.8,1\}\}$ are presented in Table \textbf{??}. The integration limits of the aformentioned Cavalieri 
-integrals are functions and are determined by the integrand $f(\tau)$ and the integrator $g_t^{\alpha}(\tau)$. The shape of the infini
+The set of functions $\{g_{10}^{\alpha}(\tau)|\alpha\in\{0,0.2,\cdots,0.8,1\}\}$ are presented in Table \textbf{??} and depicted in Figure\textbf{??}.
+The integration limits of the aformentioned Cavalieri
+integrals are functions and are determined by the integrand $f(\tau)$ and the integrator $g_t^{\alpha}(\tau)$.
+The set of functions $\{a_{10}^{\alpha}(y)|\alpha\in\{0,0.2,\cdots,0.8,1\}\}$ that can be
+associated with the integrals in Eq~{??} and Eq~{??} are presented in Table~\textbf{??}. Note that neither $g_t^{\alpha}(\tau)$ nor $a_t^{\alpha}(y)$ are static functions, 
+they depend on the value of $\alpha$ and $t$.
+This implies that a fractional integral of order $\alpha$ and extent $t$ can be interpeted as an infitesimal sum of an infinite number of infinitesimals whose
+shape is determined by $\alpha$ and $t$.
+
+To make things clearer lets set the value of $\alpha$ to $0.8$ and the value of $t$ to 10 and then depict the region associated that is associated with the Cavalieri integral which is obtained
+
+the obtained Lets depict the geometric interpretation
+
+%The integration limits of the aformentioned Cavalieri 
+%integrals are functions and are determined by the integrand $f(\tau)$ and the integrator $g_t^{\alpha}(\tau)$. Recall that a Cavalieri integral can 
+%be interpreted as an infinite sum of non-rectanguar infinitesimals whose shape is determined by its lower integration limit $a_t^{\alpha}(y)$. The set of functions 
+%$\{a_{10}^{f,\alpha}(y)|\alpha\in\{0,0.2,\cdots,0.8,1\}\}$ that can be associated with the integrals in Eq~{??} and Eq~{??} are presented in Table~\textbf{??}. Note that 
+%$a_t^{\alpha}(y)$ is not a static function it depends on the order of integration $\alpha$ and the integration limit $t$. The fact that $a_t^{\alpha}(y)$ is dependend 
+%on $t$ implies that a fractional integral of a particular order cannot be converted to a single Cavalieri integral, but rather to an infinite set $\mathcal{C}$ of Cavalieri integrals.
+%Each element of $\mathcal{C}$ is associated with a particular choice of $t$.
+Let $\mathcal{B}_f = \{b_{t}^{f,\alpha}(y)|\alpha\in\{0,0.2,\cdots,0.8,1\}\}$.
+In Fig.~\ref{fig:geo1} and Fig.~\ref{fig:geo2} we plot the elements of $\mathcal{B}$.
+%The brigther the function the larger $t$ is.
+For the case $t=10$ we also plot the integration strips.
+The fractional integral $\frac{1}{\Gamma(\alpha)}\int_0^10 f(\tau) (t-\tau)^{\alpha-1}~d\tau$ can therefore
+%be interpreted as the sum of inThey clearly do not match the other functions.
+
+\begin{enumerate}
+ \item Examples.
+ \item If we evaluate \textbf{[is this word correct?]} these integrals we obtaine the functions in Table \textbf{??}. These functions are plotted in Fig xx.
+ \item Assign a geometric interpretation by converting to a Riemann-Stieltjes integral and then to a Cavalieri integral.
+ \item \textbf{[Is there a need to mention the fact that it is mapped to a set of different Cavalieri integrals]}. Note that we obtain a different 
+ Cavalieri integral for each value of alpha and t.
+ \item Let us fix alpha and t to specific values, ie write down the integrals. The function b the left most function in the leftmost panel (plotted in the lightest 
+ shade of gray of all the y-valued functions. The integral , and by implication , can be inerpreted as the are of the region formed by f, b and the x-axis. This 
+ area can be obtained by summing together an infinite number of infinitesimals whose shape is determined by b. This are can be approximated by using integration strips. These 
+ strips is depicted using dashed lines. The area of this region and $t$ forms a specific point on the curves in Fig. The point is plotted in the same shade of gray than b.
+ \item If we take another value of t we obtain a different region. Note that b and b are not mere translations of each other. Changing the integration limit alters the 
+ shape of the infinitesimal we need to use.
+Althoug both t and alpa alters the shape of b, it is only alpha that fundamentally changes ....
+\textbf{[how to state this shape altering thing i do not know]}
+ \item Need to finish the discussion of al the points mapping to the other figures. 
+ \item Summary of overall interpretation of fractional integral.....
+\end{enumerate}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=1\textwidth]{geo_int1.pdf}
+\caption{A plot of $\Gamma(x)$. $\Gamma(x)$ is not defined for the non-negative integers.}
+\label{fig:geo1}
+\end{figure}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=1\textwidth]{geo_int2.pdf}
+\caption{A plot of $\Gamma(x)$. $\Gamma(x)$ is not defined for the non-negative integers.}
+\label{fig:geo2}
+\end{figure}
 

### 2019-04-14 fractional/CMJ style files/article-template.tex
added another paragraph to the article

@@
 
-To make things clearer lets set the value of $\alpha$ to $0.8$ and the value of $t$ to 10 and then depict the region associated that is associated with the Cavalieri integral which is obtained
+Lets clarify the above by working through a detailed example. Lets set the value of $\alpha$ to $\frac{4}{5}$ and the value of $t$ to 10 and then convert the 
+integrals in ?? and ?? to equivalent Cavalieri integrals. If we evaluate these Cavalieri integrals we obtain the area of two regions $A$ and $B$. Both $A$ and $B$ are bounded by the $x$-axis, 
+$f(x)$ and $b_{10}^{\frac{4}{5}}(y)$. Region $A$ and $B$ are depicted in the rightmost panel of Fig ?? and Fig ??. Note that the curves $\{b_{t}^{\frac{4}{5}}(y)|t\in\{2,4,6,8,10\}\}$ are plotted 
+using a greyscale. The shade with which $b_t^{\alpha}(y)$ is depicted becomes lighter as the value of $t$ increases.  is the lighter the curve associated with $b_t^{\alpha}(y)$ is.
+
+We depict We depict $b_10^{\alpha}(y)$ with the lightest
+shade of
+depicted in the right most   depict the region associated that is associated with the Cavalieri integral which is obtained
 

### 2019-04-17 fractional/CMJ style files/article-template.tex
improved example section quite dramatically

@@
 \centering
+ \begin{tabular}{|c || c|} 
+ \hline
+ Symbol & Definition  \\ [0.1ex]
+ \hline 
+ \rule{0pt}{2.5ex}
+ $\mathsf{G}^{10}$ & $\{g_{10}^{\alpha}(\tau)|\alpha\in\{0,\frac{1}{5},\frac{2}{5},\frac{3}{5},\frac{4}{5}\}\}$\\ [0.5ex]
+ $\mathsf{H}^{10}$ & $\{h_{10}^{\alpha}(\tau)|\alpha\in\{0,\frac{1}{5},\frac{2}{5},\frac{3}{5},\frac{4}{5}\}\}$\\ [0.5ex]
+ $\mathsf{A}^{10}$ & $\{a_{10}^{\alpha}(\tau)|\alpha\in\{0,\frac{1}{5},\frac{2}{5},\frac{3}{5},\frac{4}{5}\}\}$\\ [0.5ex]
+ $\mathsf{B}^{10}$ & $\{b_{10}^{\alpha}(\tau)|\alpha\in\{0,\frac{1}{5},\frac{2}{5},\frac{3}{5},\frac{4}{5}\}\}$\\ [0.5ex]
+ $\mathsf{B}^{\frac{4}{5}}_1$ & $\{b_{t}^{\frac{4}{5}}(\tau)|t\in\alpha\in\{2,4,6,8,10\}$\\ [0.5ex]
+ $\mathsf{B}^{\frac{4}{5}}_2$ & $\{b_{10}^{\frac{4}{5}}(\tau)-c|c\in\in\{0,2,4,6,8\}$\\ [0.5ex]
+ \hline 
+ \end{tabular}
+\end{table}
+
+\begin{table}[h!]
+\centering
  \begin{tabular}{||c|| c| c||} 
@@
 In this section we will illustrate the usefulness of the proposed geometric framework at the hand of two examples.
-Consider the two fractional integrals:
 
+Let us first consider the following fractional integral:
 \begin{equation}
-\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \frac{1}{\Gamma(\alpha)}\int_0^t \tau(t-\tau)^{\alpha-1}~d\tau 
+\label{eq:ex1_raw}
+\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \frac{1}{\Gamma(\alpha)}\int_0^t \tau(t-\tau)^{\alpha-1}~d\tau. 
 \end{equation}
+We can assign a geometric interpretation to the above fractional integral by converting it into a Cavalieri integral using two steps. First, we convert 
+the above integral into a Riemann-Stieltjes integral:
+\begin{equation}
+\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \int_0^t f(\tau)~dg_t^{\alpha}(\tau). 
+\end{equation}
+We then convert the resulting Riemann-Stieltjes integral into a Cavalieri integral:
+\begin{equation}
+\label{eq:ex1}
+\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \int_0^t f(\tau)~dg_t^{\alpha}(\tau)=\int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau. 
+\end{equation}
+We know that a Cavalieri integral can be interpreted as the area which is obtained by summing together the area associated with an infinite number of non-rectangular infinitesimals whose shape 
+is determined by the integration limits of the Cavalieri integral. Note that neither $g_t^{\alpha}(\tau)$ nor $a_t^{\alpha}(y)$ are static functions, 
+they depend on the value of $\alpha$ and $t$.
+This implies that a fractional integral of order $\alpha$ and extent $t$ can be interpeted as the area obtained by summing together the area associated with an infinite number of infinitesimals whose
+shape is determined by $\alpha$ and $t$, i.e. the geometric interpretation of Eq.~\eqref{eq:ex1_raw} is non-static as it depends on the value of $\alpha$ and $t$.
 
-and
+Lets clarify the above by working through a detailed example. If we set the value of $\alpha$ to $\frac{4}{5}$ and the value of $t$ to 10 in Eq.~\eqref{eq:ex1} we obtain:
+\begin{equation}
+\int_{a_{10}^{\frac{4}{5}}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau. 
+\end{equation}
+This integral can be interpreted as the area of the region bounded by the $x$-axis, the function $f(y)$ and the function $b_{10}^{\frac{4}{5}}(y)$. Let us denote 
+this region with the symbol $R_1$. The region $R_1$ is depicted and labelled in the left most panel of Figure.~\ref{??}. The function
 
-\begin{equation}
-\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \frac{1}{\Gamma(\alpha)}\int_0^t \sqrt{\tau}(t-\tau)^{\alpha-1}~d\tau.
-\end{equation}
-
-\noindent
-$\frac{1}{\Gamma(\alpha)}\int_0^t \tau(t-\tau)^{\alpha-1}~d\tau$ and $\frac{1}{\Gamma(\alpha)}\int_0^t \sqrt{\tau}(t-\tau)^{\alpha-1}~d\tau$.\\
+convert the 
+integrals in ?? and ?? to equivalent Cavalieri integrals.
 
@@
 integrals in ?? and ?? to equivalent Cavalieri integrals. If we evaluate these Cavalieri integrals we obtain the area of two regions $A$ and $B$. Both $A$ and $B$ are bounded by the $x$-axis, 
-$f(x)$ and $b_{10}^{\frac{4}{5}}(y)$. Region $A$ and $B$ are depicted in the rightmost panel of Fig ?? and Fig ??. Note that the curves $\{b_{t}^{\frac{4}{5}}(y)|t\in\{2,4,6,8,10\}\}$ are plotted 
-using a greyscale. The shade with which $b_t^{\alpha}(y)$ is depicted becomes lighter as the value of $t$ increases.  is the lighter the curve associated with $b_t^{\alpha}(y)$ is.
+$f(x)$ and $b_{10}^{\frac{4}{5}}(y)$. Region $A$ and $B$ are respectively depicted in the rightmost panel of Fig ?? and Fig ??. The area of $A$ and $B$ can be approximated
+by summing together the area of non-rectangular integration strips that inscribes $A$ and $B$. The case in which we use five integration strips is depicted in 
+Fig ?? and Fig ??. The analytic expressions of the right sides of these integration strips are elements of the set $\mathsf{A} = \{b_{10}^{\frac{4}{5}}(y) - c|c\in\{0,2,4,6,8\}\}$. The 
+curves are plotted using dashed lines.
+
+The curves $\mathsf{B} = \{b_{t}^{\frac{4}{5}}(y)|t\in\{2,4,6,8,10\}\}$ are plotted in different shades of grey.
+The shade with which $b_t^{\alpha}(y)$ is depicted becomes lighter as the value of $t$ increases.
+Note
+that $\mathsf{A}\neq \mathsf{B}$. The sides of the integration strips
+
+is the lighter the curve associated with $b_t^{\alpha}(y)$ is.
 
@@
 the obtained Lets depict the geometric interpretation
+
+%\begin{equation}
+%\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \frac{1}{\Gamma(\alpha)}\int_0^t \sqrt{\tau}(t-\tau)^{\alpha-1}~d\tau.
+%\end{equation}
 

### 2019-04-17 fractional/CMJ style files/article-template.tex
made improvements to example section --- still lots todo

@@
 \end{equation}
-We can assign a geometric interpretation to the above fractional integral by converting it into a Cavalieri integral using two steps. First, we convert 
+The function $f(\tau) =\tau$ is depicted in Figure~\ref{??}.
+We can assign a geometric interpretation to the above fractional integral by converting it into a Cavalieri integral using two steps.
+First, we convert
 the above integral into a Riemann-Stieltjes integral:
@@
 \begin{equation}
-\int_{a_{10}^{\frac{4}{5}}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau. 
+\int_{a_{10}^{\frac{4}{5}}(y)}^{b_{10}^{\frac{4}{5}}(y)} f(\tau)~d\tau. 
 \end{equation}
-This integral can be interpreted as the area of the region bounded by the $x$-axis, the function $f(y)$ and the function $b_{10}^{\frac{4}{5}}(y)$. Let us denote 
-this region with the symbol $R_1$. The region $R_1$ is depicted and labelled in the left most panel of Figure.~\ref{??}. The function
+This integral can be interpreted as the area of the region bounded by the $x$-axis, the function $f(\tau)$ and the function $b_{10}^{\frac{4}{5}}(y)$. Let us denote 
+this region with the symbol $R_{10}^{\frac{4}{5}}$.
+The region $R_{10}^{\frac{4}{5}}$ is depicted and labelled in the right-most panel of Figure.~\ref{??}.
+We are now in a position to assign a geometric
+interpretaion to Eq.~\eqref{}. We can approximate the area of $R_{10}^{\frac{4}{5}}$
+by summing together the area of non-rectangular integration strips that inscribe $R_{10}^{\frac{4}{5}}$.
+The only resctriction being: the sides of these non-rectangualar integration strips have to be translations of $b_{10}^{\frac{4}{5}}(y)$.
+Lets now choose to approximate the area of $R_{10}^{\frac{4}{5}}$ using five integration strips of equal width.
+The aformentioned integration strips are depicted in the right-most panel of Figure~\ref{??}.
+The sides of the integration strips are depicted using dashed lines. The more integration strips we consider the better our approximation of $R_{10}^{\frac{4}{5}}$ becomes.
+
+We can better approximate the area of $R_{10}^{\frac{4}{5}}$ by increasing the number of integrations strips we use .
+Increasing the number of integration strips we use improves our approximation of the area of $R_{10}^{\frac{4}{5}}$
+If we decide on using five integration strips
+
+that 
+we use whose sides are translations of $b_{10}^{\frac{4}{5}}(y)$
+
+Each panel of 
+Figure~\ref{??} depicts the function $f(\tau)$ and the set of curves $\mathsf{B}_T^{\alpha}$. The set $\mathsf{B}_T^{\alpha}$ is defined in Table~\ref{??} and contains 
+all the Cavalieri integral upper limits obtained by fixing the order of integration $\alpha$ to a specific value.
+In each panel, we depict the set of curves $\mathsf{B}_T^{\alpha}$ using different shades of grey.
+The shade with which $b_t^{\alpha}(y)$ is depicted becomes lighter as the value of $t$ increases.
+
+The The $y$-valued functions are depicted in different shades of gray. The $\tau$-valued fun
+
+The curve in the rightmost panel of 
+Figure~\ref{} which is depicted in the lightest shade of gray of
+
+The function $b_{10}^{\frac{4}{5}}(y)$ 
+depicted in the lightest shade of gray used within the right-most panel
+
+The right-most panel of Figure.~\ref{??} contains 
+a few $y$-valued curves, each one depicted in a different shade of gray. The curve depicted in the lightest shade of gray is
+
+In each of the panels  curves $\mathsf{B}_1^{\alpha}$
 

### 2019-04-25 fractional/CMJ style files/article-template.tex
improved description

@@
 \end{equation}
+
 We know that a Cavalieri integral can be interpreted as the area which is obtained by summing together the area associated with an infinite number of non-rectangular infinitesimals whose shape 
@@
 \begin{equation}
-\int_{a_{10}^{\frac{4}{5}}(y)}^{b_{10}^{\frac{4}{5}}(y)} f(\tau)~d\tau. 
+\int_{a_{10}^{\frac{4}{5}}(y)}^{b_{10}^{\frac{4}{5}}(y)} f(\tau)~d\tau 
 \end{equation}
-This integral can be interpreted as the area of the region bounded by the $x$-axis, the function $f(\tau)$ and the function $b_{10}^{\frac{4}{5}}(y)$. Let us denote 
-this region with the symbol $R_{10}^{\frac{4}{5}}$.
+Let $R_{10}^{\frac{4}{5}}$ denote the region which is bounded by the $x$-axis, the function $f(\tau)$ and the function $b_{10}^{\frac{4}{5}}(y)$.
 The region $R_{10}^{\frac{4}{5}}$ is depicted and labelled in the right-most panel of Figure.~\ref{??}.
 We are now in a position to assign a geometric
-interpretaion to Eq.~\eqref{}. We can approximate the area of $R_{10}^{\frac{4}{5}}$
-by summing together the area of non-rectangular integration strips that inscribe $R_{10}^{\frac{4}{5}}$.
+interpretaion to Eq.~\eqref{}.
+We can approximate the area of $R_{10}^{\frac{4}{5}}$ by summing together the area of $n$ non-rectangular integration strips of the same width that inscribe $R_{10}^{\frac{4}{5}}$.
 The only resctriction being: the sides of these non-rectangualar integration strips have to be translations of $b_{10}^{\frac{4}{5}}(y)$.
-Lets now choose to approximate the area of $R_{10}^{\frac{4}{5}}$ using five integration strips of equal width.
-The aformentioned integration strips are depicted in the right-most panel of Figure~\ref{??}.
+The case in which we try to approximate the area of $R_{10}^{\frac{4}{5}}$ using only five non-rectangular integration strips of equal width is depicted in the right-most panel of Figure~\ref{??}.
+The sides of the
+aforementioned five integration strips are depicted in Fig.~\ref{??} using dahsed lines. Taking the limit of the aformentioned sum as $n\rightarrow \infty$ results in 
+Eq??, i.e. the area of $R_{10}^{\frac{4}{5}}$.
+
+In the limit this sum approaches the area of $R_{10}^{\frac{4}{5}}$
+
+In general can use $n$ integration strips to approximate 
+the area If we are to sum together the area of  non-rectangular integration strips whose sides are translations of $b_{10}^{\frac{4}{5}}(y)$ then the result our summation would tend to
+the area of $R_{10}^{\frac{4}{5}}$.
+
+Lets now choose to approximate the area of $R_{10}^{\frac{4}{5}}$ using five non-rectangualr integration strips of equal width. Mathematically speaking, this is accomplished 
+by setting $n$ to 5 in Eq??. The aformentioned integration strips are depicted in the right-most panel of Figure~\ref{??}.
 The sides of the integration strips are depicted using dashed lines. The more integration strips we consider the better our approximation of $R_{10}^{\frac{4}{5}}$ becomes.

### 2019-04-26 fractional/CMJ style files/article-template.tex
added a new paragraph

@@
 \end{equation}
-Let $R_{10}^{\frac{4}{5}}$ denote the region which is bounded by the $x$-axis, the function $f(\tau)$ and the function $b_{10}^{\frac{4}{5}}(y)$.
+Let $R_{10}^{\frac{4}{5}}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{10}^{\frac{4}{5}}(y)$.
 The region $R_{10}^{\frac{4}{5}}$ is depicted and labelled in the right-most panel of Figure.~\ref{??}.
@@
 The only resctriction being: the sides of these non-rectangualar integration strips have to be translations of $b_{10}^{\frac{4}{5}}(y)$.
+Taking the limit of the aformentioned sum as $n\rightarrow \infty$ results in 
+Eq??, i.e.
+the area of $R_{10}^{\frac{4}{5}}$.
 The case in which we try to approximate the area of $R_{10}^{\frac{4}{5}}$ using only five non-rectangular integration strips of equal width is depicted in the right-most panel of Figure~\ref{??}.
 The sides of the
-aforementioned five integration strips are depicted in Fig.~\ref{??} using dahsed lines. Taking the limit of the aformentioned sum as $n\rightarrow \infty$ results in 
-Eq??, i.e. the area of $R_{10}^{\frac{4}{5}}$.
+aforementioned five integration strips are depicted in Fig.~\ref{??} using dahsed lines.
+The analytic expressions associated with these dashed curves are contained in the set $\mathsf{B}_{10}^{\frac{4}{5}}$.
 
-In the limit this sum approaches the area of $R_{10}^{\frac{4}{5}}$
+If we set the value of $\alpha$ to $\frac{4}{5}$, but we do not fix the value of $t$ then Eq.~\eqref{eq:ex1} reduces to:
+\begin{equation}
+\int_{a_{t}^{\frac{4}{5}}(y)}^{b_{t}^{\frac{4}{5}}(y)} f(\tau)~d\tau 
+\end{equation}
+If we evaluate the above integral we obtain the area of the region $R_{t}^{\frac{4}{5}}$.
+The region $R_{t}^{\frac{4}{5}}$ is the region bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{t}^{\frac{4}{5}}(y)$.
+Note that $R_{t}^{\frac{4}{5}}$ is a function of $t$. The regions $\mathsf{R}^{\frac{4}{5}}$ are depicted in the rightmost panel of Fig\textbf{??}.
+
+The boundaries of these regions are depicted in varying shades of gray.
+
+We depict $R_{t}^{\frac{4}{5}}$ in the left most panel of Fig.~\textbf{??} for all $t\in\mathsf{T}$. The set of functions
+
+If we change the value of $t$ we change the area
 
 In general can use $n$ integration strips to approximate
+
 the area If we are to sum together the area of  non-rectangular integration strips whose sides are translations of $b_{10}^{\frac{4}{5}}(y)$ then the result our summation would tend to

### 2019-04-26 fractional/CMJ style files/article-template.tex
added a new paragraph

@@
 The region $R_{t}^{\frac{4}{5}}$ is the region bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{t}^{\frac{4}{5}}(y)$.
-Note that $R_{t}^{\frac{4}{5}}$ is a function of $t$. The regions $\mathsf{R}^{\frac{4}{5}}$ are depicted in the rightmost panel of Fig\textbf{??}.
+Note that $R_{t}^{\frac{4}{5}}$ is a function of $t$.
+The regions contained in the set $\mathsf{R}^{\frac{4}{5}}$ are depicted in the rightmost panel of Fig\textbf{??}.
+Let $\mathsf{B}^{\frac{4}{5}}$ contain the right
+edges of the regions contained in the set $\mathsf{R}^{\frac{4}{5}}$. The edges in $\mathsf{B}^{\frac{4}{5}}$ are depicted using different shades of gray. The edges that are associated 
+with larger values of $t$ are depicted using lighter shades of gray than those that are associated with smaller values of $t$. Note that b and b are not equal, i.e. altering $t$ will alter 
+the shape of the integration strip used  . Changing the value of $t$ alters the shape of the non-rectangular integration strip which is needed
+
+limit alters the
+shape of the infinitesimal we need to use.
+
+The shade with which the aformentioned edges are depicted becomes lighter as the value of $t$ increases.
 

### 2019-04-30 fractional/CMJ style files/article-template.tex
started improving the example section quite a bit, comming together

@@
 
+Varying both $\alpha$ and $t$ results in Eq.~\ref{eq:ex1}.
+Eq.
+can be associated with a multitude of regions.
+Let $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}=\{R_t^{\alpha}|t\in\mathsf{T},~\alpha\in\mathsf{A}\}$.
+The regions in the set $\mathsf{R}_{\mathsf{T}}$
+are depicted in Fig.~\textbf{??}. The regions in Fig that are depicted in the same panel were generated by varying $t$, whilst fixing the value of $\alpha$.
+
 If we set the value of $\alpha$ to $\frac{4}{5}$, but we do not fix the value of $t$ then Eq.~\eqref{eq:ex1} reduces to:
@@
 The region $R_{t}^{\frac{4}{5}}$ is the region bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{t}^{\frac{4}{5}}(y)$.
-Note that $R_{t}^{\frac{4}{5}}$ is a function of $t$.
+Note that the shape of $R_{t}^{\frac{4}{5}}$ depends on the value of $t$.
 The regions contained in the set $\mathsf{R}^{\frac{4}{5}}$ are depicted in the rightmost panel of Fig\textbf{??}.
 Let $\mathsf{B}^{\frac{4}{5}}$ contain the right
-edges of the regions contained in the set $\mathsf{R}^{\frac{4}{5}}$. The edges in $\mathsf{B}^{\frac{4}{5}}$ are depicted using different shades of gray. The edges that are associated 
-with larger values of $t$ are depicted using lighter shades of gray than those that are associated with smaller values of $t$. Note that b and b are not equal, i.e. altering $t$ will alter 
-the shape of the integration strip used  . Changing the value of $t$ alters the shape of the non-rectangular integration strip which is needed
+edges of the regions contained in the set $\mathsf{R}^{\frac{4}{5}}$.
+The shape of the edges in $\mathsf{B}^{\frac{4}{5}}$ depend on the value of $t$.
+The edges in $\mathsf{B}^{\frac{4}{5}}$ are depicted in Fig??
+using different shades of gray.
+The shade with which the aformentioned curves are depicted becomes lighter
+as the value of $t$ increases. The two sets b and b are not equal, i.e. the shape of the infinitesimals that make up the regions contained in 
+R are dependent on $t$. Although the infinitesimals that make up the regions contained in R have different shapes their form do share common characteristics.
+
+altering $t$ alters the geometric interpretaion of 
+Eq???. The shape of the inifinitesimals that make up the region that is associated with Eq depend on the value of $t$.
+
+the shape of the integration strip one has to use to construct the infinite sum that underpins the  used to create the   .
+Changing the value of $t$ alters the shape of the non-rectangular integration strip which is needed
 

### 2019-04-30 fractional/CMJ style files/article-template.tex
added more text to example section

@@
 The regions in the set $\mathsf{R}_{\mathsf{T}}$
-are depicted in Fig.~\textbf{??}. The regions in Fig that are depicted in the same panel were generated by varying $t$, whilst fixing the value of $\alpha$.
+are depicted in Fig.~\textbf{??}. The regions that are depicted in each of the panels of Fig.~\ref{??} were generated by varying $t$, whilst keeping the value of $\alpha$ fixed. 
+The title of each panel indicate which $\alpha$-value was used to generate the regions depicted in each panel. The only difference between the regions located in each 
+panel is their right edges. The right edges of the regions in each panel are depicted using varying shades of gray. The lighter the shade with which an edge is depicted 
+the larger the $t$-value is that was used to generate it.
+
+Each of the regions depicted in Fig.~\ref{} are made up of an infinite number of infinitesimals, the shape of which is determined by their right edges, i.e. by the value 
+of both $\alpha$ and $t$. The notion that $t$ alters the shape of the infinitesimals can easily be confirmed through visual inspection. The 
+dashed grey curves and the solid grey-tinted curves in the right-most panel are not the same, i.e.$\mathsf{B}_T^{\alpha}\neq\mathcal{B}_T^{\alpha}$.
+
+that make up the regions in Fig are confirmed by the following observation: $\mathsf{B}_T^{\alpha}\neq\mathcal{B}_T^{\alpha}$.
+We can visually verify that this observation is in fact true for $alpha=\frac{4}{5}$ by inspecting the right-most panel in Fig.~\ref{??}.
+The dashed curves and the grey tinted curves in this panel do not allign.
+
+the upper limit 
+of the Cavalieri integral in Eq. As the upper limit of the Cavalieri integral depends on
+
+As the shape of the infinitesimals which make up the regions depicted in Fig depend of the integration limit of the 
+Cavalieri integral or stated differently on the value of $t$ and $\alpha$.
 

### 2019-04-30 fractional/CMJ style files/article-template.tex
made good progress with paper, example section

@@
 
-Each of the regions depicted in Fig.~\ref{} are made up of an infinite number of infinitesimals, the shape of which is determined by their right edges, i.e. by the value 
-of both $\alpha$ and $t$. The notion that $t$ alters the shape of the infinitesimals can easily be confirmed through visual inspection. The 
-dashed grey curves and the solid grey-tinted curves in the right-most panel are not the same, i.e.$\mathsf{B}_T^{\alpha}\neq\mathcal{B}_T^{\alpha}$.
+As was the case for $R$, each of the regions depicted in Fig.~\ref{} are made up of an infinite number of infinitesimals, the shape of which is determined by their right edges, i.e. by the value 
+of both $\alpha$ and $t$. The notion that $t$ and $\alpha$ alters the shape of the infinitesimals can easily be confirmed through visual inspection. In the case of $\alpha$: 
+the grey-tinted solid curves depicted in each panel are not equal to one-another.
+Similarly, in the case of $t$: the dashed grey curves and the solid grey-tinted curves in the right-most panel are not equal to one-another, i.e.$\mathsf{B}_T^{\alpha}\neq\mathcal{B}_T^{\alpha}$.
+
+Interestingly, the effect of $\alpha$ on the shape of the infinitesimals which make up the regions depicted in Fige is larger than that of $t$. 
+The curves associated with the ininitesimals obtained by varying $t$, whilst keeping the value of $\alpha$ fixed are very similar in nature and there exists a high degree of correlation between them (if their
+size are ignored).
+The curves associated with the infinitesimals obtained by varying $\alpha$, whilst keeping the value of $t$ fixed are quite different from one another (the aforementioned curves are not highly correlated with
+one another).
+
+The area associated with the regions depicted in Fig. are plotted in Fig using circular markers. The circular marker is depicted in Figure using the same tint-of-gray
+
+it is $\alpha$  
+Although $\alpha$ and $t$ alters the shape of the infinitesimals which make up the regions depicted in Fig.,
 

### 2019-04-30 fractional/CMJ style files/article-template.tex
made good progress on paper

@@
 
-The area associated with the regions depicted in Fig. are plotted in Fig using circular markers. The circular marker is depicted in Figure using the same tint-of-gray
+If we evaluate the integral in Eq for all $\alpha\in \mathsf{A}$ we obtain the curves in the left-most column of Table.... These curves are depicted in Fig.
+The area of the regions depicted in Fig are also plotted in Fig using circular markers. As expected, the circular markers that correspond to the areas of the regions 
+from a particular choice of $\alpha$ (i.e. from a particular panel of Fig) in Fig lie on the curve in Fig that is associated with the same choice of $alpha$. Moreover, note that we have adopted the 
+same color scheme in Fig and Fig. Using the same color scheme in both Figures makes it clear which of the area values in Fig can be associated with which regions in Fig.
+
+The circular markers in Figure ?? is depicted using the same tint-of-gray with which the right edge of the region  in question is depicted in Fig.
+
+Each of the curves 
+in Fig can therefore be associated with one of the panels in Fig. The area associated with the regions depicted in each of the panels in Fig. are plotted on the curves 
+in 
+associated with a particular panel appropriate 
+curves 
+in Fig using circular markers. The circular marker is depicted in Figure using the same tint-of-gray with which the 
+right edge of the region in question is depicted in Fig.
 

### 2019-05-07 fractional/CMJ style files/article-template.tex
improved example section once again

@@
 \usepackage{college-math-j}
+\usepackage{xfrac}
 
@@
 
-We know that a Cavalieri integral can be interpreted as the area which is obtained by summing together the area associated with an infinite number of non-rectangular infinitesimals whose shape 
-is determined by the integration limits of the Cavalieri integral. Note that neither $g_t^{\alpha}(\tau)$ nor $a_t^{\alpha}(y)$ are static functions, 
-they depend on the value of $\alpha$ and $t$.
+%We know that a Cavalieri integral can be interpreted as the area which is obtained by summing together the area associated with an infinite number of non-rectangular infinitesimals whose shape 
+%is determined by the integration limits of the Cavalieri integral. Note that neither $g_t^{\alpha}(\tau)$ nor $a_t^{\alpha}(y)$ are static functions, 
+%they depend on the value of $\alpha$ and $t$.
 This implies that a fractional integral of order $\alpha$ and extent $t$ can be interpeted as the area obtained by summing together the area associated with an infinite number of infinitesimals whose
-shape is determined by $\alpha$ and $t$, i.e. the geometric interpretation of Eq.~\eqref{eq:ex1_raw} is non-static as it depends on the value of $\alpha$ and $t$.
+%shape is determined by $\alpha$ and $t$, i.e. the geometric interpretation of Eq.~\eqref{eq:ex1_raw} is non-static as it depends on the value of $\alpha$ and $t$.
 
-Lets clarify the above by working through a detailed example. If we set the value of $\alpha$ to $\frac{4}{5}$ and the value of $t$ to 10 in Eq.~\eqref{eq:ex1} we obtain:
+If we set the value of $\alpha$ to $\sfrac{4}{5}$ and the value of $t$ to 10 in Eq.~\eqref{eq:ex1} we obtain:
 \begin{equation}
-\int_{a_{10}^{\frac{4}{5}}(y)}^{b_{10}^{\frac{4}{5}}(y)} f(\tau)~d\tau 
+\label{eq:ex1_specific}
+A_{10}^{\sfrac{4}{5}}=\int_{a_{10}^{\frac{4}{5}}(y)}^{b_{10}^{\frac{4}{5}}(y)} f(\tau)~d\tau 
 \end{equation}
-Let $R_{10}^{\frac{4}{5}}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{10}^{\frac{4}{5}}(y)$.
-The region $R_{10}^{\frac{4}{5}}$ is depicted and labelled in the right-most panel of Figure.~\ref{??}.
-We are now in a position to assign a geometric
-interpretaion to Eq.~\eqref{}.
-We can approximate the area of $R_{10}^{\frac{4}{5}}$ by summing together the area of $n$ non-rectangular integration strips of the same width that inscribe $R_{10}^{\frac{4}{5}}$.
-The only resctriction being: the sides of these non-rectangualar integration strips have to be translations of $b_{10}^{\frac{4}{5}}(y)$.
-Taking the limit of the aformentioned sum as $n\rightarrow \infty$ results in 
-Eq??, i.e.
-the area of $R_{10}^{\frac{4}{5}}$.
-The case in which we try to approximate the area of $R_{10}^{\frac{4}{5}}$ using only five non-rectangular integration strips of equal width is depicted in the right-most panel of Figure~\ref{??}.
-The sides of the
-aforementioned five integration strips are depicted in Fig.~\ref{??} using dahsed lines.
-The analytic expressions associated with these dashed curves are contained in the set $\mathsf{B}_{10}^{\frac{4}{5}}$.
+Let $R_{10}^{\sfrac{4}{5}}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{10}^{\sfrac{4}{5}}(y)$.
+The region $R_{10}^{\sfrac{4}{5}}$ is depicted and labelled in the right-most panel of Figure.~\ref{??}.
+Moreover, let $A_{10}^{\sfrac{4}{5}}$ denote the area of $R_{10}^{\sfrac{4}{5}}$. We are now in a position to assign a geometric interpretation to Eq.~\eqref{eq:ex1_specific}.  
+We can approximate the area of $A_{10}^{\sfrac{4}{5}}$ by summing together the area of $n$ equal width non-rectangular integration strips that inscribe $R_{10}^{\sfrac{4}{5}}$. 
+Furthermore, the sides of these non-rectangular integration strips have to be translations of $b_{10}^{\sfrac{4}{5}}(y)$.
+If we take the limit of the aforementioned sum as $n\rightarrow \infty$ we obtain $A_{10}^{\sfrac{4}{5}}$, i.e. the region $R_{10}^{\sfrac{4}{5}}$ is made up 
+of an infinite number of infinitesimals; all of them being translations of $b_{10}^{\sfrac{4}{5}}(y)$.
+The special case in which we approximate $A_{10}^{\sfrac{4}{5}}$ using five equal width non-rectangular integration strips is depicted in the right-most panel of Figure~\ref{??}.
+The sides of the aforementioned five integration strips are depicted in Fig.~\ref{??} using dashed lines. Let $\mathsf{B}_{10}^{\sfrac{4}{5}}$ denote the set containing these dashed curves.
 
-Varying both $\alpha$ and $t$ results in Eq.~\ref{eq:ex1}.
-Eq.
-can be associated with a multitude of regions.
-Let $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}=\{R_t^{\alpha}|t\in\mathsf{T},~\alpha\in\mathsf{A}\}$.
-The regions in the set $\mathsf{R}_{\mathsf{T}}$
-are depicted in Fig.~\textbf{??}. The regions that are depicted in each of the panels of Fig.~\ref{??} were generated by varying $t$, whilst keeping the value of $\alpha$ fixed. 
+Varying both $\alpha$ and $t$ results in Eq.~\eqref{eq:ex1}. In contrast with Eq.~\eqref{eq:ex1_specific}, Eq.~\eqref{eq:ex1} can be associated with a multitude of regions. 
+Let $R_{t}^{\alpha}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{t}^{\alpha}(y)$.
+Moreover, let $A_{t}^{\alpha}$ denote the area of $R_{t}^{\alpha}$ and let $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}=\{R_t^{\alpha}|t\in\mathsf{T},~\alpha\in\mathsf{A}\}$.
+The regions in the set $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}$ are depicted in Fig.~\textbf{??}.
+The regions that are depicted in each of the panels of Fig.~\ref{??} were generated by varying $t$, whilst keeping the value of $\alpha$ fixed.
 The title of each panel indicate which $\alpha$-value was used to generate the regions depicted in each panel. The only difference between the regions located in each 
-panel is their right edges. The right edges of the regions in each panel are depicted using varying shades of gray. The lighter the shade with which an edge is depicted 
-the larger the $t$-value is that was used to generate it.
+panel is their right edges. The right edges of the regions in each panel are depicted using varying shades of gray. The lighter the shade with which an edge is depicted, 
+the larger the $t$-value is, that was used to generate it.
 
-As was the case for $R$, each of the regions depicted in Fig.~\ref{} are made up of an infinite number of infinitesimals, the shape of which is determined by their right edges, i.e. by the value 
-of both $\alpha$ and $t$. The notion that $t$ and $\alpha$ alters the shape of the infinitesimals can easily be confirmed through visual inspection. In the case of $\alpha$: 
-the grey-tinted solid curves depicted in each panel are not equal to one-another.
-Similarly, in the case of $t$: the dashed grey curves and the solid grey-tinted curves in the right-most panel are not equal to one-another, i.e.$\mathsf{B}_T^{\alpha}\neq\mathcal{B}_T^{\alpha}$.
-
-Interestingly, the effect of $\alpha$ on the shape of the infinitesimals which make up the regions depicted in Fige is larger than that of $t$. 
-The curves associated with the ininitesimals obtained by varying $t$, whilst keeping the value of $\alpha$ fixed are very similar in nature and there exists a high degree of correlation between them (if their
+As was the case for $R_{10}^{\sfrac{4}{5}}$, each of the regions depicted in Fig.~\ref{} are made up of an infinite number of infinitesimals.
+The infinitesimals that make up a specific region are translations of that region's right edge.
+The following observations can be made by inspecting Fig.\ref{??}: 
+\begin{description}
+ \item[Effect of $\alpha$] the grey-tinted solid curves depicted in each panel are not equal to one-another.
+ \item[Effect of $t$] the dashed grey curves and the solid grey-tinted curves in the right-most panel are not equal to one-another.
+\end{description}
+We can therefore draw the following conclusion: the value of both $\alpha$ and $t$ alters the shape of the infinitesimals that make up the regions in Fig~\ref{??}.
+Interestingly, the effect of $\alpha$ on the shape of the infinitesimals that make up the regions depicted in Fig~\ref{??} is larger than the effect that $t$ has on their shape.
+The curves associated with the infinitesimals obtained by varying $t$, whilst keeping the value of $\alpha$ fixed are very similar in nature and there exists a high degree of correlation between them (if their
 size are ignored).
@@
 one another).
+
+%In the case of $\alpha$: the grey-tinted solid curves depicted in each panel are not equal to one-another.
+Similarly, in the case of $t$: the dashed grey curves and the solid grey-tinted curves in the right-most panel are not equal to one-another, i.e.$\mathsf{B}_T^{\alpha}\neq\mathcal{B}_T^{\alpha}$.
 

### 2019-05-07 fractional/CMJ style files/article-template.tex
added more meat to example section

@@
 The region $R_{10}^{\sfrac{4}{5}}$ is depicted and labelled in the right-most panel of Figure.~\ref{??}.
-Moreover, let $A_{10}^{\sfrac{4}{5}}$ denote the area of $R_{10}^{\sfrac{4}{5}}$. We are now in a position to assign a geometric interpretation to Eq.~\eqref{eq:ex1_specific}.  
+Moreover, let $A_{10}^{\sfrac{4}{5}}$ denote the area of $R_{10}^{\sfrac{4}{5}}$. We are now in a position to assign a geometric interpretation to Eq.~\eqref{eq:ex1_specific} as it 
+contains a Cavalieri integral.
 We can approximate the area of $A_{10}^{\sfrac{4}{5}}$ by summing together the area of $n$ equal width non-rectangular integration strips that inscribe $R_{10}^{\sfrac{4}{5}}$.
@@
 
-Varying both $\alpha$ and $t$ results in Eq.~\eqref{eq:ex1}. In contrast with Eq.~\eqref{eq:ex1_specific}, Eq.~\eqref{eq:ex1} can be associated with a multitude of regions. 
+Varying both $\alpha$ and $t$ results in Eq.~\eqref{eq:ex1}. In contrast with Eq.~\eqref{eq:ex1_specific}, Eq.~\eqref{eq:ex1} can be associated with more than one region. 
 Let $R_{t}^{\alpha}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{t}^{\alpha}(y)$.
@@
 \begin{description}
- \item[Effect of $\alpha$] the grey-tinted solid curves depicted in each panel are not equal to one-another.
- \item[Effect of $t$] the dashed grey curves and the solid grey-tinted curves in the right-most panel are not equal to one-another.
+ \item[Effect of $\alpha$] the grey-tinted solid curves depicted in the different panels of Fig.~\ref{} are not equal to one-another.
+ \item[Effect of $t$] the grey-tinted solid curves depicted in each of the panels of Fig.~\ref{} are not translations of one-another.
+Moreover, the dashed grey curves and the solid grey-tinted curves in the right-most panel are not equal to one-another.
 \end{description}
@@
 
-If we evaluate the integral in Eq for all $\alpha\in \mathsf{A}$ we obtain the curves in the left-most column of Table.... These curves are depicted in Fig.
-The area of the regions depicted in Fig are also plotted in Fig using circular markers. As expected, the circular markers that correspond to the areas of the regions 
-from a particular choice of $\alpha$ (i.e. from a particular panel of Fig) in Fig lie on the curve in Fig that is associated with the same choice of $alpha$. Moreover, note that we have adopted the 
-same color scheme in Fig and Fig. Using the same color scheme in both Figures makes it clear which of the area values in Fig can be associated with which regions in Fig.
+If we evaluate the integral in Eq.~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ we obtain the curves in the left-most column of Table~\ref{??}. These curves are depicted in Fig~\ref{??}.
+The area of the regions depicted in Fig.~\ref{??} are also plotted in Fig.~\ref{??} using circular markers.
+As expected, the circular markers in Fig.~\ref{??} that correspond to the areas of the regions in Fig.~\ref{??}
+associated with a particular choice of $\alpha$ (i.e.
+regions depicted in a particular panel of Fig.~\ref{??}) fall on the curve in Fig.~\ref{??}; associated with the same choice of $\alpha$.
+Moreover, note that we have adopted the
+same coloring scheme in Fig.~\ref{??} and Fig.~\ref{??}.
+Using the same coloring scheme in both figures makes it clear which of the area values in Fig.~\ref{??} can be associated with which regions in Fig.~\ref{??}.
+To summarize, Fig.~\ref{??}, therefore, depicts a non-static non-rectangular sum-based geometric interpretation of Eq.~\eqref{}. Moreover, Fig.~\ref{??} corroborates this 
+geometric interpretation.
+
+Let us know consider a different fractional integral:
+\begin{equation}
+\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \frac{1}{\Gamma(\alpha)}\int_0^t \sqrt{\tau}(t-\tau)^{\alpha-1}~d\tau. 
+\end{equation}
+If we evaluate the integral in Eq.~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ we obtain the curves in the right-most column of Table~\ref{??}. These curves are depicted in Fig~\ref{??}.
+The non-static non-rectangular sum-based geometric interpretation associated with Eq.~\eqref{eq:ex1} is depicted in Fig. The validity of this interpretation is corroborated by Fig.
+
+To conclude this section, a fractional integral of order $\alpha$ and extent $t$ can be interpreted as the area obtained by summing together the area associated with an infinite number of infinitesimals whose
+shape is determined by $\alpha$ and $t$. The geometric interpretation of a fractional integral is, therefore, non-static as it depends on the value of both $\alpha$ and $t$.
+
+%the fractional integral in Eq.~\ref{??} can be interpreted as the area which is obtained by summing together the area associated with an infinite number of non-rectangular infinitesimals whose shape 
+%is determined by the integration limits of the Cavalieri integral. Note that neither $g_t^{\alpha}(\tau)$ nor $a_t^{\alpha}(y)$ are static functions, 
+%they depend on the value of $\alpha$ and $t$.
+This implies that a fractional integral of order $\alpha$ and extent $t$ can be interpeted as the area obtained by summing together the area associated with an infinite number of infinitesimals whose
+%shape is determined by $\alpha$ and $t$, i.e. the geometric interpretation of Eq.~\eqref{eq:ex1_raw} is non-static as it depends on the value of $\alpha$ and $t$.
 

### 2019-05-21 fractional/CMJ style files/article-template.tex
added more text to article

@@
 
-The fractional integral is defined as (need to be more explicit here). Need to add how it has come about... Start with a single integral, expand to the general case and then 
-to a general $\alpha$. 
+Recall that the Riemann-Liouville fractional integral of order $\alpha$ is defined as:
 \begin{equation}
+\label{eq:RL_frac_int}
 \frac{1}{\Gamma(\alpha)}\int_{0}^{t}f(\tau)(t-\tau)^{\alpha-1}~d\tau
@@
 
-Podlubny showed that the fractional integral can be rewritten as a Riemann-Stieltjes integral:
+Podlubny showed that the above fractional integral can be rewritten as a Riemann-Stieltjes integral:
 \begin{equation}
@@
 
-Note that $g_t^{\alpha}(\tau)$ is always invertable, since $\frac{d g_t^{\alpha}}{d \tau} = \frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)}>0$ for $\tau\in[0,t]$.
+Note that $g_t^{\alpha}(\tau)$ is always invertable, since $\frac{d g_t^{\alpha}}{d \tau} = \frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)}>0$ for $\tau\in[0,t]$. The inverse 
+of $g_t^{\alpha}(\tau)$ is equal to:
+\begin{equation}
+h_t^{\alpha}(x) = t - \sqrt[\alpha]{t^{\alpha} - \Gamma(\alpha+1)x}
+\end{equation}
 
-We can now transform Equation~\ref{eq:rs} into an equivalent Cavalieri integral:
+Grobler et.
+al showed that it is trivial to convert a Riemann-Stieltjes integral into a Cavalieri integral.
+We review this conversion procedure in the Cavalieri section of this paper.
+Applying their approach to Eq.~\ref{eq:rs} results in:
 \begin{equation}
@@
 \begin{equation}
-a_t^{\alpha}(y) = f^{-1}(y) - \frac{t^{\alpha}-(t-f^{-1}(y))^{\alpha}}{\Gamma(\alpha+1)}
+a_t^{\alpha}(y) = f^{-1}(y) - \frac{t^{\alpha}-(t-f^{-1}(y))^{\alpha}}{\Gamma(\alpha+1)}.
 \end{equation}
+Note, Eq.~\eqref{} is obtained by substituting Eq.~\eqref{} into Eq.~\eqref{}.
 
-Since Equation~\ref{eq:cav} is a Cavalieri integral, it has a clear geometric interpretation. The integral in eq xxx can be interpreted as an infinite
+Since Equation~\ref{eq:cav} is a Cavalieri integral, it has a clear geometric interpretation. The integral in Equation~\ref{eq:RL_frac_int} can, therefore, be interpreted as an infinite
 sum of infinitesimally small non–rectangular integration strips whose shape is determined by $\alpha$ and $t$. The shape of the integration 
@@
 reduces to a normal Riemann integral as the integration strips become rectangular for this particular choice of $\alpha$ (its shape is now also no longer affected by $t$).
-
-\begin{equation}
-h_t^{\alpha}(x) = t - \sqrt[\alpha]{t^{\alpha} - \Gamma(\alpha+1)x}
-\end{equation}
 
@@
 The region $R_{10}^{\sfrac{4}{5}}$ is depicted and labelled in the right-most panel of Figure.~\ref{??}.
-Moreover, let $A_{10}^{\sfrac{4}{5}}$ denote the area of $R_{10}^{\sfrac{4}{5}}$. We are now in a position to assign a geometric interpretation to Eq.~\eqref{eq:ex1_specific} as it 
-contains a Cavalieri integral.
-We can approximate the area of $A_{10}^{\sfrac{4}{5}}$ by summing together the area of $n$ equal width non-rectangular integration strips that inscribe $R_{10}^{\sfrac{4}{5}}$.
-Furthermore, the sides of these non-rectangular integration strips have to be translations of $b_{10}^{\sfrac{4}{5}}(y)$.
-If we take the limit of the aforementioned sum as $n\rightarrow \infty$ we obtain $A_{10}^{\sfrac{4}{5}}$, i.e. the region $R_{10}^{\sfrac{4}{5}}$ is made up 
-of an infinite number of infinitesimals; all of them being translations of $b_{10}^{\sfrac{4}{5}}(y)$.
-The special case in which we approximate $A_{10}^{\sfrac{4}{5}}$ using five equal width non-rectangular integration strips is depicted in the right-most panel of Figure~\ref{??}.
+Moreover, let $A_{10}^{\sfrac{4}{5}}$ denote the area of $R_{10}^{\sfrac{4}{5}}$.
+We can approximate the area of $R_{10}^{\sfrac{4}{5}}$ by summing together the area of $n$ equal width non-rectangular integration strips that inscribe $R_{10}^{\sfrac{4}{5}}$.
+Furthermore, the sides of the non-rectangular integration strips we use in this approximation have to be translations of $b_{10}^{\sfrac{4}{5}}(y)$.
+If we take the limit of the aforementioned sum as $n\rightarrow \infty$ we obtain $A_{10}^{\sfrac{4}{5}}$, i.e. if we evaluate the Cavalieri 
+integral in Eq.~\eqref{??} we obtain $A_{10}^{\sfrac{4}{5}}$ (as we mentioned in the previous section).
+We can, therefore, think of Eq.~\eqref{} as implying that that the region  $R_{10}^{\sfrac{4}{5}}$ is made up
+of an infinite number of non-rectangular infinitesimals; all of them being translations of $b_{10}^{\sfrac{4}{5}}(y)$.
+Moreover, the special case in which we approximate $A_{10}^{\sfrac{4}{5}}$ using five equal width non-rectangular integration strips is depicted in the right-most panel of Figure~\ref{??}.
 The sides of the aforementioned five integration strips are depicted in Fig.~\ref{??} using dashed lines. Let $\mathsf{B}_{10}^{\sfrac{4}{5}}$ denote the set containing these dashed curves.
+
+%We can, therefore, interpet Eq.~\eqref{}  The region $R_{10}^{\sfrac{4}{5}}$ is, therefore, made up 
+%of an infinite number of non-rectangular infinitesimals; all of them being translations of $b_{10}^{\sfrac{4}{5}}(y)$.
 

### 2019-05-21 fractional/CMJ style files/article-template.tex
added more text

@@
 \section{Riemann-Liouville Fractional Integral}
-Let
+In this section we derive the definition of the Riemann-Liouville fractional integral of order $\alpha$. Let
 \begin{equation}
@@
 
+Let $\mathsf{A} = \{0,0.2,0.4,0.6,0.8,1\}$. The analytic expressions of $g_t^{\alpha}(\tau)$ and $h_t^{\alpha}(x)$ are presented in Table~\ref{eq:} for $\alpha\in\mathsf{A}$ and $t=10$. 
+The expressions in Table~\ref{eq:} are depicted in Fig~\ref{fig:}.
+
 Grobler et.
@@
 
-Since Equation~\ref{eq:cav} is a Cavalieri integral, it has a clear geometric interpretation. The integral in Equation~\ref{eq:RL_frac_int} can, therefore, be interpreted as an infinite
-sum of infinitesimally small non–rectangular integration strips whose shape is determined by $\alpha$ and $t$. The shape of the integration 
-strip will change if either $\alpha$ or $t$ is changed. If $\alpha$ is equal to one, however, then the integral 
-reduces to a normal Riemann integral as the integration strips become rectangular for this particular choice of $\alpha$ (its shape is now also no longer affected by $t$).
+Since Equation~\ref{eq:cav} is a Cavalieri integral, it has a clear geometric interpretation. The integral in Equation~\ref{eq:RL_frac_int} can, therefore, be interpreted as the area obtained 
+by summing toghether the area of an infinite number of infinitesimally small non–rectangular integration strips whose shape is determined by $\alpha$ and $t$. The shape of the integration 
+strip will change if either $\alpha$ or $t$ is changed.
+If $\alpha$ is equal to one, however, then the integral reduces to a normal Riemann integral as the integration strips become rectangular for this particular choice of $\alpha$ (its shape is now also no longer affected by $t$).
 
-By employing $h$ we can transform eq.~\ref{eq:cav} into the following Riemann integral:
+Furthermore, Eq.~\eqref{??} implies that we can use $h_t^{\alpha}(x)$ to convert Eq.~\eqref{eq:cav} into the following Riemann integral:
 \begin{equation}
@@
 \end{equation}
+We can, therefore, evaluate Eq.~\eqref{eq:cav} in one of two ways: we can either evaluate Eq.~\eqref{} or we can evaluate Eq.~\eqref{}.
 

### 2019-05-21 fractional/CMJ style files/article-template.tex
started adding text to explain the purpose of the example section

@@
 The function $f(\tau) =\tau$ is depicted in Figure~\ref{??}.
-We can assign a geometric interpretation to the above fractional integral by converting it into a Cavalieri integral using two steps.
+As we mentioned in the previous section, we can assign a geometric interpretation to the above fractional integral by converting it into a Cavalieri integral using two steps.
 First, we convert
@@
 \end{equation}
+
+As we mentioned in the previous section Eq.~\ref{eq:ex1} has a clear geometric interpretation. It can be interpreted as the area obtained by summing togheher the areas of an infinite 
+number of infinitesimals whose shape is determined by $\alpha$ and $t$. The thing which remains unclear, however, is in what way does $\alpha$ and $t$ affect the 
+shape of the aforementioned infinitesimals. We will this question using two steps: we will first investigate the shape of the infinitesimal we obtain by fixing 
+$\alpha$ and $t$ to specific values. We will then explore how varying the value of $\alpha$ and $t$ affects the shape of the infinitesimals.
 

### 2019-05-22 fractional/CMJ style files/article-template.tex
made good progress in describing the example section of paper

--- 2019-05-21 fractional/CMJ style files/article-template.tex
@@
 \section{Riemann-Liouville Fractional Integral}
-In this section we derive the definition of the Riemann-Liouville fractional integral of order $\alpha$. Let
+In this section we present the definition of the Riemann-Liouville fractional integral of order $\alpha$. Let
 \begin{equation}
@@
 \end{equation}
+
+As we mentioned in the previous section Eq.~\ref{eq:ex1} has a clear geometric interpretation. It can be interpreted as the area obtained by summing togheher the areas of an infinite 
+number of infinitesimals whose shape is determined by $\alpha$ and $t$, i.e. the aforementioned infinitesimals have to be translations of $b_{\alpha}^t(y)$ which, in turn, is 
+function of $\alpha$ and $t$. The geometric interpretation of Eq.~\eqref{eq:ex1_raw} is, therefore, non-static as it depends on the value of $\alpha$ and $t$. 
+The thing which remains unclear, however, is in what way does $\alpha$ and $t$ affect the shape of the aforementioned infinitesimals, i.e.
+how does the value of $\alpha$ and $t$ affect the shape of $b_{\alpha}^t(y)$.
+We will answer this question using two steps.
+First off, we will fix the value of $alpha$ and $t$ in Eq.~\eqref{} and then depict $b_{\alpha}^t(y)$.
+We will then explore how varying the value of $\alpha$ and $t$ in Eq.~\eqref{} affects the shape $b_{\alpha}^t(y)$.
 
@@
 Moreover, let $A_{10}^{\sfrac{4}{5}}$ denote the area of $R_{10}^{\sfrac{4}{5}}$.
-We can approximate the area of $R_{10}^{\sfrac{4}{5}}$ by summing together the area of $n$ equal width non-rectangular integration strips that inscribe $R_{10}^{\sfrac{4}{5}}$.
-Furthermore, the sides of the non-rectangular integration strips we use in this approximation have to be translations of $b_{10}^{\sfrac{4}{5}}(y)$.
-If we take the limit of the aforementioned sum as $n\rightarrow \infty$ we obtain $A_{10}^{\sfrac{4}{5}}$, i.e. if we evaluate the Cavalieri 
-integral in Eq.~\eqref{??} we obtain $A_{10}^{\sfrac{4}{5}}$ (as we mentioned in the previous section).
-We can, therefore, think of Eq.~\eqref{} as implying that that the region  $R_{10}^{\sfrac{4}{5}}$ is made up
+For the sake of completeness, lets first verify whether we can emplloy the Cavalieri integral in Eq.~\ref{eq:ex1_specific} to compute $A_{10}^{\sfrac{4}{5}}$ from first principles.
+We can approximate the area of $R_{10}^{\sfrac{4}{5}}$ by summing together the area of $n$ equal width non-rectangular integration strips that inscribe $R_{10}^{\sfrac{4}{5}}$, i.e. we can 
+construct a so called Cavalieri sum. Furthermore, the sides of the non-rectangular integration strips we use in this approximation have to be translations of $b_{10}^{\sfrac{4}{5}}(y)$.
+If we take the limit of the aforementioned sum as $n\rightarrow \infty$ we obtain $A_{10}^{\sfrac{4}{5}}$, i.e.
+the result obtained via the aforementioned limit is the Cavalieri integral found in Eq.~\eqref{eq:ex1_specific}.
+In conclusion, we can think of Eq.~\eqref{} as implying that the region $R_{10}^{\sfrac{4}{5}}$ is made up
 of an infinite number of non-rectangular infinitesimals; all of them being translations of $b_{10}^{\sfrac{4}{5}}(y)$.
+Note, the rightmost curve depicted in the rightmost panel of Fig...
+is $b_{10}^{\sfrac{4}{5}}(y)$.
 Moreover, the special case in which we approximate $A_{10}^{\sfrac{4}{5}}$ using five equal width non-rectangular integration strips is depicted in the right-most panel of Figure~\ref{??}.
@@
 panel is their right edges. The right edges of the regions in each panel are depicted using varying shades of gray. The lighter the shade with which an edge is depicted, 
-the larger the $t$-value is, that was used to generate it.
+the larger the $t$-value is, that is assoiciated with it.
 
@@
 \end{description}
-We can therefore draw the following conclusion: the value of both $\alpha$ and $t$ alters the shape of the infinitesimals that make up the regions in Fig~\ref{??}.
+We can therefore draw the following conclusion: the value of both $\alpha$ and $t$ alters the shape of the infinitesimals (i.e.
+$b_{t}^{\alpha}(y)$) that make up the regions in Fig~\ref{??}.
 Interestingly, the effect of $\alpha$ on the shape of the infinitesimals that make up the regions depicted in Fig~\ref{??} is larger than the effect that $t$ has on their shape.
 The curves associated with the infinitesimals obtained by varying $t$, whilst keeping the value of $\alpha$ fixed are very similar in nature and there exists a high degree of correlation between them (if their
-size are ignored).
+sizes are ignored).
 The curves associated with the infinitesimals obtained by varying $\alpha$, whilst keeping the value of $t$ fixed are quite different from one another (the aforementioned curves are not highly correlated with

### 2019-05-22 fractional/CMJ style files/article-template.tex
fixed Riemann-Stieltjes section

@@
 \noindent
-\textbf{NEED TO REWRITE SOME OF IT} with $(x_i^2)_{i=0}^n$ being arbitrary partition points on the $x$-axis. Eq.~\eqref{eq:g_int2} shows us that the function of the integrator $g$ is to
-map points in the interval $[a',b']$ to other locations on the $x$-axis. When $g$ is monotone increasing, it maps points in the interval $[a',b']$ to $[a,b]$,
-with $a = g(a')$ and $b = g(b')$. The integral in Equation~\ref{eq:g_int2} is hard to evaluate in its present form. If $g$ is differentiable, however, then it becomes trivial to 
+with $(x_i^2)_{i=0}^n$ being arbitrary partition points on the $x$-axis. 
+The function $g$ is known as the integrator and if it is monotone increasing then it maps points in the interval $[a',b,]$ to the interval $[a,b]$, with $a = g(a')$ and $b = g(b')$.
+The integral in Equation~\ref{eq:g_int2} is hard to evaluate in its present form. If $g$ is differentiable, however, then it becomes trivial to 
 evaluate a Riemann-Stieltjes integral due to the following identity:

### 2019-05-22 fractional/CMJ style files/article-template.tex
starting to make some real progress with cleaning up the paper

@@
 The function $g$ is known as the integrator and if it is monotone increasing then it maps points in the interval $[a',b,]$ to the interval $[a,b]$, with $a = g(a')$ and $b = g(b')$.
-The integral in Equation~\ref{eq:g_int2} is hard to evaluate in its present form. If $g$ is differentiable, however, then it becomes trivial to 
+The integral in Eq.~\eqref{eq:g_int2} is hard to evaluate in its present form. If $g$ is differentiable, however, then it becomes trivial to 
 evaluate a Riemann-Stieltjes integral due to the following identity:
@@
 
+\noindent
 There, however, exists a more straightforward way do determine the area of $R$, i.e. we can sum together the area of non-rectangular integration strips inscribing $R$ instead of
@@
 \end{equation}
-The partition points $(x_i^2)_{i=0}^{n}$ are depicted in Fig.~\ref{fig:caval2}. Note that Equation~\ref{eq:cav_sum} approximates the area of $R$. In the limit Equation~\ref{eq:cav_sum} approaches 
+The partition points $(x_i^2)_{i=0}^{n}$ are depicted in Fig.~\ref{fig:caval2}. Note that Eq.~\eqref{eq:cav_sum} approximates the area of $R$. In the limit Eq.~\eqref{eq:cav_sum} approaches 
 the Cavalieri integral:
@@
 
+\noindent
 Conversely, if $g$ is known (and not $a(y)$) and $g(a') = a$ then we can calculate $a(y)$ using the following:
@@
 \end{equation}
-Note the power of Equation~\ref{eq:a_y} it allows us to transform a Riemann-Stieltjes integral into a Cavalieri integral. 
-This transformation allows us to give a geometric interpretation of a Riemann-Stieltjes integral. The interpretation being,
-the sum of an infinite amount of non-rectangular infinitesimals whose shape is determined by $a(y)$.
+Note the power of Eq.~\eqref{eq:a_y} it allows us to transform a Riemann-Stieltjes integral into an equivalent Cavalieri integral. 
+Furthermore, this transformation enables us to assign a geometric interpretation to a Riemann-Stieltjes integral. The interpretation being:
+it represents the area obtained by summing together the area of an infinite number of non-rectangular infinitesimals whose shape is determined by $a(y)$.
 
@@
 \begin{equation}
-\Gamma(x) = \int_0^{\infty} t^{x-1} e^{-t}\,dt
+\Gamma(x) = \int_0^{\infty} t^{x-1} e^{-t}\,dt.
 \end{equation}
+The function $\Gamma(x)$ is depicted in Fig.~\ref{fig:gamma} for $x\in(-5,5)$.
 \begin{figure}[htb]
@@
 \includegraphics[width=0.75\textwidth]{gamma.pdf}
-\caption{A plot of $\Gamma(x)$. $\Gamma(x)$ is not defined for the non-negative integers.}
+\caption{A plot of $\Gamma(x)$ for $x\in(-5,5)$. $\Gamma(x)$ is not defined for the non-negative integers.}
 \label{fig:gamma}
@@
 \end{equation}
-If we apply the above operator in a repetative manner to $f$ we obtain the $n$th antiderivative of $f$ based at 0:
+If we apply the above operator in a repetitive manner to $f$ we obtain the $n$th antiderivative of $f$ based at 0:
 \begin{equation}
@@
 \end{equation}
-Applying Cauchy's formula for repetative integration to the above $n$th antiderivative of $f$ helps us express the above $n$th antiderivative as a single integral. 
-Applying Cauchy's formula to Equation~\ref{eq:n_anti} results in:
+Applying Cauchy's formula for repetitive integration to the above $n$th antiderivative of $f$ helps us express the above $n$th antiderivative as a single integral. 
+Applying Cauchy's formula to Eq.~\eqref{eq:n_anti} results in:
 \begin{equation}
@@
 \end{equation}
-As an example if $f(x)=x$ and $n=2$ then Equation~\ref{eq:cauchy} reduces to:
+As an example if $f(x)=x$ and $n=2$ then Eq.~\eqref{eq:cauchy} reduces to:
 \begin{equation}
@@
 \end{equation}
-The definition in Equation~\ref{eq:cauchy} can now be extended to an arbitrary fractional order by replacing $(n-1)!$ with the Gamma function:
+The definition in Eq.~\eqref{eq:cauchy} can now be extended to an arbitrary fractional order by replacing $(n-1)!$ with the Gamma function (see Fig.~\ref{fig:gamma}):
 \begin{equation}
@@
 \end{equation}
-Equation~\ref{eq:frac_integral} is known as the Riemann-Liouville fractional integral of order $\alpha$. As an example if $f(x)=x$ and $\alpha=\frac{1}{2}$ then 
-Equation~\ref{eq:frac_integral} reduces to:
+Eq.~\eqref{eq:frac_integral} is known as the Riemann-Liouville fractional integral of order $\alpha$. As an example if $f(x)=x$ and $\alpha=\frac{1}{2}$ then 
+Eq.~\eqref{eq:frac_integral} reduces to:
 \begin{equation}
@@
 
-Podlubny showed that the above fractional integral can be rewritten as a Riemann-Stieltjes integral:
+\noindent
+Podlubny et al. showed that the above fractional integral can be rewritten as a Riemann-Stieltjes integral:
 \begin{equation}
@@
 
-Note that $g_t^{\alpha}(\tau)$ is always invertable, since $\frac{d g_t^{\alpha}}{d \tau} = \frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)}>0$ for $\tau\in[0,t]$. The inverse 
+\noindent
+Note that $g_t^{\alpha}(\tau)$ is always invertible, since $\frac{d g_t^{\alpha}}{d \tau} = \frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)}>0$ for $\tau\in[0,t]$. The inverse 
 of $g_t^{\alpha}(\tau)$ is equal to:
 \begin{equation}
-h_t^{\alpha}(x) = t - \sqrt[\alpha]{t^{\alpha} - \Gamma(\alpha+1)x}
+h_t^{\alpha}(\tau) = t - \sqrt[\alpha]{t^{\alpha} - \Gamma(\alpha+1)\tau}
 \end{equation}
 
-Let $\mathsf{A} = \{0,0.2,0.4,0.6,0.8,1\}$. The analytic expressions of $g_t^{\alpha}(\tau)$ and $h_t^{\alpha}(x)$ are presented in Table~\ref{eq:} for $\alpha\in\mathsf{A}$ and $t=10$. 
-The expressions in Table~\ref{eq:} are depicted in Fig~\ref{fig:}.
+\noindent
+Let $\mathsf{A} = \{0,0.2,0.4,0.6,0.8,1\}$.
+The analytic expressions of $g_{10}^{\alpha}(\tau)$ and $h_{10}^{\alpha}(\tau)$ are presented in Table~\ref{tab:gandh} for $\alpha\in\mathsf{A}$ and $t=10$.
+The expressions in Table~\ref{tab:gandh} are depicted in Fig~\ref{fig:gandh}.
+
+\begin{table}[h!]
+ \centering
+ \caption{The analytic expressions of $g_{10}^{\alpha}(\tau)$ and $h_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}$.}
+ \label{tab:gandh}
+ \begin{tabular}{|c || c | c|} 
+ \hline
+ $\alpha$ & $g_{10}^{\alpha}(\tau)$ & $h_{10}^{\alpha}(\tau)$ \\ [0.5ex] 
+ \hline\hline
+ $0$ & 0 & $y=0$ \\ 
+ $0.2$ & $[\Gamma\left (\frac{6}{5} \right )]^{-1}\left(\sqrt[5]{10}-\sqrt[5]{10-\tau}\right)$ & $10 - \left ( \sqrt[5]{10} -  \Gamma\left (\frac{6}{5} \right ) \tau \right )^5$  \\
+ $0.4$ & $[\Gamma\left (\frac{7}{5} \right )]^{-1}\left(\sqrt[5]{10^2}-\sqrt[5]{(10-\tau)^2}\right)$ & $10 - \sqrt{\left ( \sqrt[5]{10} -  \Gamma\left (\frac{7}{5} \right ) \tau \right )^5}$ \\
+ $0.6$ & $[\Gamma\left (\frac{8}{5} \right )]^{-1}\left(\sqrt[5]{10^3}-\sqrt[5]{(10-\tau)^3}\right)$ & $10 - \sqrt[3]{\left ( \sqrt[5]{10} -  \Gamma\left (\frac{8}{5} \right ) \tau \right )^5}$ \\
+ $0.8$ & $[\Gamma\left (\frac{9}{5} \right )]^{-1}\left(\sqrt[5]{10^4}-\sqrt[5]{(10-\tau)^4}\right)$ & $10 - \sqrt[4]{\left ( \sqrt[5]{10} -  \Gamma\left (\frac{9}{5} \right ) \tau \right )^5}$ \\ [1ex]
+ $1$ & $\tau$ & $\tau$ \\ [1ex] 
+ \hline
+ \end{tabular}
+ \end{table}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.75\textwidth]{gh.pdf}
+\caption{This figure depicts the curves of $g_{10}^{\alpha}(\tau)$ and $h_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}$. The curves associated with $g$ are plotted using 
+solid lines, while the curves plotted with dashed lines are associated with $h$. The lighter the shade with which a curve is depicted, the larger the $\alpha$-value is, that is associated with it.
+}
+\label{fig:gandh}
+\end{figure}
 
@@
 
-Since Equation~\ref{eq:cav} is a Cavalieri integral, it has a clear geometric interpretation. The integral in Equation~\ref{eq:RL_frac_int} can, therefore, be interpreted as the area obtained 
+Since Eq.~\eqref{eq:cav} is a Cavalieri integral, it has a clear geometric interpretation. The integral in Eq.~\eqref{eq:RL_frac_int} can, therefore, be interpreted as the area obtained 
 by summing toghether the area of an infinite number of infinitesimally small non–rectangular integration strips whose shape is determined by $\alpha$ and $t$. The shape of the integration 
@@
 We can, therefore, evaluate Eq.~\eqref{eq:cav} in one of two ways: we can either evaluate Eq.~\eqref{} or we can evaluate Eq.~\eqref{}.
-
-\begin{table}[h!]
-\centering
- \begin{tabular}{|c || c | c|} 
- \hline
- $\alpha$ & $g_{10}^{\alpha}(\tau)$ & $h_{10}^{\alpha}(\tau)$ \\ [0.5ex] 
- \hline\hline
- $0$ & 0 & $y=0$ \\ 
- $0.2$ & $[\Gamma\left (\frac{6}{5} \right )]^{-1}\left(\sqrt[5]{10}-\sqrt[5]{10-\tau}\right)$ & $10 - \left ( \sqrt[5]{10} -  \Gamma\left (\frac{6}{5} \right ) \tau \right )^5$  \\
- $0.4$ & $[\Gamma\left (\frac{7}{5} \right )]^{-1}\left(\sqrt[5]{10^2}-\sqrt[5]{(10-\tau)^2}\right)$ & $10 - \sqrt{\left ( \sqrt[5]{10} -  \Gamma\left (\frac{7}{5} \right ) \tau \right )^5}$ \\
- $0.6$ & $[\Gamma\left (\frac{8}{5} \right )]^{-1}\left(\sqrt[5]{10^3}-\sqrt[5]{(10-\tau)^3}\right)$ & $10 - \sqrt[3]{\left ( \sqrt[5]{10} -  \Gamma\left (\frac{8}{5} \right ) \tau \right )^5}$ \\
- $0.8$ & $[\Gamma\left (\frac{9}{5} \right )]^{-1}\left(\sqrt[5]{10^4}-\sqrt[5]{(10-\tau)^4}\right)$ & $10 - \sqrt[4]{\left ( \sqrt[5]{10} -  \Gamma\left (\frac{9}{5} \right ) \tau \right )^5}$ \\ [1ex]
- $1$ & $\tau$ & $\tau$ \\ [1ex] 
- \hline
- \end{tabular}
-\end{table}
 
@@
 
-\begin{table}[h!]
-\centering
- \begin{tabular}{|c || c|} 
- \hline
- Symbol & Definition  \\ [0.1ex]
- \hline 
- \rule{0pt}{2.5ex}
- $\mathsf{G}^{10}$ & $\{g_{10}^{\alpha}(\tau)|\alpha\in\{0,\frac{1}{5},\frac{2}{5},\frac{3}{5},\frac{4}{5}\}\}$\\ [0.5ex]
- $\mathsf{H}^{10}$ & $\{h_{10}^{\alpha}(\tau)|\alpha\in\{0,\frac{1}{5},\frac{2}{5},\frac{3}{5},\frac{4}{5}\}\}$\\ [0.5ex]
- $\mathsf{A}^{10}$ & $\{a_{10}^{\alpha}(\tau)|\alpha\in\{0,\frac{1}{5},\frac{2}{5},\frac{3}{5},\frac{4}{5}\}\}$\\ [0.5ex]
- $\mathsf{B}^{10}$ & $\{b_{10}^{\alpha}(\tau)|\alpha\in\{0,\frac{1}{5},\frac{2}{5},\frac{3}{5},\frac{4}{5}\}\}$\\ [0.5ex]
- $\mathsf{B}^{\frac{4}{5}}_1$ & $\{b_{t}^{\frac{4}{5}}(\tau)|t\in\alpha\in\{2,4,6,8,10\}$\\ [0.5ex]
- $\mathsf{B}^{\frac{4}{5}}_2$ & $\{b_{10}^{\frac{4}{5}}(\tau)-c|c\in\in\{0,2,4,6,8\}$\\ [0.5ex]
- \hline 
- \end{tabular}
-\end{table}
+% \begin{table}[h!]
+% \centering
+%  \begin{tabular}{|c || c|} 
+%  \hline
+%  Symbol & Definition  \\ [0.1ex]
+%  \hline 
+%  \rule{0pt}{2.5ex}
+%  $\mathsf{G}^{10}$ & $\{g_{10}^{\alpha}(\tau)|\alpha\in\{0,\frac{1}{5},\frac{2}{5},\frac{3}{5},\frac{4}{5}\}\}$\\ [0.5ex]
+%  $\mathsf{H}^{10}$ & $\{h_{10}^{\alpha}(\tau)|\alpha\in\{0,\frac{1}{5},\frac{2}{5},\frac{3}{5},\frac{4}{5}\}\}$\\ [0.5ex]
+%  $\mathsf{A}^{10}$ & $\{a_{10}^{\alpha}(\tau)|\alpha\in\{0,\frac{1}{5},\frac{2}{5},\frac{3}{5},\frac{4}{5}\}\}$\\ [0.5ex]
+%  $\mathsf{B}^{10}$ & $\{b_{10}^{\alpha}(\tau)|\alpha\in\{0,\frac{1}{5},\frac{2}{5},\frac{3}{5},\frac{4}{5}\}\}$\\ [0.5ex]
+%  $\mathsf{B}^{\frac{4}{5}}_1$ & $\{b_{t}^{\frac{4}{5}}(\tau)|t\in\alpha\in\{2,4,6,8,10\}$\\ [0.5ex]
+%  $\mathsf{B}^{\frac{4}{5}}_2$ & $\{b_{10}^{\frac{4}{5}}(\tau)-c|c\in\in\{0,2,4,6,8\}$\\ [0.5ex]
+%  \hline 
+%  \end{tabular}
+% \end{table}
 

### 2019-05-22 fractional/CMJ style files/article-template.tex
almost through geo section

@@
 \begin{equation}
+\label{eq:g_rl}
 g_t^{\alpha}(\tau) = \frac{\left \{t^{\alpha} - (t-\tau)^{\alpha} \right \}}{\Gamma(\alpha+1)}. 
@@
 
-Grobler et.
+\noindent
+Furthermore, Grobler et.
 al showed that it is trivial to convert a Riemann-Stieltjes integral into a Cavalieri integral.
-We review this conversion procedure in the Cavalieri section of this paper.
-Applying their approach to Eq.~\ref{eq:rs} results in:
+We review this conversion procedure in the Cavalieri section of this paper (see Fig.~\ref{fig:caval2}).
+If we apply their conversion steps to Eq.~\eqref{eq:rs} we obtain:
 \begin{equation}
@@
 \begin{equation}
+\label{eq:cav_a}
 a_t^{\alpha}(y) = f^{-1}(y) - \frac{t^{\alpha}-(t-f^{-1}(y))^{\alpha}}{\Gamma(\alpha+1)}.
 \end{equation}
-Note, Eq.~\eqref{} is obtained by substituting Eq.~\eqref{} into Eq.~\eqref{}.
+Eq.~\eqref{eq:cav_a} is obtained by substituting Eq.~\eqref{eq:g_rl} into Eq.~\eqref{eq:a_y}.
 
-Since Eq.~\eqref{eq:cav} is a Cavalieri integral, it has a clear geometric interpretation. The integral in Eq.~\eqref{eq:RL_frac_int} can, therefore, be interpreted as the area obtained 
-by summing toghether the area of an infinite number of infinitesimally small non–rectangular integration strips whose shape is determined by $\alpha$ and $t$. The shape of the integration 
-strip will change if either $\alpha$ or $t$ is changed.
+\noindent
+Since, Eq.~\eqref{eq:cav} is a Cavalieri integral it has a clear geometric interpretation (see Fig.~\ref{fig:caval2}).
+The integral in Eq.~\eqref{eq:RL_frac_int} can, therefore, be interpreted as the area obtained
+by summing together the area of an infinite number of infinitesimally small non–rectangular integration strips whose shape is determined by $\alpha$ and $t$. The shape of theses integration 
+strips will change if either $\alpha$ or $t$ is changed.
 If $\alpha$ is equal to one, however, then the integral reduces to a normal Riemann integral as the integration strips become rectangular for this particular choice of $\alpha$ (its shape is now also no longer affected by $t$).

### 2019-05-22 fractional/CMJ style files/article-template.tex
finished geo section

@@
 \begin{equation}
+\label{eq:main_cav}
 \int_{a(y)}^{b(y)}f(x)\,dx =\int_a^b f \circ h (x)\, dx = \int_{a'}^{b'} f(x) dg(x).
@@
 \noindent
-Since, Eq.~\eqref{eq:cav} is a Cavalieri integral it has a clear geometric interpretation (see Fig.~\ref{fig:caval2}).
-The integral in Eq.~\eqref{eq:RL_frac_int} can, therefore, be interpreted as the area obtained
-by summing together the area of an infinite number of infinitesimally small non–rectangular integration strips whose shape is determined by $\alpha$ and $t$. The shape of theses integration 
-strips will change if either $\alpha$ or $t$ is changed.
-If $\alpha$ is equal to one, however, then the integral reduces to a normal Riemann integral as the integration strips become rectangular for this particular choice of $\alpha$ (its shape is now also no longer affected by $t$).
+We can easily assign a geometric interpretation to Eq.~\eqref{eq:cav}, since it is a Cavalieri integral (see Fig.~\ref{fig:caval2}).
+The fractional integral in Eq.~\eqref{eq:RL_frac_int} can, therefore, be interpreted as the area obtained
+by summing together the area of an infinite number of infinitesimally small non-rectangular integration strips whose shape is determined by $\alpha$ and $t$.
+If $\alpha$ is equal to one, however, then the integral reduces to a normal Riemann integral as the integration strips become rectangular for this particular choice of $\alpha$ (its shape becomes independent of $t$).\\
 
-Furthermore, Eq.~\eqref{??} implies that we can use $h_t^{\alpha}(x)$ to convert Eq.~\eqref{eq:cav} into the following Riemann integral:
+\noindent
+Interestingly, Eq.~\eqref{eq:main_cav} implies that we can use $h_t^{\alpha}(\tau)$ to convert Eq.~\eqref{eq:cav} into the following Riemann integral:
 \begin{equation}
+\label{eq:option2}
 \int_0^{\frac{t^{\alpha}}{\Gamma(\alpha+1)}} f\circ h_{\alpha}^t (\tau) d\tau.  
 \end{equation}
-We can, therefore, evaluate Eq.~\eqref{eq:cav} in one of two ways: we can either evaluate Eq.~\eqref{} or we can evaluate Eq.~\eqref{}.
+We can, therefore, evaluate Eq.~\eqref{eq:cav} in one of two ways: we can either evaluate Eq.~\eqref{eq:rs} or we can evaluate Eq.~\eqref{eq:option2}.
 

### 2019-05-22 fractional/CMJ style files/article-template.tex
add article

@@
 \section{Examples}
-In this section we will illustrate the usefulness of the proposed geometric framework at the hand of two examples.
+In this section we will illustrate the usefulness of the non-static non-rectangular sum-based geometric interpretation we presented in the previous section at the 
+hand of two examples.\\
 
+\noindent
 Let us first consider the following fractional integral:
@@
 \end{equation}
-The function $f(\tau) =\tau$ is depicted in Figure~\ref{??}.
+The function $f(\tau) =\tau$ is depicted in Fig.~\ref{fig:geo1}.
 As we mentioned in the previous section, we can assign a geometric interpretation to the above fractional integral by converting it into a Cavalieri integral using two steps.
@@
 
-As we mentioned in the previous section Eq.~\ref{eq:ex1} has a clear geometric interpretation. It can be interpreted as the area obtained by summing togheher the areas of an infinite 
-number of infinitesimals whose shape is determined by $\alpha$ and $t$, i.e. the aforementioned infinitesimals have to be translations of $b_{\alpha}^t(y)$ which, in turn, is 
+\begin{figure}[htb]
+\centering
+\includegraphics[width=1\textwidth]{geo_int1.pdf}
+\caption{The non-static non-rectangular sum-based geometric interpretation of Eq.~\eqref{eq:ex1_raw}.}
+\label{fig:geo1}
+\end{figure}
+
+\noindent
+Since Eq.~\ref{eq:ex1}, is a Cavalieri integral it has a known geometric interpretation (see Fig.~\ref{fig:caval2}).
+It can be interpreted as the area obtained by summing together the areas of an infinite
+number of infinitesimals whose shape is determined by $\alpha$ and $t$. Moreover, these infinitesimals have to be translations of $b_t^{\alpha}(y)$ which, in turn, is 
 function of $\alpha$ and $t$. The geometric interpretation of Eq.~\eqref{eq:ex1_raw} is, therefore, non-static as it depends on the value of $\alpha$ and $t$. 
-The thing which remains unclear, however, is in what way does $\alpha$ and $t$ affect the shape of the aforementioned infinitesimals, i.e.
-how does the value of $\alpha$ and $t$ affect the shape of $b_{\alpha}^t(y)$.
-We will answer this question using two steps.
-First off, we will fix the value of $alpha$ and $t$ in Eq.~\eqref{} and then depict $b_{\alpha}^t(y)$.
-We will then explore how varying the value of $\alpha$ and $t$ in Eq.~\eqref{} affects the shape $b_{\alpha}^t(y)$.
+There is one thing, however, which remains unclear: in what way does $\alpha$ and $t$ affect the shape of the aforementioned infinitesimals, i.e.
+how does the value of $\alpha$ and $t$ affect the shape of $b_t^{\alpha}(y)$.
+We will answer this question by using two basic steps.
+First off, we will fix the value of $\alpha$ and $t$ in Eq.~\eqref{eq:ex1} and then depict $b_t^{\alpha}(y)$.
+We will then explore how varying the value of $\alpha$ and $t$ in Eq.~\eqref{eq:ex1} affects the shape $b_t^{\alpha}(y)$.\\
 
@@
 
+\noindent
 If we set the value of $\alpha$ to $\sfrac{4}{5}$ and the value of $t$ to 10 in Eq.~\eqref{eq:ex1} we obtain:
@@
 Let $R_{10}^{\sfrac{4}{5}}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{10}^{\sfrac{4}{5}}(y)$.
-The region $R_{10}^{\sfrac{4}{5}}$ is depicted and labelled in the right-most panel of Figure.~\ref{??}.
+The region $R_{10}^{\sfrac{4}{5}}$ is depicted in the right-most panel of Fig.~\ref{fig:geo1}.
+It is the largest of all the
+regions that are depicted in the right-most panel of Fig.~\ref{fig:geo1}.
 Moreover, let $A_{10}^{\sfrac{4}{5}}$ denote the area of $R_{10}^{\sfrac{4}{5}}$.
-For the sake of completeness, lets first verify whether we can emplloy the Cavalieri integral in Eq.~\ref{eq:ex1_specific} to compute $A_{10}^{\sfrac{4}{5}}$ from first principles.
+For the sake of completeness, lets first verify that we can employ the Cavalieri integral in Eq.~\ref{eq:ex1_specific} to compute $A_{10}^{\sfrac{4}{5}}$ from first principles.
 We can approximate the area of $R_{10}^{\sfrac{4}{5}}$ by summing together the area of $n$ equal width non-rectangular integration strips that inscribe $R_{10}^{\sfrac{4}{5}}$, i.e. we can 
-construct a so called Cavalieri sum. Furthermore, the sides of the non-rectangular integration strips we use in this approximation have to be translations of $b_{10}^{\sfrac{4}{5}}(y)$.
-If we take the limit of the aforementioned sum as $n\rightarrow \infty$ we obtain $A_{10}^{\sfrac{4}{5}}$, i.e.
+construct a Cavalieri sum (see Eq.~\eqref{eq:cav_sum}). Note, the sides of the non-rectangular integration strips we use in this approximation have to be translations of $b_{10}^{\sfrac{4}{5}}(y)$.
+If we take the limit of the aforementioned sum as $n\rightarrow \infty$ we approach $A_{10}^{\sfrac{4}{5}}$, i.e.
 the result obtained via the aforementioned limit is the Cavalieri integral found in Eq.~\eqref{eq:ex1_specific}.
-In conclusion, we can think of Eq.~\eqref{} as implying that the region $R_{10}^{\sfrac{4}{5}}$ is made up
+In conclusion, we can think of Eq.~\eqref{eq:ex1_specific} as implying that the region $R_{10}^{\sfrac{4}{5}}$ is made up
 of an infinite number of non-rectangular infinitesimals; all of them being translations of $b_{10}^{\sfrac{4}{5}}(y)$.
-Note, the rightmost curve depicted in the rightmost panel of Fig...
-is $b_{10}^{\sfrac{4}{5}}(y)$.
-Moreover, the special case in which we approximate $A_{10}^{\sfrac{4}{5}}$ using five equal width non-rectangular integration strips is depicted in the right-most panel of Figure~\ref{??}.
-The sides of the aforementioned five integration strips are depicted in Fig.~\ref{??} using dashed lines. Let $\mathsf{B}_{10}^{\sfrac{4}{5}}$ denote the set containing these dashed curves.
+Note, the right-most curve depicted in the right-most panel of Fig.~\ref{fig:geo1} is $b_{10}^{\sfrac{4}{5}}(y)$.
+Moreover, the special case in which we approximate $A_{10}^{\sfrac{4}{5}}$ using five equal width non-rectangular integration strips is depicted in the right-most panel of Fig.~\ref{fig:geo1}.
+The sides of the aforementioned five integration strips are depicted in Fig.~\ref{fig:geo1} using dashed lines.\\
 
+%Let $\mathsf{B}_{10}^{\sfrac{4}{5}}$ denote the set containing these dashed curves.
 %We can, therefore, interpet Eq.~\eqref{}  The region $R_{10}^{\sfrac{4}{5}}$ is, therefore, made up 
@@
 
+\noindent
 Varying both $\alpha$ and $t$ results in Eq.~\eqref{eq:ex1}. In contrast with Eq.~\eqref{eq:ex1_specific}, Eq.~\eqref{eq:ex1} can be associated with more than one region. 
 Let $R_{t}^{\alpha}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{t}^{\alpha}(y)$.
-Moreover, let $A_{t}^{\alpha}$ denote the area of $R_{t}^{\alpha}$ and let $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}=\{R_t^{\alpha}|t\in\mathsf{T},~\alpha\in\mathsf{A}\}$.
-The regions in the set $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}$ are depicted in Fig.~\textbf{??}.
-The regions that are depicted in each of the panels of Fig.~\ref{??} were generated by varying $t$, whilst keeping the value of $\alpha$ fixed.
+Moreover, let $A_{t}^{\alpha}$ denote the area of $R_{t}^{\alpha}$ and let $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}=\{R_t^{\alpha}|t\in\mathsf{T},~\alpha\in\mathsf{A}\}$  with $\mathsf{T}=\{2,4,6,8,10\}$.
+The regions in the set $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}$ are depicted in Fig.~\ref{fig:geo1}.
+The regions that are depicted in each of the panels of Fig.~\ref{fig:geo1} were generated by varying $t$, whilst keeping the value of $\alpha$ fixed.
 The title of each panel indicate which $\alpha$-value was used to generate the regions depicted in each panel. The only difference between the regions located in each 
 panel is their right edges. The right edges of the regions in each panel are depicted using varying shades of gray. The lighter the shade with which an edge is depicted, 
-the larger the $t$-value is, that is assoiciated with it.
+the larger the $t$-value is, that is associated with it.\\
 
-As was the case for $R_{10}^{\sfrac{4}{5}}$, each of the regions depicted in Fig.~\ref{} are made up of an infinite number of infinitesimals.
+\noindent
+As was the case for $R_{10}^{\sfrac{4}{5}}$, each of the regions depicted in Fig.~\ref{fig:geo1} are made up of an infinite number of infinitesimals.
 The infinitesimals that make up a specific region are translations of that region's right edge.
-The following observations can be made by inspecting Fig.\ref{??}: 
+The following observations can be made by inspecting Fig.~\ref{fig:geo1}: 
 \begin{description}
@@
 \centering
-\includegraphics[width=1\textwidth]{geo_int1.pdf}
-\caption{A plot of $\Gamma(x)$. $\Gamma(x)$ is not defined for the non-negative integers.}
-\label{fig:geo1}
-\end{figure}
-
-\begin{figure}[htb]
-\centering
 \includegraphics[width=1\textwidth]{geo_int2.pdf}

### 2019-05-22 fractional/CMJ style files/article-template.tex
almost half-way with edits

@@
 \noindent
-As was the case for $R_{10}^{\sfrac{4}{5}}$, each of the regions depicted in Fig.~\ref{fig:geo1} are made up of an infinite number of infinitesimals.
+As was the case for $R_{10}^{\sfrac{4}{5}}$, Eq.~\eqref{eq:ex1} implies that we can assume that each of the regions depicted in Fig.~\ref{fig:geo1} are made up of an infinite number of infinitesimals.
 The infinitesimals that make up a specific region are translations of that region's right edge.
@@
 We can therefore draw the following conclusion: the value of both $\alpha$ and $t$ alters the shape of the infinitesimals (i.e.
-$b_{t}^{\alpha}(y)$) that make up the regions in Fig~\ref{??}.
+the upper limit $b_{t}^{\alpha}(y)$ of Eq.~\eqref{eq:ex1} depends on $\alpha$ and $t$) that make up the regions in Fig~\ref{??}.
 Interestingly, the effect of $\alpha$ on the shape of the infinitesimals that make up the regions depicted in Fig~\ref{??} is larger than the effect that $t$ has on their shape.

### 2019-05-23 fractional/CMJ style files/article-template.tex
seeing the light in the tunnel

--- 2019-05-22 fractional/CMJ style files/article-template.tex
@@
 
-\begin{table}[h!]
-\centering
- \begin{tabular}{|c || c | c|} 
- \hline
- & \multicolumn{2}{|c|}{$a_{10}^{\alpha}(\tau)$}\\
- \hline
- &$f(\tau) = \tau$ & $f(\tau)=\sqrt{\tau}$ \\ [0.5ex] 
- \hline\hline
- $0$ & 0 & $y=0$ \\ 
- $0.2$ & $y-[\Gamma\left (\frac{6}{5} \right )]^{-1}\left(\sqrt[5]{10}-\sqrt[5]{10-y}\right)$ & $y^2-[\Gamma\left (\frac{6}{5} \right )]^{-1}\left(\sqrt[5]{10}-\sqrt[5]{10-y^2}\right)$  \\
- $0.4$ & $y-[\Gamma\left (\frac{7}{5} \right )]^{-1}\left(\sqrt[5]{10^2}-\sqrt[5]{(10-y)^2}\right)$ & $y^2-[\Gamma\left (\frac{7}{5} \right )]^{-1}\left(\sqrt[5]{10^2}-\sqrt[5]{(10-y^2)^2}\right)$ \\
- $0.6$ & $y-[\Gamma\left (\frac{8}{5} \right )]^{-1}\left(\sqrt[5]{10^3}-\sqrt[5]{(10-y)^3}\right)$ & $y^2-[\Gamma\left (\frac{8}{5} \right )]^{-1}\left(\sqrt[5]{10^3}-\sqrt[5]{(10-y^2)^3}\right)$ \\
- $0.8$ & $y-[\Gamma\left (\frac{9}{5} \right )]^{-1}\left(\sqrt[5]{10^4}-\sqrt[5]{(10-y)^4}\right)$ & $y^2-[\Gamma\left (\frac{9}{5} \right )]^{-1}\left(\sqrt[5]{10^4}-\sqrt[5]{(10-y^2)^4}\right)$ \\ [1ex]
- $1$ & $\tau$ & $\tau$ \\ [1ex] 
- \hline
- \end{tabular}
-\end{table}
+% \begin{table}[h!]
+% \centering
+%  \begin{tabular}{|c || c | c|} 
+%  \hline
+%  & \multicolumn{2}{|c|}{$a_{10}^{\alpha}(\tau)$}\\
+%  \hline
+%  &$f(\tau) = \tau$ & $f(\tau)=\sqrt{\tau}$ \\ [0.5ex] 
+%  \hline\hline
+%  $0$ & 0 & $y=0$ \\ 
+%  $0.2$ & $y-[\Gamma\left (\frac{6}{5} \right )]^{-1}\left(\sqrt[5]{10}-\sqrt[5]{10-y}\right)$ & $y^2-[\Gamma\left (\frac{6}{5} \right )]^{-1}\left(\sqrt[5]{10}-\sqrt[5]{10-y^2}\right)$  \\
+%  $0.4$ & $y-[\Gamma\left (\frac{7}{5} \right )]^{-1}\left(\sqrt[5]{10^2}-\sqrt[5]{(10-y)^2}\right)$ & $y^2-[\Gamma\left (\frac{7}{5} \right )]^{-1}\left(\sqrt[5]{10^2}-\sqrt[5]{(10-y^2)^2}\right)$ \\
+%  $0.6$ & $y-[\Gamma\left (\frac{8}{5} \right )]^{-1}\left(\sqrt[5]{10^3}-\sqrt[5]{(10-y)^3}\right)$ & $y^2-[\Gamma\left (\frac{8}{5} \right )]^{-1}\left(\sqrt[5]{10^3}-\sqrt[5]{(10-y^2)^3}\right)$ \\
+%  $0.8$ & $y-[\Gamma\left (\frac{9}{5} \right )]^{-1}\left(\sqrt[5]{10^4}-\sqrt[5]{(10-y)^4}\right)$ & $y^2-[\Gamma\left (\frac{9}{5} \right )]^{-1}\left(\sqrt[5]{10^4}-\sqrt[5]{(10-y^2)^4}\right)$ \\ [1ex]
+%  $1$ & $\tau$ & $\tau$ \\ [1ex] 
+%  \hline
+%  \end{tabular}
+% \end{table}
 
@@
 % \end{table}
-
-\begin{table}[h!]
-\centering
- \begin{tabular}{||c|| c| c||} 
- \hline
- $\alpha$ & $\frac{1}{\Gamma(\alpha)}\int_0^t \tau(t-\tau)^{\alpha-1}~d\tau$ & $\frac{1}{\Gamma(\alpha)}\int_0^t \sqrt{\tau}(t-\tau)^{\alpha-1}~d\tau$ \\[0.5ex]
- \hline\hline
- \rule{0pt}{2.5ex}
- $0$ & $t$ & $\sqrt{t}$  \\  
- \rule{0pt}{2.5ex}
- $0.2$ & $\frac{25}{6\Gamma(\frac{1}{5})} t^{\frac{6}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{17}{10})} t^{\frac{7}{10}}$  \\ 
- \rule{0pt}{2.5ex}
- $0.4$ & $\frac{25}{14\Gamma(\frac{2}{5})} t^{\frac{7}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{19}{10})} t^{\frac{9}{10}}$  \\
- \rule{0pt}{2.5ex}
- $0.6$ & $\frac{25}{24\Gamma(\frac{3}{5})} t^{\frac{8}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{21}{10})} t^{\frac{11}{10}}$  \\ 
- \rule{0pt}{2.5ex}
- $0.8$ & $\frac{25}{36\Gamma(\frac{4}{5})} t^{\frac{9}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{23}{10})} t^{\frac{13}{10}}$  \\ 
- \rule{0pt}{2.5ex}
- $1$ & $\frac{1}{2}t^2$  & $\frac{2}{3}t^{\frac{3}{2}}$  \\ [1ex]
- \hline
- \end{tabular}
-\end{table}
 
@@
 Moreover, the special case in which we approximate $A_{10}^{\sfrac{4}{5}}$ using five equal width non-rectangular integration strips is depicted in the right-most panel of Fig.~\ref{fig:geo1}.
-The sides of the aforementioned five integration strips are depicted in Fig.~\ref{fig:geo1} using dashed lines.\\
+The sides of the aforementioned five integration strips are depicted in Fig.~\ref{fig:geo1} using dashed lines.
+Let, $\mathcal{B}_{\mathsf{T}}^{\sfrac{4}{5}}=\{b_{10}^{\frac{4}{5}}(y)-c|c\in(\mathsf{T}-2)\}$ with $\mathsf{T}=\{2,4,6,8,10\}$.\\
 
@@
 Varying both $\alpha$ and $t$ results in Eq.~\eqref{eq:ex1}. In contrast with Eq.~\eqref{eq:ex1_specific}, Eq.~\eqref{eq:ex1} can be associated with more than one region. 
-Let $R_{t}^{\alpha}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{t}^{\alpha}(y)$.
-Moreover, let $A_{t}^{\alpha}$ denote the area of $R_{t}^{\alpha}$ and let $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}=\{R_t^{\alpha}|t\in\mathsf{T},~\alpha\in\mathsf{A}\}$  with $\mathsf{T}=\{2,4,6,8,10\}$.
+Let $R_{t}^{\alpha}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{t}^{\alpha}(y)$. Note that $b_{t}^{\alpha}(y)$ forms the 
+right-most edge of $R_{t}^{\alpha}$.
+Moreover, let $A_{t}^{\alpha}$ denote the area of $R_{t}^{\alpha}$ and let $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}=\{R_t^{\alpha}|t\in\mathsf{T},~\alpha\in\mathsf{A}\}$ and
+$\mathsf{B}_{\mathsf{T}}^{\mathsf{A}}=\{b_t^{\alpha}(y)|t\in\mathsf{T},~\alpha\in\mathsf{A}\}$. 
 The regions in the set $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}$ are depicted in Fig.~\ref{fig:geo1}.
@@
 \noindent
-As was the case for $R_{10}^{\sfrac{4}{5}}$, each of the regions depicted in Fig.~\ref{fig:geo1} are made up of an infinite number of infinitesimals.
+As was the case for Eq.~\eqref{eq:ex1_specific} and $R_{10}^{\sfrac{4}{5}}$, Eq.~\eqref{eq:ex1} implies that we can assume that each of the regions depicted in Fig.~\ref{fig:geo1} are made up of an infinite number of infinitesimals.
 The infinitesimals that make up a specific region are translations of that region's right edge.
@@
 \begin{description}
- \item[Effect of $\alpha$] the grey-tinted solid curves depicted in the different panels of Fig.~\ref{} are not equal to one-another.
- \item[Effect of $t$] the grey-tinted solid curves depicted in each of the panels of Fig.~\ref{} are not translations of one-another.
-Moreover, the dashed grey curves and the solid grey-tinted curves in the right-most panel are not equal to one-another.
+ \item[Effect of $\alpha$] the grey-tinted solid curves depicted in the different panels of Fig.~\ref{fig:geo1} are not equal to one-another, i.e.
+$\mathsf{B}_{\mathsf{T}}^{\alpha_1}\neq\mathsf{B}_{\mathsf{T}}^{\alpha_2}$.
+ \item[Effect of $t$] the grey-tinted solid curves depicted in each of the panels of Fig.~\ref{fig:geo1} are not translations of one-another.
+Moreover, the dashed grey curves and the solid grey-tinted curves in the right-most panel are not equal to one-another, i.e.
+$\mathsf{B}_{\mathsf{T}}^{\sfrac{4}{5}}\neq\mathcal{B}_{\mathsf{T}}^{\sfrac{4}{5}}$.
 \end{description}
 We can therefore draw the following conclusion: the value of both $\alpha$ and $t$ alters the shape of the infinitesimals (i.e.
-$b_{t}^{\alpha}(y)$) that make up the regions in Fig~\ref{??}.
-Interestingly, the effect of $\alpha$ on the shape of the infinitesimals that make up the regions depicted in Fig~\ref{??} is larger than the effect that $t$ has on their shape.
+the upper limit $b_{t}^{\alpha}(y)$ of Eq.~\eqref{eq:ex1} depends on $\alpha$ and $t$) that make up the regions in Fig.~\ref{fig:geo1}.
+Interestingly, the effect of $\alpha$ on the shape of the infinitesimals that make up the regions depicted in Fig.~\ref{fig:geo1} is larger than the effect that $t$ has on their shape.
 The curves associated with the infinitesimals obtained by varying $t$, whilst keeping the value of $\alpha$ fixed are very similar in nature and there exists a high degree of correlation between them (if their
@@
 The curves associated with the infinitesimals obtained by varying $\alpha$, whilst keeping the value of $t$ fixed are quite different from one another (the aforementioned curves are not highly correlated with
-one another).
+one another).\\
 
@@
 
-If we evaluate the integral in Eq.~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ we obtain the curves in the left-most column of Table~\ref{??}. These curves are depicted in Fig~\ref{??}.
-The area of the regions depicted in Fig.~\ref{??} are also plotted in Fig.~\ref{??} using circular markers.
-As expected, the circular markers in Fig.~\ref{??} that correspond to the areas of the regions in Fig.~\ref{??}
+\begin{table}[h!]
+\centering
+\caption{Curves obtained by evaluating Eq.~\eqref{eq:ex1} and Eq.~\eqref{eq:ex2} for all $\alpha\in \mathsf{A}$ using either Eq.~\eqref{eq:rs} or Eq.~\eqref{eq:option2}.}
+\label{tab:eval}
+\begin{tabular}{||c|| c| c||} 
+ \hline
+ $\alpha$ & $\frac{1}{\Gamma(\alpha)}\int_0^t \tau(t-\tau)^{\alpha-1}~d\tau$ & $\frac{1}{\Gamma(\alpha)}\int_0^t \sqrt{\tau}(t-\tau)^{\alpha-1}~d\tau$ \\[0.5ex]
+ \hline\hline
+ \rule{0pt}{2.5ex}
+ $0$ & $t$ & $\sqrt{t}$  \\  
+ \rule{0pt}{2.5ex}
+ $0.2$ & $\frac{25}{6\Gamma(\frac{1}{5})} t^{\frac{6}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{17}{10})} t^{\frac{7}{10}}$  \\ 
+ \rule{0pt}{2.5ex}
+ $0.4$ & $\frac{25}{14\Gamma(\frac{2}{5})} t^{\frac{7}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{19}{10})} t^{\frac{9}{10}}$  \\
+ \rule{0pt}{2.5ex}
+ $0.6$ & $\frac{25}{24\Gamma(\frac{3}{5})} t^{\frac{8}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{21}{10})} t^{\frac{11}{10}}$  \\ 
+ \rule{0pt}{2.5ex}
+ $0.8$ & $\frac{25}{36\Gamma(\frac{4}{5})} t^{\frac{9}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{23}{10})} t^{\frac{13}{10}}$  \\ 
+ \rule{0pt}{2.5ex}
+ $1$ & $\frac{1}{2}t^2$  & $\frac{2}{3}t^{\frac{3}{2}}$  \\ [1ex]
+ \hline
+ \end{tabular}
+\end{table}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=1\textwidth]{func_eval1.pdf}
+\caption{Depicts the curves which are obtained by evaluating Eq.~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ using either Eq.~\eqref{eq:rs} or Eq.~\eqref{eq:option2}.}
+\label{fig:eval1}
+\end{figure}
+
+\noindent
+If we evaluate the integral in Eq.~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ (using either Eq.~\eqref{eq:rs} or Eq.~\eqref{eq:option2}) we obtain the curves in the 
+left-most column of Table~\ref{tab:eval}. These curves are depicted in Fig.~\ref{fig:eval1}.
+The area of the regions depicted in Fig.~\ref{fig:geo1} are also plotted in Fig.~\ref{fig:eval1} using circular markers.
+As expected, the circular markers in Fig.~\ref{fig:eval1} that correspond to the areas of the regions in Fig.~\ref{fig:eval1}
 associated with a particular choice of $\alpha$ (i.e.
-regions depicted in a particular panel of Fig.~\ref{??}) fall on the curve in Fig.~\ref{??}; associated with the same choice of $\alpha$.
+regions depicted in a particular panel of Fig.~\ref{fig:geo1}) fall on the curve in Fig.~\ref{fig:eval1}; associated with the same choice of $\alpha$.
 Moreover, note that we have adopted the
-same coloring scheme in Fig.~\ref{??} and Fig.~\ref{??}.
-Using the same coloring scheme in both figures makes it clear which of the area values in Fig.~\ref{??} can be associated with which regions in Fig.~\ref{??}.
-To summarize, Fig.~\ref{??}, therefore, depicts a non-static non-rectangular sum-based geometric interpretation of Eq.~\eqref{}. Moreover, Fig.~\ref{??} corroborates this 
-geometric interpretation.
+same coloring scheme in Fig.~\ref{fig:geo1} and Fig.~\ref{fig:eval1}.
+Using the same coloring scheme in both figures makes it clear which of the area values in Fig.~\ref{fig:eval1} can be associated with which regions in Fig.~\ref{fig:geo1}.
+To summarize, Fig.~\ref{fig:geo1}, therefore, depicts a non-static non-rectangular sum-based geometric interpretation of Eq.~\eqref{eq:ex1}. Moreover, Fig.~\ref{fig:eval1} corroborates this 
+geometric interpretation.\\
 
+\noindent
 Let us know consider a different fractional integral:
 \begin{equation}
+\label{eq:ex2}
 \frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \frac{1}{\Gamma(\alpha)}\int_0^t \sqrt{\tau}(t-\tau)^{\alpha-1}~d\tau. 
 \end{equation}
-If we evaluate the integral in Eq.~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ we obtain the curves in the right-most column of Table~\ref{??}. These curves are depicted in Fig~\ref{??}.
-The non-static non-rectangular sum-based geometric interpretation associated with Eq.~\eqref{eq:ex1} is depicted in Fig. The validity of this interpretation is corroborated by Fig.
+The non-static non-rectangular sum-based geometric interpretation associated with Eq.~\eqref{eq:ex1} is depicted in Fig.~\ref{fig:geo2}. 
+If we evaluate the integral in Eq.~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ we obtain the curves in the right-most column of Table~\ref{tab:eval}. 
+These curves are depicted in Fig~\ref{fig:eval2}.
+The validity of the non-static non-rectangular sum-based geometric interpretation depicted in Fig.~\ref{fig:geo2} is corroborated by Fig.~\ref{fig:eval2}.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=1\textwidth]{geo_int2.pdf}
+\caption{The non-static non-rectangular sum-based geometric interpretation of Eq.~\eqref{eq:ex2}.}
+\label{fig:geo2}
+\end{figure}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=1\textwidth]{func_eval2.pdf}
+\caption{Depicts the curves which are obtained by evaluating Eq.~\eqref{eq:ex2} for all $\alpha\in \mathsf{A}$ using either Eq.~\eqref{eq:rs} or Eq.~\eqref{eq:option2}.}
+\label{fig:eval2}
+\end{figure}
 
@@
 
-The circular markers in Figure ?? is depicted using the same tint-of-gray with which the right edge of the region  in question is depicted in Fig.
-
-Each of the curves 
-in Fig can therefore be associated with one of the panels in Fig. The area associated with the regions depicted in each of the panels in Fig. are plotted on the curves 
-in 
-associated with a particular panel appropriate 
-curves 
-in Fig using circular markers. The circular marker is depicted in Figure using the same tint-of-gray with which the 
-right edge of the region in question is depicted in Fig.
-
-it is $\alpha$  
-Although $\alpha$ and $t$ alters the shape of the infinitesimals which make up the regions depicted in Fig.,
-
-that make up the regions in Fig are confirmed by the following observation: $\mathsf{B}_T^{\alpha}\neq\mathcal{B}_T^{\alpha}$.
-We can visually verify that this observation is in fact true for $alpha=\frac{4}{5}$ by inspecting the right-most panel in Fig.~\ref{??}.
+% The circular markers in Figure ?? is depicted using the same tint-of-gray with which the right edge of the region  in question is depicted in Fig.
+% 
+% Each of the curves 
+% in Fig can therefore be associated with one of the panels in Fig. The area associated with the regions depicted in each of the panels in Fig. are plotted on the curves 
+% in 
+% associated with a particular panel appropriate 
+% curves 
+% in Fig using circular markers. The circular marker is depicted in Figure using the same tint-of-gray with which the 
+% right edge of the region in question is depicted in Fig.  
+% 
+% it is $\alpha$  
+% Although $\alpha$ and $t$ alters the shape of the infinitesimals which make up the regions depicted in Fig.,  
+% 
+% that make up the regions in Fig are confirmed by the following observation: $\mathsf{B}_T^{\alpha}\neq\mathcal{B}_T^{\alpha}$.
+% We can visually verify that this observation is in fact true for $alpha=\frac{4}{5}$ by inspecting the right-most panel in Fig.~\ref{??}.
 The dashed curves and the grey tinted curves in this panel do not allign.
-
-the upper limit 
-of the Cavalieri integral in Eq. As the upper limit of the Cavalieri integral depends on
-
-As the shape of the infinitesimals which make up the regions depicted in Fig depend of the integration limit of the 
-Cavalieri integral or stated differently on the value of $t$ and $\alpha$.
-
-If we set the value of $\alpha$ to $\frac{4}{5}$, but we do not fix the value of $t$ then Eq.~\eqref{eq:ex1} reduces to:
-\begin{equation}
-\int_{a_{t}^{\frac{4}{5}}(y)}^{b_{t}^{\frac{4}{5}}(y)} f(\tau)~d\tau 
-\end{equation}
-If we evaluate the above integral we obtain the area of the region $R_{t}^{\frac{4}{5}}$.
+% 
+% 
+% 
+% the upper limit 
+% of the Cavalieri integral in Eq. As the upper limit of the Cavalieri integral depends on
+% 
+% As the shape of the infinitesimals which make up the regions depicted in Fig depend of the integration limit of the 
+% Cavalieri integral or stated differently on the value of $t$ and $\alpha$.  
+% 
+% If we set the value of $\alpha$ to $\frac{4}{5}$, but we do not fix the value of $t$ then Eq.~\eqref{eq:ex1} reduces to:
+% \begin{equation}
+% \int_{a_{t}^{\frac{4}{5}}(y)}^{b_{t}^{\frac{4}{5}}(y)} f(\tau)~d\tau 
+% \end{equation}
+% If we evaluate the above integral we obtain the area of the region $R_{t}^{\frac{4}{5}}$.
 The region $R_{t}^{\frac{4}{5}}$ is the region bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{t}^{\frac{4}{5}}(y)$.
-Note that the shape of $R_{t}^{\frac{4}{5}}$ depends on the value of $t$.
+% Note that the shape of $R_{t}^{\frac{4}{5}}$ depends on the value of $t$.
 The regions contained in the set $\mathsf{R}^{\frac{4}{5}}$ are depicted in the rightmost panel of Fig\textbf{??}.
 Let $\mathsf{B}^{\frac{4}{5}}$ contain the right
-edges of the regions contained in the set $\mathsf{R}^{\frac{4}{5}}$.
+% edges of the regions contained in the set $\mathsf{R}^{\frac{4}{5}}$.
 The shape of the edges in $\mathsf{B}^{\frac{4}{5}}$ depend on the value of $t$.
@@
 The shade with which the aformentioned curves are depicted becomes lighter
-as the value of $t$ increases. The two sets b and b are not equal, i.e. the shape of the infinitesimals that make up the regions contained in 
-R are dependent on $t$. Although the infinitesimals that make up the regions contained in R have different shapes their form do share common characteristics.
-
-altering $t$ alters the geometric interpretaion of 
-Eq???. The shape of the inifinitesimals that make up the region that is associated with Eq depend on the value of $t$.
-
-the shape of the integration strip one has to use to construct the infinite sum that underpins the  used to create the   .
+% as the value of $t$ increases. The two sets b and b are not equal, i.e. the shape of the infinitesimals that make up the regions contained in 
+% R are dependent on $t$. Although the infinitesimals that make up the regions contained in R have different shapes their form do share common characteristics. 
+% 
+% 
+% altering $t$ alters the geometric interpretaion of 
+% Eq???. The shape of the inifinitesimals that make up the region that is associated with Eq depend on the value of $t$. 
+% 
+% 
+% the shape of the integration strip one has to use to construct the infinite sum that underpins the  used to create the   .
 Changing the value of $t$ alters the shape of the non-rectangular integration strip which is needed
-
-limit alters the
-shape of the infinitesimal we need to use.
-
-The shade with which the aformentioned edges are depicted becomes lighter as the value of $t$ increases.
-
-The boundaries of these regions are depicted in varying shades of gray.
-
-We depict $R_{t}^{\frac{4}{5}}$ in the left most panel of Fig.~\textbf{??} for all $t\in\mathsf{T}$. The set of functions
-
-If we change the value of $t$ we change the area
-
-In general can use $n$ integration strips to approximate
-
-the area If we are to sum together the area of  non-rectangular integration strips whose sides are translations of $b_{10}^{\frac{4}{5}}(y)$ then the result our summation would tend to
-the area of $R_{10}^{\frac{4}{5}}$.
-
-Lets now choose to approximate the area of $R_{10}^{\frac{4}{5}}$ using five non-rectangualr integration strips of equal width. Mathematically speaking, this is accomplished 
-by setting $n$ to 5 in Eq??. The aformentioned integration strips are depicted in the right-most panel of Figure~\ref{??}.
-The sides of the integration strips are depicted using dashed lines. The more integration strips we consider the better our approximation of $R_{10}^{\frac{4}{5}}$ becomes.
-
-We can better approximate the area of $R_{10}^{\frac{4}{5}}$ by increasing the number of integrations strips we use .
+% 
+% 
+% limit alters the
+% shape of the infinitesimal we need to use.
+% 
+% 
+% The shade with which the aformentioned edges are depicted becomes lighter as the value of $t$ increases.
+% 
+% 
+% 
+% The boundaries of these regions are depicted in varying shades of gray.  
+% 
+% 
+% We depict $R_{t}^{\frac{4}{5}}$ in the left most panel of Fig.~\textbf{??} for all $t\in\mathsf{T}$. The set of functions   
+% 
+% 
+% If we change the value of $t$ we change the area 
+% 
+% 
+% In general can use $n$ integration strips to approximate 
+% 
+% 
+% 
+% the area If we are to sum together the area of  non-rectangular integration strips whose sides are translations of $b_{10}^{\frac{4}{5}}(y)$ then the result our summation would tend to
+% the area of $R_{10}^{\frac{4}{5}}$. 
+% 
+% 
+% Lets now choose to approximate the area of $R_{10}^{\frac{4}{5}}$ using five non-rectangualr integration strips of equal width. Mathematically speaking, this is accomplished 
+% by setting $n$ to 5 in Eq??. The aformentioned integration strips are depicted in the right-most panel of Figure~\ref{??}.
+% The sides of the integration strips are depicted using dashed lines. The more integration strips we consider the better our approximation of $R_{10}^{\frac{4}{5}}$ becomes. 
+% 
+% 
+% 
+% We can better approximate the area of $R_{10}^{\frac{4}{5}}$ by increasing the number of integrations strips we use .
 Increasing the number of integration strips we use improves our approximation of the area of $R_{10}^{\frac{4}{5}}$
-If we decide on using five integration strips
-
-that 
-we use whose sides are translations of $b_{10}^{\frac{4}{5}}(y)$
-
-Each panel of 
-Figure~\ref{??} depicts the function $f(\tau)$ and the set of curves $\mathsf{B}_T^{\alpha}$. The set $\mathsf{B}_T^{\alpha}$ is defined in Table~\ref{??} and contains 
-all the Cavalieri integral upper limits obtained by fixing the order of integration $\alpha$ to a specific value.
+% If we decide on using five integration strips 
+% 
+% 
+% that 
+% we use whose sides are translations of $b_{10}^{\frac{4}{5}}(y)$ 
+% 
+% 
+% Each panel of 
+% Figure~\ref{??} depicts the function $f(\tau)$ and the set of curves $\mathsf{B}_T^{\alpha}$. The set $\mathsf{B}_T^{\alpha}$ is defined in Table~\ref{??} and contains 
+% all the Cavalieri integral upper limits obtained by fixing the order of integration $\alpha$ to a specific value.
 In each panel, we depict the set of curves $\mathsf{B}_T^{\alpha}$ using different shades of grey.
-The shade with which $b_t^{\alpha}(y)$ is depicted becomes lighter as the value of $t$ increases.
-
-The The $y$-valued functions are depicted in different shades of gray. The $\tau$-valued fun
-
-The curve in the rightmost panel of 
-Figure~\ref{} which is depicted in the lightest shade of gray of
-
-The function $b_{10}^{\frac{4}{5}}(y)$ 
-depicted in the lightest shade of gray used within the right-most panel
-
-The right-most panel of Figure.~\ref{??} contains 
-a few $y$-valued curves, each one depicted in a different shade of gray. The curve depicted in the lightest shade of gray is
-
-In each of the panels  curves $\mathsf{B}_1^{\alpha}$
-
-convert the 
-integrals in ?? and ?? to equivalent Cavalieri integrals.
-
-We can assign a geometric interpretation to the above fractional integrals by converting them into Cavalieri integrals. This can be achieved by first 
-converting the above integrals into Riemann-Stieltjes integrals and then converting the resulting integrals into Cavalieri integrals. Exaclty how these conversion are 
-to be performed is discussed in the previous section.
+% The shade with which $b_t^{\alpha}(y)$ is depicted becomes lighter as the value of $t$ increases.
+% 
+% 
+% The The $y$-valued functions are depicted in different shades of gray. The $\tau$-valued fun 
+% 
+% The curve in the rightmost panel of 
+% Figure~\ref{} which is depicted in the lightest shade of gray of 
+% 
+% The function $b_{10}^{\frac{4}{5}}(y)$ 
+% depicted in the lightest shade of gray used within the right-most panel
+% 
+% 
+% The right-most panel of Figure.~\ref{??} contains 
+% a few $y$-valued curves, each one depicted in a different shade of gray. The curve depicted in the lightest shade of gray is  
+% 
+% 
+% In each of the panels  curves $\mathsf{B}_1^{\alpha}$
+% 
+% convert the 
+% integrals in ?? and ?? to equivalent Cavalieri integrals.
+% 
+% 
+% We can assign a geometric interpretation to the above fractional integrals by converting them into Cavalieri integrals. This can be achieved by first 
+% converting the above integrals into Riemann-Stieltjes integrals and then converting the resulting integrals into Cavalieri integrals. Exaclty how these conversion are 
+% to be performed is discussed in the previous section.
 The inegrator $g_t^{\alpha}(\tau)$ of the aforementioned intermediate Riemann-Stieltjes integrals are equal and independent of the integrand $f(\tau)$.
-The set of functions $\{g_{10}^{\alpha}(\tau)|\alpha\in\{0,0.2,\cdots,0.8,1\}\}$ are presented in Table \textbf{??} and depicted in Figure\textbf{??}.
+% The set of functions $\{g_{10}^{\alpha}(\tau)|\alpha\in\{0,0.2,\cdots,0.8,1\}\}$ are presented in Table \textbf{??} and depicted in Figure\textbf{??}.
 The integration limits of the aformentioned Cavalieri
-integrals are functions and are determined by the integrand $f(\tau)$ and the integrator $g_t^{\alpha}(\tau)$.
+% integrals are functions and are determined by the integrand $f(\tau)$ and the integrator $g_t^{\alpha}(\tau)$.
 The set of functions $\{a_{10}^{\alpha}(y)|\alpha\in\{0,0.2,\cdots,0.8,1\}\}$ that can be
-associated with the integrals in Eq~{??} and Eq~{??} are presented in Table~\textbf{??}. Note that neither $g_t^{\alpha}(\tau)$ nor $a_t^{\alpha}(y)$ are static functions, 
-they depend on the value of $\alpha$ and $t$.
+% associated with the integrals in Eq~{??} and Eq~{??} are presented in Table~\textbf{??}. Note that neither $g_t^{\alpha}(\tau)$ nor $a_t^{\alpha}(y)$ are static functions, 
+% they depend on the value of $\alpha$ and $t$.
 This implies that a fractional integral of order $\alpha$ and extent $t$ can be interpeted as an infitesimal sum of an infinite number of infinitesimals whose
-shape is determined by $\alpha$ and $t$.
-
-Lets clarify the above by working through a detailed example. Lets set the value of $\alpha$ to $\frac{4}{5}$ and the value of $t$ to 10 and then convert the 
-integrals in ?? and ?? to equivalent Cavalieri integrals. If we evaluate these Cavalieri integrals we obtain the area of two regions $A$ and $B$. Both $A$ and $B$ are bounded by the $x$-axis, 
-$f(x)$ and $b_{10}^{\frac{4}{5}}(y)$. Region $A$ and $B$ are respectively depicted in the rightmost panel of Fig ?? and Fig ??. The area of $A$ and $B$ can be approximated
-by summing together the area of non-rectangular integration strips that inscribes $A$ and $B$. The case in which we use five integration strips is depicted in 
-Fig ?? and Fig ??. The analytic expressions of the right sides of these integration strips are elements of the set $\mathsf{A} = \{b_{10}^{\frac{4}{5}}(y) - c|c\in\{0,2,4,6,8\}\}$. The 
-curves are plotted using dashed lines.
-
-The curves $\mathsf{B} = \{b_{t}^{\frac{4}{5}}(y)|t\in\{2,4,6,8,10\}\}$ are plotted in different shades of grey.
+% shape is determined by $\alpha$ and $t$.
+% 
+% Lets clarify the above by working through a detailed example. Lets set the value of $\alpha$ to $\frac{4}{5}$ and the value of $t$ to 10 and then convert the 
+% integrals in ?? and ?? to equivalent Cavalieri integrals. If we evaluate these Cavalieri integrals we obtain the area of two regions $A$ and $B$. Both $A$ and $B$ are bounded by the $x$-axis, 
+% $f(x)$ and $b_{10}^{\frac{4}{5}}(y)$. Region $A$ and $B$ are respectively depicted in the rightmost panel of Fig ?? and Fig ??. The area of $A$ and $B$ can be approximated
+% by summing together the area of non-rectangular integration strips that inscribes $A$ and $B$. The case in which we use five integration strips is depicted in 
+% Fig ?? and Fig ??. The analytic expressions of the right sides of these integration strips are elements of the set $\mathsf{A} = \{b_{10}^{\frac{4}{5}}(y) - c|c\in\{0,2,4,6,8\}\}$. The 
+% curves are plotted using dashed lines. 
+% 
+% The curves $\mathsf{B} = \{b_{t}^{\frac{4}{5}}(y)|t\in\{2,4,6,8,10\}\}$ are plotted in different shades of grey.
 The shade with which $b_t^{\alpha}(y)$ is depicted becomes lighter as the value of $t$ increases.
 Note
-that $\mathsf{A}\neq \mathsf{B}$. The sides of the integration strips
-
-is the lighter the curve associated with $b_t^{\alpha}(y)$ is.
-
-We depict We depict $b_10^{\alpha}(y)$ with the lightest
-shade of
-depicted in the right most   depict the region associated that is associated with the Cavalieri integral which is obtained
-
-the obtained Lets depict the geometric interpretation
+% that $\mathsf{A}\neq \mathsf{B}$. The sides of the integration strips 
+% 
+% 
+% is the lighter the curve associated with $b_t^{\alpha}(y)$ is.
+% 
+% We depict We depict $b_10^{\alpha}(y)$ with the lightest
+% shade of
+% depicted in the right most   depict the region associated that is associated with the Cavalieri integral which is obtained 
+% 
+% 
+% the obtained Lets depict the geometric interpretation
 
@@
 
-\begin{enumerate}
- \item Examples.
- \item If we evaluate \textbf{[is this word correct?]} these integrals we obtaine the functions in Table \textbf{??}. These functions are plotted in Fig xx.
- \item Assign a geometric interpretation by converting to a Riemann-Stieltjes integral and then to a Cavalieri integral.
- \item \textbf{[Is there a need to mention the fact that it is mapped to a set of different Cavalieri integrals]}. Note that we obtain a different 
- Cavalieri integral for each value of alpha and t.
- \item Let us fix alpha and t to specific values, ie write down the integrals. The function b the left most function in the leftmost panel (plotted in the lightest 
- shade of gray of all the y-valued functions. The integral , and by implication , can be inerpreted as the are of the region formed by f, b and the x-axis. This 
- area can be obtained by summing together an infinite number of infinitesimals whose shape is determined by b. This are can be approximated by using integration strips. These 
- strips is depicted using dashed lines. The area of this region and $t$ forms a specific point on the curves in Fig. The point is plotted in the same shade of gray than b.
- \item If we take another value of t we obtain a different region. Note that b and b are not mere translations of each other. Changing the integration limit alters the 
- shape of the infinitesimal we need to use.
+% \begin{enumerate}
+%  \item Examples.
+%  \item If we evaluate \textbf{[is this word correct?]} these integrals we obtaine the functions in Table \textbf{??}. These functions are plotted in Fig xx.
+%  \item Assign a geometric interpretation by converting to a Riemann-Stieltjes integral and then to a Cavalieri integral.
+%  \item \textbf{[Is there a need to mention the fact that it is mapped to a set of different Cavalieri integrals]}. Note that we obtain a different 
+%  Cavalieri integral for each value of alpha and t.
+%  \item Let us fix alpha and t to specific values, ie write down the integrals. The function b the left most function in the leftmost panel (plotted in the lightest 
+%  shade of gray of all the y-valued functions. The integral , and by implication , can be inerpreted as the are of the region formed by f, b and the x-axis. This 
+%  area can be obtained by summing together an infinite number of infinitesimals whose shape is determined by b. This are can be approximated by using integration strips. These 
+%  strips is depicted using dashed lines. The area of this region and $t$ forms a specific point on the curves in Fig. The point is plotted in the same shade of gray than b.
+%  \item If we take another value of t we obtain a different region. Note that b and b are not mere translations of each other. Changing the integration limit alters the 
+%  shape of the infinitesimal we need to use.
 Althoug both t and alpa alters the shape of b, it is only alpha that fundamentally changes ....
 \textbf{[how to state this shape altering thing i do not know]}
- \item Need to finish the discussion of al the points mapping to the other figures. 
- \item Summary of overall interpretation of fractional integral.....
-\end{enumerate}
+%  \item Need to finish the discussion of al the points mapping to the other figures. 
+%  \item Summary of overall interpretation of fractional integral.....
+% \end{enumerate}
 
-\begin{figure}[htb]
-\centering
-\includegraphics[width=1\textwidth]{geo_int2.pdf}
-\caption{A plot of $\Gamma(x)$. $\Gamma(x)$ is not defined for the non-negative integers.}
-\label{fig:geo2}
-\end{figure}
-
-These steps 
-were discussed in more detail in the previous section.
-
-The steps to visualize the above two integrals were described in the previous paragraph. We first convert the integrals into Riemann-Stieltjes integrals. The 
-Riemann-Stieltjes integrals are then converted to Cavalieri integrals. We can then simply depict the Cavalieri integrals and in doing so obtain a geometric interpretaion
-of the original fractional integrals. Importantly, for each value of $t$ we obtain a different
+% These steps 
+% were discussed in more detail in the previous section. 
+% 
+% The steps to visualize the above two integrals were described in the previous paragraph. We first convert the integrals into Riemann-Stieltjes integrals. The 
+% Riemann-Stieltjes integrals are then converted to Cavalieri integrals. We can then simply depict the Cavalieri integrals and in doing so obtain a geometric interpretaion
+% of the original fractional integrals. Importantly, for each value of $t$ we obtain a different
 

### 2019-05-27 fractional/CMJ style files/article-template.tex
started adding literature review

@@
 \usepackage{xfrac}
+\usepackage{textcomp}
 
@@
 A natural question which arises when one inspects this notation is: Can $n$ be a non-integer value? L'Hospital phrased it differently: ``\emph{What if $n$ be a $\frac{1}{2}$?}''. 
-In a letter Leibniz sent to L'Hospital, he himself commented on this intriguing question: ``\emph{This is an apparant paradox from which, one day, useful 
-consequences will be drawn}.''
+In a letter Leibniz sent to L'Hospital, Leibniz comments on L'Hospital's question with the following remark: ``\emph{This is an apparant paradox from which, one day, useful 
+consequences will be drawn}'' \cite{ross77,machado14}.\\
 
-The mathematical discipline in which we study the extension of derivatives and integrals to non-integer orders is known as fractional calculus. Liouville and Riemann laid most 
-of theoretical groundwork which was needed to develop the field of fractional calculus. Fractional calculus has now developed into a mature discipline. 
+\noindent
+The mathematical discipline in which we study the extension of derivatives and integrals to non-integer orders is known as fractional calculus. Euler, Liouville and Riemann laid most 
+of theoretical groundwork which was needed to develop the field of fractional calculus \cite{davis59,liouville1832,riemann1876}.
+Fractional calculus has now developed into a mature discipline \cite{machado14}.
 However, there is one aspect of the discipline which only started to develop fairly recently: its physical and geometric interpretability.
 At the first international conference on fractional calculus in
-New Haven (USA) (which took place in 1974) it was pointed out that literature lacked an acceptable geometric and physical interpretation of fractional calculus.
+New Haven (USA) (which took place in 1974) it was pointed out that literature lacked an acceptable geometric and physical interpretation of fractional calculus \cite{ross06}.
 Subsequently, the last few decades has seen
@@
 \begin{thebibliography}{1}
+
+\bibitem{ross77} Ross,~B. (1977). The development of fractional calculus 1695--1900. \textit{Hist. Math.} 4(1): 75--89.
+
+\bibitem{liouville1832} Liouville,~J.
+(1832).
+M\'{e}moire sur l\textquotesingle integration de l\textquotesingle \'{e}quation $(mx^2+nx+p)\frac{d^2y}{dx^2}+(qx+r)\frac{dy}{dx}+sy$ \`{a} l\textquotesingle aide des diff\'{e}rentielles \`{a} indices
+que\textquotesingle conques. \textit{Journal d l\textquotesingle Ecole Polytechnique.} 13(21): 163--186.
+
+\bibitem{riemann1876} Riemann,~B.~G.~F (1876). Gesammelte Werke.
+
+\bibitem{davis59} Davis,~P.~J. (1959). "Leonhard Euler's Integral: A Historical Profile of the Gamma Function". \textit{Amer. Math. Monthly}. 66(10): 849--869
+
+\bibitem{machado14} Machado,~J.~T., Galhano,~A.~M., Trujillo,~J.~J. (2014). On development of fractional calculus during the last fifty years. \textit{Scientometrics}. 98(1): 577-582.
+
+\bibitem{ross06} Ross,~B.
+(Ed.).
+(2006).
+\textit{Fractional calculus and its applications: proceedings of the international conference held at the University of New Haven, June 1974}, Vol.
+457, Springer.
+
 \bibitem{parker13} Adam Parker, Who solved the Bernoulli equation and how did they do it? \textit{Coll. Math. J.} \textbf{44} (2013) 89--97.

### 2019-05-27 fractional/CMJ style files/article-template.tex
added lit

@@
 The mathematical discipline in which we study the extension of derivatives and integrals to non-integer orders is known as fractional calculus. Euler, Liouville and Riemann laid most 
-of theoretical groundwork which was needed to develop the field of fractional calculus \cite{davis59,liouville1832,riemann1876}.
+of theoretical groundwork which was needed to develop the field of fractional calculus \cite{davis59,liouville1832,riemann1876,laurent1884}.
 Fractional calculus has now developed into a mature discipline \cite{machado14}.
@@
 Subsequently, the last few decades has seen
-a number of papers that attempt to rectify this. There now exists probabilistic interpretations, geometric interpretations, physical interpretations and ecenomic 
-interpretations of fractional order integrals and differentials.
+a number of papers that attempt to rectify this.
+There now exists probabilistic interpretations \cite{stanislavsky04,machado03}, geometric interpretations \cite{adda97,tarasov16,podlubny02}, physical interpretations \cite{cioc16,rutman95} and economic
+interpretations \cite{tarasova17} of fractional order integrals and differentials.\\
 
+\noindent
 In this article we specifically focus on the geometric interpretation of fractional integrals.
-To be more specific, we present a novel geometric interpretation of the Riemann-Liouville fractional integral.
+To be more specific, we present a novel geometric interpretation of the Riemann-Liouville fractional integral \cite{laurent1884}.
 As we mentioned earlier, Riemann and Liouville played an important role in the development of fractional calculus. Their work was crucial in defining what is now know as 
-the Riemann-Lioville fractional integral. At this point in time the reader should be made aware of the fact that there exists many other accepted fractional integral definitions in the literature.
+the Riemann-Liouville fractional integral \cite{laurent1884}.
+At this point in time the reader should be made aware of the fact that there exists many other accepted fractional integral definitions in the literature.
 We, however, do not discuss them any further in this article. Investigating whether one can apply the proposed framework to other fractional integral definitions will be adressed in a 
@@
 
-\bibitem{davis59} Davis,~P.~J. (1959). "Leonhard Euler's Integral: A Historical Profile of the Gamma Function". \textit{Amer. Math. Monthly}. 66(10): 849--869
+\bibitem{davis59} Davis,~P.~J. (1959). Leonhard Euler's Integral: A Historical Profile of the Gamma Function. \textit{Amer. Math. Monthly}. 66(10): 849--869
 
@@
 
+%Probability
+\bibitem{stanislavsky04} Stanislavsky,~A.~A. (2004).  Probability interpretation of the integral of fractional order, \textit{Theoretical and Mathematical Physics.} 138(3): 418--431.
+
+\bibitem{machado03} Machado,~J.~T. (2003). A probabilistic interpretation of the fractional-order differentiation. \textit{Fract. Calc. Appl. Anal.} 6(1): 73--80.
+
+\bibitem{adda97} Adda,~F.~B. (1997). Geometric interpretation of the fractional derivative. \textit{Journal of Fract. Calc.}, 11: 21--52.
+
+%Geometric
+\bibitem{tarasov16} Tarasov,~V.~E. (2016). Geometric interpretation of fractional-order derivative. \textit{Fract. Calc. Appl. Anal.} 19(5): 1200--1221.
+
+\bibitem{podlubny02} Podlubny,~I. (2002). Geometric and Physical Interpretation of Fractional Integration and Fractional Differentiation, \textit{Fract. Calc. Appl. Anal.} 5(4): 367--386.
+
+%Physical
+\bibitem{cioc16} Cioc, R.
+(2016).
+Physical and geometrical interpretation of Gr\"{u}nwald-Letnikov differintegrals: Measurement of path and acceleration.
+\textit{Fract.
+Calc.
+Appl.
+Anal.} 19(1): 161--172.
+
+\bibitem{rutman95} Rutman,~R.S. (1995). On physical interpretations of fractional integration and differentiation. \textit{Theoretical and Mathematical Physics.} 105(3):1509--1519
+
+%Economic
+\bibitem{tarasova17} Tarasova,~V.~V., Tarasov,~V.~E. (2017). Economic Interpretation of Fractional Derivatives. \textit{Progress in Fractional Differentiation and Applications.} 3(1):1--7.
+
 \bibitem{parker13} Adam Parker, Who solved the Bernoulli equation and how did they do it? \textit{Coll. Math. J.} \textbf{44} (2013) 89--97.
+
+\bibitem{laurent1884} Laurent, H. (1884). Sur le calcul des d\'{e}riv\'{e}es \`{a} indices quelconques. \textit{Nouv Annales de Mathem\'{e}matiques.} 3(3):240--252.
 

### 2019-05-27 fractional/CMJ style files/article-template.tex
newest version of article

@@
 A natural question which arises when one inspects this notation is: Can $n$ be a non-integer value? L'Hospital phrased it differently: ``\emph{What if $n$ be a $\frac{1}{2}$?}''. 
-In a letter Leibniz sent to L'Hospital, Leibniz comments on L'Hospital's question with the following remark: ``\emph{This is an apparant paradox from which, one day, useful 
+In a letter Leibniz sent to L'Hospital, Leibniz comments on L'Hospital's question by making the following prophetic remark: ``\emph{This is an apparant paradox from which, one day, useful 
 consequences will be drawn}'' \cite{ross77,machado14}.\\
@@
 At this point in time the reader should be made aware of the fact that there exists many other accepted fractional integral definitions in the literature.
-We, however, do not discuss them any further in this article. Investigating whether one can apply the proposed framework to other fractional integral definitions will be adressed in a 
-future endeavour.
-
-Moreover, the geometric interpretation we present here is especially useful from a pedigogical point of view as it is similar in nature to the definition of classical integration.
-The Riemann integral
-can be interpreted as an infinite sum of rectangular infinitesimals. In this paper, we show that the Riemann-Liouville fractional integral can be interpreted 
-as an infinite sum of non-rectangular infinitesimals whose shape is determined by the order of integration $\alpha$ and the integration limit $x$.
-
-The geometric interpretation we present in this paper is an extension of the fractional geometric framework presented by Podlubny. Podlubny showed that a fractional Riemann-Liouville 
+We, however, do not discuss them any further in this article.
+Investigating whether one can apply the proposed framework to other fractional integral definitions will be presented in future work.
+The geometric interpretation we present in this paper is an extension of the fractional geometric framework presented by Podlubny \cite{podlubny02}.
+Podlubny showed that a fractional Riemann-Liouville
 integral can be converted to a Riemann-Stieltjes integral. Furthermore, Grobler showed that a Riemann-Stieltjes integral can be interpreted as an infiniesimal sum of 
 non-rectangular infinitesimels, i.e.
-a Riemann-Stieltjes integral can be converted into a Cavalieri integral.
-If we combine these two ideas together we obtain the geometric interpretaion contained in the
-previous paragraph.
+a Riemann-Stieltjes integral can be converted into a Cavalieri integral \cite{ackermann12,?}.
+Combining these two ideas together results in the following geometric
+interpretation: the Riemann-Liouville fractional integral can be interpreted as an infinite sum of non-rectangular infinitesimals whose shape is determined by the order of integration $\alpha$ and the integration limit $t$.\\
 
+\noindent
 We specifically wrote this paper for people with a pedagogical interest, undergraduate students and for the layman who finds integration theory intriguing and 
@@
 fractional calculus they generally are quite interested in the subject. This is quite evident from perusing mathematical social media platforms and from surveying 
-articles published in undergraduate journals [].
+articles published in undergraduate journals \cite{munkhammar05}.
 One of the reasons undergraduates struggle to grasp fractional calculus, apart from it not normally being taught as part of the undergraduate curricilum, is because,
 it is such an abstract concept.
-We believe that the geometric interpretation we present in this paper will provide undergraduates with the insight that they need to quickly grasp and understand the fundamental
+We believe that the geometric interpretation we present in this paper, as it is similar in nature to the definition of classical integration, will provide undergraduates with the insight that they need to quickly grasp and understand the fundamental
 concepts that unerpin fractional calculus.
 We also hope that this paper will enable and encourage undergraduate lectures to already introduce students to this fascinating mathematical discipline as part of their
-undergraduate training.
+undergraduate training.\\
 
-We start the paper by reviewing the definition of the Riemann-Stieltjes and Cavalieri integral. We then present the definition of the Riemann-Lioville fractional integral. 
+\noindent
+We start the paper by reviewing the definition of the Riemann-Stieltjes and Cavalieri integral. We then present the definition of the Riemann-Liouville fractional integral. 
 We end the paper by presenting our novel geometric interpretation and a conclusion.
@@
 
+\bibitem{ackermann12} Ackermann,~E.~R, Grobler,~T.~L., Kleynhans,~W., Olivier,~J.~C., Salmon,~B.~P, van Zyl,~A.~J. (2012). Cavalieri
+Integration. \textit{Quaest. Math.} 35(3): 265–296.
+
 \bibitem{parker13} Adam Parker, Who solved the Bernoulli equation and how did they do it? \textit{Coll. Math. J.} \textbf{44} (2013) 89--97.
@@
 \bibitem{laurent1884} Laurent, H. (1884). Sur le calcul des d\'{e}riv\'{e}es \`{a} indices quelconques. \textit{Nouv Annales de Mathem\'{e}matiques.} 3(3):240--252.
+
+\bibitem{munkhammar05} Munkhammar, J. (2005). Fractional calculus and the Taylor-Riemann series. \textit{Rose-Hulman Undergraduate Mathematics Journal}, 6(1): 6.
 

### 2019-05-27 fractional/CMJ style files/article-template.tex
added file to x

@@
 At this point in time the reader should be made aware of the fact that there exists many other accepted fractional integral definitions in the literature.
-We, however, do not discuss them any further in this article.
-Investigating whether one can apply the proposed framework to other fractional integral definitions will be presented in future work.
-The geometric interpretation we present in this paper is an extension of the fractional geometric framework presented by Podlubny \cite{podlubny02}.
-Podlubny showed that a fractional Riemann-Liouville
-integral can be converted to a Riemann-Stieltjes integral. Furthermore, Grobler showed that a Riemann-Stieltjes integral can be interpreted as an infiniesimal sum of 
-non-rectangular infinitesimels, i.e.
+We, however, deem thhese definitions to be beyond the scope of the current article and as such we do not discuss them any further in this work. The geometric interpretation 
+we present here is an extension of the geometric interpretation presented by Podlubny\cite{podlubny02}. Podlubny showed that a Riemann-Liouville fractional integral 
+can be converted into a Riemann-Stieltjes integral. Furthermore, Grobler showed that a Riemann-Stieltjes integral can be interpreted as the are obtained by summing toghether 
+the area of an infinite number of non-rectangular infinitesimels, i.e.
 a Riemann-Stieltjes integral can be converted into a Cavalieri integral \cite{ackermann12,?}.

### 2019-05-28 fractional/CMJ style files/article-template.tex
added a new article

@@
 The mathematical discipline in which we study the extension of derivatives and integrals to non-integer orders is known as fractional calculus. Euler, Liouville and Riemann laid most 
-of theoretical groundwork which was needed to develop the field of fractional calculus \cite{davis59,liouville1832,riemann1876,laurent1884}.
+of the theoretical groundwork which was needed to develop the field of fractional calculus \cite{davis59,liouville1832,riemann1876,laurent1884}.
 Fractional calculus has now developed into a mature discipline \cite{machado14}.
@@
 At this point in time the reader should be made aware of the fact that there exists many other accepted fractional integral definitions in the literature.
-We, however, deem thhese definitions to be beyond the scope of the current article and as such we do not discuss them any further in this work. The geometric interpretation 
-we present here is an extension of the geometric interpretation presented by Podlubny\cite{podlubny02}. Podlubny showed that a Riemann-Liouville fractional integral 
-can be converted into a Riemann-Stieltjes integral. Furthermore, Grobler showed that a Riemann-Stieltjes integral can be interpreted as the are obtained by summing toghether 
+We, however, deem these definitions to be beyond the scope of the current article and as such we do not discuss them any further in this work. Furthermore, the geometric interpretation 
+we present here is an extension of the geometric interpretation presented by Podlubny \cite{podlubny02}. Podlubny showed that a Riemann-Liouville fractional integral 
+can be converted into a Riemann-Stieltjes integral. Furthermore, Grobler showed that a Riemann-Stieltjes integral can be interpreted as the area whis is obtained by summing toghether 
 the area of an infinite number of non-rectangular infinitesimels, i.e.
@@
 Combining these two ideas together results in the following geometric
-interpretation: the Riemann-Liouville fractional integral can be interpreted as an infinite sum of non-rectangular infinitesimals whose shape is determined by the order of integration $\alpha$ and the integration limit $t$.\\
+interpretation: the Riemann-Liouville fractional integral can be interpreted as the area which is obtained by summing together the area of an infinite number of non-rectangular infinitesimals whose shape is determined by the order of integration $\alpha$ and the integration limit $t$.\\
 
 \noindent
-We specifically wrote this paper for people with a pedagogical interest, undergraduate students and for the layman who finds integration theory intriguing and 
+It should be noted that we specifically wrote this paper for people with a pedagogical interest, undergraduate students and for the layman who finds integration theory intriguing and 
 as such we will try to steer clear from using too many mathematical definitions and proofs. We will rather convey our ideas using as many examples as possible. From the 
@@
 articles published in undergraduate journals \cite{munkhammar05}.
-One of the reasons undergraduates struggle to grasp fractional calculus, apart from it not normally being taught as part of the undergraduate curricilum, is because,
-it is such an abstract concept.
+Undergraduates struggle to grasp fractional calculus, because it is very abstract.
 We believe that the geometric interpretation we present in this paper, as it is similar in nature to the definition of classical integration, will provide undergraduates with the insight that they need to quickly grasp and understand the fundamental
-concepts that unerpin fractional calculus.
-We also hope that this paper will enable and encourage undergraduate lectures to already introduce students to this fascinating mathematical discipline as part of their
-undergraduate training.\\
+concepts that unerpin fractional calculus.\\
+
+%We also hope that this paper will enable and encourage lectures to teach this fascinating mathematical discipline to undergraduate students.\\
 
 \noindent
-We start the paper by reviewing the definition of the Riemann-Stieltjes and Cavalieri integral. We then present the definition of the Riemann-Liouville fractional integral. 
-We end the paper by presenting our novel geometric interpretation and a conclusion.
+We start the paper by reviewing the definition of the Riemann-Stieltjes integreal, the Cavalieri integral and the Euler function.
+We then present the definition of the Riemann-Liouville fractional integral.
+We end the paper by presenting our novel geometric interpretation, some examples and a conclusion.
 
@@
 
-\section{First-level section heading}
-
-Section headings use an initial capital letter on the first word, with subsequent words lowercase.
+% \section{First-level section heading}
+% 
+% Section headings use an initial capital letter on the first word, with subsequent words lowercase.
 In general, the style of the journal is to leave all section headings unnumbered.
 Consult the journal editor if you wish to depart from this and other conventions.
-
-\subsection{Second-level heading}
-
-The same goes for second-level headings.
+% 
+% \subsection{Second-level heading}
+% 
+% The same goes for second-level headings.
 It is not necessary to add font commands to make the math within heads bold and sans serif; this change will occur automatically when the production style is applied.
-
-\section{Graphics}
-
-Figures for the \textsc{Journal} can be submitted as either color or black \& white graphics.
+% 
+% \section{Graphics}
+% 
+% Figures for the \textsc{Journal} can be submitted as either color or black \& white graphics.
 Generally, color graphics will be used for the online publication, and converted to black \& white images for the print journal.
 We recommend using whatever graphics program you are most comfortable with, so long as the submitted graphic is provided as a separate file using a standard file format.
-
-For best results, please follow the following guidelines:
-\begin{enumerate}
-\item Bitmapped file formats---preferably TIFF or JPEG, but not BMP---are appropriate for photographs, using a resolution of at least 300 dpi at the final scaled size of the image.
-\item Line art will reproduce best if provided in vector form, preferably EPS.
-\item Alternatively, both photographs and line art can alternatively be provided as PDF files.
+% 
+% For best results, please follow the following guidelines:
+% \begin{enumerate}
+% \item Bitmapped file formats---preferably TIFF or JPEG, but not BMP---are appropriate for photographs, using a resolution of at least 300 dpi at the final scaled size of the image.
+% \item Line art will reproduce best if provided in vector form, preferably EPS.
+% \item Alternatively, both photographs and line art can alternatively be provided as PDF files.
 Note that creating a PDF does not affect whether the graphic is a bitmap or vector; saving a scanned piece of line art as PDF does not convert it to scalable line art.
-\item If you generating graphics using a \TeX\ package, please be sure to provide a PDF of the manuscript.
+% \item If you generating graphics using a \TeX\ package, please be sure to provide a PDF of the manuscript.
 In the production process, \TeX-generated graphics will eventually be converted to more conventional graphics so the \textsc{Journal} can be delivered in e-reader formats.
-\item For photos of contributing authors, we prefer photos that are not cropped tight to the author's profile, so that production staff can crop the head shot to an equal height and width.
+% \item For photos of contributing authors, we prefer photos that are not cropped tight to the author's profile, so that production staff can crop the head shot to an equal height and width.
 If possible, avoid photographs that have excess shadows or glare.
-\end{enumerate}
-
-\section{Theorems, definitions, proofs, and all that}
-
-Following the defaults of the \texttt{amsthm} package, styling is provided for \texttt{theorem}, \texttt{definition}, and \texttt{remark} styles, although the latter two use the same styling.
-
-\begin{theorem}[Pythagorean Theorem]
-Theorems, lemmas, axioms, and the like are stylized using italicized text. These environments can be numbered or unnumbered, at the author's discretion.
-\end{theorem}
-
-\begin{proof}
-Proofs set in roman (upright) text, and conclude with an ``end of proof'' (q.e.d.) symbol that is set automatically when you end the proof environment.
+% \end{enumerate}
+% 
+% \section{Theorems, definitions, proofs, and all that}
+% 
+% Following the defaults of the \texttt{amsthm} package, styling is provided for \texttt{theorem}, \texttt{definition}, and \texttt{remark} styles, although the latter two use the same styling.
+% 
+% \begin{theorem}[Pythagorean Theorem]
+% Theorems, lemmas, axioms, and the like are stylized using italicized text. These environments can be numbered or unnumbered, at the author's discretion.
+% \end{theorem}
+% 
+% \begin{proof}
+% Proofs set in roman (upright) text, and conclude with an ``end of proof'' (q.e.d.) symbol that is set automatically when you end the proof environment.
 When the proof ends with an equation or other non-text element, you need to add \verb~\qedhere~ to the element to set the end of proof symbol; see the \texttt{amsthm} package documentation for more details.
-\end{proof}
-
-\begin{definition}[Secant Line]
-Definitions, remarks, and notation are stylized as roman text.  They are typically unnumbered, but there are no hard-and-fast rules about numbering.
-\end{definition}
-
-\begin{remark}
-Remarks stylize the same as definitions.
-\end{remark}
-
-Note that the \textit{College Mathematics Journal\/} is meant to be accessible to a broad audience, so heavy use of theorem-like formalisms is generally discouraged.
+% \end{proof}
+% 
+% \begin{definition}[Secant Line]
+% Definitions, remarks, and notation are stylized as roman text.  They are typically unnumbered, but there are no hard-and-fast rules about numbering.
+% \end{definition}
+% 
+% \begin{remark}
+% Remarks stylize the same as definitions.
+% \end{remark}
+% 
+% Note that the \textit{College Mathematics Journal\/} is meant to be accessible to a broad audience, so heavy use of theorem-like formalisms is generally discouraged.
 

### 2019-05-29 fractional/CMJ style files/article-template.tex
added more references and fixed some minor issues

@@
 The mathematical discipline in which we study the extension of derivatives and integrals to non-integer orders is known as fractional calculus. Euler, Liouville and Riemann laid most 
-of the theoretical groundwork which was needed to develop the field of fractional calculus \cite{davis59,liouville1832,riemann1876,laurent1884}.
+of the theoretical groundwork which was needed to develop the field of fractional calculus \cite{davis59,euler1738,liouville1832,riemann1876,laurent1884}.
 Fractional calculus has now developed into a mature discipline \cite{machado14}.
@@
 the area of an infinite number of non-rectangular infinitesimels, i.e.
-a Riemann-Stieltjes integral can be converted into a Cavalieri integral \cite{ackermann12,?}.
+a Riemann-Stieltjes integral can be converted into a Cavalieri integral \cite{ackermann12,grobler19}.
 Combining these two ideas together results in the following geometric
@@
 \section{Riemann-Stieltjes Integral}
-Recall that the Riemann-Stieltjes integral is defined as follows:
+Recall that the Riemann-Stieltjes integral is defined as follows \cite{bartle76}:
 \begin{equation}
@@
 \section{Cavalieri Integral}
-Let the region $R$ be bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$ and $b(y)=4-y$. This region is shown in Fig.~\ref{fig:caval2}.\\
+In this section we define the Cavalieri integral \cite{ackermann12}.
+Let the region $R$ be bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$ and $b(y)=4-y$.
+This region is shown in Fig.~\ref{fig:caval2}.\\
 %\begin{figure}[htb]
@@
 \noindent
-Conversely, if $g$ is known (and not $a(y)$) and $g(a') = a$ then we can calculate $a(y)$ using the following:
+Conversely, if $g$ is known (and not $a(y)$) and $g(a') = a$ then we can calculate $a(y)$ using the following \cite{grobler19}:
 \begin{equation}
@@
 \end{equation}
-Note the power of Eq.~\eqref{eq:a_y} it allows us to transform a Riemann-Stieltjes integral into an equivalent Cavalieri integral. 
+Eq.~\eqref{eq:a_y} allows us to transform a Riemann-Stieltjes integral into an equivalent Cavalieri integral. 
 Furthermore, this transformation enables us to assign a geometric interpretation to a Riemann-Stieltjes integral. The interpretation being:
-it represents the area obtained by summing together the area of an infinite number of non-rectangular infinitesimals whose shape is determined by $a(y)$.
+it represents the area obtained by summing together the area of an infinite number of non-rectangular infinitesimals; all of them being translations of $a(y)$.
 
 \section{Gamma Function}
-The gamma function was first devised by Euler.
+The gamma function was first devised by Euler \cite{euler1738}.
 The gamma function is defined for all real numbers except for the non-negative integers.
@@
 \section{Riemann-Liouville Fractional Integral}
-In this section we present the definition of the Riemann-Liouville fractional integral of order $\alpha$. Let
+In this section we present the definition of the Riemann-Liouville fractional integral of order $\alpha$ \cite{laurent1884}. Let
 \begin{equation}
-If(x) := \int_0^x f(t) dt.
+If(t) := \int_0^t f(\tau)~d\tau.
 \end{equation}
@@
 \label{eq:n_anti}
-I^nf(x) = \int_0^x\int_0^{x_1}\cdots \int_0^{x_{n-1}}f(x_n)~dx_n\cdots dx_2 dx_1.
+I^nf(t) = \int_0^t\int_0^{t_1}\cdots \int_0^{t_{n-1}}f(t_n)~dt_n\cdots dt_2 dt_1.
 \end{equation}
@@
 \label{eq:cauchy}
-I^nf(x) = \frac{1}{(n-1)!}\int_0^x (x-t)^{n-1}f(t)~dt.
+I^nf(t) = \frac{1}{(n-1)!}\int_0^t (t-\tau)^{n-1}f(\tau)~d\tau.
 \end{equation}
-As an example if $f(x)=x$ and $n=2$ then Eq.~\eqref{eq:cauchy} reduces to:
+As an example if $f(t)=t$ and $n=2$ then Eq.~\eqref{eq:cauchy} reduces to:
 \begin{equation}
-I^2f(x) = \int_0^x (x-t)t~dt = \frac{t^2x}{2} - \frac{t^3}{3} \Bigg |_0^x = \frac{x^3}{3!}.
+I^2f(t) = \int_0^t (t-\tau)t~dt = \frac{\tau^2 t}{2} - \frac{\tau^3}{3} \Bigg |_0^t = \frac{t^3}{3!}.
 \end{equation}
@@
 \label{eq:frac_integral}
-I^{\alpha}f(x) = \frac{1}{\Gamma(\alpha)}\int_0^x (x-t)^{\alpha-1}f(t)~dt.
+I^{\alpha}f(t) = \frac{1}{\Gamma(\alpha)}\int_0^t (t-\tau)^{\alpha-1}f(\tau)~d\tau.
 \end{equation}
-Eq.~\eqref{eq:frac_integral} is known as the Riemann-Liouville fractional integral of order $\alpha$. As an example if $f(x)=x$ and $\alpha=\frac{1}{2}$ then 
+Eq.~\eqref{eq:frac_integral} is known as the Riemann-Liouville fractional integral of order $\alpha$. As an example if $f(t)=t$ and $\alpha=\frac{1}{2}$ then 
 Eq.~\eqref{eq:frac_integral} reduces to:
 \begin{equation}
-I^{\frac{1}{2}}f(x) = \frac{1}{\Gamma(\frac{1}{2})} \int_0^x \frac{t}{\sqrt{x-t}} dt = \frac{1}{\sqrt{\pi}}\left [ -\frac{2}{3}\sqrt{x-t}(t+2x)\right] \Bigg |_0^x=\frac{4}{3\sqrt{\pi}}x^{\frac{3}{2}}.
+I^{\frac{1}{2}}f(\tau) = \frac{1}{\Gamma(\frac{1}{2})} \int_0^t \frac{\tau}{\sqrt{t-\tau}} dt = \frac{1}{\sqrt{\pi}}\left [ -\frac{2}{3}\sqrt{t-\tau}(t+2x)\right] \Bigg |_0^t=\frac{4}{3\sqrt{\pi}}t^{\frac{3}{2}}.
 \end{equation}
@@
 \begin{equation}
-I^{\alpha}I^{\beta}f(x) = I^{\alpha+\beta}f(x). 
+I^{\alpha}I^{\beta}f(t) = I^{\alpha+\beta}f(t). 
 \end{equation}
@@
 \section{Geometric Interpretation of the Riemann-Liouville Fractional Integral}
-
+In this section we present a novel geometric interpretation of the Riemann-Liouville fractional integral. 
 Recall that the Riemann-Liouville fractional integral of order $\alpha$ is defined as:
@@
 \noindent
-Podlubny et al. showed that the above fractional integral can be rewritten as a Riemann-Stieltjes integral:
+Podlubny showed that the above fractional integral can be rewritten as a Riemann-Stieltjes integral \cite{podlubny02}:
 \begin{equation}
@@
 \noindent
-Let $\mathsf{A} = \{0,0.2,0.4,0.6,0.8,1\}$.
-The analytic expressions of $g_{10}^{\alpha}(\tau)$ and $h_{10}^{\alpha}(\tau)$ are presented in Table~\ref{tab:gandh} for $\alpha\in\mathsf{A}$ and $t=10$.
+Let $\mathsf{A} = \{0,0.2,0.4,0.6,0.8,1\}$. The analytic expressions of $g_{10}^{\alpha}(\tau)$ and $h_{10}^{\alpha}(\tau)$ are presented in Table~\ref{tab:gandh} for $\alpha\in\mathsf{A}$. 
 The expressions in Table~\ref{tab:gandh} are depicted in Fig~\ref{fig:gandh}.
@@
 \noindent
-Furthermore, Grobler et.
-al showed that it is trivial to convert a Riemann-Stieltjes integral into a Cavalieri integral.
-We review this conversion procedure in the Cavalieri section of this paper (see Fig.~\ref{fig:caval2}).
-If we apply their conversion steps to Eq.~\eqref{eq:rs} we obtain:
+Furthermore, Grobler showed that it is trivial to convert a Riemann-Stieltjes integral into a Cavalieri integral \cite{ackermann12,grobler19} (see Fig.~\ref{fig:caval2} and the Cavalieri section of this paper for more details).
+If we apply conversion steps he outlines in \cite{grobler19} to Eq.~\eqref{eq:rs} we obtain:
 \begin{equation}
@@
 \noindent
-We can easily assign a geometric interpretation to Eq.~\eqref{eq:cav}, since it is a Cavalieri integral (see Fig.~\ref{fig:caval2}).
+We can now assign a geometric interpretation to Eq.~\eqref{eq:cav}, since it is a Cavalieri integral (see Fig.~\ref{fig:caval2} and the Cavalieri section of this paper).
 The fractional integral in Eq.~\eqref{eq:RL_frac_int} can, therefore, be interpreted as the area obtained
@@
 \end{equation}
-The function $f(\tau) =\tau$ is depicted in Fig.~\ref{fig:geo1}.
+The function $f(t) =t$ is depicted in Fig.~\ref{fig:geo1}.
 As we mentioned in the previous section, we can assign a geometric interpretation to the above fractional integral by converting it into a Cavalieri integral using two steps.
@@
 
-\bibitem{parker13} Adam Parker, Who solved the Bernoulli equation and how did they do it? \textit{Coll. Math. J.} \textbf{44} (2013) 89--97.
+\bibitem{parker13} Adam Parker, Who solved the Bernoulli equation and how did they do it? \textit{Coll. Math. J.} \textbf{44} 89--97.
 
-\bibitem{laurent1884} Laurent, H. (1884). Sur le calcul des d\'{e}riv\'{e}es \`{a} indices quelconques. \textit{Nouv Annales de Mathem\'{e}matiques.} 3(3):240--252.
+\bibitem{laurent1884} Laurent,~H. (1884). Sur le calcul des d\'{e}riv\'{e}es \`{a} indices quelconques. \textit{Nouv Annales de Mathem\'{e}matiques.} 3(3):240--252.
 
-\bibitem{munkhammar05} Munkhammar, J. (2005). Fractional calculus and the Taylor-Riemann series. \textit{Rose-Hulman Undergraduate Mathematics Journal}, 6(1): 6.
+\bibitem{munkhammar05} Munkhammar,~J. (2005). Fractional calculus and the Taylor-Riemann series. \textit{Rose-Hulman Undergraduate Mathematics Journal}, 6(1): 6.
+
+\bibitem{grobler19} Grobler,~T.L. (2019). Visualization of the Riemann-Stieltjes integral. \textit{Coll. Math. J.} 50(3): 198--209.
+
+\bibitem{bartle76} Bartle,~R.~G. (1976). \textit{The Elements of Real Analysis.} New York: Wiley.
+
+\bibitem{euler1738} Euler,~L. (1738). De progressionibus transcendentibus seu quarum termini generales algebraice dari nequeunt. \textit{Commentarii academiae scientiarum Petropolitanae}. 36--57.
 

### 2019-05-29 fractional/CMJ style files/article-template.tex
added new figures

@@
 \end{equation}
-As an example if $f(t)=t$ and $n=2$ then Eq.~\eqref{eq:cauchy} reduces to:
+As an example if $f(\tau)=\tau$ and $n=2$ then Eq.~\eqref{eq:cauchy} reduces to:
 \begin{equation}
@@
 \end{equation}
-Eq.~\eqref{eq:frac_integral} is known as the Riemann-Liouville fractional integral of order $\alpha$. As an example if $f(t)=t$ and $\alpha=\frac{1}{2}$ then 
+Eq.~\eqref{eq:frac_integral} is known as the Riemann-Liouville fractional integral of order $\alpha$. As an example if $f(\tau)=\tau$ and $\alpha=\frac{1}{2}$ then 
 Eq.~\eqref{eq:frac_integral} reduces to:
@@
 Furthermore, Grobler showed that it is trivial to convert a Riemann-Stieltjes integral into a Cavalieri integral \cite{ackermann12,grobler19} (see Fig.~\ref{fig:caval2} and the Cavalieri section of this paper for more details).
-If we apply conversion steps he outlines in \cite{grobler19} to Eq.~\eqref{eq:rs} we obtain:
+If we follow the conversion steps outlined in \cite{grobler19} to Eq.~\eqref{eq:rs} we obtain:
 \begin{equation}
@@
 \end{equation}
-The function $f(t) =t$ is depicted in Fig.~\ref{fig:geo1}.
+The function $f(\tau) =\tau$ is depicted in Fig.~\ref{fig:geo1}.
 As we mentioned in the previous section, we can assign a geometric interpretation to the above fractional integral by converting it into a Cavalieri integral using two steps.
@@
 \centering
-\includegraphics[width=1\textwidth]{geo_int1.pdf}
+\includegraphics[width=0.75\textwidth]{geo_int1.pdf}
 \caption{The non-static non-rectangular sum-based geometric interpretation of Eq.~\eqref{eq:ex1_raw}.}
@@
 It can be interpreted as the area obtained by summing together the areas of an infinite
-number of infinitesimals whose shape is determined by $\alpha$ and $t$. Moreover, these infinitesimals have to be translations of $b_t^{\alpha}(y)$ which, in turn, is 
-function of $\alpha$ and $t$. The geometric interpretation of Eq.~\eqref{eq:ex1_raw} is, therefore, non-static as it depends on the value of $\alpha$ and $t$. 
+number of infinitesimals whose shape is determined by $\alpha$ and $t$, i.e.
+these infinitesimals have to be translations of $b_t^{\alpha}(y)$.
+The geometric interpretation of Eq.~\eqref{eq:ex1_raw} is, therefore, non-static as it depends on the value of $\alpha$ and $t$.
 There is one thing, however, which remains unclear: in what way does $\alpha$ and $t$ affect the shape of the aforementioned infinitesimals, i.e.
 how does the value of $\alpha$ and $t$ affect the shape of $b_t^{\alpha}(y)$.
-We will answer this question by using two basic steps.
+We will answer this question by working through a detailed example.\\
+
+%using two basic steps.
 First off, we will fix the value of $\alpha$ and $t$ in Eq.~\eqref{eq:ex1} and then depict $b_t^{\alpha}(y)$.
 We will then explore how varying the value of $\alpha$ and $t$ in Eq.~\eqref{eq:ex1} affects the shape $b_t^{\alpha}(y)$.\\
-
 %We know that a Cavalieri integral can be interpreted as the area which is obtained by summing together the area associated with an infinite number of non-rectangular infinitesimals whose shape 
@@
 the result obtained via the aforementioned limit is the Cavalieri integral found in Eq.~\eqref{eq:ex1_specific}.
-In conclusion, we can think of Eq.~\eqref{eq:ex1_specific} as implying that the region $R_{10}^{\sfrac{4}{5}}$ is made up
+This then verifies
+the assertion we made earlier. Eq.~\eqref{eq:ex1_specific}, therefore, implies that the region $R_{10}^{\sfrac{4}{5}}$ is made up 
 of an infinite number of non-rectangular infinitesimals; all of them being translations of $b_{10}^{\sfrac{4}{5}}(y)$.
@@
 \centering
-\includegraphics[width=1\textwidth]{func_eval1.pdf}
+\includegraphics[width=0.75\textwidth]{func_eval1.pdf}
 \caption{Depicts the curves which are obtained by evaluating Eq.~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ using either Eq.~\eqref{eq:rs} or Eq.~\eqref{eq:option2}.}
@@
 \centering
-\includegraphics[width=1\textwidth]{geo_int2.pdf}
+\includegraphics[width=0.75\textwidth]{geo_int2.pdf}
 \caption{The non-static non-rectangular sum-based geometric interpretation of Eq.~\eqref{eq:ex2}.}
@@
 \centering
-\includegraphics[width=1\textwidth]{func_eval2.pdf}
+\includegraphics[width=0.75\textwidth]{func_eval2.pdf}
 \caption{Depicts the curves which are obtained by evaluating Eq.~\eqref{eq:ex2} for all $\alpha\in \mathsf{A}$ using either Eq.~\eqref{eq:rs} or Eq.~\eqref{eq:option2}.}
@@
 
-\begin{acknowledgment}
-The authors wish to thank the Greek polymath Anonymous, whose prolific works are an endless source of inspiration.
-\end{acknowledgment}
+%\begin{acknowledgment}
+%The authors wish to thank the Greek polymath Anonymous, whose prolific works are an endless source of inspiration.
+%\end{acknowledgment}
 
 \begin{abstract}
+Having geometrical ideas  interpretations of complex mathematical ideas is crucial if we
 An abstract should not contain concrete mathematics, but rather should be discrete.

### 2019-05-29 fractional/CMJ style files/article-template.tex
newest version

@@
 
-\title{Visualization of [fulle name] Fractional Integrals}
+\title{Visualization of the Riemann-Liouville Fractional Integral}
 \author{Woodrow Wilson and Herbert Hoover} %%leave blank in initial submission to allow for double blind reviewing
@@
 
-To conclude this section, a fractional integral of order $\alpha$ and extent $t$ can be interpreted as the area obtained by summing together the area associated with an infinite number of infinitesimals whose
-shape is determined by $\alpha$ and $t$. The geometric interpretation of a fractional integral is, therefore, non-static as it depends on the value of both $\alpha$ and $t$.
+%To conclude this section, a fractional integral of order $\alpha$ and extent $t$ can be interpreted as the area obtained by summing together the area associated with an infinite number of infinitesimals whose
+%shape is determined by $\alpha$ and $t$. The geometric interpretation of a fractional integral is, therefore, non-static as it depends on the value of both $\alpha$ and $t$.
 
@@
 \begin{abstract}
-Having geometrical ideas  interpretations of complex mathematical ideas is crucial if we
-An abstract should not contain concrete mathematics, but rather should be discrete.
-Be brief and avoid using mathematical notation except where absolutely necessary, since this brief synopsis will be used by search engines to identify your article!
+In this paper we present a novel geometric interpetation of the Riemann-Liouville fractional integral. We found that a Riemann-Liouville integral can 
+be thought of as the area obtained by summing together the area of an infinite number of non-rectangular infinitesimals whose shape is determined by the 
+order of integration $\alpha$ and the integration limit $t$. We also emphasize the pedagogical benefits that this interpretation offers, as it is very 
+similar in nature to the geometric interpretation that is associated with classic Riemann integrals.   
 \end{abstract}

### 2019-05-29 fractional/func_explorer.py
newest code

@@ -16,6 +16,10 @@ import math
 #    x = -0.25*y**(2.0/3.0) + 9.0/2.0*y**(1.0/3.0) - 11
 #    return x
 
+def ys(y):
+    x = y**2
+    return x
+
 def a1(y,alpha,t,b):
     x = y - 1.0/math.gamma(alpha+1)*(t**alpha - (t-y)**alpha)
     return x+b
@@ -44,27 +48,6 @@ def f2(x):
 
 def f2_inv(y):
     return y**2
-
-def plt_gh_functions(alpha = np.array([0.2,0.4,0.6,0.8,1.0]),t=10,num=1000):
-    tau = np.linspace(0,t,num)
-    #[0.125,0.25,0.375,0.5,0.625,0.75,0.875,1.0]
-    v = np.linspace(0,1.5,len(alpha))
-
-    for k in range(len(alpha)):
-        tau2 = np.linspace(0,(t**alpha[k])/math.gamma(alpha[k]+1),num)
-        y1 = g_func(tau,alpha[k],t)
-        y2 = h_func(tau2,alpha[k],t)
-        col = [v[k]/2,v[k]/2,v[k]/2]    
-        plt.plot(tau,y1,color=col)
-        plt.plot(tau2,y2,color=col,ls = "--")
-
-    plt.xlabel(r"$\tau$")
-    plt.ylabel(r"$y$")
-    plt.xlim([0,10])
-    plt.ylim([0,10])
-    plt.show()
-
-
 
 def plot_g_functions(t_vector,alpha_vector,tau_points):
     fig, ax = plt.subplots(len(t_vector), len(alpha_vector), sharex='all', sharey='all')
@@ -105,45 +88,6 @@ def plot_a_functions(t_vector,alpha_vector,y_points,f_inv,f):
               ax[k,i].set_ylabel("t = "+str(round(t_vector[k],1)))
     plt.show() 
 
-def plot_b_functions(t_vector=np.array([2,4,6,8,10]),alpha_vector=np.array([0.2,0.4,0.6,0.8]),y_points=50000,f_inv=f1_inv,f=f1):
-    #plt.grid('on')
-    fig,ax = plt.subplots(1,len(alpha_vector),sharex='all', sharey='all')
-    #plt.grid('on')
-    v = np.linspace(0,1.5,len(t_vector))
-
[…]

### 2019-05-30 fractional/CMJ style files/article-template.tex
added some minor corrections

@@
 \noindent
-Leibniz, who is regarded by many scholars as the farther of calculus, is credited with inventing the following notation: $\frac{d^n y}{d x^n}$. 
+Leibniz, who is regarded by many scholars as the father of calculus, is credited with inventing the following notation: $\frac{d^n y}{d x^n}$. 
 A natural question which arises when one inspects this notation is: Can $n$ be a non-integer value? L'Hospital phrased it differently: ``\emph{What if $n$ be a $\frac{1}{2}$?}''. 
@@
 As we mentioned earlier, Riemann and Liouville played an important role in the development of fractional calculus. Their work was crucial in defining what is now know as 
-the Riemann-Liouville fractional integral \cite{laurent1884}.
+the Riemann-Liouville fractional integral based at 0 \cite{laurent1884}.
 At this point in time the reader should be made aware of the fact that there exists many other accepted fractional integral definitions in the literature.
@@
 \noindent
-It should be noted that we specifically wrote this paper for people with a pedagogical interest, undergraduate students and for the layman who finds integration theory intriguing and 
+It is important for the reader to realize that we specifically wrote this paper for people with a pedagogical interest, undergraduate students and for the layman who finds integration theory intriguing and
 as such we will try to steer clear from using too many mathematical definitions and proofs. We will rather convey our ideas using as many examples as possible. From the 
@@
 Furthermore, this transformation enables us to assign a geometric interpretation to a Riemann-Stieltjes integral. The interpretation being:
-it represents the area obtained by summing together the area of an infinite number of non-rectangular infinitesimals; all of them being translations of $a(y)$.
+it represents the area obtained by summing together the area of an infinite number of non-rectangular infinitesimals; all of them being translations of $a(y)$. Note,
+$b(y) = a(y) + (b-a)$.
 
@@
 \begin{equation}
-I^{\frac{1}{2}}f(\tau) = \frac{1}{\Gamma(\frac{1}{2})} \int_0^t \frac{\tau}{\sqrt{t-\tau}} dt = \frac{1}{\sqrt{\pi}}\left [ -\frac{2}{3}\sqrt{t-\tau}(t+2x)\right] \Bigg |_0^t=\frac{4}{3\sqrt{\pi}}t^{\frac{3}{2}}.
+I^{\frac{1}{2}}f(t) = \frac{1}{\Gamma(\frac{1}{2})} \int_0^t \frac{\tau}{\sqrt{t-\tau}} dt = \frac{1}{\sqrt{\pi}}\left [ -\frac{2}{3}\sqrt{t-\tau}(t+2x)\right] \Bigg |_0^t=\frac{4}{3\sqrt{\pi}}t^{\frac{3}{2}}.
 \end{equation}
@@
 \noindent
-Furthermore, Grobler showed that it is trivial to convert a Riemann-Stieltjes integral into a Cavalieri integral \cite{ackermann12,grobler19} (see Fig.~\ref{fig:caval2} and the Cavalieri section of this paper for more details).
-If we follow the conversion steps outlined in \cite{grobler19} to Eq.~\eqref{eq:rs} we obtain:
+Furthermore, Grobler showed that it is trivial to convert a Riemann-Stieltjes integral into a Cavalieri integral \cite{ackermann12,grobler19} (see Fig.~\ref{fig:caval2} and the Cavalieri section of this paper if more details are required).
+If we apply Grobler's conversion method to Eq.~\eqref{eq:rs} we obtain:
 \begin{equation}
@@
 \end{equation}
-Eq.~\eqref{eq:cav_a} is obtained by substituting Eq.~\eqref{eq:g_rl} into Eq.~\eqref{eq:a_y}.
+Eq.~\eqref{eq:cav_a} is obtained by substituting Eq.~\eqref{eq:g_rl} into Eq.~\eqref{eq:a_y}. Note, $b_t^{\alpha}(y) = a_t^{\alpha}(y) + \frac{t^{\alpha}}{\Gamma(\alpha+1)}$.
 
@@
 \label{eq:ex1}
-\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \int_0^t f(\tau)~dg_t^{\alpha}(\tau)=\int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau. 
+\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \int_0^t f(\tau)~dg_t^{\alpha}(\tau)=\int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau,
+\end{equation}
+with
+\begin{equation}
+a_t^{\alpha}(y) = y - \frac{t^{\alpha}-(t-y)^{\alpha}}{\Gamma(\alpha+1)}.
 \end{equation}
@@
 It is the largest of all the
-regions that are depicted in the right-most panel of Fig.~\ref{fig:geo1}.
-Moreover, let $A_{10}^{\sfrac{4}{5}}$ denote the area of $R_{10}^{\sfrac{4}{5}}$.
-For the sake of completeness, lets first verify that we can employ the Cavalieri integral in Eq.~\ref{eq:ex1_specific} to compute $A_{10}^{\sfrac{4}{5}}$ from first principles.
+regions that are depicted in the right-most panel of Fig.~\ref{fig:geo1}. Moreover, let $A_{10}^{\sfrac{4}{5}}$ denote the area of $R_{10}^{\sfrac{4}{5}}$. 
 We can approximate the area of $R_{10}^{\sfrac{4}{5}}$ by summing together the area of $n$ equal width non-rectangular integration strips that inscribe $R_{10}^{\sfrac{4}{5}}$, i.e. we can 
 construct a Cavalieri sum (see Eq.~\eqref{eq:cav_sum}). Note, the sides of the non-rectangular integration strips we use in this approximation have to be translations of $b_{10}^{\sfrac{4}{5}}(y)$.
-If we take the limit of the aforementioned sum as $n\rightarrow \infty$ we approach $A_{10}^{\sfrac{4}{5}}$, i.e.
-the result obtained via the aforementioned limit is the Cavalieri integral found in Eq.~\eqref{eq:ex1_specific}.
-This then verifies
-the assertion we made earlier. Eq.~\eqref{eq:ex1_specific}, therefore, implies that the region $R_{10}^{\sfrac{4}{5}}$ is made up 
-of an infinite number of non-rectangular infinitesimals; all of them being translations of $b_{10}^{\sfrac{4}{5}}(y)$.
+If we take the limit of the aforementioned sum as $n\rightarrow \infty$ we approach $A_{10}^{\sfrac{4}{5}}$.  
+Eq.~\eqref{eq:ex1_specific}, therefore, implies that the region $R_{10}^{\sfrac{4}{5}}$ is made up 
+of an infinite number of non-rectangular infinitesimals; all of them being translations of $b_{10}^{\sfrac{4}{5}}(y)$, i.e.
+we can compute $A_{10}^{\sfrac{4}{5}}$ by evaluating the Cavalieri integral found in Eq.~\eqref{eq:ex1_specific}.
 Note, the right-most curve depicted in the right-most panel of Fig.~\ref{fig:geo1} is $b_{10}^{\sfrac{4}{5}}(y)$.
@@
 
+%We have thus verified that we can employ the Cavalieri integral in Eq.~\ref{eq:ex1_specific} to compute $A_{10}^{\sfrac{4}{5}}$ from first principles.
 %Let $\mathsf{B}_{10}^{\sfrac{4}{5}}$ denote the set containing these dashed curves.
@@
 \end{description}
-We can therefore draw the following conclusion: the value of both $\alpha$ and $t$ alters the shape of the infinitesimals (i.e.
-the upper limit $b_{t}^{\alpha}(y)$ of Eq.~\eqref{eq:ex1} depends on $\alpha$ and $t$) that make up the regions in Fig.~\ref{fig:geo1}.
+We can therefore draw the following conclusion: the value of both $\alpha$ and $t$ alters the shape of the infinitesimals ($b_{t}^{\alpha}(y)$ depends on $\alpha$ and $t$) that make up the regions in Fig.~\ref{fig:geo1}.
 Interestingly, the effect of $\alpha$ on the shape of the infinitesimals that make up the regions depicted in Fig.~\ref{fig:geo1} is larger than the effect that $t$ has on their shape.
@@
 \begin{abstract}
-In this paper we present a novel geometric interpetation of the Riemann-Liouville fractional integral. We found that a Riemann-Liouville integral can 
+We presented a novel geometric interpetation of the Riemann-Liouville fractional integral. We found that a Riemann-Liouville integral can 
 be thought of as the area obtained by summing together the area of an infinite number of non-rectangular infinitesimals whose shape is determined by the 
-order of integration $\alpha$ and the integration limit $t$. We also emphasize the pedagogical benefits that this interpretation offers, as it is very 
-similar in nature to the geometric interpretation that is associated with classic Riemann integrals.   
+order of integration $\alpha$ and the integration limit $t$. We also showed that this geometric interpretation offers many pedagogical benefits as it is very similar
+in nature to the geometric interpreation of the Riemann integral.   
 \end{abstract}

### 2019-05-30 fractional/CMJ style files/article-template.tex
fixed spelling mistakes typos alphabetic list of authors

@@
 \title{Visualization of the Riemann-Liouville Fractional Integral}
-\author{Woodrow Wilson and Herbert Hoover} %%leave blank in initial submission to allow for double blind reviewing
+%\author{Woodrow Wilson and Herbert Hoover} %%leave blank in initial submission to allow for double blind reviewing
 %\author{ }
@@
 A natural question which arises when one inspects this notation is: Can $n$ be a non-integer value? L'Hospital phrased it differently: ``\emph{What if $n$ be a $\frac{1}{2}$?}''. 
-In a letter Leibniz sent to L'Hospital, Leibniz comments on L'Hospital's question by making the following prophetic remark: ``\emph{This is an apparant paradox from which, one day, useful 
-consequences will be drawn}'' \cite{ross77,machado14}.\\
+In a letter Leibniz sent to L'Hospital, Leibniz comments on L'Hospital's question by making the following prophetic remark: ``\emph{This is an apparent paradox from which, one day, useful 
+consequences will be drawn}'' \cite{ross77,machado14,machado17}.\\
 
@@
 of the theoretical groundwork which was needed to develop the field of fractional calculus \cite{davis59,euler1738,liouville1832,riemann1876,laurent1884}.
-Fractional calculus has now developed into a mature discipline \cite{machado14}.
+Fractional calculus has now developed into a mature discipline \cite{machado14,machado17}.
 However, there is one aspect of the discipline which only started to develop fairly recently: its physical and geometric interpretability.
@@
 a number of papers that attempt to rectify this.
-There now exists probabilistic interpretations \cite{stanislavsky04,machado03}, geometric interpretations \cite{adda97,tarasov16,podlubny02}, physical interpretations \cite{cioc16,rutman95} and economic
+There now exists probabilistic interpretations \cite{stanislavsky04,machado03}, geometric interpretations \cite{adda97,tarasov16,podlubny02}, physical interpretations \cite{cioc16,rutman95, nigmatullin92, gomez14} and economic
 interpretations \cite{tarasova17} of fractional order integrals and differentials.\\
@@
 In this article we specifically focus on the geometric interpretation of fractional integrals.
-To be more specific, we present a novel geometric interpretation of the Riemann-Liouville fractional integral \cite{laurent1884}.
-As we mentioned earlier, Riemann and Liouville played an important role in the development of fractional calculus. Their work was crucial in defining what is now know as 
-the Riemann-Liouville fractional integral based at 0 \cite{laurent1884}.
+To be more specific, we present a novel geometric interpretation of the Riemann-Liouville fractional integral based at 0 \cite{laurent1884}.
+As we mentioned earlier, Riemann and Liouville played an important role in the development of fractional calculus. Their work was crucial in defining what is now known as 
+the Riemann-Liouville fractional integral \cite{laurent1884}.
 At this point in time the reader should be made aware of the fact that there exists many other accepted fractional integral definitions in the literature.
@@
 we present here is an extension of the geometric interpretation presented by Podlubny \cite{podlubny02}. Podlubny showed that a Riemann-Liouville fractional integral 
-can be converted into a Riemann-Stieltjes integral. Furthermore, Grobler showed that a Riemann-Stieltjes integral can be interpreted as the area whis is obtained by summing toghether 
-the area of an infinite number of non-rectangular infinitesimels, i.e.
+can be converted into a Riemann-Stieltjes integral. Furthermore, Grobler showed that a Riemann-Stieltjes integral can be interpreted as the area which is obtained by summing together 
+the area of an infinite number of non-rectangular infinitesimals, i.e.
 a Riemann-Stieltjes integral can be converted into a Cavalieri integral \cite{ackermann12,grobler19}.
@@
 We believe that the geometric interpretation we present in this paper, as it is similar in nature to the definition of classical integration, will provide undergraduates with the insight that they need to quickly grasp and understand the fundamental
-concepts that unerpin fractional calculus.\\
+concepts that underpin fractional calculus.\\
 
@@
 \noindent
-We start the paper by reviewing the definition of the Riemann-Stieltjes integreal, the Cavalieri integral and the Euler function.
+We start the paper by reviewing the definition of the Riemann-Stieltjes integral, the Cavalieri integral and the Euler function.
 We then present the definition of the Riemann-Liouville fractional integral.
@@
 \end{equation}
-with
-\begin{equation}
-a_t^{\alpha}(y) = y - \frac{t^{\alpha}-(t-y)^{\alpha}}{\Gamma(\alpha+1)}.
-\end{equation}
+with $a_t^{\alpha}(y) = y - \frac{t^{\alpha}-(t-y)^{\alpha}}{\Gamma(\alpha+1)}.$
 
@@
 \begin{description}
- \item[Effect of $\alpha$] the grey-tinted solid curves depicted in the different panels of Fig.~\ref{fig:geo1} are not equal to one-another, i.e.
+ \item[Effect of $\alpha$] the gray-tinted solid curves depicted in the different panels of Fig.~\ref{fig:geo1} are not equal to one-another, i.e.
 $\mathsf{B}_{\mathsf{T}}^{\alpha_1}\neq\mathsf{B}_{\mathsf{T}}^{\alpha_2}$.
- \item[Effect of $t$] the grey-tinted solid curves depicted in each of the panels of Fig.~\ref{fig:geo1} are not translations of one-another.
-Moreover, the dashed grey curves and the solid grey-tinted curves in the right-most panel are not equal to one-another, i.e.
+ \item[Effect of $t$] the gray-tinted solid curves depicted in each of the panels of Fig.~\ref{fig:geo1} are not translations of one-another.
+Moreover, the dashed gray curves and the solid gray-tinted curves in the right-most panel are not equal to one-another, i.e.
 $\mathsf{B}_{\mathsf{T}}^{\sfrac{4}{5}}\neq\mathcal{B}_{\mathsf{T}}^{\sfrac{4}{5}}$.
@@
 
-%In the case of $\alpha$: the grey-tinted solid curves depicted in each panel are not equal to one-another.
-Similarly, in the case of $t$: the dashed grey curves and the solid grey-tinted curves in the right-most panel are not equal to one-another, i.e.$\mathsf{B}_T^{\alpha}\neq\mathcal{B}_T^{\alpha}$.
+%In the case of $\alpha$: the gray-tinted solid curves depicted in each panel are not equal to one-another.
+Similarly, in the case of $t$: the dashed gray curves and the solid gray-tinted curves in the right-most panel are not equal to one-another, i.e.$\mathsf{B}_T^{\alpha}\neq\mathcal{B}_T^{\alpha}$.
 
@@
 % We can visually verify that this observation is in fact true for $alpha=\frac{4}{5}$ by inspecting the right-most panel in Fig.~\ref{??}.
-The dashed curves and the grey tinted curves in this panel do not allign.
+The dashed curves and the gray tinted curves in this panel do not allign.
 % 
@@
 % all the Cavalieri integral upper limits obtained by fixing the order of integration $\alpha$ to a specific value.
-In each panel, we depict the set of curves $\mathsf{B}_T^{\alpha}$ using different shades of grey.
+In each panel, we depict the set of curves $\mathsf{B}_T^{\alpha}$ using different shades of gray.
 % The shade with which $b_t^{\alpha}(y)$ is depicted becomes lighter as the value of $t$ increases.
@@
 % 
-% The curves $\mathsf{B} = \{b_{t}^{\frac{4}{5}}(y)|t\in\{2,4,6,8,10\}\}$ are plotted in different shades of grey.
+% The curves $\mathsf{B} = \{b_{t}^{\frac{4}{5}}(y)|t\in\{2,4,6,8,10\}\}$ are plotted in different shades of gray.
 The shade with which $b_t^{\alpha}(y)$ is depicted becomes lighter as the value of $t$ increases.
@@
 \begin{abstract}
-We presented a novel geometric interpetation of the Riemann-Liouville fractional integral. We found that a Riemann-Liouville integral can 
+We presented a novel geometric interpretation of the Riemann-Liouville fractional integral. We found that a Riemann-Liouville integral can 
 be thought of as the area obtained by summing together the area of an infinite number of non-rectangular infinitesimals whose shape is determined by the 
 order of integration $\alpha$ and the integration limit $t$. We also showed that this geometric interpretation offers many pedagogical benefits as it is very similar
-in nature to the geometric interpreation of the Riemann integral.   
+in nature to the geometric interpretation of the Riemann integral.   
 \end{abstract}
@@
 
-\bibitem{ross77} Ross,~B. (1977). The development of fractional calculus 1695--1900. \textit{Hist. Math.} 4(1): 75--89.
+\bibitem{ackermann12} Ackermann,~E.~R, Grobler,~T.~L., Kleynhans,~W., Olivier,~J.~C., Salmon,~B.~P, van Zyl,~A.~J. (2012). Cavalieri
+Integration. \textit{Quaest. Math.} 35(3): 265–296.
 
-\bibitem{liouville1832} Liouville,~J.
-(1832).
-M\'{e}moire sur l\textquotesingle integration de l\textquotesingle \'{e}quation $(mx^2+nx+p)\frac{d^2y}{dx^2}+(qx+r)\frac{dy}{dx}+sy$ \`{a} l\textquotesingle aide des diff\'{e}rentielles \`{a} indices
-que\textquotesingle conques. \textit{Journal d l\textquotesingle Ecole Polytechnique.} 13(21): 163--186.
+\bibitem{adda97} Adda,~F.~B. (1997). Geometric interpretation of the fractional derivative. \textit{J. of Fract. Calc.}, 11: 21--52.
 
-\bibitem{riemann1876} Riemann,~B.~G.~F (1876). Gesammelte Werke.
-
-\bibitem{davis59} Davis,~P.~J. (1959). Leonhard Euler's Integral: A Historical Profile of the Gamma Function. \textit{Amer. Math. Monthly}. 66(10): 849--869
-
-\bibitem{machado14} Machado,~J.~T., Galhano,~A.~M., Trujillo,~J.~J. (2014). On development of fractional calculus during the last fifty years. \textit{Scientometrics}. 98(1): 577-582.
-
-\bibitem{ross06} Ross,~B.
-(Ed.).
-(2006).
-\textit{Fractional calculus and its applications: proceedings of the international conference held at the University of New Haven, June 1974}, Vol.
-457, Springer.
-
-%Probability
-\bibitem{stanislavsky04} Stanislavsky,~A.~A. (2004).  Probability interpretation of the integral of fractional order, \textit{Theoretical and Mathematical Physics.} 138(3): 418--431.
-
-\bibitem{machado03} Machado,~J.~T. (2003). A probabilistic interpretation of the fractional-order differentiation. \textit{Fract. Calc. Appl. Anal.} 6(1): 73--80.
-
-\bibitem{adda97} Adda,~F.~B. (1997). Geometric interpretation of the fractional derivative. \textit{Journal of Fract. Calc.}, 11: 21--52.
-
-%Geometric
-\bibitem{tarasov16} Tarasov,~V.~E. (2016). Geometric interpretation of fractional-order derivative. \textit{Fract. Calc. Appl. Anal.} 19(5): 1200--1221.
-
-\bibitem{podlubny02} Podlubny,~I. (2002). Geometric and Physical Interpretation of Fractional Integration and Fractional Differentiation, \textit{Fract. Calc. Appl. Anal.} 5(4): 367--386.
+\bibitem{bartle76} Bartle,~R.~G. (1976). \textit{The Elements of Real Analysis.} New York: Wiley.
 
@@
 
-\bibitem{rutman95} Rutman,~R.S. (1995). On physical interpretations of fractional integration and differentiation. \textit{Theoretical and Mathematical Physics.} 105(3):1509--1519
+\bibitem{davis59} Davis,~P.~J. (1959). Leonhard Euler's Integral: A Historical Profile of the Gamma Function. \textit{Amer. Math. Monthly}. 66(10): 849--869
 
-%Economic
-\bibitem{tarasova17} Tarasova,~V.~V., Tarasov,~V.~E. (2017). Economic Interpretation of Fractional Derivatives. \textit{Progress in Fractional Differentiation and Applications.} 3(1):1--7.
+\bibitem{euler1738} Euler,~L. (1738). De progressionibus transcendentibus seu quarum termini generales algebraice dari nequeunt. \textit{Commentarii academiae scientiarum Petropolitanae}. 36--57.
 
-\bibitem{ackermann12} Ackermann,~E.~R, Grobler,~T.~L., Kleynhans,~W., Olivier,~J.~C., Salmon,~B.~P, van Zyl,~A.~J. (2012). Cavalieri
-Integration. \textit{Quaest. Math.} 35(3): 265–296.
+\bibitem{gomez14} Gomez-Aguilara,~J.~F., Razo-Hernandez,~R., Granados-Lieberman, D.~ A (2014). Physical interpretation of fractional
+calculus in observable terms: analysis of the fractional time constant and the transitory response. \textit{Revista Mexicana de Fisica.} 60: 32--38
 
-\bibitem{parker13} Adam Parker, Who solved the Bernoulli equation and how did they do it? \textit{Coll. Math. J.} \textbf{44} 89--97.
+\bibitem{grobler19} Grobler,~T.~L. (2019). Visualization of the Riemann-Stieltjes integral. \textit{Coll. Math. J.} 50(3): 198--209.
 
@@
 
-\bibitem{munkhammar05} Munkhammar,~J. (2005). Fractional calculus and the Taylor-Riemann series. \textit{Rose-Hulman Undergraduate Mathematics Journal}, 6(1): 6.
+\bibitem{liouville1832} Liouville,~J.
+(1832).
+M\'{e}moire sur l\textquotesingle integration de l\textquotesingle \'{e}quation $(mx^2+nx+p)\frac{d^2y}{dx^2}+(qx+r)\frac{dy}{dx}+sy$ \`{a} l\textquotesingle aide des diff\'{e}rentielles \`{a} indices
+que\textquotesingle conques. \textit{Journal d l\textquotesingle Ecole Polytechnique.} 13(21): 163--186.
 
-\bibitem{grobler19} Grobler,~T.L. (2019). Visualization of the Riemann-Stieltjes integral. \textit{Coll. Math. J.} 50(3): 198--209.
+\bibitem{machado03} Machado,~J.~T. (2003). A probabilistic interpretation of the fractional-order differentiation. \textit{Fract. Calc. Appl. Anal.} 6(1): 73--80.
 
-\bibitem{bartle76} Bartle,~R.~G. (1976). \textit{The Elements of Real Analysis.} New York: Wiley.
+\bibitem{machado14} Machado,~J.~T., Galhano,~A.~M., Trujillo,~J.~J. (2014). On development of fractional calculus during the last fifty years. \textit{Scientometrics}. 98(1): 577-582.
 
-\bibitem{euler1738} Euler,~L. (1738). De progressionibus transcendentibus seu quarum termini generales algebraice dari nequeunt. \textit{Commentarii academiae scientiarum Petropolitanae}. 36--57.
+\bibitem{machado17} Machado,~J.~T., Kiryakova,~V. (2017). The chronicles of fractional calculus. \textit{Fract. Calc. Appl. Anal.} 20(2): 307--336.
 
-\bibitem{hopkins} Brian Hopkins, ed., \textit{Resources for Teaching Discrete Mathematics}, Mathematical Association of America, Washington DC, 2009.
+\bibitem{munkhammar05} Munkhammar,~J. (2005). Fractional calculus and the Taylor-Riemann series. \textit{Rose-Hulman Undergrad. Math. J.}, 6(1): 6.
+
+%physical
+\bibitem{nigmatullin92} Nigmatullin,~R.~R (1992). A fractional integral and its physical interpretation. \textit{Theor. and Math. Phys.} 90(3): 242--251.
+
+\bibitem{podlubny02} Podlubny,~I. (2002). Geometric and Physical Interpretation of Fractional Integration and Fractional Differentiation, \textit{Fract. Calc. Appl. Anal.} 5(4): 367--386.
+
+\bibitem{riemann1876} Riemann,~B.~G.~F (1876). Gesammelte Werke.
+
+\bibitem{ross77} Ross,~B. (1977). The development of fractional calculus 1695--1900. \textit{Hist. Math.} 4(1): 75--89.
+
+\bibitem{ross06} Ross,~B.
+(Ed.).
+(2006).
+\textit{Fractional calculus and its applications: proceedings of the international conference held at the University of New Haven, June 1974}, Vol.
+457, Springer.
+
+\bibitem{rutman95} Rutman,~R.S. (1995). On physical interpretations of fractional integration and differentiation. \textit{Theor. and Math. Phys.} 105(3):1509--1519
+
+ %Probability
+\bibitem{stanislavsky04} Stanislavsky,~A.~A. (2004).  Probability interpretation of the integral of fractional order, \textit{Theor. and Math. Phys.} 138(3): 418--431.
+
+%Geometric
+\bibitem{tarasov16} Tarasov,~V.~E. (2016). Geometric interpretation of fractional-order derivative. \textit{Fract. Calc. Appl. Anal.} 19(5): 1200--1221.
+
+%Economic
+\bibitem{tarasova17} Tarasova,~V.~V., Tarasov,~V.~E. (2017). Economic Interpretation of Fractional Derivatives. \textit{Prog. in Fract. Diff. and Appl.} 3(1):1--7.
+
 \end{thebibliography}

### 2019-05-30 fractional/CMJ style files/article-template.tex
final check in

@@
 construct a Cavalieri sum (see Eq.~\eqref{eq:cav_sum}). Note, the sides of the non-rectangular integration strips we use in this approximation have to be translations of $b_{10}^{\sfrac{4}{5}}(y)$.
-If we take the limit of the aforementioned sum as $n\rightarrow \infty$ we approach $A_{10}^{\sfrac{4}{5}}$.  
+If we take the limit of the aforementioned sum as $n\rightarrow \infty$ we approach the Cavalieri integral in Eq.~\eqref{eq:ex1_specific}, i.e. $A_{10}^{\sfrac{4}{5}}$.  
 Eq.~\eqref{eq:ex1_specific}, therefore, implies that the region $R_{10}^{\sfrac{4}{5}}$ is made up 
-of an infinite number of non-rectangular infinitesimals; all of them being translations of $b_{10}^{\sfrac{4}{5}}(y)$, i.e.
-we can compute $A_{10}^{\sfrac{4}{5}}$ by evaluating the Cavalieri integral found in Eq.~\eqref{eq:ex1_specific}.
+of an infinite number of non-rectangular infinitesimals; all of them being translations of $b_{10}^{\sfrac{4}{5}}(y)$.
 Note, the right-most curve depicted in the right-most panel of Fig.~\ref{fig:geo1} is $b_{10}^{\sfrac{4}{5}}(y)$.

### 2019-05-31 fractional/CMJ style files/article-template.tex
added Cornelia's comments

@@
 The mathematical discipline in which we study the extension of derivatives and integrals to non-integer orders is known as fractional calculus. Euler, Liouville and Riemann laid most 
-of the theoretical groundwork which was needed to develop the field of fractional calculus \cite{davis59,euler1738,liouville1832,riemann1876,laurent1884}.
+of the theoretical groundwork, which was needed to develop the field of fractional calculus \cite{davis59,euler1738,liouville1832,riemann1876,laurent1884}.
 Fractional calculus has now developed into a mature discipline \cite{machado14,machado17}.
@@
 New Haven (USA) (which took place in 1974) it was pointed out that literature lacked an acceptable geometric and physical interpretation of fractional calculus \cite{ross06}.
-Subsequently, the last few decades has seen
+Subsequently, the last few decades have seen
 a number of papers that attempt to rectify this.
-There now exists probabilistic interpretations \cite{stanislavsky04,machado03}, geometric interpretations \cite{adda97,tarasov16,podlubny02}, physical interpretations \cite{cioc16,rutman95, nigmatullin92, gomez14} and economic
+There now exist probabilistic interpretations \cite{stanislavsky04,machado03}, geometric interpretations \cite{adda97,tarasov16,podlubny02}, physical interpretations \cite{cioc16,rutman95, nigmatullin92, gomez14} and economic
 interpretations \cite{tarasova17} of fractional order integrals and differentials.\\
@@
 a Riemann-Stieltjes integral can be converted into a Cavalieri integral \cite{ackermann12,grobler19}.
-Combining these two ideas together results in the following geometric
+Combining these two ideas results in the following geometric
 interpretation: the Riemann-Liouville fractional integral can be interpreted as the area which is obtained by summing together the area of an infinite number of non-rectangular infinitesimals whose shape is determined by the order of integration $\alpha$ and the integration limit $t$.\\
@@
 as such we will try to steer clear from using too many mathematical definitions and proofs. We will rather convey our ideas using as many examples as possible. From the 
-three groups mentioned we believe that the undergraduate student will find this article the most useful. Although undergraduate students have a limited understanding of 
-fractional calculus they generally are quite interested in the subject. This is quite evident from perusing mathematical social media platforms and from surveying 
+three groups mentioned we believe that the undergraduate student will find this article most useful. Although undergraduate students tend to have a limited understanding of 
+fractional calculus they generally are quite interested in the subject. This is evident from perusing mathematical social media platforms and from surveying 
 articles published in undergraduate journals \cite{munkhammar05}.
@@
 We start the paper by reviewing the definition of the Riemann-Stieltjes integral, the Cavalieri integral and the Euler function.
-We then present the definition of the Riemann-Liouville fractional integral.
-We end the paper by presenting our novel geometric interpretation, some examples and a conclusion.
+We then present the definition of the Riemann-Liouville fractional integral and we end the paper by presenting our novel geometric interpretation, some examples and a conclusion.
 
@@
 \caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$.
-The figure also depicts the partition points $x_i^2$ as used in the Cavalieri sum (see Eq.~\ref{eq:cav_sum}).
+The figure also depicts the partition points $x_i^2$ as used in the Cavalieri sum (see Eq.~\eqref{eq:cav_sum}).
 Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
@@
 \centering
-\includegraphics[width=0.75\textwidth]{gamma.pdf}
+\includegraphics[width=0.75\textwidth]{gamma.eps}
 \caption{A plot of $\Gamma(x)$ for $x\in(-5,5)$. $\Gamma(x)$ is not defined for the non-negative integers.}
@@
 \centering
-\includegraphics[width=0.75\textwidth]{gh.pdf}
+\includegraphics[width=0.75\textwidth]{gh.eps}
 \caption{This figure depicts the curves of $g_{10}^{\alpha}(\tau)$ and $h_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}$. The curves associated with $g$ are plotted using 
-solid lines, while the curves plotted with dashed lines are associated with $h$. The lighter the shade with which a curve is depicted, the larger the $\alpha$-value is, that is associated with it.
+solid lines, while the curves plotted with dashed lines are associated with $h$. The lighter the shade with which a curve is depicted, the larger the $\alpha$-value is that is associated with it.
 }
@@
 \centering
-\includegraphics[width=0.75\textwidth]{geo_int1.pdf}
+\includegraphics[width=0.75\textwidth]{geo_int1.eps}
 \caption{The non-static non-rectangular sum-based geometric interpretation of Eq.~\eqref{eq:ex1_raw}.}
@@
 \noindent
-Since Eq.~\ref{eq:ex1}, is a Cavalieri integral it has a known geometric interpretation (see Fig.~\ref{fig:caval2}).
+Since Eq.~\eqref{eq:ex1}, is a Cavalieri integral it has a known geometric interpretation (see Fig.~\ref{fig:caval2}).
 It can be interpreted as the area obtained by summing together the areas of an infinite
@@
 The geometric interpretation of Eq.~\eqref{eq:ex1_raw} is, therefore, non-static as it depends on the value of $\alpha$ and $t$.
-There is one thing, however, which remains unclear: in what way does $\alpha$ and $t$ affect the shape of the aforementioned infinitesimals, i.e.
+There is one thing, however, which remains unclear: in what way do $\alpha$ and $t$ affect the shape of the aforementioned infinitesimals, i.e.
 how does the value of $\alpha$ and $t$ affect the shape of $b_t^{\alpha}(y)$.
@@
 \label{eq:ex1_specific}
-A_{10}^{\sfrac{4}{5}}=\int_{a_{10}^{\frac{4}{5}}(y)}^{b_{10}^{\frac{4}{5}}(y)} f(\tau)~d\tau 
+A_{10}^{\sfrac{4}{5}}=\int_{a_{10}^{\sfrac{4}{5}}(y)}^{b_{10}^{\sfrac{4}{5}}(y)} f(\tau)~d\tau 
 \end{equation}
@@
 The sides of the aforementioned five integration strips are depicted in Fig.~\ref{fig:geo1} using dashed lines.
-Let, $\mathcal{B}_{\mathsf{T}}^{\sfrac{4}{5}}=\{b_{10}^{\frac{4}{5}}(y)-c|c\in(\mathsf{T}-2)\}$ with $\mathsf{T}=\{2,4,6,8,10\}$.\\
+Let, $\mathcal{B}_{\mathsf{T}}^{\sfrac{4}{5}}=\{b_{10}^{\sfrac{4}{5}}(y)-c|c\in(\mathsf{T}-2)\}$ with $\mathsf{T}=\{2,4,6,8,10\}$.\\
 
-%We have thus verified that we can employ the Cavalieri integral in Eq.~\ref{eq:ex1_specific} to compute $A_{10}^{\sfrac{4}{5}}$ from first principles.
+%We have thus verified that we can employ the Cavalieri integral in Eq.~\eqref{eq:ex1_specific} to compute $A_{10}^{\sfrac{4}{5}}$ from first principles.
 %Let $\mathsf{B}_{10}^{\sfrac{4}{5}}$ denote the set containing these dashed curves.
@@
 The regions that are depicted in each of the panels of Fig.~\ref{fig:geo1} were generated by varying $t$, whilst keeping the value of $\alpha$ fixed.
-The title of each panel indicate which $\alpha$-value was used to generate the regions depicted in each panel. The only difference between the regions located in each 
+The title of each panel indicates which $\alpha$-value was used to generate the regions depicted in each panel. The only difference between the regions located in each 
 panel is their right edges. The right edges of the regions in each panel are depicted using varying shades of gray. The lighter the shade with which an edge is depicted, 
-the larger the $t$-value is, that is associated with it.\\
+the larger the $t$-value is that is associated with it.\\
 
@@
 \begin{description}
- \item[Effect of $\alpha$] the gray-tinted solid curves depicted in the different panels of Fig.~\ref{fig:geo1} are not equal to one-another, i.e.
+ \item[Effect of $\alpha$] the gray-tinted solid curves depicted in the different panels of Fig.~\ref{fig:geo1} are not equal to one another, i.e.
 $\mathsf{B}_{\mathsf{T}}^{\alpha_1}\neq\mathsf{B}_{\mathsf{T}}^{\alpha_2}$.
- \item[Effect of $t$] the gray-tinted solid curves depicted in each of the panels of Fig.~\ref{fig:geo1} are not translations of one-another.
-Moreover, the dashed gray curves and the solid gray-tinted curves in the right-most panel are not equal to one-another, i.e.
+ \item[Effect of $t$] the gray-tinted solid curves depicted in each of the panels of Fig.~\ref{fig:geo1} are not translations of one another.
+Moreover, the dashed gray curves and the solid gray-tinted curves in the right-most panel are not equal to one another, i.e.
 $\mathsf{B}_{\mathsf{T}}^{\sfrac{4}{5}}\neq\mathcal{B}_{\mathsf{T}}^{\sfrac{4}{5}}$.
@@
  \rule{0pt}{2.5ex}
- $0.2$ & $\frac{25}{6\Gamma(\frac{1}{5})} t^{\frac{6}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{17}{10})} t^{\frac{7}{10}}$  \\ 
+ $0.2$ & $\frac{25}{6\Gamma(\frac{1}{5})} t^{\sfrac{6}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{17}{10})} t^{\sfrac{7}{10}}$  \\ 
  \rule{0pt}{2.5ex}
- $0.4$ & $\frac{25}{14\Gamma(\frac{2}{5})} t^{\frac{7}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{19}{10})} t^{\frac{9}{10}}$  \\
+ $0.4$ & $\frac{25}{14\Gamma(\frac{2}{5})} t^{\sfrac{7}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{19}{10})} t^{\sfrac{9}{10}}$  \\
  \rule{0pt}{2.5ex}
- $0.6$ & $\frac{25}{24\Gamma(\frac{3}{5})} t^{\frac{8}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{21}{10})} t^{\frac{11}{10}}$  \\ 
+ $0.6$ & $\frac{25}{24\Gamma(\frac{3}{5})} t^{\sfrac{8}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{21}{10})} t^{\sfrac{11}{10}}$  \\ 
  \rule{0pt}{2.5ex}
- $0.8$ & $\frac{25}{36\Gamma(\frac{4}{5})} t^{\frac{9}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{23}{10})} t^{\frac{13}{10}}$  \\ 
+ $0.8$ & $\frac{25}{36\Gamma(\frac{4}{5})} t^{\sfrac{9}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{23}{10})} t^{\sfrac{13}{10}}$  \\ 
  \rule{0pt}{2.5ex}
- $1$ & $\frac{1}{2}t^2$  & $\frac{2}{3}t^{\frac{3}{2}}$  \\ [1ex]
+ $1$ & $\frac{1}{2}t^2$  & $\frac{2}{3}t^{\sfrac{3}{2}}$  \\ [1ex]
  \hline
@@
 \centering
-\includegraphics[width=0.75\textwidth]{func_eval1.pdf}
+\includegraphics[width=0.75\textwidth]{func_eval1.eps}
 \caption{Depicts the curves which are obtained by evaluating Eq.~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ using either Eq.~\eqref{eq:rs} or Eq.~\eqref{eq:option2}.}
@@
 \noindent
-Let us know consider a different fractional integral:
+Let us now consider a different fractional integral:
 \begin{equation}
@@
 \centering
-\includegraphics[width=0.75\textwidth]{geo_int2.pdf}
+\includegraphics[width=0.75\textwidth]{geo_int2.eps}
 \caption{The non-static non-rectangular sum-based geometric interpretation of Eq.~\eqref{eq:ex2}.}
@@
 \centering
-\includegraphics[width=0.75\textwidth]{func_eval2.pdf}
+\includegraphics[width=0.75\textwidth]{func_eval2.eps}
 \caption{Depicts the curves which are obtained by evaluating Eq.~\eqref{eq:ex2} for all $\alpha\in \mathsf{A}$ using either Eq.~\eqref{eq:rs} or Eq.~\eqref{eq:option2}.}
@@
 
-%the fractional integral in Eq.~\ref{??} can be interpreted as the area which is obtained by summing together the area associated with an infinite number of non-rectangular infinitesimals whose shape 
+%the fractional integral in Eq.~\eqref{??} can be interpreted as the area which is obtained by summing together the area associated with an infinite number of non-rectangular infinitesimals whose shape
 %is determined by the integration limits of the Cavalieri integral. Note that neither $g_t^{\alpha}(\tau)$ nor $a_t^{\alpha}(y)$ are static functions, 

### 2019-07-02 Cav2D/func_plotter.py
main definitions of Cav integral writtten down

@@ -1,0 +1,578 @@
+import numpy as np
+import scipy as sp
+import pylab as plt
+import math
+
+from mpl_toolkits import mplot3d
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+#from scipy.stats import gamma
+
+#def func_ex1(x):
+#    y = (2*x+8)**3
+#    return y
+
+#def a_ex1(y):
+#    x = -0.25*y**(2.0/3.0) + 9.0/2.0*y**(1.0/3.0) - 19
+#    return x
+
+#def a_ex2(y):
+#    x = -0.25*y**(2.0/3.0) + 9.0/2.0*y**(1.0/3.0) - 11
+#    return x
+
+def a1(y,alpha,t,b):
+    x = y - 1.0/math.gamma(alpha+1)*(t**alpha - (t-y)**alpha)
+    return x+b
+
+def g1(x,alpha,t):
+    return 1.0/math.gamma(alpha+1)*(t**alpha-(t-x)**alpha)
+
+
+def g_func(tau,alpha,t):
+    return (1.0/math.gamma(alpha+1))*(t**alpha-(t-tau)**alpha)
+
+def h_func(tau,alpha,t):
+    return t - (t**alpha-math.gamma(alpha+1)*tau)**(1.0/alpha)
+
+def a_func(y,alpha,t,f_inv):
+    return f_inv(y) - (1.0/math.gamma(alpha+1))*(t**alpha - (t-f_inv(y))**alpha)
+
+def f1(x):
+    return x
+
+def f1_inv(y):
+    return (y);
+
+def f2(x):
+    return np.sqrt(x)
+
+def f2_inv(y):
+    return y**2
+
+def plt_gh_functions(alpha = np.array([0.2,0.4,0.6,0.8,1.0]),t=10,num=1000):
+    tau = np.linspace(0,t,num)
+    #[0.125,0.25,0.375,0.5,0.625,0.75,0.875,1.0]
+    v = np.linspace(0,1.5,len(alpha))
+
+    for k in range(len(alpha)):
+        tau2 = np.linspace(0,(t**alpha[k])/math.gamma(alpha[k]+1),num)
+        y1 = g_func(tau,alpha[k],t)
+        y2 = h_func(tau2,alpha[k],t)
+        col = [v[k]/2,v[k]/2,v[k]/2]    
+        plt.plot(tau,y1,color=col)
[…]

### 2019-07-03 Cav2D/func_plotter.py
made progress with 3d plotting

@@ -5,574 +5,243 @@ import math
 
 from mpl_toolkits import mplot3d
 
+from mpl_toolkits.mplot3d.art3d import Poly3DCollection, Line3DCollection
+from mpl_toolkits.mplot3d import Axes3D
+
 import numpy as np
 import matplotlib.pyplot as plt
 
-#from scipy.stats import gamma
+def point_plot():
+    # create x,y
+    xx, yy = np.meshgrid(range(3), range(3))
 
-#def func_ex1(x):
-#    y = (2*x+8)**3
-#    return y
+    # calculate corresponding z
+    z = 0.5 * xx
 
-#def a_ex1(y):
-#    x = -0.25*y**(2.0/3.0) + 9.0/2.0*y**(1.0/3.0) - 19
-#    return x
+    plt3d = plt.figure().gca(projection='3d')
+    # plot the surface
+    plt3d.plot_surface(xx, yy, z, alpha=0.2)
 
-#def a_ex2(y):
-#    x = -0.25*y**(2.0/3.0) + 9.0/2.0*y**(1.0/3.0) - 11
-#    return x
+    # calculate corresponding z
+    z = yy
 
-def a1(y,alpha,t,b):
-    x = y - 1.0/math.gamma(alpha+1)*(t**alpha - (t-y)**alpha)
-    return x+b
+    # plot the surface
+    plt3d.plot_surface(xx, yy, z, alpha=0.2)
+    #plt.show()
 
-def g1(x,alpha,t):
-    return 1.0/math.gamma(alpha+1)*(t**alpha-(t-x)**alpha)
+    # calculate corresponding z
+    z = -1*yy -1*xx + 4
+    # plot the surface
+    plt3d.plot_surface(xx, yy, z, alpha=0.2)
+ 
 
+    ax = plt.gca()
+    ax.hold(True)
 
-def g_func(tau,alpha,t):
-    return (1.0/math.gamma(alpha+1))*(t**alpha-(t-tau)**alpha)
+    coordinates = np.array([[0,0,0],[1,0,0],[0,1,0],[1,1,0],[0,0,1],[1,0,1],[0,1,1],[1,1,1]])   
+    print(coordinates.shape)
+    #ax.scatter3D(coordinates[:,0], coordinates[:,1], coordinates[:,2],c="r"); 
+    #plt.show()
 
-def h_func(tau,alpha,t):
[…]

### 2019-07-09 Cav2D/func_plotter.py
started adding letters to plot

@@ -73,7 +73,7 @@ def point_plot():
     #plt.show()
 
 
-def create_xy_1(a=0,b=4,c=0,d=4,Nx = 5,Ny = 5):
+def create_xy_1(a=0,b=4,c=0,d=4,Nx = 10,Ny = 10):
     x = np.linspace(a,b,Nx)
     y = np.linspace(c,d,Ny)
     xx,yy = np.meshgrid(x,y)
@@ -89,7 +89,7 @@ def x_2_func_line(x,y,a,c,A,C,K):
     y2 = (y-c)*T2 - (x-a)*PC_inv + K*PC_inv
     return x2,y2
 
-def create_xy_2_line(xx, yy,a=0.0, c=0.0, A=0.5, C=1.0, K = 8):
+def create_xy_2_line(xx, yy,a=0.0, c=0.0, A=2, C=1.0, K = 8):
     xx2 = np.zeros(xx.shape,dtype=float)
     yy2 = np.zeros(yy.shape,dtype=float)
     #print(xx2)
@@ -115,11 +115,50 @@ def test(xx,yy,xx2,yy2,zz2,K=8):
 
     ax = plt.gca()
     ax.hold(True)
-    ax.scatter3D(xx2.flatten(), yy2.flatten(), zz2.flatten() ,c="b",alpha=0.2); 
-    ax.scatter3D(xx.flatten(), yy.flatten(), np.zeros((len(yy.flatten()),),dtype=float) ,c="r",alpha=0.2); 
+    #ax.scatter3D(xx2.flatten(), yy2.flatten(), zz2.flatten() ,c="b",alpha=0.2); 
+    #ax.scatter3D(xx.flatten(), yy.flatten(), np.zeros((len(yy.flatten()),),dtype=float) ,c="r",alpha=0.2); 
 
     delta_x = yy[1,0] - yy[0,0]
     delta_y = xx[0,1] - xx[0,0]
+
+
+    volume = np.zeros((8,3),dtype=float)
+
+    volume[0,0] = xx[0,0]
+    volume[0,1] = yy[0,0]
+    volume[1,0] = xx[0,-1]
+    volume[1,1] = yy[0,-1]
+    volume[2,0] = xx[-1,0]
+    volume[2,1] = yy[-1,0]
+    volume[3,0] = xx[-1,-1]
+    volume[3,1] = yy[-1,-1]
+
+    volume[4,0] = xx2[0,0]
[…]

### 2019-07-09 Cav2D/func_plotter.py
added table of double integrals

@@ -272,7 +272,8 @@ def test(xx,yy,xx2,yy2,zz2,K=8):
     ax.plot(np.array([volume[3,0],volume[7,0]]), np.array([volume[3,1],volume[7,1]]), 'black') 
     ax.plot(np.array([volume[1,0],volume[5,0]]), np.array([volume[1,1],volume[5,1]]), 'black') 
     ax.plot(np.array([4.0/3.0,4.0/3.0]), np.array([16.0/3.0,8.0/3.0]), 'black',ls="-.") 
-    ax.plot(np.array([1.6,1.6]), np.array([4,3.2]), 'black',ls="-.") 
+    ax.plot(np.array([1.6,1.6]), np.array([4,0]), 'black',ls="-.") 
+    ax.plot(np.array([0.8,0.8]), np.array([5.6,4]), 'black',ls="-.") 
     
 
 
@@ -280,9 +281,19 @@ def test(xx,yy,xx2,yy2,zz2,K=8):
     ax.annotate('B', xy=(4, 0), xytext=(4+0.06, -0.12))
     ax.annotate('C', xy=(0, 4), xytext=(-0.12, 4))
     ax.annotate('D', xy=(4, 4), xytext=(4+0.03, 4))
-    ax.annotate('E', xy=(1.6, 3.2), xytext=(1.6, 3.2-0.3))
+    ax.annotate('E', xy=(1.6, 3.2), xytext=(1.6+0.01, 3.2-0.31))
     ax.annotate('F', xy=(4.8, 1.6), xytext=(4.8+0.03, 1.6))
     ax.annotate('G', xy=(0.8, 5.6), xytext=(0.8, 5.6+0.03))
+    ax.annotate('H', xy=(4.0/3.0, 16.0/3.0), xytext=(4.0/3.0, 16.0/3.0+0.03))
+    ax.annotate('I', xy=(4.0/3.0, 4), xytext=(4.0/3.0+0.03, 4+0.04))
+    ax.annotate('J', xy=(4.0/3.0, 8.0/3.0), xytext=(4.0/3.0+0.06, 8.0/3.0-0.04))
+    ax.annotate('K', xy=(1.6, 4), xytext=(1.6, 4+0.04))
+    ax.annotate('L', xy=(4, 2), xytext=(4, 2+0.04))
+    ax.annotate('M', xy=(1.6, 0), xytext=(1.6+0.01, 0+0.05))
[…]

### 2019-07-09 Cav2D/func_plotter.py
completed volume equals check

@@ -81,10 +81,15 @@ def create_xy_1(a=0,b=4,c=0,d=4,Nx = 10,Ny = 10):
 
 def x_2_func_line(x,y,a,c,A,C,K):
     P = 1 + ((A+C)/(A*C))
+    print("P = "+str(P))
     T1 = (P*A-1)/(P*A)
+    print("T1 = "+str(T1))
     T2 = (P*C-1)/(P*C)
+    print("T2 = "+str(T2)) 
     PA_inv = 1.0/(P*A)
     PC_inv = 1.0/(P*C)
+    print("PA_inv = "+str(PA_inv))
+    print("PC_inv = "+str(PC_inv))
     x2 = (x-a)*T1 - (y-c)*PA_inv + K*PA_inv
     y2 = (y-c)*T2 - (x-a)*PC_inv + K*PC_inv
     return x2,y2
@@ -293,6 +298,9 @@ def test(xx,yy,xx2,yy2,zz2,K=8):
     ax.annotate('N', xy=(0.8, 4), xytext=(0.8, 4-0.3))
     ax.set_xlabel("$x$")
     ax.set_ylabel("$y$")
+
+    v = np.array([2.73067,8.256,0.5333333,3.95062,0.505679,0.293926,5.952,0.5333333,0.341333,0.606815,0.316049,1.58025])
+    print(np.sum(v))
 
 
     #x1 = np.linspace(0,2,200)

### 2019-07-10 Cav2D/func_plotter.py
cleaned up the code a bit

@@ -108,7 +108,11 @@ def func_p(xx2,yy2,K=8):
     zz2 = -xx2-yy2 + K
     return zz2
 
-def test(xx,yy,xx2,yy2,zz2,K=8):
+def plot_figures(xx,yy,xx2,yy2,zz2,K=8):
+    
+
+    #PLOT PLANE
+    ############################################################
     # create x,y
     xx_new, yy_new = np.meshgrid(range(7), range(7))
 
@@ -120,13 +124,13 @@ def test(xx,yy,xx2,yy2,zz2,K=8):
 
     ax = plt.gca()
     ax.hold(True)
+    ############################################################
+    
     #ax.scatter3D(xx2.flatten(), yy2.flatten(), zz2.flatten() ,c="b",alpha=0.2); 
     #ax.scatter3D(xx.flatten(), yy.flatten(), np.zeros((len(yy.flatten()),),dtype=float) ,c="r",alpha=0.2); 
-
-    delta_x = yy[1,0] - yy[0,0]
-    delta_y = xx[0,1] - xx[0,0]
-
-
+    
+    #PLOT VOLUME
+    ############################################################
     volume = np.zeros((8,3),dtype=float)
 
     volume[0,0] = xx[0,0]
@@ -163,104 +167,69 @@ def test(xx,yy,xx2,yy2,zz2,K=8):
     ax.plot3D(np.array([volume[2,0],volume[6,0]]), np.array([volume[2,1],volume[6,1]]), np.array([volume[2,2],volume[6,2]]), 'black') 
     ax.plot3D(np.array([volume[3,0],volume[7,0]]), np.array([volume[3,1],volume[7,1]]), np.array([volume[3,2],volume[7,2]]), 'black') 
     ax.plot3D(np.array([volume[1,0],volume[5,0]]), np.array([volume[1,1],volume[5,1]]), np.array([volume[1,2],volume[5,2]]), 'black') 
+    ############################################################
                           
-
-    print(delta_x)
-    print(delta_y)
-
-    #z_order = xx.shape[0]*zz.shape[1]
-
-    t1 = range(xx.shape[0])
-    t2 = range(yy.shape[1])
-    t1 = t1[::-1]
-    t2 = t2[::-1]
-
-    for j in range(1,2):
-        for i in range(4,5):
-
-            four_points_1 = np.zeros((4,3),dtype=float)
-            four_points_2 = np.zeros((4,3),dtype=float)
+    
+    #DRAW INTEGRATION STRIP
[…]

### 2019-07-11 Cav2D/func_plotter.py
tested translation of parametric curves

@@ -277,10 +277,29 @@ def plot_figures(xx,yy,xx2,yy2,zz2,K=8):
 
     ############################################################
     
+def plot_parametric_test():
+    plt3d = plt.figure().gca(projection='3d')
+    t = np.linspace(1,10,100)
+    x = -2*t
+    y = t
+    z = 4*t**2-4
+
+    ax = plt.gca()
+    ax.hold(True)
+    ax.plot3D(x, y, z, 'black')
+    ax.plot3D((x+2)+10,(y-1)+10,z,'red')
+    ax.scatter3D(-2,1,0)
+    ax.scatter3D(10,10,0)
+    plt.xlabel('x')
+    plt.ylabel('y')
+    plt.show() 
+     
     
  
 
 if __name__ == "__main__":
+   plot_parametric_test()
+
    xx,yy = create_xy_1()
    print(xx)
    print(yy)
@@ -292,16 +311,27 @@ if __name__ == "__main__":
 
    plot_figures(xx,yy,xx2,yy2,zz2)
   
+   
+   #PLOTS THE DOTS (CREATE FILLED POLYGONS)???
    for i in range(xx.shape[0]):
        for j in range(yy.shape[1]):
            plt.plot(xx[i,j],yy[i,j],"bo")
            plt.plot(xx2[i,j],yy2[i,j],"ro")
 
+   x = np.array([xx[0,0],xx[0,-1],xx[-1,-1],xx[-1,0]])
+   y = np.array([yy[0,0],yy[0,-1],yy[-1,-1],yy[-1,0]])
+   x2 = np.array([xx2[0,0],xx2[0,-1],xx2[-1,-1],xx2[-1,0]])
+   y2 = np.array([yy2[0,0],yy2[0,-1],yy2[-1,-1],yy2[-1,0]])
    plt.show()
+   #plt.figure(figsize=(8, 8))
+   #plt.axis('equal')
+   plt.fill(x, y,"b",x2,y2,"r",alpha=0.2,edgecolor='black', linewidth=3)
+   plt.xlim(0,5.1)
+   plt.xlabel("$x$")
+   plt.ylabel("$y$")
+   plt.show() 
 
-   #point_plot()
-   
-   
+  
 
 
 

### 2019-07-12 Cav2D/func_plotter.py
started adding second example code

@@ -285,7 +285,7 @@ def plot_parametric_test():
     z = 4*t**2-4
 
     ax = plt.gca()
-    ax.hold(True)
+    ax.hold(True) 
     ax.plot3D(x, y, z, 'black')
     ax.plot3D((x+2)+10,(y-1)+10,z,'red')
     ax.scatter3D(-2,1,0)
@@ -294,12 +294,62 @@ def plot_parametric_test():
     plt.ylabel('y')
     plt.show() 
      
+def plot_parametric_test2():
+    plt3d = plt.figure().gca(projection='3d')
+    t = np.linspace(0,10,200)
+    x = t
+    y = t
+    z = np.sqrt(t)
+
+    ax = plt.gca()
+    ax.hold(True)
+    ax.plot3D(x, y, z, 'black')
+    #ax.plot3D((x+2)+10,(y-1)+10,z,'red')
+    #ax.scatter3D(-2,1,0)
+    #ax.scatter3D(10,10,0)
+    plt.xlabel('x')
+    plt.ylabel('y')
+    plt.show() 
+
+def create_xy_2_sphere(xx,yy,p=True):
+
+    xx2 = np.zeros(xx.shape,dtype=float)
+    yy2 = np.zeros(xx.shape,dtype=float)
+
+    for k in range(xx.shape[0]):
+        for j in range(xx.shape[1]):
+            K = -4*xx[k,j]**2 + 8*xx[k,j]*yy[k,j] + 4*xx[k,j] - 4*yy[k,j]**2+4*yy[k,j] + 33
+            if p:
+               t = 0.25*(-2*xx[k,j]-2*yy[k,j] - 1 + np.sqrt(K)) 
+            else:
+               t = 0.25*(-2*xx[k,j]-2*yy[k,j] - 1 - np.sqrt(K)) 
+            xx2[k,j] = xx[k,j] + t
+            yy2[k,j] = yy[k,j] + t
     
- 
+    return xx2,yy2   
+
 
 if __name__ == "__main__":
-   plot_parametric_test()
+   xx,yy = create_xy_1(Nx = 10,Ny = 10,b=1,d=1)
+   xx2,yy2 = create_xy_2_sphere(xx,yy,p=True)
+   for i in range(xx.shape[0]):
+       for j in range(yy.shape[1]):
+           plt.plot(xx[i,j],yy[i,j],"bo")
[…]

### 2019-07-12 Cav2D/func_plotter.py
added a lot of the 3D plotting

@@ -120,7 +120,9 @@ def plot_figures(xx,yy,xx2,yy2,zz2,K=8):
     z = -1*yy_new -1*xx_new + K
 
     plt3d = plt.figure().gca(projection='3d')
-    plt3d.plot_surface(xx_new, yy_new, z, alpha=0.2)
+    plt3d.plot_surface(xx2, yy2, zz2, alpha=0.2)
+
+    #plt3d.plot_surface(xx_new, yy_new, z, alpha=0.2)
 
     ax = plt.gca()
     ax.hold(True)
@@ -315,6 +317,7 @@ def create_xy_2_sphere(xx,yy,p=True):
 
     xx2 = np.zeros(xx.shape,dtype=float)
     yy2 = np.zeros(xx.shape,dtype=float)
+    t_m = np.zeros(xx.shape,dtype=float)
 
     for k in range(xx.shape[0]):
         for j in range(xx.shape[1]):
@@ -323,15 +326,245 @@ def create_xy_2_sphere(xx,yy,p=True):
                t = 0.25*(-2*xx[k,j]-2*yy[k,j] - 1 + np.sqrt(K)) 
             else:
                t = 0.25*(-2*xx[k,j]-2*yy[k,j] - 1 - np.sqrt(K)) 
+            t_m[k,j] = t
             xx2[k,j] = xx[k,j] + t
             yy2[k,j] = yy[k,j] + t
     
-    return xx2,yy2   
+    return xx2,yy2,t_m   
+
+def plot_volume2(xx,yy,xx2,yy2,t):
+    
+
+    #PLOT PLANE
+    ############################################################
+    # create x,y
+    #xx_new, yy_new = np.meshgrid(np.linspace(0,4,200), np.linspace(0,4,200))
+
+    # calculate corresponding z
+    z = np.sqrt(-xx2**2-yy2**2+4)
+
+    plt3d = plt.figure().gca(projection='3d')
+    plt3d.plot_surface(xx2, yy2, z, alpha=0.2)
+
+    ax = plt.gca()
+    ax.hold(True)
+
+    n = np.array([0,-1])
+
+    x_v = np.zeros((4,),dtype=float)
+    y_v = np.zeros((4,),dtype=float)
+
+    c = 0
+
+    for k in n:
+        for j in n:
+
+            t_max = t[k,j]
+            t_v = np.linspace(0,t_max,200)
+
+            x = xx[k,j] + t_v
+            y = yy[k,j] + t_v 
[…]

### 2019-07-15 Cav2D/func_plotter.py
added red line and started adding letters to region plot

@@ -354,6 +354,13 @@ def plot_volume2(xx,yy,xx2,yy2,t):
     x_v = np.zeros((4,),dtype=float)
     y_v = np.zeros((4,),dtype=float)
 
+    t_max = t[t.shape[0]/2,t.shape[0]/2]
+    t_v = np.linspace(0,t_max,200)
+    x = xx[t.shape[0]/2,t.shape[0]/2] + t_v
+    y = yy[t.shape[0]/2,t.shape[0]/2] + t_v 
+    z = 0 + np.sqrt(t_v)
+    ax.plot3D(x,y,z,"red")        
+
     c = 0
 
     for k in n:
@@ -399,15 +406,64 @@ def plot_volume2(xx,yy,xx2,yy2,t):
 
     ax.plot3D(np.array([0,0]),np.array([0,1]),np.array([0,0]),"black") 
     ax.plot3D(np.array([0,1]),np.array([0,0]),np.array([0,0]),"black") 
-    ax.plot3D(np.array([1,1]),np.array([1,0]),np.array([0,0]),"black") 
-    ax.plot3D(np.array([1,0]),np.array([1,1]),np.array([0,0]),"black") 
+    ax.plot3D(np.array([1,1]),np.array([1,0]),np.array([0,0]),"black",ls="--") 
+    ax.plot3D(np.array([1,0]),np.array([1,1]),np.array([0,0]),"black",ls="--") 
     #ax.plot3D(np.array([1,0]),np.array([1,1]),np.array([0,0]),"black") 
     #ax.plot3D(np.array([0,1]),np.array([1,1]),np.array([0,0]),"black")
     #print(xx[k,j])
     #plt.zlim(0,2)
     plt.show()
     ############################################################
+    fig = plt.figure()
+    ax = fig.add_subplot(111)
+
+    for k in range(4):
+        if k == 0:
+           x = np.linspace(x_v[2],x_v[0],100)
+           y = np.sqrt(-x**2 -x+4)
+        elif k == 1:
+           x = np.linspace(x_v[0],x_v[1],100)
+           y = 0.5*(np.sqrt(17-4*x**2)-1)
+        elif k == 2:
+           x = np.linspace(x_v[3],x_v[1],100)
+           y = np.sqrt(-x**2-(x-1)+4)
[…]

### 2019-07-15 Cav2D/func_plotter.py
added letters to sphere plot

@@ -458,6 +458,13 @@ def plot_volume2(xx,yy,xx2,yy2,t):
 
     ax.annotate('I', xy=(x_v[2], 1), xytext=(x_v[2], 1-0.07))
 
+    ax.annotate('J', xy=(1, 0.5*(np.sqrt(21-4*1**2)-1)), xytext=(1, 0.5*(np.sqrt(21-4*1**2)-1)+0.03))
+    ax.annotate('K', xy=(1, np.sqrt(-1**2 -1+4)), xytext=(1+0.01, np.sqrt(-1**2 -1+4)+0.01))
+    ax.annotate('L', xy=(x_v[0], 0.5*(np.sqrt(21-4*x_v[0]**2)-1)), xytext=(x_v[0], 0.5*(np.sqrt(21-4*x_v[0]**2)-1)+0.03))
+    ax.annotate('M', xy=(x_v[0], x_v[0]-1), xytext=(x_v[0], x_v[0]-1-0.06))
+    ax.annotate('N', xy=(x_v[3], 0.5*(np.sqrt(17-4*x_v[3]**2)-1)), xytext=(x_v[3]+0.01, 0.5*(np.sqrt(17-4*x_v[3]**2)-1)))
+    #ax.annotate('K', xy=(1, 1), xytext=(x_v[2], 1-0.07))
+
     ax.set_xlabel("$x$")
     ax.set_ylabel("$y$")
     

### 2019-07-15 Cav2D/func_plotter.py
added filled region code

@@ -408,6 +408,10 @@ def plot_volume2(xx,yy,xx2,yy2,t):
     ax.plot3D(np.array([0,1]),np.array([0,0]),np.array([0,0]),"black") 
     ax.plot3D(np.array([1,1]),np.array([1,0]),np.array([0,0]),"black",ls="--") 
     ax.plot3D(np.array([1,0]),np.array([1,1]),np.array([0,0]),"black",ls="--") 
+    ax.set_xlabel("$x$")
+    ax.set_ylabel("$y$")
+    ax.set_zlabel("$z$")
+    
     #ax.plot3D(np.array([1,0]),np.array([1,1]),np.array([0,0]),"black") 
     #ax.plot3D(np.array([0,1]),np.array([1,1]),np.array([0,0]),"black")
     #print(xx[k,j])
@@ -473,7 +477,37 @@ def plot_volume2(xx,yy,xx2,yy2,t):
 
     #ax.scatter3D(xx2.flatten(), yy2.flatten(), zz2.flatten() ,c="b",alpha=0.2); 
     #ax.scatter3D(xx.flatten(), yy.flatten(), np.zeros((len(yy.flatten()),),dtype=float) ,c="r",alpha=0.2); 
+       
+    x = np.linspace(x_v[2],x_v[1],100)
+    y1 = np.zeros((100,),dtype=float)
+    y2 = np.zeros((100,),dtype=float)
+
+    for k in range(len(x)):
+        if (x[k]>x_v[0]):
+           y1[k] = 0.5*(np.sqrt(17-4*x[k]**2)-1)
+        else:
+           y1[k] = np.sqrt(-x[k]**2 -x[k]+4)
+
+        if (x[k]>x_v[3]):
+           y2[k] = np.sqrt(-x[k]**2-(x[k]-1)+4)
+        else:
+           y2[k] = 0.5*(np.sqrt(21-4*x[k]**2)-1)
+
+    plt.fill_between(x, y1, y2, color='red',alpha=0.2)
+    plt.plot(x,y1,"black",alpha=0.2,linewidth=3)
+    plt.plot(x,y2,"black",alpha=0.2,linewidth=3)
     
+    x = np.array([xx[0,0],xx[0,-1],xx[-1,-1],xx[-1,0]])
+    y = np.array([yy[0,0],yy[0,-1],yy[-1,-1],yy[-1,0]])
[…]

### 2019-07-16 Cav2D/func_plotter.py
fixed proj sphere

@@ -447,7 +447,7 @@ def plot_volume2(xx,yy,xx2,yy2,t):
     ax.plot(np.array([1,x_v[1]]),np.array([0,y_v[1]]),"black")
 
     ax.plot(np.array([x_v[2],x_v[2]]),np.array([y_v[2],1]),"black",ls = "-.")
-    ax.plot(np.array([1,1]),np.array([1,0.5*(np.sqrt(21-4*1**2)-1)]),"black",ls = "-.")
+    ax.plot(np.array([1,1]),np.array([1,np.sqrt(-1**2 -1+4)]),"black",ls = "-.")
     ax.plot(np.array([x_v[0],x_v[0]]),np.array([x_v[0]-1,0.5*(np.sqrt(21-4*x_v[0]**2)-1)]),"black",ls = "-.")
     ax.plot(np.array([x_v[3],x_v[3]]),np.array([y_v[3],0.5*(np.sqrt(17-4*x_v[3]**2)-1)]),"black",ls = "-.")
 
@@ -462,16 +462,17 @@ def plot_volume2(xx,yy,xx2,yy2,t):
 
     ax.annotate('I', xy=(x_v[2], 1), xytext=(x_v[2], 1-0.07))
 
-    ax.annotate('J', xy=(1, 0.5*(np.sqrt(21-4*1**2)-1)), xytext=(1, 0.5*(np.sqrt(21-4*1**2)-1)+0.03))
-    ax.annotate('K', xy=(1, np.sqrt(-1**2 -1+4)), xytext=(1+0.01, np.sqrt(-1**2 -1+4)+0.01))
-    ax.annotate('L', xy=(x_v[0], 0.5*(np.sqrt(21-4*x_v[0]**2)-1)), xytext=(x_v[0], 0.5*(np.sqrt(21-4*x_v[0]**2)-1)+0.03))
-    ax.annotate('M', xy=(x_v[0], x_v[0]-1), xytext=(x_v[0], x_v[0]-1-0.06))
-    ax.annotate('N', xy=(x_v[3], 0.5*(np.sqrt(17-4*x_v[3]**2)-1)), xytext=(x_v[3]+0.01, 0.5*(np.sqrt(17-4*x_v[3]**2)-1)))
[…]

### 2019-07-16 Cav2D/func_plotter.py
computed volume

@@ -507,6 +507,10 @@ def plot_volume2(xx,yy,xx2,yy2,t):
     plt.ylabel("$y$")
     plt.show()
 
+    volume_v = np.array([0.266667,0.0844182,0.0625933,0.266667,0.0519962,0.071572,0.0234433,0.0128692,0.00547412,0.00547412,0.00921532,0.00912802])
+
+    print("v = "+str(np.sum(volume_v)))
+    #v = 0.8695177800000001
    
 
     

### 2019-07-17 Cav2D/func_plotter.py
added second example to latex

@@ -464,9 +464,12 @@ def plot_volume2(xx,yy,xx2,yy2,t):
 
     #ax.annotate('J', xy=(1, 0.5*(np.sqrt(21-4*1**2)-1)), xytext=(1, 0.5*(np.sqrt(21-4*1**2)-1)+0.03))
     ax.annotate('J', xy=(1, np.sqrt(-1**2 -1+4)), xytext=(1+0.01, np.sqrt(-1**2 -1+4)+0.01))
+    print("J = ",str(np.sqrt(-1**2 -1+4)))
     ax.annotate('K', xy=(x_v[0], 0.5*(np.sqrt(21-4*x_v[0]**2)-1)), xytext=(x_v[0], 0.5*(np.sqrt(21-4*x_v[0]**2)-1)+0.03))
+    print("K = ",str(0.5*(np.sqrt(21-4*x_v[0]**2)-1)))
     ax.annotate('L', xy=(x_v[0], x_v[0]-1), xytext=(x_v[0], x_v[0]-1-0.06))
     ax.annotate('M', xy=(x_v[3], 0.5*(np.sqrt(17-4*x_v[3]**2)-1)), xytext=(x_v[3]+0.01, 0.5*(np.sqrt(17-4*x_v[3]**2)-1)))
+    print("M = ",str(0.5*(np.sqrt(17-4*x_v[3]**2)-1)))
     #ax.annotate('K', xy=(1, 1), xytext=(x_v[2], 1-0.07))
 
     ax.set_xlabel("$x$")
@@ -507,7 +510,7 @@ def plot_volume2(xx,yy,xx2,yy2,t):
     plt.ylabel("$y$")
     plt.show()
 
-    volume_v = np.array([0.266667,0.0844182,0.0625933,0.266667,0.0519962,0.071572,0.0234433,0.0128692,0.00547412,0.00547412,0.00921532,0.00912802])
+    volume_v = np.array([0.2666667,0.0844182,0.0625933,0.2666667,0.0519962,0.071572,0.0234433,0.0128692,0.00547412,0.00921532,0.00912802])
 
     print("v = "+str(np.sum(volume_v)))
     #v = 0.8695177800000001

### 2019-07-19 Cav2D/article-template.tex
started the journal paper

--- 2019-05-30 fractional/CMJ style files/article-template.tex
@@
 
-\title{Visualization of the Riemann-Liouville Fractional Integral}
+\title{Computing volume via non-linear rectangular prisms}
 %\author{Woodrow Wilson and Herbert Hoover} %%leave blank in initial submission to allow for double blind reviewing
@@
 \noindent
-Leibniz, who is regarded by many scholars as the father of calculus, is credited with inventing the following notation: $\frac{d^n y}{d x^n}$. 
-A natural question which arises when one inspects this notation is: Can $n$ be a non-integer value? L'Hospital phrased it differently: ``\emph{What if $n$ be a $\frac{1}{2}$?}''. 
-In a letter Leibniz sent to L'Hospital, Leibniz comments on L'Hospital's question by making the following prophetic remark: ``\emph{This is an apparent paradox from which, one day, useful 
-consequences will be drawn}'' \cite{ross77,machado14,machado17}.\\
 
-\noindent
-The mathematical discipline in which we study the extension of derivatives and integrals to non-integer orders is known as fractional calculus. Euler, Liouville and Riemann laid most 
-of the theoretical groundwork which was needed to develop the field of fractional calculus \cite{davis59,euler1738,liouville1832,riemann1876,laurent1884}.
-Fractional calculus has now developed into a mature discipline \cite{machado14,machado17}.
-However, there is one aspect of the discipline which only started to develop fairly recently: its physical and geometric interpretability.
-At the first international conference on fractional calculus in
-New Haven (USA) (which took place in 1974) it was pointed out that literature lacked an acceptable geometric and physical interpretation of fractional calculus \cite{ross06}.
-Subsequently, the last few decades has seen
-a number of papers that attempt to rectify this.
-There now exists probabilistic interpretations \cite{stanislavsky04,machado03}, geometric interpretations \cite{adda97,tarasov16,podlubny02}, physical interpretations \cite{cioc16,rutman95, nigmatullin92, gomez14} and economic
-interpretations \cite{tarasova17} of fractional order integrals and differentials.\\
-
-\noindent
-In this article we specifically focus on the geometric interpretation of fractional integrals.
-To be more specific, we present a novel geometric interpretation of the Riemann-Liouville fractional integral based at 0 \cite{laurent1884}.
-As we mentioned earlier, Riemann and Liouville played an important role in the development of fractional calculus. Their work was crucial in defining what is now known as 
-the Riemann-Liouville fractional integral \cite{laurent1884}.
-At this point in time the reader should be made aware of the fact that there exists many other accepted fractional integral definitions in the literature.
-We, however, deem these definitions to be beyond the scope of the current article and as such we do not discuss them any further in this work. Furthermore, the geometric interpretation 
-we present here is an extension of the geometric interpretation presented by Podlubny \cite{podlubny02}. Podlubny showed that a Riemann-Liouville fractional integral 
-can be converted into a Riemann-Stieltjes integral. Furthermore, Grobler showed that a Riemann-Stieltjes integral can be interpreted as the area which is obtained by summing together 
-the area of an infinite number of non-rectangular infinitesimals, i.e.
-a Riemann-Stieltjes integral can be converted into a Cavalieri integral \cite{ackermann12,grobler19}.
-Combining these two ideas together results in the following geometric
-interpretation: the Riemann-Liouville fractional integral can be interpreted as the area which is obtained by summing together the area of an infinite number of non-rectangular infinitesimals whose shape is determined by the order of integration $\alpha$ and the integration limit $t$.\\
-
-\noindent
-It is important for the reader to realize that we specifically wrote this paper for people with a pedagogical interest, undergraduate students and for the layman who finds integration theory intriguing and
-as such we will try to steer clear from using too many mathematical definitions and proofs. We will rather convey our ideas using as many examples as possible. From the 
-three groups mentioned we believe that the undergraduate student will find this article the most useful. Although undergraduate students have a limited understanding of 
-fractional calculus they generally are quite interested in the subject. This is quite evident from perusing mathematical social media platforms and from surveying 
-articles published in undergraduate journals \cite{munkhammar05}.
-Undergraduates struggle to grasp fractional calculus, because it is very abstract.
-We believe that the geometric interpretation we present in this paper, as it is similar in nature to the definition of classical integration, will provide undergraduates with the insight that they need to quickly grasp and understand the fundamental
-concepts that underpin fractional calculus.\\
-
-%We also hope that this paper will enable and encourage lectures to teach this fascinating mathematical discipline to undergraduate students.\\
-
-\noindent
-We start the paper by reviewing the definition of the Riemann-Stieltjes integral, the Cavalieri integral and the Euler function.
-We then present the definition of the Riemann-Liouville fractional integral.
-We end the paper by presenting our novel geometric interpretation, some examples and a conclusion.
-
-%Due to the 
-%Even though most undergraduates have a limited understanding of fractional-order calculus they generally are quite interested in the subject. This is quite 
-%evident from perusing mathematical social media platforms and from surveying articles published in undergraduate journals []. One of the reason fractional calculus is not generally 
-%taught at the undegraduate level is due to the fact that the notion is quite abstract and it is therefore difficult to interpret geometrically. In this paper adress this shortcomming by presenting  
-%a novel geometric interpretation of the Riemann-Liouville fractional integral which is similar in nature to the classical interpretation of classical integration. Our hope is that this 
-%geometric interpretation will encourage and enable undergraduate lectures to introduce undergraduates to this fascinating mathematical discipline.
-
-%Our hope is that the geometric 
-%interpretation we present here will encourage and enable undergraduate lectures to introduce undergraduates to this fascinating mathematical discipline.
-
-%We therefore only present the min-
-%imum number of mathematical definitions that are needed to convey the new geometric framework.
-
-%This article is not an in depth study into the field of integral calculus, but should rather be viewed as an introductory text
-
-%It is important to point out at this point that there exists numerous acccepted definitions of fractional integration and differentiation. For the sake of 
-%simplicity we decided to focus on one In this paper we will focus 
-%on the Riemann-Lioville fractional integral.
-
-%There are many accepted definitions of fractional order differentiation and integration. In this paper we will only focus
-
-%In particular, their contribution played a crucial part in defining what is now known as the 
-%Riemann-Lioville fractional integral. In this paper, we present a novel geometric interpretation of the Riemann-Lioville fractional integral which is similar 
-%in nature to the classical interpretation of an ordinary Riemann integral. An ordinary Riemann integral can be interpreted as an infinitesimal sum of rectangular 
-%infinitesimals.
-
-%In this paper we present a novel geometric interpretation of the Riemann-Liouville fractional integral. There are in fact many accepted definitions of fractional integration 
-%The interpretation we present here is especially useful from 
-%a pedigogical point of view as it is similar in nature to the definition of classical integration.
-as an infinite sum of rectangular infinitesimals.
-In this paper, we demonstrate at the hand of examples that the Riemann-Liouville fractional integral can be interpreted
-%as an infinite sum of non-rectangular infinitesimals whose shape is determined by the order of integration $\alpha$ and the integration limit $x$.
-Furthermore, please note that the intended audience of this
-%paper is undergraduate students and lecturers and as such we do not present .  In ordinary integration we can interpret the integral
-
-%Fractional calculus can be summarized as the generalization of integer-order differentiation and integration to an arbitrary order.
-%Fractional-order calculus is as old as classical calculus itself.
-In this paper, we will mainly focus our attention on fractional-order integration and in particular investigate the Riemann-Liouville fractional
-%integral. It is Liouville and Riemann who laid much of the groundwork which was needed to define what is now known as the Riemann-Liouville fractional integral [Laurent’].
-
-%The idea of integer-order differentiation and integration is well known to most undergraduates.
-However, undergraduates are less familiar with the idea of an arbitrary order differential or integral (i.e.
-fractional-order calculus).
-%Even though most undergraduates have a limited understanding of fractional-order calculus they generally are quite interested in the subject. This is quite 
-%evident from perusing mathematical social media platforms and from surveying articles published in undergraduate journals []. One of the reason fractional calculus is not generally 
-%taught at the undegraduate level is due to the fact that the notion is quite abstract and it is therefore difficult to interpret geometrically. In this paper adress this shortcomming by presenting  
-%a novel geometric interpretation of the Riemann-Liouville fractional integral which is similar in nature to the classical interpretation of classical integration. Our hope is that this 
-%geometric interpretation will encourage and enable undergraduate lectures to introduce undergraduates to this fascinating mathematical discipline.
-
-\section{Riemann-Stieltjes Integral}
-Recall that the Riemann-Stieltjes integral is defined as follows \cite{bartle76}:
-\begin{equation}
-\label{eq:g_int2}
-\int_{a'}^{b'} f(x) dg(x) =  \lim_{n \rightarrow \infty}\sum_{i=0}^{n-1} f(x_i^2)[g(x_{i+1}^2)-g(x_{i}^2)], 
-\end{equation}
-%Fig.~\ref{fig:2d_geo} depicts a region whose area can be determined by considering non--rectangular integration strips.
-%. Note that the shape of the integration strips are determined by $a(y)$. 
-%In Fig.~\ref{fig:2d_geo}, the function $a(y)$ is depicted in red. If we translate $a(y)$ along the $x$-axis we actually create two partitions on the $x$-axis, 
-%i.e. $(x_i^1)_{i=0}^{n}$ and $(x_i^2)_{i=0}^{n}$ with $x_i^1\in[a,b]$ and $x_i^2\in[a',b']$.  To map partition points in $[a',b']$ to partition points 
-%in $[a,b]$ we use the function $g$. The reverse is achieved through $h$. The functions $g$ and $h$ depend soly on $a(y)$ and are also 
-%computed with it.
-\noindent
-with $(x_i^2)_{i=0}^n$ being arbitrary partition points on the $x$-axis. 
-The function $g$ is known as the integrator and if it is monotone increasing then it maps points in the interval $[a',b,]$ to the interval $[a,b]$, with $a = g(a')$ and $b = g(b')$.
-The integral in Eq.~\eqref{eq:g_int2} is hard to evaluate in its present form. If $g$ is differentiable, however, then it becomes trivial to 
-evaluate a Riemann-Stieltjes integral due to the following identity:
-\begin{equation}
-\int_{a'}^{b'} f(x) dg(x) = \int_{a'}^{b'} f(x)g'(x)~dx.
-\end{equation}
-As an example:
-\begin{equation}
-\int_{\frac{1}{2}}^{2} f(x) dg(x)=\int_{\frac{1}{2}}^2 x~d2x = \int_{\frac{1}{2}}^2 2x~dx = 3.75. 
-\end{equation}
-
-\section{Cavalieri Integral}
-In this section we define the Cavalieri integral \cite{ackermann12}.
-Let the region $R$ be bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$ and $b(y)=4-y$.
-This region is shown in Fig.~\ref{fig:caval2}.\\
-%\begin{figure}[htb]
-%\centering
-%\includegraphics[width=0.3\textwidth]{fig12}
-%\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$. Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
-%\label{fig:ex1}
-%\end{figure}
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.75\textwidth]{fig13.eps}
-\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$.
-The figure also depicts the partition points $x_i^2$ as used in the Cavalieri sum (see Eq.~\ref{eq:cav_sum}).
-Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
-\label{fig:caval2}
-\end{figure}
-
-\noindent
-The area of $R$ can be determined as follows if we employ the classical notion of integration:
-\begin{equation}
-\int_0^2x\, dx+\int_2^44-x\, dx- \int_0^{\frac{1}{2}}x\, dx-\int_{\frac{1}{2}}^11-x\, dx = 3.75. 
-\end{equation}
-
-\noindent
-There, however, exists a more straightforward way do determine the area of $R$, i.e. we can sum together the area of non-rectangular integration strips inscribing $R$ instead of
-having to sum together the area of multiple rectangular integration strips.
-Moreover, the shape of the non-rectangular integration strips we should use is determined by the function $a(y)$.
-We can express this notion more formally as
-follows, let $(x_i^1)_{i=0}^{n}$ denote a partition on the $x$-axis, such that $a = x_0^1 < x_1^1 < \cdots < x_n^1 = b$, and $\Delta x_i^1 = x_{i+1}^1 - x_i^1$.
-We are now able to construct the following sum (the lower Cavalieri sum):
-\begin{equation}
-\label{eq:cav_sum}
-\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1.
-\end{equation}
-The partition points $(x_i^2)_{i=0}^{n}$ are depicted in Fig.~\ref{fig:caval2}. Note that Eq.~\eqref{eq:cav_sum} approximates the area of $R$. In the limit Eq.~\eqref{eq:cav_sum} approaches 
-the Cavalieri integral:
-\begin{equation}
-\label{eq:caval1}
-\int_{a(y)}^{b(y)}f(x)\, dx = \lim_{n\to \infty}\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1.
-\end{equation}
-It is, however, quite hard to evaluate the above integral directly. Fortunately, it is easy to convert a Cavalieri integral into an equivalent Riemann or Riemann-Stieltjes 
-integral by using the transformation functions $h$ and $g$. Expressed mathematically:
-\begin{equation}
-\label{eq:main_cav}
-\int_{a(y)}^{b(y)}f(x)\,dx =\int_a^b f \circ h (x)\, dx = \int_{a'}^{b'} f(x) dg(x).
-\end{equation}
-We can calculate $g$ as follows:
-\begin{equation}
-g(x) = x - a\circ f(x) + a.
-\end{equation}
-Moreover, $h=g^{-1}$. We can now evaluate the Cavalieri integral by using its equivalent Riemann or Rieman-Stieltjes integral.
-If we use its Riemann equivalent we obtain:
-\begin{equation}
-\int_{a(y)}^{b(y)}f(x)\, dx = \int_a^b f \circ h (x)\, dx = \dfrac{1}{2}\int_1^4x\, dx = 3.75.  
-\end{equation}
-If we use its Riemann-Stieltjes equivalent we obtain:
-\begin{equation}
-\int_{a(y)}^{b(y)}f(x)\, dx = \int_{a'}^{b'} f \, dg(x) = \int_{\frac{1}{2}}^2x\, d2x = 3.75.  
-\end{equation}
-
-\noindent
-Conversely, if $g$ is known (and not $a(y)$) and $g(a') = a$ then we can calculate $a(y)$ using the following \cite{grobler19}:
-\begin{equation}
-\label{eq:a_y}
-a(y) = f^{-1}(y) - g\circ f^{-1}(y) + g(a'). 
-\end{equation}
-Eq.~\eqref{eq:a_y} allows us to transform a Riemann-Stieltjes integral into an equivalent Cavalieri integral. 
-Furthermore, this transformation enables us to assign a geometric interpretation to a Riemann-Stieltjes integral. The interpretation being:
-it represents the area obtained by summing together the area of an infinite number of non-rectangular infinitesimals; all of them being translations of $a(y)$. Note,
-$b(y) = a(y) + (b-a)$.
-
-\section{Gamma Function}
-The gamma function was first devised by Euler \cite{euler1738}.
-The gamma function is defined for all real numbers except for the non-negative integers.
-Moreover, it is a natural extension of the factorial function to the real numbers.
-The Gamma function is defined as:
-\begin{equation}
-\Gamma(x) = \int_0^{\infty} t^{x-1} e^{-t}\,dt.
-\end{equation}
-The function $\Gamma(x)$ is depicted in Fig.~\ref{fig:gamma} for $x\in(-5,5)$.
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.75\textwidth]{gamma.pdf}
-\caption{A plot of $\Gamma(x)$ for $x\in(-5,5)$. $\Gamma(x)$ is not defined for the non-negative integers.}
-\label{fig:gamma}
-\end{figure}
-
-\section{Riemann-Liouville Fractional Integral}
-In this section we present the definition of the Riemann-Liouville fractional integral of order $\alpha$ \cite{laurent1884}. Let
-\begin{equation}
-If(t) := \int_0^t f(\tau)~d\tau.
-\end{equation}
-If we apply the above operator in a repetitive manner to $f$ we obtain the $n$th antiderivative of $f$ based at 0:
-\begin{equation}
-\label{eq:n_anti}
-I^nf(t) = \int_0^t\int_0^{t_1}\cdots \int_0^{t_{n-1}}f(t_n)~dt_n\cdots dt_2 dt_1.
-\end{equation}
-Applying Cauchy's formula for repetitive integration to the above $n$th antiderivative of $f$ helps us express the above $n$th antiderivative as a single integral. 
-Applying Cauchy's formula to Eq.~\eqref{eq:n_anti} results in:
-\begin{equation}
-\label{eq:cauchy}
-I^nf(t) = \frac{1}{(n-1)!}\int_0^t (t-\tau)^{n-1}f(\tau)~d\tau.
-\end{equation}
-As an example if $f(\tau)=\tau$ and $n=2$ then Eq.~\eqref{eq:cauchy} reduces to:
-\begin{equation}
-I^2f(t) = \int_0^t (t-\tau)t~dt = \frac{\tau^2 t}{2} - \frac{\tau^3}{3} \Bigg |_0^t = \frac{t^3}{3!}.
-\end{equation}
-The definition in Eq.~\eqref{eq:cauchy} can now be extended to an arbitrary fractional order by replacing $(n-1)!$ with the Gamma function (see Fig.~\ref{fig:gamma}):
-\begin{equation}
-\label{eq:frac_integral}
-I^{\alpha}f(t) = \frac{1}{\Gamma(\alpha)}\int_0^t (t-\tau)^{\alpha-1}f(\tau)~d\tau.
-\end{equation}
-Eq.~\eqref{eq:frac_integral} is known as the Riemann-Liouville fractional integral of order $\alpha$. As an example if $f(\tau)=\tau$ and $\alpha=\frac{1}{2}$ then 
-Eq.~\eqref{eq:frac_integral} reduces to:
-\begin{equation}
-I^{\frac{1}{2}}f(t) = \frac{1}{\Gamma(\frac{1}{2})} \int_0^t \frac{\tau}{\sqrt{t-\tau}} dt = \frac{1}{\sqrt{\pi}}\left [ -\frac{2}{3}\sqrt{t-\tau}(t+2x)\right] \Bigg |_0^t=\frac{4}{3\sqrt{\pi}}t^{\frac{3}{2}}.
-\end{equation}
-Furthermore, it is straightforward to show that the $I$ operator satisfies:
-\begin{equation}
-I^{\alpha}I^{\beta}f(t) = I^{\alpha+\beta}f(t). 
-\end{equation}
-
-\section{Geometric Interpretation of the Riemann-Liouville Fractional Integral}
-In this section we present a novel geometric interpretation of the Riemann-Liouville fractional integral. 
-Recall that the Riemann-Liouville fractional integral of order $\alpha$ is defined as:
-\begin{equation}
-\label{eq:RL_frac_int}
-\frac{1}{\Gamma(\alpha)}\int_{0}^{t}f(\tau)(t-\tau)^{\alpha-1}~d\tau
-\end{equation}
-
-\noindent
-Podlubny showed that the above fractional integral can be rewritten as a Riemann-Stieltjes integral \cite{podlubny02}:
-\begin{equation}
-\label{eq:rs}
-\int_0^{t} f(\tau)~dg_t(\tau),
-\end{equation}
-with 
-\begin{equation}
-\label{eq:g_rl}
-g_t^{\alpha}(\tau) = \frac{\left \{t^{\alpha} - (t-\tau)^{\alpha} \right \}}{\Gamma(\alpha+1)}. 
-\end{equation}
-
-\noindent
-Note that $g_t^{\alpha}(\tau)$ is always invertible, since $\frac{d g_t^{\alpha}}{d \tau} = \frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)}>0$ for $\tau\in[0,t]$. The inverse 
-of $g_t^{\alpha}(\tau)$ is equal to:
-\begin{equation}
-h_t^{\alpha}(\tau) = t - \sqrt[\alpha]{t^{\alpha} - \Gamma(\alpha+1)\tau}
-\end{equation}
-
-\noindent
-Let $\mathsf{A} = \{0,0.2,0.4,0.6,0.8,1\}$. The analytic expressions of $g_{10}^{\alpha}(\tau)$ and $h_{10}^{\alpha}(\tau)$ are presented in Table~\ref{tab:gandh} for $\alpha\in\mathsf{A}$. 
-The expressions in Table~\ref{tab:gandh} are depicted in Fig~\ref{fig:gandh}.
-
-\begin{table}[h!]
- \centering
- \caption{The analytic expressions of $g_{10}^{\alpha}(\tau)$ and $h_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}$.}
- \label{tab:gandh}
- \begin{tabular}{|c || c | c|} 
- \hline
- $\alpha$ & $g_{10}^{\alpha}(\tau)$ & $h_{10}^{\alpha}(\tau)$ \\ [0.5ex] 
- \hline\hline
- $0$ & 0 & $y=0$ \\ 
- $0.2$ & $[\Gamma\left (\frac{6}{5} \right )]^{-1}\left(\sqrt[5]{10}-\sqrt[5]{10-\tau}\right)$ & $10 - \left ( \sqrt[5]{10} -  \Gamma\left (\frac{6}{5} \right ) \tau \right )^5$  \\
- $0.4$ & $[\Gamma\left (\frac{7}{5} \right )]^{-1}\left(\sqrt[5]{10^2}-\sqrt[5]{(10-\tau)^2}\right)$ & $10 - \sqrt{\left ( \sqrt[5]{10} -  \Gamma\left (\frac{7}{5} \right ) \tau \right )^5}$ \\
- $0.6$ & $[\Gamma\left (\frac{8}{5} \right )]^{-1}\left(\sqrt[5]{10^3}-\sqrt[5]{(10-\tau)^3}\right)$ & $10 - \sqrt[3]{\left ( \sqrt[5]{10} -  \Gamma\left (\frac{8}{5} \right ) \tau \right )^5}$ \\
- $0.8$ & $[\Gamma\left (\frac{9}{5} \right )]^{-1}\left(\sqrt[5]{10^4}-\sqrt[5]{(10-\tau)^4}\right)$ & $10 - \sqrt[4]{\left ( \sqrt[5]{10} -  \Gamma\left (\frac{9}{5} \right ) \tau \right )^5}$ \\ [1ex]
- $1$ & $\tau$ & $\tau$ \\ [1ex] 
- \hline
- \end{tabular}
- \end{table}
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.75\textwidth]{gh.pdf}
-\caption{This figure depicts the curves of $g_{10}^{\alpha}(\tau)$ and $h_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}$. The curves associated with $g$ are plotted using 
-solid lines, while the curves plotted with dashed lines are associated with $h$. The lighter the shade with which a curve is depicted, the larger the $\alpha$-value is, that is associated with it.
-}
-\label{fig:gandh}
-\end{figure}
-
-\noindent
-Furthermore, Grobler showed that it is trivial to convert a Riemann-Stieltjes integral into a Cavalieri integral \cite{ackermann12,grobler19} (see Fig.~\ref{fig:caval2} and the Cavalieri section of this paper if more details are required).
-If we apply Grobler's conversion method to Eq.~\eqref{eq:rs} we obtain:
-\begin{equation}
-\label{eq:cav}
-\int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau, 
-\end{equation}
-with
-\begin{equation}
-\label{eq:cav_a}
-a_t^{\alpha}(y) = f^{-1}(y) - \frac{t^{\alpha}-(t-f^{-1}(y))^{\alpha}}{\Gamma(\alpha+1)}.
-\end{equation}
-Eq.~\eqref{eq:cav_a} is obtained by substituting Eq.~\eqref{eq:g_rl} into Eq.~\eqref{eq:a_y}. Note, $b_t^{\alpha}(y) = a_t^{\alpha}(y) + \frac{t^{\alpha}}{\Gamma(\alpha+1)}$.
-
-\noindent
-We can now assign a geometric interpretation to Eq.~\eqref{eq:cav}, since it is a Cavalieri integral (see Fig.~\ref{fig:caval2} and the Cavalieri section of this paper).
-The fractional integral in Eq.~\eqref{eq:RL_frac_int} can, therefore, be interpreted as the area obtained
-by summing together the area of an infinite number of infinitesimally small non-rectangular integration strips whose shape is determined by $\alpha$ and $t$.
-If $\alpha$ is equal to one, however, then the integral reduces to a normal Riemann integral as the integration strips become rectangular for this particular choice of $\alpha$ (its shape becomes independent of $t$).\\
-
-\noindent
-Interestingly, Eq.~\eqref{eq:main_cav} implies that we can use $h_t^{\alpha}(\tau)$ to convert Eq.~\eqref{eq:cav} into the following Riemann integral:
-\begin{equation}
-\label{eq:option2}
-\int_0^{\frac{t^{\alpha}}{\Gamma(\alpha+1)}} f\circ h_{\alpha}^t (\tau) d\tau.  
-\end{equation}
-We can, therefore, evaluate Eq.~\eqref{eq:cav} in one of two ways: we can either evaluate Eq.~\eqref{eq:rs} or we can evaluate Eq.~\eqref{eq:option2}.
-
-% \begin{table}[h!]
-% \centering
-%  \begin{tabular}{|c || c | c|} 
-%  \hline
-%  & \multicolumn{2}{|c|}{$a_{10}^{\alpha}(\tau)$}\\
-%  \hline
-%  &$f(\tau) = \tau$ & $f(\tau)=\sqrt{\tau}$ \\ [0.5ex] 
-%  \hline\hline
-%  $0$ & 0 & $y=0$ \\ 
-%  $0.2$ & $y-[\Gamma\left (\frac{6}{5} \right )]^{-1}\left(\sqrt[5]{10}-\sqrt[5]{10-y}\right)$ & $y^2-[\Gamma\left (\frac{6}{5} \right )]^{-1}\left(\sqrt[5]{10}-\sqrt[5]{10-y^2}\right)$  \\
-%  $0.4$ & $y-[\Gamma\left (\frac{7}{5} \right )]^{-1}\left(\sqrt[5]{10^2}-\sqrt[5]{(10-y)^2}\right)$ & $y^2-[\Gamma\left (\frac{7}{5} \right )]^{-1}\left(\sqrt[5]{10^2}-\sqrt[5]{(10-y^2)^2}\right)$ \\
-%  $0.6$ & $y-[\Gamma\left (\frac{8}{5} \right )]^{-1}\left(\sqrt[5]{10^3}-\sqrt[5]{(10-y)^3}\right)$ & $y^2-[\Gamma\left (\frac{8}{5} \right )]^{-1}\left(\sqrt[5]{10^3}-\sqrt[5]{(10-y^2)^3}\right)$ \\
-%  $0.8$ & $y-[\Gamma\left (\frac{9}{5} \right )]^{-1}\left(\sqrt[5]{10^4}-\sqrt[5]{(10-y)^4}\right)$ & $y^2-[\Gamma\left (\frac{9}{5} \right )]^{-1}\left(\sqrt[5]{10^4}-\sqrt[5]{(10-y^2)^4}\right)$ \\ [1ex]
-%  $1$ & $\tau$ & $\tau$ \\ [1ex] 
-%  \hline
-%  \end{tabular}
-% \end{table}
-
-% \begin{table}[h!]
-% \centering
-%  \begin{tabular}{|c || c|} 
-%  \hline
-%  Symbol & Definition  \\ [0.1ex]
-%  \hline 
-%  \rule{0pt}{2.5ex}
-%  $\mathsf{G}^{10}$ & $\{g_{10}^{\alpha}(\tau)|\alpha\in\{0,\frac{1}{5},\frac{2}{5},\frac{3}{5},\frac{4}{5}\}\}$\\ [0.5ex]
-%  $\mathsf{H}^{10}$ & $\{h_{10}^{\alpha}(\tau)|\alpha\in\{0,\frac{1}{5},\frac{2}{5},\frac{3}{5},\frac{4}{5}\}\}$\\ [0.5ex]
-%  $\mathsf{A}^{10}$ & $\{a_{10}^{\alpha}(\tau)|\alpha\in\{0,\frac{1}{5},\frac{2}{5},\frac{3}{5},\frac{4}{5}\}\}$\\ [0.5ex]
-%  $\mathsf{B}^{10}$ & $\{b_{10}^{\alpha}(\tau)|\alpha\in\{0,\frac{1}{5},\frac{2}{5},\frac{3}{5},\frac{4}{5}\}\}$\\ [0.5ex]
-%  $\mathsf{B}^{\frac{4}{5}}_1$ & $\{b_{t}^{\frac{4}{5}}(\tau)|t\in\alpha\in\{2,4,6,8,10\}$\\ [0.5ex]
-%  $\mathsf{B}^{\frac{4}{5}}_2$ & $\{b_{10}^{\frac{4}{5}}(\tau)-c|c\in\in\{0,2,4,6,8\}$\\ [0.5ex]
-%  \hline 
-%  \end{tabular}
-% \end{table}
-
-\section{Examples}
-In this section we will illustrate the usefulness of the non-static non-rectangular sum-based geometric interpretation we presented in the previous section at the 
-hand of two examples.\\
-
-\noindent
-Let us first consider the following fractional integral:
-\begin{equation}
-\label{eq:ex1_raw}
-\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \frac{1}{\Gamma(\alpha)}\int_0^t \tau(t-\tau)^{\alpha-1}~d\tau. 
-\end{equation}
-The function $f(\tau) =\tau$ is depicted in Fig.~\ref{fig:geo1}.
-As we mentioned in the previous section, we can assign a geometric interpretation to the above fractional integral by converting it into a Cavalieri integral using two steps.
-First, we convert
-the above integral into a Riemann-Stieltjes integral:
-\begin{equation}
-\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \int_0^t f(\tau)~dg_t^{\alpha}(\tau). 
-\end{equation}
-We then convert the resulting Riemann-Stieltjes integral into a Cavalieri integral:
-\begin{equation}
-\label{eq:ex1}
-\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \int_0^t f(\tau)~dg_t^{\alpha}(\tau)=\int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau,
-\end{equation}
-with $a_t^{\alpha}(y) = y - \frac{t^{\alpha}-(t-y)^{\alpha}}{\Gamma(\alpha+1)}.$
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.75\textwidth]{geo_int1.pdf}
-\caption{The non-static non-rectangular sum-based geometric interpretation of Eq.~\eqref{eq:ex1_raw}.}
-\label{fig:geo1}
-\end{figure}
-
-\noindent
-Since Eq.~\ref{eq:ex1}, is a Cavalieri integral it has a known geometric interpretation (see Fig.~\ref{fig:caval2}).
-It can be interpreted as the area obtained by summing together the areas of an infinite
-number of infinitesimals whose shape is determined by $\alpha$ and $t$, i.e.
-these infinitesimals have to be translations of $b_t^{\alpha}(y)$.
-The geometric interpretation of Eq.~\eqref{eq:ex1_raw} is, therefore, non-static as it depends on the value of $\alpha$ and $t$.
-There is one thing, however, which remains unclear: in what way does $\alpha$ and $t$ affect the shape of the aforementioned infinitesimals, i.e.
-how does the value of $\alpha$ and $t$ affect the shape of $b_t^{\alpha}(y)$.
-We will answer this question by working through a detailed example.\\
-
-%using two basic steps.
-First off, we will fix the value of $\alpha$ and $t$ in Eq.~\eqref{eq:ex1} and then depict $b_t^{\alpha}(y)$.
-We will then explore how varying the value of $\alpha$ and $t$ in Eq.~\eqref{eq:ex1} affects the shape $b_t^{\alpha}(y)$.\\
-%We know that a Cavalieri integral can be interpreted as the area which is obtained by summing together the area associated with an infinite number of non-rectangular infinitesimals whose shape 
-%is determined by the integration limits of the Cavalieri integral. Note that neither $g_t^{\alpha}(\tau)$ nor $a_t^{\alpha}(y)$ are static functions, 
-%they depend on the value of $\alpha$ and $t$.
-This implies that a fractional integral of order $\alpha$ and extent $t$ can be interpeted as the area obtained by summing together the area associated with an infinite number of infinitesimals whose
-%shape is determined by $\alpha$ and $t$, i.e. the geometric interpretation of Eq.~\eqref{eq:ex1_raw} is non-static as it depends on the value of $\alpha$ and $t$.
-
-\noindent
-If we set the value of $\alpha$ to $\sfrac{4}{5}$ and the value of $t$ to 10 in Eq.~\eqref{eq:ex1} we obtain:
-\begin{equation}
-\label{eq:ex1_specific}
-A_{10}^{\sfrac{4}{5}}=\int_{a_{10}^{\frac{4}{5}}(y)}^{b_{10}^{\frac{4}{5}}(y)} f(\tau)~d\tau 
-\end{equation}
-Let $R_{10}^{\sfrac{4}{5}}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{10}^{\sfrac{4}{5}}(y)$.
-The region $R_{10}^{\sfrac{4}{5}}$ is depicted in the right-most panel of Fig.~\ref{fig:geo1}.
-It is the largest of all the
-regions that are depicted in the right-most panel of Fig.~\ref{fig:geo1}. Moreover, let $A_{10}^{\sfrac{4}{5}}$ denote the area of $R_{10}^{\sfrac{4}{5}}$. 
-We can approximate the area of $R_{10}^{\sfrac{4}{5}}$ by summing together the area of $n$ equal width non-rectangular integration strips that inscribe $R_{10}^{\sfrac{4}{5}}$, i.e. we can 
-construct a Cavalieri sum (see Eq.~\eqref{eq:cav_sum}). Note, the sides of the non-rectangular integration strips we use in this approximation have to be translations of $b_{10}^{\sfrac{4}{5}}(y)$.
-If we take the limit of the aforementioned sum as $n\rightarrow \infty$ we approach the Cavalieri integral in Eq.~\eqref{eq:ex1_specific}, i.e. $A_{10}^{\sfrac{4}{5}}$.  
-Eq.~\eqref{eq:ex1_specific}, therefore, implies that the region $R_{10}^{\sfrac{4}{5}}$ is made up 
-of an infinite number of non-rectangular infinitesimals; all of them being translations of $b_{10}^{\sfrac{4}{5}}(y)$.
-Note, the right-most curve depicted in the right-most panel of Fig.~\ref{fig:geo1} is $b_{10}^{\sfrac{4}{5}}(y)$.
-Moreover, the special case in which we approximate $A_{10}^{\sfrac{4}{5}}$ using five equal width non-rectangular integration strips is depicted in the right-most panel of Fig.~\ref{fig:geo1}.
-The sides of the aforementioned five integration strips are depicted in Fig.~\ref{fig:geo1} using dashed lines.
-Let, $\mathcal{B}_{\mathsf{T}}^{\sfrac{4}{5}}=\{b_{10}^{\frac{4}{5}}(y)-c|c\in(\mathsf{T}-2)\}$ with $\mathsf{T}=\{2,4,6,8,10\}$.\\
-
-%We have thus verified that we can employ the Cavalieri integral in Eq.~\ref{eq:ex1_specific} to compute $A_{10}^{\sfrac{4}{5}}$ from first principles.
-%Let $\mathsf{B}_{10}^{\sfrac{4}{5}}$ denote the set containing these dashed curves.
-%We can, therefore, interpet Eq.~\eqref{}  The region $R_{10}^{\sfrac{4}{5}}$ is, therefore, made up 
-%of an infinite number of non-rectangular infinitesimals; all of them being translations of $b_{10}^{\sfrac{4}{5}}(y)$.
-
-\noindent
-Varying both $\alpha$ and $t$ results in Eq.~\eqref{eq:ex1}. In contrast with Eq.~\eqref{eq:ex1_specific}, Eq.~\eqref{eq:ex1} can be associated with more than one region. 
-Let $R_{t}^{\alpha}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{t}^{\alpha}(y)$. Note that $b_{t}^{\alpha}(y)$ forms the 
-right-most edge of $R_{t}^{\alpha}$.
-Moreover, let $A_{t}^{\alpha}$ denote the area of $R_{t}^{\alpha}$ and let $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}=\{R_t^{\alpha}|t\in\mathsf{T},~\alpha\in\mathsf{A}\}$ and
-$\mathsf{B}_{\mathsf{T}}^{\mathsf{A}}=\{b_t^{\alpha}(y)|t\in\mathsf{T},~\alpha\in\mathsf{A}\}$. 
-The regions in the set $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}$ are depicted in Fig.~\ref{fig:geo1}.
-The regions that are depicted in each of the panels of Fig.~\ref{fig:geo1} were generated by varying $t$, whilst keeping the value of $\alpha$ fixed.
-The title of each panel indicate which $\alpha$-value was used to generate the regions depicted in each panel. The only difference between the regions located in each 
-panel is their right edges. The right edges of the regions in each panel are depicted using varying shades of gray. The lighter the shade with which an edge is depicted, 
-the larger the $t$-value is, that is associated with it.\\
-
-\noindent
-As was the case for Eq.~\eqref{eq:ex1_specific} and $R_{10}^{\sfrac{4}{5}}$, Eq.~\eqref{eq:ex1} implies that we can assume that each of the regions depicted in Fig.~\ref{fig:geo1} are made up of an infinite number of infinitesimals.
-The infinitesimals that make up a specific region are translations of that region's right edge.
-The following observations can be made by inspecting Fig.~\ref{fig:geo1}: 
-\begin{description}
- \item[Effect of $\alpha$] the gray-tinted solid curves depicted in the different panels of Fig.~\ref{fig:geo1} are not equal to one-another, i.e.
-$\mathsf{B}_{\mathsf{T}}^{\alpha_1}\neq\mathsf{B}_{\mathsf{T}}^{\alpha_2}$.
- \item[Effect of $t$] the gray-tinted solid curves depicted in each of the panels of Fig.~\ref{fig:geo1} are not translations of one-another.
-Moreover, the dashed gray curves and the solid gray-tinted curves in the right-most panel are not equal to one-another, i.e.
-$\mathsf{B}_{\mathsf{T}}^{\sfrac{4}{5}}\neq\mathcal{B}_{\mathsf{T}}^{\sfrac{4}{5}}$.
-\end{description}
-We can therefore draw the following conclusion: the value of both $\alpha$ and $t$ alters the shape of the infinitesimals ($b_{t}^{\alpha}(y)$ depends on $\alpha$ and $t$) that make up the regions in Fig.~\ref{fig:geo1}.
-Interestingly, the effect of $\alpha$ on the shape of the infinitesimals that make up the regions depicted in Fig.~\ref{fig:geo1} is larger than the effect that $t$ has on their shape.
-The curves associated with the infinitesimals obtained by varying $t$, whilst keeping the value of $\alpha$ fixed are very similar in nature and there exists a high degree of correlation between them (if their
-sizes are ignored).
-The curves associated with the infinitesimals obtained by varying $\alpha$, whilst keeping the value of $t$ fixed are quite different from one another (the aforementioned curves are not highly correlated with
-one another).\\
-
-%In the case of $\alpha$: the gray-tinted solid curves depicted in each panel are not equal to one-another.
-Similarly, in the case of $t$: the dashed gray curves and the solid gray-tinted curves in the right-most panel are not equal to one-another, i.e.$\mathsf{B}_T^{\alpha}\neq\mathcal{B}_T^{\alpha}$.
-
-\begin{table}[h!]
-\centering
-\caption{Curves obtained by evaluating Eq.~\eqref{eq:ex1} and Eq.~\eqref{eq:ex2} for all $\alpha\in \mathsf{A}$ using either Eq.~\eqref{eq:rs} or Eq.~\eqref{eq:option2}.}
-\label{tab:eval}
-\begin{tabular}{||c|| c| c||} 
- \hline
- $\alpha$ & $\frac{1}{\Gamma(\alpha)}\int_0^t \tau(t-\tau)^{\alpha-1}~d\tau$ & $\frac{1}{\Gamma(\alpha)}\int_0^t \sqrt{\tau}(t-\tau)^{\alpha-1}~d\tau$ \\[0.5ex]
- \hline\hline
- \rule{0pt}{2.5ex}
- $0$ & $t$ & $\sqrt{t}$  \\  
- \rule{0pt}{2.5ex}
- $0.2$ & $\frac{25}{6\Gamma(\frac{1}{5})} t^{\frac{6}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{17}{10})} t^{\frac{7}{10}}$  \\ 
- \rule{0pt}{2.5ex}
- $0.4$ & $\frac{25}{14\Gamma(\frac{2}{5})} t^{\frac{7}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{19}{10})} t^{\frac{9}{10}}$  \\
- \rule{0pt}{2.5ex}
- $0.6$ & $\frac{25}{24\Gamma(\frac{3}{5})} t^{\frac{8}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{21}{10})} t^{\frac{11}{10}}$  \\ 
- \rule{0pt}{2.5ex}
- $0.8$ & $\frac{25}{36\Gamma(\frac{4}{5})} t^{\frac{9}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{23}{10})} t^{\frac{13}{10}}$  \\ 
- \rule{0pt}{2.5ex}
- $1$ & $\frac{1}{2}t^2$  & $\frac{2}{3}t^{\frac{3}{2}}$  \\ [1ex]
- \hline
- \end{tabular}
-\end{table}
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.75\textwidth]{func_eval1.pdf}
-\caption{Depicts the curves which are obtained by evaluating Eq.~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ using either Eq.~\eqref{eq:rs} or Eq.~\eqref{eq:option2}.}
-\label{fig:eval1}
-\end{figure}
-
-\noindent
-If we evaluate the integral in Eq.~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ (using either Eq.~\eqref{eq:rs} or Eq.~\eqref{eq:option2}) we obtain the curves in the 
-left-most column of Table~\ref{tab:eval}. These curves are depicted in Fig.~\ref{fig:eval1}.
-The area of the regions depicted in Fig.~\ref{fig:geo1} are also plotted in Fig.~\ref{fig:eval1} using circular markers.
-As expected, the circular markers in Fig.~\ref{fig:eval1} that correspond to the areas of the regions in Fig.~\ref{fig:eval1}
-associated with a particular choice of $\alpha$ (i.e.
-regions depicted in a particular panel of Fig.~\ref{fig:geo1}) fall on the curve in Fig.~\ref{fig:eval1}; associated with the same choice of $\alpha$.
-Moreover, note that we have adopted the
-same coloring scheme in Fig.~\ref{fig:geo1} and Fig.~\ref{fig:eval1}.
-Using the same coloring scheme in both figures makes it clear which of the area values in Fig.~\ref{fig:eval1} can be associated with which regions in Fig.~\ref{fig:geo1}.
-To summarize, Fig.~\ref{fig:geo1}, therefore, depicts a non-static non-rectangular sum-based geometric interpretation of Eq.~\eqref{eq:ex1}. Moreover, Fig.~\ref{fig:eval1} corroborates this 
-geometric interpretation.\\
-
-\noindent
-Let us know consider a different fractional integral:
-\begin{equation}
-\label{eq:ex2}
-\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \frac{1}{\Gamma(\alpha)}\int_0^t \sqrt{\tau}(t-\tau)^{\alpha-1}~d\tau. 
-\end{equation}
-The non-static non-rectangular sum-based geometric interpretation associated with Eq.~\eqref{eq:ex1} is depicted in Fig.~\ref{fig:geo2}. 
-If we evaluate the integral in Eq.~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ we obtain the curves in the right-most column of Table~\ref{tab:eval}. 
-These curves are depicted in Fig~\ref{fig:eval2}.
-The validity of the non-static non-rectangular sum-based geometric interpretation depicted in Fig.~\ref{fig:geo2} is corroborated by Fig.~\ref{fig:eval2}.
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.75\textwidth]{geo_int2.pdf}
-\caption{The non-static non-rectangular sum-based geometric interpretation of Eq.~\eqref{eq:ex2}.}
-\label{fig:geo2}
-\end{figure}
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.75\textwidth]{func_eval2.pdf}
-\caption{Depicts the curves which are obtained by evaluating Eq.~\eqref{eq:ex2} for all $\alpha\in \mathsf{A}$ using either Eq.~\eqref{eq:rs} or Eq.~\eqref{eq:option2}.}
-\label{fig:eval2}
-\end{figure}
-
-%To conclude this section, a fractional integral of order $\alpha$ and extent $t$ can be interpreted as the area obtained by summing together the area associated with an infinite number of infinitesimals whose
-%shape is determined by $\alpha$ and $t$. The geometric interpretation of a fractional integral is, therefore, non-static as it depends on the value of both $\alpha$ and $t$.
-
-%the fractional integral in Eq.~\ref{??} can be interpreted as the area which is obtained by summing together the area associated with an infinite number of non-rectangular infinitesimals whose shape 
-%is determined by the integration limits of the Cavalieri integral. Note that neither $g_t^{\alpha}(\tau)$ nor $a_t^{\alpha}(y)$ are static functions, 
-%they depend on the value of $\alpha$ and $t$.
-This implies that a fractional integral of order $\alpha$ and extent $t$ can be interpeted as the area obtained by summing together the area associated with an infinite number of infinitesimals whose
-%shape is determined by $\alpha$ and $t$, i.e. the geometric interpretation of Eq.~\eqref{eq:ex1_raw} is non-static as it depends on the value of $\alpha$ and $t$.
-
-% The circular markers in Figure ?? is depicted using the same tint-of-gray with which the right edge of the region  in question is depicted in Fig.
-% 
-% Each of the curves 
-% in Fig can therefore be associated with one of the panels in Fig. The area associated with the regions depicted in each of the panels in Fig. are plotted on the curves 
-% in 
-% associated with a particular panel appropriate 
-% curves 
-% in Fig using circular markers. The circular marker is depicted in Figure using the same tint-of-gray with which the 
-% right edge of the region in question is depicted in Fig.  
-% 
-% it is $\alpha$  
-% Although $\alpha$ and $t$ alters the shape of the infinitesimals which make up the regions depicted in Fig.,  
-% 
-% that make up the regions in Fig are confirmed by the following observation: $\mathsf{B}_T^{\alpha}\neq\mathcal{B}_T^{\alpha}$.
-% We can visually verify that this observation is in fact true for $alpha=\frac{4}{5}$ by inspecting the right-most panel in Fig.~\ref{??}.
-The dashed curves and the gray tinted curves in this panel do not allign.
-% 
-% 
-% 
-% the upper limit 
-% of the Cavalieri integral in Eq. As the upper limit of the Cavalieri integral depends on
-% 
-% As the shape of the infinitesimals which make up the regions depicted in Fig depend of the integration limit of the 
-% Cavalieri integral or stated differently on the value of $t$ and $\alpha$.  
-% 
-% If we set the value of $\alpha$ to $\frac{4}{5}$, but we do not fix the value of $t$ then Eq.~\eqref{eq:ex1} reduces to:
-% \begin{equation}
-% \int_{a_{t}^{\frac{4}{5}}(y)}^{b_{t}^{\frac{4}{5}}(y)} f(\tau)~d\tau 
-% \end{equation}
-% If we evaluate the above integral we obtain the area of the region $R_{t}^{\frac{4}{5}}$.
-The region $R_{t}^{\frac{4}{5}}$ is the region bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{t}^{\frac{4}{5}}(y)$.
-% Note that the shape of $R_{t}^{\frac{4}{5}}$ depends on the value of $t$.
-The regions contained in the set $\mathsf{R}^{\frac{4}{5}}$ are depicted in the rightmost panel of Fig\textbf{??}.
-Let $\mathsf{B}^{\frac{4}{5}}$ contain the right
-% edges of the regions contained in the set $\mathsf{R}^{\frac{4}{5}}$.
-The shape of the edges in $\mathsf{B}^{\frac{4}{5}}$ depend on the value of $t$.
-The edges in $\mathsf{B}^{\frac{4}{5}}$ are depicted in Fig??
-using different shades of gray.
-The shade with which the aformentioned curves are depicted becomes lighter
-% as the value of $t$ increases. The two sets b and b are not equal, i.e. the shape of the infinitesimals that make up the regions contained in 
-% R are dependent on $t$. Although the infinitesimals that make up the regions contained in R have different shapes their form do share common characteristics. 
-% 
-% 
-% altering $t$ alters the geometric interpretaion of 
-% Eq???. The shape of the inifinitesimals that make up the region that is associated with Eq depend on the value of $t$. 
-% 
-% 
-% the shape of the integration strip one has to use to construct the infinite sum that underpins the  used to create the   .
-Changing the value of $t$ alters the shape of the non-rectangular integration strip which is needed
-% 
-% 
-% limit alters the
-% shape of the infinitesimal we need to use.
-% 
-% 
-% The shade with which the aformentioned edges are depicted becomes lighter as the value of $t$ increases.
-% 
-% 
-% 
-% The boundaries of these regions are depicted in varying shades of gray.  
-% 
-% 
-% We depict $R_{t}^{\frac{4}{5}}$ in the left most panel of Fig.~\textbf{??} for all $t\in\mathsf{T}$. The set of functions   
-% 
-% 
-% If we change the value of $t$ we change the area 
-% 
-% 
-% In general can use $n$ integration strips to approximate 
-% 
-% 
-% 
-% the area If we are to sum together the area of  non-rectangular integration strips whose sides are translations of $b_{10}^{\frac{4}{5}}(y)$ then the result our summation would tend to
-% the area of $R_{10}^{\frac{4}{5}}$. 
-% 
-% 
-% Lets now choose to approximate the area of $R_{10}^{\frac{4}{5}}$ using five non-rectangualr integration strips of equal width. Mathematically speaking, this is accomplished 
-% by setting $n$ to 5 in Eq??. The aformentioned integration strips are depicted in the right-most panel of Figure~\ref{??}.
-% The sides of the integration strips are depicted using dashed lines. The more integration strips we consider the better our approximation of $R_{10}^{\frac{4}{5}}$ becomes. 
-% 
-% 
-% 
-% We can better approximate the area of $R_{10}^{\frac{4}{5}}$ by increasing the number of integrations strips we use .
-Increasing the number of integration strips we use improves our approximation of the area of $R_{10}^{\frac{4}{5}}$
-% If we decide on using five integration strips 
-% 
-% 
-% that 
-% we use whose sides are translations of $b_{10}^{\frac{4}{5}}(y)$ 
-% 
-% 
-% Each panel of 
-% Figure~\ref{??} depicts the function $f(\tau)$ and the set of curves $\mathsf{B}_T^{\alpha}$. The set $\mathsf{B}_T^{\alpha}$ is defined in Table~\ref{??} and contains 
-% all the Cavalieri integral upper limits obtained by fixing the order of integration $\alpha$ to a specific value.
-In each panel, we depict the set of curves $\mathsf{B}_T^{\alpha}$ using different shades of gray.
-% The shade with which $b_t^{\alpha}(y)$ is depicted becomes lighter as the value of $t$ increases.
-% 
-% 
-% The The $y$-valued functions are depicted in different shades of gray. The $\tau$-valued fun 
-% 
-% The curve in the rightmost panel of 
-% Figure~\ref{} which is depicted in the lightest shade of gray of 
-% 
-% The function $b_{10}^{\frac{4}{5}}(y)$ 
-% depicted in the lightest shade of gray used within the right-most panel
-% 
-% 
-% The right-most panel of Figure.~\ref{??} contains 
-% a few $y$-valued curves, each one depicted in a different shade of gray. The curve depicted in the lightest shade of gray is  
-% 
-% 
-% In each of the panels  curves $\mathsf{B}_1^{\alpha}$
-% 
-% convert the 
-% integrals in ?? and ?? to equivalent Cavalieri integrals.
-% 
-% 
-% We can assign a geometric interpretation to the above fractional integrals by converting them into Cavalieri integrals. This can be achieved by first 
-% converting the above integrals into Riemann-Stieltjes integrals and then converting the resulting integrals into Cavalieri integrals. Exaclty how these conversion are 
-% to be performed is discussed in the previous section.
-The inegrator $g_t^{\alpha}(\tau)$ of the aforementioned intermediate Riemann-Stieltjes integrals are equal and independent of the integrand $f(\tau)$.
-% The set of functions $\{g_{10}^{\alpha}(\tau)|\alpha\in\{0,0.2,\cdots,0.8,1\}\}$ are presented in Table \textbf{??} and depicted in Figure\textbf{??}.
-The integration limits of the aformentioned Cavalieri
-% integrals are functions and are determined by the integrand $f(\tau)$ and the integrator $g_t^{\alpha}(\tau)$.
-The set of functions $\{a_{10}^{\alpha}(y)|\alpha\in\{0,0.2,\cdots,0.8,1\}\}$ that can be
-% associated with the integrals in Eq~{??} and Eq~{??} are presented in Table~\textbf{??}. Note that neither $g_t^{\alpha}(\tau)$ nor $a_t^{\alpha}(y)$ are static functions, 
-% they depend on the value of $\alpha$ and $t$.
-This implies that a fractional integral of order $\alpha$ and extent $t$ can be interpeted as an infitesimal sum of an infinite number of infinitesimals whose
-% shape is determined by $\alpha$ and $t$.
-% 
-% Lets clarify the above by working through a detailed example. Lets set the value of $\alpha$ to $\frac{4}{5}$ and the value of $t$ to 10 and then convert the 
-% integrals in ?? and ?? to equivalent Cavalieri integrals. If we evaluate these Cavalieri integrals we obtain the area of two regions $A$ and $B$. Both $A$ and $B$ are bounded by the $x$-axis, 
-% $f(x)$ and $b_{10}^{\frac{4}{5}}(y)$. Region $A$ and $B$ are respectively depicted in the rightmost panel of Fig ?? and Fig ??. The area of $A$ and $B$ can be approximated
-% by summing together the area of non-rectangular integration strips that inscribes $A$ and $B$. The case in which we use five integration strips is depicted in 
-% Fig ?? and Fig ??. The analytic expressions of the right sides of these integration strips are elements of the set $\mathsf{A} = \{b_{10}^{\frac{4}{5}}(y) - c|c\in\{0,2,4,6,8\}\}$. The 
-% curves are plotted using dashed lines. 
-% 
-% The curves $\mathsf{B} = \{b_{t}^{\frac{4}{5}}(y)|t\in\{2,4,6,8,10\}\}$ are plotted in different shades of gray.
-The shade with which $b_t^{\alpha}(y)$ is depicted becomes lighter as the value of $t$ increases.
-Note
-% that $\mathsf{A}\neq \mathsf{B}$. The sides of the integration strips 
-% 
-% 
-% is the lighter the curve associated with $b_t^{\alpha}(y)$ is.
-% 
-% We depict We depict $b_10^{\alpha}(y)$ with the lightest
-% shade of
-% depicted in the right most   depict the region associated that is associated with the Cavalieri integral which is obtained 
-% 
-% 
-% the obtained Lets depict the geometric interpretation
-
-%\begin{equation}
-%\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \frac{1}{\Gamma(\alpha)}\int_0^t \sqrt{\tau}(t-\tau)^{\alpha-1}~d\tau.
-%\end{equation}
-
-%The integration limits of the aformentioned Cavalieri 
-%integrals are functions and are determined by the integrand $f(\tau)$ and the integrator $g_t^{\alpha}(\tau)$. Recall that a Cavalieri integral can 
-%be interpreted as an infinite sum of non-rectanguar infinitesimals whose shape is determined by its lower integration limit $a_t^{\alpha}(y)$. The set of functions 
-%$\{a_{10}^{f,\alpha}(y)|\alpha\in\{0,0.2,\cdots,0.8,1\}\}$ that can be associated with the integrals in Eq~{??} and Eq~{??} are presented in Table~\textbf{??}. Note that 
-%$a_t^{\alpha}(y)$ is not a static function it depends on the order of integration $\alpha$ and the integration limit $t$. The fact that $a_t^{\alpha}(y)$ is dependend 
-%on $t$ implies that a fractional integral of a particular order cannot be converted to a single Cavalieri integral, but rather to an infinite set $\mathcal{C}$ of Cavalieri integrals.
-%Each element of $\mathcal{C}$ is associated with a particular choice of $t$.
-Let $\mathcal{B}_f = \{b_{t}^{f,\alpha}(y)|\alpha\in\{0,0.2,\cdots,0.8,1\}\}$.
-In Fig.~\ref{fig:geo1} and Fig.~\ref{fig:geo2} we plot the elements of $\mathcal{B}$.
-%The brigther the function the larger $t$ is.
-For the case $t=10$ we also plot the integration strips.
-The fractional integral $\frac{1}{\Gamma(\alpha)}\int_0^10 f(\tau) (t-\tau)^{\alpha-1}~d\tau$ can therefore
-%be interpreted as the sum of inThey clearly do not match the other functions.
-
-% \begin{enumerate}
-%  \item Examples.
-%  \item If we evaluate \textbf{[is this word correct?]} these integrals we obtaine the functions in Table \textbf{??}. These functions are plotted in Fig xx.
-%  \item Assign a geometric interpretation by converting to a Riemann-Stieltjes integral and then to a Cavalieri integral.
-%  \item \textbf{[Is there a need to mention the fact that it is mapped to a set of different Cavalieri integrals]}. Note that we obtain a different 
-%  Cavalieri integral for each value of alpha and t.
-%  \item Let us fix alpha and t to specific values, ie write down the integrals. The function b the left most function in the leftmost panel (plotted in the lightest 
-%  shade of gray of all the y-valued functions. The integral , and by implication , can be inerpreted as the are of the region formed by f, b and the x-axis. This 
-%  area can be obtained by summing together an infinite number of infinitesimals whose shape is determined by b. This are can be approximated by using integration strips. These 
-%  strips is depicted using dashed lines. The area of this region and $t$ forms a specific point on the curves in Fig. The point is plotted in the same shade of gray than b.
-%  \item If we take another value of t we obtain a different region. Note that b and b are not mere translations of each other. Changing the integration limit alters the 
-%  shape of the infinitesimal we need to use.
-Althoug both t and alpa alters the shape of b, it is only alpha that fundamentally changes ....
-\textbf{[how to state this shape altering thing i do not know]}
-%  \item Need to finish the discussion of al the points mapping to the other figures. 
-%  \item Summary of overall interpretation of fractional integral.....
-% \end{enumerate}
-
-% These steps 
-% were discussed in more detail in the previous section. 
-% 
-% The steps to visualize the above two integrals were described in the previous paragraph. We first convert the integrals into Riemann-Stieltjes integrals. The 
-% Riemann-Stieltjes integrals are then converted to Cavalieri integrals. We can then simply depict the Cavalieri integrals and in doing so obtain a geometric interpretaion
-% of the original fractional integrals. Importantly, for each value of $t$ we obtain a different
-
-% \section{First-level section heading}
-% 
-% Section headings use an initial capital letter on the first word, with subsequent words lowercase.
-In general, the style of the journal is to leave all section headings unnumbered.
-Consult the journal editor if you wish to depart from this and other conventions.
-% 
-% \subsection{Second-level heading}
-% 
-% The same goes for second-level headings.
-It is not necessary to add font commands to make the math within heads bold and sans serif; this change will occur automatically when the production style is applied.
-% 
-% \section{Graphics}
-% 
-% Figures for the \textsc{Journal} can be submitted as either color or black \& white graphics.
-Generally, color graphics will be used for the online publication, and converted to black \& white images for the print journal.
-We recommend using whatever graphics program you are most comfortable with, so long as the submitted graphic is provided as a separate file using a standard file format.
-% 
-% For best results, please follow the following guidelines:
-% \begin{enumerate}
-% \item Bitmapped file formats---preferably TIFF or JPEG, but not BMP---are appropriate for photographs, using a resolution of at least 300 dpi at the final scaled size of the image.
-% \item Line art will reproduce best if provided in vector form, preferably EPS.
-% \item Alternatively, both photographs and line art can alternatively be provided as PDF files.
-Note that creating a PDF does not affect whether the graphic is a bitmap or vector; saving a scanned piece of line art as PDF does not convert it to scalable line art.
-% \item If you generating graphics using a \TeX\ package, please be sure to provide a PDF of the manuscript.
-In the production process, \TeX-generated graphics will eventually be converted to more conventional graphics so the \textsc{Journal} can be delivered in e-reader formats.
-% \item For photos of contributing authors, we prefer photos that are not cropped tight to the author's profile, so that production staff can crop the head shot to an equal height and width.
-If possible, avoid photographs that have excess shadows or glare.
-% \end{enumerate}
-% 
-% \section{Theorems, definitions, proofs, and all that}
-% 
-% Following the defaults of the \texttt{amsthm} package, styling is provided for \texttt{theorem}, \texttt{definition}, and \texttt{remark} styles, although the latter two use the same styling.
-% 
-% \begin{theorem}[Pythagorean Theorem]
-% Theorems, lemmas, axioms, and the like are stylized using italicized text. These environments can be numbered or unnumbered, at the author's discretion.
-% \end{theorem}
-% 
-% \begin{proof}
-% Proofs set in roman (upright) text, and conclude with an ``end of proof'' (q.e.d.) symbol that is set automatically when you end the proof environment.
-When the proof ends with an equation or other non-text element, you need to add \verb~\qedhere~ to the element to set the end of proof symbol; see the \texttt{amsthm} package documentation for more details.
-% \end{proof}
-% 
-% \begin{definition}[Secant Line]
-% Definitions, remarks, and notation are stylized as roman text.  They are typically unnumbered, but there are no hard-and-fast rules about numbering.
-% \end{definition}
-% 
-% \begin{remark}
-% Remarks stylize the same as definitions.
-% \end{remark}
-% 
-% Note that the \textit{College Mathematics Journal\/} is meant to be accessible to a broad audience, so heavy use of theorem-like formalisms is generally discouraged.
-
-%\begin{acknowledgment}
-%The authors wish to thank the Greek polymath Anonymous, whose prolific works are an endless source of inspiration.
-%\end{acknowledgment}
+hallo
 

### 2019-07-19 Cav2D/article-template.tex
started to add history of cavalieri to article

@@
 \noindent
-
-hallo
+Bonaventura Cavalieri was a mathematician who lived in the 17th centuray. He made numerous contributions to the fields of optics, astronomy and geometry. 
+In 1935, a moon crater, Cavalerius, was officially named after him to comemorate his achievments and to honor his memory (see Fig ) \cite{?}.
+Cavalieri was a student of Galileo. He served as a professor of mathematics at the university of Bologna from 1629 until his death in 1647. Galileo had the following 
+to say about Cavalieri Galileo wrote the following
 

### 2019-07-24 Cav2D/article-template.tex
added the description of the method of indivisiles

--- 2019-07-19 Cav2D/article-template.tex
@@
 \noindent
+Bonaventura Cavalieri was a mathematician who lived in the 17th century. He made numerous contributions to the fields of optics, astronomy and geometry. 
+Cavalieri was a student of Galileo. He served as a professor of mathematics at the university of Bologna from 1629 until his death in 1647. 
+Galileo held Cavalieri in high esteem as is evedent from the following extract of a reference letter Galileo wrote in which he recommended Cavalieri for the chair of mathematics at Bologna: ``\emph{few, perhaps none, from
+Archimedes onwards, have investigated so deeply and have entered so far into the science of geometry}''.
+In 1935, a moon crater, Cavalerius, was officially named after him to commemorate his achievements and to honor his memory (see Fig ) \cite{?}.
+Cavalieri's most notable achievement was the publication of his
+treatise, \emph{Geometria indivisibilibus}, in which he describes the precalculus method of indivisibles. The method of indivisibles can be attributed to the ancient Greeks,
+in this case Democritus and Archimedes. The method is used to compute the area and the volume of complex planar figures and solids, respectively.
+It works by finding a planar figure or a solid, whose area or volume can easily be computed, which is Cavalieri congruent to a planar figure or solid whose 
+area or volume is unknown. Two planar figures or solids are Cavalieri congruent if they can be decomposed into the same set of parallel ``indivisibles''. An indivisible of 
+a planar figure is any cord of the planar figure. An indivisible of a solid is any planar section of a solid. Two indivisibles are equal if they are of the same length or area.
 
-hallo
+%One first divides a complex planar figure whose area is unknown into indivisible parallel chords. These cords are then translated 
+%in such a way that the original planar figure is transformed into a planar figure whose area is easily computable. The volume of a complex solid can be computed 
+%in a similar manner. 
+%In this method areas of complex planar figures are computed by dividing such figures into indivisible parallel chords. One then 
+%finds another planar figure whose area is known that consists of the exact same set of chords. The area of the complex planar figure is then
 

### 2019-07-24 Cav2D/article-template.tex
added Cavalieri's principle

@@
 a planar figure is any cord of the planar figure. An indivisible of a solid is any planar section of a solid. Two indivisibles are equal if they are of the same length or area.
+It is Cavalieri's principle that assures us that two planar figures or solids that are composed of the same set of indivisibles have equal area or volume. Cavalieri's principle 
+in $\mathbb{R}^3$ is stated below without proof:
+
+\begin{theorem}[Cavalieri's principle in $\mathbb{R}^3$]
+If two solids are included between a pair of parallel planes, and if the areas of
+the two sections cut by them on any plane parallel to the including planes are always
+equal, then the volumes of the two solids are equal.
+\end{theorem}
 

### 2019-07-24 Cav2D/article-template.tex
addeda description of nonlinear column

@@
 \end{theorem}
+
+\noindent
+Fig~\ref{??} depicts a classic rectangular prism or column as well as a \emph{non-linear rectangular prism or column}. The volumes of the two solids in Fig~\ref{??} are equal due 
+to Cavalieri's principle. Note that in this article we use the non-standerdized term non-linear rectangular prism or column to refer to a solid that has a rectangular 
+base and lateral edges that are non-linear and translations of one another.
 

### 2019-07-24 Cav2D/func_plotter.py
added prismatoid calculations --- not working as of yet

@@ -515,10 +515,137 @@ def plot_volume2(xx,yy,xx2,yy2,t):
     print("v = "+str(np.sum(volume_v)))
     #v = 0.8695177800000001
    
+def d3(A,B):
+
+    return np.sqrt((A[0]-B[0])**2+(A[1]-B[1])**2+(A[2]-B[2])**2)
+
+def area_trap(a,b,c,d):
+    return np.sqrt(c**2 - 0.25*(((c**2-d**2)/(b-a)) + (b-a))**2)*(a+b)*0.5
+
+def area_heron(a,b,c):
+    S = 0.5*(a+b+c)
+    return np.sqrt(S*(S-a)*(S-b)*(S-c))
+
+
+def volume_of_prismatoid():
+    #base 1
+    #A, E, G, C
+
+    A = np.zeros((3,),dtype=float)
+    E = np.copy(A)
+    G = np.copy(A)
+    C = np.copy(A)
+
+    E[0] = 8.0/5.0
+    E[1] = 16.0/5.0
+    E[2] = -E[0]-E[1]+8
+
+    G[0] = 4.0/5.0
+    G[1] = 28.0/5.0
+    G[2] = -G[0]-G[1]+8
+
+    C[1] = 4.0
+
+    a = d3(G,C)
+    b = d3(A,E)
+    c = d3(G,E)
+    d = d3(C,A)
+
+    A1 = area_trap(a,b,c,d) 
+    print("A1 = ",A1)
+
+    #base 2
+    #QRD (middle cross-section)
+    Q = np.zeros((3,),dtype=float)
+    R = np.copy(Q)
+    D = np.copy(Q)
+
+    Q[0] = 2.0
+    
+    #2x-4 = -0.5x+4
+    R[0] = 8/2.5
+    R[1] = 2*R[0]-4
+    R[2] = -R[0]-R[1]+8
+
+    D[0] = 4.0
+    D[1] = 4.0
+    
+    a = d3(Q,R)
+    b = d3(R,D)
+    c = d3(D,Q)
+
+    A2 = area_heron(a,b,c)
+    print("A2 = ",A2)
+
+    #base 3
+    #BDF
+    B = np.zeros((3,),dtype=float)
+    D = np.copy(B)
+    F = np.copy(B)
+
+    B[0] = 4.0
+    
+    D[0] = 4.0
+    D[1] = 4.0
+
+    F[0] = 24.0/5.0
+    F[1] = 8.0/5.0
[…]

### 2019-07-24 Cav2D/func_plotter.py
added prismatoid calculations --- not working as of yet attempt 2

@@ -633,11 +633,41 @@ def volume_of_prismatoid():
 
     V = (1.0/6.0)*h*(A1+4*A2+A3)
     print("V = ",V)
-    V = (1.0/6.0)*4*(A1+4*A2+A3)
-    print("V = ",V)
+    
+    #TESTING NEW HEIGHT IDEA
+    
+    V1 = np.zeros((3,),dtype=float)
+    V2 = np.copy(V1)
+    V3 = np.copy(V2)
+    V4 = np.copy(V3)
 
+    V1[0] = h/2.0
+
+    V2[0] = h/2.0
+    V2[1] = 4.0
+
+    V3[0] = (h+4)/2.5
+    V3[1] = -0.5*V3[0]+4
+    V3[2] = -V3[0]-V3[1]+8
+
+    V4[0] = (h+6)/2.5
+    V4[1] = -0.5*V4[0]+6
+    V4[2] = -V4[0]-V4[1]+8
+
+    a = d3(V2,V4)
+    b = d3(V1,V3)
+    c = d3(V4,V3)
+    d = d3(V1,V2)
+  
+    A2a = area_trap(a,b,c,d) 
+    
+    Va = (1.0/6.0)*4*(A1+4*A2a+A3)
+    print("Va = ",Va)
 
     
+
+    
+
 
  
      

### 2019-07-26 Cav2D/func_plotter.py
fixed prismatoid error

@@ -220,8 +220,114 @@ def plot_figures(xx,yy,xx2,yy2,zz2,K=8):
 
     ax.add_collection3d(faces)
 
+    B = np.zeros((3,),dtype=float)
+    D = np.copy(B)
+    F = np.copy(B)
+
+    #BASE 1
+    #########################
+    B[0] = 4.0
+    
+    D[0] = 4.0
+    D[1] = 4.0
+
+    F[0] = 24.0/5.0
+    F[1] = 8.0/5.0
+    F[2] = -F[0]-F[1]+8
+
+    vrtx = [[B,D,F]]  
+ 
+    faces = Poly3DCollection(vrtx, linewidths=1, edgecolors='k',facecolors='cyan',alpha=0.3)
+    faces.set_facecolor((1,1,0,0.1))
+
+    ax.add_collection3d(faces)
+    #########################
+    
+    #BASE 2
+    #########################
+    V1 = np.zeros((3,),dtype=float)
+    V2 = np.copy(V1)
+    V3 = np.copy(V2)
+    V4 = np.copy(V3)
+
+    V1[0] = 2
+
+    V2[0] = 2
+    V2[1] = 4.0
+
+    #2x-4 = -0.5x+4
+    V3[0] = 8/2.5
+    V3[1] = 2*V3[0]-4
+    V3[2] = -V3[0]-V3[1]+8
+
+    #2x = -0.5x+6
+    V4[0] = (6)/2.5
+    V4[1] = -0.5*V4[0]+6
+    V4[2] = -V4[0]-V4[1]+8
+    
+    vrtx = [[V1,V2,V4,V3]]  
+ 
+    faces = Poly3DCollection(vrtx, linewidths=1, edgecolors='k',facecolors='red',alpha=0.3)
+    faces.set_facecolor((1,0,0,0.1))
+
+    ax.add_collection3d(faces)
+    #########################
+    #BASE 3
+    #########################
+
+    A = np.zeros((3,),dtype=float)
+    E = np.copy(A)
+    G = np.copy(A)
+    C = np.copy(A)
+
+    E[0] = 8.0/5.0
+    E[1] = 16.0/5.0
+    E[2] = -E[0]-E[1]+8
+
+    G[0] = 4.0/5.0
+    G[1] = 28.0/5.0
+    G[2] = -G[0]-G[1]+8
+
+    C[1] = 4.0
+    vrtx = [[A,E,G,C]]  
[…]

### 2019-07-30 Cav2D/article-template.tex
copied cavalieri section need to rewrite section completely

@@
 base and lateral edges that are non-linear and translations of one another.
+
+\section{Cavalieri Integral}
+In this section we define the Cavalieri integral \cite{ackermann12}.
+Let the region $R$ be bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$ and $b(y)=4-y$.
+This region is shown in Fig.~\ref{fig:caval2}.\\
+%\begin{figure}[htb]
+%\centering
+%\includegraphics[width=0.3\textwidth]{fig12}
+%\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$. Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
+%\label{fig:ex1}
+%\end{figure}
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.75\textwidth]{fig13.eps}
+\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$.
+The figure also depicts the partition points $x_i^2$ as used in the Cavalieri sum (see Eq.~\eqref{eq:cav_sum}).
+Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
+\label{fig:caval2}
+\end{figure}
+
+\noindent
+The area of $R$ can be determined as follows if we employ the classical notion of integration:
+\begin{equation}
+\int_0^2x\, dx+\int_2^44-x\, dx- \int_0^{\frac{1}{2}}x\, dx-\int_{\frac{1}{2}}^11-x\, dx = 3.75. 
+\end{equation}
+
+\noindent
+There, however, exists a more straightforward way do determine the area of $R$, i.e. we can sum together the area of non-rectangular integration strips inscribing $R$ instead of
+having to sum together the area of multiple rectangular integration strips.
+Moreover, the shape of the non-rectangular integration strips we should use is determined by the function $a(y)$.
+We can express this notion more formally as
+follows, let $(x_i^1)_{i=0}^{n}$ denote a partition on the $x$-axis, such that $a = x_0^1 < x_1^1 < \cdots < x_n^1 = b$, and $\Delta x_i^1 = x_{i+1}^1 - x_i^1$.
+We are now able to construct the following sum (the lower Cavalieri sum):
+\begin{equation}
+\label{eq:cav_sum}
+\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1.
+\end{equation}
+The partition points $(x_i^2)_{i=0}^{n}$ are depicted in Fig.~\ref{fig:caval2}. Note that Eq.~\eqref{eq:cav_sum} approximates the area of $R$. In the limit Eq.~\eqref{eq:cav_sum} approaches 
+the Cavalieri integral:
+\begin{equation}
+\label{eq:caval1}
+\int_{a(y)}^{b(y)}f(x)\, dx = \lim_{n\to \infty}\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1.
+\end{equation}
+It is, however, quite hard to evaluate the above integral directly. Fortunately, it is easy to convert a Cavalieri integral into an equivalent Riemann or Riemann-Stieltjes 
+integral by using the transformation functions $h$ and $g$. Expressed mathematically:
+\begin{equation}
+\label{eq:main_cav}
+\int_{a(y)}^{b(y)}f(x)\,dx =\int_a^b f \circ h (x)\, dx = \int_{a'}^{b'} f(x) dg(x).
+\end{equation}
+We can calculate $g$ as follows:
+\begin{equation}
+g(x) = x - a\circ f(x) + a.
+\end{equation}
+Moreover, $h=g^{-1}$. We can now evaluate the Cavalieri integral by using its equivalent Riemann or Rieman-Stieltjes integral.
+If we use its Riemann equivalent we obtain:
+\begin{equation}
+\int_{a(y)}^{b(y)}f(x)\, dx = \int_a^b f \circ h (x)\, dx = \dfrac{1}{2}\int_1^4x\, dx = 3.75.  
+\end{equation}
+If we use its Riemann-Stieltjes equivalent we obtain:
+\begin{equation}
+\int_{a(y)}^{b(y)}f(x)\, dx = \int_{a'}^{b'} f \, dg(x) = \int_{\frac{1}{2}}^2x\, d2x = 3.75.  
+\end{equation}
+
+\noindent
+Conversely, if $g$ is known (and not $a(y)$) and $g(a') = a$ then we can calculate $a(y)$ using the following \cite{grobler19}:
+\begin{equation}
+\label{eq:a_y}
+a(y) = f^{-1}(y) - g\circ f^{-1}(y) + g(a'). 
+\end{equation}
+Eq.~\eqref{eq:a_y} allows us to transform a Riemann-Stieltjes integral into an equivalent Cavalieri integral. 
+Furthermore, this transformation enables us to assign a geometric interpretation to a Riemann-Stieltjes integral. The interpretation being:
+it represents the area obtained by summing together the area of an infinite number of non-rectangular infinitesimals; all of them being translations of $a(y)$. Note,
+$b(y) = a(y) + (b-a)$.
 

### 2019-07-30 Cav2D/article-template.tex
editing cav definition

@@
 In this section we define the Cavalieri integral \cite{ackermann12}.
-Let the region $R$ be bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$ and $b(y)=4-y$.
-This region is shown in Fig.~\ref{fig:caval2}.\\
+
+Let the region $R$ be bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$ and $b(y)=4-y$. This region is shown in Fig.~\ref{fig:caval2}.\\
 %\begin{figure}[htb]
@@
 %\end{figure}
+
 \begin{figure}[htb]
@@
 \noindent
-The area of $R$ can be determined as follows if we employ the classical notion of integration:
+We can compute the area of $R$ as follows:
 \begin{equation}
@@
 \noindent
+However, the area of $R$ can also be determined via the Cavalieri integral:
+\begin{equation}
+\label{eq:caval1}
+\int_{a(y)}^{b(y)}f(x)\, dx = \lim_{n\to \infty}\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1,
+\end{equation}
+with $\Delta x_i^1 = x_{i+1}^1 - x_i^1$. The partition points $(x_i^1)_{i=0}^{n}$ and $(x_i^2)_{i=0}^{n}$ are depicted in Fig.~\ref{fig:caval2}. Note that 
+$\Delta x_i^1$ and $f(x_i^2)$ can be interpreted as the width and the height of the $i$-th non-rectangular integration strip inscribing $R$. Their product, therefore, represents the 
+area of the aformentioned integration strip. The right hand side of Equation~\eqref{eq:caval1} can therefore be interpreted as the area which 
+is obtained
+
+We can also compute the area of $R$ by summing together non-rectangular integration strips inscribing $R$.
+
 There, however, exists a more straightforward way do determine the area of $R$, i.e. we can sum together the area of non-rectangular integration strips inscribing $R$ instead of

### 2019-07-30 Cav2D/article-template.tex
added starting math for cavalieri parametric 2d

--- 2019-07-24 Cav2D/article-template.tex
@@
 \usepackage{textcomp}
+
+%MAKING THE CAVALIERI INTEGRAL NOTATION
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\makeatletter
+%\let\DOTSI\relax % amsmath support for \dots
+\newcommand*{\cint}{%
+  \DOTSI
+  \mathop{%
+    \mathpalette\@LetterOnInt{\mathbf{c}}%
+  }%
+  \mkern-\thinmuskip % thin space is inserted between two \mathop
+  \int
+}
+\newcommand*{\@LetterOnInt}[2]{%
+  \sbox0{$#1\int\m@th$}%
+  \sbox2{$%
+    \ifx#1\displaystyle
+      \textstyle
+    \else
+      \scriptscriptstyle
+    \fi
+    #2%
+  \m@th$}%
+  \dimen@=.4\dimexpr\ht0+\dp0\relax
+  \ifdim\dimexpr\ht2+\dp2\relax>\dimen@
+    \sbox2{\resizebox*{!}{\dimen@}{\unhcopy2}}%
+  \fi
+  \dimen@=\wd0 %
+  \ifdim\wd2>\dimen@
+    \dimen@=\wd2 %
+  \fi
+  \rlap{\hbox to \dimen@{\hfil
+    $#1\vcenter{\copy2}\m@th$%
+  \hfil}}%
+  \ifdim\dimen@>\wd0 %
+    \kern.5\dimexpr\dimen@-\wd0\relax
+  \fi
+}
+\makeatother
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 base and lateral edges that are non-linear and translations of one another.
+
+\section{Cavalieri Integral}
+In this section we define the Cavalieri integral \cite{ackermann12}.
+
+Let the region $R$ be bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$ and $b(y)=4-y$. This region is shown in Fig.~\ref{fig:caval2}.\\
+%\begin{figure}[htb]
+%\centering
+%\includegraphics[width=0.3\textwidth]{fig12}
+%\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$. Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
+%\label{fig:ex1}
+%\end{figure}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.75\textwidth]{fig13.eps}
+\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$.
+The figure also depicts the partition points $x_i^1$ and $x_i^2$ as used in the Cavalieri sum (see Eq.~\eqref{eq:cav_sum}).
+Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
+\label{fig:caval2}
+\end{figure}
+
+\noindent
+We can compute the area of $R$ as follows:
+\begin{equation}
+\int_0^2x\, dx+\int_2^44-x\, dx- \int_0^{\frac{1}{2}}x\, dx-\int_{\frac{1}{2}}^11-x\, dx = 3.75. 
+\end{equation}
+
+\noindent
+Alternatively, the area of $R$ can also be determined via the Cavalieri integral:
+\begin{equation}
+\label{eq:caval1}
+\int_{a(y)}^{b(y)}f(x)\, dx = \lim_{n\to \infty}\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1,
+\end{equation}
+with $\Delta x_i^1 = x_{i+1}^1 - x_i^1$.
+Furthermore, the partition points $(x_i^1)_{i=0}^{n}$ and $(x_i^2)_{i=0}^{n}$ are depicted in Fig.~\ref{fig:caval2}.
+Let us review why this is in fact the case:
+\begin{itemize}
+ \item $\Delta x_i^1 = x_{i+1}^1 - x_i^1$ represents the width of a non-rectangular integration strip.
+ \item $f(x_i^2)$ represents the height of a non-rectangular integration strip.
+ \item $f(x_i^2)\Delta x_i^1$ represents the height of a non-rectangular integration strip (due to Cavalieri's principle).
+ \item The Cavalieri sum $\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1$, therefore, approximates the area of $R$.
+ \item In the limit the Cavalieri sum, therefore, approaches the area of $R$.
+\end{itemize}
+
+\noindent
+The Cavalieri integral is, however, hard to evaluate directly. Fortunately, it is easy to convert a Cavalieri integral into an equivalent Riemann integral:
+\begin{equation}
+\int_{a(y)}^{b(y)}f(x)\, dx = \int_{a}^{b} f\circ h(x)~dx, 
+\end{equation}
+with $a(0) = a$, $b(0)=b$ and $h = g^{-1}$. Furthermore, $g(x) = x - a\circ f(x) + a$.
+
+\noindent
+The area of $R$ can, therefore, also be computed as follows:
+\begin{equation}
+\int_{a(y)}^{b(y)}f(x)\, dx = \int_a^b f \circ h (x)\, dx = \dfrac{1}{2}\int_1^4x\, dx = 3.75.  
+\end{equation}
+
+\noindent
+Expressing \eqref{eq:caval1} in vector calculus notation
+
+\begin{equation}
+\int_{a(y)}^{b(y)}f(x)\, dx =\cint_a^b f(x)~dx, 
+\end{equation}
+with $\mathbf{c}(t) = <c_x(t),c_y(t)>$ denoting a vector equation that passes through the origin and is a translation of $a(y)$. We can express $a(y)$ as $\mathbf{c}(t) + <a,0>$.
+Note that partition $x_i^1$ and $x_i^2$ are related to each other via: 
+\begin{equation}
+\label{eq:pat_rel}
+<x_i^2,f(x_i^2)> = <x_i^1,0> + <c_x(t),c_y(t)> 
+\end{equation}
+
+It follows from Eq.~\eqref{eq:pat_rel} that 
+\begin{equation}
+c_y(t) = f(x_i^1 + c_x(t)). 
+\end{equation}
+We can therefore express $t$ as a function of $x_i^1$. We can now compute $h(x_i^1) = x_i^1 + t(x_i^1)$.
 

### 2019-07-31 Cav2D/article-template.tex
added some text to reson for needing vector calculus
improved vector notation

@@
 
+As will become apparent later on in the article extending the definition of the Cavalieri integral as it appears in ?? into $\mathbb{R}^3$ is problematic. However,
+if the definition in ?? is first re-expressed in vector calculus notation then it becomes trivial to extend it into $\mathbb{R}^3$.
+
+Let $\mathbf{c}(t) = \left <c_x(t),c_y(t) \right>$ be the vector equation of $a(y)-a$.
+Note that, for every coordinate $(x_i^1,x_i^2) \in [a,b]  [a',b']$ there exists a unique $t\in\mathbb{R}$ such that
+\begin{equation}
+\label{eq:pat_rel}
+\left <x_i^2,f(x_i^2) \right > = \left <x_i^1,0 \right> + \left<c_x(t),c_y(t) \right > 
+\end{equation}
+Equation~\eqref{eq:pat_rel} can be rewritten as
+\begin{equation}
+\label{eq:t_func}
+c_y(t) = f(x_i^1 + c_x(t)).
+\end{equation}
+Equation~\eqref{eq:t_func} implies that $t$ can be expressed in terms of $x_i^1$. We can, therefore, calculate $h(x_i^1)$ using $t(x_i^1)$ via:
+\begin{equation}
+\label{eq:h_func}
+x_i^2 = h(x_i^1) = x_i^1 + c_x\circ t(x_i^1).
+\end{equation}
+Equation~\eqref{eq:h_func} is a trivial consequence of the definition of $h$ and Equation~\eqref{eq:pat_rel}.
+
+and as such $t(x_i^1)$ can be used to determine $h(x_i^1)$.
+i.e. $t$ is a function
+
+It is therefore possible to define $t$ in terms of $x_i^1$.
+
 \noindent

### 2019-08-01 Cav2D/article-template.tex
added more text on cavalieri

--- 2019-07-30 Cav2D/article-template.tex
@@
 \end{equation}
-with $a(0) = a$, $b(0)=b$ and $h = g^{-1}$. Furthermore, $g(x) = x - a\circ f(x) + a$.
+with $a(0) = a$ and $b(0)=b$.
+The function $h$ is known as the transformation function and it maps $x_i^1\in[a,b]$ to $x_i^2\in[a',b']$.
+It can be constructed via the function $g(x) = x - a\circ f(x) + a$ as
+$h=g^{-1}$.
 
@@
 \noindent
-Expressing \eqref{eq:caval1} in vector calculus notation
+Intersestingly, the definition in Eq.~\eqref{??} can also be formulated via vector calculus notation.
+As will become apparent later on in the article extending the definition of the Cavalieri integral as it appears in ??
+into $\mathbb{R}^3$ is problematic.
+However,
+if the definition in ?? is first re-expressed in vector calculus notation then it becomes trivial to extend it into $\mathbb{R}^3$.
 
-\begin{equation}
-\int_{a(y)}^{b(y)}f(x)\, dx =\cint_a^b f(x)~dx, 
-\end{equation}
-with $\mathbf{c}(t) = <c_x(t),c_y(t)>$ denoting a vector equation that passes through the origin and is a translation of $a(y)$. We can express $a(y)$ as $\mathbf{c}(t) + <a,0>$.
-Note that partition $x_i^1$ and $x_i^2$ are related to each other via: 
+\noindent
+Let $\mathbf{c}(t) = \left <c_x(t),c_y(t) \right>$ be the vector equation of $a(y)-a$.
+Note that, for every coordinate $(x_i^1,x_i^2) \in [a,b] \times [a',b']$ there exists a unique $t\in\mathbb{R}$ such that
 \begin{equation}
 \label{eq:pat_rel}
-<x_i^2,f(x_i^2)> = <x_i^1,0> + <c_x(t),c_y(t)> 
+\left <x_i^2,f(x_i^2) \right > = \left <x_i^1,0 \right> + \left<c_x(t),c_y(t) \right >.
 \end{equation}
+We can rewrite Equation~\eqref{eq:pat_rel} as
+\begin{equation}
+\label{eq:t_func}
+c_y(t) = f(x_i^1 + c_x(t)),
+\end{equation}
+which highlights the fact that $t$ is a function of $x_i^1$. If we substitute $t(x_i)$ into Equation~\ref{eq:pat_rel} we obtain
+\begin{equation}
+\label{eq:h_func}
+x_i^2 = x_i^1 + c_x\circ t(x_i^1).
+\end{equation}
+Note that Equation~\eqref{eq:h_func} is nothing more than the function $h$ expressed in terms of $t$, i.e. $x_i^2 = h(x_i^1) = x_i^1 + c_x\circ t(x_i^1)$.
+Equation~\eqref{eq:h_func} implies
 
-It follows from Eq.~\eqref{eq:pat_rel} that 
-\begin{equation}
-c_y(t) = f(x_i^1 + c_x(t)). 
-\end{equation}
-We can therefore express $t$ as a function of $x_i^1$. We can now compute $h(x_i^1) = x_i^1 + t(x_i^1)$.
+% and as such $t(x_i^1)$ can be used to determine $h(x_i^1)$.
+% i.e. $t$ is a function 
+% It is therefore possible to define $t$ in terms of $x_i^1$.  
+% \noindent
+% Expressing \eqref{eq:caval1} in vector calculus notation
+% \begin{equation}
+% \int_{a(y)}^{b(y)}f(x)\, dx =\cint_a^b f(x)~dx, 
+% \end{equation}
+% with $\mathbf{c}(t) = <c_x(t),c_y(t)>$ denoting a vector equation that passes through the origin and is a translation of $a(y)$. We can express $a(y)$ as $\mathbf{c}(t) + <a,0>$.
+% Note that partition $x_i^1$ and $x_i^2$ are related to each other via: 
+% \begin{equation}
+% \label{eq:pat_rel}
+% <x_i^2,f(x_i^2)> = <x_i^1,0> + <c_x(t),c_y(t)> 
+% \end{equation}
+% It follows from Eq.~\eqref{eq:pat_rel} that 
+% \begin{equation}
+% c_y(t) = f(x_i^1 + c_x(t)). 
+% \end{equation}
+% We can therefore express $t$ as a function of $x_i^1$. We can now compute $h(x_i^1) = x_i^1 + t(x_i^1)$.
 

### 2019-08-01 Cav2D/article-template.tex
new notation for cavalieri --- semi nice

@@
 
+Let $\mathbf{c}(t) = \left <c_x(t),c_y(t) \right>$ be the vector equation of $a(y)-a$. The notation which we have been using to denote a Cavalieri integral up until now 
+in the paper was first proposed by Ackermann. Going forward in this paper, however, we propose making use of the following alternative notation:
+\begin{equation}
+\label{eq:new_def_cavalieri}
+\int \limits_{\mathcal{C}} f(x)~dx := \int_{a(y)}^{b(y)}f(x)~dx,
+\end{equation}
+with $\mathcal{C} = \{\mathbf{c}(t),[a,b]\}$. Note that $\left<a,0\right> + \mathbf{c}(t)$ and $\left<b,0\right> + \mathbf{c}(t)$ are the vector equations of $a(y)$ and 
+$b(y)$. The reason for this change in notation will become clear to the reader at a later stage. In turns out, that we can use $\mathbf{c}(t)$ to construct $h(x)$ via:
+\begin{equation}
+\label{eq:h_func}
+x_i^2 = h(x_i^1) = x_i^1 + c_x\circ t(x_i^1).
+\end{equation}
+
+\noindent
+We will now show that this is indeed the case. Note that, for every coordinate $(x_i^1,x_i^2) \in [a,b] \times [a',b']$ there exists a unique $t\in\mathbb{R}$ such that
+\begin{equation}
+\label{eq:pat_rel}
+\left <x_i^2,f(x_i^2) \right > = \left <x_i^1,0 \right> + \left<c_x(t),c_y(t) \right >.
+\end{equation}
+We can rewrite Equation~\eqref{eq:pat_rel} as
+\begin{equation}
+\label{eq:t_func}
+c_y(t) = f(x_i^1 + c_x(t)).
+\end{equation}
+We can now solve for $t$ in Equation~\eqref{eq:t_func} in terms of $x_i^1$. If we substitute the solution $t(x_i)$ into Equation~\ref{eq:pat_rel} we obtain Equation~\ref{eq:h_func}.
+
+In turns out that $h$ can be constructed
+
+as the reader progresses through the paper. As will become apparent later on in this paper defining your Cavalieri integral in terms of $\mathbf{c}(t)$ instead of 
+$a(y)$ makes it trivial to extend its defintion into $\mathbb{R}^3$.
+
+In Equation~\eqref{eq:new_def_cavalieri}, we denote the $\{\mathbf{c}(t),[a,b]\}$ via $\mathcal{C}$. Furthermore, $\mathbf{c}(t)$ denotes the vector equation of 
+$a(y)-a$.
+
+an alternative notation
+
 \noindent
@@
 However,
-if the definition in ?? is first re-expressed in vector calculus notation then it becomes trivial to extend it into $\mathbb{R}^3$.
+if the definition in ?? is first re-expressed in vector calculus notation then it becomes trivial to extend it into $\mathbb{R}^3$.\\
 
 \noindent
-Let $\mathbf{c}(t) = \left <c_x(t),c_y(t) \right>$ be the vector equation of $a(y)-a$.
-Note that, for every coordinate $(x_i^1,x_i^2) \in [a,b] \times [a',b']$ there exists a unique $t\in\mathbb{R}$ such that
+We will now show that this is indeed the case. Note that, for every coordinate $(x_i^1,x_i^2) \in [a,b] \times [a',b']$ there exists a unique $t\in\mathbb{R}$ such that
 \begin{equation}
@@
 \label{eq:t_func}
-c_y(t) = f(x_i^1 + c_x(t)),
+c_y(t) = f(x_i^1 + c_x(t)).
 \end{equation}
-which highlights the fact that $t$ is a function of $x_i^1$. If we substitute $t(x_i)$ into Equation~\ref{eq:pat_rel} we obtain
+We can now solve for $t$ in Equation~\eqref{eq:t_func} in terms of $x_i^1$. If we substitute the solution $t(x_i)$ into Equation~\ref{eq:pat_rel} we obtain
 \begin{equation}
@@
 Note that Equation~\eqref{eq:h_func} is nothing more than the function $h$ expressed in terms of $t$, i.e. $x_i^2 = h(x_i^1) = x_i^1 + c_x\circ t(x_i^1)$.
+We can, therefore compute $h(x)$ from $\mathbf{c}(t)$ and as such we can can define the Cavalieri integral in terms of $\mathbf{c}(t)$ instead of $a(y)$. In light 
+of this observation we propose the following alternative notation to denote a Cavalieri integral 
+\begin{equation}
+\int  
+\end{equation}
+
 Equation~\eqref{eq:h_func} implies

### 2019-08-06 Cav2D/func_plotter.py
started adding some annotations to the plot --- useful for article

@@ -267,7 +267,7 @@ def plot_figures(xx,yy,xx2,yy2,zz2,K=8):
     
     vrtx = [[V1,V2,V4,V3]]  
  
-    faces = Poly3DCollection(vrtx, linewidths=1, edgecolors='k',facecolors='red',alpha=0.3)
+    faces = Poly3DCollection(vrtx, linewidths=2, edgecolors='k',facecolors='red',alpha=0.3)
     faces.set_facecolor((1,0,0,0.1))
 
     ax.add_collection3d(faces)
@@ -384,6 +384,633 @@ def plot_figures(xx,yy,xx2,yy2,zz2,K=8):
     print(np.sum(v))
 
     ############################################################
+
+def plot_paper_figure(xx,yy,xx2,yy2,zz2,K=8):
+    
+
+    #PLOT PLANE
+    ############################################################
+    # create x,y
+    xx_new, yy_new = np.meshgrid(range(7), range(7))
+
+    # calculate corresponding z
+    z = -1*yy_new -1*xx_new + K
+
+    plt3d = plt.figure().gca(projection='3d')
+    plt3d.plot_surface(xx2, yy2, zz2, alpha=0.2)
+
+    #plt3d.plot_surface(xx_new, yy_new, z, alpha=0.2)
+
+    ax = plt.gca()
+    ax.hold(True)
+    ############################################################
+    
+    #ax.scatter3D(xx2.flatten(), yy2.flatten(), zz2.flatten() ,c="b",alpha=0.2); 
+    #ax.scatter3D(xx.flatten(), yy.flatten(), np.zeros((len(yy.flatten()),),dtype=float) ,c="r",alpha=0.2); 
+    
+    #PLOT VOLUME
+    ############################################################
+    volume = np.zeros((8,3),dtype=float)
+
+    volume[0,0] = xx[0,0]
+    volume[0,1] = yy[0,0]
+    volume[1,0] = xx[0,-1]
+    volume[1,1] = yy[0,-1]
+    volume[2,0] = xx[-1,0]
+    volume[2,1] = yy[-1,0]
+    volume[3,0] = xx[-1,-1]
+    volume[3,1] = yy[-1,-1]
+
+    volume[4,0] = xx2[0,0]
+    volume[4,1] = yy2[0,0]
[…]

### 2019-08-07 Cav2D/func_plotter.py
started polishing paper figures

@@ -397,7 +397,7 @@ def plot_paper_figure(xx,yy,xx2,yy2,zz2,K=8):
     z = -1*yy_new -1*xx_new + K
 
     plt3d = plt.figure().gca(projection='3d')
-    plt3d.plot_surface(xx2, yy2, zz2, alpha=0.2)
+    plt3d.plot_surface(xx2, yy2, zz2, color="red",alpha=0.2)
 
     #plt3d.plot_surface(xx_new, yy_new, z, alpha=0.2)
 
@@ -435,15 +435,15 @@ def plot_paper_figure(xx,yy,xx2,yy2,zz2,K=8):
     volume[7,2] = zz2[-1,-1]
 
     ax.plot3D(np.array([volume[0,0],volume[1,0]]), np.array([volume[0,1],volume[1,1]]), np.array([volume[0,2],volume[1,2]]), 'black') 
-    ax.plot3D(np.array([volume[1,0],volume[3,0]]), np.array([volume[1,1],volume[3,1]]), np.array([volume[1,2],volume[3,2]]), 'black',ls="--") 
+    ax.plot3D(np.array([volume[1,0],volume[3,0]]), np.array([volume[1,1],volume[3,1]]), np.array([volume[1,2],volume[3,2]]), 'black') 
     ax.plot3D(np.array([volume[3,0],volume[2,0]]), np.array([volume[3,1],volume[2,1]]), np.array([volume[3,2],volume[2,2]]), 'black',ls="--") 
-    ax.plot3D(np.array([volume[2,0],volume[0,0]]), np.array([volume[2,1],volume[0,1]]), np.array([volume[2,2],volume[0,2]]), 'black') 
+    ax.plot3D(np.array([volume[2,0],volume[0,0]]), np.array([volume[2,1],volume[0,1]]), np.array([volume[2,2],volume[0,2]]), 'black',ls="--") 
     ax.plot3D(np.array([volume[4,0],volume[5,0]]), np.array([volume[4,1],volume[5,1]]), np.array([volume[4,2],volume[5,2]]), 'black') 
     ax.plot3D(np.array([volume[5,0],volume[7,0]]), np.array([volume[5,1],volume[7,1]]), np.array([volume[5,2],volume[7,2]]), 'black') 
[…]

### 2019-08-07 Cav2D/article-template.tex
added most of the images to the article

@@
 
+\noindent
+The area of $R$ can, therefore, also be computed as follows:
+\begin{equation}
+\int_{a(y)}^{b(y)}f(x)\, dx = \int_a^b f \circ h (x)\, dx = \dfrac{1}{2}\int_1^4x\, dx = 3.75.  
+\end{equation}
+
 Let $\mathbf{c}(t) = \left <c_x(t),c_y(t) \right>$ be the vector equation of $a(y)-a$. The notation which we have been using to denote a Cavalieri integral up until now 
@@
 \end{equation}
-We can now solve for $t$ in Equation~\eqref{eq:t_func} in terms of $x_i^1$. If we substitute the solution $t(x_i)$ into Equation~\ref{eq:pat_rel} we obtain Equation~\ref{eq:h_func}.
+We can now solve for $t$ in Equation~\eqref{eq:t_func} in terms of $x_i^1$. If we substitute the solution $t(x_i)$ so obtained into Equation~\ref{eq:pat_rel} we obtain Equation~\ref{eq:h_func}.
 
-In turns out that $h$ can be constructed
+In the case of $R$ we have that $\mathbf{c}(t) = \left<-\frac{1}{2} t,\frac{1}{2} t\right>$. If we solve for $t$ in terms of $x_i^1$ after having substituted $\mathbf{c}(t)$ into Eq we obtain 
+$t(x_i^1) = x_i^1$. If we now substitute our solution $t(x_i^1)$ into Eq we obtain, as required, $h(x_i^1) = \frac{1}{2}x_i^2$. This result, therefore, validates Eq ??.
 
-as the reader progresses through the paper. As will become apparent later on in this paper defining your Cavalieri integral in terms of $\mathbf{c}(t)$ instead of 
-$a(y)$ makes it trivial to extend its defintion into $\mathbb{R}^3$.
+\section{Two Dimensional Cavalieri Integral}
 
-In Equation~\eqref{eq:new_def_cavalieri}, we denote the $\{\mathbf{c}(t),[a,b]\}$ via $\mathcal{C}$. Furthermore, $\mathbf{c}(t)$ denotes the vector equation of 
-$a(y)-a$.
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.75\textwidth]{prismatoid.pdf}
+\caption{xx}
+\label{fig:prismatoid}
+\end{figure}
 
-an alternative notation
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.5\textwidth]{prismatoid_real.jpg}
+\caption{xx}
+\label{fig:prismatoid_real}
+\end{figure}
 
-\noindent
-The area of $R$ can, therefore, also be computed as follows:
-\begin{equation}
-\int_{a(y)}^{b(y)}f(x)\, dx = \int_a^b f \circ h (x)\, dx = \dfrac{1}{2}\int_1^4x\, dx = 3.75.  
-\end{equation}
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.75\textwidth]{prismatoid_solid.pdf}
+\caption{xx}
+\label{fig:prismatoid_solid}
+\end{figure}
 
-\noindent
-Intersestingly, the definition in Eq.~\eqref{??} can also be formulated via vector calculus notation.
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.75\textwidth]{prismatoid_regions.pdf}
+\caption{xx}
+\label{fig:prismatoid_solid}
+\end{figure}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.75\textwidth]{prismatoid_xy.pdf}
+\caption{xx}
+\label{fig:prismatoid_solid}
+\end{figure}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.75\textwidth]{sphere_solid.pdf}
+\caption{xx}
+\label{fig:prismatoid_solid}
+\end{figure}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.75\textwidth]{sphere_regions.pdf}
+\caption{xx}
+\label{fig:prismatoid_solid}
+\end{figure}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.75\textwidth]{sphere_xy.pdf}
+\caption{xx}
+\label{fig:prismatoid_solid}
+\end{figure}
+
+%in In turns out that $h$ can be constructed 
+%as the reader progresses through the paper. As will become apparent later on in this paper defining your Cavalieri integral in terms of $\mathbf{c}(t)$ instead of 
+%$a(y)$ makes it trivial to extend its defintion into $\mathbb{R}^3$.
+%In Equation~\eqref{eq:new_def_cavalieri}, we denote the $\{\mathbf{c}(t),[a,b]\}$ via $\mathcal{C}$. Furthermore, $\mathbf{c}(t)$ denotes the vector equation of 
+%$a(y)-a$.
+%an alternative notation
+
+% \noindent
+% Intersestingly, the definition in Eq.~\eqref{??} can also be formulated via vector calculus notation.
 As will become apparent later on in the article extending the definition of the Cavalieri integral as it appears in ??
@@
 However,
-if the definition in ?? is first re-expressed in vector calculus notation then it becomes trivial to extend it into $\mathbb{R}^3$.\\
-
-\noindent
-We will now show that this is indeed the case. Note that, for every coordinate $(x_i^1,x_i^2) \in [a,b] \times [a',b']$ there exists a unique $t\in\mathbb{R}$ such that
-\begin{equation}
-\label{eq:pat_rel}
-\left <x_i^2,f(x_i^2) \right > = \left <x_i^1,0 \right> + \left<c_x(t),c_y(t) \right >.
-\end{equation}
-We can rewrite Equation~\eqref{eq:pat_rel} as
-\begin{equation}
-\label{eq:t_func}
-c_y(t) = f(x_i^1 + c_x(t)).
-\end{equation}
-We can now solve for $t$ in Equation~\eqref{eq:t_func} in terms of $x_i^1$. If we substitute the solution $t(x_i)$ into Equation~\ref{eq:pat_rel} we obtain
-\begin{equation}
-\label{eq:h_func}
-x_i^2 = x_i^1 + c_x\circ t(x_i^1).
-\end{equation}
-Note that Equation~\eqref{eq:h_func} is nothing more than the function $h$ expressed in terms of $t$, i.e. $x_i^2 = h(x_i^1) = x_i^1 + c_x\circ t(x_i^1)$.
-We can, therefore compute $h(x)$ from $\mathbf{c}(t)$ and as such we can can define the Cavalieri integral in terms of $\mathbf{c}(t)$ instead of $a(y)$. In light 
-of this observation we propose the following alternative notation to denote a Cavalieri integral 
-\begin{equation}
-\int  
-\end{equation}
-
-Equation~\eqref{eq:h_func} implies
+% if the definition in ?? is first re-expressed in vector calculus notation then it becomes trivial to extend it into $\mathbb{R}^3$.\\
+% 
+% \noindent
+% We will now show that this is indeed the case. Note that, for every coordinate $(x_i^1,x_i^2) \in [a,b] \times [a',b']$ there exists a unique $t\in\mathbb{R}$ such that
+% \begin{equation}
+% \label{eq:pat_rel}
+% \left <x_i^2,f(x_i^2) \right > = \left <x_i^1,0 \right> + \left<c_x(t),c_y(t) \right >.
+% \end{equation}
+% We can rewrite Equation~\eqref{eq:pat_rel} as
+% \begin{equation}
+% \label{eq:t_func}
+% c_y(t) = f(x_i^1 + c_x(t)).
+% \end{equation}
+% We can now solve for $t$ in Equation~\eqref{eq:t_func} in terms of $x_i^1$. If we substitute the solution $t(x_i)$ into Equation~\ref{eq:pat_rel} we obtain
+% \begin{equation}
+% \label{eq:h_func}
+% x_i^2 = x_i^1 + c_x\circ t(x_i^1).
+% \end{equation}
+% Note that Equation~\eqref{eq:h_func} is nothing more than the function $h$ expressed in terms of $t$, i.e. $x_i^2 = h(x_i^1) = x_i^1 + c_x\circ t(x_i^1)$.
+% We can, therefore compute $h(x)$ from $\mathbf{c}(t)$ and as such we can can define the Cavalieri integral in terms of $\mathbf{c}(t)$ instead of $a(y)$. In light 
+% of this observation we propose the following alternative notation to denote a Cavalieri integral 
+% \begin{equation}
+% \int  
+% \end{equation}
 

### 2019-08-07 Cav2D/article-template.tex
added most of the figures to the article

@@
 In 1935, a moon crater, Cavalerius, was officially named after him to commemorate his achievements and to honor his memory (see Fig ) \cite{?}.
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.4\textwidth]{crater.jpg}
+\caption{xx}
+\label{fig:crater}
+\end{figure}
 Cavalieri's most notable achievement was the publication of his 
@@
 \end{theorem}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.5\textwidth]{cav_principle.pdf}
+\caption{xx}
+\label{fig:cav_principle}
+\end{figure}
 

### 2019-08-07 Cav2D/article-template.tex
added some description of the prismatoid S

@@
 \section{Two Dimensional Cavalieri Integral}
+Let $\mathcal{S}$ be the solid which is bounded by the planes $f(x,y)=-x-y+8$, $2x$, $2(x-4)$, $y$, $y-4$ as well as the $xy$-plane. Solid $\mathcal{S}$ is depicted 
+in Figure~\ref{fig:prismatoid}, Figure~\ref{fig:prismatoid_real} and Figure~\ref{fig:prismatoid_solid}. Solid $\mathcal{S}$ is a prismatoid, since all of its 
+vertices lie in two parallel planes. Furthermore, all of its lateral faces are trapezoids or triangles. The volume of $S$ can easily be computed using the 
+volume equation of a prismatoid. The details of this computation is described in the caption of Figure~\ref{fig:prismatoid}.
 

### 2019-08-07 Cav2D/article-template.tex
added small definition of R and S

@@
 \section{Two Dimensional Cavalieri Integral}
-Let $\mathcal{S}$ be the solid which is bounded by the planes $f(x,y)=-x-y+8$, $2x$, $2(x-4)$, $y$, $y-4$ as well as the $xy$-plane. Solid $\mathcal{S}$ is depicted 
+Let $\mathcal{S}$ be the solid which is bounded by the planes $f(x,y)=-x-y+8$, $2x$, $2(x-4)$, $y$, $y-4$ and the $xy$-plane. Solid $\mathcal{S}$ is depicted 
 in Figure~\ref{fig:prismatoid}, Figure~\ref{fig:prismatoid_real} and Figure~\ref{fig:prismatoid_solid}. Solid $\mathcal{S}$ is a prismatoid, since all of its 
-vertices lie in two parallel planes. Furthermore, all of its lateral faces are trapezoids or triangles. The volume of $S$ can easily be computed using the 
-volume equation of a prismatoid. The details of this computation is described in the caption of Figure~\ref{fig:prismatoid}.
+vertices lie in two parallel planes. Furthermore, all of its lateral faces are trapezoids or triangles. The volume of $\mathcal{S}$, $V_{\mathcal{S}}$, can easily be computed using the 
+volume equation of a prismatoid. The details of this computation is described in the caption of Figure~\ref{fig:prismatoid}. According to the prismatoid volume 
+equation $V_{\mathcal{S}}=25.6$.
+
+Note that $\mathbf{c}(t) = -\left<\frac{1}{2}t,t,t\right>$ is the line of intersection between the planes $2x$ and $y$. Furthermore, the line 
+$\mathbf{c}(t)$ passes through the origin. The line $\mathbf{c}(t)$ is depicted and labelled in Figure~\ref{fig:prismatoid_solid}. Let 
+\begin{equation}
+R = \{(x,y)\in\mathbb{R}^2|0 \geq x \geq 4, 0 \geq x \geq 4\} \nonumber
+\end{equation}
+and
+\begin{equation}
+S = \{(x,y)\in\mathbb{R}^2|-\sfrac{1}{3}y+\sfrac{8}{3}\geq x\geq -\sfrac{1}{3}y+\sfrac{16}{3}, \sfrac{1}{2} x + 4\geq y \geq \sfrac{1}{2} x + 6 \}. \nonumber
+\end{equation}
+The region $S$ and $R$ is depicted in Figure~\ref{fig:prismatoid_solid} and Figure~\ref{fig:prismatoid_regions}.
+Furthermore, let the transformation $T$ map the $xy$--coordinate $(x_i^1,y_i^1)\in R$ at which $\mathbf{c}(t) + \left <x_i^1,y_i^2,0 \right >$ intersects the
+$xy$-plane to the $xy$--coordinate $(x_i^2,y_i^2)\in S$ at which $\mathbf{c}(t) + \left <x_i^1,y_i^2,0 \right >$ intersects $f(x,y)$.
+
+$R = \{(x,y)\in\mathbb{R}^2|0 \geq x \geq 4, 0 \geq x \geq 4\}$
+and $S = \{(x,y)\in\mathbb{R}^2|-\sfrac{1}{3}y+\sfrac{8}{3}\geq x\leq -\sfrac{1}{3}y+\sfrac{16}{3} \}$.
+
+The line $\mathbf{c}(t)$  is depicted and labelled in
 
@@
 \caption{xx}
-\label{fig:prismatoid_solid}
+\label{fig:prismatoid_regions}
 \end{figure}
@@
 \caption{xx}
-\label{fig:prismatoid_solid}
+\label{fig:prismatoid_xy}
 \end{figure}
@@
 \caption{xx}
-\label{fig:prismatoid_solid}
+\label{fig:sphere_solid}
 \end{figure}
@@
 \caption{xx}
-\label{fig:prismatoid_solid}
+\label{fig:sphere_regions}
 \end{figure}

### 2019-08-07 Cav2D/article-template.tex
added more text to two dimensional definition

@@
  \item $f(x_i^2)$ represents the height of a non-rectangular integration strip.
- \item $f(x_i^2)\Delta x_i^1$ represents the height of a non-rectangular integration strip (due to Cavalieri's principle).
+ \item $f(x_i^2)\Delta x_i^1$ represents the area of a non-rectangular integration strip (due to Cavalieri's principle).
  \item The Cavalieri sum $\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1$, therefore, approximates the area of $R$.
@@
 \end{equation}
-The region $S$ and $R$ is depicted in Figure~\ref{fig:prismatoid_solid} and Figure~\ref{fig:prismatoid_regions}.
-Furthermore, let the transformation $T$ map the $xy$--coordinate $(x_i^1,y_i^1)\in R$ at which $\mathbf{c}(t) + \left <x_i^1,y_i^2,0 \right >$ intersects the
-$xy$-plane to the $xy$--coordinate $(x_i^2,y_i^2)\in S$ at which $\mathbf{c}(t) + \left <x_i^1,y_i^2,0 \right >$ intersects $f(x,y)$.
+The region $S$ and $R$ is depicted in Figure~\ref{fig:prismatoid_solid} and Figure~\ref{fig:prismatoid_regions}. Let us now subdivide $R$ into 
+subrectangles $R_{ij} = [x_{i},x_{i+1}] \times [y_{j},y_{j+1}]$ of equal width $\Delta x^1 = \Delta x_i^1 = x_{i+1}-x_i$ and length $\Delta y^1= \Delta y_j^1 = y_{j+1}-y_j$. 
+Furthermore, let the transformation $T$ map the $xy$--coordinate $(x_i^1,y_i^1)\in R$ at which $\mathbf{c}(t) + \left <x_i^1,y_i^1,0 \right >$ intersects the 
+$xy$-plane to the $xy$--coordinate $(x_i^2,y_j^2)\in S$ at which $\mathbf{c}(t) + \left <x_i^1,y_j^1,0 \right >$ intersects $f(x,y)$. 
+We can now approximate $\mathcal{S}_V$ via:
+\begin{equation}
+V_{\mathcal{S}} \approx \sum_{i=0}^n \sum_{j=0}^m f(x_i^2,y_j^2) \Delta x_i^1 \Delta y_j^1.
+\end{equation}
 

### 2019-08-08 Cav2D/article-template.tex
added initial formula for cav 2d

--- 2019-08-07 Cav2D/article-template.tex
@@
 
-\section{Two Dimensional Cavalieri Integral}
+\section{Double Cavalieri Integral}
 Let $\mathcal{S}$ be the solid which is bounded by the planes $f(x,y)=-x-y+8$, $2x$, $2(x-4)$, $y$, $y-4$ and the $xy$-plane. Solid $\mathcal{S}$ is depicted 
@@
 
-Note that $\mathbf{c}(t) = -\left<\frac{1}{2}t,t,t\right>$ is the line of intersection between the planes $2x$ and $y$. Furthermore, the line 
+Let $\mathbf{c}(t) = -\left<\frac{1}{2}t,t,t\right>$ be the line of intersection between the planes $2x$ and $y$. Furthermore, note that the line 
 $\mathbf{c}(t)$ passes through the origin. The line $\mathbf{c}(t)$ is depicted and labelled in Figure~\ref{fig:prismatoid_solid}. Let 
@@
 \begin{equation}
-S = \{(x,y)\in\mathbb{R}^2|-\sfrac{1}{3}y+\sfrac{8}{3}\geq x\geq -\sfrac{1}{3}y+\sfrac{16}{3}, \sfrac{1}{2} x + 4\geq y \geq \sfrac{1}{2} x + 6 \}. \nonumber
+S = \{(x,y)\in\mathbb{R}^2|-\sfrac{1}{3}y+\sfrac{8}{3}\leq x\leq -\sfrac{1}{3}y+\sfrac{16}{3}, \sfrac{1}{2} x + 4\leq y \leq \sfrac{1}{2} x + 6 \}. \nonumber
 \end{equation}
-The region $S$ and $R$ is depicted in Figure~\ref{fig:prismatoid_solid} and Figure~\ref{fig:prismatoid_regions}.
-Furthermore, let the transformation $T$ map the $xy$--coordinate $(x_i^1,y_i^1)\in R$ at which $\mathbf{c}(t) + \left <x_i^1,y_i^2,0 \right >$ intersects the
-$xy$-plane to the $xy$--coordinate $(x_i^2,y_i^2)\in S$ at which $\mathbf{c}(t) + \left <x_i^1,y_i^2,0 \right >$ intersects $f(x,y)$.
+The region $S$ and $R$ are depicted in Figure~\ref{fig:prismatoid_solid} and Figure~\ref{fig:prismatoid_regions}. Let us now subdivide $R$ into $n\times m$
+subrectangles $R_{ij} = [x_{i},x_{i+1}] \times [y_{j},y_{j+1}]$ of equal width $\Delta x^1 = \Delta x_i^1 = x_{i+1}-x_i$ and length $\Delta y^1= \Delta y_j^1 = y_{j+1}-y_j$. 
+Furthermore, let the transformation $T$ map the $xy$--coordinate $(x_i^1,y_i^1)\in R$ (the lower left vertice of $R_{ij}$) at which $\mathbf{c}(t) + \left <x_i^1,y_i^1,0 \right >$ intersects the 
+$xy$-plane to the $xy$--coordinate $(x_i^2,y_j^2)\in S$ at which $\mathbf{c}(t) + \left <x_i^1,y_j^1,0 \right >$ intersects $f(x,y)$ (Figure~\ref{fig:prismatoid_solid} and Figure~\ref{fig:prismatoid_regions}).
+%The transformation $T$ is defined by the following equations:
+%\begin{equation}
+%x_i^2 = h(x_i^1,y_i^1)
+%\end{equation}
+%and
+%\begin{equation}
+%y_i^2 = s(x_i^1,y_i^1)
+%\end{equation}
+We can approximate $\mathcal{S}_V$ via:
+\begin{equation}
+V_{\mathcal{S}} \approx \sum_{i=0}^{n-1} \sum_{j=0}^{m-1} f(x_i^2,y_j^2) \Delta x_i^1 \Delta y_j^1.
+\end{equation}
+Let us verify that this is indeed the case:
+\begin{itemize}
+\item $\Delta x_i^1$ and $\Delta y_i^i$ represent the width and the length of subrectangle $R_{ij}$.
+\item The product $\Delta A = \Delta x_i^1\times \Delta y_i^i$ represent the area of subrectangle $R_{ij}$.
+\item $f(x_i^2,y_i^2)$ represents the height of a non-linear rectangular column or prism $\mathcal{K}_{ij}$ whose base is $R_{ij}$. Furthermore, the lateral edges of this column are all translations 
+of $\mathbf{c}(t)$ along the $xy$-plane. 
+\item The product $f(x_i^2,y_i^2)\times \Delta A$ represents the volume of $\mathcal{K}_{ij}$ (due to Cavalieri's principle).
+\item The double Cavalieri sum $\sum_{i=0}^{n-1} \sum_{j=0}^{m-1} f(x_i^2,y_j^2) \Delta A$, therefore, approximates $V_{\mathcal{S}}$. 
+\item In the limit the double Cavalieri sum approaches $V_{\mathcal{S}}$ (if this limit exists). 
+\end{itemize}
+
+In this paper, we will refer to aformentioned limit as the two dimensional Cavalieri integral and we will denote this integral as follows:
+
+\begin{equation}
+\label{eq:cav_2d}
+\iint \limits_{\mathcal{C}} f(x,y)~dA = \lim_{n,m \rightarrow \infty}  \sum_{i=0}^{n-1} \sum_{j=0}^{m-1} f(x_i^2,y_j^2) \Delta x_i^1 \Delta y_j^1,
+\end{equation}
+with $\mathcal{C} = \{\mathbf{c}(t),R\}$. As is the case for the single Cavalieri integral, Equation~\eqref{eq:cav_2d} is difficult to evaluate in its current form. Luckily, the double 
+Cavalieri integral can be converted into an equivalent Riemann integral using the transformation $T$. In general the transformation $T$ is defined via the following 
+equations:
+\begin{equation}
+x_i^2 = h(x_i^1,y_i^2)~\textrm{and}~y_i^2 = s(x_i^1,y_i^1) 
+\end{equation}
+We can now rewrite Equation~\eqref{eq:cav_2d} as follows:
+
+\begin{eqnarray}
+\iint\limits_{\!\mathcal{C}} f(x,y) dA &=& \lim_{n,m\rightarrow \infty} \sum_{j=1}^n\sum_{i=1}^n f(x_{ij}^2,y_{ij}^2) \Delta x_{ij}^1\Delta y_{ij}^1\\
+&=&  \lim_{n,m\rightarrow \infty} \sum_{j=1}^n\sum_{i=1}^n f(g(x_{ij}^1,y_{ij}^1),r(x_{ij}^1,y_{ij}^1)) \Delta x_{ij}^1\Delta y_{ij}^1\\
+&=& \int_a^b\int_c^d f(g(x,y),r(x,y))~dx~dy.
+\end{eqnarray}
+
+Note that, for every coordinate pair there exists a unique $t\in \mathbb{R}$ such that
+
+\begin{equation}
+\label{eq:vector_2}
+\left< x_i^2, y_i^2, f(x_i^2,y_i^2) \right > = \left < x_i^1, y_i^1, 0 \right > + \left <c_x(t),c_y(t),c_z(t)\right >  
+\end{equation}
+
+The above equation can be re-expressed as
+
+\begin{equation}
+c_z(t) = f(x_i^1 + c_x(t),y_i^1 + c_y(t)). 
+\end{equation}
+
+We can now solve for $t$ in terms of $x_i^1$ and $y_i^1$. If we substitute this solution into Equation~\ref{eq:vector_2} we obtain
+
+\begin{equation}
+x_i^2 = h(x_i^1,y_i^1) = x_i^1 + c_x\circ t(x_i^1,y_i^1) 
+\end{equation}
+and 
+\begin{equation}
+y_i^2 = s(x_i^1,y_i^1) = y_i^1 + c_y\circ t(x_i^1,y_i^1) 
+\end{equation}
 

### 2019-08-12 Cav2D/article-template.tex
added some definitions of c

@@
 \section{Double Cavalieri Integral}
+Without any the loss of generality, let $R = [a,b]\times [c,d] = \{(x,y)\in \mathbb{R}^2|a \leq x \leq b, c \leq y \leq d\}$.
+If a curve $\mathbf{c}(t) = \left <c_x(t),c_y(t), c_z(t) \right >$ in $\mathbb{R}^3$ intersects the $xy$ plane at the origin and $\mathbf{c}(t) + \left < e,f,0 \right >$ intersects 
+the surface $f(x,y)$ at a single point for all $(e,f)\in R$ then $\mathbf{c}(t)$ is a translational curve 
+with respect to $f(x,y)$ on $R$.
+Let us now subdivide $R$ into $n\times m$ subrectangles $R_{ij} = [x_{i},x_{i+1}] \times [y_{j},y_{j+1}]$ of equal width $\Delta x^1 = \Delta x_i^1 = x_{i+1}-x_i\ll (b-a)$ and length $\Delta y^1= \Delta y_j^1 = y_{j+1}-y_j\ll(d-c)$.
+Furthermore, let the transformation $T$ map the $xy$--coordinate $(x_i^1,y_i^1)\in R$ (the lower left vertice of $R_{ij}$) at which $\mathbf{c}(t) + \left <x_i^1,y_i^1,0 \right >$ intersects the 
+$xy$-plane to the $xy$--coordinate at which $\mathbf{c}(t) + \left <x_i^1,y_j^1,0 \right >$ intersects $f(x,y)$. Note, the domain of $T$ is $R$. Moreover, let us denote the range 
+of $T$ with $\mathcal{S}$. The transformation $T:R\rightarrow S$ maps every point $(x_i^1,y_i^1)\in R$ to a point $(x_i^2,y_i^2)\in S$ and is formally defined as follows:
+\begin{equation}
+x_i^2 = h(x_i^1,y_i^1) = x_i^1 + c_x\circ t(x_i^1,y_i^1) 
+\end{equation}
+and 
+\begin{equation}
+y_i^2 = s(x_i^1,y_i^1) = y_i^1 + c_y\circ t(x_i^1,y_i^1). 
+\end{equation}
+
 Let $\mathcal{S}$ be the solid which is bounded by the planes $f(x,y)=-x-y+8$, $2x$, $2(x-4)$, $y$, $y-4$ and the $xy$-plane. Solid $\mathcal{S}$ is depicted 
@@
 The region $S$ and $R$ are depicted in Figure~\ref{fig:prismatoid_solid} and Figure~\ref{fig:prismatoid_regions}. Let us now subdivide $R$ into $n\times m$
-subrectangles $R_{ij} = [x_{i},x_{i+1}] \times [y_{j},y_{j+1}]$ of equal width $\Delta x^1 = \Delta x_i^1 = x_{i+1}-x_i$ and length $\Delta y^1= \Delta y_j^1 = y_{j+1}-y_j$. 
+subrectangles $R_{ij} = [x_{i},x_{i+1}] \times [y_{j},y_{j+1}]$ of equal width $\Delta x^1 = \Delta x_i^1 = x_{i+1}-x_i<<(b-a)$ and length $\Delta y^1= \Delta y_j^1 = y_{j+1}-y_j<<(d-c)$. 
 Furthermore, let the transformation $T$ map the $xy$--coordinate $(x_i^1,y_i^1)\in R$ (the lower left vertice of $R_{ij}$) at which $\mathbf{c}(t) + \left <x_i^1,y_i^1,0 \right >$ intersects the 

### 2019-08-12 Cav2D/article-template.tex
added definition of S

@@
 \begin{equation}
-x_i^2 = h(x_i^1,y_i^1) = x_i^1 + c_x\circ t(x_i^1,y_i^1) 
+x_i^2 = h(x_i^1,y_i^1)~\textrm{and}~y_i^2 = s(x_i^1,y_i^1).
 \end{equation}
-and 
+Let $\mathcal{S}$ denote a solid that has the following charachteristics:
+\begin{itemize}
+ \item $R$ and $S_f = \{(x,y,z)\in\mathbb{R}^3|(x,y)\in S ~ \textrm{and} ~ z=f(x,y)\}$ as basis.
+ \item The following four lateral edges:
+ \begin{itemize}
+ \item The segement of $\mathbf{c}(t) + \left <a, c,0\right>$ which starts at $(a,c,0)$ and ends at $(h(a,c),s(a,c),f(h(a,c),s(a,c))$.
+ \item The segement of $\mathbf{c}(t) + \left <a, d,0\right>$ which starts at $(a,d,0)$ and ends at $(h(a,d),s(a,d),f(h(a,d),s(a,d))$.
+ \item The segement of $\mathbf{c}(t) + \left <b, c,0\right>$ which starts at $(b,c,0)$ and ends at \\$(h(b,c),s(b,c),f(h(b,c),s(b,c))$.
+ \item The segement of $\mathbf{c}(t) + \left <b, d,0\right>$ which starts at $(b,d,0)$ and ends at $(h(b,d),s(b,d),f(h(b,d),s(b,d))$.
+ \end{itemize}
+\end{itemize}
+We can approximate the volume of $\mathcal{S}$, $\mathcal{S}_V$, via:
 \begin{equation}
-y_i^2 = s(x_i^1,y_i^1) = y_i^1 + c_y\circ t(x_i^1,y_i^1). 
+V_{\mathcal{S}} \approx \sum_{i=0}^{n-1} \sum_{j=0}^{m-1} f(x_i^2,y_j^2) \Delta x_i^1 \Delta y_j^1.
 \end{equation}
+Let us verify that this is indeed the case:
+\begin{itemize}
+\item $\Delta x_i^1$ and $\Delta y_i^i$ represent the width and the length of subrectangle $R_{ij}$.
+\item The product $\Delta A = \Delta x_i^1\times \Delta y_i^i$ represent the area of subrectangle $R_{ij}$.
+\item $f(x_i^2,y_i^2)$ represents the height of a non-linear rectangular column or prism $\mathcal{K}_{ij}$ whose base is $R_{ij}$. Furthermore, the lateral edges of this column are all translations 
+of $\mathbf{c}(t)$ along the $xy$-plane. 
+\item The product $f(x_i^2,y_i^2)\times \Delta A$ represents the volume of $\mathcal{K}_{ij}$ (due to Cavalieri's principle).
+\item The double Cavalieri sum $\sum_{i=0}^{n-1} \sum_{j=0}^{m-1} f(x_i^2,y_j^2) \Delta A$, therefore, approximates $V_{\mathcal{S}}$. 
+\item In the limit the double Cavalieri sum approaches $V_{\mathcal{S}}$ (if this limit exists). 
+\end{itemize}
 
@@
 \end{equation}
+
+%Let $S_f = \{(x,y,z)\in\mathbb{R}^3|(x,y)\in S ~ \textrm{and} ~ z=f(x,y)\}$.
+Note that in $\mathbb{R}^3$, $R$ has the following vertices $\mathbf{v}_{R} = \{(x,y,z)\in\mathbb{R}^3|x\in\{a,b\},y\in\{c,d\}~\textrm{and}~z=0\}$,
+%while $S_f$ has the following vertices $\mathbf{v}_{S_f} = \{(x,y,z)\in\mathbb{R}^3|x\in\{a,b\},y\in\{c,d\}~\textrm{and}~z=f(h(x,y),s(x,y))\}$.
 

### 2019-08-13 Cav2D/article-template.tex
added more details to paper

--- 2019-08-12 Cav2D/article-template.tex
@@
 \section{Double Cavalieri Integral}
-Without any the loss of generality, let $R = [a,b]\times [c,d] = \{(x,y)\in \mathbb{R}^2|a \leq x \leq b, c \leq y \leq d\}$.
+Without the loss of generality, consider the surface $f(x,y)$ the curve $\mathbf{c}(t)$ and the region $R = [a,b]\times [c,d] = \{(x,y)\in \mathbb{R}^2|a \leq x \leq b, c \leq y \leq d\}$.
+
+\begin{definition}[Translational curve in $\mathbb{R}^3$]
 If a curve $\mathbf{c}(t) = \left <c_x(t),c_y(t), c_z(t) \right >$ in $\mathbb{R}^3$ intersects the $xy$ plane at the origin and $\mathbf{c}(t) + \left < e,f,0 \right >$ intersects 
@@
 with respect to $f(x,y)$ on $R$. 
+\end{definition}
+
+Moreover, assume that $\mathbf{c}(t)$ is a translational curve with respect to $f(x,y)$ on $R$.
+
 Let us now subdivide $R$ into $n\times m$ subrectangles $R_{ij} = [x_{i},x_{i+1}] \times [y_{j},y_{j+1}]$ of equal width $\Delta x^1 = \Delta x_i^1 = x_{i+1}-x_i\ll (b-a)$ and length $\Delta y^1= \Delta y_j^1 = y_{j+1}-y_j\ll(d-c)$.
+
 Furthermore, let the transformation $T$ map the $xy$--coordinate $(x_i^1,y_i^1)\in R$ (the lower left vertice of $R_{ij}$) at which $\mathbf{c}(t) + \left <x_i^1,y_i^1,0 \right >$ intersects the 
 $xy$-plane to the $xy$--coordinate at which $\mathbf{c}(t) + \left <x_i^1,y_j^1,0 \right >$ intersects $f(x,y)$. Note, the domain of $T$ is $R$. Moreover, let us denote the range 
-of $T$ with $\mathcal{S}$. The transformation $T:R\rightarrow S$ maps every point $(x_i^1,y_i^1)\in R$ to a point $(x_i^2,y_i^2)\in S$ and is formally defined as follows:
+of $T$ with $S$. The transformation $T:R\rightarrow S$ maps every point $(x_i^1,y_i^1)\in R$ to a point $(x_i^2,y_i^2)\in S$ and is formally defined as follows:
 \begin{equation}
-x_i^2 = h(x_i^1,y_i^1) = x_i^1 + c_x\circ t(x_i^1,y_i^1) 
+x_i^2 = h(x_i^1,y_i^1)~\textrm{and}~y_i^2 = s(x_i^1,y_i^1).
 \end{equation}
-and 
+
+Without any loss of generality, assume that $f(x,y)\geq0$. Also, let $S_f = \{(x,y,z)\in\mathbb{R}^3|(x,y)\in S ~ \textrm{and} ~ z=f(x,y)\}$. 
+Let $\mathcal{S}$ denote the solid which is obtained by connecting the vertices of $R$ and $S_f$ via translations of $\mathbf{c}(t)$ along 
+the $xy$ plane.
+
+%We can construct 
+%a solid We can use $\mathbf{c}(t)$, 
+%$R$ and $f(x,y)$ to construct a solid $\mathcal{S}$. The bottom and the top base of $\mathcal{S}$ is $R$ and $S_f$. The solid $\mathcal{S}$ also has the following four 
+%lateral edges: 
+%\begin{itemize}
+%\item The segement of $\mathbf{c}(t) + \left <a, c,0\right>$ which starts at $(a,c,0)$ and ends at\\$(h(a,c),s(a,c),f(h(a,c),s(a,c))$.
+%\item The segement of $\mathbf{c}(t) + \left <a, d,0\right>$ which starts at $(a,d,0)$ and ends at\\$(h(a,d),s(a,d),f(h(a,d),s(a,d))$.
+%\item The segement of $\mathbf{c}(t) + \left <b, c,0\right>$ which starts at $(b,c,0)$ and ends at\\$(h(b,c),s(b,c),f(h(b,c),s(b,c))$.
+%\item The segement of $\mathbf{c}(t) + \left <b, d,0\right>$ which starts at $(b,d,0)$ and ends at\\$(h(b,d),s(b,d),f(h(b,d),s(b,d))$.
+%\end{itemize}
+
+Let $V_{\mathcal{S}}$ denote the volume of $\mathcal{S}$. We can approximate $V_{\mathcal{S}}$ with:
 \begin{equation}
-y_i^2 = s(x_i^1,y_i^1) = y_i^1 + c_y\circ t(x_i^1,y_i^1). 
+V_{\mathcal{S}} \approx \sum_{i=0}^{n-1} \sum_{j=0}^{m-1} f(x_i^2,y_j^2) \Delta x_i^1 \Delta y_j^1.
 \end{equation}
+Let us verify that this is indeed the case:
+\begin{itemize}
+\item $\Delta x_i^1$ and $\Delta y_i^i$ represent the width and the length of subrectangle $R_{ij}$.
+\item The product $\Delta A = \Delta x_i^1\times \Delta y_i^i$ represent the area of subrectangle $R_{ij}$.
+\item $f(x_i^2,y_i^2)$ represents the height of a non-linear rectangular column or prism $\mathcal{K}_{ij}$ whose base is $R_{ij}$. Furthermore, the lateral edges of this column are all translations 
+of $\mathbf{c}(t)$ along the $xy$-plane. The cross-section between any parallel plane to the $xy$-axis that intersects $\mathcal{K}_{ij}$ is a rectangle with the same dimensions as $R_{ij}$. 
+\item The product $f(x_i^2,y_i^2)\times \Delta A$ represents the volume of $\mathcal{K}_{ij}$ (due to Cavalieri's principle).
+\item The double Cavalieri sum $\sum_{i=0}^{n-1} \sum_{j=0}^{m-1} f(x_i^2,y_j^2) \Delta A$, therefore, approximates $V_{\mathcal{S}}$. 
+\item In the limit the double Cavalieri sum approaches $V_{\mathcal{S}}$ (if this limit exists). 
+\end{itemize}
 

### 2019-08-14 Cav2D/article-template.tex
better discription of S

@@
 \section{Double Cavalieri Integral}
-Without the loss of generality, consider the surface $f(x,y)$ the curve $\mathbf{c}(t)$ and the region $R = [a,b]\times [c,d] = \{(x,y)\in \mathbb{R}^2|a \leq x \leq b, c \leq y \leq d\}$.
+Without the loss of generality, consider the surface $f(x,y)$, the curve $\mathbf{c}(t)$\\$=\left <c_x(t),c_y(t), c_z(t) \right >$ and the region $R = [a,b]\times [c,d] = \{(x,y)\in \mathbb{R}^2|a \leq x \leq b, c \leq y \leq d\}$.
 
 \begin{definition}[Translational curve in $\mathbb{R}^3$]
-If a curve $\mathbf{c}(t) = \left <c_x(t),c_y(t), c_z(t) \right >$ in $\mathbb{R}^3$ intersects the $xy$ plane at the origin and $\mathbf{c}(t) + \left < e,f,0 \right >$ intersects 
+If a curve $\mathbf{c}(t)$ in $\mathbb{R}^3$ intersects the $xy$ plane at the origin and $\mathbf{c}(t) + \left < e,f,0 \right >$ intersects 
 the surface $f(x,y)$ at a single point for all $(e,f)\in R$ then $\mathbf{c}(t)$ is a translational curve 
@@
 
+\noindent
 Moreover, assume that $\mathbf{c}(t)$ is a translational curve with respect to $f(x,y)$ on $R$.
-
-Let us now subdivide $R$ into $n\times m$ subrectangles $R_{ij} = [x_{i},x_{i+1}] \times [y_{j},y_{j+1}]$ of equal width $\Delta x^1 = \Delta x_i^1 = x_{i+1}-x_i\ll (b-a)$ and length $\Delta y^1= \Delta y_j^1 = y_{j+1}-y_j\ll(d-c)$.
-
+Let us first subdivide $R$ into $n\times m$ subrectangles $R_{ij} = [x_{i},x_{i+1}] \times [y_{j},y_{j+1}]$ of equal width $\Delta x^1 = \Delta x_i^1 = x_{i+1}-x_i\ll (b-a)$ and length $\Delta y^1= \Delta y_j^1 = y_{j+1}-y_j\ll(d-c)$.
 Furthermore, let the transformation $T$ map the $xy$--coordinate $(x_i^1,y_i^1)\in R$ (the lower left vertice of $R_{ij}$) at which $\mathbf{c}(t) + \left <x_i^1,y_i^1,0 \right >$ intersects the 
 $xy$-plane to the $xy$--coordinate at which $\mathbf{c}(t) + \left <x_i^1,y_j^1,0 \right >$ intersects $f(x,y)$. Note, the domain of $T$ is $R$. Moreover, let us denote the range 
-of $T$ with $S$. The transformation $T:R\rightarrow S$ maps every point $(x_i^1,y_i^1)\in R$ to a point $(x_i^2,y_i^2)\in S$ and is formally defined as follows:
+of $T$ with $S$.
+As the subdivision of $R$ can be made arbitrarily small, $T:R\rightarrow S$ actually maps every point $(x_i^1,y_i^1)\in R$ to a point $(x_i^2,y_i^2)\in S$.
+In general, the transformation $T$ is defined as follows:
 \begin{equation}
@@
 
-Without any loss of generality, assume that $f(x,y)\geq0$. Also, let $S_f = \{(x,y,z)\in\mathbb{R}^3|(x,y)\in S ~ \textrm{and} ~ z=f(x,y)\}$. 
-Let $\mathcal{S}$ denote the solid which is obtained by connecting the vertices of $R$ and $S_f$ via translations of $\mathbf{c}(t)$ along 
-the $xy$ plane.
+%We will now show 
+%that we can approximate $V_{\mathcal{S}}$ by summing together the volume of $n$ non-linear prisms that cicumscribe $\mathcal{S}$ and that as $n\rightarrow \infty$ 
+%the aformentioned sum approaches $V_{\mathcal{S}}$. 
+%Without any loss of generality, assume that $f(x,y)\geq0$. Also, let $S_f = \{(x,y,z)\in\mathbb{R}^3|(x,y)\in S ~ \textrm{and} ~ z=f(x,y)\}$. 
+%Let $\mathcal{S}$ denote the solid which is obtained by connecting the vertices of $R$ and $S_f$ via translations of $\mathbf{c}(t)$ along 
+%the $xy$ plane.
 
@@
 
-Let $V_{\mathcal{S}}$ denote the volume of $\mathcal{S}$. We can approximate $V_{\mathcal{S}}$ with:
+\noindent
+Also, let $S_f = \{(x,y,z)\in\mathbb{R}^3|(x,y)\in S ~ \textrm{and} ~ z=f(x,y)\}$.
+Let us further assume that $f(x,y) > 0$ for all $(x,y)\in S$.
+Let $\mathcal{S}$ denote the solid which is obtained by connecting the vertices of $R$ and
+$S_f$ via translations of $\mathbf{c}(t)$ along the $xy$ plane and then closing the resulting open faces that form due to the aformentioned connections.
+Let $V_{\mathcal{S}}$ denote the volume of $\mathcal{S}$.
+We can approximate $V_{\mathcal{S}}$ with:
 \begin{equation}
@@
 \item $f(x_i^2,y_i^2)$ represents the height of a non-linear rectangular column or prism $\mathcal{K}_{ij}$ whose base is $R_{ij}$. Furthermore, the lateral edges of this column are all translations 
-of $\mathbf{c}(t)$ along the $xy$-plane. The cross-section between any parallel plane to the $xy$-axis that intersects $\mathcal{K}_{ij}$ is a rectangle with the same dimensions as $R_{ij}$. 
+of $\mathbf{c}(t)$ along the $xy$-plane. The cross-section between any parallel plane to the $xy$-plane and $\mathcal{K}_{ij}$ is a rectangle with the same dimensions as $R_{ij}$. 
 \item The product $f(x_i^2,y_i^2)\times \Delta A$ represents the volume of $\mathcal{K}_{ij}$ (due to Cavalieri's principle).
@@
 \end{itemize}
+
+\noindent
+In this paper, we will refer to aforementioned limit as the double Cavalieri integral and we will denote this integral as follows:
+
+\begin{equation}
+\label{eq:cav_2d}
+\iint \limits_{\mathcal{C}} f(x,y)~dA = \lim_{n,m \rightarrow \infty}  \sum_{i=0}^{n-1} \sum_{j=0}^{m-1} f(x_i^2,y_j^2) \Delta x_i^1 \Delta y_j^1,
+\end{equation}
+with $\mathcal{C} = \{\mathbf{c}(t),R\}$. As is the case for the single Cavalieri integral, Equation~\eqref{eq:cav_2d} is difficult to evaluate in its current form. Luckily, the double 
+Cavalieri integral can be converted into an equivalent double Riemann integral using the transformation $T$:
+
+\begin{eqnarray}
+\iint\limits_{\!\mathcal{C}} f(x,y) dA &=& \lim_{n,m\rightarrow \infty} \sum_{j=1}^n\sum_{i=1}^n f(x_{ij}^2,y_{ij}^2) \Delta x_{ij}^1\Delta y_{ij}^1\\
+&=&  \lim_{n,m\rightarrow \infty} \sum_{j=1}^n\sum_{i=1}^n f(h(x_{ij}^1,y_{ij}^1),s(x_{ij}^1,y_{ij}^1)) \Delta x_{ij}^1\Delta y_{ij}^1\\
+&=& \int_a^b\int_c^d f(h(x,y),s(x,y))~dx~dy.
+\end{eqnarray}
+
+\noindent
+The only thing that now remains is to find expressions for $h$ and $s$. Note that, for every coordinate pair $(x_i^1,y_i^1)$ and $(x_i^2,y_i^2)$ there exists a unique $t\in \mathbb{R}$ such that 
+\begin{equation}
+\label{eq:vector_2}
+\left< x_i^2, y_i^2, f(x_i^2,y_i^2) \right > = \left < x_i^1, y_i^1, 0 \right > + \left <c_x(t),c_y(t),c_z(t)\right >  
+\end{equation}
+The above equation can be re-expressed as:
+\begin{equation}
+c_z(t) = f(x_i^1 + c_x(t),y_i^1 + c_y(t)). 
+\end{equation}
+We can now solve for $t$ in terms of $x_i^1$ and $y_i^1$. If we substitute this solution into Equation~\ref{eq:vector_2} we obtain:
+\begin{equation}
+x_i^2 = h(x_i^1,y_i^1) = x_i^1 + c_x\circ t(x_i^1,y_i^1) 
+\end{equation}
+and 
+\begin{equation}
+y_i^2 = s(x_i^1,y_i^1) = y_i^1 + c_y\circ t(x_i^1,y_i^1) 
+\end{equation}
 
@@
 %\end{equation}
-We can approximate $\mathcal{S}_V$ via:
-\begin{equation}
-V_{\mathcal{S}} \approx \sum_{i=0}^{n-1} \sum_{j=0}^{m-1} f(x_i^2,y_j^2) \Delta x_i^1 \Delta y_j^1.
-\end{equation}
-Let us verify that this is indeed the case:
-\begin{itemize}
-\item $\Delta x_i^1$ and $\Delta y_i^i$ represent the width and the length of subrectangle $R_{ij}$.
-\item The product $\Delta A = \Delta x_i^1\times \Delta y_i^i$ represent the area of subrectangle $R_{ij}$.
-\item $f(x_i^2,y_i^2)$ represents the height of a non-linear rectangular column or prism $\mathcal{K}_{ij}$ whose base is $R_{ij}$. Furthermore, the lateral edges of this column are all translations 
-of $\mathbf{c}(t)$ along the $xy$-plane. 
-\item The product $f(x_i^2,y_i^2)\times \Delta A$ represents the volume of $\mathcal{K}_{ij}$ (due to Cavalieri's principle).
-\item The double Cavalieri sum $\sum_{i=0}^{n-1} \sum_{j=0}^{m-1} f(x_i^2,y_j^2) \Delta A$, therefore, approximates $V_{\mathcal{S}}$. 
-\item In the limit the double Cavalieri sum approaches $V_{\mathcal{S}}$ (if this limit exists). 
-\end{itemize}
-
-In this paper, we will refer to aformentioned limit as the two dimensional Cavalieri integral and we will denote this integral as follows:
-
-\begin{equation}
-\label{eq:cav_2d}
-\iint \limits_{\mathcal{C}} f(x,y)~dA = \lim_{n,m \rightarrow \infty}  \sum_{i=0}^{n-1} \sum_{j=0}^{m-1} f(x_i^2,y_j^2) \Delta x_i^1 \Delta y_j^1,
-\end{equation}
-with $\mathcal{C} = \{\mathbf{c}(t),R\}$. As is the case for the single Cavalieri integral, Equation~\eqref{eq:cav_2d} is difficult to evaluate in its current form. Luckily, the double 
-Cavalieri integral can be converted into an equivalent Riemann integral using the transformation $T$. In general the transformation $T$ is defined via the following 
-equations:
-\begin{equation}
-x_i^2 = h(x_i^1,y_i^2)~\textrm{and}~y_i^2 = s(x_i^1,y_i^1) 
-\end{equation}
-We can now rewrite Equation~\eqref{eq:cav_2d} as follows:
-
-\begin{eqnarray}
-\iint\limits_{\!\mathcal{C}} f(x,y) dA &=& \lim_{n,m\rightarrow \infty} \sum_{j=1}^n\sum_{i=1}^n f(x_{ij}^2,y_{ij}^2) \Delta x_{ij}^1\Delta y_{ij}^1\\
-&=&  \lim_{n,m\rightarrow \infty} \sum_{j=1}^n\sum_{i=1}^n f(g(x_{ij}^1,y_{ij}^1),r(x_{ij}^1,y_{ij}^1)) \Delta x_{ij}^1\Delta y_{ij}^1\\
-&=& \int_a^b\int_c^d f(g(x,y),r(x,y))~dx~dy.
-\end{eqnarray}
-
-Note that, for every coordinate pair there exists a unique $t\in \mathbb{R}$ such that
-
-\begin{equation}
-\label{eq:vector_2}
-\left< x_i^2, y_i^2, f(x_i^2,y_i^2) \right > = \left < x_i^1, y_i^1, 0 \right > + \left <c_x(t),c_y(t),c_z(t)\right >  
-\end{equation}
-
-The above equation can be re-expressed as
-
-\begin{equation}
-c_z(t) = f(x_i^1 + c_x(t),y_i^1 + c_y(t)). 
-\end{equation}
-
-We can now solve for $t$ in terms of $x_i^1$ and $y_i^1$. If we substitute this solution into Equation~\ref{eq:vector_2} we obtain
-
-\begin{equation}
-x_i^2 = h(x_i^1,y_i^1) = x_i^1 + c_x\circ t(x_i^1,y_i^1) 
-\end{equation}
-and 
-\begin{equation}
-y_i^2 = s(x_i^1,y_i^1) = y_i^1 + c_y\circ t(x_i^1,y_i^1) 
-\end{equation}
 

### 2019-08-14 Cav2D/article-template.tex
started one dimensional section

@@
 \section{Cavalieri Integral}
-In this section we define the Cavalieri integral \cite{ackermann12}.
+The single Cavalieri integral was originally defined in \cite{ackermann12} without having to resort to vector calculus.
+In this section we will define the Cavalieri integral using vector calculus.
+As the reader will undoubtedly realize, if we define the single Cavalieri integral using vector calculus then it becomes trivial to
+extend its definition into $\mathbb{R}^3$.\\
 
-Let the region $R$ be bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$ and $b(y)=4-y$. This region is shown in Fig.~\ref{fig:caval2}.\\
+%In this section we define the Cavalieri integral \cite{ackermann12}.
+
+\noindent
+Consider the curve $f(x)$, the curve $\mathbf{c}(t)=\left <c_x(t),c_y(t) \right >$ and the interval $[a,b]$.
+
+\begin{definition}[Translational curve in $\mathbb{R}^2$]
+If a curve $\mathbf{c}(t)$ in $\mathbb{R}^2$ intersects the $x$ axis at the origin and $\mathbf{c}(t) + \left < e,0 \right >$ intersects 
+the curve $f(x)$ at a single point for all $e\in [a,b]$ then $\mathbf{c}(t)$ is a translational curve 
+with respect to $f(x)$ on $[a,b]$. 
+\end{definition}
+
+\noindent
+Moreover, assume that $\mathbf{c}(t)$ is a translational curve with respect to $f(x)$ on $[a,b]$. Let us first partition $[a,b]$ into $n$ subintervals $[x_{i},x_{i+1}]$ of equal 
+width $\Delta x^1 = \Delta x_i^1 = x_{i+1}-x_i\ll (b-a)$.
+Furthermore, let the transformation function $h$ map the $x$--coordinate $x_i^1\in [a,b]$ at which $\mathbf{c}(t) + \left <x_i^1,0 \right >$ intersects the
+$x$-axis to the $x$--coordinate at which $\mathbf{c}(t) + \left <x_i^1,0 \right >$ intersects $f(x,y)$. Note, the domain of $h$ is $[a,b]$. Let $a'$ denote the $x$-coordinate 
+at which $\mathbf{c}(t) + \left <a,0 \right >$ intersects $f(x,y)$ and let $b'$ denote the $x$-coordinate 
+at which $\mathbf{c}(t) + \left <b,0 \right >$ intersects $f(x,y)$.  Note, the range 
+of $h$ is $[a',b']$. As the partition of $[a,b]$ can be made arbitrarily fine, $h:[a,b]\rightarrow [a',b']$ actually maps every point $x_i^1\in [a,b]$ to a point $x_i^2\in [a',b']$. \\
+
+\noindent
+Let $R$ denote the region which is bounded by $f(x,y)$, $\mathbf{c}(t)+\left <a,0\right >$, $\mathbf{c}(t)+\left <b,0\right >$ and the $x$-axis. Let the $A_R$ denote 
+the area of $R$. We can approximate $A_R$ with:
+\begin{equation}
+ \label{eq:caval1}
+ \int_{a(y)}^{b(y)}f(x)\, dx = \lim_{n\to \infty}\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1,
+ \end{equation}
+Let us verify that this is indeed the case:
+ \begin{itemize}
+  \item $\Delta x_i^1 = x_{i+1}^1 - x_i^1$ represents the width of a non-rectangular integration strip.
+  \item $f(x_i^2)$ represents the height of a non-rectangular integration strip.
+  \item $f(x_i^2)\Delta x_i^1$ represents the area of a non-rectangular integration strip (due to Cavalieri's principle).
+  \item The Cavalieri sum $\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1$, therefore, approximates the area of $R$.
+  \item In the limit the Cavalieri sum, therefore, approaches the area of $R$.
+ \end{itemize}
+
+%Let the region $R$ be bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$ and $b(y)=4-y$. This region is shown in Fig.~\ref{fig:caval2}.\\
 %\begin{figure}[htb]
@@
 
-\noindent
-We can compute the area of $R$ as follows:
-\begin{equation}
-\int_0^2x\, dx+\int_2^44-x\, dx- \int_0^{\frac{1}{2}}x\, dx-\int_{\frac{1}{2}}^11-x\, dx = 3.75. 
-\end{equation}
+% \noindent
+% We can compute the area of $R$ as follows:
+% \begin{equation}
+% \int_0^2x\, dx+\int_2^44-x\, dx- \int_0^{\frac{1}{2}}x\, dx-\int_{\frac{1}{2}}^11-x\, dx = 3.75. 
+% \end{equation}
+% 
+% \noindent
+% Alternatively, the area of $R$ can also be determined via the Cavalieri integral:
+% \begin{equation}
+% \label{eq:caval1}
+% \int_{a(y)}^{b(y)}f(x)\, dx = \lim_{n\to \infty}\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1,
+% \end{equation}
+% with $\Delta x_i^1 = x_{i+1}^1 - x_i^1$.
+Furthermore, the partition points $(x_i^1)_{i=0}^{n}$ and $(x_i^2)_{i=0}^{n}$ are depicted in Fig.~\ref{fig:caval2}.
+Let us review why this is in fact the case:
+% \begin{itemize}
+%  \item $\Delta x_i^1 = x_{i+1}^1 - x_i^1$ represents the width of a non-rectangular integration strip.
+%  \item $f(x_i^2)$ represents the height of a non-rectangular integration strip.
+%  \item $f(x_i^2)\Delta x_i^1$ represents the area of a non-rectangular integration strip (due to Cavalieri's principle).
+%  \item The Cavalieri sum $\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1$, therefore, approximates the area of $R$.
+%  \item In the limit the Cavalieri sum, therefore, approaches the area of $R$.
+% \end{itemize}
+% 
+% \noindent
+% The Cavalieri integral is, however, hard to evaluate directly. Fortunately, it is easy to convert a Cavalieri integral into an equivalent Riemann integral:
+% \begin{equation}
+% \int_{a(y)}^{b(y)}f(x)\, dx = \int_{a}^{b} f\circ h(x)~dx, 
+% \end{equation}
+% with $a(0) = a$ and $b(0)=b$.
+The function $h$ is known as the transformation function and it maps $x_i^1\in[a,b]$ to $x_i^2\in[a',b']$.
+It can be constructed via the function $g(x) = x - a\circ f(x) + a$ as
+% $h=g^{-1}$.
+% 
+% \noindent
+% The area of $R$ can, therefore, also be computed as follows:
+% \begin{equation}
+% \int_{a(y)}^{b(y)}f(x)\, dx = \int_a^b f \circ h (x)\, dx = \dfrac{1}{2}\int_1^4x\, dx = 3.75.  
+% \end{equation}
+% 
+% Let $\mathbf{c}(t) = \left <c_x(t),c_y(t) \right>$ be the vector equation of $a(y)-a$. The notation which we have been using to denote a Cavalieri integral up until now 
+% in the paper was first proposed by Ackermann. Going forward in this paper, however, we propose making use of the following alternative notation:
+% \begin{equation}
+% \label{eq:new_def_cavalieri}
+% \int \limits_{\mathcal{C}} f(x)~dx := \int_{a(y)}^{b(y)}f(x)~dx,
+% \end{equation}
+% with $\mathcal{C} = \{\mathbf{c}(t),[a,b]\}$. Note that $\left<a,0\right> + \mathbf{c}(t)$ and $\left<b,0\right> + \mathbf{c}(t)$ are the vector equations of $a(y)$ and 
+% $b(y)$. The reason for this change in notation will become clear to the reader at a later stage. In turns out, that we can use $\mathbf{c}(t)$ to construct $h(x)$ via:
+% \begin{equation}
+% \label{eq:h_func}
+% x_i^2 = h(x_i^1) = x_i^1 + c_x\circ t(x_i^1).
+% \end{equation}
+% 
+% \noindent
+% We will now show that this is indeed the case. Note that, for every coordinate $(x_i^1,x_i^2) \in [a,b] \times [a',b']$ there exists a unique $t\in\mathbb{R}$ such that
+% \begin{equation}
+% \label{eq:pat_rel}
+% \left <x_i^2,f(x_i^2) \right > = \left <x_i^1,0 \right> + \left<c_x(t),c_y(t) \right >.
+% \end{equation}
+% We can rewrite Equation~\eqref{eq:pat_rel} as
+% \begin{equation}
+% \label{eq:t_func}
+% c_y(t) = f(x_i^1 + c_x(t)).
+% \end{equation}
+% We can now solve for $t$ in Equation~\eqref{eq:t_func} in terms of $x_i^1$. If we substitute the solution $t(x_i)$ so obtained into Equation~\ref{eq:pat_rel} we obtain Equation~\ref{eq:h_func}.
+% 
+% In the case of $R$ we have that $\mathbf{c}(t) = \left<-\frac{1}{2} t,\frac{1}{2} t\right>$. If we solve for $t$ in terms of $x_i^1$ after having substituted $\mathbf{c}(t)$ into Eq we obtain 
+% $t(x_i^1) = x_i^1$. If we now substitute our solution $t(x_i^1)$ into Eq we obtain, as required, $h(x_i^1) = \frac{1}{2}x_i^2$. This result, therefore, validates Eq ??.
+
+\section{Double Cavalieri Integral}
+In this section we define the double Cavalieri integral and we show that it can be used to calculate the volume of solids that can be decomposed into an infinite 
+number of non-linear regtangular infinitesimals.\\
 
 \noindent
-Alternatively, the area of $R$ can also be determined via the Cavalieri integral:
-\begin{equation}
-\label{eq:caval1}
-\int_{a(y)}^{b(y)}f(x)\, dx = \lim_{n\to \infty}\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1,
-\end{equation}
-with $\Delta x_i^1 = x_{i+1}^1 - x_i^1$.
-Furthermore, the partition points $(x_i^1)_{i=0}^{n}$ and $(x_i^2)_{i=0}^{n}$ are depicted in Fig.~\ref{fig:caval2}.
-Let us review why this is in fact the case:
-\begin{itemize}
- \item $\Delta x_i^1 = x_{i+1}^1 - x_i^1$ represents the width of a non-rectangular integration strip.
- \item $f(x_i^2)$ represents the height of a non-rectangular integration strip.
- \item $f(x_i^2)\Delta x_i^1$ represents the area of a non-rectangular integration strip (due to Cavalieri's principle).
- \item The Cavalieri sum $\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1$, therefore, approximates the area of $R$.
- \item In the limit the Cavalieri sum, therefore, approaches the area of $R$.
-\end{itemize}
-
-\noindent
-The Cavalieri integral is, however, hard to evaluate directly. Fortunately, it is easy to convert a Cavalieri integral into an equivalent Riemann integral:
-\begin{equation}
-\int_{a(y)}^{b(y)}f(x)\, dx = \int_{a}^{b} f\circ h(x)~dx, 
-\end{equation}
-with $a(0) = a$ and $b(0)=b$.
-The function $h$ is known as the transformation function and it maps $x_i^1\in[a,b]$ to $x_i^2\in[a',b']$.
-It can be constructed via the function $g(x) = x - a\circ f(x) + a$ as
-$h=g^{-1}$.
-
-\noindent
-The area of $R$ can, therefore, also be computed as follows:
-\begin{equation}
-\int_{a(y)}^{b(y)}f(x)\, dx = \int_a^b f \circ h (x)\, dx = \dfrac{1}{2}\int_1^4x\, dx = 3.75.  
-\end{equation}
-
-Let $\mathbf{c}(t) = \left <c_x(t),c_y(t) \right>$ be the vector equation of $a(y)-a$. The notation which we have been using to denote a Cavalieri integral up until now 
-in the paper was first proposed by Ackermann. Going forward in this paper, however, we propose making use of the following alternative notation:
-\begin{equation}
-\label{eq:new_def_cavalieri}
-\int \limits_{\mathcal{C}} f(x)~dx := \int_{a(y)}^{b(y)}f(x)~dx,
-\end{equation}
-with $\mathcal{C} = \{\mathbf{c}(t),[a,b]\}$. Note that $\left<a,0\right> + \mathbf{c}(t)$ and $\left<b,0\right> + \mathbf{c}(t)$ are the vector equations of $a(y)$ and 
-$b(y)$. The reason for this change in notation will become clear to the reader at a later stage. In turns out, that we can use $\mathbf{c}(t)$ to construct $h(x)$ via:
-\begin{equation}
-\label{eq:h_func}
-x_i^2 = h(x_i^1) = x_i^1 + c_x\circ t(x_i^1).
-\end{equation}
-
-\noindent
-We will now show that this is indeed the case. Note that, for every coordinate $(x_i^1,x_i^2) \in [a,b] \times [a',b']$ there exists a unique $t\in\mathbb{R}$ such that
-\begin{equation}
-\label{eq:pat_rel}
-\left <x_i^2,f(x_i^2) \right > = \left <x_i^1,0 \right> + \left<c_x(t),c_y(t) \right >.
-\end{equation}
-We can rewrite Equation~\eqref{eq:pat_rel} as
-\begin{equation}
-\label{eq:t_func}
-c_y(t) = f(x_i^1 + c_x(t)).
-\end{equation}
-We can now solve for $t$ in Equation~\eqref{eq:t_func} in terms of $x_i^1$. If we substitute the solution $t(x_i)$ so obtained into Equation~\ref{eq:pat_rel} we obtain Equation~\ref{eq:h_func}.
-
-In the case of $R$ we have that $\mathbf{c}(t) = \left<-\frac{1}{2} t,\frac{1}{2} t\right>$. If we solve for $t$ in terms of $x_i^1$ after having substituted $\mathbf{c}(t)$ into Eq we obtain 
-$t(x_i^1) = x_i^1$. If we now substitute our solution $t(x_i^1)$ into Eq we obtain, as required, $h(x_i^1) = \frac{1}{2}x_i^2$. This result, therefore, validates Eq ??.
-
-\section{Double Cavalieri Integral}
 Without the loss of generality, consider the surface $f(x,y)$, the curve $\mathbf{c}(t)$\\$=\left <c_x(t),c_y(t), c_z(t) \right >$ and the region $R = [a,b]\times [c,d] = \{(x,y)\in \mathbb{R}^2|a \leq x \leq b, c \leq y \leq d\}$.
@@
 Moreover, assume that $\mathbf{c}(t)$ is a translational curve with respect to $f(x,y)$ on $R$.
-Let us first subdivide $R$ into $n\times m$ subrectangles $R_{ij} = [x_{i},x_{i+1}] \times [y_{j},y_{j+1}]$ of equal width $\Delta x^1 = \Delta x_i^1 = x_{i+1}-x_i\ll (b-a)$ and length $\Delta y^1= \Delta y_j^1 = y_{j+1}-y_j\ll(d-c)$.
+Let us first partition $R$ into $n\times m$ subrectangles $R_{ij} = [x_{i},x_{i+1}] \times [y_{j},y_{j+1}]$ of equal width $\Delta x^1 = \Delta x_i^1 = x_{i+1}-x_i\ll (b-a)$ and length $\Delta y^1= \Delta y_j^1 = y_{j+1}-y_j\ll(d-c)$.
 Furthermore, let the transformation $T$ map the $xy$--coordinate $(x_i^1,y_i^1)\in R$ (the lower left vertice of $R_{ij}$) at which $\mathbf{c}(t) + \left <x_i^1,y_i^1,0 \right >$ intersects the 
@@
 of $T$ with $S$.
-As the subdivision of $R$ can be made arbitrarily small, $T:R\rightarrow S$ actually maps every point $(x_i^1,y_i^1)\in R$ to a point $(x_i^2,y_i^2)\in S$.
+As the paartition of $R$ can be made arbitrarily fine, $T:R\rightarrow S$ actually maps every point $(x_i^1,y_i^1)\in R$ to a point $(x_i^2,y_i^2)\in S$.
 In general, the transformation $T$ is defined as follows:
@@
 Let $\mathcal{S}$ denote the solid which is obtained by connecting the vertices of $R$ and
-$S_f$ via translations of $\mathbf{c}(t)$ along the $xy$ plane and then closing the resulting open faces that form due to the aformentioned connections.
+$S_f$ via translations of $\mathbf{c}(t)$ along the $xy$ plane and then closing the resulting open faces that form due to the aformentioned connections by employing appropriate surfaces.
 Let $V_{\mathcal{S}}$ denote the volume of $\mathcal{S}$.
@@
 \noindent
-In this paper, we will refer to aforementioned limit as the double Cavalieri integral and we will denote this integral as follows:
+In this paper, we will refer to the aforementioned limit as the double Cavalieri integral and we will denote this integral as follows:
 
@@
 \noindent
-The only thing that now remains is to find expressions for $h$ and $s$. Note that, for every coordinate pair $(x_i^1,y_i^1)$ and $(x_i^2,y_i^2)$ there exists a unique $t\in \mathbb{R}$ such that 
+The only thing that now remains is to find expressions for $h$ and $s$.
+Note that, for every coordinate pair $(x_i^1,y_i^1)\in R$ and $(x_i^2,y_i^2)\in S$ there exists a unique $t\in \mathbb{R}$ such that
 \begin{equation}
@@
 \begin{equation}
-y_i^2 = s(x_i^1,y_i^1) = y_i^1 + c_y\circ t(x_i^1,y_i^1) 
+y_i^2 = s(x_i^1,y_i^1) = y_i^1 + c_y\circ t(x_i^1,y_i^1). 
 \end{equation}

### 2019-08-14 Cav2D/article-template.tex
finished single cavalieri section

@@
 The single Cavalieri integral was originally defined in \cite{ackermann12} without having to resort to vector calculus.
-In this section we will define the Cavalieri integral using vector calculus.
+In this section we will redefine the Cavalieri integral using vector calculus notation.
 As the reader will undoubtedly realize, if we define the single Cavalieri integral using vector calculus then it becomes trivial to
@@
  \label{eq:caval1}
- \int_{a(y)}^{b(y)}f(x)\, dx = \lim_{n\to \infty}\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1,
+ A_R \approx \sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1,
  \end{equation}
@@
  \end{itemize}
+
+\noindent
+The aforementioned limit is known as Cavalieri integral and in this paper we denote this integral as follows:
+
+\begin{equation}
+\label{eq:cav_1d}
+\int \limits_{\mathcal{C}} f(x)~dx = \lim_{n \rightarrow \infty}  \sum_{i=0}^{n-1} f(x_i^2) \Delta x_i^1,
+\end{equation}
+with $\mathcal{C} = \{\mathbf{c}(t),[a,b]\}$. Equation~\eqref{eq:cav_1d} is difficult to evaluate in its current form. Luckily, the Cavalieri integral 
+can be converted into an equivalent Riemann integral using the transformation $h$:
+ \begin{equation}
+ \int \limits_{\mathcal{C}} f(x)\, dx = \int_{a}^{b} f\circ h(x)~dx. 
+\end{equation}
+
+\noindent
+The only thing that now remains is to find an expression for $h$. Note that, for every coordinate $(x_i^1,x_i^2) \in [a,b] \times [a',b']$ there exists a unique $t\in\mathbb{R}$ such that
+\begin{equation}
+ \label{eq:pat_rel_1d}
+ \left <x_i^2,f(x_i^2) \right > = \left <x_i^1,0 \right> + \left<c_x(t),c_y(t) \right >.
+ \end{equation}
+ We can rewrite Equation~\eqref{eq:pat_rel_1d} as
+ \begin{equation}
+ \label{eq:t_func_1d}
+ c_y(t) = f(x_i^1 + c_x(t)).
+ \end{equation}
+ We can now solve for $t$ in Equation~\eqref{eq:t_func_1d} in terms of $x_i^1$. If we substitute the solution $t(x_i)$ so obtained into Equation~\ref{eq:pat_rel_1d} we obtain 
+\begin{equation}
+\label{eq:h_func_1d}
+ x_i^2 = h(x_i^1) = x_i^1 + c_x\circ t(x_i^1).
+\end{equation}
+
+\noindent
+Note, the Cavalieri integral is denoted in \cite{ackermann12} via:
+\begin{equation}
+\label{eq:cav_1d}
+\int_{a(y)}^{b(y)} f(x)~dx = \lim_{n \rightarrow \infty}  \sum_{i=0}^{n-1} f(x_i^2) \Delta x_i^1,
+\end{equation}
+where $a(y)$ denotes the functional representation of $\mathbf{c}(t) + \left <a,0 \right >$ and $b(y) = a(y)+(b-a)$.
 

### 2019-08-14 Cav2D/article-template.tex
making sure it is synced

@@
   \item The Cavalieri sum $\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1$, therefore, approximates the area of $R$.
-  \item In the limit the Cavalieri sum, therefore, approaches the area of $R$.
+  \item In the limit the Cavalieri sum (if this limit exists), therefore, approaches the area of $R$.
  \end{itemize}
@@
 \noindent
-The aforementioned limit is known as Cavalieri integral and in this paper we denote this integral as follows:
+The aforementioned limit is known as the Cavalieri integral and in this paper we denote this integral as follows:
 

### 2019-08-14 Cav2D/article-template.tex
starting miing in real world example

@@
 
-\title{Computing volume via non-linear rectangular prisms}
+\title{Computing volume via non-linear rectangular infinitesimals}
 %\author{Woodrow Wilson and Herbert Hoover} %%leave blank in initial submission to allow for double blind reviewing
@@
 Let $\mathcal{S}$ denote the solid which is obtained by connecting the vertices of $R$ and
-$S_f$ via translations of $\mathbf{c}(t)$ along the $xy$ plane and then closing the resulting open faces that form due to the aformentioned connections by employing appropriate surfaces.
-Let $V_{\mathcal{S}}$ denote the volume of $\mathcal{S}$.
-We can approximate $V_{\mathcal{S}}$ with:
+$S_f$ via translations of $\mathbf{c}(t)$ along the $xy$ plane and then closing the resulting open faces that form due to the aforementioned connections by employing appropriate surfaces. 
+As an example, the solid $\mathcal{S}$ depicted in Figure~\ref{fig:prismatoid_solid} is obtained if we set $f(x,y) = -x - y + 8$, $\mathbf{c}(t) = -\left<\frac{1}{2}t,t,t\right>$ and $R = \{(x,y)\in\mathbb{R}^2|0 \geq x \geq 4, 0 \geq x \geq 4\} \nonumber$.
+Moreover, the domain $R$ and the range $S$ of the transformation function $T$ which is associated with the solid $\mathcal{S}$ that is depicted in Figure~\ref{fig:prismatoid_solid} is depicted in Figure~\ref{fig:prismatoid_regions}.
+Let $V_{\mathcal{S}}$ denote the volume of $\mathcal{S}$. We can approximate $V_{\mathcal{S}}$ with:
 \begin{equation}
@@
 \end{itemize}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.75\textwidth]{prismatoid_solid.pdf}
+\caption{xx}
+\label{fig:prismatoid_solid}
+\end{figure}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.75\textwidth]{prismatoid_regions.pdf}
+\caption{xx}
+\label{fig:prismatoid_regions}
+\end{figure}
 
@@
 \label{fig:prismatoid_real}
-\end{figure}
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.75\textwidth]{prismatoid_solid.pdf}
-\caption{xx}
-\label{fig:prismatoid_solid}
-\end{figure}
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.75\textwidth]{prismatoid_regions.pdf}
-\caption{xx}
-\label{fig:prismatoid_regions}
 \end{figure}

### 2019-08-14 Cav2D/article-template.tex
made good progress on paper

@@
 \noindent
-Let $R$ denote the region which is bounded by $f(x,y)$, $\mathbf{c}(t)+\left <a,0\right >$, $\mathbf{c}(t)+\left <b,0\right >$ and the $x$-axis. Let the $A_R$ denote 
-the area of $R$. We can approximate $A_R$ with:
+Let $R$ denote the region which is bounded by $f(x,y)$, $\mathbf{c}(t)+\left <a,0\right >$, $\mathbf{c}(t)+\left <b,0\right >$ and the $x$-axis. 
+As an example, the region $R$ depicted in Figure~\ref{fig:caval2} is obtained if we set $f(x) = x$, $\mathbf{c}(t) = \left<-\frac{1}{2} t,\frac{1}{2} t\right>$, $a = 1$ and $b = 4$.
+Let $A_R$ denote the area of $R$. We can approximate $A_R$ with:
 \begin{equation}
@@
  \end{equation}
-Let us verify that this is indeed the case:
+Let us verify that this is indeed the case. If we closely inspect Equation~\ref{eq:caval1} and Figure~\ref{fig:caval2} we notice the following:
  \begin{itemize}
@@
  \end{itemize}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.75\textwidth]{fig13.eps}
+\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$.
+The figure also depicts the partition points $x_i^1$ and $x_i^2$ as used in the Cavalieri sum (see Eq.~\eqref{eq:cav_sum}).
+Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
+\label{fig:caval2}
+\end{figure}
 
@@
 %\end{figure}
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.75\textwidth]{fig13.eps}
-\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$.
-The figure also depicts the partition points $x_i^1$ and $x_i^2$ as used in the Cavalieri sum (see Eq.~\eqref{eq:cav_sum}).
-Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
-\label{fig:caval2}
-\end{figure}
 
@@
 As an example, the solid $\mathcal{S}$ depicted in Figure~\ref{fig:prismatoid_solid} is obtained if we set $f(x,y) = -x - y + 8$, $\mathbf{c}(t) = -\left<\frac{1}{2}t,t,t\right>$ and $R = \{(x,y)\in\mathbb{R}^2|0 \geq x \geq 4, 0 \geq x \geq 4\} \nonumber$.
-Moreover, the domain $R$ and the range $S$ of the transformation function $T$ which is associated with the solid $\mathcal{S}$ that is depicted in Figure~\ref{fig:prismatoid_solid} is depicted in Figure~\ref{fig:prismatoid_regions}.
+Moreover, the domain $R$ and the range $S$ of the transformation function $T$ which is associated with the solid $\mathcal{S}$ is depicted in Figure~\ref{fig:prismatoid_regions}.  
 Let $V_{\mathcal{S}}$ denote the volume of $\mathcal{S}$. We can approximate $V_{\mathcal{S}}$ with:
 \begin{equation}
+\label{eq:cav_sum_2d}
 V_{\mathcal{S}} \approx \sum_{i=0}^{n-1} \sum_{j=0}^{m-1} f(x_i^2,y_j^2) \Delta x_i^1 \Delta y_j^1.
 \end{equation}
-Let us verify that this is indeed the case:
+Let us verify that this is indeed the case. If we closely inspect Equation~\ref{eq:cav_sum_2d} and Figure~\ref{fig:prismatoid_solid} we notice the following:
 \begin{itemize}
 \item $\Delta x_i^1$ and $\Delta y_i^i$ represent the width and the length of subrectangle $R_{ij}$.
-\item The product $\Delta A = \Delta x_i^1\times \Delta y_i^i$ represent the area of subrectangle $R_{ij}$.
+\item The product $\Delta A = \Delta x_i^1\times \Delta y_i^i$ represents the area of subrectangle $R_{ij}$.
 \item $f(x_i^2,y_i^2)$ represents the height of a non-linear rectangular column or prism $\mathcal{K}_{ij}$ whose base is $R_{ij}$. Furthermore, the lateral edges of this column are all translations 

### 2019-08-14 Cav2D/article-template.tex
started working on the first example

@@
 
+\section{Prismatoid}
 Let $\mathcal{S}$ be the solid which is bounded by the planes $f(x,y)=-x-y+8$, $2x$, $2(x-4)$, $y$, $y-4$ and the $xy$-plane. Solid $\mathcal{S}$ is depicted 
-in Figure~\ref{fig:prismatoid}, Figure~\ref{fig:prismatoid_real} and Figure~\ref{fig:prismatoid_solid}. Solid $\mathcal{S}$ is a prismatoid, since all of its 
-vertices lie in two parallel planes. Furthermore, all of its lateral faces are trapezoids or triangles. The volume of $\mathcal{S}$, $V_{\mathcal{S}}$, can easily be computed using the 
-volume equation of a prismatoid. The details of this computation is described in the caption of Figure~\ref{fig:prismatoid}. According to the prismatoid volume 
-equation $V_{\mathcal{S}}=25.6$.
+in Figure~\ref{fig:prismatoid_solid}, Figure~\ref{fig:prismatoid} and Figure~\ref{fig:prismatoid_real}. Solid $\mathcal{S}$ is a prismatoid, since all of its 
+vertices lie in two parallel planes.
+Furthermore, all of its lateral faces are trapezoids or triangles.
+Note that, the line of intersection between $2x$ and $y$ is $\mathbf{c}(t) = -\left<\frac{1}{2}t,t,t\right>$.
+The line $\mathbf{c}(t)$ is depicted and labelled in Figure~\ref{fig:prismatoid_solid}.
+
+As we alluded to in the previous section we can calculate $V_{\mathcal{S}}$ using the double Cavalieri integral:
+\begin{equation}
+\iint\limits_{\!\mathcal{C}} f(x,y) dA =  \int_a^b\int_c^d f(h(x,y),s(x,y))~dx~dy,
+\end{equation}
+with $\mathcal{C}=\{\mathbf{c}(t),R\}$. We can, however, only evaluate the above integral if the transformation $T$ is known (see Figure ). We can find $T$ using Equation
 
@@
 %while $S_f$ has the following vertices $\mathbf{v}_{S_f} = \{(x,y,z)\in\mathbb{R}^3|x\in\{a,b\},y\in\{c,d\}~\textrm{and}~z=f(h(x,y),s(x,y))\}$.
+
+We can easily compute $V_{\mathcal{S}}$ using the 
+volume equation of a prismatoid. The details of this computation is described in the caption of Figure~\ref{fig:prismatoid}. According to the prismatoid volume 
+equation $V_{\mathcal{S}}=25.6$.\\
 

### 2019-08-14 Cav2D/article-template.tex
progress with prismatoid section

@@
 in Figure~\ref{fig:prismatoid_solid}, Figure~\ref{fig:prismatoid} and Figure~\ref{fig:prismatoid_real}. Solid $\mathcal{S}$ is a prismatoid, since all of its 
-vertices lie in two parallel planes.
-Furthermore, all of its lateral faces are trapezoids or triangles.
-Note that, the line of intersection between $2x$ and $y$ is $\mathbf{c}(t) = -\left<\frac{1}{2}t,t,t\right>$.
-The line $\mathbf{c}(t)$ is depicted and labelled in Figure~\ref{fig:prismatoid_solid}.
+vertices lie in two parallel planes. Furthermore, all of its lateral faces are trapezoids or triangles (if viewed from the side). Also note the following: the base of $\mathcal{S}$ is the region 
+ $R = [0,4]\times [0,4]$ and that the line of intersection between $2x$ and $y$ is $\mathbf{c}(t) = -\left<\frac{1}{2}t,t,t\right>$. The region $R$ and the line $\mathbf{c}(t)$ are
+also depicted and labelled in Figure~\ref{fig:prismatoid_solid}.\\
 
+\noindent
 As we alluded to in the previous section we can calculate $V_{\mathcal{S}}$ using the double Cavalieri integral:

### 2019-08-14 Cav2D/article-template.tex
more progress with prismatoid section

@@
 \end{equation}
-with $\mathcal{C}=\{\mathbf{c}(t),R\}$. We can, however, only evaluate the above integral if the transformation $T$ is known (see Figure ). We can find $T$ using Equation
+with $\mathcal{C}=\{\mathbf{c}(t),R\}$. We can, however, only evaluate the above integral if the transformation $T$ is known (see Figure ). We can find $T$ using Equation and 
+Equation. To evaluate Equation and Equation we first need to express $t$ in terms of $x_i^1$ and $y_i^1$. If we substitute $f(x,y)$ and $\mathbf{c}(t)$ into Equation we find 
+the following expression for $t$:
+\begin{equation}
+xxx. 
+\end{equation}
+If we substitute $xxx$ into Equation and Equation we obtain:
+\begin{equation}
+yyyy 
+\end{equation}
+and
+\begin{equation}
+zzzz 
+\end{equation}
+If we substitute yyyy and zzzz into kkkk we obtain:
+
+We can easily verify that the $V_{\mathcal{S}}$ we computed is correct, since S is a prismatoid. According to the prismatoid volume 
+equation $V_{\mathcal{S}}=25.6$. The details of this computation is described in the caption of Figure~\ref{fig:prismatoid}. This result verifies 
+the fact that
 

### 2019-08-14 Cav2D/article-template.tex
made some progress with prismatoid section

--- 2019-08-14 Cav2D/article-template.tex
@@
 Let us first partition $R$ into $n\times m$ subrectangles $R_{ij} = [x_{i},x_{i+1}] \times [y_{j},y_{j+1}]$ of equal width $\Delta x^1 = \Delta x_i^1 = x_{i+1}-x_i\ll (b-a)$ and length $\Delta y^1= \Delta y_j^1 = y_{j+1}-y_j\ll(d-c)$.
-Furthermore, let the transformation $T$ map the $xy$--coordinate $(x_i^1,y_i^1)\in R$ (the lower left vertice of $R_{ij}$) at which $\mathbf{c}(t) + \left <x_i^1,y_i^1,0 \right >$ intersects the 
+Furthermore, let the transformation $T$ map the $xy$--coordinate $(x_i^1,y_j^1)\in R$ (the lower left vertice of $R_{ij}$) at which $\mathbf{c}(t) + \left <x_i^1,y_j^1,0 \right >$ intersects the 
 $xy$-plane to the $xy$--coordinate at which $\mathbf{c}(t) + \left <x_i^1,y_j^1,0 \right >$ intersects $f(x,y)$. Note, the domain of $T$ is $R$. Moreover, let us denote the range 
 of $T$ with $S$.
-As the paartition of $R$ can be made arbitrarily fine, $T:R\rightarrow S$ actually maps every point $(x_i^1,y_i^1)\in R$ to a point $(x_i^2,y_i^2)\in S$.
+As the paartition of $R$ can be made arbitrarily fine, $T:R\rightarrow S$ actually maps every point $(x_i^1,y_j^1)\in R$ to a point $(x_i^2,y_j^2)\in S$.
 In general, the transformation $T$ is defined as follows:
 \begin{equation}
-x_i^2 = h(x_i^1,y_i^1)~\textrm{and}~y_i^2 = s(x_i^1,y_i^1).
+x_i^2 = h(x_i^1,y_j^1)~\textrm{and}~y_j^2 = s(x_i^1,y_j^1).
 \end{equation}
@@
 \begin{itemize}
-\item $\Delta x_i^1$ and $\Delta y_i^i$ represent the width and the length of subrectangle $R_{ij}$.
-\item The product $\Delta A = \Delta x_i^1\times \Delta y_i^i$ represents the area of subrectangle $R_{ij}$.
-\item $f(x_i^2,y_i^2)$ represents the height of a non-linear rectangular column or prism $\mathcal{K}_{ij}$ whose base is $R_{ij}$. Furthermore, the lateral edges of this column are all translations 
+\item $\Delta x_i^1$ and $\Delta y_j^1$ represent the width and the length of subrectangle $R_{ij}$.
+\item The product $\Delta A = \Delta x_i^1\times \Delta y_j^1$ represents the area of subrectangle $R_{ij}$.
+\item $f(x_i^2,y_j^2)$ represents the height of a non-linear rectangular column or prism $\mathcal{K}_{ij}$ whose base is $R_{ij}$. Furthermore, the lateral edges of this column are all translations 
 of $\mathbf{c}(t)$ along the $xy$-plane. The cross-section between any parallel plane to the $xy$-plane and $\mathcal{K}_{ij}$ is a rectangle with the same dimensions as $R_{ij}$. 
-\item The product $f(x_i^2,y_i^2)\times \Delta A$ represents the volume of $\mathcal{K}_{ij}$ (due to Cavalieri's principle).
+\item The product $f(x_i^2,y_j^2)\times \Delta A$ represents the volume of $\mathcal{K}_{ij}$ (due to Cavalieri's principle).
 \item The double Cavalieri sum $\sum_{i=0}^{n-1} \sum_{j=0}^{m-1} f(x_i^2,y_j^2) \Delta A$, therefore, approximates $V_{\mathcal{S}}$. 
@@
 \begin{eqnarray}
-\iint\limits_{\!\mathcal{C}} f(x,y) dA &=& \lim_{n,m\rightarrow \infty} \sum_{j=1}^n\sum_{i=1}^n f(x_{ij}^2,y_{ij}^2) \Delta x_{ij}^1\Delta y_{ij}^1\\
-&=&  \lim_{n,m\rightarrow \infty} \sum_{j=1}^n\sum_{i=1}^n f(h(x_{ij}^1,y_{ij}^1),s(x_{ij}^1,y_{ij}^1)) \Delta x_{ij}^1\Delta y_{ij}^1\\
+\iint\limits_{\!\mathcal{C}} f(x,y) dA &=& \lim_{n,m\rightarrow \infty} \sum_{j=1}^n\sum_{i=1}^n f(x_i^2,y_j^2) \Delta x_i^1\Delta y_j^1\\
+&=&  \lim_{n,m\rightarrow \infty} \sum_{j=1}^n\sum_{i=1}^n f(h(x_i^1,y_j^1),s(x_i^1,y_j^1)) \Delta x_i^1\Delta y_j^1\\
 &=& \int_a^b\int_c^d f(h(x,y),s(x,y))~dx~dy.
@@
 The only thing that now remains is to find expressions for $h$ and $s$.
-Note that, for every coordinate pair $(x_i^1,y_i^1)\in R$ and $(x_i^2,y_i^2)\in S$ there exists a unique $t\in \mathbb{R}$ such that
+Note that, for every coordinate pair $(x_i^1,y_j^1)\in R$ and $(x_i^2,y_j^2)\in S$ there exists a unique $t\in \mathbb{R}$ such that
 \begin{equation}
 \label{eq:vector_2}
-\left< x_i^2, y_i^2, f(x_i^2,y_i^2) \right > = \left < x_i^1, y_i^1, 0 \right > + \left <c_x(t),c_y(t),c_z(t)\right >  
+\left< x_i^2, y_j^2, f(x_i^2,y_j^2) \right > = \left < x_i^1, y_j^1, 0 \right > + \left <c_x(t),c_y(t),c_z(t)\right >  
 \end{equation}
@@
 \begin{equation}
-c_z(t) = f(x_i^1 + c_x(t),y_i^1 + c_y(t)). 
+\label{eq:c_z}
+c_z(t) = f(x_i^1 + c_x(t),y_j^1 + c_y(t)). 
 \end{equation}
-We can now solve for $t$ in terms of $x_i^1$ and $y_i^1$. If we substitute this solution into Equation~\ref{eq:vector_2} we obtain:
+We can now solve for $t$ in terms of $x_i^1$ and $y_j^1$. If we substitute this solution into Equation~\ref{eq:vector_2} we obtain:
 \begin{equation}
-x_i^2 = h(x_i^1,y_i^1) = x_i^1 + c_x\circ t(x_i^1,y_i^1) 
+\label{eq:h_2d}
+x_i^2 = h(x_i^1,y_j^1) = x_i^1 + c_x\circ t(x_i^1,y_j^1) 
 \end{equation}
@@
 \begin{equation}
-y_i^2 = s(x_i^1,y_i^1) = y_i^1 + c_y\circ t(x_i^1,y_i^1). 
+\label{eq:s_2d}
+y_j^2 = s(x_i^1,y_j^1) = y_j^1 + c_y\circ t(x_i^1,y_j^1). 
 \end{equation}
@@
 in Figure~\ref{fig:prismatoid_solid}, Figure~\ref{fig:prismatoid} and Figure~\ref{fig:prismatoid_real}. Solid $\mathcal{S}$ is a prismatoid, since all of its 
-vertices lie in two parallel planes. Furthermore, all of its lateral faces are trapezoids or triangles (if viewed from the side). Also note the following: the base of $\mathcal{S}$ is the region 
- $R = [0,4]\times [0,4]$ and that the line of intersection between $2x$ and $y$ is $\mathbf{c}(t) = -\left<\frac{1}{2}t,t,t\right>$. The region $R$ and the line $\mathbf{c}(t)$ are
+vertices lie in two parallel planes. Furthermore, all of its lateral faces are trapezoids or triangles (if viewed from the top). Also note the following: the base of $\mathcal{S}$ is the region 
+ $R = [0,4]\times [0,4]$ (if viewed from the front) and that the line of intersection between $2x$ and $y$ is $\mathbf{c}(t) = -\left<\frac{1}{2}t,t,t\right>$.
+The region $R$ and the line $\mathbf{c}(t)$ are
 also depicted and labelled in Figure~\ref{fig:prismatoid_solid}.\\
@@
 \begin{equation}
-\iint\limits_{\!\mathcal{C}} f(x,y) dA =  \int_a^b\int_c^d f(h(x,y),s(x,y))~dx~dy,
+\label{eq:cav_ex1}
+V_{\mathcal{S}} = \iint\limits_{\!\mathcal{C}} f(x,y) dA =  \int_a^b\int_c^d f(h(x,y),s(x,y))~dx~dy,
 \end{equation}
-with $\mathcal{C}=\{\mathbf{c}(t),R\}$. We can, however, only evaluate the above integral if the transformation $T$ is known (see Figure ). We can find $T$ using Equation
+with $\mathcal{C}=\{\mathbf{c}(t),R\}$.
+We can, however, only evaluate the above integral if the transformation $T$ is known (see Figure~\ref{fig:prismatoid_regions}).
+We can find $T$ using Equation~\eqref{eq:h_2d} and
+Equation~\eqref{eq:s_2d}.
+To evaluate Equation~\eqref{eq:h_2d} and Equation~\eqref{eq:s_2d} we first need to express $t$ in terms of $x_i^1$ and $y_j^1$.
+If we substitute $f(x,y)$ and $\mathbf{c}(t)$ into Equation~\eqref{eq:c_z} and then solve for $t$ we obtain:
+\begin{equation}
+t(x_i^1,y_j^1) = \frac{x_i^1 + y_j^1 + 8}{5} 
+\end{equation}
+Substituting $t(x_i^1,y_j^1)$ into Equation~\eqref{eq:h_2d} and Equation~\eqref{eq:s_2d} results in:
+\begin{equation}
+x_{i}^2 = h(x_{i}^1,y_{j}^1) = \frac{4}{5} x_{i}^1 - \frac{1}{5} y_{j}^1 + \frac{8}{5}  
+\end{equation}
+and
+\begin{equation}
+y_{j}^2 = r(x_{i}^1,y_{j}^1) = \frac{3}{5} x_{i}^1 - \frac{2}{5} y_{j}^1 + \frac{16}{5}.  
+\end{equation}
+We can now evaluate Equation~\eqref{eq:cav_ex1}:
+\begin{eqnarray}
+V_{\mathcal{S}}=\iint\limits_{\!\mathcal{C}} f(x,y) dA &=& \int_0^4\int_0^4 f(h(x,y),r(x,y))~dydx\\
+&=& \int_0^4 \int_0^4 -\frac{7}{5}x + \frac{3}{5} y + \frac{16}{5}~dydx\\
+&=& 25.6
+\end{eqnarray}
+
+We can easily verify that the $V_{\mathcal{S}}$ we computed is correct, since S is a prismatoid. According to the prismatoid volume 
+equation $V_{\mathcal{S}}=25.6$. The details of this computation is described in the caption of Figure~\ref{fig:prismatoid}. This result verifies 
+the fact that
 
@@
 subrectangles $R_{ij} = [x_{i},x_{i+1}] \times [y_{j},y_{j+1}]$ of equal width $\Delta x^1 = \Delta x_i^1 = x_{i+1}-x_i<<(b-a)$ and length $\Delta y^1= \Delta y_j^1 = y_{j+1}-y_j<<(d-c)$. 
-Furthermore, let the transformation $T$ map the $xy$--coordinate $(x_i^1,y_i^1)\in R$ (the lower left vertice of $R_{ij}$) at which $\mathbf{c}(t) + \left <x_i^1,y_i^1,0 \right >$ intersects the 
+Furthermore, let the transformation $T$ map the $xy$--coordinate $(x_i^1,y_j^1)\in R$ (the lower left vertice of $R_{ij}$) at which $\mathbf{c}(t) + \left <x_i^1,y_j^1,0 \right >$ intersects the 
 $xy$-plane to the $xy$--coordinate $(x_i^2,y_j^2)\in S$ at which $\mathbf{c}(t) + \left <x_i^1,y_j^1,0 \right >$ intersects $f(x,y)$ (Figure~\ref{fig:prismatoid_solid} and Figure~\ref{fig:prismatoid_regions}).
@@
 %\begin{equation}
-%x_i^2 = h(x_i^1,y_i^1)
+%x_i^2 = h(x_i^1,y_j^1)
 %\end{equation}
@@
 %\begin{equation}
-%y_i^2 = s(x_i^1,y_i^1)
+%y_j^2 = s(x_i^1,y_j^1)
 %\end{equation}

### 2019-08-15 Cav2D/article-template.tex
started second example

@@
 
-\noindent
-As we alluded to in the previous section we can calculate $V_{\mathcal{S}}$ using the double Cavalieri integral:
-\begin{equation}
-\label{eq:cav_ex1}
-V_{\mathcal{S}} = \iint\limits_{\!\mathcal{C}} f(x,y) dA =  \int_a^b\int_c^d f(h(x,y),s(x,y))~dx~dy,
-\end{equation}
-with $\mathcal{C}=\{\mathbf{c}(t),R\}$.
-We can, however, only evaluate the above integral if the transformation $T$ is known (see Figure~\ref{fig:prismatoid_regions}).
-We can find $T$ using Equation~\eqref{eq:h_2d} and
-Equation~\eqref{eq:s_2d}.
-To evaluate Equation~\eqref{eq:h_2d} and Equation~\eqref{eq:s_2d} we first need to express $t$ in terms of $x_i^1$ and $y_j^1$.
-If we substitute $f(x,y)$ and $\mathbf{c}(t)$ into Equation~\eqref{eq:c_z} and then solve for $t$ we obtain:
-\begin{equation}
-t(x_i^1,y_j^1) = \frac{x_i^1 + y_j^1 + 8}{5} 
-\end{equation}
-Substituting $t(x_i^1,y_j^1)$ into Equation~\eqref{eq:h_2d} and Equation~\eqref{eq:s_2d} results in:
-\begin{equation}
-x_{i}^2 = h(x_{i}^1,y_{j}^1) = \frac{4}{5} x_{i}^1 - \frac{1}{5} y_{j}^1 + \frac{8}{5}  
-\end{equation}
-and
-\begin{equation}
-y_{j}^2 = r(x_{i}^1,y_{j}^1) = \frac{3}{5} x_{i}^1 - \frac{2}{5} y_{j}^1 + \frac{16}{5}.  
-\end{equation}
-We can now evaluate Equation~\eqref{eq:cav_ex1}:
-\begin{eqnarray}
-V_{\mathcal{S}}=\iint\limits_{\!\mathcal{C}} f(x,y) dA &=& \int_0^4\int_0^4 f(h(x,y),r(x,y))~dydx\\
-&=& \int_0^4 \int_0^4 -\frac{7}{5}x + \frac{3}{5} y + \frac{16}{5}~dydx\\
-&=& 25.6
-\end{eqnarray}
-
-We can easily verify that the $V_{\mathcal{S}}$ we computed is correct, since S is a prismatoid. According to the prismatoid volume 
-equation $V_{\mathcal{S}}=25.6$. The details of this computation is described in the caption of Figure~\ref{fig:prismatoid}. This result verifies 
-the fact that
-
-Let $\mathbf{c}(t) = -\left<\frac{1}{2}t,t,t\right>$ be the line of intersection between the planes $2x$ and $y$. Furthermore, note that the line 
-$\mathbf{c}(t)$ passes through the origin. The line $\mathbf{c}(t)$ is depicted and labelled in Figure~\ref{fig:prismatoid_solid}. Let 
-\begin{equation}
-R = \{(x,y)\in\mathbb{R}^2|0 \geq x \geq 4, 0 \geq x \geq 4\} \nonumber
-\end{equation}
-and
-\begin{equation}
-S = \{(x,y)\in\mathbb{R}^2|-\sfrac{1}{3}y+\sfrac{8}{3}\leq x\leq -\sfrac{1}{3}y+\sfrac{16}{3}, \sfrac{1}{2} x + 4\leq y \leq \sfrac{1}{2} x + 6 \}. \nonumber
-\end{equation}
-The region $S$ and $R$ are depicted in Figure~\ref{fig:prismatoid_solid} and Figure~\ref{fig:prismatoid_regions}. Let us now subdivide $R$ into $n\times m$
-subrectangles $R_{ij} = [x_{i},x_{i+1}] \times [y_{j},y_{j+1}]$ of equal width $\Delta x^1 = \Delta x_i^1 = x_{i+1}-x_i<<(b-a)$ and length $\Delta y^1= \Delta y_j^1 = y_{j+1}-y_j<<(d-c)$. 
-Furthermore, let the transformation $T$ map the $xy$--coordinate $(x_i^1,y_j^1)\in R$ (the lower left vertice of $R_{ij}$) at which $\mathbf{c}(t) + \left <x_i^1,y_j^1,0 \right >$ intersects the 
-$xy$-plane to the $xy$--coordinate $(x_i^2,y_j^2)\in S$ at which $\mathbf{c}(t) + \left <x_i^1,y_j^1,0 \right >$ intersects $f(x,y)$ (Figure~\ref{fig:prismatoid_solid} and Figure~\ref{fig:prismatoid_regions}).
-%The transformation $T$ is defined by the following equations:
-%\begin{equation}
-%x_i^2 = h(x_i^1,y_j^1)
-%\end{equation}
-%and
-%\begin{equation}
-%y_j^2 = s(x_i^1,y_j^1)
-%\end{equation}
-
-%Let $S_f = \{(x,y,z)\in\mathbb{R}^3|(x,y)\in S ~ \textrm{and} ~ z=f(x,y)\}$.
-Note that in $\mathbb{R}^3$, $R$ has the following vertices $\mathbf{v}_{R} = \{(x,y,z)\in\mathbb{R}^3|x\in\{a,b\},y\in\{c,d\}~\textrm{and}~z=0\}$,
-%while $S_f$ has the following vertices $\mathbf{v}_{S_f} = \{(x,y,z)\in\mathbb{R}^3|x\in\{a,b\},y\in\{c,d\}~\textrm{and}~z=f(h(x,y),s(x,y))\}$.
-
-We can easily compute $V_{\mathcal{S}}$ using the 
-volume equation of a prismatoid. The details of this computation is described in the caption of Figure~\ref{fig:prismatoid}. According to the prismatoid volume 
-equation $V_{\mathcal{S}}=25.6$.\\
-
-$R = \{(x,y)\in\mathbb{R}^2|0 \geq x \geq 4, 0 \geq x \geq 4\}$
-and $S = \{(x,y)\in\mathbb{R}^2|-\sfrac{1}{3}y+\sfrac{8}{3}\geq x\leq -\sfrac{1}{3}y+\sfrac{16}{3} \}$.
-
-The line $\mathbf{c}(t)$  is depicted and labelled in
-
 \begin{figure}[htb]
@@
 
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.75\textwidth]{prismatoid_xy.pdf}
-\caption{xx}
-\label{fig:prismatoid_xy}
-\end{figure}
+\noindent
+As we alluded to in the previous section we can calculate $V_{\mathcal{S}}$ using the double Cavalieri integral:
+\begin{equation}
+\label{eq:cav_ex1}
+V_{\mathcal{S}} = \iint\limits_{\!\mathcal{C}} f(x,y) dA =  \int_a^b\int_c^d f(h(x,y),s(x,y))~dx~dy,
+\end{equation}
+with $\mathcal{C}=\{\mathbf{c}(t),R\}$.
+We can, however, only evaluate the above integral if the transformation $T$ is known (see Figure~\ref{fig:prismatoid_regions}).
+We can find $T$ using Equation~\eqref{eq:h_2d} and
+Equation~\eqref{eq:s_2d}.
+To evaluate Equation~\eqref{eq:h_2d} and Equation~\eqref{eq:s_2d} we first need to express $t$ in terms of $x_i^1$ and $y_j^1$.
+If we substitute $f(x,y)$ and $\mathbf{c}(t)$ into Equation~\eqref{eq:c_z} and then solve for $t$ we obtain:
+\begin{equation}
+t(x_i^1,y_j^1) = \frac{x_i^1}{5} + \frac{y_j^1}{5} + \frac{8}{5}. 
+\end{equation}
+Substituting $t(x_i^1,y_j^1)$ into Equation~\eqref{eq:h_2d} and Equation~\eqref{eq:s_2d} results in:
+\begin{equation}
+x_{i}^2 = h(x_{i}^1,y_{j}^1) = \frac{4}{5} x_{i}^1 - \frac{1}{5} y_{j}^1 + \frac{8}{5}  
+\end{equation}
+and
+\begin{equation}
+y_{j}^2 = r(x_{i}^1,y_{j}^1) = \frac{3}{5} x_{i}^1 - \frac{2}{5} y_{j}^1 + \frac{16}{5}.  
+\end{equation}
+We can now evaluate Equation~\eqref{eq:cav_ex1}:
+\begin{eqnarray}
+\label{eq:final_int_prismatoid}
+V_{\mathcal{S}}=\iint\limits_{\!\mathcal{C}} f(x,y) dA &=& \int_0^4\int_0^4 f(h(x,y),r(x,y))~dydx\\
+&=& \int_0^4 \int_0^4 -\frac{7}{5}x + \frac{3}{5} y + \frac{16}{5}~dydx\\
+&=& 25.6
+\end{eqnarray}
+
+\noindent
+We can easily verify that the $V_{\mathcal{S}} = 25.6$ is in fact correct, since $\mathcal{S}$ is a prismatoid. According to the prismatoid volume 
+equation $V_{\mathcal{S}}=25.6$. The details of this computation is described in the caption of Figure~\ref{fig:prismatoid}. This then validates Equation~\ref{eq:final_int_prismatoid}.
+
+% Let $\mathbf{c}(t) = -\left<\frac{1}{2}t,t,t\right>$ be the line of intersection between the planes $2x$ and $y$. Furthermore, note that the line 
+% $\mathbf{c}(t)$ passes through the origin. The line $\mathbf{c}(t)$ is depicted and labelled in Figure~\ref{fig:prismatoid_solid}. Let 
+% \begin{equation}
+% R = \{(x,y)\in\mathbb{R}^2|0 \geq x \geq 4, 0 \geq x \geq 4\} \nonumber
+% \end{equation}
+% and
+% \begin{equation}
+% S = \{(x,y)\in\mathbb{R}^2|-\sfrac{1}{3}y+\sfrac{8}{3}\leq x\leq -\sfrac{1}{3}y+\sfrac{16}{3}, \sfrac{1}{2} x + 4\leq y \leq \sfrac{1}{2} x + 6 \}. \nonumber
+% \end{equation}
+% The region $S$ and $R$ are depicted in Figure~\ref{fig:prismatoid_solid} and Figure~\ref{fig:prismatoid_regions}. Let us now subdivide $R$ into $n\times m$
+% subrectangles $R_{ij} = [x_{i},x_{i+1}] \times [y_{j},y_{j+1}]$ of equal width $\Delta x^1 = \Delta x_i^1 = x_{i+1}-x_i<<(b-a)$ and length $\Delta y^1= \Delta y_j^1 = y_{j+1}-y_j<<(d-c)$. 
+% Furthermore, let the transformation $T$ map the $xy$--coordinate $(x_i^1,y_j^1)\in R$ (the lower left vertice of $R_{ij}$) at which $\mathbf{c}(t) + \left <x_i^1,y_j^1,0 \right >$ intersects the 
+% $xy$-plane to the $xy$--coordinate $(x_i^2,y_j^2)\in S$ at which $\mathbf{c}(t) + \left <x_i^1,y_j^1,0 \right >$ intersects $f(x,y)$ (Figure~\ref{fig:prismatoid_solid} and Figure~\ref{fig:prismatoid_regions}).
+% %The transformation $T$ is defined by the following equations:
+% %\begin{equation}
+% %x_i^2 = h(x_i^1,y_j^1)
+% %\end{equation}
+% %and
+% %\begin{equation}
+% %y_j^2 = s(x_i^1,y_j^1)
+% %\end{equation}
+% 
+% %Let $S_f = \{(x,y,z)\in\mathbb{R}^3|(x,y)\in S ~ \textrm{and} ~ z=f(x,y)\}$.
+Note that in $\mathbb{R}^3$, $R$ has the following vertices $\mathbf{v}_{R} = \{(x,y,z)\in\mathbb{R}^3|x\in\{a,b\},y\in\{c,d\}~\textrm{and}~z=0\}$,
+% %while $S_f$ has the following vertices $\mathbf{v}_{S_f} = \{(x,y,z)\in\mathbb{R}^3|x\in\{a,b\},y\in\{c,d\}~\textrm{and}~z=f(h(x,y),s(x,y))\}$. 
+% 
+% We can easily compute $V_{\mathcal{S}}$ using the 
+% volume equation of a prismatoid. The details of this computation is described in the caption of Figure~\ref{fig:prismatoid}. According to the prismatoid volume 
+% equation $V_{\mathcal{S}}=25.6$.\\
+
+% $R = \{(x,y)\in\mathbb{R}^2|0 \geq x \geq 4, 0 \geq x \geq 4\}$
+% and $S = \{(x,y)\in\mathbb{R}^2|-\sfrac{1}{3}y+\sfrac{8}{3}\geq x\leq -\sfrac{1}{3}y+\sfrac{16}{3} \}$.
+% 
+% 
+% 
+% The line $\mathbf{c}(t)$  is depicted and labelled in
+
+% \begin{figure}[htb]
+% \centering
+% \includegraphics[width=0.75\textwidth]{prismatoid_xy.pdf}
+% \caption{xx}
+% \label{fig:prismatoid_xy}
+% \end{figure}
+
+\section{Another example}
+Let $\mathcal{S}$ be the solid which is bounded by the planes $f(x,y)=\sqrt{-x^2-y^2+4}$, $\sqrt{x}$, $\sqrt{x-1}$, $\sqrt{y}$, $\sqrt{y-1}$ and the $xy$-plane. Solid $\mathcal{S}$ is depicted 
+in Figure~\ref{fig:sphere_solid}. Also note the following: the base of $\mathcal{S}$ is the region 
+$R = [0,1]\times [0,1]$ (if viewed from the front) and that the curve of intersection between $\sqrt{x}$ and $\sqrt{y}$ is $\mathbf{c}(t) = \left < t,t,\sqrt{t}\right >$.
+
+We can compute $V_{\mathcal{S}}$ as follows:
+\begin{equation}
+\label{eq:cav_ex2}
+V_{\mathcal{S}} = \iint\limits_{\!\mathcal{C}} f(x,y) dA =  \int_a^b\int_c^d f(h(x,y),s(x,y))~dx~dy,
+\end{equation}
+with $\mathcal{C}=\{\mathbf{c}(t),R\}$. We, however, first need to calculate $T$ if we wish to evaluate Equation~\ref{eq:cav_ex2} (see Figure~\ref{fig:sphere_regions}). We can determine $T$ via 
+Equation~\eqref{eq:h_2d} and Equation~\eqref{eq:s_2d}. Equation~\eqref{eq:h_2d} and Equation~\eqref{eq:s_2d} in turn requires $t(x_i^1,y_j^2)$, which can be calculated with
 
@@
 \caption{xx}
-\label{fig:sphere_solid}
+\label{fig:sphere_xy}
 \end{figure}

### 2019-08-15 Cav2D/article-template.tex
very good progress with second example

@@
 in Figure~\ref{fig:sphere_solid}. Also note the following: the base of $\mathcal{S}$ is the region 
-$R = [0,1]\times [0,1]$ (if viewed from the front) and that the curve of intersection between $\sqrt{x}$ and $\sqrt{y}$ is $\mathbf{c}(t) = \left < t,t,\sqrt{t}\right >$.
+$R = [0,1]\times [0,1]$ (if viewed from the front) and that the curve of intersection between $\sqrt{x}$ and $\sqrt{y}$ is $\mathbf{c}(t) = \left < t,t,\sqrt{t}\right >$. \\
 
-We can compute $V_{\mathcal{S}}$ as follows:
+\noindent
+Since $\mathcal{S}$ can be decomposed into an infinite number of non-linear rectangular infinitesimals we can compute its volume using:
 \begin{equation}
@@
 with $\mathcal{C}=\{\mathbf{c}(t),R\}$. We, however, first need to calculate $T$ if we wish to evaluate Equation~\ref{eq:cav_ex2} (see Figure~\ref{fig:sphere_regions}). We can determine $T$ via 
-Equation~\eqref{eq:h_2d} and Equation~\eqref{eq:s_2d}. Equation~\eqref{eq:h_2d} and Equation~\eqref{eq:s_2d} in turn requires $t(x_i^1,y_j^2)$, which can be calculated with
+Equation~\eqref{eq:h_2d} and Equation~\eqref{eq:s_2d}. Equation~\eqref{eq:h_2d} and Equation~\eqref{eq:s_2d} in turn requires $t(x_i^1,y_j^2)$, which can be obtained via Equation~\eqref{eq:c_z}.
+If we substite $f(x,y)$ and $\mathbf{c}(t)$ into Equation~\eqref{eq:c_z} and then solve for $t$ we obtain:
+\begin{equation}
+t = \frac{1}{4}[-2 x_{i}^1 - 2 y_{j}^1  -  1 + K(x_{i}^1,y_{j}^1)],
+\end{equation}
+where
+\begin{equation}
+K(x_{i}^1,y_{j}^1) = \sqrt{-4(x_{i}^1)^2+4x_{i}^1+8x_{i}^1y_{j}^1-4(y_{j}^1)^2+4y_{j}^1 + 33}. 
+\end{equation}
+With $t(x_i^1,y_j^1)$ we can find expressions for $h$ and $s$ by employing Equation~\eqref{eq:c_z}. The obtained expressions of $h$ and $s$ can then be used to evaluate Equation~\eqref{eq:cav_ex2}:  
+\begin{eqnarray}
+\iint\limits_{\!\mathcal{C}} f(x,y) dA &=& \int_0^1\int_0^1 f(h(x,y),r(x,y))~dydx\\
+&=& \int_0^1 \int_0^1 \sqrt{-(x+t(x,y))^2 - (y+t(x,y))^2 + 4} ~dydx\\
+&=& 0.864043
+\end{eqnarray}
+
+We can verify that $V_{\mathcal{S}}=0.864043$ is indeed correct via tradiosional calculus. We can first subdivide the $xy$-projection of $\mathcal{S}$ into regions
+
+\begin{table}
+\caption{Double integrals for sphere. $c_1 \approx 1.1861407$, $c_2 \approx 1.6861407$, $c_3 \approx 0.6861407$ and $c_4 \approx 1.3507811$. $r_1(x) = \frac{1}{2}[\sqrt{17-4x^2}-1]$,
+$r_2(x) = \sqrt{-x^2-x+4}$, $r_3(x) = \sqrt{-x^2-(x-1)+4}$ and $r_4(x) = \frac{1}{2}[\sqrt{21-4x^2}-1]$.} 
+\begin{center}
+
+\begin{tabular}{|l l l l l l l l|}
+  $k$ & Vertices & $a$ & $b$  & $g_1$ & $g_2$ & $f_k$ & $\iint\limits_{\!R_k} f_k~dA$\\
+  1 & ABD & 0 & 1& 0 & $x$ & $\sqrt{y}$ & 0.2667\\
+  2 & BLED& 1& $c_1$ & $x-1$ & $x$ & $\sqrt{y} - \sqrt{x-1}$& 0.0844\\
+  3 & LFE& $c_1$ & $c_2$ & $x-1$ & $r_1(x)$&$\sqrt{y} - \sqrt{x-1}$&0.0626\\
+  4 & ADC& 0 & 1 & $x$ & 1 & $\sqrt{x}$ &0.2667\\
+  5 & CIG& 0 & $c_3$ & 1 & $x+1$ & $\sqrt{x} - \sqrt{y-1}$ &0.0520\\
+  6 & IDJG& $c_3$ & 1 & 1 & $r_2(x)$ & $\sqrt{x} - \sqrt{y-1}$&0.0716\\
+  7 & DEJ& 1& $c_1$& $x$ & $r_2(x)$ & $\sqrt{x} - \sqrt{y-1}$&0.0234\\ 
+  8 & EKG& $c_3$& $c_1$& $r_2(x)$ & $r_4(x)$ & $\sqrt{-x^2-y^2+4}-\sqrt{y-1}$&0.0129\\ 
+  9 & EHK& $c_1$& $c_4$& $x$& $r_4(x)$ & $\sqrt{-x^2-y^2+4}-\sqrt{y-1}$&0.0055\\
+  10& EMH& $c_1$& $c_4$& $r_1(x)$& $x$ & $\sqrt{-x^2-y^2+4}-\sqrt{x-1}$&0.0092\\
+  11& MFH& $c_4$& $c_2$& $r_1(x)$& $r_3(x)$ & $\sqrt{-x^2-y^2+4}-\sqrt{x-1}$&0.0091\\ 
+  %1 & AEM & 0 & \sfrac{8}{5}  & 0 & $2x$ &  $y$ & 2.7307 \\
+  %2 & MELB & \sfrac{8}{5} & 4  & 0 & -$\frac{1}{2}x+4$ & $y$ & 8.2560 \\
+  %3 & BLF & 4 & \sfrac{24}{5} & $2x-8$ & -$\frac{1}{2}x+4$ & $y-2(x-4)$ & 0.5333 \\
+  %4 & ACIJ & 0 & \sfrac{4}{3} & $2x$ & 4 & $2x$ & 3.9506\\
+  %5 & JIE & \sfrac{4}{3} & \sfrac{8}{5} & $2x$ & $-3x+8$ & $2x$ & 0.5058\\ 
+  %6 & EIK & \sfrac{4}{3} & \sfrac{8}{5} & $-3x+8$ & 4 &  $-x-y+8$ & 0.2939 \\ 
+  %7 & EKDL & \sfrac{8}{5} & 4 & $-\frac{1}{2}x+4$ & 4 &  $-x-y+8$ & 5.9520 \\ 
+  %8 & LDF & 4 & \sfrac{24}{5} & $-\frac{1}{2}x+4$ & $-3x+16$ & $-x-y+8-2(x-4)$ & 0.5333 \\ 
+  %9 & CGN & 0 & \sfrac{4}{5} & 4 & $2x+4$ & $2x-(y-4)$ & 0.3413 \\ 
+  %10 & NCI & \sfrac{4}{5} & \sfrac{4}{3} & 4 & $-3x+8$ & $2x-(y-4)$ & 0.6068 \\
+  %11 & ICH & \sfrac{4}{5} & \sfrac{4}{3} & $-3x+8$ & $-\frac{1}{2}x+6$ & $-x-y+8-(y-4)$&0.3160\\
+  %12 & IHD & \sfrac{4}{3}& 4  & 4 & $-\frac{1}{2}x+6$ & $-x-y+8-(y-4)$&1.5803\\
+\end{tabular}
+
+\end{center}
+
+\end{table}
 

### 2019-08-15 Cav2D/article-template.tex
very good progress with second example

@@
 \end{equation}
-With $t(x_i^1,y_j^1)$ we can find expressions for $h$ and $s$ by employing Equation~\eqref{eq:c_z}. The obtained expressions of $h$ and $s$ can then be used to evaluate Equation~\eqref{eq:cav_ex2}:  
+As mentioned earlier, we can use $t(x_i^1,y_j^1)$ to find expressions for $h$ and $s$. The expressions of $h$ and $s$ so obtained can then be used to evaluate Equation~\eqref{eq:cav_ex2}:  
 \begin{eqnarray}
@@
 
-We can verify that $V_{\mathcal{S}}=0.864043$ is indeed correct via tradiosional calculus. We can first subdivide the $xy$-projection of $\mathcal{S}$ into regions
+\noindent
+We can verify that $V_{\mathcal{S}}=0.864043$ is indeed correct via a more traditional route.
+We first need to project $\mathcal{S}$ onto the $xy$ plane (see Figure~\ref{fig:sphere_xy}).
+We can then subdivide this projection into multiple regions (see Table~\ref{tab:table1}).
+Doing so actually results in $\mathcal{S}$ being decomposed into multiple solids.
+We can then
+compute the volume of the aforementioned solids. These computed volumes can then be added together to find the total volume of $\mathcal{S}$. The calculation details 
+of this approach is presented in Table~\ref{tab:table1}. Table~\ref{tab:table1} verifies that the volume of $\mathcal{S}$ is indeed $0.864043$.
 
 \begin{table}
+
 \caption{Double integrals for sphere. $c_1 \approx 1.1861407$, $c_2 \approx 1.6861407$, $c_3 \approx 0.6861407$ and $c_4 \approx 1.3507811$. $r_1(x) = \frac{1}{2}[\sqrt{17-4x^2}-1]$,
 $r_2(x) = \sqrt{-x^2-x+4}$, $r_3(x) = \sqrt{-x^2-(x-1)+4}$ and $r_4(x) = \frac{1}{2}[\sqrt{21-4x^2}-1]$.} 
+\label{tab:table1}
 \begin{center}

### 2019-08-15 Cav2D/article-template.tex
improved introduction somewhat

@@
 Cavalieri was a student of Galileo. He served as a professor of mathematics at the university of Bologna from 1629 until his death in 1647. 
-Galileo held Cavalieri in high esteem as is evedent from the following extract of a reference letter Galileo wrote in which he recommended Cavalieri for the chair of mathematics at Bologna: ``\emph{few, perhaps none, from
+Galileo held Cavalieri in high esteem. Galileo made the following remark in a reference letter he wrote on Cavalieri's behalf: ``\emph{few, perhaps none, from 
 Archimedes onwards, have investigated so deeply and have entered so far into the science of geometry}''.
-In 1935, a moon crater, Cavalerius, was officially named after him to commemorate his achievements and to honor his memory (see Fig ) \cite{?}.
+In 1935, a moon crater, Cavalerius, was officially named after Cavalieri to commemorate his achievements and to honor his memory (see Figure~\ref{fig:crater}) \cite{?}.
 \begin{figure}[htb]
@@
 \includegraphics[width=0.4\textwidth]{crater.jpg}
-\caption{xx}
+\caption{The moon crater Cavalerius. In 1935, this crater was officially named after Cavalieri.}
 \label{fig:crater}
@@
 It works by finding a planar figure or a solid, whose area or volume can easily be computed, which is Cavalieri congruent to a planar figure or solid whose 
-area or volume is unknown. Two planar figures or solids are Cavalieri congruent if they can be decomposed into the same set of parallel ``indivisibles''. An indivisible of 
+area or volume is unknown.
+Two planar figures or solids that are Cavalieri congruent have equal area or volume.
+Two planar figures or solids are Cavalieri congruent if they can be decomposed into the same set of parallel ``indivisibles''.
+An indivisible of
 a planar figure is any cord of the planar figure. An indivisible of a solid is any planar section of a solid. Two indivisibles are equal if they are of the same length or area.
@@
 \includegraphics[width=0.5\textwidth]{cav_principle.pdf}
-\caption{xx}
+\caption{Illustration of Cavalier's principle in $\mathbb{R}^3$. The volume of the left rectangular prism is equal to the volume of the right non-linear reectangular prism 
+due to Cavalieri's principle in $\mathbb{R}^3$.}
 \label{fig:cav_principle}
@@
 \noindent
-Fig~\ref{??} depicts a classic rectangular prism or column as well as a \emph{non-linear rectangular prism or column}. The volumes of the two solids in Fig~\ref{??} are equal due 
-to Cavalieri's principle. Note that in this article we use the non-standerdized term non-linear rectangular prism or column to refer to a solid that has a rectangular 
-base and lateral edges that are non-linear and translations of one another.
+Figure~\ref{fig:cav_principle} depicts a classic rectangular prism or column as well as a \emph{non-linear rectangular prism or column}.
+The volumes of the two solids in Fig~\ref{fig:cav_principle} are equal due
+to Cavalieri's principle. Note that in this article we use the non-standerdized phrase non-linear rectangular prism or column to refer to a solid that has rectangular 
+basis and lateral edges that are non-linear curves.
+Moreover, the four lateral edges of this solid also need to be translations of one another.
+In this paper, we will also take the liberty to refer to a non-linear rectangular prism whose base's
+lenght and widht both tend to zero as a non-linear rectangular infinitesimal. \\
+
+\noindent
+Ackermann
 

### 2019-08-15 Cav2D/article-template.tex
added a paragraph to introduction

@@
 The volumes of the two solids in Fig~\ref{fig:cav_principle} are equal due
-to Cavalieri's principle. Note that in this article we use the non-standerdized phrase non-linear rectangular prism or column to refer to a solid that has rectangular 
+to Cavalieri's principle. Note that in this article we use the non-standardized phrase non-linear rectangular prism or column to refer to a solid that has rectangular 
 basis and lateral edges that are non-linear curves.
@@
 \noindent
-Ackermann
+Ackermann et al. utilized the idea of using non-rectangular integration strips to perform integration in $\mathbb{R}^2$ and in doing so developed the Cavalieri integral. 
+The area of a non-rectangular integration strip is computed via Cavalieri’s principle in $\mathbb{R}^2$.
+The Cavalieri integral has proven to be very useful as a visualization tool.
+In this paper we extend the Cavalieri integral into $\mathbb{R}^3$, i.e.
+we use Cavalieri's principle in $\mathbb{R}^3$ to define the double
+Cavalieri integral. We also show that if a solid can be decomposed into an infinite number of non-linear rectangular infinitesimals then its volume can be computed 
+by the double Cavalieri integral. Whether the double Cavalieri integral will prove to be an equally useful visualization tool will be investigated as part of a future endeavor.
+The examples we provide at the end of the paper can also be used by an undergraduate Calculus lecturer to improve their students' understanding into the process of integration.
+
+and show that we can determine the volume of solids that .
 

### 2019-08-16 Cav2D/article-template.tex
added a paragraph to introduction

--- 2019-08-15 Cav2D/article-template.tex
@@
 
-\title{Computing volume via non-linear rectangular infinitesimals}
+\title{Computing volume via non-uniform rectangular infinitesimals}
 %\author{Woodrow Wilson and Herbert Hoover} %%leave blank in initial submission to allow for double blind reviewing
@@
 Bonaventura Cavalieri was a mathematician who lived in the 17th century. He made numerous contributions to the fields of optics, astronomy and geometry.
-Cavalieri was a student of Galileo. He served as a professor of mathematics at the university of Bologna from 1629 until his death in 1647. 
-Galileo held Cavalieri in high esteem. Galileo made the following remark in a reference letter he wrote on Cavalieri's behalf: ``\emph{few, perhaps none, from 
+He served as a professor of mathematics at the university of Bologna from 1629 until his death in 1647. 
+Cavalieri was a student of Galileo. Galileo held Cavalieri in high esteem. Galileo made the following remark in a reference letter he wrote on Cavalieri's behalf: ``\emph{few, perhaps none, from 
 Archimedes onwards, have investigated so deeply and have entered so far into the science of geometry}''.
@@
 \includegraphics[width=0.4\textwidth]{crater.jpg}
-\caption{The moon crater Cavalerius. In 1935, this crater was officially named after Cavalieri.}
+\caption{The moon crater Cavalerius, which is named after Bonaventura Cavalieri.}
 \label{fig:crater}
@@
 treatise, \emph{Geometria indivisibilibus}, in which he describes the precalculus method of indivisibles. The method of indivisibles can be attributed to the ancient Greeks,
-in this case Democritus and Archimedes. The method is used to compute the area and the volume of complex planar figures and solids, respectively.
-It works by finding a planar figure or a solid, whose area or volume can easily be computed, which is Cavalieri congruent to a planar figure or solid whose 
-area or volume is unknown.
-Two planar figures or solids that are Cavalieri congruent have equal area or volume.
-Two planar figures or solids are Cavalieri congruent if they can be decomposed into the same set of parallel ``indivisibles''.
-An indivisible of
+in this case Democritus and Archimedes. The method is used to compute the area and the volume of complex planar figures and solids, respectively.\\
+
+\noindent
+Two planar figures or solids are Cavalieri congruent if they can be decomposed into the same set of parallel ``indivisibles''. An indivisible of 
 a planar figure is any cord of the planar figure. An indivisible of a solid is any planar section of a solid. Two indivisibles are equal if they are of the same length or area.
@@
 \end{theorem}
+\noindent
+The method of indivisibles works by finding a planar figure or a solid, whose area or volume can easily be computed, which is Cavalieri congruent to a planar figure or solid whose 
+area or volume is difficult to compute.
 
@@
 \includegraphics[width=0.5\textwidth]{cav_principle.pdf}
-\caption{Illustration of Cavalier's principle in $\mathbb{R}^3$. The volume of the left rectangular prism is equal to the volume of the right non-linear reectangular prism 
+\caption{Illustration of Cavalier's principle in $\mathbb{R}^3$. The volume of the left rectangular prism is equal to the volume of the right non-uniform reectangular prism 
 due to Cavalieri's principle in $\mathbb{R}^3$.}
@@
 \noindent
-Figure~\ref{fig:cav_principle} depicts a classic rectangular prism or column as well as a \emph{non-linear rectangular prism or column}.
-The volumes of the two solids in Fig~\ref{fig:cav_principle} are equal due
-to Cavalieri's principle. Note that in this article we use the non-standerdized phrase non-linear rectangular prism or column to refer to a solid that has rectangular 
-basis and lateral edges that are non-linear curves.
-Moreover, the four lateral edges of this solid also need to be translations of one another.
+Figure~\ref{fig:cav_principle} depicts a classic rectangular prism or column (left solid) as well as a \emph{non-uniform rectangular prism or column} (right solid).
+The volumes of the two solids in Figure~\ref{fig:cav_principle} are equal due
+to Cavalieri's principle. Note that in this article we use the non-standardized phrase non-unifor rectangular prism or column to refer to a solid that has rectangular 
+basis and lateral edges that are either oblique lines or non-linear curves.
+Moreover, the four lateral edges of the aformentioned solid also need to be translations of one another.
 In this paper, we will also take the liberty to refer to a non-linear rectangular prism whose base's
-lenght and widht both tend to zero as a non-linear rectangular infinitesimal. \\
+lenght and widht both tend to zero as a non-uniform rectangular infinitesimal. \\
 
 \noindent
-Ackermann
+Ackermann et al. utilized the idea of using non-rectangular integration strips to perform integration in $\mathbb{R}^2$ and in doing so developed the Cavalieri integral \cite{ackermann12}. 
+The area of a non-rectangular integration strip is computed via Cavalieri’s principle.
+The Cavalieri integral has proven to be very useful: it can be used to visualize the Riemann-Stieltjes integral \cite{grobler19}.
+In this paper, we extend the Cavalieri integral into $\mathbb{R}^3$, i.e.
+we use Cavalieri's principle in $\mathbb{R}^3$ to define the double
+Cavalieri integral. We also show that if a solid can be decomposed into an infinite number of non-uniform rectangular infinitesimals then its volume can be computed 
+by the double Cavalieri integral. Whether the double Cavalieri integral will prove to be an equally useful visualization tool will be investigated as part of a future endeavor.
+Moreover, the examples we provide at the end of the paper are presented in such a way that they will deepen undergraduate Calculus students' understanding into the 
+process of integration. As this paper is mainly meant to be read by undergraduate students as well as the layman who is interested in the theory of integration we will 
+try to steer clear from using too many formal definitions and proofs and rather convey our ideas via worked out examples.\\
+
+\noindent
+We start the paper by defining the single and double Cavalieri integral. We end our paper with two worked out examples.
 
 \section{Cavalieri Integral}
-The single Cavalieri integral was originally defined in \cite{ackermann12} without having to resort to vector calculus.
-In this section we will redefine the Cavalieri integral using vector calculus notation.
+The single Cavalieri integral was originally defined by Ackermann et al.
+without having to resort to vector calculus \cite{ackermann12}.
+In this section, however, we will define the Cavalieri integral using vector calculus notation.
 As the reader will undoubtedly realize, if we define the single Cavalieri integral using vector calculus then it becomes trivial to
@@
 \noindent
-Consider the curve $f(x)$, the curve $\mathbf{c}(t)=\left <c_x(t),c_y(t) \right >$ and the interval $[a,b]$.
+Consider the continuous real-valued function $f(x)$, the continuous curve $\mathbf{c}(t)=\left <c_x(t),c_y(t) \right >$ and the interval $[a,b]$.
 
@@
 If a curve $\mathbf{c}(t)$ in $\mathbb{R}^2$ intersects the $x$ axis at the origin and $\mathbf{c}(t) + \left < e,0 \right >$ intersects 
-the curve $f(x)$ at a single point for all $e\in [a,b]$ then $\mathbf{c}(t)$ is a translational curve 
+the function $f(x)$ at a single point for all $e\in [a,b]$ then $\mathbf{c}(t)$ is a translational curve 
 with respect to $f(x)$ on $[a,b]$. 
@@
 Furthermore, let the transformation function $h$ map the $x$--coordinate $x_i^1\in [a,b]$ at which $\mathbf{c}(t) + \left <x_i^1,0 \right >$ intersects the
-$x$-axis to the $x$--coordinate at which $\mathbf{c}(t) + \left <x_i^1,0 \right >$ intersects $f(x,y)$. Note, the domain of $h$ is $[a,b]$. Let $a'$ denote the $x$-coordinate 
-at which $\mathbf{c}(t) + \left <a,0 \right >$ intersects $f(x,y)$ and let $b'$ denote the $x$-coordinate 
-at which $\mathbf{c}(t) + \left <b,0 \right >$ intersects $f(x,y)$.  Note, the range 
+$x$-axis to the $x$--coordinate at which $\mathbf{c}(t) + \left <x_i^1,0 \right >$ intersects $f(x)$. Note, the domain of $h$ is $[a,b]$. Let $a'$ denote the $x$-coordinate 
+at which $\mathbf{c}(t) + \left <a,0 \right >$ intersects $f(x)$ and let $b'$ denote the $x$-coordinate 
+at which $\mathbf{c}(t) + \left <b,0 \right >$ intersects $f(x)$.  Note, the range 
 of $h$ is $[a',b']$. As the partition of $[a,b]$ can be made arbitrarily fine, $h:[a,b]\rightarrow [a',b']$ actually maps every point $x_i^1\in [a,b]$ to a point $x_i^2\in [a',b']$. \\
@@
 \noindent
-Let $R$ denote the region which is bounded by $f(x,y)$, $\mathbf{c}(t)+\left <a,0\right >$, $\mathbf{c}(t)+\left <b,0\right >$ and the $x$-axis. 
-As an example, the region $R$ depicted in Figure~\ref{fig:caval2} is obtained if we set $f(x) = x$, $\mathbf{c}(t) = \left<-\frac{1}{2} t,\frac{1}{2} t\right>$, $a = 1$ and $b = 4$.
-Let $A_R$ denote the area of $R$. We can approximate $A_R$ with:
+Let $R$ denote the region which is bounded by $f(x)$, $\mathbf{c}(t)+\left <a,0\right >$, $\mathbf{c}(t)+\left <b,0\right >$ and the $x$-axis. 
+As an example, the region $R$ depicted in Figure~\ref{fig:caval2} is obtained if we set $f(x) = x$, $\mathbf{c}(t) = \frac{1}{2}\left<- t, t\right>$, $a = 1$ and $b = 4$.
+In general, let $A_R$ denote the area of $R$. We can approximate $A_R$ with:
 \begin{equation}
  \label{eq:caval1}
- A_R \approx \sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1,
+ A_R \approx \sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1.
  \end{equation}
@@
 \caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$.
-The figure also depicts the partition points $x_i^1$ and $x_i^2$ as used in the Cavalieri sum (see Eq.~\eqref{eq:cav_sum}).
+The parametric representation of $a(y)$ is $\mathbf{c}(t) = \frac{1}{2} \left <-t,t \right >$.
+The figure also depicts the partition points $x_i^1$ and $x_i^2$ as used in the Cavalieri sum (see Eq.~\eqref{eq:caval1}).
 Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
@@
 \noindent
-Note, the Cavalieri integral is denoted in \cite{ackermann12} via:
+The area of the region $R$ depicted in Figure~\ref{fig:caval2} can, therefore, be computed as follows:
+\begin{equation}
+\int \limits_{\mathcal{C}} f(x)~dx = \int_a^b f \circ h (x)\, dx = \dfrac{1}{2}\int_1^4x\, dx = 3.75.  
+\end{equation}
+The expression for $h$ was found by employing Equation~\eqref{eq:pat_rel_1d}, Equation~\eqref{eq:t_func_1d} and Equation~\eqref{eq:h_func_1d}. Let us now verify that 
+this result is correct by using a more conventional approach:
+\begin{equation}
+\int_0^2x\, dx+\int_2^44-x\, dx- \int_0^{\frac{1}{2}}x\, dx-\int_{\frac{1}{2}}^11-x\, dx = 3.75. 
+\end{equation}
+
+\noindent
+In \cite{ackermann12}, the Cavalieri integral is denoted via:
 \begin{equation}

### 2019-08-16 Cav2D/article-template.tex
started adding prismatoid description

@@
 The parametric representation of $a(y)$ is $\mathbf{c}(t) = \frac{1}{2} \left <-t,t \right >$.
-The figure also depicts the partition points $x_i^1$ and $x_i^2$ as used in the Cavalieri sum (see Eq.~\eqref{eq:caval1}).
+The figure also depicts the partition points $x_i^1$ and $x_i^2$ as used in the Cavalieri sum (see Equation~\eqref{eq:caval1}).
 Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
@@
 \noindent
-In \cite{ackermann12}, the Cavalieri integral is denoted via:
-\begin{equation}
-\label{eq:cav_1d}
-\int_{a(y)}^{b(y)} f(x)~dx = \lim_{n \rightarrow \infty}  \sum_{i=0}^{n-1} f(x_i^2) \Delta x_i^1,
-\end{equation}
-where $a(y)$ denotes the functional representation of $\mathbf{c}(t) + \left <a,0 \right >$ and $b(y) = a(y)+(b-a)$.
+In \cite{ackermann12}, the Cavalieri integral is denoted via $\int_{a(y)}^{b(y)} f(x)~dx$, where $a(y)$ denotes the functional representation of $\mathbf{c}(t) + \left <a,0 \right >$ and $b(y) = a(y)+(b-a)$
 
@@
 \noindent
-Without the loss of generality, consider the surface $f(x,y)$, the curve $\mathbf{c}(t)$\\$=\left <c_x(t),c_y(t), c_z(t) \right >$ and the region $R = [a,b]\times [c,d] = \{(x,y)\in \mathbb{R}^2|a \leq x \leq b, c \leq y \leq d\}$.
+Without the loss of generality, consider the continuous surface $f(x,y)$, the continuous curve $\mathbf{c}(t)=\left <c_x(t),c_y(t), c_z(t) \right >$ and the region $R = [a,b]\times [c,d] = \{(x,y)\in \mathbb{R}^2|a \leq x \leq b, c \leq y \leq d\}$.
 
@@
 of $T$ with $S$.
-As the paartition of $R$ can be made arbitrarily fine, $T:R\rightarrow S$ actually maps every point $(x_i^1,y_j^1)\in R$ to a point $(x_i^2,y_j^2)\in S$.
+As the partition of $R$ can be made arbitrarily fine, $T:R\rightarrow S$ actually maps every point $(x_i^1,y_j^1)\in R$ to a point $(x_i^2,y_j^2)\in S$.
 In general, the transformation $T$ is defined as follows:
@@
 Let $\mathcal{S}$ denote the solid which is obtained by connecting the vertices of $R$ and
-$S_f$ via translations of $\mathbf{c}(t)$ along the $xy$ plane and then closing the resulting open faces that form due to the aforementioned connections by employing appropriate surfaces. 
+$S_f$ via translations of $\mathbf{c}(t)$ along the $xy$ plane and then closing the resulting open faces that form due to the aforementioned connections by employing appropriate surfaces. Note that 
+$\mathcal{S}$ can be decomposed into an infinite number of non-uniform rectangular infinitesimals.
 As an example, the solid $\mathcal{S}$ depicted in Figure~\ref{fig:prismatoid_solid} is obtained if we set $f(x,y) = -x - y + 8$, $\mathbf{c}(t) = -\left<\frac{1}{2}t,t,t\right>$ and $R = \{(x,y)\in\mathbb{R}^2|0 \geq x \geq 4, 0 \geq x \geq 4\} \nonumber$.
 Moreover, the domain $R$ and the range $S$ of the transformation function $T$ which is associated with the solid $\mathcal{S}$ is depicted in Figure~\ref{fig:prismatoid_regions}.  
-Let $V_{\mathcal{S}}$ denote the volume of $\mathcal{S}$. We can approximate $V_{\mathcal{S}}$ with:
+In general, let $V_{\mathcal{S}}$ denote the volume of $\mathcal{S}$. We can approximate $V_{\mathcal{S}}$ with:
 \begin{equation}
@@
 \includegraphics[width=0.75\textwidth]{prismatoid_solid.pdf}
-\caption{xx}
+\caption{The solid $\mathcal{S}$ which is bounded by the planes $f(x,y)=-x-y+8$, $2x$, $2(x-4)$, $y$, $y-4$ and the $xy$-plane. The figure also depicts the partition 
+points $(x_i^1,y_i^1)\in\mathcal{R}$ and $(x_i^1,y_i^1)\in\mathcal{R}$ which is used in the double Cavalieri sum (see Equation~\eqref{eq:cav_2d}).}
 \label{fig:prismatoid_solid}
@@
 \includegraphics[width=0.75\textwidth]{prismatoid_regions.pdf}
-\caption{xx}
+\caption{The transformation function $T$ which is associated with the solid $\mathcal{S}$ depicted in Figure~\ref{fig:prismatoid_solid}.}
 \label{fig:prismatoid_regions}
@@
 \centering
-\includegraphics[width=0.75\textwidth]{prismatoid.pdf}
-\caption{xx}
-\label{fig:prismatoid}
+\includegraphics[width=0.5\textwidth]{prismatoid_real.jpg}
+\caption{A physical not-to-scale model of the solid $\mathcal{S}$ depicted in Figure~\ref{fig:prismatoid_solid}.}
+\label{fig:prismatoid_real}
 \end{figure}
@@
 \centering
-\includegraphics[width=0.5\textwidth]{prismatoid_real.jpg}
-\caption{xx}
-\label{fig:prismatoid_real}
+\includegraphics[width=0.75\textwidth]{prismatoid.pdf}
+\caption{The solid depicted in Figure~\ref{fig:prismatoid_solid} is a prismatoid. We can, therefore, calculate its volume with the prismatoid volume equation: $V_{\mathcal{S}}$. If the 
+areas of the two parallel faces are A1 and A3, the cross-sectional area of the intersection of the prismatoid with a plane midway between the two parallel faces is A2, 
+and the height (the distance between the two parallel faces) is h, then the volume of the prismatoid is given by  }
+\label{fig:prismatoid}
 \end{figure}

### 2019-08-16 Cav2D/article-template.tex
captions to figures

@@
 \includegraphics[width=0.75\textwidth]{prismatoid.pdf}
-\caption{The solid depicted in Figure~\ref{fig:prismatoid_solid} is a prismatoid. We can, therefore, calculate its volume with the prismatoid volume equation: $V_{\mathcal{S}}$. If the 
-areas of the two parallel faces are A1 and A3, the cross-sectional area of the intersection of the prismatoid with a plane midway between the two parallel faces is A2, 
-and the height (the distance between the two parallel faces) is h, then the volume of the prismatoid is given by  }
+\caption{Another depiction of the solid $\mathcal{S}$ found in Figure~\ref{fig:prismatoid_solid} which highlights the fact that $\mathcal{S}$ is a prismatoid.
+We can, therefore, calculate its volume with the prismatoid volume equation: $V_{\mathcal{S}}= \frac{h}{6}(A_1+4A_2+A_3)$.
+Note, the area of the two basis of $\mathcal{S}$ are denoted by $A1$ and $A3$, the cross-sectional area of the intersection of $\mathcal{S}$ with a plane midway between the two basis is denoted via $A2$,
+and the height of $\mathcal{S}$ is denoted by $h$. Moreover, also note that the surfaces associated with $A1$, $A2$ and $A3$ are depicted in the above figure using shaded sheets. For $\mathcal{S}$ 
+$A1=$, $A2=$, $A3 = $ and $h=$. The volume of $\mathcal{S}$ is, therefore, $25.6$.}
 \label{fig:prismatoid}
@@
 \includegraphics[width=0.75\textwidth]{sphere_solid.pdf}
-\caption{xx}
+\caption{The solid $\mathcal{S}$ which is bounded by the planes $f(x,y)=\sqrt{-x^2-y^2+4}$, $\sqrt{x}$, $\sqrt{x-1}$, $\sqrt{y}$, $\sqrt{y-1}$ and the $xy$-plane.}
 \label{fig:sphere_solid}
@@
 \includegraphics[width=0.75\textwidth]{sphere_regions.pdf}
-\caption{xx}
+\caption{The transformation $T$ associated with the solid $\mathcal{S}$ depicted in Figure~\ref{fig:sphere_solid}.}
 \label{fig:sphere_regions}
@@
 \includegraphics[width=0.75\textwidth]{sphere_xy.pdf}
-\caption{xx}
+\caption{The $xy$-projection of the solid $\mathcal{S}$ depicted in Figure~\ref{fig:sphere_solid} onto the $xy$-plane.}
 \label{fig:sphere_xy}

### 2019-08-16 Cav2D/func_plotter.py
fixed prismatoid volume

@@ -1450,7 +1450,12 @@ def volume_of_prismatoid():
     d = d3(V1,V2)
   
     A2a = area_trap(a,b,c,d) 
-    
+
+    print("h = ",h)
+    print("A1 = ",A1)
+    print("A2a = ",A2a)
+    print("A3 = ",A3)    
+
     Va = (1.0/6.0)*h*(A1+4*A2a+A3)
     print("Va = ",Va)
 

### 2019-08-16 Cav2D/article-template.tex
fixed prismatoid volume
added a summary

@@
 and the height of $\mathcal{S}$ is denoted by $h$. Moreover, also note that the surfaces associated with $A1$, $A2$ and $A3$ are depicted in the above figure using shaded sheets. For $\mathcal{S}$ 
-$A1=$, $A2=$, $A3 = $ and $h=$. The volume of $\mathcal{S}$ is, therefore, $25.6$.}
+$A1=10.7331$, $A2= 7.1554$, $A3 = 3.5777$ and $h = 3.5777$. The volume of $\mathcal{S}$ is, therefore, $25.6$.}
 \label{fig:prismatoid}
@@
 
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.75\textwidth]{sphere_solid.pdf}
+\caption{The solid $\mathcal{S}$ which is bounded by the planes $f(x,y)=\sqrt{-x^2-y^2+4}$, $\sqrt{x}$, $\sqrt{x-1}$, $\sqrt{y}$, $\sqrt{y-1}$ and the $xy$-plane.}
+\label{fig:sphere_solid}
+\end{figure}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.75\textwidth]{sphere_regions.pdf}
+\caption{The transformation $T$ associated with the solid $\mathcal{S}$ depicted in Figure~\ref{fig:sphere_solid}.}
+\label{fig:sphere_regions}
+\end{figure}
+
 \noindent
@@
 
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.75\textwidth]{sphere_xy.pdf}
+\caption{The projection of the solid $\mathcal{S}$ depicted in Figure~\ref{fig:sphere_solid} onto the $xy$-plane.}
+\label{fig:sphere_xy}
+\end{figure}
+
 \begin{table}
 
-\caption{Double integrals for sphere. $c_1 \approx 1.1861407$, $c_2 \approx 1.6861407$, $c_3 \approx 0.6861407$ and $c_4 \approx 1.3507811$. $r_1(x) = \frac{1}{2}[\sqrt{17-4x^2}-1]$,
-$r_2(x) = \sqrt{-x^2-x+4}$, $r_3(x) = \sqrt{-x^2-(x-1)+4}$ and $r_4(x) = \frac{1}{2}[\sqrt{21-4x^2}-1]$.} 
+\caption{Computing the volume of the solid $\mathcal{S}$ depicted in Figure~\ref{fig:sphere_solid} using a more traditional approach.
+The region $R_k$ is bounded by $x=a$, $x=b$, $g_1(x)$ and $g_2(x)$.
+Moreover, $c_1 \approx 1.1861407$, $c_2 \approx 1.6861407$, $c_3 \approx 0.6861407$ and $c_4 \approx 1.3507811$.
+$r_1(x) = \frac{1}{2}[\sqrt{17-4x^2}-1]$,
+$r_2(x) = \sqrt{-x^2-x+4}$, $r_3(x) = \sqrt{-x^2-(x-1)+4}$ and $r_4(x) = \frac{1}{2}[\sqrt{21-4x^2}-1]$. If we sum the last column we obtain the volume of $\mathcal{S}$ which is $0.864043$.} 
 \label{tab:table1}
@@
 \end{table}
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.75\textwidth]{sphere_solid.pdf}
-\caption{The solid $\mathcal{S}$ which is bounded by the planes $f(x,y)=\sqrt{-x^2-y^2+4}$, $\sqrt{x}$, $\sqrt{x-1}$, $\sqrt{y}$, $\sqrt{y-1}$ and the $xy$-plane.}
-\label{fig:sphere_solid}
-\end{figure}
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.75\textwidth]{sphere_regions.pdf}
-\caption{The transformation $T$ associated with the solid $\mathcal{S}$ depicted in Figure~\ref{fig:sphere_solid}.}
-\label{fig:sphere_regions}
-\end{figure}
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.75\textwidth]{sphere_xy.pdf}
-\caption{The $xy$-projection of the solid $\mathcal{S}$ depicted in Figure~\ref{fig:sphere_solid} onto the $xy$-plane.}
-\label{fig:sphere_xy}
-\end{figure}
 
@@
 \begin{abstract}
-We presented a novel geometric interpretation of the Riemann-Liouville fractional integral. We found that a Riemann-Liouville integral can 
-be thought of as the area obtained by summing together the area of an infinite number of non-rectangular infinitesimals whose shape is determined by the 
-order of integration $\alpha$ and the integration limit $t$. We also showed that this geometric interpretation offers many pedagogical benefits as it is very similar
-in nature to the geometric interpretation of the Riemann integral.   
+In this paper we extended the Cavalieri integral into three dimensional euclidean space, i.e. we defined the double Cavalieri integral. 
+We also showed that this integral can be used to compute the volume of solids that can be decomposed into an infinite number of 
+non-uniform rectangular infinitesimals. We end the paper with two fully worked out examples. In the first example we compute the 
+volume of a prismatoid using the double Cavalieri integral. In the second example we compute the volume of a complex solid which is housed within a sphere using the double Cavalieri integral.
 \end{abstract}

### 2019-08-16 Cav2D/article-template.tex
fixed the figures

@@
 \caption{Illustration of Cavalier's principle in $\mathbb{R}^3$. The volume of the left rectangular prism is equal to the volume of the right non-uniform reectangular prism 
-due to Cavalieri's principle in $\mathbb{R}^3$.}
+due to Cavalieri's principle in $\mathbb{R}^3$. The infinitesimals associated with the two solids are also depicted.}
 \label{fig:cav_principle}
@@
 In this paper, we will also take the liberty to refer to a non-linear rectangular prism whose base's
-lenght and widht both tend to zero as a non-uniform rectangular infinitesimal. \\
+lenght and widht both tend to zero as a \emph{non-uniform rectangular infinitesimal}. \\
 

### 2019-08-16 Cav2D/func_plotter.py

@@ -602,16 +602,17 @@ def plot_paper_figure(xx,yy,xx2,yy2,zz2,K=8):
     Ce[1] = (yy[0,0]+yy2[0,0])/2.0
     Ce[2] = zz2[0,0]/2.0
     
-    ax.text(-1.1, 0, 0, r"$(x_i^1,y_i^1)$", "y")
+    ax.text(-1.1, 0, 0, r"$(x_i^1,y_j^1)$", "y")
 
-    ax.text(xx2[0,0]-1.3, yy2[0,0]-0.3, 0, r"$(x_i^2,y_i^2)$", "y")
+    ax.text(xx2[0,0]-1.3, yy2[0,0]-0.3, 0, r"$(x_i^2,y_j^2)$", "y")
 
-    ax.text(xx2[0,0]-1.6, yy2[0,0], zz2[0,0], r"$f(x_i^2,y_i^2)$", "x")
+    ax.text(xx2[0,0]-1.6, yy2[0,0], zz2[0,0], r"$f(x_i^2,y_j^2)$", "x")
 
     ax.text(0, -0.6, 0, r"$\Delta x_i^1$", "x")
-    ax.text(0.4, 0.3, 0, r"$\Delta y_i^1$", "y")
+    ax.text(0.4, 0.3, 0, r"$\Delta y_j^1$", "y")
 
     ax.text(Ce[0],Ce[1],Ce[2],r"$\mathbf{c}(t)$","x")
+    ax.text(Ce[0]/2,Ce[1]/2,Ce[2]/2,r"$\mathcal{K}_{ij}$","x")
 
     ax.text(2, 2, 0, r"$R$", "x")
     ax.text(2.9, 3.2, 0, r"$S$", "x")
@@ -1252,9 +1253,9 @@ def plot_volume2(xx,yy,xx2,yy2,t):
     #plt.axis('equal')
     plt.fill(x, y,"b",alpha=0.2,edgecolor='black', linewidth=3)
 
-    plt.annotate('$R-(x_i^1,y_i^1)$', xy=(0.5, 0.5), xytext=(0.4, 0.4))
+    plt.annotate('$R-(x_i^1,y_j^1)$', xy=(0.5, 0.5), xytext=(0.4, 0.4))
     plt.scatter(0.5,0.5,color="b",s=30, marker="o",alpha=0.8)
-    plt.annotate('$S-(x_i^2,y_i^2)$', xy=(1.3, 1.3), xytext=(1.18, 1.35))
[…]

### 2019-08-16 Cav2D/article-template.tex
fixed non-linear reference

@@
 Moreover, the four lateral edges of the aformentioned solid also need to be translations of one another.
-In this paper, we will also take the liberty to refer to a non-linear rectangular prism whose base's
+In this paper, we will also take the liberty to refer to a non-uniform rectangular prism whose base's
 lenght and widht both tend to zero as a \emph{non-uniform rectangular infinitesimal}. \\
@@
 Moreover, the examples we provide at the end of the paper are presented in such a way that they will deepen undergraduate Calculus students' understanding into the 
-process of integration. As this paper is mainly meant to be read by undergraduate students as well as the layman who is interested in the theory of integration we will 
-try to steer clear from using too many formal definitions and proofs and rather convey our ideas via worked out examples.\\
+process of integration.
+Furhtermore, we will try to steer clear from using too many formal definitions and proofs and rather convey our ideas via worked out examples, as this paper is mainly meant to be read by undergraduate students as well as the layman who is interested in the theory of integration.\\
 
@@
 In this section we define the double Cavalieri integral and we show that it can be used to calculate the volume of solids that can be decomposed into an infinite 
-number of non-linear regtangular infinitesimals.\\
+number of non-uniform regtangular infinitesimals.\\
 
@@
 %We will now show 
-%that we can approximate $V_{\mathcal{S}}$ by summing together the volume of $n$ non-linear prisms that cicumscribe $\mathcal{S}$ and that as $n\rightarrow \infty$ 
+%that we can approximate $V_{\mathcal{S}}$ by summing together the volume of $n$ non-uniform prisms that cicumscribe $\mathcal{S}$ and that as $n\rightarrow \infty$ 
 %the aformentioned sum approaches $V_{\mathcal{S}}$. 
@@
 \item The product $\Delta A = \Delta x_i^1\times \Delta y_j^1$ represents the area of subrectangle $R_{ij}$.
-\item $f(x_i^2,y_j^2)$ represents the height of a non-linear rectangular column or prism $\mathcal{K}_{ij}$ whose base is $R_{ij}$. Furthermore, the lateral edges of this column are all translations 
+\item $f(x_i^2,y_j^2)$ represents the height of a non-uniform rectangular column or prism $\mathcal{K}_{ij}$ whose base is $R_{ij}$. Furthermore, the lateral edges of this column are all translations 
 of $\mathbf{c}(t)$ along the $xy$-plane. The cross-section between any parallel plane to the $xy$-plane and $\mathcal{K}_{ij}$ is a rectangle with the same dimensions as $R_{ij}$. 
@@
 \noindent
-Since $\mathcal{S}$ can be decomposed into an infinite number of non-linear rectangular infinitesimals we can compute its volume using:
+Since $\mathcal{S}$ can be decomposed into an infinite number of non-uniform rectangular infinitesimals we can compute its volume using:
 \begin{equation}

### 2019-08-19 Cav2D/article-template.tex
added some references

@@
 
-\title{Computing volume via non-uniform rectangular infinitesimals}
+\title{Computing volume via oblique or irregularly shaped rectangular infinitesimals}
 %\author{Woodrow Wilson and Herbert Hoover} %%leave blank in initial submission to allow for double blind reviewing
@@
 Bonaventura Cavalieri was a mathematician who lived in the 17th century. He made numerous contributions to the fields of optics, astronomy and geometry.
-He served as a professor of mathematics at the university of Bologna from 1629 until his death in 1647. 
+He served as a professor of mathematics at the university of Bologna from 1629 until his death in 1647 \cite{andersen1985,eves1991,jullien2015}. 
 Cavalieri was a student of Galileo. Galileo held Cavalieri in high esteem. Galileo made the following remark in a reference letter he wrote on Cavalieri's behalf: ``\emph{few, perhaps none, from 
-Archimedes onwards, have investigated so deeply and have entered so far into the science of geometry}''.
-In 1935, a moon crater, Cavalerius, was officially named after Cavalieri to commemorate his achievements and to honor his memory (see Figure~\ref{fig:crater}) \cite{?}.
+Archimedes onwards, have investigated so deeply and have entered so far into the science of geometry}'' \cite{gonzalez2018}.
+In 1935, a moon crater, Cavalerius, was officially named after Cavalieri to commemorate his achievements and to honor his memory (see Figure~\ref{fig:crater}) \cite{blagg1935}.
 \begin{figure}[htb]
@@
 \includegraphics[width=0.4\textwidth]{crater.jpg}
-\caption{The moon crater Cavalerius, which is named after Bonaventura Cavalieri.}
+\caption{The moon crater Cavalerius, which is named after Bonaventura Cavalieri. James Stuby / Wikimedia Commons / Public Domain.}
 \label{fig:crater}
@@
 treatise, \emph{Geometria indivisibilibus}, in which he describes the precalculus method of indivisibles. The method of indivisibles can be attributed to the ancient Greeks,
-in this case Democritus and Archimedes. The method is used to compute the area and the volume of complex planar figures and solids, respectively.\\
+in this case Democritus and Archimedes \cite{eves1991}. The method is used to compute the area and the volume of complex planar figures and solids, respectively.\\
 
@@
 a planar figure is any cord of the planar figure. An indivisible of a solid is any planar section of a solid. Two indivisibles are equal if they are of the same length or area.
-It is Cavalieri's principle that assures us that two planar figures or solids that are composed of the same set of indivisibles have equal area or volume. Cavalieri's principle 
+It is Cavalieri's principle that assures us that two planar figures or solids that are composed of the same set of indivisibles have equal area or volume \cite{andersen1985,eves1991,jullien2015,malik1984,wildberger2002,william1917,young1985}.
+Cavalieri's principle
 in $\mathbb{R}^3$ is stated below without proof:
@@
 the two sections cut by them on any plane parallel to the including planes are always
-equal, then the volumes of the two solids are equal.
+equal, then the volumes of the two solids are equal (see Figure~\ref{fig:cav_principle}).
 \end{theorem}
@@
 \includegraphics[width=0.5\textwidth]{cav_principle.pdf}
-\caption{Illustration of Cavalier's principle in $\mathbb{R}^3$. The volume of the left rectangular prism is equal to the volume of the right non-uniform reectangular prism 
-due to Cavalieri's principle in $\mathbb{R}^3$. The infinitesimals associated with the two solids are also depicted.}
+\caption{Illustration of Cavalier's principle in $\mathbb{R}^3$. The volume of the left rectangular prism is equal to the volume of the right irregularly shaped rectangular prism 
+due to Cavalieri's principle in $\mathbb{R}^3$. The infinitesimals associated with these two solids are also depicted.}
 \label{fig:cav_principle}
@@
 \noindent
-Figure~\ref{fig:cav_principle} depicts a classic rectangular prism or column (left solid) as well as a \emph{non-uniform rectangular prism or column} (right solid).
+Figure~\ref{fig:cav_principle} depicts a classic rectangular prism or column (left solid) as well as an \emph{irregular rectangular prism or column} (right solid).
 The volumes of the two solids in Figure~\ref{fig:cav_principle} are equal due
-to Cavalieri's principle. Note that in this article we use the non-standardized phrase non-unifor rectangular prism or column to refer to a solid that has rectangular 
-basis and lateral edges that are either oblique lines or non-linear curves.
+to Cavalieri's principle. Note that in this article we use the non-standardized phrase irregular rectangular prism or column to refer to a solid that has rectangular 
+basis and lateral edges that are non-linear curves.
 Moreover, the four lateral edges of the aformentioned solid also need to be translations of one another.
-In this paper, we will also take the liberty to refer to a non-uniform rectangular prism whose base's
-lenght and widht both tend to zero as a \emph{non-uniform rectangular infinitesimal}. \\
+In this paper, we will also take the liberty to refer to an irregular rectangular prism whose base's
+lenght and widht both tend to zero as an \emph{irregular rectangular infinitesimal}. \\
 
@@
 we use Cavalieri's principle in $\mathbb{R}^3$ to define the double
-Cavalieri integral. We also show that if a solid can be decomposed into an infinite number of non-uniform rectangular infinitesimals then its volume can be computed 
+Cavalieri integral. We also show that if a solid can be decomposed into an infinite number of irregularly shaped rectangular infinitesimals then its volume can be computed 
 by the double Cavalieri integral. Whether the double Cavalieri integral will prove to be an equally useful visualization tool will be investigated as part of a future endeavor.
@@
 process of integration.
-Furhtermore, we will try to steer clear from using too many formal definitions and proofs and rather convey our ideas via worked out examples, as this paper is mainly meant to be read by undergraduate students as well as the layman who is interested in the theory of integration.\\
+Furhtermore, as this paper is mainly meant to be read by undergraduate students as well as the layman who is interested in the theory of integration, we will as far as possible try to steer clear from using too many formal definitions and proofs and rather convey our ideas via worked out examples.\\
 
@@
 The single Cavalieri integral was originally defined by Ackermann et al.
-without having to resort to vector calculus \cite{ackermann12}.
+without having to resort to vector calculus \cite{ackermann12,stewart1999}.
 In this section, however, we will define the Cavalieri integral using vector calculus notation.
@@
 In this section we define the double Cavalieri integral and we show that it can be used to calculate the volume of solids that can be decomposed into an infinite 
-number of non-uniform regtangular infinitesimals.\\
+number of irregularly shaped regtangular infinitesimals.\\
 
@@
 $S_f$ via translations of $\mathbf{c}(t)$ along the $xy$ plane and then closing the resulting open faces that form due to the aforementioned connections by employing appropriate surfaces. Note that 
-$\mathcal{S}$ can be decomposed into an infinite number of non-uniform rectangular infinitesimals.
+$\mathcal{S}$ can be decomposed into an infinite number of irregularly shaped rectangular infinitesimals.
 As an example, the solid $\mathcal{S}$ depicted in Figure~\ref{fig:prismatoid_solid} is obtained if we set $f(x,y) = -x - y + 8$, $\mathbf{c}(t) = -\left<\frac{1}{2}t,t,t\right>$ and $R = \{(x,y)\in\mathbb{R}^2|0 \geq x \geq 4, 0 \geq x \geq 4\} \nonumber$.
@@
 \item The product $\Delta A = \Delta x_i^1\times \Delta y_j^1$ represents the area of subrectangle $R_{ij}$.
-\item $f(x_i^2,y_j^2)$ represents the height of a non-uniform rectangular column or prism $\mathcal{K}_{ij}$ whose base is $R_{ij}$. Furthermore, the lateral edges of this column are all translations 
+\item $f(x_i^2,y_j^2)$ represents the height of an irregular rectangular column or prism $\mathcal{K}_{ij}$ (or in the case of Figure~\ref{fig:prismatoid_solid} and oblique rectangular prism) whose base is $R_{ij}$.
+Furthermore, the lateral edges of this column are all translations
 of $\mathbf{c}(t)$ along the $xy$-plane. The cross-section between any parallel plane to the $xy$-plane and $\mathcal{K}_{ij}$ is a rectangle with the same dimensions as $R_{ij}$. 
@@
 in Figure~\ref{fig:prismatoid_solid}, Figure~\ref{fig:prismatoid} and Figure~\ref{fig:prismatoid_real}. Solid $\mathcal{S}$ is a prismatoid, since all of its 
-vertices lie in two parallel planes. Furthermore, all of its lateral faces are trapezoids or triangles (if viewed from the top). Also note the following: the base of $\mathcal{S}$ is the region 
+vertices lie in two parallel planes.
+Furthermore, all of its lateral faces are trapezoids or triangles (if viewed from the top) \cite{bradley1979}.
+Also note the following: the base of $\mathcal{S}$ is the region
  $R = [0,4]\times [0,4]$ (if viewed from the front) and that the line of intersection between $2x$ and $y$ is $\mathbf{c}(t) = -\left<\frac{1}{2}t,t,t\right>$.
@@
 Note, the area of the two basis of $\mathcal{S}$ are denoted by $A1$ and $A3$, the cross-sectional area of the intersection of $\mathcal{S}$ with a plane midway between the two basis is denoted via $A2$,
-and the height of $\mathcal{S}$ is denoted by $h$. Moreover, also note that the surfaces associated with $A1$, $A2$ and $A3$ are depicted in the above figure using shaded sheets. For $\mathcal{S}$ 
+and the height of $\mathcal{S}$ is denoted by $h$. Moreover, also note that the surfaces associated with $A1$, $A2$ and $A3$ are depicted in the above figure using shaded sheets. For $\mathcal{S}$, 
 $A1=10.7331$, $A2= 7.1554$, $A3 = 3.5777$ and $h = 3.5777$. The volume of $\mathcal{S}$ is, therefore, $25.6$.}
@@
 \begin{equation}
-t(x_i^1,y_j^1) = \frac{x_i^1}{5} + \frac{y_j^1}{5} + \frac{8}{5}. 
+t(x_i^1,y_j^1) = \frac{1}{5}x_i^1 + \frac{1}{5}y_j^1 + \frac{8}{5}. 
 \end{equation}
@@
 \noindent
-We can easily verify that the $V_{\mathcal{S}} = 25.6$ is in fact correct, since $\mathcal{S}$ is a prismatoid. According to the prismatoid volume 
-equation $V_{\mathcal{S}}=25.6$. The details of this computation is described in the caption of Figure~\ref{fig:prismatoid}. This then validates Equation~\ref{eq:final_int_prismatoid}.
+We can easily verify that the $V_{\mathcal{S}} = 25.6$ is in fact correct, since $\mathcal{S}$ is a prismatoid. Indeed, according to the prismatoid volume 
+equation,  $V_{\mathcal{S}}=25.6$. The details of this computation is described in the caption of Figure~\ref{fig:prismatoid}.
 
@@
 \noindent
-Since $\mathcal{S}$ can be decomposed into an infinite number of non-uniform rectangular infinitesimals we can compute its volume using:
+Since $\mathcal{S}$ can be decomposed into an infinite number of irregularly shaped rectangular infinitesimals we can compute its volume using:
 \begin{equation}
@@
 \caption{Computing the volume of the solid $\mathcal{S}$ depicted in Figure~\ref{fig:sphere_solid} using a more traditional approach.
-The region $R_k$ is bounded by $x=a$, $x=b$, $g_1(x)$ and $g_2(x)$.
+The region $R_k$ is bounded by $x=a$, $x=b$, $g_1(x)$ and $g_2(x)$ (see Figure~\ref{fig:sphere_xy}).
 Moreover, $c_1 \approx 1.1861407$, $c_2 \approx 1.6861407$, $c_3 \approx 0.6861407$ and $c_4 \approx 1.3507811$.
@@
 We also showed that this integral can be used to compute the volume of solids that can be decomposed into an infinite number of 
-non-uniform rectangular infinitesimals. We end the paper with two fully worked out examples. In the first example we compute the 
-volume of a prismatoid using the double Cavalieri integral. In the second example we compute the volume of a complex solid which is housed within a sphere using the double Cavalieri integral.
+irrgularly shaped rectangular infinitesimals. We end the paper with two fully worked out examples. In the first example we compute the 
+volume of a prismatoid using the double Cavalieri integral.
+In the second example we compute the volume of a complex irregular shaped solid which is housed within a sphere using the double Cavalieri integral.
 \end{abstract}
@@
 
-\bibitem{adda97} Adda,~F.~B. (1997). Geometric interpretation of the fractional derivative. \textit{J. of Fract. Calc.}, 11: 21--52.
+\bibitem{andersen1985}
+K.~Andersen. (1985). Cavalieri's Method of Indivisibles. \emph{Arch. Hist. Exact Sci.} 31(4): 291--367.
 
-\bibitem{bartle76} Bartle,~R.~G. (1976). \textit{The Elements of Real Analysis.} New York: Wiley.
+\bibitem{blagg1935}
+M.~A Blagg, A. Blagg and K. M{\"u}ller. (1935). \emph{Named Lunar Formations}. Percy Lund, Humphries and Co. Ltd.
 
-%Physical
-\bibitem{cioc16} Cioc, R.
-(2016).
-Physical and geometrical interpretation of Gr\"{u}nwald-Letnikov differintegrals: Measurement of path and acceleration.
-\textit{Fract.
-Calc.
-Appl.
-Anal.} 19(1): 161--172.
+\bibitem{bradley1979}
+A.~D.~Bradley. (1979). Prismatoid, Prismoid, Generalized Prismoid. \emph{Amer. Math. Monthly.} 86(6): 486--490.
 
-\bibitem{davis59} Davis,~P.~J. (1959). Leonhard Euler's Integral: A Historical Profile of the Gamma Function. \textit{Amer. Math. Monthly}. 66(10): 849--869
+\bibitem{eves1991}
+H.~Eves. (1991). Two Surprising Theorems on Cavalieri Congruence. \emph{College Math. J.} 22(2): 118--124.
 
-\bibitem{euler1738} Euler,~L. (1738). De progressionibus transcendentibus seu quarum termini generales algebraice dari nequeunt. \textit{Commentarii academiae scientiarum Petropolitanae}. 36--57.
-
-\bibitem{gomez14} Gomez-Aguilara,~J.~F., Razo-Hernandez,~R., Granados-Lieberman, D.~ A (2014). Physical interpretation of fractional
-calculus in observable terms: analysis of the fractional time constant and the transitory response. \textit{Revista Mexicana de Fisica.} 60: 32--38
+\bibitem{gonzalez2018} D.~L.~Gonz{\'a}lez, D.~L.~Rabiti, J.~H.~E~Cartwright. 2018. Bonaventura Cavalieri and Bologna. \emph{Math. Intelligencer}. 40(2): 21--29.
 
@@
 
-\bibitem{laurent1884} Laurent,~H. (1884). Sur le calcul des d\'{e}riv\'{e}es \`{a} indices quelconques. \textit{Nouv Annales de Mathem\'{e}matiques.} 3(3):240--252.
+\bibitem{jullien2015} V.~Jullien (Ed.). (2015). \emph{Seventeenth-Century Indivisibles Revisited}. Boston: Birkh{\"a}user.
 
-\bibitem{liouville1832} Liouville,~J.
-(1832).
-M\'{e}moire sur l\textquotesingle integration de l\textquotesingle \'{e}quation $(mx^2+nx+p)\frac{d^2y}{dx^2}+(qx+r)\frac{dy}{dx}+sy$ \`{a} l\textquotesingle aide des diff\'{e}rentielles \`{a} indices
-que\textquotesingle conques. \textit{Journal d l\textquotesingle Ecole Polytechnique.} 13(21): 163--186.
+\bibitem{malik1984}
+H.~A~Malik. (1984). A Note on Cavalieri Integration, \emph{Math. Mag.} 57(3): 154--156.
 
-\bibitem{machado03} Machado,~J.~T. (2003). A probabilistic interpretation of the fractional-order differentiation. \textit{Fract. Calc. Appl. Anal.} 6(1): 73--80.
+\bibitem{stewart1999}
+J. Stewart. (1999) \emph{Calculus, Early Transcendentals}. Brooks/Cole Publish Company.
 
-\bibitem{machado14} Machado,~J.~T., Galhano,~A.~M., Trujillo,~J.~J. (2014). On development of fractional calculus during the last fifty years. \textit{Scientometrics}. 98(1): 577-582.
+\bibitem{wildberger2002}
+W.~N.~Wildeberger. (2002). A New Proof of Cavalieri's Quadrature Formula. \emph{Amer. Math. Monthly.} 109(9): 843--845.
 
-\bibitem{machado17} Machado,~J.~T., Kiryakova,~V. (2017). The chronicles of fractional calculus. \textit{Fract. Calc. Appl. Anal.} 20(2): 307--336.
+\bibitem{william1917}
+E.~G.~William. (1917). Cavalieri's Theorem in his own Words, \emph{Amer. Math. Monthly.} 95(10): 447--451.
 
-\bibitem{munkhammar05} Munkhammar,~J. (2005). Fractional calculus and the Taylor-Riemann series. \textit{Rose-Hulman Undergrad. Math. J.}, 6(1): 6.
-
-%physical
-\bibitem{nigmatullin92} Nigmatullin,~R.~R (1992). A fractional integral and its physical interpretation. \textit{Theor. and Math. Phys.} 90(3): 242--251.
-
-\bibitem{podlubny02} Podlubny,~I. (2002). Geometric and Physical Interpretation of Fractional Integration and Fractional Differentiation, \textit{Fract. Calc. Appl. Anal.} 5(4): 367--386.
-
-\bibitem{riemann1876} Riemann,~B.~G.~F (1876). Gesammelte Werke.
-
-\bibitem{ross77} Ross,~B. (1977). The development of fractional calculus 1695--1900. \textit{Hist. Math.} 4(1): 75--89.
-
-\bibitem{ross06} Ross,~B.
-(Ed.).
-(2006).
-\textit{Fractional calculus and its applications: proceedings of the international conference held at the University of New Haven, June 1974}, Vol.
-457, Springer.
-
-\bibitem{rutman95} Rutman,~R.S. (1995). On physical interpretations of fractional integration and differentiation. \textit{Theor. and Math. Phys.} 105(3):1509--1519
-
- %Probability
-\bibitem{stanislavsky04} Stanislavsky,~A.~A. (2004).  Probability interpretation of the integral of fractional order, \textit{Theor. and Math. Phys.} 138(3): 418--431.
-
-%Geometric
-\bibitem{tarasov16} Tarasov,~V.~E. (2016). Geometric interpretation of fractional-order derivative. \textit{Fract. Calc. Appl. Anal.} 19(5): 1200--1221.
-
-%Economic
-\bibitem{tarasova17} Tarasova,~V.~V., Tarasov,~V.~E. (2017). Economic Interpretation of Fractional Derivatives. \textit{Prog. in Fract. Diff. and Appl.} 3(1):1--7.
+\bibitem{young1985}
+L. Lay-Young, S. Kangshen. (1985). The Chinese Concept of Cavalieri's Principle and Its Application, \emph{Hist. Math.}, 12: 219--228.
 

### 2019-08-20 Cav2D/article-template.tex
initial fixes of article

@@
 The single Cavalieri integral was originally defined by Ackermann et al.
-without having to resort to vector calculus \cite{ackermann12,stewart1999}.
-In this section, however, we will define the Cavalieri integral using vector calculus notation.
+without having to resort to vector calculus \cite{ackermann12}.
+In this section, however, we will define the Cavalieri integral using vector calculus notation \cite{stewart1999}.
 As the reader will undoubtedly realize, if we define the single Cavalieri integral using vector calculus then it becomes trivial to
@@
 the function $f(x)$ at a single point for all $e\in [a,b]$ then $\mathbf{c}(t)$ is a translational curve 
-with respect to $f(x)$ on $[a,b]$. 
+with respect to $f(x)$ on $[a,b]$ \cite{ackermann12}. 
 \end{definition}
@@
  \begin{equation}
- \int \limits_{\mathcal{C}} f(x)\, dx = \int_{a}^{b} f\circ h(x)~dx. 
+ \int \limits_{\mathcal{C}} f(x)\, dx = \int_{a}^{b} f\circ h(x)~dx. \nonumber
 \end{equation}
@@
  \end{equation}
- We can now solve for $t$ in Equation~\eqref{eq:t_func_1d} in terms of $x_i^1$. If we substitute the solution $t(x_i)$ so obtained into Equation~\ref{eq:pat_rel_1d} we obtain 
+ We can now solve for $t$ in Equation~\eqref{eq:t_func_1d} in terms of $x_i^1$. If we substitute the solution $t(x_i)$ so obtained into Equation~\eqref{eq:pat_rel_1d} we obtain 
 \begin{equation}
@@
 \noindent
-The area of the region $R$ depicted in Figure~\ref{fig:caval2} can, therefore, be computed as follows:
+Let us now compute the area of the region $R$ depicted in Figure~\ref{fig:caval2} using the Cavalieri integral:
 \begin{equation}
-\int \limits_{\mathcal{C}} f(x)~dx = \int_a^b f \circ h (x)\, dx = \dfrac{1}{2}\int_1^4x\, dx = 3.75.  
+\int \limits_{\mathcal{C}} f(x)~dx = \int_a^b f \circ h (x)\, dx = \dfrac{1}{2}\int_1^4x\, dx = 3.75. \nonumber 
 \end{equation}
@@
 \begin{equation}
-\int_0^2x\, dx+\int_2^44-x\, dx- \int_0^{\frac{1}{2}}x\, dx-\int_{\frac{1}{2}}^11-x\, dx = 3.75. 
+\int_0^2x\, dx+\int_2^44-x\, dx- \int_0^{\frac{1}{2}}x\, dx-\int_{\frac{1}{2}}^11-x\, dx = 3.75. \nonumber
 \end{equation}
@@
 \noindent
-In \cite{ackermann12}, the Cavalieri integral is denoted via $\int_{a(y)}^{b(y)} f(x)~dx$, where $a(y)$ denotes the functional representation of $\mathbf{c}(t) + \left <a,0 \right >$ and $b(y) = a(y)+(b-a)$
+In \cite{ackermann12}, the Cavalieri integral is denoted via $\int_{a(y)}^{b(y)} f(x)~dx$, where $a(y)$ denotes the functional representation of $\mathbf{c}(t) + \left <a,0 \right >$ and $b(y) = a(y)+(b-a)$.
 
@@
 \section{Double Cavalieri Integral}
-In this section we define the double Cavalieri integral and we show that it can be used to calculate the volume of solids that can be decomposed into an infinite 
+In this section we extend the definition of the Cavalieri integral into $\mathbb{R}^3$, i.e.
+we define the double Cavalieri integral.
+We also show that it can be used to calculate the volume of solids that can be decomposed into an infinite
 number of irregularly shaped regtangular infinitesimals.\\
@@
 \begin{equation}
-x_i^2 = h(x_i^1,y_j^1)~\textrm{and}~y_j^2 = s(x_i^1,y_j^1).
+x_i^2 = h(x_i^1,y_j^1)~\textrm{and}~y_j^2 = s(x_i^1,y_j^1).\nonumber
 \end{equation}
@@
 \end{equation}
-Let us verify that this is indeed the case. If we closely inspect Equation~\ref{eq:cav_sum_2d} and Figure~\ref{fig:prismatoid_solid} we notice the following:
+Let us verify that this is indeed the case. If we closely inspect Equation~\eqref{eq:cav_sum_2d} and Figure~\ref{fig:prismatoid_solid} we notice the following:
 \begin{itemize}
@@
 \caption{The solid $\mathcal{S}$ which is bounded by the planes $f(x,y)=-x-y+8$, $2x$, $2(x-4)$, $y$, $y-4$ and the $xy$-plane. The figure also depicts the partition 
-points $(x_i^1,y_i^1)\in\mathcal{R}$ and $(x_i^1,y_i^1)\in\mathcal{R}$ which is used in the double Cavalieri sum (see Equation~\eqref{eq:cav_2d}).}
+points $(x_i^1,y_j^1)\in\mathcal{R}$ and $(x_i^2,y_j^2)\in\mathcal{S}$ which is used in the double Cavalieri sum (see Equation~\eqref{eq:cav_sum_2d}).}
 \label{fig:prismatoid_solid}
@@
 \begin{eqnarray}
-\iint\limits_{\!\mathcal{C}} f(x,y) dA &=& \lim_{n,m\rightarrow \infty} \sum_{j=1}^n\sum_{i=1}^n f(x_i^2,y_j^2) \Delta x_i^1\Delta y_j^1\\
-&=&  \lim_{n,m\rightarrow \infty} \sum_{j=1}^n\sum_{i=1}^n f(h(x_i^1,y_j^1),s(x_i^1,y_j^1)) \Delta x_i^1\Delta y_j^1\\
-&=& \int_a^b\int_c^d f(h(x,y),s(x,y))~dx~dy.
+\iint\limits_{\!\mathcal{C}} f(x,y) dA &=& \lim_{n,m\rightarrow \infty} \sum_{j=1}^n\sum_{i=1}^n f(x_i^2,y_j^2) \Delta x_i^1\Delta y_j^1\nonumber\\
+&=&  \lim_{n,m\rightarrow \infty} \sum_{j=1}^n\sum_{i=1}^n f(h(x_i^1,y_j^1),s(x_i^1,y_j^1)) \Delta x_i^1\Delta y_j^1\nonumber\\
+&=& \int_a^b\int_c^d f(h(x,y),s(x,y))~dx~dy.\nonumber
 \end{eqnarray}
@@
 \end{equation}
-We can now solve for $t$ in terms of $x_i^1$ and $y_j^1$. If we substitute this solution into Equation~\ref{eq:vector_2} we obtain:
+We can now solve for $t$ in terms of $x_i^1$ and $y_j^1$. If we substitute this solution into Equation~\eqref{eq:vector_2} we obtain:
 \begin{equation}
@@
 \centering
-\includegraphics[width=0.5\textwidth]{prismatoid_real.jpg}
+\includegraphics[width=0.4\textwidth]{prismatoid_real.jpg}
 \caption{A physical not-to-scale model of the solid $\mathcal{S}$ depicted in Figure~\ref{fig:prismatoid_solid}.}
@@
 \begin{equation}
-t(x_i^1,y_j^1) = \frac{1}{5}x_i^1 + \frac{1}{5}y_j^1 + \frac{8}{5}. 
+t(x_i^1,y_j^1) = \frac{1}{5}x_i^1 + \frac{1}{5}y_j^1 + \frac{8}{5}. \nonumber
 \end{equation}
@@
 \begin{equation}
-x_{i}^2 = h(x_{i}^1,y_{j}^1) = \frac{4}{5} x_{i}^1 - \frac{1}{5} y_{j}^1 + \frac{8}{5}  
+x_{i}^2 = h(x_{i}^1,y_{j}^1) = \frac{4}{5} x_{i}^1 - \frac{1}{5} y_{j}^1 + \frac{8}{5}  \nonumber
 \end{equation}
@@
 \begin{equation}
-y_{j}^2 = r(x_{i}^1,y_{j}^1) = \frac{3}{5} x_{i}^1 - \frac{2}{5} y_{j}^1 + \frac{16}{5}.  
+y_{j}^2 = s(x_{i}^1,y_{j}^1) = \frac{3}{5} x_{i}^1 - \frac{2}{5} y_{j}^1 + \frac{16}{5}.  \nonumber
 \end{equation}
@@
 \label{eq:final_int_prismatoid}
-V_{\mathcal{S}}=\iint\limits_{\!\mathcal{C}} f(x,y) dA &=& \int_0^4\int_0^4 f(h(x,y),r(x,y))~dydx\\
-&=& \int_0^4 \int_0^4 -\frac{7}{5}x + \frac{3}{5} y + \frac{16}{5}~dydx\\
-&=& 25.6
+V_{\mathcal{S}}=\iint\limits_{\!\mathcal{C}} f(x,y) dA &=& \int_0^4\int_0^4 f(h(x,y),s(x,y))~dydx\nonumber\\
+&=& \int_0^4 \int_0^4 -\frac{7}{5}x + \frac{3}{5} y + \frac{16}{5}~dydx\nonumber\\
+&=& 25.6.\nonumber
 \end{eqnarray}
@@
 \end{equation}
-with $\mathcal{C}=\{\mathbf{c}(t),R\}$. We, however, first need to calculate $T$ if we wish to evaluate Equation~\ref{eq:cav_ex2} (see Figure~\ref{fig:sphere_regions}). We can determine $T$ via 
+with $\mathcal{C}=\{\mathbf{c}(t),R\}$. We, however, first need to calculate $T$ if we wish to evaluate Equation~\eqref{eq:cav_ex2} (see Figure~\ref{fig:sphere_regions}). We can determine $T$ via 
 Equation~\eqref{eq:h_2d} and Equation~\eqref{eq:s_2d}. Equation~\eqref{eq:h_2d} and Equation~\eqref{eq:s_2d} in turn requires $t(x_i^1,y_j^2)$, which can be obtained via Equation~\eqref{eq:c_z}.
@@
 \begin{equation}
-t = \frac{1}{4}[-2 x_{i}^1 - 2 y_{j}^1  -  1 + K(x_{i}^1,y_{j}^1)],
+t = \frac{1}{4}[-2 x_{i}^1 - 2 y_{j}^1  -  1 + K(x_{i}^1,y_{j}^1)],\nonumber
 \end{equation}
@@
 \begin{equation}
-K(x_{i}^1,y_{j}^1) = \sqrt{-4(x_{i}^1)^2+4x_{i}^1+8x_{i}^1y_{j}^1-4(y_{j}^1)^2+4y_{j}^1 + 33}. 
+K(x_{i}^1,y_{j}^1) = \sqrt{-4(x_{i}^1)^2+4x_{i}^1+8x_{i}^1y_{j}^1-4(y_{j}^1)^2+4y_{j}^1 + 33}.\nonumber
 \end{equation}
@@
 \begin{eqnarray}
-\iint\limits_{\!\mathcal{C}} f(x,y) dA &=& \int_0^1\int_0^1 f(h(x,y),r(x,y))~dydx\\
-&=& \int_0^1 \int_0^1 \sqrt{-(x+t(x,y))^2 - (y+t(x,y))^2 + 4} ~dydx\\
-&=& 0.864043
+\iint\limits_{\!\mathcal{C}} f(x,y) dA &=& \int_0^1\int_0^1 f(h(x,y),s(x,y))~dydx\nonumber\\
+&=& \int_0^1 \int_0^1 \sqrt{-(x+t(x,y))^2 - (y+t(x,y))^2 + 4} ~dydx\nonumber\\
+&=& 0.864043.\nonumber
 \end{eqnarray}

### 2019-08-20 Cav2D/article-template.tex
fixed very important mistake

@@
 $\mathcal{S}$ can be decomposed into an infinite number of irregularly shaped rectangular infinitesimals.
-As an example, the solid $\mathcal{S}$ depicted in Figure~\ref{fig:prismatoid_solid} is obtained if we set $f(x,y) = -x - y + 8$, $\mathbf{c}(t) = -\left<\frac{1}{2}t,t,t\right>$ and $R = \{(x,y)\in\mathbb{R}^2|0 \geq x \geq 4, 0 \geq x \geq 4\} \nonumber$.
+As an example, the solid $\mathcal{S}$ depicted in Figure~\ref{fig:prismatoid_solid} is obtained if we set $f(x,y) = -x - y + 8$, $\mathbf{c}(t) = \left<\frac{1}{2}t,t,t\right>$ and $R = \{(x,y)\in\mathbb{R}^2|0 \geq x \geq 4, 0 \geq x \geq 4\} \nonumber$.
 Moreover, the domain $R$ and the range $S$ of the transformation function $T$ which is associated with the solid $\mathcal{S}$ is depicted in Figure~\ref{fig:prismatoid_regions}.  
@@
 Also note the following: the base of $\mathcal{S}$ is the region
- $R = [0,4]\times [0,4]$ (if viewed from the front) and that the line of intersection between $2x$ and $y$ is $\mathbf{c}(t) = -\left<\frac{1}{2}t,t,t\right>$.
+ $R = [0,4]\times [0,4]$ (if viewed from the front) and that the line of intersection between $2x$ and $y$ is $\mathbf{c}(t) = \left<\frac{1}{2}t,t,t\right>$.
 The region $R$ and the line $\mathbf{c}(t)$ are
@@
 \begin{equation}
-t(x_i^1,y_j^1) = \frac{1}{5}x_i^1 + \frac{1}{5}y_j^1 + \frac{8}{5}. \nonumber
+t(x_i^1,y_j^1) = -\frac{2}{5}x_i^1 - \frac{2}{5}y_j^1 + \frac{16}{5}. \nonumber
 \end{equation}
@@
 \begin{equation}
-y_{j}^2 = s(x_{i}^1,y_{j}^1) = \frac{3}{5} x_{i}^1 - \frac{2}{5} y_{j}^1 + \frac{16}{5}.  \nonumber
+y_{j}^2 = s(x_{i}^1,y_{j}^1) = -\frac{2}{5} x_{i}^1 + \frac{3}{5} y_{j}^1 + \frac{16}{5}.  \nonumber
 \end{equation}
@@
 V_{\mathcal{S}}=\iint\limits_{\!\mathcal{C}} f(x,y) dA &=& \int_0^4\int_0^4 f(h(x,y),s(x,y))~dydx\nonumber\\
-&=& \int_0^4 \int_0^4 -\frac{7}{5}x + \frac{3}{5} y + \frac{16}{5}~dydx\nonumber\\
+&=& \int_0^4 \int_0^4 -\frac{2}{5}x - \frac{2}{5} y + \frac{16}{5}~dydx\nonumber\\
 &=& 25.6.\nonumber
@@
 \begin{equation}
-t = \frac{1}{4}[-2 x_{i}^1 - 2 y_{j}^1  -  1 + K(x_{i}^1,y_{j}^1)],\nonumber
+t(x_{i}^1,y_{j}^1) = \frac{1}{4}[-2 x_{i}^1 - 2 y_{j}^1  -  1 + K(x_{i}^1,y_{j}^1)],\nonumber
 \end{equation}

### 2019-08-20 Cav2D/article-template.tex
spelling mistakes

@@
 
-\title{Computing volume via oblique or irregularly shaped rectangular infinitesimals}
+\title{Computing volume via irregularly shaped rectangular prisms}
 %\author{Woodrow Wilson and Herbert Hoover} %%leave blank in initial submission to allow for double blind reviewing
@@
 basis and lateral edges that are non-linear curves.
-Moreover, the four lateral edges of the aformentioned solid also need to be translations of one another.
+Moreover, the four lateral edges of the aforementioned solid also need to be translations of one another.
 In this paper, we will also take the liberty to refer to an irregular rectangular prism whose base's
-lenght and widht both tend to zero as an \emph{irregular rectangular infinitesimal}. \\
+length and width both tend to zero as an \emph{irregular rectangular infinitesimal}. \\
 
@@
 process of integration.
-Furhtermore, as this paper is mainly meant to be read by undergraduate students as well as the layman who is interested in the theory of integration, we will as far as possible try to steer clear from using too many formal definitions and proofs and rather convey our ideas via worked out examples.\\
+Furthermore, as this paper is mainly meant to be read by undergraduate students as well as the layman who is interested in the theory of integration, we will as far as possible try to steer clear from using too many formal definitions and proofs and rather convey our ideas via worked out examples.\\
 
@@
 We also show that it can be used to calculate the volume of solids that can be decomposed into an infinite
-number of irregularly shaped regtangular infinitesimals.\\
+number of irregularly shaped rectangular infinitesimals.\\
 
@@
 Let us first partition $R$ into $n\times m$ subrectangles $R_{ij} = [x_{i},x_{i+1}] \times [y_{j},y_{j+1}]$ of equal width $\Delta x^1 = \Delta x_i^1 = x_{i+1}-x_i\ll (b-a)$ and length $\Delta y^1= \Delta y_j^1 = y_{j+1}-y_j\ll(d-c)$.
-Furthermore, let the transformation $T$ map the $xy$--coordinate $(x_i^1,y_j^1)\in R$ (the lower left vertice of $R_{ij}$) at which $\mathbf{c}(t) + \left <x_i^1,y_j^1,0 \right >$ intersects the 
+Furthermore, let the transformation $T$ map the $xy$--coordinate $(x_i^1,y_j^1)\in R$ (the lower left vertex of $R_{ij}$) at which $\mathbf{c}(t) + \left <x_i^1,y_j^1,0 \right >$ intersects the 
 $xy$-plane to the $xy$--coordinate at which $\mathbf{c}(t) + \left <x_i^1,y_j^1,0 \right >$ intersects $f(x,y)$. Note, the domain of $T$ is $R$. Moreover, let us denote the range 
@@
 \section{Another example}
-Let $\mathcal{S}$ be the solid which is bounded by the planes $f(x,y)=\sqrt{-x^2-y^2+4}$, $\sqrt{x}$, $\sqrt{x-1}$, $\sqrt{y}$, $\sqrt{y-1}$ and the $xy$-plane. Solid $\mathcal{S}$ is depicted 
+Let $\mathcal{S}$ be the solid which is bounded by the surfaces $f(x,y)=\sqrt{-x^2-y^2+4}$, $\sqrt{x}$, $\sqrt{x-1}$, $\sqrt{y}$, $\sqrt{y-1}$ and the $xy$-plane. Solid $\mathcal{S}$ is depicted 
 in Figure~\ref{fig:sphere_solid}. Also note the following: the base of $\mathcal{S}$ is the region 
@@
 \includegraphics[width=0.75\textwidth]{sphere_solid.pdf}
-\caption{The solid $\mathcal{S}$ which is bounded by the planes $f(x,y)=\sqrt{-x^2-y^2+4}$, $\sqrt{x}$, $\sqrt{x-1}$, $\sqrt{y}$, $\sqrt{y-1}$ and the $xy$-plane.}
+\caption{The solid $\mathcal{S}$ which is bounded by the surfaces $f(x,y)=\sqrt{-x^2-y^2+4}$, $\sqrt{x}$, $\sqrt{x-1}$, $\sqrt{y}$, $\sqrt{y-1}$ and the $xy$-plane.}
 \label{fig:sphere_solid}
@@
 We also showed that this integral can be used to compute the volume of solids that can be decomposed into an infinite number of 
-irrgularly shaped rectangular infinitesimals. We end the paper with two fully worked out examples. In the first example we compute the 
+irregularly shaped rectangular infinitesimals. We end the paper with two fully worked out examples. In the first example we compute the 
 volume of a prismatoid using the double Cavalieri integral.

### 2019-08-21 Cav2D/article-template.tex
title change
fixed small bugs

@@
 
-\title{Computing volume via irregularly shaped rectangular prisms}
+\title{Computing volume using irregularly shaped rectangular prisms}
 %\author{Woodrow Wilson and Herbert Hoover} %%leave blank in initial submission to allow for double blind reviewing
@@
 a planar figure is any cord of the planar figure. An indivisible of a solid is any planar section of a solid. Two indivisibles are equal if they are of the same length or area.
-It is Cavalieri's principle that assures us that two planar figures or solids that are composed of the same set of indivisibles have equal area or volume \cite{andersen1985,eves1991,jullien2015,malik1984,wildberger2002,william1917,young1985}.
+Cavalieri's principle assures us that two planar figures or solids that are composed of the same set of indivisibles have equal area or volume \cite{andersen1985,eves1991,jullien2015,malik1984,wildberger2002,william1917,young1985}.
 Cavalieri's principle
@@
 at which $\mathbf{c}(t) + \left <b,0 \right >$ intersects $f(x)$.  Note, the range 
-of $h$ is $[a',b']$. As the partition of $[a,b]$ can be made arbitrarily fine, $h:[a,b]\rightarrow [a',b']$ actually maps every point $x_i^1\in [a,b]$ to a point $x_i^2\in [a',b']$. \\
+of $h$ is $[a',b']$ (assuming $h$ is monotone increaing).
+As the partition of $[a,b]$ can be made arbitrarily fine, $h:[a,b]\rightarrow [a',b']$ actually maps every point $x_i^1\in [a,b]$ to a point $x_i^2\in [a',b']$.
+\\
 
@@
 \caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$.
-The parametric representation of $a(y)$ is $\mathbf{c}(t) = \frac{1}{2} \left <-t,t \right >$.
+The parametric representation of $a(y)$ is $\mathbf{c}(t) = \frac{1}{2} \left <-t,t \right >+\left<a,0\right>$.
 The figure also depicts the partition points $x_i^1$ and $x_i^2$ as used in the Cavalieri sum (see Equation~\eqref{eq:caval1}).
@@
  \end{equation}
- We can now solve for $t$ in Equation~\eqref{eq:t_func_1d} in terms of $x_i^1$. If we substitute the solution $t(x_i)$ so obtained into Equation~\eqref{eq:pat_rel_1d} we obtain 
+ We can now solve for $t$ in Equation~\eqref{eq:t_func_1d} in terms of $x_i^1$. If we substitute the solution $t(x_i^1)$ so obtained into Equation~\eqref{eq:pat_rel_1d} we obtain 
 \begin{equation}
@@
 $S_f$ via translations of $\mathbf{c}(t)$ along the $xy$ plane and then closing the resulting open faces that form due to the aforementioned connections by employing appropriate surfaces. Note that 
-$\mathcal{S}$ can be decomposed into an infinite number of irregularly shaped rectangular infinitesimals.
+$\mathcal{S}$ so formed can per definition be decomposed into an infinite number of irregularly shaped rectangular infinitesimals.
 As an example, the solid $\mathcal{S}$ depicted in Figure~\ref{fig:prismatoid_solid} is obtained if we set $f(x,y) = -x - y + 8$, $\mathbf{c}(t) = \left<\frac{1}{2}t,t,t\right>$ and $R = \{(x,y)\in\mathbb{R}^2|0 \geq x \geq 4, 0 \geq x \geq 4\} \nonumber$.
@@
 with $\mathcal{C}=\{\mathbf{c}(t),R\}$. We, however, first need to calculate $T$ if we wish to evaluate Equation~\eqref{eq:cav_ex2} (see Figure~\ref{fig:sphere_regions}). We can determine $T$ via 
-Equation~\eqref{eq:h_2d} and Equation~\eqref{eq:s_2d}. Equation~\eqref{eq:h_2d} and Equation~\eqref{eq:s_2d} in turn requires $t(x_i^1,y_j^2)$, which can be obtained via Equation~\eqref{eq:c_z}.
+Equation~\eqref{eq:h_2d} and Equation~\eqref{eq:s_2d}. Equation~\eqref{eq:h_2d} and Equation~\eqref{eq:s_2d} in turn requires $t(x_i^1,y_j^1)$, which can be obtained via Equation~\eqref{eq:c_z}.
 If we substite $f(x,y)$ and $\mathbf{c}(t)$ into Equation~\eqref{eq:c_z} and then solve for $t$ we obtain:

### 2019-09-20 fractional/func_plotter.py
newest code

@@ -420,15 +420,90 @@ def plot_frac_int2():
     ax.yaxis.set_major_locator(MaxNLocator(integer=True))    
     plt.show()
 
+def g(tau,alpha=0.8,t = 0):
+    g = (1/math.gamma(alpha+1))*(t**alpha+(tau-t)**alpha)
+    return g
+
+def test_a_y(y,alpha=0.8,t = 0,add_constant=True):
+    if add_constant:
+       a = y+10 - (1.0/math.gamma(alpha+1))*(t**(alpha)+(y+10-t)**alpha) + (t**alpha)/(math.gamma(alpha+1))
+    else:
+       a = y - (1.0/math.gamma(alpha+1))*(t**(alpha)+(y-t)**alpha)
+    return a
+
+def test_g(tau,alpha=0.8,t=5):
+    g = (1/math.gamma(1+alpha))*(t**(alpha)+(tau-t)**alpha)
+    return g
+
+def test_a(y,alpha=0.8,t=5):
+    y = y - (1/math.gamma(1+alpha))*(t**alpha+(y-t)**alpha) + (1/math.gamma(alpha+1))*t**(alpha)
+    return y
+
+
 
 if __name__ == "__main__":
-   plot_frac_int1()
-   plot_frac_int2()
+   #TEST NEW IDEA
+
+   y = np.linspace(5,10,100)
+   a = test_a(y)
+
+   a0 = test_g(5)
+   print(a0)
+
+   b0 = test_g(7)
+   print(b0)
+
+   b1 = test_g(6)
+   print(b0)
+
+   C = b0-a0
+   C2 = b1-a0
+
+   plt.plot(a,y)
+   plt.plot(a+C,y)
+   plt.plot(a+C2,y)
+   x = np.linspace(4,10,100)
+   plt.plot(x,x)
+
+   plt.axvline(x=a0)
+   plt.axvline(x=b0)
+
+   plt.show()   
+
+
+   '''
+   y = np.linspace(-20,5,100)
+
+   a = test_a_y(y)
+
+   a_0 = test_a_y(0)
+   print(a_0)
+
+   g_5 =g(0)
+   print(g_5)
+
+   C = a_0-g_5
+   print(C)
+
+   b = g(10)+C
+   print(b)
+
+   x = np.linspace(-10,10,100)
+   f = x-10
+   plt.plot(a,y)
+   plt.plot(a+b-a_0,y)
+   
+   plt.plot(x,f)
+   plt.show()
+   '''
+
[…]

### 2019-09-20 fractional/func_plotter.py
newest version

@@ -436,40 +436,69 @@ def test_g(tau,alpha=0.8,t=5):
     return g
 
 def test_a(y,alpha=0.8,t=5):
-    y = y - (1/math.gamma(1+alpha))*(t**alpha+(y-t)**alpha) + (1/math.gamma(alpha+1))*t**(alpha)
+    y = y+10 - (1/math.gamma(1+alpha))*(t**alpha+(y+10-t)**alpha) + (1/math.gamma(alpha+1))*t**(alpha)
     return y
+
+def plot_b_functions(t_vector=np.array([0,2,4,6,8]),alpha_vector=np.array([0.2,0.4,0.6,0.8]),y_points=50000):
+    #plt.grid('on')
+    fig,ax = plt.subplots(1,len(alpha_vector),sharex='all', sharey='all')
+    #plt.grid('on')
+
+    v = np.linspace(0,1.5,len(t_vector))
+
+    for i in range(len(alpha_vector)):
+        x = np.linspace(0,t_vector[-1]+2,y_points)
+        
+        ax[i].plot(x,x-10,"k") 
+        if i == 0:
+           ax[i].set_xlabel(r"$\tau$")
+           ax[i].set_ylabel(r"$y$")
+        ax[i].set_title(r"$\alpha = $"+str(alpha_vector[i]))
+        for k in range(len(t_vector)):
+            y = np.linspace(0,t_vector[k]-10,y_points)
+            #g0 = test_g(t_vector[k],alpha_vector[i],t_vector[k])
+            a = test_a(y,alpha_vector[i],t_vector[k])
+            #b_p = h_func(b,alpha_vector[i],t_vector[-1])
+            #y2 = np.linspace(0,f(b_p),y_points)
+            col = [v[k]/2,v[k]/2,v[k]/2]    
+        
+            ax[i].plot(a,y,color=col) 
+            #if i == len(alpha_vector)-1:
+            #   ax[i].plot(a_func(y2,alpha_vector[i],t_vector[-1],f_inv)+b,y2,color=col,ls="--") 
+            #ax[i].set_xlim([0,t_vector[-1]+0.6])
+            ax[i].set_ylim([t_vector[0]-10,0]) 
+              
+    plt.show()  
 
 
 
 if __name__ == "__main__":
    #TEST NEW IDEA
 
-   y = np.linspace(5,10,100)
[…]

### 2019-09-20 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
started new paper

%%% Template for AUTHOR's DRAFT paper in FCAA, WITHOUT Journal's head  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% by V. Kiryakova, updated Nov. 1, 2014
%%% uses "fcaa.cls", or "fcaa-var.cls" as modifications of "amsart.cls" for the FCAA format,
%%% and auxiliary file "fcaa_style.tex" fixing page margins, fontsize, defs for theorems, proofs etc.
%%% Put the files "fcaa.cls", "fcaa-var.cls" and "fcaa_style.tex" in same directory you prepare the paper

  %\documentclass[twoside,reqno,11pt]{fcaa}  %%% or in case of problems, use as below: %
   \documentclass[twoside,reqno,11pt]{fcaa-var} %

 \input fcaa_style

%%%%%%%%%%%%%%%%%%%%
 \usepackage{hyperref} % Editor will use to create hyperlinks %
 %%% but if the author has problems with the above style file,
 %%% then comment the line \usepackage{hyperref} or replace by this below:
 % \usepackage{upref}
%%%%%%%%%%%%%%%%%%%%

% to have 2-digits numbering for equation, use:
 \def\theequation{\arabic{section}.\arabic{equation}}

%%%%%%  First page footnote for Copyright and Springer logo
 \def\themycopyrightfootnote{\vspace*{3pt}
 \copyright \, Year\,  Diogenes  Co., Sofia
   \par  \noindent pp. xxx--xxx, DOI: ......................
   \hfill  \vspace*{-36pt}
   % \mbox{\includegraphics[scale=0.65]{DeGryuter.eps}}
  }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \setcounter{page}{1}
  \thispagestyle{empty}

 %%%%%%%%%%%%%%% begin make title %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%% TITLE: texts in [.] is abbreviated (1st line) title for running heads
 %%% Author(s): put in brackets [.] the short author's name

 \title[VISUALIZATION OF THE FRACTIONAL INTEGRAL \dots]{VISUALIZATION OF THE RIEMANN-LIOUVILLE FRACTIONAL INTEGRAL \\ [3pt] IN ``FCAA'' JOURNAL}
 \author[\normalsize V. Kiryakova, S. Author]{\normalsize Virginia Kiryakova $^1$, Second Author $^2$}

 %%% obligatory give the full and abbreviated authors' names %%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
                    % THE BEGINNING %
 \begin{document}

 \vbox to 2.5cm { \vfill }

%%% to make empty space of approx. 2.5cm %%%%%%
%%% will be replaced by Editor with the journal's and publoishers logos %%%%%%%%

 \bigskip \medskip

%%%% Abstract %%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{abstract}

Text of the abstract. Text of the abstract. Text of the abstract.
Text of the abstract. Text of the abstract. Text of the abstract.
Text of the abstract. It should give a comprehensive idea about the
paper's subject and the author's results. The Abstract (and the first 2 pages of the paper) will be
available free at DeGryuter's website for the journal.

 \medskip

{\it MSC 2010\/}: Primary 26A33;
                  Secondary 33E12, 34A08, 34K37, 35R11, 60G22, ...

 \smallskip

{\it Key Words and Phrases}: fractional calculus, Mittag-Leffler
type functions, fractional ordinary and partial differential
equations, ...

 \end{abstract}

 \maketitle

%%%%%%% end make title %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \vspace*{-16pt}

%%%%%%%% begin papers' body %%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%% Section 1 %%%%%%%%%%%%%
%\section{Introduction}\label{Sec:1}

\section{First section of the paper}\label{sec:1}

\setcounter{section}{1}
\setcounter{equation}{0}\setcounter{theorem}{0}

Text ... (for details, see \cite{GasRah}, \cite{Rosbl}, \cite{Kir},
\cite{Moak}) ...

%%%% example of definition %%%%
 \begin{definition}\label{Def3}
Text of Definition~\ref{Def3}.
 \end{definition}

   \vspace*{-12pt} %%% example of subsection:
 \subsection{Preliminary results}\label{subsec:1.1}

%%%% example of theorem %%%%%%%%%%
 \begin{theorem}\label{Th1}
Text of Theorem~\ref{Th1} ....
 \end{theorem}

 \proof %%%%%%%%%%%%%
 Give here the proof of Theorem~\ref{Th1}. Example for
equation:
\begin{equation}\label{eq1}
ax^2+bx +c =0.
\end{equation}
 As seen by equation \eqref{eq1}, it is ...
 The proof follows from Ref. \cite{Moak}.
 \proofend %%%%%%%%%%

%%%% example of corollary %%%%
 \begin{corollary}\label{Cor2}
Text of Corollary~\ref{Cor2} ....
 \end{corollary}

 \proof
 Here comes the proof of Corollary~\ref{Cor2}.
 \proofend

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Second section of the paper}\label{sec:2}

\setcounter{section}{2}
\setcounter{equation}{0}\setcounter{theorem}{0}

 Text ... As seen in Section~\ref{sec:1}, the equation
(\ref{eq1}), $ a\neq 0$, has the solutions
 \begin{equation}\label{eq2}
 x_{1,2}= {\frac {-b \pm \sqrt{b^2-4ac}}{2a}}\,.
 \end{equation}

 %%% example of example %%%%%
 \begin{example}\label{Ex1}
 Let us take in (\ref{eq2}) ... Then, by Theorem~\ref{Th1}, ...
 \end{example}

 \begin{example}\label{Ex2}
 Under same conditions as in Example~\ref{Ex1}, we consider ...
 \end{example}

The figures should be input in the LaTeX file as eps-files, as below:

%%%%%%%%% example for figure %%%%%%%%%%%%%%%%%%%
  \begin{center}
  \includegraphics[scale=0.4]{figure.eps}
 % \hspace*{2cm}
 % \includegraphics[scale=0.7]{figure2.eps}

 \bigskip

  Fig. 2.1: Control loop
  \end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

 Often figures include texts or Latin, Greek etc. letters.
 We kindly ask the authors to take care that no texts fonts need to be embedded, by saving first the text as curves.
 Just in case, along with the obligatory eps-files, please send us also some alternative figures' files in  pdf-, jpg-, etc. format.

\section{Cavalieri Integral}
\label{sec:cav_integral}

 \begin{definition}\label{Def3}
Text of Definition~\ref{Def3}.
 \end{definition}

\begin{definition}\label{def:trans}
A continuous real--valued function $a(y)$ is called a translational function with respect to a continuous real--valued function $f(x)$ on the interval $[a,b]$ if 
$\{x\in\mathbb{R}|a\circ f(x) + z = x\}$ is a singleton, for every $z\in[0,b-a]$ and $a(0) = a$.
\end{definition}

\begin{definition}\label{def:h}
The mapping $h : [a, b] \rightarrow [a',b']$, which maps $x_i^1 \in [a, b]$ to $x_i^2 \in [a',b']$, is defined as
$h(x_i^1) =$ $\{x_i^2 \in [a' ,b'] | a\circ f(x_i^2) + [x_i^1 - a] = x_i^2$ , $a = a(0)\}$
\end{definition}

\begin{theorem}
The mapping $h(x)$ is a strictly monotone continious function. The function $h(x)$ is, therefore, invertable.
\end{theorem}

\noindent
The function $h(x)$ is known as the transformation function.

\begin{definition}\label{def:g}
The mapping $g:[a', b'] \rightarrow [a, b]$, which maps $x_i^2 \in [a' , b']$ to $x_i^1\in [a, b]$,
is defined as $g(x_i^2) = x_i^2 - a \circ f (x_i^2) + a$.
\end{definition}

\noindent
Note that $g = h^{-1}$ per definition. Moreover $g$ is guaranteed to exist, since $h$ is bijective.

\begin{definition}\label{def:cav_integral}
Define a partition $\mathcal{P}_1$ of $[a,b]$ to be a set of points $x_0^1, x_1^1,\cdots,x_n^1$, 
where $a = x_0^1 \leq x_1^1 \leq \cdots \leq x_n^1 = b$. For each partition 
$\mathcal{P}_1$ of $[a,b]$ write $\Delta x_k^1 = x_k^1-x_{k-1}^1$. 
%Since both boundaries of any integration strip are necessarily
%translations of the translational function $a(y)$, we can apply the transformation
%function $h$ to the partition $\mathcal{P}_1$. 
If the transformation function $h$ is strictly increasing,
the application of $h$ to the partition $\mathcal{P}_1$ induces a new partition $\mathcal{P}_2 = \{x_0^2, x_1^2,\cdots, x_n^2\}$.
Otherwise, if $h$ is strictly decreasing, the application of $h$ induces a reversed partition $\mathcal{P}_2 = \{x_n^2, \cdots, x_1^2,x_0^2\}$. It
can be assumed that $h$ is strictly increasing, without any loss of generality.  Let 
$M_k = \sup \{f (x), h(x_{i-1}^1) = x_{i-1}^2 \leq x \leq x_i^2 = h(x_i^1)\}$, $m_k = \inf \{f (x), h(x_{i-1}^1) = x_{i-1}^2 \leq x \leq x_i^2 = h(x_i^1)\}$, and set 
\begin{equation}
\label{eq:c_up}
\mathcal{C}_U(\mathcal{P}_1,f,h) = \sum_{k=1}^n M_k \Delta x_k, 
\end{equation}
and
\begin{equation}
\label{eq:c_low}
\mathcal{C}_L(\mathcal{P}_1,f,h) = \sum_{k=1}^n m_k \Delta x_k. 
\end{equation}
The sums in Eq.~\eqref{eq:c_up} and Eq.~\eqref{eq:c_low} are respectively called the the upper and lower Cavalieri sums.
If there is a unique number $I$ that satisfies the inequality $\mathcal{C}_L(\mathcal{P}_1,f,h)\leq I \leq \mathcal{C}_U(\mathcal{P}_1,f,h)$ for all 
partitions $\mathcal{P}_1$ of $[a,b]$, then $I$ is called the Cavalieri integral of $f$ from $a(y)$ to $b(y)$ and is denoted by
\begin{equation}
\int_{a(y)}^{b(y)} f(x) dx.
\end{equation}
\end{definition}

\begin{theorem}
The following Cavalieri, Riemann, and Riemann--Stieltjes integrals are equivalent
\begin{equation}
\int_{a(y)}^{b(y)} f(x) dx = \int_a^b f\circ h(x) dx = \int_{a'}^{b'} f(x)dg(x). 
\end{equation}
\end{theorem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}

 The author thanks his institution for the support, under Grant No ...

%%%%%%%%%% References %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% arranged in ALPHABETIC ORDER of Authors' Families
%%%% for articles, insert also DOI numbers if available

 \begin{thebibliography}{99}
 \normalsize

%%%% example for a book %%%%%%%%%%%%%

\bibitem{GasRah}
 G. Gasper, M. Rahman,
 \emph{Basic Hypergeometric Series}.
 Cambridge University Press, Cambridge (1990).

%%%% example for article in FCAA journal %%%%%%%%%%%%%%%%%

\bibitem{Kir}
 V. Kiryakova,
 A brief story about the operators of generalized
fractional calculus.
 \emph{Fract. Calc. Appl. Anal.} \textbf{11}, No 2 (2008), 201--218; DOI: ..........

%%%% example for journal's article %%%%%%%%%%%%%%%%%

\bibitem{Moak}
 D.S. Moak,
 The $q$-analogue of the Laguerre polynomials.
\emph{J. Math. Anal. Appl.} \textbf{81}, No 1 (1981), 20--47. % ; doi: ........

%%%% example for a paper in Proceedings %%%%%%%%%%%%%

\bibitem{Rosbl}
 M. Rosenblum,
 Generalized Hermite polynomials and the Bose-like oscillator
 calculus.
 In: \emph{Operator Theory: Advances and Applications},
 Birkh\"auser, Basel (1994), 369--396.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{thebibliography} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%% put authors' addresses here, in \it %%%%%%%%

 \bigskip \smallskip

 \it

 \noindent
   %(First) Author's full postal address
$^1$ Institute of Mathematics and Informatics \\
Bulgarian Academy of Sciences \\
"Acad. G. Bontchev" Str., Block 8 \\
Sofia -- 1113, BULGARIA  \\[4pt]
  e-mail: virginia@diogenes.bg
\hfill Received: November 1, 2014 \\[12pt]
  % Second Author's address
$^2$ Dept. of Physics, University of Bologna\\
Via Irnerio 46, I -- 40126 Bologna, ITALY \\[4pt]
  e-mail: .....

\end{document} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-09-20 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
started fleshing out Cavalieri section

@@
 
- \begin{definition}\label{Def3}
-Text of Definition~\ref{Def3}.
- \end{definition}
+Ackerman et al. used the notion of non-rectangular integration strips to define the so called Cavalieri integral. The area of a non-rectangular 
+integration strip is calculated using Cavalieri's principle. The formal definition of the Cavalieri integral is given in Definition~\ref{def:cav_integral}.
+It is, however, our experience that Definition~\ref{def:cav_integral} is hard to assimilate if it is encounterd by a reader for the first time. We, therefore, encourage 
+readers who are not familiar with the Cavalieri integral to rather first read Section~\ref{??} instead. The reader should only refer back to the definitions 
+presented in this sections when things in Section~\ref{??} become unclear.
+Moreover, the definitions presented below were taken from [?].
+Furthermore, none of the theorems in this sections are proved, the proofs are contained in [].
 
@@
 \end{definition}
+
+Let $a(y)$ be a translational function with respect to a real--valued function $f(x)$ on the interval $[a,b]$.
+Moreover, $b(y) = a(y) + (b-a)$.
+Furthermore, the functions $a(y)$ and $b(y)$ intersect $f(x)$ at $a'$ and $b'$ respectively.
+These assertions are assumed to be true throughout the paper and will not be repeated again.
 
@@
 
-\noindent
-Note that $g = h^{-1}$ per definition. Moreover $g$ is guaranteed to exist, since $h$ is bijective.
+\begin{theorem}
+The mapping $g(x)$ is a strictly monotone continious function. The function $g(x)$ is, therefore, invertable.
+\end{theorem}
+
+\begin{theorem}
+The function $g(x)$ is equal to $h^{-1}(x)$.
+\end{theorem}
+
+The function $g(x)$ is known as the inverse transformation function.
 
@@
 \label{eq:c_up}
-\mathcal{C}_U(\mathcal{P}_1,f,h) = \sum_{k=1}^n M_k \Delta x_k, 
+\mathcal{C}_U(\mathcal{P}_1,f,h) = \sum_{k=1}^n M_k \Delta x_k^1, 
 \end{equation}
@@
 \label{eq:c_low}
-\mathcal{C}_L(\mathcal{P}_1,f,h) = \sum_{k=1}^n m_k \Delta x_k. 
+\mathcal{C}_L(\mathcal{P}_1,f,h) = \sum_{k=1}^n m_k \Delta x_k^1. 
 \end{equation}

### 2019-09-20 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
added superscript comment

@@
 Moreover, the definitions presented below were taken from [?].
-Furthermore, none of the theorems in this sections are proved, the proofs are contained in [].
+Furthermore, none of the theorems in this section are proved, the proofs can be found in [].
 
@@
 \end{definition}
+
+Note that the superscripts of the $x$-coordinates in the above definitions indicate to which partition, either $\mathcal{P}_1$ or $\mathcal{P}_2$, the $x$-coordinate in question belongs.
 

### 2019-09-20 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
added worked example - not finished

@@
 
- \title[VISUALIZATION OF THE FRACTIONAL INTEGRAL \dots]{VISUALIZATION OF THE RIEMANN-LIOUVILLE FRACTIONAL INTEGRAL \\ [3pt] IN ``FCAA'' JOURNAL}
+ \title[VISUALIZATION OF FRACTIONAL INTEGRALS]{VISUALIZATION OF THE RIEMANN-LIOUVILLE FRACTIONAL INTEGRAL \\ [3pt] IN ``FCAA'' JOURNAL}
  \author[\normalsize V. Kiryakova, S. Author]{\normalsize Virginia Kiryakova $^1$, Second Author $^2$}
@@
 Ackerman et al. used the notion of non-rectangular integration strips to define the so called Cavalieri integral. The area of a non-rectangular 
-integration strip is calculated using Cavalieri's principle. The formal definition of the Cavalieri integral is given in Definition~\ref{def:cav_integral}.
+integration strip is calculated using Cavalieri's principle. Cavalieri's principle is stated below without proof:
+\begin{theorem}
+Suppose two regions in a plane are included between two parallel lines in that plane. If every line parallel to these
+two lines intersects both regions in line segments of equal length, then the two regions have equal areas. NEED CITATION
+\end{theorem}
+The definition of the Cavalieri integral is presented in Definition~\ref{def:cav_integral}.
 It is, however, our experience that Definition~\ref{def:cav_integral} is hard to assimilate if it is encounterd by a reader for the first time. We, therefore, encourage 
-readers who are not familiar with the Cavalieri integral to rather first read Section~\ref{??} instead. The reader should only refer back to the definitions 
-presented in this sections when things in Section~\ref{??} become unclear.
+readers who are not familiar with the Cavalieri integral to rather first read Section~\ref{??} instead.
+The reader who is not familiar with the Cavalieri integral should only refer back to the definitions
+presented in this section when things in Section~\ref{??} become unclear.
 Moreover, the definitions presented below were taken from [?].
@@
 \begin{theorem}
+\label{t:inv}
 The function $g(x)$ is equal to $h^{-1}(x)$.
@@
 \begin{theorem}
+\label{t:conv}
 The following Cavalieri, Riemann, and Riemann--Stieltjes integrals are equivalent
@@
 \end{theorem}
+
+\section{Cavalieri Integral: Clarifying Example}
+\label{sec:cav_integral_example}
+The example which we present below was taken from \cite{?}.
+Let the region $R$ be bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$ and $b(y)=4-y$.
+This region is depicted in Fig.~\ref{fig:caval2}.\\
+%\begin{figure}[htb]
+%\centering
+%\includegraphics[width=0.3\textwidth]{fig12}
+%\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$. Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
+%\label{fig:ex1}
+%\end{figure}
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.75\textwidth]{fig13.pdf}
+\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$.
+In the case of $R$: $a=1$, $b=4$, $a'=\frac{1}{2}$ and $b'=2$.
+The figure also depicts the partition points $x_i^2$ as used in the Cavalieri sum (see Equation~\eqref{eq:cav_sum}).
+Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
+\label{fig:caval2}
+\end{figure}
+
+%\noindent
+%The area of $R$ can be determined as follows if we employ the classical notion of integration:
+%\begin{equation}
+%\int_0^2x\, dx+\int_2^44-x\, dx- \int_0^{\frac{1}{2}}x\, dx-\int_{\frac{1}{2}}^11-x\, dx = 3.75. 
+%\end{equation}
+
+The area of $R$ can be approximated by summing together the area of rectangular integrations strips that inscribe $R$. There, however, exist a more 
+straightforward way in which we can approximate the area of $R$: we can sum together the area of non-rectangular integration strips inscribing $R$. This alternative approach 
+will only succeed it the sides of the aforementioned integration strips are all tranlsations of the function $a(y)$.
+
+Let us express this idea more formally. Let $(x_i^1)_{i=0}^{n}$ denote a partition on the $x$-axis, such that $a = x_0^1 < x_1^1 < \cdots < x_n^1 = b$, and $\Delta x_i^1 = x_{i+1}^1 - x_i^1$.
+We are now able to construct the following lower Cavalieri sum (Equation~\ref{eq:c_low}):
+\begin{equation}
+\label{eq:cav_sum}
+\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1.
+\end{equation}
+The partition points $(x_i^2)_{i=0}^{n}$ are depicted in Fig.~\ref{fig:caval2}.
+Cavalieri's principle tells us that the area of integration strip $i$ is equal to $f(x_i^2)\Delta x_i^1$.
+Equation.~\eqref{eq:cav_sum}, therefore, approximates the area of $R$.
+In the limit Eq.~\eqref{eq:cav_sum} approaches
+the Cavalieri integral (Definition~\ref{def:cav_integral}):
+\begin{equation}
+\label{eq:caval1}
+\int_{a(y)}^{b(y)}f(x)\, dx = \lim_{n\to \infty}\sum_{i=0}^{n-1} f(x_i^2)\Delta x_i^1.
+\end{equation}
+It is, however, quite hard to evaluate the above integral directly. Fortunately, it is easy to convert a Cavalieri integral into an equivalent Riemann or Riemann-Stieltjes 
+integral by using the functions $h$ and $g$ (Theorem~\ref{t:conv}). Expressed mathematically:
+\begin{equation}
+\label{eq:main_cav}
+\int_{a(y)}^{b(y)}f(x)\,dx =\int_a^b f \circ h (x)\, dx = \int_{a'}^{b'} f(x) dg(x).
+\end{equation}
+We can calculate $g$ as follows (Definition~\ref{def:g}):
+\begin{equation}
+g(x) = x - a\circ f(x) + a.
+\end{equation}
+Moreover, $h=g^{-1}$ (Theorem~\ref{t:inv}). We can now evaluate the Cavalieri integral by using its equivalent Riemann or Rieman-Stieltjes integral.
+If we use its Riemann equivalent we obtain:
+\begin{equation}
+\int_{a(y)}^{b(y)}f(x)\, dx = \int_a^b f \circ h (x)\, dx = \dfrac{1}{2}\int_1^4x\, dx = 3.75.  
+\end{equation}
+If we use its Riemann-Stieltjes equivalent we obtain:
+\begin{equation}
+\int_{a(y)}^{b(y)}f(x)\, dx = \int_{a'}^{b'} f \, dg(x) = \int_{\frac{1}{2}}^2x\, d2x = 3.75.  
+\end{equation}
+
+\noindent
+Conversely, if $g$ is known (and not $a(y)$) and $g(a') = a$ then we can calculate $a(y)$ using the following \cite{grobler19}:
+\begin{equation}
+\label{eq:a_y}
+a(y) = f^{-1}(y) - g\circ f^{-1}(y) + g(a'). 
+\end{equation}
+Eq.~\eqref{eq:a_y} allows us to transform a Riemann-Stieltjes integral into an equivalent Cavalieri integral. 
+Furthermore, this transformation enables us to assign a geometric interpretation to a Riemann-Stieltjes integral. The interpretation being:
+it represents the area obtained by summing together the area of an infinite number of non-rectangular infinitesimals; all of them being translations of $a(y)$. Note,
+$b(y) = a(y) + (b-a)$.
 

### 2019-09-23 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
added inverse procedure theorem

@@
 \end{theorem}
+\begin{theorem}
+Let $\widetilde{g}(x)$ and $f(x)$ be known (continious) invertable real-valued functions.
+Moreover, let $a'\in \mathbb{R}$ and $b'\in \mathbb{R}$.
+If $f^{-1}(0) - \widetilde{g}\circ f^{-1}(0) + g(a')$ exists then there exists a unique
+$C\in\mathbb{R}$ such that 
+\begin{equation}
+\int_{a'}^{b'} f(x)~dg(x) = \int_{a(y)}^{b(y)} f(x)~dx, 
+\end{equation}
+where $g(x) = \widetilde{g}(x) + C$ and $a(y) = f^{-1}(y)-\widetilde{g}\circ f^{-1}(y) + \widetilde{g}(a')$.
+\end{theorem}
 
@@
 
-The area of $R$ can be approximated by summing together the area of rectangular integrations strips that inscribe $R$. There, however, exist a more 
-straightforward way in which we can approximate the area of $R$: we can sum together the area of non-rectangular integration strips inscribing $R$. This alternative approach 
+It seems much more straightforward to approximate the area of $R$ via non-overlapping non-rectangular integration strips that toghether inscribe $R$ than having to 
+rectangular integration strips. This alternative approach 
 will only succeed it the sides of the aforementioned integration strips are all tranlsations of the function $a(y)$.

### 2019-09-25 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
added more clarification on Cavalieri sections

--- 2019-09-20 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
@@
 
-\begin{theorem}
-The mapping $h(x)$ is a strictly monotone continious function. The function $h(x)$ is, therefore, invertable.
-\end{theorem}
-
-\noindent
-The function $h(x)$ is known as the transformation function.
-
 \begin{definition}\label{def:g}
@@
 \begin{theorem}
-The mapping $g(x)$ is a strictly monotone continious function. The function $g(x)$ is, therefore, invertable.
+The mapping $h(x)$ is a strictly monotone continuous function. The function $h(x)$ is, therefore, invertable.
 \end{theorem}
@@
 
-The function $g(x)$ is known as the inverse transformation function.
+\noindent
+The functions $h(x)$ and $g(x)$ are known as the transformation function and the inverse transformation function, respectively.
 
@@
 \label{t:conv}
-The following Cavalieri, Riemann, and Riemann--Stieltjes integrals are equivalent
+The following Cavalieri, Riemann, and Riemann--Stieltjes integrals are equivalent:
 \begin{equation}
-\int_{a(y)}^{b(y)} f(x) dx = \int_a^b f\circ h(x) dx = \int_{a'}^{b'} f(x)dg(x). 
+\int_{a(y)}^{b(y)} f(x)\,dx = \int_a^b f\circ h(x)\,dx = \int_{a'}^{b'} f(x)\,dg(x),
 \end{equation}
+with $g(x) = x-a\circ f(x) + a$ and $h(x) = g^{-1}(x)$.
 \end{theorem}
+
+Theorem~\ref{t:conv} tells us how to convert a Cavalieri integral into an equivalent Riemann or Riemann-Stieltjes integral. It, however, tells us nothing about the reverse 
+procedure, if we are given a Riemann-Stieltjes integral how do we convert it into a Cavalieri integral. The theorem below stipulates the conditions that are required to perform the latter conversion.
+
+\begin{theorem}
+\label{t:reverse}
+Let $\widetilde{g}(x)$ and $f(x)$ be known (continuous) invertable real-valued functions.
+Moreover, let $a'\in \mathbb{R}$ and $b'\in \mathbb{R}$.
+If $f^{-1}(0) - \widetilde{g}\circ f^{-1}(0) + \widetilde{g}(a')$ exists then there exists a unique
+$C\in\mathbb{R}$ such that 
+\begin{equation}
+\int_{a'}^{b'} f(x)\,dg(x)~\textrm{and}~\int_{a(y)}^{b(y)} f(x)\,dx, 
+\end{equation}
+where $g(x) = \widetilde{g}(x) + C$ and $a(y) = f^{-1}(y)-\widetilde{g}\circ f^{-1}(y) + \widetilde{g}(a')$, have the exact same 
+geometric meaning.
+\end{theorem}
+
+To clarify the above theorem, consider the Riemann-Stieltjes integral $\int_{a'}^{b'} f(x)\,d\,\widetilde{g}(x)$. We can now compute the following:
+\begin{itemize}
+ \item $a(y) = f^{-1}(y)-\widetilde{g}\circ f^{-1}(y) + \widetilde{g}(a')$.
+ \item $a = a(0)$.
+ \item $C = a - \widetilde{g}(a')$.
+ \item $g(x) = \widetilde{g}(x) + C$.
+ \item $b = g(b')$ and $b(y) = a(y) + (b-a)$.
+\end{itemize}
+The integrals $\int_{a'}^{b'} f(x)\,d\,\widetilde{g}(x)$ and $\int_{a'}^{b'} f(x)\,dg(x)$ are equivalent (we obtain the same result when they are evaluated).
+Moreover, the integrals $\int_{a'}^{b'} f(x)\,d\,g(x)$ and $\int_{a(y)}^{b(y)}f(x)~dx$ have the exact same geometric meaning.
+Note, however, that
+$\int_{a'}^{b'} f(x)\,d\,\widetilde{g}(x)$ and $\int_{a(y)}^{b(y)}f(x)~dx$ do not have the exact same geometric meaning.
+
+%To clarify the above theorem, the Riemann-Stieltjes integral $\int_{a'}^{b'} f(x)\,d\,\widetilde{g}(x)$ can be converted into an equivalent Cavalieri integral $\int_{a(y)}^{b(y)}f(x)~dx$ (we obtain the same value when we evaluate the aforementioned integrals).
+The Cavalieri
+%integral so obtained does however not have the same geometric meaning as $\int_{a'}^{b'} f(x)\,d\,\widetilde{g}(x)$.
+Fortunately, the Riemann-Stieltjes integral $\int_{a'}^{b'} f(x) \,d\,\widetilde{g}(x)$
+%can be converted into an equivalent Riemann-Stieltjes integral $\int_{a'}^{b'} f(x)\,dg(x)$.
+Note that $\int_{a'}^{b'} f(x)\,d\,\widetilde{g}(x) = \int_{a'}^{b'} f(x)\,dg(x)$, by Theorem~\ref{??}.
+In contrast to the original Riemann-Stieltjes integral, the Riemann-Stieltjes integral so obtained has the exact same geometric meaning as $\int_{a(y)}^{b(y)} f(x)\,dx$.
 
@@
 
-The area of $R$ can be approximated by summing together the area of rectangular integrations strips that inscribe $R$. There, however, exist a more 
-straightforward way in which we can approximate the area of $R$: we can sum together the area of non-rectangular integration strips inscribing $R$. This alternative approach 
+We can approximate the area of $R$ by using rectangular integration strips.
+It, however, seems much more straightforward to approximate the area of $R$ via non-overlapping non-rectangular integration strips that toghether inscribe $R$.
+This alternative approach
 will only succeed it the sides of the aforementioned integration strips are all tranlsations of the function $a(y)$.
@@
 \label{eq:main_cav}
-\int_{a(y)}^{b(y)}f(x)\,dx =\int_a^b f \circ h (x)\, dx = \int_{a'}^{b'} f(x) dg(x).
+\int_{a(y)}^{b(y)}f(x)\,dx =\int_a^b f \circ h (x)\, dx = \int_{a'}^{b'} f(x) dg(x),
 \end{equation}
@@
 \end{equation}
-Moreover, $h=g^{-1}$ (Theorem~\ref{t:inv}). We can now evaluate the Cavalieri integral by using its equivalent Riemann or Rieman-Stieltjes integral.
-If we use its Riemann equivalent we obtain:
+Moreover, $h=g^{-1}$ (Theorem~\ref{t:inv}). We can now evaluate the Cavalieri using one of two ways:
 \begin{equation}
-\int_{a(y)}^{b(y)}f(x)\, dx = \int_a^b f \circ h (x)\, dx = \dfrac{1}{2}\int_1^4x\, dx = 3.75.  
+\int_{a(y)}^{b(y)}f(x)\, dx = \int_a^b f \circ h (x)\, dx = \dfrac{1}{2}\int_1^4x\, dx = 3.75,  
 \end{equation}
-If we use its Riemann-Stieltjes equivalent we obtain:
+or
 \begin{equation}
 \int_{a(y)}^{b(y)}f(x)\, dx = \int_{a'}^{b'} f \, dg(x) = \int_{\frac{1}{2}}^2x\, d2x = 3.75.  
+\end{equation}
+Note, that for the example presented in this section $h(x) = \frac{1}{2}x$ and $g(x) = 2x$.
+
+We can easily verify that the above is correct by using a more traditional route:
+\begin{equation}
+\int_0^2x\, dx+\int_2^44-x\, dx- \int_0^{\frac{1}{2}}x\, dx-\int_{\frac{1}{2}}^11-x\, dx = 3.75. 
 \end{equation}

### 2019-09-25 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
fleshed out the background sections a lot more

@@
 \begin{itemize}
- \item $a(y) = f^{-1}(y)-\widetilde{g}\circ f^{-1}(y) + \widetilde{g}(a')$.
- \item $a = a(0)$.
- \item $C = a - \widetilde{g}(a')$.
- \item $g(x) = \widetilde{g}(x) + C$.
- \item $b = g(b')$ and $b(y) = a(y) + (b-a)$.
+ \item Compute $a(y)$ using: 
+\begin{equation}
+a(y) = f^{-1}(y)-\widetilde{g}\circ f^{-1}(y) + \widetilde{g}(a'). 
+\end{equation}
+ \item Compute $a = a(0)$.
+ \item Compute $C = a - \widetilde{g}(a')$.
+ \item Compute $g(x) = \widetilde{g}(x) + C$.
+ \item Compute $b = g(b')$ and $b(y) = a(y) + (b-a)$.
 \end{itemize}
@@
 \end{equation}
-Note, that for the example presented in this section $h(x) = \frac{1}{2}x$ and $g(x) = 2x$.
+Note, that in the above two equations: $h(x) = \frac{1}{2}x$ and $g(x) = 2x$.
 
@@
 
-\noindent
-Conversely, if $g$ is known (and not $a(y)$) and $g(a') = a$ then we can calculate $a(y)$ using the following \cite{grobler19}:
+Conversely, consider the following Riemann-Stieltjes integral:
 \begin{equation}
-\label{eq:a_y}
-a(y) = f^{-1}(y) - g\circ f^{-1}(y) + g(a'). 
+\int_{a'}^{b'} \,d\,\widetilde{g}(x) = \int_{\frac{1}{2}}^2 x\,d2x.
 \end{equation}
-Eq.~\eqref{eq:a_y} allows us to transform a Riemann-Stieltjes integral into an equivalent Cavalieri integral. 
-Furthermore, this transformation enables us to assign a geometric interpretation to a Riemann-Stieltjes integral. The interpretation being:
-it represents the area obtained by summing together the area of an infinite number of non-rectangular infinitesimals; all of them being translations of $a(y)$. Note,
-$b(y) = a(y) + (b-a)$.
+We can convert this Riemann-Stieltjes integral into a Cavalieri integral via the following conversion steps (see Theorem~\ref{??} and the last paragraph of Section~\ref{??}):
+\begin{itemize}
+ \item $a(y) = f^{-1}(y) - \widetilde{g}\circ f^{-1}(y)+ \widetilde{g}(a') = 1-y$.
+ \item $a(0) = 1$.
+ \item $C = a - \widetilde{g}(a') = 0$.
+ \item $g(x) = \widetilde{g}(x) + C = 2x$.
+ \item $b = g(b') = 4$ and $b(y) = a(y) + (b-a) = 4-y$.
+\end{itemize}
+The integrals $\int_{\frac{1}{2}}^{2} x\,d2x$  and $\int_{1-y}^{4-y} x\,dx$ have the exact same geometric meaning, since $C=0$.
 

### 2019-09-25 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
improved fractional integral section

@@
 
+\section{Left-sided Riemann-Liouville Fractional Integral}
+In this section we review the definition of the left-sided Riemann-Liouville fractional integral of order $\alpha$ (based at $a'$) \cite{laurent1884}.
+Please note that in this paper from this point going forward our variable of integration will be $\tau$ instead of $x$.
+It is our opinion that this notational change improves the readability of the paper.
+Let
+\begin{equation}
+_{a'}I_t\, f(t) := \int_{a'}^t f(\tau)~d\tau.
+\end{equation}
+If we apply the above operator in a repetitive manner to $f$ we obtain the $n$th antiderivative of $f$ based at $a'$:
+\begin{equation}
+\label{eq:n_anti}
+_{a'}I_t^n\,f(t) = \int_{a'}^t\int_{a'}^{\tau_1}\cdots \int_0^{\tau_{n-1}}f(\tau_n)~d\tau_n\cdots d\tau_2 d\tau_1.
+\end{equation}
+Applying Cauchy's repetitive integration formula to Eq.~\eqref{eq:n_anti} results in:
+\begin{equation}
+\label{eq:cauchy}
+_{a'}I_t^n\,f(t) = \frac{1}{(n-1)!}\int_0^t (t-\tau)^{n-1}f(\tau)~d\tau.
+\end{equation}
+As an example if $f(t)=t$, $n=2$ and $a'=0$ then Eq.~\eqref{eq:cauchy} reduces to:
+\begin{equation}
+_{0}I_t^2\,f(t) = \int_0^t (t-\tau)\tau~d\tau = \frac{\tau^2 t}{2} - \frac{\tau^3}{3} \Bigg |_0^t = \frac{t^3}{3!}.
+\end{equation}
+The definition in Eq.~\eqref{eq:cauchy} can now be extended to an arbitrary fractional order by replacing $(n-1)!$ with the Gamma function (see Fig.~\ref{fig:gamma}):
+\begin{equation}
+\label{eq:frac_integral}
+_{a'}I_t^{\alpha}f(t) = \frac{1}{\Gamma(\alpha)}\int_{a'}^t (t-\tau)^{\alpha-1}f(\tau)~d\tau.
+\end{equation}
+Eq.~\eqref{eq:frac_integral} is known as the left-sided Riemann-Liouville fractional integral of order $\alpha$. As an example if $f(t)=t$, $\alpha=\frac{1}{2}$ and $a'=0$ then 
+Eq.~\eqref{eq:frac_integral} reduces to:
+\begin{equation}
+_0 I_t^{\frac{1}{2}}\,f(t) = \frac{1}{\Gamma(\frac{1}{2})} \int_0^t \frac{\tau}{\sqrt{t-\tau}} d\tau = \frac{1}{\sqrt{\pi}}\left [ -\frac{2}{3}\sqrt{t-\tau}(2t+\tau)\right] \Bigg |_0^t=\frac{4}{3\sqrt{\pi}}t^{\frac{3}{2}}.
+\end{equation}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.75\textwidth]{gamma.pdf}
+\caption{A plot of $\Gamma(x) = \int_0^{\infty} t^{x-1} e^{-t}\,dt$ for $x\in(-5,5)$.
+$\Gamma(x)$ is not defined for the negative integers.
+Moreover, it is a natural extension of the factorial function to the real numbers \cite{euler1738}.}
+\label{fig:gamma}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-09-25 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
added more sections

@@
 \section{Left-sided Riemann-Liouville Fractional Integral}
-In this section we review the definition of the left-sided Riemann-Liouville fractional integral of order $\alpha$ (based at $a'$) \cite{laurent1884}.
-Please note that in this paper from this point going forward our variable of integration will be $\tau$ instead of $x$.
-It is our opinion that this notational change improves the readability of the paper.
-Let
+In this section we review the definition of the left-sided Riemann-Liouville fractional integral of order $\alpha$ (based at $a'$) \cite{laurent1884}. Let
 \begin{equation}
@@
 \end{equation}
+Please note that in this paper from this point going forward our variable of integration will be $\tau$ instead of $x$.
+It is of our opinion that this notational change improves the readability of the paper (if $\tau$ is our variable of integration then it makes sense to choose $t$ to denote our upper integration limit in Eq.~\ref{??}).
 If we apply the above operator in a repetitive manner to $f$ we obtain the $n$th antiderivative of $f$ based at $a'$:
@@
 \end{figure}
+
+\section{Geometric Interpretation of the Left-sided Riemann-Liouville Fractional Integral}
+
+\subsection{Converting into a Riemann-Stieltjes integral}
+Podlubny showed that the Left-sided Riemann-Liouville fractional integral can be rewritten as a Riemann-Stieltjes integral \cite{podlubny02}:
+\begin{theorem}
+The following integrals are equivalent
+\begin{equation}
+_{a'}I_t^{\alpha}\,f(t) = \frac{1}{\Gamma(\alpha)}\int_{a'}^{t}(t-\tau)^{\alpha-1}f(\tau)~d\tau = \int_{a'}^{t} f(\tau)~dg_t^{\alpha}(\tau), 
+\end{equation}
+with 
+\begin{equation}
+\label{eq:g_rl}
+g_t^{\alpha}(\tau) = \frac{\left \{t^{\alpha} - (t-\tau)^{\alpha} \right \}}{\Gamma(\alpha+1)}. 
+\end{equation}
+\end{theorem}
+
+\begin{proof}
+Note that 
+\begin{equation}
+\label{eq:diff}
+\frac{dg_t^{\alpha}(\tau)}{d\tau} = \frac{\alpha(t-\tau)^{\alpha-1}}{\Gamma(\alpha+1)} =\frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)}. 
+\end{equation}
+Furthermore,
+\begin{equation}
+\label{eq:inter_step}
+\int_{a'}^{t} f(\tau)\,dg_t^{\alpha}(\tau) = \int_{a'}^{t} f(\tau) \frac{dg_t^{\alpha}(\tau)}{d\tau}\,dg_t^{\alpha}(\tau). 
+\end{equation}
+The desired result is obtained by substituting Equation~\eqref{eq:diff} into Equation~\eqref{eq:inter_step}.  
+\end{proof}
+
+In this section we present a novel geometric interpretation of the Riemann-Liouville fractional integral. 
+Recall that the Riemann-Liouville fractional integral of order $\alpha$ is defined as:
+\begin{equation}
+\label{eq:RL_frac_int}
+\frac{1}{\Gamma(\alpha)}\int_{0}^{t}f(\tau)(t-\tau)^{\alpha-1}~d\tau
+\end{equation}
+
+\noindent
+Podlubny showed that the above fractional integral can be rewritten as a Riemann-Stieltjes integral \cite{podlubny02}:
+\begin{equation}
+\label{eq:rs}
+\int_0^{t} f(\tau)~dg_t(\tau),
+\end{equation}
+with 
+\begin{equation}
+\label{eq:g_rl}
+g_t^{\alpha}(\tau) = \frac{\left \{t^{\alpha} - (t-\tau)^{\alpha} \right \}}{\Gamma(\alpha+1)}. 
+\end{equation}
+
+\noindent
+Note that $g_t^{\alpha}(\tau)$ is always invertible, since $\frac{d g_t^{\alpha}}{d \tau} = \frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)}>0$ for $\tau\in[0,t]$. The inverse 
+of $g_t^{\alpha}(\tau)$ is equal to:
+\begin{equation}
+h_t^{\alpha}(\tau) = t - \sqrt[\alpha]{t^{\alpha} - \Gamma(\alpha+1)\tau}
+\end{equation}
+
+\noindent
+Let $\mathsf{A} = \{0,0.2,0.4,0.6,0.8,1\}$. The analytic expressions of $g_{10}^{\alpha}(\tau)$ and $h_{10}^{\alpha}(\tau)$ are presented in Table~\ref{tab:gandh} for $\alpha\in\mathsf{A}$. 
+The expressions in Table~\ref{tab:gandh} are depicted in Fig~\ref{fig:gandh}.
+
+\begin{table}[h!]
+ \centering
+ \caption{The analytic expressions of $g_{10}^{\alpha}(\tau)$ and $h_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}$.}
+ \label{tab:gandh}
+ \begin{tabular}{|c || c | c|} 
+ \hline
+ $\alpha$ & $g_{10}^{\alpha}(\tau)$ & $h_{10}^{\alpha}(\tau)$ \\ [0.5ex] 
+ \hline\hline
+ $0$ & 0 & $y=0$ \\ 
+ $0.2$ & $[\Gamma\left (\frac{6}{5} \right )]^{-1}\left(\sqrt[5]{10}-\sqrt[5]{10-\tau}\right)$ & $10 - \left ( \sqrt[5]{10} -  \Gamma\left (\frac{6}{5} \right ) \tau \right )^5$  \\
+ $0.4$ & $[\Gamma\left (\frac{7}{5} \right )]^{-1}\left(\sqrt[5]{10^2}-\sqrt[5]{(10-\tau)^2}\right)$ & $10 - \sqrt{\left ( \sqrt[5]{10} -  \Gamma\left (\frac{7}{5} \right ) \tau \right )^5}$ \\
+ $0.6$ & $[\Gamma\left (\frac{8}{5} \right )]^{-1}\left(\sqrt[5]{10^3}-\sqrt[5]{(10-\tau)^3}\right)$ & $10 - \sqrt[3]{\left ( \sqrt[5]{10} -  \Gamma\left (\frac{8}{5} \right ) \tau \right )^5}$ \\
+ $0.8$ & $[\Gamma\left (\frac{9}{5} \right )]^{-1}\left(\sqrt[5]{10^4}-\sqrt[5]{(10-\tau)^4}\right)$ & $10 - \sqrt[4]{\left ( \sqrt[5]{10} -  \Gamma\left (\frac{9}{5} \right ) \tau \right )^5}$ \\ [1ex]
+ $1$ & $\tau$ & $\tau$ \\ [1ex] 
+ \hline
+ \end{tabular}
+ \end{table}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.75\textwidth]{gh.pdf}
+\caption{This figure depicts the curves of $g_{10}^{\alpha}(\tau)$ and $h_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}$. The curves associated with $g$ are plotted using 
+solid lines, while the curves plotted with dashed lines are associated with $h$. The lighter the shade with which a curve is depicted, the larger the $\alpha$-value is that is associated with it.
+}
+\label{fig:gandh}
+\end{figure}
+
+\noindent
+Furthermore, Grobler showed that it is trivial to convert a Riemann-Stieltjes integral into a Cavalieri integral \cite{ackermann12,grobler19} (see Fig.~\ref{fig:caval2} and the Cavalieri section of this paper if more details are required).
+If we apply Grobler's conversion method to Eq.~\eqref{eq:rs} we obtain:
+\begin{equation}
+\label{eq:cav}
+\int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau, 
+\end{equation}
+with
+\begin{equation}
+\label{eq:cav_a}
+a_t^{\alpha}(y) = f^{-1}(y) - \frac{t^{\alpha}-(t-f^{-1}(y))^{\alpha}}{\Gamma(\alpha+1)}.
+\end{equation}
+Eq.~\eqref{eq:cav_a} is obtained by substituting Eq.~\eqref{eq:g_rl} into Eq.~\eqref{eq:a_y}. Note, $b_t^{\alpha}(y) = a_t^{\alpha}(y) + \frac{t^{\alpha}}{\Gamma(\alpha+1)}$.
+
+\noindent
+We can now assign a geometric interpretation to Eq.~\eqref{eq:cav}, since it is a Cavalieri integral (see Fig.~\ref{fig:caval2} and the Cavalieri section of this paper).
+The fractional integral in Eq.~\eqref{eq:RL_frac_int} can, therefore, be interpreted as the area obtained
+by summing together the area of an infinite number of infinitesimally small non-rectangular integration strips whose shape is determined by $\alpha$ and $t$.
+If $\alpha$ is equal to one, however, then the integral reduces to a normal Riemann integral as the integration strips become rectangular for this particular choice of $\alpha$ (its shape becomes independent of $t$).\\
+
+\noindent
+Interestingly, Eq.~\eqref{eq:main_cav} implies that we can use $h_t^{\alpha}(\tau)$ to convert Eq.~\eqref{eq:cav} into the following Riemann integral:
+\begin{equation}
+\label{eq:option2}
+\int_0^{\frac{t^{\alpha}}{\Gamma(\alpha+1)}} f\circ h_{\alpha}^t (\tau) d\tau.  
+\end{equation}
+We can, therefore, evaluate Eq.~\eqref{eq:cav} in one of two ways: we can either evaluate Eq.~\eqref{eq:rs} or we can evaluate Eq.~\eqref{eq:option2}.
 

### 2019-09-26 fractional/FCAA/Authors Kit (Updated)/wire3d_demo.py
added old framework --- plotting ability

@@ -1,0 +1,185 @@
+import numpy as np
+from mpl_toolkits.mplot3d import Axes3D
+import matplotlib.pyplot as plt
+import random
+import math
+from matplotlib.collections import PolyCollection
+from matplotlib.colors import colorConverter
+from mpl_toolkits.mplot3d import Axes3D
+from mpl_toolkits.mplot3d.art3d import Poly3DCollection
+
+def f_x(x,y):
+    return np.sqrt(x)
+
+def g_x(x,z):
+  return x
+
+def g_x_2(x,z,t=5,a=0.5):
+    return (t**(a)-(t-x)**(a))/math.gamma(a+1)
+
+fig = plt.figure()
+
+x_max = 5.0
+d = 0.01
+y_max = g_x_2(x_max,0)
+z_max = f_x(x_max,0)
+
+#PLOT SURFACES
+
+#PLOT g_x
+ax = fig.add_subplot(111, projection='3d')
+x = np.arange(0, x_max, d)
+z = np.arange(0, z_max, d)
+X, Z = np.meshgrid(x, z)
+ys = np.array([g_x_2(x,z) for x,z in zip(np.ravel(X), np.ravel(Z))])
+Y = ys.reshape(X.shape)
+ax.plot_surface(X, Y, Z,color="blue",alpha=0.2,linewidth=0)
+
+#PLOT f_x
+x = np.arange(0, x_max, d)
+y = np.arange(0, y_max, d)
+X, Y = np.meshgrid(x, y)
+zs = np.array([f_x(x,y) for x,y in zip(np.ravel(X), np.ravel(Y))])
+Z = zs.reshape(X.shape)
+ax.plot_surface(X, Y, Z,color="black",alpha=0.2,linewidth=0)
+
+
+#PLOT CURVES
+x = np.arange(0, x_max, d)
+
+#PLOT PROJECTION
+ax.plot(np.zeros(x.shape),g_x_2(x,0),f_x(x,0),color="black")
+#print(np.zeros(x.shape))
+#print(g_x_2(x,0))
+#print(f_x(x,0))
+#PLOT INTERSECTION
+ax.plot(x,g_x_2(x,0),f_x(x,0),color="black",linestyle='dashed',linewidth=1.5)
+#print(x)
+#print(g_x_2(x,0))
+#print(f_x(x,0))
+
+xs = np.zeros(x.shape)
[…]

### 2019-10-02 fractional/FCAA/Authors Kit (Updated)/wire3d_demo.py
added subplot

@@ -17,87 +17,108 @@ def g_x(x,z):
 def g_x_2(x,z,t=5,a=0.5):
     return (t**(a)-(t-x)**(a))/math.gamma(a+1)
 
+import matplotlib 
+#plt.locator_params(nbins=4)
+
 fig = plt.figure()
+matplotlib.rcParams.update({'font.size': 10})
 
-x_max = 5.0
+counter = 1
+
+alpha = np.array([0.3,0.6,0.9])
+t_v = np.array([3,6,9])
 d = 0.01
-y_max = g_x_2(x_max,0)
-z_max = f_x(x_max,0)
 
-#PLOT SURFACES
+for i in range(3):
+   for j in range(3):
+	ax = fig.add_subplot(3,3,counter, projection='3d')	
+        x_max = t_v[j]
+        y_max = g_x_2(x_max,0,t=t_v[j],a=alpha[i])
+        z_max = f_x(x_max,0)
 
-#PLOT g_x
-ax = fig.add_subplot(111, projection='3d')
-x = np.arange(0, x_max, d)
-z = np.arange(0, z_max, d)
-X, Z = np.meshgrid(x, z)
-ys = np.array([g_x_2(x,z) for x,z in zip(np.ravel(X), np.ravel(Z))])
-Y = ys.reshape(X.shape)
-ax.plot_surface(X, Y, Z,color="blue",alpha=0.2,linewidth=0)
+        #PLOT SURFACES
 
-#PLOT f_x
-x = np.arange(0, x_max, d)
-y = np.arange(0, y_max, d)
-X, Y = np.meshgrid(x, y)
-zs = np.array([f_x(x,y) for x,y in zip(np.ravel(X), np.ravel(Y))])
-Z = zs.reshape(X.shape)
-ax.plot_surface(X, Y, Z,color="black",alpha=0.2,linewidth=0)
+        #PLOT g_x
+        x = np.arange(0, x_max, d)
+        z = np.arange(0, z_max, d)
+        X, Z = np.meshgrid(x, z)
+        ys = np.array([g_x_2(x,z,t=t_v[j],a=alpha[i]) for x,z in zip(np.ravel(X), np.ravel(Z))])
+        Y = ys.reshape(X.shape)
+        ax.plot_surface(X, Y, Z,color="blue",alpha=0.2,linewidth=0)
+
+        #PLOT f_x
+        x = np.arange(0, x_max, d)
[…]

### 2019-10-02 fractional/FCAA/Authors Kit (Updated)/wire3d_demo.py
newest code

@@ -21,7 +21,7 @@ import matplotlib
 #plt.locator_params(nbins=4)
 
 fig = plt.figure()
-matplotlib.rcParams.update({'font.size': 10})
+matplotlib.rcParams.update({'font.size': 22})
 
 counter = 1
 
@@ -105,19 +105,33 @@ for i in range(3):
 	#matplotlib.rc('zlabel', labelsize=20)
         tick_spacing = 1
         import matplotlib.ticker as ticker
+        ax.view_init(30,200)
 
-        ax.xaxis.set_major_locator(ticker.MultipleLocator(tick_spacing+1))
+
+        if counter == 2:
+           ax.set_xlabel(r'$\tau$',labelpad=10)
+	   ax.set_ylabel(r'$g_t^{\alpha}(\tau)$',labelpad=18)
+	   ax.set_zlabel(r'$f(\tau)$')
+
+        if counter <=3:
+           ax.set_title(r"$t = $"+str(t_v[counter-1]))
+
+        if counter == 1 or counter ==4 or counter == 7:
+           ax.set_zlabel(r'$\alpha =$'+str(alpha[i]))
+
+
+        if j == 2: 
+           ax.xaxis.set_major_locator(ticker.MultipleLocator(tick_spacing+2))
+        else:
+           ax.xaxis.set_major_locator(ticker.MultipleLocator(tick_spacing+1))
         ax.yaxis.set_major_locator(ticker.MultipleLocator(tick_spacing))
 	ax.zaxis.set_major_locator(ticker.MultipleLocator(tick_spacing))
 	
-        ax.set_xlabel(r'$\tau$')
-	ax.set_ylabel(r'$g_t^{\alpha}(\tau)$')
-	ax.set_zlabel(r'$f(\tau)$')
         
 
-	ax.view_init(30,220)
+	ax.view_init(30,200)
         counter = counter + 1 
-plt.tight_layout()
+#plt.tight_layout(h_pad=0.5,w_pad=0.5,pad=0.5)
 plt.show()
 
 

### 2019-10-02 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
newest version of article

@@
 %\end{figure}
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.75\textwidth]{fig13.pdf}
-\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$.
+%\begin{figure}[htb]
+%\centering
+%\includegraphics[width=0.75\textwidth]{fig13.pdf}
+%\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$.
 In the case of $R$: $a=1$, $b=4$, $a'=\frac{1}{2}$ and $b'=2$.
@@
 Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
-\label{fig:caval2}
-\end{figure}
+%\label{fig:caval2}
+%\end{figure}
 
@@
 \label{eq:n_anti}
-_{a'}I_t^n\,f(t) = \int_{a'}^t\int_{a'}^{\tau_1}\cdots \int_0^{\tau_{n-1}}f(\tau_n)~d\tau_n\cdots d\tau_2 d\tau_1.
+_{a'}I_t^n\,f(t) = \int_{a'}^t\int_{a'}^{\tau_1}\cdots \int_{a'}^{\tau_{n-1}}f(\tau_n)~d\tau_n\cdots d\tau_2 d\tau_1.
 \end{equation}
@@
 \label{eq:cauchy}
-_{a'}I_t^n\,f(t) = \frac{1}{(n-1)!}\int_0^t (t-\tau)^{n-1}f(\tau)~d\tau.
+_{a'}I_t^n\,f(t) = \frac{1}{(n-1)!}\int_{a'}^t (t-\tau)^{n-1}f(\tau)~d\tau.
 \end{equation}
@@
 \caption{This figure depicts the curves of $g_{10}^{\alpha}(\tau)$ and $h_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}$. The curves associated with $g$ are plotted using 
+solid lines, while the curves plotted wit h dashed lines are associated with $h$. The lighter the shade with which a curve is depicted, the larger the $\alpha$-value is that is associated with it.
+}
+\label{fig:gandh}
+\end{figure}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=1.0\textwidth]{vis_old.pdf}
+\caption{This figure depicts the curves of $g_{10}^{\alpha}(\tau)$ and $h_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}$. The curves associated with $g$ are plotted using 
 solid lines, while the curves plotted with dashed lines are associated with $h$. The lighter the shade with which a curve is depicted, the larger the $\alpha$-value is that is associated with it.

### 2019-10-02 fractional/FCAA/Authors Kit (Updated)/wire3d_demo.py
fixed minor gx bug

@@ -27,13 +27,16 @@ counter = 1
 
 alpha = np.array([0.3,0.6,0.9])
 t_v = np.array([3,6,9])
-d = 0.01
+d = 0.1
 
 for i in range(3):
    for j in range(3):
 	ax = fig.add_subplot(3,3,counter, projection='3d')	
         x_max = t_v[j]
         y_max = g_x_2(x_max,0,t=t_v[j],a=alpha[i])
+        print(counter)
+        print(x_max)
+        print(y_max)
         z_max = f_x(x_max,0)
 
         #PLOT SURFACES
@@ -48,7 +51,7 @@ for i in range(3):
 
         #PLOT f_x
         x = np.arange(0, x_max, d)
-        y = np.arange(0, y_max, d)
+        y = np.linspace(0, ys[-1], 100)
         X, Y = np.meshgrid(x, y)
         zs = np.array([f_x(x,y) for x,y in zip(np.ravel(X), np.ravel(Y))])
         Z = zs.reshape(X.shape)

### 2019-10-03 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
newest article

@@
 \label{eq:inter_step}
-\int_{a'}^{t} f(\tau)\,dg_t^{\alpha}(\tau) = \int_{a'}^{t} f(\tau) \frac{dg_t^{\alpha}(\tau)}{d\tau}\,dg_t^{\alpha}(\tau). 
+\int_{a'}^{t} f(\tau)\,dg_t^{\alpha}(\tau) = \int_{a'}^{t} f(\tau) \frac{dg_t^{\alpha}(\tau)}{d\tau}\,d\tau. 
 \end{equation}
@@
 
-In this section we present a novel geometric interpretation of the Riemann-Liouville fractional integral. 
-Recall that the Riemann-Liouville fractional integral of order $\alpha$ is defined as:
+\begin{theorem}
+If $\tau\in(-\infty,t]$ then $g_t^{\alpha}(\tau)$ is an invertable function. Its inverse is:
 \begin{equation}
-\label{eq:RL_frac_int}
-\frac{1}{\Gamma(\alpha)}\int_{0}^{t}f(\tau)(t-\tau)^{\alpha-1}~d\tau
+h_t^{\alpha}(\tau) = t - \sqrt[\alpha]{t^{\alpha} - \Gamma(\alpha+1)\tau}.
 \end{equation}
-
-\noindent
-Podlubny showed that the above fractional integral can be rewritten as a Riemann-Stieltjes integral \cite{podlubny02}:
-\begin{equation}
-\label{eq:rs}
-\int_0^{t} f(\tau)~dg_t(\tau),
-\end{equation}
-with 
-\begin{equation}
-\label{eq:g_rl}
-g_t^{\alpha}(\tau) = \frac{\left \{t^{\alpha} - (t-\tau)^{\alpha} \right \}}{\Gamma(\alpha+1)}. 
-\end{equation}
-
-\noindent
-Note that $g_t^{\alpha}(\tau)$ is always invertible, since $\frac{d g_t^{\alpha}}{d \tau} = \frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)}>0$ for $\tau\in[0,t]$. The inverse 
-of $g_t^{\alpha}(\tau)$ is equal to:
-\begin{equation}
-h_t^{\alpha}(\tau) = t - \sqrt[\alpha]{t^{\alpha} - \Gamma(\alpha+1)\tau}
-\end{equation}
+\end{theorem}
+\begin{proof}
+The function $g_t^{\alpha}$ is invertable, since $\frac{d g_t^{\alpha}}{d\tau}=\frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)} > 0$ if $\tau\in(-\infty,t]$. The inverse now follows trivially.  
+\end{proof}
 
@@
  \centering
- \caption{The analytic expressions of $g_{10}^{\alpha}(\tau)$ and $h_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}$.}
+ \caption{The analytic expressions of $g_{10}^{\alpha}(\tau)$ and $h_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}$. The expressions in this table are depicted in Fig~\ref{fig:gandh}.}
  \label{tab:gandh}
@@
  $0.2$ & $[\Gamma\left (\frac{6}{5} \right )]^{-1}\left(\sqrt[5]{10}-\sqrt[5]{10-\tau}\right)$ & $10 - \left ( \sqrt[5]{10} -  \Gamma\left (\frac{6}{5} \right ) \tau \right )^5$  \\
- $0.4$ & $[\Gamma\left (\frac{7}{5} \right )]^{-1}\left(\sqrt[5]{10^2}-\sqrt[5]{(10-\tau)^2}\right)$ & $10 - \sqrt{\left ( \sqrt[5]{10} -  \Gamma\left (\frac{7}{5} \right ) \tau \right )^5}$ \\
- $0.6$ & $[\Gamma\left (\frac{8}{5} \right )]^{-1}\left(\sqrt[5]{10^3}-\sqrt[5]{(10-\tau)^3}\right)$ & $10 - \sqrt[3]{\left ( \sqrt[5]{10} -  \Gamma\left (\frac{8}{5} \right ) \tau \right )^5}$ \\
- $0.8$ & $[\Gamma\left (\frac{9}{5} \right )]^{-1}\left(\sqrt[5]{10^4}-\sqrt[5]{(10-\tau)^4}\right)$ & $10 - \sqrt[4]{\left ( \sqrt[5]{10} -  \Gamma\left (\frac{9}{5} \right ) \tau \right )^5}$ \\ [1ex]
+ $0.4$ & $[\Gamma\left (\frac{7}{5} \right )]^{-1}\left(\sqrt[5]{10^2}-\sqrt[5]{(10-\tau)^2}\right)$ & $10 - \sqrt{\left ( \sqrt[5]{10^2} -  \Gamma\left (\frac{7}{5} \right ) \tau \right )^5}$ \\
+ $0.6$ & $[\Gamma\left (\frac{8}{5} \right )]^{-1}\left(\sqrt[5]{10^3}-\sqrt[5]{(10-\tau)^3}\right)$ & $10 - \sqrt[3]{\left ( \sqrt[5]{10^3} -  \Gamma\left (\frac{8}{5} \right ) \tau \right )^5}$ \\
+ $0.8$ & $[\Gamma\left (\frac{9}{5} \right )]^{-1}\left(\sqrt[5]{10^4}-\sqrt[5]{(10-\tau)^4}\right)$ & $10 - \sqrt[4]{\left ( \sqrt[5]{10^4} -  \Gamma\left (\frac{9}{5} \right ) \tau \right )^5}$ \\ [1ex]
  $1$ & $\tau$ & $\tau$ \\ [1ex] 

### 2019-10-03 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
started making sense of paper wording

@@
 
+\begin{definition}
+The Riemann-Stieltjes integral $\int_{a'}^{b'} f(x)\,dg(x)$ and the Cavalieri integral $\int_{a(y)}^{b(y)}f(x)\,dx$ are said to be geometrically equivalent if the same result is obtained when they are evaluated and $g(a')=a(0)=a$.
+\end{definition}
+
 Theorem~\ref{t:conv} tells us how to convert a Cavalieri integral into an equivalent Riemann or Riemann-Stieltjes integral. It, however, tells us nothing about the reverse 
@@
 Let $\widetilde{g}(x)$ and $f(x)$ be known (continuous) invertable real-valued functions.
+The function $\widetilde{g}(x)$ should also be differentiable.
 Moreover, let $a'\in \mathbb{R}$ and $b'\in \mathbb{R}$.
-If $f^{-1}(0) - \widetilde{g}\circ f^{-1}(0) + \widetilde{g}(a')$ exists then there exists a unique
+If $a(y)=f^{-1}(y) - \widetilde{g}\circ f^{-1}(y) + \widetilde{g}(a')$ and $a(0)$ exists then there exists a unique
 $C\in\mathbb{R}$ such that 
@@
 \end{equation}
-where $g(x) = \widetilde{g}(x) + C$ and $a(y) = f^{-1}(y)-\widetilde{g}\circ f^{-1}(y) + \widetilde{g}(a')$, have the exact same 
-geometric meaning.
+where $g(x) = \widetilde{g}(x) + C$, are geometrically equivalent.
 \end{theorem}
@@
 \end{itemize}
-The integrals $\int_{a'}^{b'} f(x)\,d\,\widetilde{g}(x)$ and $\int_{a'}^{b'} f(x)\,dg(x)$ are equivalent (we obtain the same result when they are evaluated).
-Moreover, the integrals $\int_{a'}^{b'} f(x)\,d\,g(x)$ and $\int_{a(y)}^{b(y)}f(x)~dx$ have the exact same geometric meaning.
+Note that $\int_{a'}^{b'} f(x)\,d\,\widetilde{g}(x)=\int_{a'}^{b'} f(x)\,dg(x)$ due to Theorem xx.
+Moreover, Moreover, the integrals $\int_{a'}^{b'} f(x)\,d\,g(x)$ and $\int_{a(y)}^{b(y)}f(x)~dx$ are geometrically equivalent.
 Note, however, that
-$\int_{a'}^{b'} f(x)\,d\,\widetilde{g}(x)$ and $\int_{a(y)}^{b(y)}f(x)~dx$ do not have the exact same geometric meaning.
+$\int_{a'}^{b'} f(x)\,d\,\widetilde{g}(x)$ and $\int_{a(y)}^{b(y)}f(x)~dx$ are not geometrically equivalent.
 
@@
 \begin{theorem}
-If $\tau\in(-\infty,t]$ then $g_t^{\alpha}(\tau)$ is an invertable function. Its inverse is:
+The function $g_t^{\alpha}(\tau)$ is invertable. Its inverse is:
 \begin{equation}
@@
 \begin{proof}
-The function $g_t^{\alpha}$ is invertable, since $\frac{d g_t^{\alpha}}{d\tau}=\frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)} > 0$ if $\tau\in(-\infty,t]$. The inverse now follows trivially.  
+The function $g_t^{\alpha}$ is invertable, since $\frac{d g_t^{\alpha}}{d\tau}=\frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)} > 0$ for $\tau\in(-\infty,t]$. The inverse now follows trivially.  
 \end{proof}
@@
 \end{figure}
+
+\section{Existing Geometric Interpretation}
+
+\section{Converting into a Cavalieri integral}
+
+\begin{theorem}
+Let $a(y)_{t}^{\alpha} = f^{-1}(y) - \widetilde{g}_t^{\alpha}\circ f^{-1}(y) + \widetilde(g)_t^{\alpha}(a')$. If $a(y)_t^{\alpha}$ and $a(0)$ exists then  
+the following integrals are equivalent:
+
+\end{theorem}
 

### 2019-10-04 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
made some progress with paper

@@
 
+\section{Riemann-Stieltjes integral}
+Let $f$ and $g$ denote real-valued functions defined on a closed interval $[a',b']$ of the real line.
+We shall suppose that both $f$ and $g$ are bounded on $[a',b']$.
+These assertions are assumed to be true throughout the paper and will not be repeated again.
+
+\begin{definition}
+Define a partition $\mathcal{P}$ of $[a',b']$ to be a set of points $x_0, x_1,\cdots,x_n$, 
+where $a' = x_0 \leq x_1 \leq \cdots \leq x_n = b'$. For each partition 
+$\mathcal{P}$ of $[a',b']$ write $\Delta g_k = g(x_k)-g(x_{k-1})$. Let 
+$M_k = \sup\{f(x),x_{k-1}\leq x \leq x_{k}\}$, $m_k = \inf\{f(x),x_{k-1}\leq x \leq x_{k}\}$, and set 
+\begin{equation}
+\label{ref:S_up}
+\mathcal{S}_U(\mathcal{P},f,g) = \sum_{k=1}^n M_k \Delta g_k, 
+\end{equation}
+and
+\begin{equation}
+\label{ref:S_low}
+\mathcal{S}_L(\mathcal{P},f,g) = \sum_{k=1}^n m_k \Delta g_k. 
+\end{equation}
+The sums in Eq.~\eqref{ref:S_up} and Eq.~\eqref{ref:S_low} are respectively called the the upper and lower Riemann-Stieltjes sums.
+If there is a unique number $I$ that satisfies the inequality $\mathcal{S}_L(\mathcal{P},f,g)\leq I \leq \mathcal{S}_U(\mathcal{P},f,g)$ for all 
+partitions $P$ of $[a',b']$, then $f$ is Riemann integrable with respect to $g$ on $[a',b']$. Moreover, $I$ is called the Riemann-Stieltjes integral of $f$ from $a'$ to $b'$ and is denoted by
+\begin{equation}
+\int_{a'}^{b'} f(x) dg(x). 
+\end{equation}
+\end{definition}
+
+\begin{theorem}
+If the derivative $g'$ exists and is continuous on $[a',b']$ and if $f$ is integrable with respect to $g$ on $[a',b']$, then the following 
+Riemann and Riemann-Stieltjes integrals are equivalent
+\begin{equation}
+\int_{a'}^{b'} f(x) dg(x) = \int_{a'}^{b'} f(x)g'(x)dx.
+\end{equation}
+\end{theorem}
+
 \section{Cavalieri Integral}
@@
 
-\begin{definition}
-The Riemann-Stieltjes integral $\int_{a'}^{b'} f(x)\,dg(x)$ and the Cavalieri integral $\int_{a(y)}^{b(y)}f(x)\,dx$ are said to be geometrically equivalent if the same result is obtained when they are evaluated and $g(a')=a(0)=a$.
-\end{definition}
-
 Theorem~\ref{t:conv} tells us how to convert a Cavalieri integral into an equivalent Riemann or Riemann-Stieltjes integral. It, however, tells us nothing about the reverse 
@@
 
+\begin{definition}
+The Riemann-Stieltjes integral $\int_{a'}^{b'} f(x)\,dg(x)$ and the Cavalieri integral $\int_{a(y)}^{b(y)}f(x)\,dx$ are said to be geometrically equivalent if the same result is obtained when they are evaluated, $g(a')=a(0)=a$ and $g(b')=b(0)=b$.
+\end{definition}
+
+Please note that the integrals in the above definition refer to two randomly 
+chosen integrals and not integrals that were obtained via Theorem~\ref{t:conv}. Integrals
+obtained using Theorem~\ref{t:conv} are geometrically equivalent by definition.
+We used the same notation in the above definitiion as that used in Theorem~\ref{t:conv} as we believe that this improves the readability and the interpretability of later definitions and theorems.
+
 \begin{theorem}
 \label{t:reverse}
-Let $\widetilde{g}(x)$ and $f(x)$ be known (continuous) invertable real-valued functions.
-The function $\widetilde{g}(x)$ should also be differentiable.
-Moreover, let $a'\in \mathbb{R}$ and $b'\in \mathbb{R}$.
-If $a(y)=f^{-1}(y) - \widetilde{g}\circ f^{-1}(y) + \widetilde{g}(a')$ and $a(0)$ exists then there exists a unique
-$C\in\mathbb{R}$ such that 
+Let $\widetilde{g}(x)$ be a known continuous, differentiable and invertable real-valued function on $[a',b']\subset\mathbb{R}$.
+Let $f(x)$ be a continious real-valued function.
+If $a(y)=f^{-1}(y) - \widetilde{g}\circ f^{-1}(y) + \widetilde{g}(a')$ and $a(0)$ exists then there exists a unique $C\in\mathbb{R}$ such that
 \begin{equation}
@@
 
-To clarify the above theorem, consider the Riemann-Stieltjes integral $\int_{a'}^{b'} f(x)\,d\,\widetilde{g}(x)$. We can now compute the following:
+To clarify the above theorem, consider the Riemann-Stieltjes integral $\int_{a'}^{b'} f(x)\,d\,\widetilde{g}(x)$.
+The Cavalieri-Stieltjes integral pair associated with this Stieltjes integral can only be determined if $C$ is known to us.
+Luckily, this can be easily obtained using the the following steps (taken from \cite{??}):
 \begin{itemize}
@@
 Note that $\int_{a'}^{b'} f(x)\,d\,\widetilde{g}(x)=\int_{a'}^{b'} f(x)\,dg(x)$ due to Theorem xx.
-Moreover, Moreover, the integrals $\int_{a'}^{b'} f(x)\,d\,g(x)$ and $\int_{a(y)}^{b(y)}f(x)~dx$ are geometrically equivalent.
+Moreover, the integrals $\int_{a'}^{b'} f(x)\,d\,g(x)$ and $\int_{a(y)}^{b(y)}f(x)~dx$ are geometrically equivalent.
 Note, however, that
 $\int_{a'}^{b'} f(x)\,d\,\widetilde{g}(x)$ and $\int_{a(y)}^{b(y)}f(x)~dx$ are not geometrically equivalent.
+
+The theorems and definitions presented in this section impose much greater restrictions on $g(x)$ and $f(x)$ than that mentioned in the begining of Section. The functions 
+$g(x)$, $\widetilde{g}(x)$ and $f(x)$ now also need to be differentiable and invertable. Moreover, the function $a(y)$ also needs to be differentiable and $a(0)$ needs to exist.
+These assertions are deemed to be true for the remainder of the paper and as such are not repeated again.
+As will become clear later on, these restrictions limit the number of fractional integrals for which the geometric framework we propose in this paper can produce meaningful results.
+This, however, does not diminish the importance of the proposed framework, since, for the integrals for which it does produce meaningful results, it will lead to new and novel insights.
 
@@
 \begin{theorem}
-The following integrals are equivalent
+Let $C\in\mathbb{R}$. The following integrals are equivalent
 \begin{equation}
@@
 \label{eq:g_rl}
-g_t^{\alpha}(\tau) = \frac{\left \{t^{\alpha} - (t-\tau)^{\alpha} \right \}}{\Gamma(\alpha+1)}. 
+g_t^{\alpha}(\tau) = \frac{\left \{t^{\alpha} - (t-\tau)^{\alpha} \right \}}{\Gamma(\alpha+1)} + C. 
 \end{equation}
@@
 \begin{equation}
-h_t^{\alpha}(\tau) = t - \sqrt[\alpha]{t^{\alpha} - \Gamma(\alpha+1)\tau}.
+h_t^{\alpha}(\tau) = t - \sqrt[\alpha]{t^{\alpha} - \Gamma(\alpha+1)(\tau-C)}.
 \end{equation}
@@
 \section{Existing Geometric Interpretation}
+Podlubny suggested to build a ``fence'' in $(\tau,g_t^{\alpha},f)$-space.
+The base of the aforementioned fence is geiven by the curve $(\tau,g_t^{\alpha}(\tau),0)$, while its height is determined by $(\tau,g_t^{\alpha}(\tau),f(\tau))$.
+The
+``shadow'' of this fence, i.e. the area under the curve which is obtained by 
+projecting this fence onto the $gf$- plane corresonds to the value which is obtained when Eq is evaluated. As an example, the visualization of  
+\begin{equation}
+xxx 
+\end{equation}
+using the fence-idea suggested by Podlubny is presented in Fig...
+
+%geometric idea is depicted in Fig for $f(t)=\sqrt{t}$, $\alpha\in\{0.3,0.6,0.9\}$ and $\t\in\{3,6,9\}$.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=1.0\textwidth]{vis_old.pdf}
+\caption{This figure depicts the visualization of Eq using the geometric framework proposed by Podlubny.
+The fence itstelf is depicted in green.
+The areas depicted in red (the shadow of the fence) correspond to the value obtained if Eq.
+is evaluated.
+The surface which is obtained
+by extending the curve $f(\tau)$ and $g_t^{\alpha}(\tau)$ along the $g$ and $f$ direction 
+is depicted in cyan and blue respectively. The curve that determines the height of the fence 
+}
+\label{fig:gandh}
+\end{figure}
 
@@
 \begin{theorem}
-Let $a(y)_{t}^{\alpha} = f^{-1}(y) - \widetilde{g}_t^{\alpha}\circ f^{-1}(y) + \widetilde(g)_t^{\alpha}(a')$. If $a(y)_t^{\alpha}$ and $a(0)$ exists then  
-the following integrals are equivalent:
-
+Let $\widetilde{g}_t^{\alpha}=\frac{\left \{t^{\alpha} - (t-\tau)^{\alpha} \right \}}{\Gamma(\alpha+1)}$ and $a(y)_{t}^{\alpha} = f^{-1}(y) - \widetilde{g}_t^{\alpha}\circ f^{-1}(y) + \widetilde{g}_t^{\alpha}(a')$.
+If $a(y)_t^{\alpha}$ and $a(0)$ exists then
+there exists a $C\in \mathbb{R}$ such that the following integrals are geometrically equivalent:
+\begin{equation}
+\int_{a'}^{b'} f(x)\,dg_t^{\alpha}(x)~\textrm{and}~\int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(x)\,dx. 
+\end{equation}
 \end{theorem}
-
-\begin{figure}[htb]
-\centering
-\includegraphics[width=1.0\textwidth]{vis_old.pdf}
-\caption{This figure depicts the curves of $g_{10}^{\alpha}(\tau)$ and $h_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}$. The curves associated with $g$ are plotted using 
-solid lines, while the curves plotted with dashed lines are associated with $h$. The lighter the shade with which a curve is depicted, the larger the $\alpha$-value is that is associated with it.
-}
-\label{fig:gandh}
-\end{figure}
 

### 2019-10-08 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
added description of Podlubny framework

@@
 Podlubny showed that the Left-sided Riemann-Liouville fractional integral can be rewritten as a Riemann-Stieltjes integral \cite{podlubny02}:
-\begin{theorem}
-Let $C\in\mathbb{R}$. The following integrals are equivalent
+
 \begin{equation}
@@
 \end{equation}
-\end{theorem}
-
-\begin{proof}
-Note that 
-\begin{equation}
-\label{eq:diff}
-\frac{dg_t^{\alpha}(\tau)}{d\tau} = \frac{\alpha(t-\tau)^{\alpha-1}}{\Gamma(\alpha+1)} =\frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)}. 
-\end{equation}
-Furthermore,
-\begin{equation}
-\label{eq:inter_step}
-\int_{a'}^{t} f(\tau)\,dg_t^{\alpha}(\tau) = \int_{a'}^{t} f(\tau) \frac{dg_t^{\alpha}(\tau)}{d\tau}\,d\tau. 
-\end{equation}
-The desired result is obtained by substituting Equation~\eqref{eq:diff} into Equation~\eqref{eq:inter_step}.  
-\end{proof}
-
-\begin{theorem}
-The function $g_t^{\alpha}(\tau)$ is invertable. Its inverse is:
+and $C\in\mathbb{R}$. Moreover, the function $g_t^{\alpha}(\tau)$ is invertable. Its inverse is:
 \begin{equation}
@@
 \end{equation}
-\end{theorem}
-\begin{proof}
-The function $g_t^{\alpha}$ is invertable, since $\frac{d g_t^{\alpha}}{d\tau}=\frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)} > 0$ for $\tau\in(-\infty,t]$. The inverse now follows trivially.  
-\end{proof}
+
+The function $g_t^{\alpha}$ is invertable, since $\frac{d g_t^{\alpha}}{d\tau}=\frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)} > 0$ for $\tau\in(-\infty,t]$.
+
+%\begin{theorem}
+%Let $C\in\mathbb{R}$. The following integrals are equivalent
+%\end{theorem}
+
+%\begin{proof}
+%Note that 
+%\begin{equation}
+%\label{eq:diff}
+%\frac{dg_t^{\alpha}(\tau)}{d\tau} = \frac{\alpha(t-\tau)^{\alpha-1}}{\Gamma(\alpha+1)} =%\frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)}. 
+%\end{equation}
+%Furthermore,
+%\begin{equation}
+%\label{eq:inter_step}
+%\int_{a'}^{t} f(\tau)\,dg_t^{\alpha}(\tau) = \int_{a'}^{t} f(\tau) \frac{dg_t^{\alpha}%(\tau)}{d\tau}\,d\tau. 
+%\end{equation}
+%The desired result is obtained by substituting Equation~\eqref{eq:diff} into Equation~\eqref{eq:inter_step}.  
+%\end{proof}
+
+%\begin{theorem}
+%The function $g_t^{\alpha}(\tau)$ is invertable. Its inverse is:
+%\begin{equation}
+%h_t^{\alpha}(\tau) = t - \sqrt[\alpha]{t^{\alpha} - \Gamma(\alpha+1)(\tau-C)}.
+%\end{equation}
+%\end{theorem}
+%\begin{proof}
+% The inverse now follows trivially.  
+%\end{proof}
 
@@
 
-\section{Existing Geometric Interpretation}
-Podlubny suggested to build a ``fence'' in $(\tau,g_t^{\alpha},f)$-space.
+\section{Podlubny's Geometric Interpretation}
+Podlubny's interpretation of fractional integrals requires the addition of an extra dimension.
+Consider the axis $\tau$, $g_t^{\alpha}$ and $f(\tau)$.
+Podlubny suggests that we build a ``fence'' in $(\tau,g_t^{\alpha},f)$-space.
 The base of the aforementioned fence is geiven by the curve $(\tau,g_t^{\alpha}(\tau),0)$, while its height is determined by $(\tau,g_t^{\alpha}(\tau),f(\tau))$.
@@
 ``shadow'' of this fence, i.e. the area under the curve which is obtained by 
-projecting this fence onto the $gf$- plane corresonds to the value which is obtained when Eq is evaluated. As an example, the visualization of  
-\begin{equation}
-xxx 
-\end{equation}
-using the fence-idea suggested by Podlubny is presented in Fig...
+projecting this fence onto the $gf$- plane corresonds to the value which is obtained when Eq is evaluated. As an example, the geometric interpretation so obtained for 
+the integrand $f(t)=\sqrt{t}$ is depicted in Figure~\ref{}.
 
@@
 \includegraphics[width=1.0\textwidth]{vis_old.pdf}
-\caption{This figure depicts the visualization of Eq using the geometric framework proposed by Podlubny.
+\caption{This figure depicts the visualization of $\frac{1}{\Gamma(\alpha)}\int_{0}^{t}(t-\tau)^{\alpha-1}\sqrt{\tau}~d\tau$ using the geometric framework proposed by Podlubny.
+As is indicated in the figure, the rows of the subfigure-grid are obtained by varying $\alpha$, while the columns of the subfigure-grid are obtained by varying $t$.
 The fence itstelf is depicted in green.
-The areas depicted in red (the shadow of the fence) correspond to the value obtained if Eq.
-is evaluated.
-The surface which is obtained
-by extending the curve $f(\tau)$ and $g_t^{\alpha}(\tau)$ along the $g$ and $f$ direction 
-is depicted in cyan and blue respectively. The curve that determines the height of the fence 
+The areas depicted in red (the shadow of the fence) correspond to the value obtained when $\frac{1}{\Gamma(\alpha)}\int_{0}^{t}(t-\tau)^{\alpha-1}\sqrt{\tau}~d\tau$ is evaluated.
+The surface which is obtained by extending the curve $f(\tau)$ and $g_t^{\alpha}(\tau)$ along the $g$ and $f$ direction is depicted in cyan and blue, respectively.
+The intersection between the blue and cyan
+surfaces represents the curve that determines the height of the aforementioned fence (depicted as a dashed curve).   
 }

### 2019-10-08 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
started rewriting reverse conversion section

@@
 Theorem~\ref{t:conv} tells us how to convert a Cavalieri integral into an equivalent Riemann or Riemann-Stieltjes integral. It, however, tells us nothing about the reverse 
-procedure, if we are given a Riemann-Stieltjes integral how do we convert it into a Cavalieri integral. The theorem below stipulates the conditions that are required to perform the latter conversion.
+procedure, if we are given a Riemann-Stieltjes integral how do we convert it into a Cavalieri integral? As will become clear in the next few paragraphs, this reverse 
+conversion is non-trivial.
 
-\begin{definition}
-The Riemann-Stieltjes integral $\int_{a'}^{b'} f(x)\,dg(x)$ and the Cavalieri integral $\int_{a(y)}^{b(y)}f(x)\,dx$ are said to be geometrically equivalent if the same result is obtained when they are evaluated, $g(a')=a(0)=a$ and $g(b')=b(0)=b$.
-\end{definition}
-
-Please note that the integrals in the above definition refer to two randomly 
-chosen integrals and not integrals that were obtained via Theorem~\ref{t:conv}. Integrals
-obtained using Theorem~\ref{t:conv} are geometrically equivalent by definition.
-We used the same notation in the above definitiion as that used in Theorem~\ref{t:conv} as we believe that this improves the readability and the interpretability of later definitions and theorems.
-
-\begin{theorem}
-\label{t:reverse}
-Let $\widetilde{g}(x)$ be a known continuous, differentiable and invertable real-valued function on $[a',b']\subset\mathbb{R}$.
-Let $f(x)$ be a continious real-valued function.
-If $a(y)=f^{-1}(y) - \widetilde{g}\circ f^{-1}(y) + \widetilde{g}(a')$ and $a(0)$ exists then there exists a unique $C\in\mathbb{R}$ such that
+Consider the Riemann-Stieltjes integral $\int_{a'}^{b'} f(x)\,\widetilde{g}(x)$. Moreover, recall that 
 \begin{equation}
-\int_{a'}^{b'} f(x)\,dg(x)~\textrm{and}~\int_{a(y)}^{b(y)} f(x)\,dx, 
+\label{eq:g_def2}
+g(x) = x - a\circ f(x) + a.
 \end{equation}
-where $g(x) = \widetilde{g}(x) + C$, are geometrically equivalent.
-\end{theorem}
-
-To clarify the above theorem, consider the Riemann-Stieltjes integral $\int_{a'}^{b'} f(x)\,d\,\widetilde{g}(x)$.
-The Cavalieri-Stieltjes integral pair associated with this Stieltjes integral can only be determined if $C$ is known to us.
-Luckily, this can be easily obtained using the the following steps (taken from \cite{??}):
-\begin{itemize}
- \item Compute $a(y)$ using: 
+Furthermore, a consequence of Theorem xx is that:
+\begin{equation}
+\int_{a'}^{b'} f(x)\,dg(x) = \int_{a'}^{b'}f(x)\,\widetilde{g}(x), 
+\end{equation}
+with $g(x) = \widetilde{g}(x) + C$ and $C\in\mathbb{R}$. It, therefore, seems impossible to compute $a(y)$ given $\widetilde{g}(x)$ as $C$ and $a$ are unknown to us a priori. However, 
+\begin{equation}
+\label{eq:implies}
+g(a') = \widetilde{g}(a') + C \implies C = a - \widetilde{g}(a'). 
+\end{equation}
+Substituting Equation~\eqref{eq:implies} into Equation~\eqref{eq:g_def2} eliminates
+both $a$ and $C$ from it. If we now solve for $a(y)$ we obtain:
 \begin{equation}
@@
 \end{equation}
+We can now compute the following:
+\begin{itemize}
 \item Compute $a = a(0)$.
@@
 \item Compute $g(x) = \widetilde{g}(x) + C$.
+\item Compute $h(x) = g^{-1}(x)$.
 \item Compute $b = g(b')$ and $b(y) = a(y) + (b-a)$.
 \end{itemize}
-Note that $\int_{a'}^{b'} f(x)\,d\,\widetilde{g}(x)=\int_{a'}^{b'} f(x)\,dg(x)$ due to Theorem xx.
+
+% \begin{definition}
+% The Riemann-Stieltjes integral $\int_{a'}^{b'} f(x)\,dg(x)$ and the Cavalieri integral $\int_{a(y)}^{b(y)}f(x)\,dx$ are said to be geometrically equivalent if the same result is obtained when they are evaluated, $g(a')=a(0)=a$ and $g(b')=b(0)=b$.
+% \end{definition}
+% 
+% Please note that the integrals in the above definition refer to two randomly 
+% chosen integrals and not integrals that were obtained via Theorem~\ref{t:conv}. Integrals
+% obtained using Theorem~\ref{t:conv} are geometrically equivalent by definition.
+% We used the same notation in the above definitiion as that used in Theorem~\ref{t:conv} as we believe that this improves the readability and the interpretability of later definitions and theorems.
+% 
+% \begin{theorem}
+% \label{t:reverse}
+% Let $\widetilde{g}(x)$ be a known continuous, differentiable and invertable real-valued function on $[a',b']\subset\mathbb{R}$.
+Let $f(x)$ be a continious real-valued function.
+If $a(y)=f^{-1}(y) - \widetilde{g}\circ f^{-1}(y) + \widetilde{g}(a')$ and $a(0)$ exists then there exists a unique $C\in\mathbb{R}$ such that
+% \begin{equation}
+% \int_{a'}^{b'} f(x)\,dg(x)~\textrm{and}~\int_{a(y)}^{b(y)} f(x)\,dx, 
+% \end{equation}
+% where $g(x) = \widetilde{g}(x) + C$, are geometrically equivalent.
+% \end{theorem}
+% 
+% To clarify the above theorem, consider the Riemann-Stieltjes integral $\int_{a'}^{b'} f(x)\,d\,\widetilde{g}(x)$.
+The Cavalieri-Stieltjes integral pair associated with this Stieltjes integral can only be determined if $C$ is known to us.
+Luckily, this can be easily obtained using the the following steps (taken from \cite{??}):
+% \begin{itemize}
+%  \item Compute $a(y)$ using: 
+% \begin{equation}
+% a(y) = f^{-1}(y)-\widetilde{g}\circ f^{-1}(y) + \widetilde{g}(a'). 
+% \end{equation}
+%  \item Compute $a = a(0)$.
+%  \item Compute $C = a - \widetilde{g}(a')$.
+%  \item Compute $g(x) = \widetilde{g}(x) + C$.
+%  \item Compute $b = g(b')$ and $b(y) = a(y) + (b-a)$.
+% \end{itemize}
+% Note that $\int_{a'}^{b'} f(x)\,d\,\widetilde{g}(x)=\int_{a'}^{b'} f(x)\,dg(x)$ due to Theorem xx.
 Moreover, the integrals $\int_{a'}^{b'} f(x)\,d\,g(x)$ and $\int_{a(y)}^{b(y)}f(x)~dx$ are geometrically equivalent.
 Note, however, that
-$\int_{a'}^{b'} f(x)\,d\,\widetilde{g}(x)$ and $\int_{a(y)}^{b(y)}f(x)~dx$ are not geometrically equivalent.
-
-The theorems and definitions presented in this section impose much greater restrictions on $g(x)$ and $f(x)$ than that mentioned in the begining of Section. The functions 
-$g(x)$, $\widetilde{g}(x)$ and $f(x)$ now also need to be differentiable and invertable. Moreover, the function $a(y)$ also needs to be differentiable and $a(0)$ needs to exist.
-These assertions are deemed to be true for the remainder of the paper and as such are not repeated again.
+% $\int_{a'}^{b'} f(x)\,d\,\widetilde{g}(x)$ and $\int_{a(y)}^{b(y)}f(x)~dx$ are not geometrically equivalent.
+% 
+% The theorems and definitions presented in this section impose much greater restrictions on $g(x)$ and $f(x)$ than that mentioned in the begining of Section. The functions 
+% $g(x)$, $\widetilde{g}(x)$ and $f(x)$ now also need to be differentiable and invertable. Moreover, the function $a(y)$ also needs to be differentiable and $a(0)$ needs to exist.
+% These assertions are deemed to be true for the remainder of the paper and as such are not repeated again.
 As will become clear later on, these restrictions limit the number of fractional integrals for which the geometric framework we propose in this paper can produce meaningful results.
@@
 \caption{This figure depicts the curves of $g_{10}^{\alpha}(\tau)$ and $h_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}$. The curves associated with $g$ are plotted using 
-solid lines, while the curves plotted wit h dashed lines are associated with $h$. The lighter the shade with which a curve is depicted, the larger the $\alpha$-value is that is associated with it.
+solid lines, while the curves plotted using dashed lines are associated with $h$. The lighter the shade with which a curve is depicted, the larger the $\alpha$-value is that is associated with it.
 }
@@
 \section{Converting into a Cavalieri integral}
+We can convert th
 

### 2019-10-08 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
started rewriting reverse conversion section

@@
 Substituting Equation~\eqref{eq:implies} into Equation~\eqref{eq:g_def2} eliminates
-both $a$ and $C$ from it. If we now solve for $a(y)$ we obtain:
+both $a$ and $C$ from it. If we then solve for $a(y)$ we obtain:
 \begin{equation}
@@
 \end{itemize}
+
+The above derivation implies that not every Riemann-Stieltjes integral can be converted into a Cavalieri integral.
+It, however, does tell us that a given Riemann-Stieltjes integral can be converted into another equivalent Riemann-Stieltjes interal that in turn can be converted into a Cavalieri integral.
+The steps that are required to perform the aformentioned conversions are described in the previous paragraph.
 

### 2019-10-09 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
made progress in reverse conversion

--- 2019-10-08 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
@@
 
-Consider the Riemann-Stieltjes integral $\int_{a'}^{b'} f(x)\,\widetilde{g}(x)$. Moreover, recall that 
+Consider the Riemann-Stieltjes integral $\int_{a'}^{b'} f(x)\,\widetilde{g}(x)$.
+Assume that $\widetilde{g}(x)$ is a differentiable and invertable real-valued function on $[a',b']$.
+Moreover, recall that
 \begin{equation}
@@
 \end{itemize}
+
+The above derivation implies that not every Riemann-Stieltjes integral can be converted into a Cavalieri integral.
+It, however, does tell us that a given Riemann-Stieltjes integral can be converted into another equivalent Riemann-Stieltjes integral.
+This newly obtained integral can then be converted into a Cavalieri integral.
+We explain this in more detail in Section~\ref{}.
+
+The theorems and definitions presented in this section impose much greater restrictions on $g(x)$ and $f(x)$ than that mentioned in the begining of Section. The functions 
+$g(x)$, and $f(x)$ now also need to be differentiable and invertable.
+Moreover, $a(0)$ must exist.
+These assertions are deemed to be true for the remainder of the paper and as such are not repeated again.
+As will become clear later on, these restrictions limit the number of fractional integrals for which the geometric framework we propose in this paper can produce meaningful results.
+This, however, does not diminish the importance of the proposed framework, since, for the integrals for which the framework does produce meaningful results, we gain valuable and novel insights.
 
@@
 
-Conversely, consider the following Riemann-Stieltjes integral:
+Recall from Section, that not every Riemann-Stieltjes integral $\int_{a'}^{b'} f(x) d\,\widetilde{g}(x)$ can directly be converted into a Cavalieri integral.
+We usually first need to convert it into an equivalent
+Riemann-Stieltjes integral $\int_{a'}^{b'} f(x) d\,g(x)$.
+The equivalent integral can then be converted into a Cavalieri integral.
+The former conversion is achieved by computing the scalar $C\in\mathbb{R}$.
+Once, $C$ is known the latter conversion follows trivially (see Section).
+
+As an example, consider the following Riemann-Stieltjes integral:
 \begin{equation}
@@
 \end{equation}
-We can convert this Riemann-Stieltjes integral into a Cavalieri integral via the following conversion steps (see Theorem~\ref{??} and the last paragraph of Section~\ref{??}):
+
+We can now compute the following (see Section~\ref{}):
 \begin{itemize}
@@
 \end{itemize}
-The integrals $\int_{\frac{1}{2}}^{2} x\,d2x$  and $\int_{1-y}^{4-y} x\,dx$ have the exact same geometric meaning, since $C=0$.
+The integrals $\int_{\frac{1}{2}}^{2} x\,d2x$  and $\int_{1-y}^{4-y} x\,dx$ are geometrically equivalent, since $C=0$.
 
@@
 \section{Converting into a Cavalieri integral}
-We can convert th
+It now follows from Section~\ref{} and Section~\ref{} that A direct consequence of Section and Section is that there exists a $C\in\mathbb{R}$ such that
 

### 2019-10-09 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
improved convert to Cavalieri section

@@
 \section{Converting into a Cavalieri integral}
-It now follows from Section~\ref{} and Section~\ref{} that A direct consequence of Section and Section is that there exists a $C\in\mathbb{R}$ such that
+Let $\widetilde{g}_t^{\alpha}(\tau) = \frac{\left \{t^{\alpha} - (t-\tau)^{\alpha} \right \}}{\Gamma(\alpha+1)}$. Since, 
+\begin{equation}
+_{a'}I_t^{\alpha}\,f(t) = \frac{1}{\Gamma(\alpha)}\int_{a'}^{t}(t-\tau)^{\alpha-1}f(\tau)~d\tau = \int_{a'}^{t} f(\tau)~dg_t^{\alpha}(\tau), 
+\end{equation}
+is a Riemann-Stieltjes integral we can convert it into a Cavalieri integral via the 
+following steps (see Section~\ref{}):
+\begin{itemize}
+ \item $a_t^{\alpha}(y) = f^{-1}(y) - \widetilde{g}_t^{\alpha}\circ f^{-1}(y)+ \widetilde{g}_t^{\alpha}(a')$.
+ \item $a = a_t^{\alpha}(0)$.
+ \item $C = a - \widetilde{g}_t^{\alpha}(a')$.
+ \item $g_t^{\alpha} = \widetilde{g}_t^{\alpha} + C$.
+ \item $b = g_t^{\alpha}(\tau)(b')$ and $b_t^{\alpha}(y) = a_t^{\alpha}(y) + (b-a)$.
+\end{itemize}
+It now follows that:
+\begin{equation}
+_{a'}I_t^{\alpha}\,f(t) =  \frac{1}{\Gamma(\alpha)}\int_{a'}^{t}(t-\tau)^{\alpha-1}f(\tau)~d\tau= \int_{a'}^{t} f(\tau)~dg_t^{\alpha}(\tau) = \int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)\,d\tau.
+\end{equation}
+
+Let $R_t^{\alpha}$ denote the region which is bounded by $a_t^{\alpha}(y)$, $b_t^{\alpha}(y)$, $f(t)$ and the $\tau$-axis. Moreover, let $A_{t}^{\alpha}$ denote the 
+area of $R_t^{\alpha}$.
+When we evaluate $_{a'}I_t^{\alpha}\,f(t)$ we obtain $A_{t}^{\alpha}$.
+Moreover, $R_t^{\alpha}$ can be decomposed into an infinite number of infinitesimals, each one of them being a translation of $a_t^{\alpha}(y)$.
+The shape of the aforementioned infenitesimals are non-static, since their shape depend on the value of $t$ and $\alpha$.
+Stated differently, we can approximate $A_{t}^{\alpha}$ via a Cavalieri sum, the shape of the integration strips used within this sum will be determined by $a_t^{\alpha}(y)$.
+In the limit this sum will approach $_{a'}I_t^{\alpha}\,f(t)$.
+The shape of the aforementioned integration strips are also non-static.
+Their shape is determined by the value of $t$ and $\alpha$.
+These assertions are all direct consequences of Eq ??.
 

### 2019-10-10 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
added examples --- still needs loads of work

@@
  % \usepackage{upref}
+ \usepackage{xfrac}
 %%%%%%%%%%%%%%%%%%%%
@@
 This newly obtained integral can then be converted into a Cavalieri integral.
-We explain this in more detail in Section~\ref{}.
+We explain this in more detail in Section~\ref{} via an example.
 
@@
 \end{equation}
-Please note that in this paper from this point going forward our variable of integration will be $\tau$ instead of $x$.
-It is of our opinion that this notational change improves the readability of the paper (if $\tau$ is our variable of integration then it makes sense to choose $t$ to denote our upper integration limit in Eq.~\ref{??}).
+Please note that in this paper from this point onwards our variable of integration will be $\tau$ instead of $x$.
+It is of our opinion that this notational change improves the readability of the paper (if $\tau$ is our variable of integration then it makes sense to choose $t$ as our upper integration limit).
 If we apply the above operator in a repetitive manner to $f$ we obtain the $n$th antiderivative of $f$ based at $a'$:
@@
 
-Let $R_t^{\alpha}$ denote the region which is bounded by $a_t^{\alpha}(y)$, $b_t^{\alpha}(y)$, $f(t)$ and the $\tau$-axis. Moreover, let $A_{t}^{\alpha}$ denote the 
+The assertions below all follow from Eq ??.
+Let $R_t^{\alpha}$ denote the region which is bounded by $a_t^{\alpha}(y)$, $b_t^{\alpha}(y)$, $f(t)$ and the $\tau$-axis.
+Moreover, let $A_{t}^{\alpha}$ denote the
 area of $R_t^{\alpha}$.
@@
 Their shape is determined by the value of $t$ and $\alpha$.
-These assertions are all direct consequences of Eq ??.
+
+\section{Examples}
+Consider the following fractional integral:
+\begin{equation}
+\label{eq:ex1_raw}
+_0I_t^{\alpha} f(t) = \frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \frac{1}{\Gamma(\alpha)}\int_0^t \tau(t-\tau)^{\alpha-1}~d\tau. 
+\end{equation}
+The function $f(t) = t$ is depicted in Fig.~\ref{fig:geo1}. Let us first convert 
+the above integral into a Riemann-Stieltjes integral (see Section~\ref{??}):
+\begin{equation}
+_0I_t^{\alpha} f(t)=\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \int_0^t f(\tau)~dg_t^{\alpha}(\tau). 
+\end{equation}
+We can now convert the above Riemann-Stieltjes integral into a Cavalieri integral (see Section~\ref{??}):
+\begin{equation}
+\label{eq:ex1}
+_0I_t^{\alpha} f(t) = \int_0^t f(\tau)~dg_t^{\alpha}(\tau)=\int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau,
+\end{equation}
+with $a_t^{\alpha}(y) = y - \frac{t^{\alpha}-(t-y)^{\alpha}}{\Gamma(\alpha+1)}$ and $b_t^{\alpha}(y) = a_t^{\alpha}(y) + \frac{t^{\alpha}}{\Gamma(\alpha+1)}$.
+Note, it turns out that for this example $a=a'=C=0$.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.75\textwidth]{geo_int1.pdf}
+\caption{The non-static non-rectangular sum-based geometric interpretation of Eq.~\eqref{eq:ex1_raw}.}
+\label{fig:geo1}
+\end{figure}
+
+% \noindent
+% Since Eq.~\eqref{eq:ex1}, is a Cavalieri integral it has a known geometric interpretation (see Fig.~\ref{fig:caval2}).
+It can be interpreted as the area obtained by summing together the areas of an infinite
+% number of infinitesimals whose shape is determined by $\alpha$ and $t$, i.e.
+these infinitesimals have to be translations of $b_t^{\alpha}(y)$.
+The geometric interpretation of Eq.~\eqref{eq:ex1_raw} is, therefore, non-static as it depends on the value of $\alpha$ and $t$.
+% There is one thing, however, which remains unclear: in what way do $\alpha$ and $t$ affect the shape of the aforementioned infinitesimals, i.e.
+how does the value of $\alpha$ and $t$ affect the shape of $b_t^{\alpha}(y)$.
+% We will answer this question by working through a detailed example.\\
+
+%using two basic steps.
+First off, we will fix the value of $\alpha$ and $t$ in Eq.~\eqref{eq:ex1} and then depict $b_t^{\alpha}(y)$.
+We will then explore how varying the value of $\alpha$ and $t$ in Eq.~\eqref{eq:ex1} affects the shape $b_t^{\alpha}(y)$.\\
+%We know that a Cavalieri integral can be interpreted as the area which is obtained by summing together the area associated with an infinite number of non-rectangular infinitesimals whose shape 
+%is determined by the integration limits of the Cavalieri integral. Note that neither $g_t^{\alpha}(\tau)$ nor $a_t^{\alpha}(y)$ are static functions, 
+%they depend on the value of $\alpha$ and $t$.
+This implies that a fractional integral of order $\alpha$ and extent $t$ can be interpeted as the area obtained by summing together the area associated with an infinite number of infinitesimals whose
+%shape is determined by $\alpha$ and $t$, i.e. the geometric interpretation of Eq.~\eqref{eq:ex1_raw} is non-static as it depends on the value of $\alpha$ and $t$.
+
+\noindent
+If we set the value of $\alpha$ to $\sfrac{4}{5}$ and the value of $t$ to 10 in Eq.~\eqref{eq:ex1} we obtain:
+\begin{equation}
+\label{eq:ex1_specific}
+_0I_{10}^{\sfrac{4}{5}} f(t) = \int_{a_{10}^{\sfrac{4}{5}}(y)}^{b_{10}^{\sfrac{4}{5}}(y)} f(\tau)~d\tau = A_{10}^{\sfrac{4}{5}}. 
+\end{equation}
+Let $R_{10}^{\sfrac{4}{5}}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{10}^{\sfrac{4}{5}}(y)$.
+The region $R_{10}^{\sfrac{4}{5}}$ is depicted in the right-most panel of Fig.~\ref{fig:geo1}.
+It is the largest of all the regions depicted in the right-most panel of Fig.~\ref{fig:geo1}.
+Moreover, let $A_{10}^{\sfrac{4}{5}}$ denote the area of $R_{10}^{\sfrac{4}{5}}$.
+When we evaluate Equation~\ref{eq:ex1_specific} we obtain $A_{10}^{\sfrac{4}{5}}$ (see Section~\ref{??}).
+Furthermore, note that dashed grey curves in the right-most panel of Fig.~\ref{fig:geo1} are translations of $b_{10}^{\sfrac{4}{5}}(y)$.\\
+
+% We can approximate the area of $R_{10}^{\sfrac{4}{5}}$ by summing together the area of $n$ equal width non-rectangular integration strips that inscribe $R_{10}^{\sfrac{4}{5}}$, i.e. we can 
+% construct a Cavalieri sum (see Eq.~\eqref{eq:cav_sum}). Note, the sides of the non-rectangular integration strips we use in this approximation have to be translations of $b_{10}^{\sfrac{4}{5}}(y)$.
+% If we take the limit of the aforementioned sum as $n\rightarrow \infty$ we approach the Cavalieri integral in Eq.~\eqref{eq:ex1_specific}, i.e. $A_{10}^{\sfrac{4}{5}}$.  
+% Eq.~\eqref{eq:ex1_specific}, therefore, implies that the region $R_{10}^{\sfrac{4}{5}}$ is made up 
+% of an infinite number of non-rectangular infinitesimals; all of them being translations of $b_{10}^{\sfrac{4}{5}}(y)$.
+Note, the right-most curve depicted in the right-most panel of Fig.~\ref{fig:geo1} is $b_{10}^{\sfrac{4}{5}}(y)$.
+Moreover, the special case in which we approximate $A_{10}^{\sfrac{4}{5}}$ using five equal width non-rectangular integration strips is depicted in the right-most panel of Fig.~\ref{fig:geo1}.
+% The sides of the aforementioned five integration strips are depicted in Fig.~\ref{fig:geo1} using dashed lines.
+Let, $\mathcal{B}_{\mathsf{T}}^{\sfrac{4}{5}}=\{b_{10}^{\sfrac{4}{5}}(y)-c|c\in(\mathsf{T}-2)\}$ with $\mathsf{T}=\{2,4,6,8,10\}$.\\
+
+%We have thus verified that we can employ the Cavalieri integral in Eq.~\eqref{eq:ex1_specific} to compute $A_{10}^{\sfrac{4}{5}}$ from first principles.
+%Let $\mathsf{B}_{10}^{\sfrac{4}{5}}$ denote the set containing these dashed curves.
+%We can, therefore, interpet Eq.~\eqref{}  The region $R_{10}^{\sfrac{4}{5}}$ is, therefore, made up 
+%of an infinite number of non-rectangular infinitesimals; all of them being translations of $b_{10}^{\sfrac{4}{5}}(y)$.
+
+\noindent
+Let $\mathsf{T}=\{2,4,6,8,10\}$.
+Varying both $\alpha$ and $t$ results in Eq.~\eqref{eq:ex1}.
+In contrast with Eq.~\eqref{eq:ex1_specific}, Eq.~\eqref{eq:ex1} can be associated with more than one region.
+Let $R_{t}^{\alpha}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{t}^{\alpha}(y)$. Note that $b_{t}^{\alpha}(y)$ forms the 
+right-most edge of $R_{t}^{\alpha}$.
+Moreover, let $A_{t}^{\alpha}$ denote the area of $R_{t}^{\alpha}$ and let $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}=\{R_t^{\alpha}|t\in\mathsf{T},~\alpha\in\mathsf{A}\}$.
+When we evaluate Eq.~\eqref{eq:ex1} we obtain $A_{t}^{\alpha}$ (see Section~\ref{??}).
+The regions in the set $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}$ are depicted in Fig.~\ref{fig:geo1}.
+The regions that are depicted in each of the panels of Fig.~\ref{fig:geo1} were generated by varying $t$, whilst keeping the value of $\alpha$ fixed.
+The title of each panel indicates which $\alpha$-value was used to generate the regions depicted in each panel.
+The only difference between the regions located in each
+panel is their right edges. The right edges of the regions in each panel are depicted using varying shades of gray. The lighter the shade with which an edge is depicted, 
+the larger the $t$-value is that is associated with it.\\
+
+\noindent
+As mentioned in Section~\ref{}, Eq.~\eqref{eq:ex1} implies that we can assume that each of the regions depicted in Fig.~\ref{fig:geo1} are made up of an infinite number of infinitesimals.
+The infinitesimals that make up the regions in Fig.~\ref{fig:geo1} are translations of each region's right edge.
+The following observations can now be made by inspecting Fig.~\ref{fig:geo1}:
+\begin{description}
+ \item[Effect of $\alpha$] the gray-tinted solid curves depicted in the different panels of Fig.~\ref{fig:geo1} are not equal to one another, i.e.
+$b_{t}^{\alpha_1}(y)\neq b_{t}^{\alpha_2}(y)$ when $\alpha_1\neq\alpha_2$.
+ \item[Effect of $t$] The dashed gray curves and the solid gray-tinted curves in the right-most panel are not equal to one another.
+The gray-tinted solid curves depicted in each of the panels of Fig.~\ref{fig:geo1} are, therefore, not translations of one another.
+\end{description}
+
+We can therefore draw the following conclusion: the value of both $\alpha$ and $t$ alters the shape of the infinitesimals that make up the regions in Fig.~\ref{fig:geo1}.
+Interestingly, the effect of $\alpha$ on the shape of the infinitesimals that make up the regions depicted in Fig.~\ref{fig:geo1} is larger than the effect that $t$ has on their shape.
+The curves associated with the infinitesimals obtained by varying $t$, whilst keeping the value of $\alpha$ fixed are very similar in nature and there exists a high degree of correlation between the aforementioned curves (if their
+sizes are ignored).
+The curves associated with the infinitesimals obtained by varying $\alpha$, whilst keeping the value of $t$ fixed are quite different from one another (the aforementioned curves are not correlated).\\
+
+%In the case of $\alpha$: the gray-tinted solid curves depicted in each panel are not equal to one-another.
+Similarly, in the case of $t$: the dashed gray curves and the solid gray-tinted curves in the right-most panel are not equal to one-another, i.e.$\mathsf{B}_T^{\alpha}\neq\mathcal{B}_T^{\alpha}$.
+
+\begin{table}[h!]
+\centering
+\caption{Curves obtained by evaluating Eq.~\eqref{eq:ex1} and Eq.~\eqref{eq:ex2} for all $\alpha\in \mathsf{A}$ using either Eq.~\eqref{eq:rs} or Eq.~\eqref{eq:option2}.}
+\label{tab:eval}
+\begin{tabular}{||c|| c| c||} 
+ \hline
+ $\alpha$ & $\frac{1}{\Gamma(\alpha)}\int_0^t \tau(t-\tau)^{\alpha-1}~d\tau$ & $\frac{1}{\Gamma(\alpha)}\int_0^t \sqrt{\tau}(t-\tau)^{\alpha-1}~d\tau$ \\[0.5ex]
+ \hline\hline
+ \rule{0pt}{2.5ex}
+ $0$ & $t$ & $\sqrt{t}$  \\  
+ \rule{0pt}{2.5ex}
+ $0.2$ & $\frac{25}{6\Gamma(\frac{1}{5})} t^{\sfrac{6}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{17}{10})} t^{\sfrac{7}{10}}$  \\ 
+ \rule{0pt}{2.5ex}
+ $0.4$ & $\frac{25}{14\Gamma(\frac{2}{5})} t^{\sfrac{7}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{19}{10})} t^{\sfrac{9}{10}}$  \\
+ \rule{0pt}{2.5ex}
+ $0.6$ & $\frac{25}{24\Gamma(\frac{3}{5})} t^{\sfrac{8}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{21}{10})} t^{\sfrac{11}{10}}$  \\ 
+ \rule{0pt}{2.5ex}
+ $0.8$ & $\frac{25}{36\Gamma(\frac{4}{5})} t^{\sfrac{9}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{23}{10})} t^{\sfrac{13}{10}}$  \\ 
+ \rule{0pt}{2.5ex}
+ $1$ & $\frac{1}{2}t^2$  & $\frac{2}{3}t^{\sfrac{3}{2}}$  \\ [1ex]
+ \hline
+ \end{tabular}
+\end{table}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.75\textwidth]{func_eval1.eps}
+\caption{Depicts the curves which are obtained by evaluating Eq.~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ using either Eq.~\eqref{eq:rs} or Eq.~\eqref{eq:option2}.}
+\label{fig:eval1}
+\end{figure}
+
+\noindent
+If we evaluate the integral in Eq.~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ (using either Eq.~\eqref{eq:rs} or Eq.~\eqref{eq:option2}) we obtain the curves in the 
+left-most column of Table~\ref{tab:eval}. These curves are depicted in Fig.~\ref{fig:eval1}.
+The area of the regions depicted in Fig.~\ref{fig:geo1} are also plotted in Fig.~\ref{fig:eval1} using circular markers.
+As expected, the circular markers in Fig.~\ref{fig:eval1} that correspond to the areas of the regions in Fig.~\ref{fig:eval1}
+associated with a particular choice of $\alpha$ (i.e.
+regions depicted in a particular panel of Fig.~\ref{fig:geo1}) fall on the curve in Fig.~\ref{fig:eval1}; associated with the same choice of $\alpha$.
+Moreover, note that we have adopted the
+same coloring scheme in Fig.~\ref{fig:geo1} and Fig.~\ref{fig:eval1}.
+Using the same coloring scheme in both figures makes it clear which of the area values in Fig.~\ref{fig:eval1} can be associated with which regions in Fig.~\ref{fig:geo1}.
+To summarize, Fig.~\ref{fig:geo1}, therefore, depicts a non-static non-rectangular infinitesimal-based geometric interpretation of Eq.~\eqref{eq:ex1}.
+Moreover, Fig.~\ref{fig:eval1} corroborates this geometric interpretation.\\
+
+\noindent
+Let us now consider a different fractional integral:
+\begin{equation}
+\label{eq:ex2}
+\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \frac{1}{\Gamma(\alpha)}\int_0^t \sqrt{\tau}(t-\tau)^{\alpha-1}~d\tau. 
+\end{equation}
+The non-static non-rectangular infinitesimal-based geometric interpretation associated with Eq.~\eqref{eq:ex1} is depicted in Fig.~\ref{fig:geo2}. 
+If we evaluate the integral in Eq.~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ we obtain the curves in the right-most column of Table~\ref{tab:eval}. 
+These curves are depicted in Fig~\ref{fig:eval2}.
+The validity of the non-static non-rectangular infinitesimal-based geometric interpretation depicted in Fig.~\ref{fig:geo2} is corroborated by Fig.~\ref{fig:eval2}.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.75\textwidth]{geo_int2.eps}
+\caption{The non-static non-rectangular sum-based geometric interpretation of Eq.~\eqref{eq:ex2}.}
+\label{fig:geo2}
+\end{figure}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.75\textwidth]{func_eval2.eps}
+\caption{Depicts the curves which are obtained by evaluating Eq.~\eqref{eq:ex2} for all $\alpha\in \mathsf{A}$ using either Eq.~\eqref{eq:rs} or Eq.~\eqref{eq:option2}.}
+\label{fig:eval2}
+\end{figure}
 

### 2019-10-16 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
added extra evaluation section
starting to make some real progress with the paper

@@
 \begin{equation}
-_{a'}I_t^{\alpha}\,f(t) = \frac{1}{\Gamma(\alpha)}\int_{a'}^{t}(t-\tau)^{\alpha-1}f(\tau)~d\tau = \int_{a'}^{t} f(\tau)~dg_t^{\alpha}(\tau), 
+_{a'}I_t^{\alpha}\,f(t) = \frac{1}{\Gamma(\alpha)}\int_{a'}^{t}(t-\tau)^{\alpha-1}f(\tau)~d\tau = \int_{a'}^{t} f(\tau)~d\,\widetilde{g}_t^{\alpha}(\tau), 
 \end{equation}
@@
 \label{eq:g_rl}
-g_t^{\alpha}(\tau) = \frac{\left \{t^{\alpha} - (t-\tau)^{\alpha} \right \}}{\Gamma(\alpha+1)} + C. 
+\widetilde{g}_t^{\alpha}(\tau) = \frac{\left \{t^{\alpha} - (t-\tau)^{\alpha} \right \}}{\Gamma(\alpha+1)}. 
 \end{equation}
-and $C\in\mathbb{R}$. Moreover, the function $g_t^{\alpha}(\tau)$ is invertable. Its inverse is:
+Moreover, the function $\widetilde{g}_t^{\alpha}(\tau)$ is invertable. Its inverse is:
 \begin{equation}
-h_t^{\alpha}(\tau) = t - \sqrt[\alpha]{t^{\alpha} - \Gamma(\alpha+1)(\tau-C)}.
+\widetilde{h}_t^{\alpha}(\tau) = t - \sqrt[\alpha]{t^{\alpha} - \Gamma(\alpha+1)(\tau)}.
 \end{equation}
 
-The function $g_t^{\alpha}$ is invertable, since $\frac{d g_t^{\alpha}}{d\tau}=\frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)} > 0$ for $\tau\in(-\infty,t]$.
+The function $\widetilde{g}_t^{\alpha}$ is invertable, since $\frac{d \widetilde{g}_t^{\alpha}}{d\tau}=\frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)} > 0$ for $\tau\in(-\infty,t]$.
 
@@
 \noindent
-Let $\mathsf{A} = \{0,0.2,0.4,0.6,0.8,1\}$. The analytic expressions of $g_{10}^{\alpha}(\tau)$ and $h_{10}^{\alpha}(\tau)$ are presented in Table~\ref{tab:gandh} for $\alpha\in\mathsf{A}$. 
+Let $\mathsf{A} = \{0,0.2,0.4,0.6,0.8,1\}$.
+The analytic expressions of $\widetilde{g}_{10}^{\alpha}(\tau)$ and $\widetilde{h}_{10}^{\alpha}(\tau)$ are presented in Table~\ref{tab:gandh} for $\alpha\in\mathsf{A}$.
 The expressions in Table~\ref{tab:gandh} are depicted in Fig~\ref{fig:gandh}.
@@
  \centering
- \caption{The analytic expressions of $g_{10}^{\alpha}(\tau)$ and $h_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}$. The expressions in this table are depicted in Fig~\ref{fig:gandh}.}
+ \caption{The analytic expressions of $\widetilde{g}_{10}^{\alpha}(\tau)$ and $\widetilde{h}_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}$.
+The expressions in this table are depicted in Fig~\ref{fig:gandh}.}
  \label{tab:gandh}
@@
  \hline 
- $\alpha$ & $g_{10}^{\alpha}(\tau)$ & $h_{10}^{\alpha}(\tau)$ \\ [0.5ex] 
+ \rule{0pt}{3ex}
+ $\alpha$ &  $\widetilde{g}_{10}^{\alpha}(\tau)$ & $\widetilde{h}_{10}^{\alpha}(\tau)$ \\
  \hline\hline
@@
 \includegraphics[width=0.75\textwidth]{gh.pdf}
-\caption{This figure depicts the curves of $g_{10}^{\alpha}(\tau)$ and $h_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}$. The curves associated with $g$ are plotted using 
-solid lines, while the curves plotted using dashed lines are associated with $h$. The lighter the shade with which a curve is depicted, the larger the $\alpha$-value is that is associated with it.
-}
+\caption{This figure depicts the curves of $\widetilde{g}_{10}^{\alpha}(\tau)$ and $\widetilde{h}_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}$.
+The curves associated with $\widetilde{g}$ are plotted using solid lines, while the curves plotted using dashed lines are associated with $\widetilde{h}$.
+The lighter the shade with which a curve is depicted, the larger the $\alpha$-value is that is associated with it.}
 \label{fig:gandh}
@@
 Podlubny's interpretation of fractional integrals requires the addition of an extra dimension.
-Consider the axis $\tau$, $g_t^{\alpha}$ and $f(\tau)$.
-Podlubny suggests that we build a ``fence'' in $(\tau,g_t^{\alpha},f)$-space.
-The base of the aforementioned fence is geiven by the curve $(\tau,g_t^{\alpha}(\tau),0)$, while its height is determined by $(\tau,g_t^{\alpha}(\tau),f(\tau))$.
-The
-``shadow'' of this fence, i.e. the area under the curve which is obtained by 
-projecting this fence onto the $gf$- plane corresonds to the value which is obtained when Eq is evaluated. As an example, the geometric interpretation so obtained for 
-the integrand $f(t)=\sqrt{t}$ is depicted in Figure~\ref{}.
+Consider the axis $\tau$, $\widetilde{g}_t^{\alpha}$ and $f(\tau)$.
+Podlubny suggests that we build a ``fence'' in $(\tau,\widetilde{g}_t^{\alpha},f)$-space.
+The base of the aforementioned fence is geiven by the curve $(\tau,\widetilde{g}_t^{\alpha}(\tau),0)$, while its height is determined by $(\tau,\widetilde{g}_t^{\alpha}(\tau),f(\tau))$.
+The ``shadow'' of this fence, i.e.
+the area under the curve which is obtained by projecting this fence onto the $\widetilde{g}f$-plane corresonds to the value which is obtained when Eq is evaluated.
+As an example, the geometric interpretation so obtained for the integrand $f(t)=\sqrt{t}$ is depicted in Figure~\ref{}.
 
@@
 \section{Converting into a Cavalieri integral}
-Let $\widetilde{g}_t^{\alpha}(\tau) = \frac{\left \{t^{\alpha} - (t-\tau)^{\alpha} \right \}}{\Gamma(\alpha+1)}$. Since, 
+Recall that,
 \begin{equation}
-_{a'}I_t^{\alpha}\,f(t) = \frac{1}{\Gamma(\alpha)}\int_{a'}^{t}(t-\tau)^{\alpha-1}f(\tau)~d\tau = \int_{a'}^{t} f(\tau)~dg_t^{\alpha}(\tau), 
+_{a'}I_t^{\alpha}\,f(t) = \frac{1}{\Gamma(\alpha)}\int_{a'}^{t}(t-\tau)^{\alpha-1}f(\tau)~d\tau = \int_{a'}^{t} f(\tau)~d\,\widetilde{g}_t^{\alpha}(\tau). 
 \end{equation}
-is a Riemann-Stieltjes integral we can convert it into a Cavalieri integral via the 
-following steps (see Section~\ref{}):
+Furthermore, we also have that (see Theorem~\ref{}):
+\begin{equation}
+\int_{a'}^{t} f(\tau)~d\,g_t^{\alpha}(\tau) = \int_{a'}^{t} f(\tau)~d\,\widetilde{g}_t^{\alpha}(\tau),  
+\end{equation}
+with $g_t^{\alpha}(\tau) = \widetilde{g}_t^{\alpha}(\tau) + C$ and $C\in\mathbb{R}$. 
+Recall, when we want to convert a Riemann-Stieltjes integral into a Cavalieri integral we normally first need to convert the Riemann-Stieltjes integral into an equivalent 
+Riemann-Stieltjes integral by computing the constant $C$.
+This latter integral can then be converted into a Cavalieri integral.
+The detail steps that are needed to perform this conversion in the case of Eq is presented below (see Section~\ref{}):
 \begin{itemize}
@@
  \item $g_t^{\alpha} = \widetilde{g}_t^{\alpha} + C$.
- \item $b = g_t^{\alpha}(\tau)(b')$ and $b_t^{\alpha}(y) = a_t^{\alpha}(y) + (b-a)$.
+ \item $b = g_t^{\alpha}(b')$ and $b_t^{\alpha}(y) = a_t^{\alpha}(y) + (b-a)$.
 \end{itemize}
@@
 
-The assertions below all follow from Eq ??.
+The assertions given below all follow from Eq ??.
 Let $R_t^{\alpha}$ denote the region which is bounded by $a_t^{\alpha}(y)$, $b_t^{\alpha}(y)$, $f(t)$ and the $\tau$-axis.
-Moreover, let $A_{t}^{\alpha}$ denote the
-area of $R_t^{\alpha}$.
+Moreover, let $A_{t}^{\alpha}$ denote the area of $R_t^{\alpha}$.
 When we evaluate $_{a'}I_t^{\alpha}\,f(t)$ we obtain $A_{t}^{\alpha}$.
@@
 Their shape is determined by the value of $t$ and $\alpha$.
+
+\section{Evaluating}
+\noindent
+Let $h_t^{\alpha}(\tau)$ be equal to the inverse of $g_t^{\alpha}(\tau)$.
+Interestingly, Eq.~\eqref{eq:main_cav} implies that we can use $h_t^{\alpha}(\tau)$ to convert Eq.~\eqref{eq:cav} into the following Riemann integral:
+\begin{equation}
+\label{eq:option2}
+\int_{g_t^{\alpha}(a')}^{\frac{t^{\alpha}}{\Gamma(\alpha+1)}+C} f\circ h_{\alpha}^t (\tau) d\tau.  
+\end{equation}
+We can, therefore, evaluate Eq.~\eqref{eq:cav} in one of two ways: we can either evaluate Eq.~\eqref{eq:rs} or we can evaluate Eq.~\eqref{eq:option2}.
 
@@
 \begin{equation}
-_0I_t^{\alpha} f(t)=\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \int_0^t f(\tau)~dg_t^{\alpha}(\tau). 
+_0I_t^{\alpha} f(t)=\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \int_0^t f(\tau)~d\,\widetilde{g}_t^{\alpha}(\tau). 
 \end{equation}
+
 We can now convert the above Riemann-Stieltjes integral into a Cavalieri integral (see Section~\ref{??}):

### 2019-10-16 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
improved the fractional part of paper

@@
 \end{equation}
-The function $f(t) = t$ is depicted in Fig.~\ref{fig:geo1}. Let us first convert 
-the above integral into a Riemann-Stieltjes integral (see Section~\ref{??}):
-\begin{equation}
-_0I_t^{\alpha} f(t)=\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \int_0^t f(\tau)~d\,\widetilde{g}_t^{\alpha}(\tau). 
-\end{equation}
-
-We can now convert the above Riemann-Stieltjes integral into a Cavalieri integral (see Section~\ref{??}):
+The function $f(t) = t$ is depicted in Fig.~\ref{fig:geo1}. We can now convert the above fractional integral into a Cavalieri integral (see Section~\ref{??}):
 \begin{equation}
 \label{eq:ex1}
-_0I_t^{\alpha} f(t) = \int_0^t f(\tau)~dg_t^{\alpha}(\tau)=\int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau,
+_0I_t^{\alpha} f(t) = \int_0^t f(\tau)~d\,\widetilde{g}_t^{\alpha}(\tau)=\int_0^t f(\tau)~d\,g_t^{\alpha}(\tau)=\int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau,
 \end{equation}
-with $a_t^{\alpha}(y) = y - \frac{t^{\alpha}-(t-y)^{\alpha}}{\Gamma(\alpha+1)}$ and $b_t^{\alpha}(y) = a_t^{\alpha}(y) + \frac{t^{\alpha}}{\Gamma(\alpha+1)}$.
-Note, it turns out that for this example $a=a'=C=0$.
+with $a_t^{\alpha}(y) = y - \frac{t^{\alpha}-(t-y)^{\alpha}}{\Gamma(\alpha+1)}$, $b_t^{\alpha}(y) = a_t^{\alpha}(y) + \frac{t^{\alpha}}{\Gamma(\alpha+1)}$ and $C=0$.
+Note, that for this example $a'=a=0$.\\
 
@@
 When we evaluate Equation~\ref{eq:ex1_specific} we obtain $A_{10}^{\sfrac{4}{5}}$ (see Section~\ref{??}).
+The region $R_{10}^{\sfrac{4}{5}}$ is not bounded by $a_{10}^{\sfrac{4}{5}}(y)$, since $a'=a=0$.
 Furthermore, note that dashed grey curves in the right-most panel of Fig.~\ref{fig:geo1} are translations of $b_{10}^{\sfrac{4}{5}}(y)$.\\
@@
 right-most edge of $R_{t}^{\alpha}$.
+The region $R_{t}^{\alpha}$ is not bounded by $a_{t}^{\alpha}(y)$, since $a'=a=0$.
 Moreover, let $A_{t}^{\alpha}$ denote the area of $R_{t}^{\alpha}$ and let $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}=\{R_t^{\alpha}|t\in\mathsf{T},~\alpha\in\mathsf{A}\}$.
@@
 \end{equation}
-The non-static non-rectangular infinitesimal-based geometric interpretation associated with Eq.~\eqref{eq:ex1} is depicted in Fig.~\ref{fig:geo2}. 
+We can now convert the above fractional integral into a Cavalieri integral (see Section~\ref{}):
+\begin{equation}
+\label{eq:ex2_cav}
+_0I_t^{\alpha} f(t) = \int_0^t f(\tau)~d\,\widetilde{g}_t^{\alpha}(\tau)=\int_0^t f(\tau)~d\,g_t^{\alpha}(\tau)=\int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau,
+\end{equation}
+with $a_t^{\alpha}(y) = y^2 - \frac{t^{\alpha}-(t-y^2)^{\alpha}}{\Gamma(\alpha+1)}$, $b_t^{\alpha}(y) = a_t^{\alpha}(y) + \frac{t^{\alpha}}{\Gamma(\alpha+1)}$ and $C=0$.
+Note, that for this example $a'=a=0$.
+The non-static non-rectangular infinitesimal-based geometric interpretation associated with Eq.~\eqref{eq:ex1}, which we construct vby employing Eq, is depicted in Fig.~\ref{fig:geo2}.
 If we evaluate the integral in Eq.~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ we obtain the curves in the right-most column of Table~\ref{tab:eval}.

### 2019-10-16 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
improved article

@@
 Theorem~\ref{t:conv} tells us how to convert a Cavalieri integral into an equivalent Riemann or Riemann-Stieltjes integral. It, however, tells us nothing about the reverse 
-procedure, if we are given a Riemann-Stieltjes integral how do we convert it into a Cavalieri integral? As will become clear in the next few paragraphs, this reverse 
-conversion is non-trivial.
+procedure, if we are given a Riemann-Stieltjes integral how do we convert it into a Cavalieri integral?
 
@@
 \end{equation}
-Furthermore, a consequence of Theorem xx is that:
+Let $g(x) = \widetilde{g}(x) + C$. Assume that the real-valued constants $C$ and $a$ are unknown. Furthermore, note that (see Theorem xx):
 \begin{equation}
@@
 \end{equation}
-with $g(x) = \widetilde{g}(x) + C$ and $C\in\mathbb{R}$. It, therefore, seems impossible to compute $a(y)$ given $\widetilde{g}(x)$ as $C$ and $a$ are unknown to us a priori. However, 
+At first, it seems impossible to compute $a(y)$ given $\widetilde{g}(x)$ as $C$ and $a$ are unknown a priori. However, 
 \begin{equation}
@@
 \end{itemize}
-
+It now follows that 
+\begin{equation}
+\int_{a'}^{b'} f(x)d\,\widetilde{g}(x) = \int_{a'}^{b'} f(x)d\,g(x):=\int_{a(y)}^{b(y)}f(x)dx. 
+\end{equation}
 The above derivation implies that not every Riemann-Stieltjes integral can be converted into a Cavalieri integral.
-It, however, does tell us that a given Riemann-Stieltjes integral can be converted into another equivalent Riemann-Stieltjes integral.
-This newly obtained integral can then be converted into a Cavalieri integral.
-We explain this in more detail in Section~\ref{} via an example.
+It, however, does tell us that every Riemann-Stieltjes integral can be converted into an equivalent Riemann-Stieltjes integral, which in turn, can be converted into a Cavalieri integral.
+The latter Riemann-Stieltjes integral is obtained by computing the constant $C$.
+These concepts are clarified in Section~\ref{} via a worked out example.
 
@@
 It, however, seems much more straightforward to approximate the area of $R$ via non-overlapping non-rectangular integration strips that toghether inscribe $R$.
-This alternative approach
-will only succeed it the sides of the aforementioned integration strips are all tranlsations of the function $a(y)$.
+Moreover, the sides of the aforementioned integration strips need to be tranlsations of the function $a(y)$.
 
-Let us express this idea more formally. Let $(x_i^1)_{i=0}^{n}$ denote a partition on the $x$-axis, such that $a = x_0^1 < x_1^1 < \cdots < x_n^1 = b$, and $\Delta x_i^1 = x_{i+1}^1 - x_i^1$.
-We are now able to construct the following lower Cavalieri sum (Equation~\ref{eq:c_low}):
+Let us express this idea more formally.
+Let $(x_i^1)_{i=0}^{n}$ denote a partition on the $x$-axis, such that $a = x_0^1 < x_1^1 < \cdots < x_n^1 = b$, and $\Delta x_i^1 = x_{i+1}^1 - x_i^1$.
+We are now able to construct the following lower Cavalieri sum (see Equation~\ref{eq:c_low}):
 \begin{equation}
@@
 In the limit Eq.~\eqref{eq:cav_sum} approaches
-the Cavalieri integral (Definition~\ref{def:cav_integral}):
+the Cavalieri integral (see Definition~\ref{def:cav_integral}):
 \begin{equation}
@@
 It is, however, quite hard to evaluate the above integral directly. Fortunately, it is easy to convert a Cavalieri integral into an equivalent Riemann or Riemann-Stieltjes 
-integral by using the functions $h$ and $g$ (Theorem~\ref{t:conv}). Expressed mathematically:
+integral by using the functions $h$ and $g$ (see Theorem~\ref{t:conv}). Expressed mathematically:
 \begin{equation}
@@
 \end{equation}
-Moreover, $h=g^{-1}$ (Theorem~\ref{t:inv}). We can now evaluate the Cavalieri using one of two ways:
+Moreover, $h=g^{-1}$ (Theorem~\ref{t:inv}). We can now evaluate in one of two ways:
 \begin{equation}
@@
 Recall from Section, that not every Riemann-Stieltjes integral $\int_{a'}^{b'} f(x) d\,\widetilde{g}(x)$ can directly be converted into a Cavalieri integral.
-We usually first need to convert it into an equivalent
-Riemann-Stieltjes integral $\int_{a'}^{b'} f(x) d\,g(x)$.
-The equivalent integral can then be converted into a Cavalieri integral.
-The former conversion is achieved by computing the scalar $C\in\mathbb{R}$.
+We usually first need to convert it into an equivalent Riemann-Stieltjes integral $\int_{a'}^{b'} f(x) d\,g(x)$.
+The Riemann-Stieltjes integral so obtained can then be converted into a Cavalieri integral.
+The former conversion is achieved by computing the scalar $C$.
 Once, $C$ is known the latter conversion follows trivially (see Section).
@@
 \begin{equation}
-\int_{a'}^{b'} \,d\,\widetilde{g}(x) = \int_{\frac{1}{2}}^2 x\,d2x.
+\int_{a'}^{b'} \,d\,\widetilde{g}(x) = \int_{\frac{1}{2}}^2 x\,d[2x+1].
 \end{equation}
@@
  \item $a(y) = f^{-1}(y) - \widetilde{g}\circ f^{-1}(y)+ \widetilde{g}(a') = 1-y$.
- \item $a(0) = 1$.
- \item $C = a - \widetilde{g}(a') = 0$.
+ \item $a = a(0) = 1$.
+ \item $C = a - \widetilde{g}(a') = -1$.
  \item $g(x) = \widetilde{g}(x) + C = 2x$.
@@
 \end{itemize}
-The integrals $\int_{\frac{1}{2}}^{2} x\,d2x$  and $\int_{1-y}^{4-y} x\,dx$ are geometrically equivalent, since $C=0$.
+It now follows that:
+\begin{equation}
+\int_{a'}^{b'} f(x)d\,\widetilde{g}(x) = \int_{a'}^{b'} f(x)d\,g(x) := \int_{a(y)}^{b(y)} f(x)dx, 
+\end{equation}
+with $a(y) = 1-y$, $b(y) = 4-y$ and $C=-1$.
 
 \section{Left-sided Riemann-Liouville Fractional Integral}
-In this section we review the definition of the left-sided Riemann-Liouville fractional integral of order $\alpha$ (based at $a'$) \cite{laurent1884}. Let
+For the sake of completeness, let us review the definition of the left-sided Riemann-Liouville fractional integral of order $\alpha$ (based at $a'$) \cite{laurent1884}. Let
 \begin{equation}
@@
 \subsection{Converting into a Riemann-Stieltjes integral}
-Podlubny showed that the Left-sided Riemann-Liouville fractional integral can be rewritten as a Riemann-Stieltjes integral \cite{podlubny02}:
+Podlubny showed that the Left-sided Riemann-Liouville fractional integral can be converted into a Riemann-Stieltjes integral \cite{podlubny02}:
 
@@
 \section{Podlubny's Geometric Interpretation}
-Podlubny's interpretation of fractional integrals requires the addition of an extra dimension.
+Podlubny assigns a geometric meaning to the fractional integral in Eq by visualizing the equivalent Riemann-Stieltjes integral contained within the same equation.
 Consider the axis $\tau$, $\widetilde{g}_t^{\alpha}$ and $f(\tau)$.
 Podlubny suggests that we build a ``fence'' in $(\tau,\widetilde{g}_t^{\alpha},f)$-space.
-The base of the aforementioned fence is geiven by the curve $(\tau,\widetilde{g}_t^{\alpha}(\tau),0)$, while its height is determined by $(\tau,\widetilde{g}_t^{\alpha}(\tau),f(\tau))$.
+The base of the aforementioned fence is given by the curve $(\tau,\widetilde{g}_t^{\alpha}(\tau),0)$, while its height is determined by $(\tau,\widetilde{g}_t^{\alpha}(\tau),f(\tau))$.
 The ``shadow'' of this fence, i.e.
@@
 \caption{This figure depicts the visualization of $\frac{1}{\Gamma(\alpha)}\int_{0}^{t}(t-\tau)^{\alpha-1}\sqrt{\tau}~d\tau$ using the geometric framework proposed by Podlubny.
-As is indicated in the figure, the rows of the subfigure-grid are obtained by varying $\alpha$, while the columns of the subfigure-grid are obtained by varying $t$.
+As is indicated in the figure, the graphs contained in each row of the subfigure-grid are obtained by varying $\alpha$, while the graphs contained in each column of the subfigure-grid are obtained by varying $t$.
 The fence itstelf is depicted in green.
 The areas depicted in red (the shadow of the fence) correspond to the value obtained when $\frac{1}{\Gamma(\alpha)}\int_{0}^{t}(t-\tau)^{\alpha-1}\sqrt{\tau}~d\tau$ is evaluated.
-The surface which is obtained by extending the curve $f(\tau)$ and $g_t^{\alpha}(\tau)$ along the $g$ and $f$ direction is depicted in cyan and blue, respectively.
+The surface which is obtained by extending the curve $f(\tau)$ and $\widetilde{g}_t^{\alpha}(\tau)$ along the $\widetilde{g}$ and $f$ direction is depicted in cyan and blue, respectively.
 The intersection between the blue and cyan
-surfaces represents the curve that determines the height of the aforementioned fence (depicted as a dashed curve).   
+surfaces represents the curve that determines the height of the aforementioned fence (and is depicted as a dashed curve).   
 }
@@
 \end{equation}
-Furthermore, we also have that (see Theorem~\ref{}):
+Let $C\in\mathbb{R}$. Furthermore, note that (see Theorem~\ref{}):
 \begin{equation}
@@
 \end{equation}
-with $g_t^{\alpha}(\tau) = \widetilde{g}_t^{\alpha}(\tau) + C$ and $C\in\mathbb{R}$. 
-Recall, when we want to convert a Riemann-Stieltjes integral into a Cavalieri integral we normally first need to convert the Riemann-Stieltjes integral into an equivalent 
-Riemann-Stieltjes integral by computing the constant $C$.
+with $g_t^{\alpha}(\tau) = \widetilde{g}_t^{\alpha}(\tau) + C$. 
+Recall, if we wish to convert a Riemann-Stieltjes integral into a Cavalieri integral we normally first need to convert the given Riemann-Stieltjes integral into an equivalent 
+Riemann-Stieltjes integral by computing a value for $C$.
 This latter integral can then be converted into a Cavalieri integral.
-The detail steps that are needed to perform this conversion in the case of Eq is presented below (see Section~\ref{}):
+The steps that are required to perform this conversion in the case of Eq is presented below (see Section~\ref{}):
 \begin{itemize}
@@
 \begin{equation}
-_{a'}I_t^{\alpha}\,f(t) =  \frac{1}{\Gamma(\alpha)}\int_{a'}^{t}(t-\tau)^{\alpha-1}f(\tau)~d\tau= \int_{a'}^{t} f(\tau)~dg_t^{\alpha}(\tau) = \int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)\,d\tau.
+_{a'}I_t^{\alpha}\,f(t) =  \frac{1}{\Gamma(\alpha)}\int_{a'}^{t}(t-\tau)^{\alpha-1}f(\tau)~d\tau= \int_{a'}^{t} f(\tau)~dg_t^{\alpha}(\tau) := \int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)\,d\tau.
 \end{equation}
 
-The assertions given below all follow from Eq ??.
+The below assertion is a direct consequence of Eq ??.
 Let $R_t^{\alpha}$ denote the region which is bounded by $a_t^{\alpha}(y)$, $b_t^{\alpha}(y)$, $f(t)$ and the $\tau$-axis.
@@
 When we evaluate $_{a'}I_t^{\alpha}\,f(t)$ we obtain $A_{t}^{\alpha}$.
-Moreover, $R_t^{\alpha}$ can be decomposed into an infinite number of infinitesimals, each one of them being a translation of $a_t^{\alpha}(y)$.
+
+%Stated differently, we can approximate $_{a'}I_t^{\alpha}\,f(t)$ via a Cavalieri sum, the shape of the integration strips used within this sum will be determined by $a_t^{\alpha}(y)$.
+In the limit this sum approaches $_{a'}I_t^{\alpha}\,f(t)$.
+The value $_{a'}I_t^{\alpha}\,f(t)$ so obtained is equal to the area of $R_t^{\alpha}$.
+$R_t^{\alpha}$ can, therefore, be decomposed into an infinite number of infinitesimals, each one of them being a translation of $a_t^{\alpha}(y)$.
 The shape of the aforementioned infenitesimals are non-static, since their shape depend on the value of $t$ and $\alpha$.
-Stated differently, we can approximate $A_{t}^{\alpha}$ via a Cavalieri sum, the shape of the integration strips used within this sum will be determined by $a_t^{\alpha}(y)$.
-In the limit this sum will approach $_{a'}I_t^{\alpha}\,f(t)$.
-The shape of the aforementioned integration strips are also non-static.
-Their shape is determined by the value of $t$ and $\alpha$.
 
@@
 
-We can therefore draw the following conclusion: the value of both $\alpha$ and $t$ alters the shape of the infinitesimals that make up the regions in Fig.~\ref{fig:geo1}.
+The following can thus be concluded: the value of both $\alpha$ and $t$ alters the shape of the infinitesimals that make up the regions in Fig.~\ref{fig:geo1}.
 Interestingly, the effect of $\alpha$ on the shape of the infinitesimals that make up the regions depicted in Fig.~\ref{fig:geo1} is larger than the effect that $t$ has on their shape.

### 2019-10-16 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
added some new sections to article

@@
 Assume that $\widetilde{g}(x)$ is a differentiable and invertable real-valued function on $[a',b']$.
-Moreover, recall that
+Assume that the real-valued constants $C$ and $a$ are unknown.
+Assume further that $C$ is chosen so that the following expression is true:
+\begin{equation}
+g(x) := \widetilde{g}(x)+C, 
+\end{equation}
+where  
 \begin{equation}
@@
 \end{equation}
-Let $g(x) = \widetilde{g}(x) + C$. Assume that the real-valued constants $C$ and $a$ are unknown. Furthermore, note that (see Theorem xx):
+Assume that the real-valued constant $a$ is unknown Furthermore, note that (see Theorem xx):
 \begin{equation}
@@
 \end{equation}
+with $g(x) = \widetilde{g}(x)+C$. 
 At first, it seems impossible to compute $a(y)$ given $\widetilde{g}(x)$ as $C$ and $a$ are unknown a priori. However, 

### 2019-10-18 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
newest version

--- 2019-10-16 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
@@
 
- \title[VISUALIZATION OF FRACTIONAL INTEGRALS]{VISUALIZATION OF THE RIEMANN-LIOUVILLE FRACTIONAL INTEGRAL \\ [3pt] IN ``FCAA'' JOURNAL}
+ \title[VISUALIZATION OF FRACTIONAL INTEGRALS]{VISUALIZATION OF THE LEFT-SIDED RIEMANN-LIOUVILLE FRACTIONAL INTEGRAL \\ [3pt] IN ``FCAA'' JOURNAL}
  \author[\normalsize V. Kiryakova, S. Author]{\normalsize Virginia Kiryakova $^1$, Second Author $^2$}
@@
 %%%% Abstract %%%%%%%%%%%%%%%%%%%%%%%%%
- \begin{abstract}
-
-Text of the abstract. Text of the abstract. Text of the abstract.
-Text of the abstract. Text of the abstract. Text of the abstract.
-Text of the abstract. It should give a comprehensive idea about the
-paper's subject and the author's results. The Abstract (and the first 2 pages of the paper) will be
-available free at DeGryuter's website for the journal.
+ \begin{abstract}In this paper we present a novel geometric interpretation of the left-sided Riemann-Liouville fractional integral.
+We found that a Riemann-Liouville integral can be thought of as the area obtained by summing together the area of an infinite number of non-rectangular infinitesimals whose shape is determined by the integral's order of integration and its upper integration limit.
+This geometric interpretation is quite useful from a pedagogical perspective as it is very similar
+in nature to the geometric interpretation of the Riemann integral.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%% Section 1 %%%%%%%%%%%%%
-%\section{Introduction}\label{Sec:1}
+% %%%%%%%%%%%%%%%%%%%%%%%%%%% Section 1 %%%%%%%%%%%%%
+% %\section{Introduction}\label{Sec:1}
+% 
+% \section{First section of the paper}\label{sec:1}
+% 
+% \setcounter{section}{1}
+% \setcounter{equation}{0}\setcounter{theorem}{0}
+% 
+% 
+% Text ... (for details, see \cite{GasRah}, \cite{Rosbl}, \cite{Kir},
+% \cite{Moak}) ...
+% 
+% %%%% example of definition %%%%
+%  \begin{definition}\label{Def3}
+% Text of Definition~\ref{Def3}.
+%  \end{definition}
+% 
+%    \vspace*{-12pt} %%% example of subsection:
+%  \subsection{Preliminary results}\label{subsec:1.1}
+% 
+% %%%% example of theorem %%%%%%%%%%
+%  \begin{theorem}\label{Th1}
+% Text of Theorem~\ref{Th1} ....
+%  \end{theorem}
+% 
+%  \proof %%%%%%%%%%%%%
+%  Give here the proof of Theorem~\ref{Th1}. Example for
+% equation:
+% \begin{equation}\label{eq1}
+% ax^2+bx +c =0.
+% \end{equation}
+%  As seen by equation \eqref{eq1}, it is ...
+%  The proof follows from Ref. \cite{Moak}.
+%  \proofend %%%%%%%%%%
+% 
+% %%%% example of corollary %%%%
+%  \begin{corollary}\label{Cor2}
+% Text of Corollary~\ref{Cor2} ....
+%  \end{corollary}
+% 
+%  \proof
+%  Here comes the proof of Corollary~\ref{Cor2}.
+%  \proofend
+% 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \section{Second section of the paper}\label{sec:2}
+% 
+% \setcounter{section}{2}
+% \setcounter{equation}{0}\setcounter{theorem}{0}
+% 
+% 
+%  Text ... As seen in Section~\ref{sec:1}, the equation
+% (\ref{eq1}), $ a\neq 0$, has the solutions
+%  \begin{equation}\label{eq2}
+%  x_{1,2}= {\frac {-b \pm \sqrt{b^2-4ac}}{2a}}\,.
+%  \end{equation}
+% 
+%  %%% example of example %%%%%
+%  \begin{example}\label{Ex1}
+%  Let us take in (\ref{eq2}) ... Then, by Theorem~\ref{Th1}, ...
+%  \end{example}
+% 
+%  \begin{example}\label{Ex2}
+%  Under same conditions as in Example~\ref{Ex1}, we consider ...
+%  \end{example}
+% 
+% 
+% The figures should be input in the LaTeX file as eps-files, as below:
+% 
+% %%%%%%%%% example for figure %%%%%%%%%%%%%%%%%%%
+%   \begin{center}
+%   \includegraphics[scale=0.4]{figure.eps}
+%  % \hspace*{2cm}
+%  % \includegraphics[scale=0.7]{figure2.eps}
+% 
+%  \bigskip
+% 
+%   Figure 2.1: Control loop
+%   \end{center}
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+%  Often figures include texts or Latin, Greek etc. letters.
+%  We kindly ask the authors to take care that no texts fonts need to be embedded, by saving first the text as curves.
+%  Just in case, along with the obligatory eps-files, please send us also some alternative figures' files in  pdf-, jpg-, etc. format.
 
-\section{First section of the paper}\label{sec:1}
+\section{Introduction}
+%Leibniz, who is regarded by many scholars as the father of calculus, is credited with inventing the following notation: $\frac{d^n y}{d x^n}$. 
+%A natural question which arises when one inspects this notation is: Can $n$ be a non-integer value? L'Hospital phrased it differently: ``\emph{What if $n$ be a $\frac{1}{2}$?}''. 
+%In a letter Leibniz sent to L'Hospital, Leibniz comments on L'Hospital's question by making the following prophetic remark: ``\emph{This is an apparent paradox from which, one day, useful 
+%consequences will be drawn}'' \cite{ross77,machado14,machado17}.\\
 
-\setcounter{section}{1}
-\setcounter{equation}{0}\setcounter{theorem}{0}
+\noindent
+The mathematical discipline in which we study the extension of derivatives and integrals to non-integer orders is known as fractional calculus. Euler, Liouville and Riemann laid most 
+of the theoretical groundwork, which was needed to develop the field of fractional calculus \cite{davis59,euler1738,liouville1832,riemann1876,laurent1884}.
+Fractional calculus has now developed into a mature discipline \cite{machado14,machado17}.
+However, there is one aspect of the discipline which only started to develop fairly recently: its physical and geometric interpretability.
+At the first international conference on fractional calculus in
+New Haven (USA) (which took place in 1974) it was pointed out that literature lacked an acceptable geometric and physical interpretation of fractional calculus \cite{ross06}.
+Subsequently, the last few decades have seen
+a number of papers that attempt to rectify this.
+There now exist probabilistic interpretations \cite{stanislavsky04,machado03}, geometric interpretations \cite{adda97,tarasov16,podlubny02}, physical interpretations \cite{cioc16,rutman95, nigmatullin92, gomez14} and economic
+interpretations \cite{tarasova17} of fractional order integrals and differentials.\\
 
-Text ... (for details, see \cite{GasRah}, \cite{Rosbl}, \cite{Kir},
-\cite{Moak}) ...
+\noindent
+In this article we specifically focus on the geometric interpretation of fractional integrals.
+To be more specific, we present a novel geometric interpretation of the left-sided Riemann-Liouville fractional integral based at $a'$ \cite{laurent1884}.
+As we mentioned earlier, Riemann and Liouville played an important role in the development of fractional calculus. Their work was crucial in defining what is now known as 
+the Riemann-Liouville fractional integral \cite{laurent1884}.
+At this point in time the reader should be made aware of the fact that there exists many other accepted fractional integral definitions in the literature.
+We, however, deem these definitions to be beyond the scope of the current article and as such we do not discuss them any further in this work. Furthermore, the geometric interpretation 
+we present here is an extension of the geometric interpretation presented by Podlubny \cite{podlubny02}. Podlubny showed that a Riemann-Liouville fractional integral 
+can be converted into a Riemann-Stieltjes integral. Moreover, Grobler showed that a Riemann-Stieltjes integral can be interpreted as the area which is obtained by summing together 
+the area of an infinite number of non-rectangular infinitesimals, i.e.
+a Riemann-Stieltjes integral can be converted into a Cavalieri integral \cite{ackermann12,grobler19}.
+Combining these two ideas results in the following geometric
+interpretation: the Riemann-Liouville fractional integral can be interpreted as the area which is obtained by summing together the area of an infinite number of non-rectangular infinitesimals whose shape is determined by the order of integration $\alpha$ and the integration limit $t$.\\
 
-%%%% example of definition %%%%
- \begin{definition}\label{Def3}
-Text of Definition~\ref{Def3}.
- \end{definition}
+\noindent
+We start the paper by reviewing the definition of the Riemann-Stieltjes integral, the Cavalieri integral and the left-sided Riemann-Liouville fractional integral.
+We then present Podlubny's original geometric framework, followed by our novel geometric framework.
+We end the paper with two examples and a conclusion.
 
-   \vspace*{-12pt} %%% example of subsection:
- \subsection{Preliminary results}\label{subsec:1.1}
-
-%%%% example of theorem %%%%%%%%%%
- \begin{theorem}\label{Th1}
-Text of Theorem~\ref{Th1} ....
- \end{theorem}
-
- \proof %%%%%%%%%%%%%
- Give here the proof of Theorem~\ref{Th1}. Example for
-equation:
-\begin{equation}\label{eq1}
-ax^2+bx +c =0.
+\section{Riemann-Stieltjes integral}
+\label{sec:rs}
+\noindent
+Let $f$ and $g$ denote real-valued functions defined on a closed interval $[a',b']$ of the real line.
+We shall suppose that both $f$ and $g$ are bounded on $[a',b']$.
+Recall that the Riemann-Stieltjes integral is defined as follows \cite{bartle76}:
+\begin{equation}
+\label{eq:g_int2}
+\int_{a'}^{b'} f(x) dg(x) =  \lim_{n \rightarrow \infty}\sum_{i=0}^{n-1} f(x_i)[g(x_{i+1})-g(x_{i})], 
 \end{equation}
- As seen by equation \eqref{eq1}, it is ...
- The proof follows from Ref. \cite{Moak}.
- \proofend %%%%%%%%%%
-
-%%%% example of corollary %%%%
- \begin{corollary}\label{Cor2}
-Text of Corollary~\ref{Cor2} ....
- \end{corollary}
-
- \proof
- Here comes the proof of Corollary~\ref{Cor2}.
- \proofend
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Second section of the paper}\label{sec:2}
-
-\setcounter{section}{2}
-\setcounter{equation}{0}\setcounter{theorem}{0}
-
- Text ... As seen in Section~\ref{sec:1}, the equation
-(\ref{eq1}), $ a\neq 0$, has the solutions
- \begin{equation}\label{eq2}
- x_{1,2}= {\frac {-b \pm \sqrt{b^2-4ac}}{2a}}\,.
+with $(x_i)_{i=0}^n$ being arbitrary partition points on the $x$-axis. 
+The function $g$ is known as the integrator and if it is monotone increasing then it maps points in the interval $[a',b,]$ to the interval $[a,b]$, with $a = g(a')$ and $b = g(b')$.
+The integral in equation~\eqref{eq:g_int2} is hard to evaluate in its present form.
+If $g$ is differentiable, however, then it becomes trivial to
+evaluate a Riemann-Stieltjes integral due to the following identity:
+\begin{equation}
+\label{eq:rs_identity}
+\int_{a'}^{b'} f(x) dg(x) = \int_{a'}^{b'} f(x)g'(x)~dx.
 \end{equation}
 
- %%% example of example %%%%%
- \begin{example}\label{Ex1}
- Let us take in (\ref{eq2}) ... Then, by Theorem~\ref{Th1}, ...
- \end{example}
-
- \begin{example}\label{Ex2}
- Under same conditions as in Example~\ref{Ex1}, we consider ...
- \end{example}
-
-The figures should be input in the LaTeX file as eps-files, as below:
-
-%%%%%%%%% example for figure %%%%%%%%%%%%%%%%%%%
-  \begin{center}
-  \includegraphics[scale=0.4]{figure.eps}
- % \hspace*{2cm}
- % \includegraphics[scale=0.7]{figure2.eps}
-
- \bigskip
-
-  Fig. 2.1: Control loop
-  \end{center}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
- Often figures include texts or Latin, Greek etc. letters.
- We kindly ask the authors to take care that no texts fonts need to be embedded, by saving first the text as curves.
- Just in case, along with the obligatory eps-files, please send us also some alternative figures' files in  pdf-, jpg-, etc. format.
-
-\section{Riemann-Stieltjes integral}
-Let $f$ and $g$ denote real-valued functions defined on a closed interval $[a',b']$ of the real line.
-We shall suppose that both $f$ and $g$ are bounded on $[a',b']$.
-These assertions are assumed to be true throughout the paper and will not be repeated again.
-
-\begin{definition}
-Define a partition $\mathcal{P}$ of $[a',b']$ to be a set of points $x_0, x_1,\cdots,x_n$, 
-where $a' = x_0 \leq x_1 \leq \cdots \leq x_n = b'$. For each partition 
-$\mathcal{P}$ of $[a',b']$ write $\Delta g_k = g(x_k)-g(x_{k-1})$. Let 
-$M_k = \sup\{f(x),x_{k-1}\leq x \leq x_{k}\}$, $m_k = \inf\{f(x),x_{k-1}\leq x \leq x_{k}\}$, and set 
-\begin{equation}
-\label{ref:S_up}
-\mathcal{S}_U(\mathcal{P},f,g) = \sum_{k=1}^n M_k \Delta g_k, 
-\end{equation}
-and
-\begin{equation}
-\label{ref:S_low}
-\mathcal{S}_L(\mathcal{P},f,g) = \sum_{k=1}^n m_k \Delta g_k. 
-\end{equation}
-The sums in Eq.~\eqref{ref:S_up} and Eq.~\eqref{ref:S_low} are respectively called the the upper and lower Riemann-Stieltjes sums.
-If there is a unique number $I$ that satisfies the inequality $\mathcal{S}_L(\mathcal{P},f,g)\leq I \leq \mathcal{S}_U(\mathcal{P},f,g)$ for all 
-partitions $P$ of $[a',b']$, then $f$ is Riemann integrable with respect to $g$ on $[a',b']$. Moreover, $I$ is called the Riemann-Stieltjes integral of $f$ from $a'$ to $b'$ and is denoted by
-\begin{equation}
-\int_{a'}^{b'} f(x) dg(x). 
-\end{equation}
-\end{definition}
-
-\begin{theorem}
-If the derivative $g'$ exists and is continuous on $[a',b']$ and if $f$ is integrable with respect to $g$ on $[a',b']$, then the following 
-Riemann and Riemann-Stieltjes integrals are equivalent
-\begin{equation}
-\int_{a'}^{b'} f(x) dg(x) = \int_{a'}^{b'} f(x)g'(x)dx.
-\end{equation}
-\end{theorem}
+% \begin{definition}
+% Define a partition $\mathcal{P}$ of $[a',b']$ to be a set of points $x_0, x_1,\cdots,x_n$, 
+% where $a' = x_0 \leq x_1 \leq \cdots \leq x_n = b'$. For each partition 
+% $\mathcal{P}$ of $[a',b']$ write $\Delta g_k = g(x_k)-g(x_{k-1})$. Let 
+% $M_k = \sup\{f(x),x_{k-1}\leq x \leq x_{k}\}$, $m_k = \inf\{f(x),x_{k-1}\leq x \leq x_{k}\}$, and set 
+% \begin{equation}
+% \label{ref:S_up}
+% \mathcal{S}_U(\mathcal{P},f,g) = \sum_{k=1}^n M_k \Delta g_k, 
+% \end{equation}
+% and
+% \begin{equation}
+% \label{ref:S_low}
+% \mathcal{S}_L(\mathcal{P},f,g) = \sum_{k=1}^n m_k \Delta g_k. 
+% \end{equation}
+% The sums in equation~\eqref{ref:S_up} and equation~\eqref{ref:S_low} are respectively called the the upper and lower Riemann-Stieltjes sums.
+% If there is a unique number $I$ that satisfies the inequality $\mathcal{S}_L(\mathcal{P},f,g)\leq I \leq \mathcal{S}_U(\mathcal{P},f,g)$ for all 
+% partitions $P$ of $[a',b']$, then $f$ is Riemann integrable with respect to $g$ on $[a',b']$. Moreover, $I$ is called the Riemann-Stieltjes integral of $f$ from $a'$ to $b'$ and is denoted by
+% \begin{equation}
+% \int_{a'}^{b'} f(x) dg(x). 
+% \end{equation}
+% \end{definition}
+% 
+% \begin{theorem}
+% If the derivative $g'$ exists and is continuous on $[a',b']$ and if $f$ is integrable with respect to $g$ on $[a',b']$, then the following 
+% Riemann and Riemann-Stieltjes integrals are equivalent
+% \begin{equation}
+% \int_{a'}^{b'} f(x) dg(x) = \int_{a'}^{b'} f(x)g'(x)dx.
+% \end{equation}
+% \end{theorem}
 
@@
 
+\noindent
 Ackerman et al. used the notion of non-rectangular integration strips to define the so called Cavalieri integral. The area of a non-rectangular 
 integration strip is calculated using Cavalieri's principle. Cavalieri's principle is stated below without proof:
+
 \begin{theorem}
-Suppose two regions in a plane are included between two parallel lines in that plane. If every line parallel to these
-two lines intersects both regions in line segments of equal length, then the two regions have equal areas. NEED CITATION
+Suppose two regions in a plane are included between two parallel lines in that plane.
+If every line parallel to these two lines intersects both regions in line segments of equal length, then the two regions have equal areas \cite{??}.
 \end{theorem}
+
 The definition of the Cavalieri integral is presented in Definition~\ref{def:cav_integral}.
-It is, however, our experience that Definition~\ref{def:cav_integral} is hard to assimilate if it is encounterd by a reader for the first time. We, therefore, encourage 
-readers who are not familiar with the Cavalieri integral to rather first read Section~\ref{??} instead.
-The reader who is not familiar with the Cavalieri integral should only refer back to the definitions
-presented in this section when things in Section~\ref{??} become unclear.
-Moreover, the definitions presented below were taken from [?].
-Furthermore, none of the theorems in this section are proved, the proofs can be found in [].
+It is, however, our experience that Definition~\ref{def:cav_integral} is hard to assimilate if it is encounterd by a reader for the first time.
+We, therefore, encourage readers who are not familiar with the Cavalieri integral to rather first read Section~\ref{sec:cav_integral_example} instead.
+The reader who is not familiar with the Cavalieri integral should only refer back to the definitions presented in this section when things in Section~\ref{sec:cav_integral_example} become unclear.
+Moreover, the definitions presented below were taken from \cite{??}.
+Furthermore, none of the theorems in this section are proved, the proofs can be found in \cite{??}.
 
@@
 
-Let $a(y)$ be a translational function with respect to a real--valued function $f(x)$ on the interval $[a,b]$.
+\noindent
+Let $a(y)$ be a translational function with respect to a function $f(x)$ on the interval $[a,b]$.
 Moreover, $b(y) = a(y) + (b-a)$.
@@
 \noindent
-The functions $h(x)$ and $g(x)$ are known as the transformation function and the inverse transformation function, respectively.
+The functions $h(x)$ and $g(x)$ are known as the transformation function and the inverse transformation function, respectively. Furthermore,
+\begin{equation}
+\label{eq:g_def}
+g(x) = x - a\circ f(x) + a 
+\end{equation}
+and
+\begin{equation}
+\label{eq:h_def}
+h(x) = g^{-1}(x). 
+\end{equation}
 
@@
 \end{equation}
-The sums in Eq.~\eqref{eq:c_up} and Eq.~\eqref{eq:c_low} are respectively called the the upper and lower Cavalieri sums.
+The sums in equation~\eqref{eq:c_up} and equation~\eqref{eq:c_low} are respectively called the the upper and lower Cavalieri sums.
 If there is a unique number $I$ that satisfies the inequality $\mathcal{C}_L(\mathcal{P}_1,f,h)\leq I \leq \mathcal{C}_U(\mathcal{P}_1,f,h)$ for all 
@@
 
+\noindent
 Note that the superscripts of the $x$-coordinates in the above definitions indicate to which partition, either $\mathcal{P}_1$ or $\mathcal{P}_2$, the $x$-coordinate in question belongs.
@@
 \begin{equation}
-\int_{a(y)}^{b(y)} f(x)\,dx = \int_a^b f\circ h(x)\,dx = \int_{a'}^{b'} f(x)\,dg(x),
+\int_{a(y)}^{b(y)} f(x)\,dx = \int_a^b f\circ h(x)\,dx = \int_{a'}^{b'} f(x)\,dg(x).
 \end{equation}
-with $g(x) = x-a\circ f(x) + a$ and $h(x) = g^{-1}(x)$.
 \end{theorem}
 
+\noindent
 Theorem~\ref{t:conv} tells us how to convert a Cavalieri integral into an equivalent Riemann or Riemann-Stieltjes integral. It, however, tells us nothing about the reverse 
-procedure, if we are given a Riemann-Stieltjes integral how do we convert it into a Cavalieri integral?
+procedure, if we are given a Riemann-Stieltjes integral how do we convert it into a Cavalieri integral?\\
 
+\noindent
 Consider the Riemann-Stieltjes integral $\int_{a'}^{b'} f(x)\,\widetilde{g}(x)$.
 Assume that $\widetilde{g}(x)$ is a differentiable and invertable real-valued function on $[a',b']$.
-Moreover, recall that
+How do we go about converting $\int_{a'}^{b'} f(x)\,\widetilde{g}(x)$ into a Cavalieri integral?
+Note that for all $K\in\mathbb{R}$ (see equation~\ref{eq:rs_identity}):
 \begin{equation}
-\label{eq:g_def2}
+\int_{a'}^{b'} f(x)\,d[\widetilde{g}(x)+K] = \int_{a'}^{b'}f(x)\,\widetilde{g}(x). 
+\end{equation}
+Furthermore, recall that
+\begin{equation}
+\label{eq:g_definition}
 g(x) = x - a\circ f(x) + a.
 \end{equation}
-Let $g(x) = \widetilde{g}(x) + C$. Assume that the real-valued constants $C$ and $a$ are unknown. Furthermore, note that (see Theorem xx):
-\begin{equation}
-\int_{a'}^{b'} f(x)\,dg(x) = \int_{a'}^{b'}f(x)\,\widetilde{g}(x), 
-\end{equation}
-At first, it seems impossible to compute $a(y)$ given $\widetilde{g}(x)$ as $C$ and $a$ are unknown a priori. However, 
+Moreover, let $C$ be a unique real-valued constant that satisfies: $g(x) := \widetilde{g}(x)+C$.
+At first, it does not seem possible to compute $a(y)$ (perform the required conversion) given only $\widetilde{g}(x)$ as $C$ and $a$ are unknown a priori.
+However,
 \begin{equation}
@@
 \end{equation}
-Substituting Equation~\eqref{eq:implies} into Equation~\eqref{eq:g_def2} eliminates
-both $a$ and $C$ from it. If we then solve for $a(y)$ we obtain:
+Substituting Equation~\eqref{eq:implies} into Equation~\eqref{eq:g_definition} eliminates both $a$ and $C$ from it. If we then solve for $a(y)$ we obtain:
 \begin{equation}
@@
 \end{itemize}
-It now follows that 
+It now follows that: 
 \begin{equation}
@@
 \end{equation}
-The above derivation implies that not every Riemann-Stieltjes integral can be converted into a Cavalieri integral.
+The above derivation implies that that not every Riemann-Stieltjes integral $\int_{a'}^{b'} f(x) d\,\widetilde{g}(x)$ can directly be converted into a Cavalieri integral.
+We normally need to first convert it into an equivalent Riemann-Stieltjes integral $\int_{a'}^{b'} f(x) d\,g(x)$.
+The Riemann-Stieltjes integral so obtained can then be converted into a Cavalieri integral.
+The former conversion is achieved by computing the real-valued constant $C$.
+Once, $C$ is known the latter conversion follows trivially.
+The above steps should be clearer to the reader once they have worked through the example presented in Section~\ref{sec:cav_integral_example}.\\
+
+%not every Riemann-Stieltjes integral can be converted into a Cavalieri integral.
 It, however, does tell us that every Riemann-Stieltjes integral can be converted into an equivalent Riemann-Stieltjes integral, which in turn, can be converted into a Cavalieri integral.
 The latter Riemann-Stieltjes integral is obtained by computing the constant $C$.
-These concepts are clarified in Section~\ref{} via a worked out example.
+The above steps should be clearer to the reader once they have worked through the example in Section~\ref{}.
 
-The theorems and definitions presented in this section impose much greater restrictions on $g(x)$ and $f(x)$ than that mentioned in the begining of Section. The functions 
-$g(x)$, and $f(x)$ now also need to be differentiable and invertable.
+\noindent
+The theorems and definitions presented in this section impose much greater restrictions on $g(x)$ and $f(x)$ than that mentioned in the begining of Section~\ref{sec:rs}.
+The functions $g(x)$ and $f(x)$ now also need to be differentiable and invertable.
 Moreover, $a(0)$ must exist.
-These assertions are deemed to be true for the remainder of the paper and as such are not repeated again.
-As will become clear later on, these restrictions limit the number of fractional integrals for which the geometric framework we propose in this paper can produce meaningful results.
-This, however, does not diminish the importance of the proposed framework, since, for the integrals for which the framework does produce meaningful results, we gain valuable and novel insights.
+These additional restrictions on $f(x)$ and $g(x)$ are assumed to be true for the remainder of the paper and as such are not repeated again.
+
+%As will become clear later on, these restrictions limit the number of fractional integrals for which the geometric framework we propose later on can produce meaningful results.
+Generally speaking, however, it does improve our understanding of fractional integration.
 
@@
 \label{sec:cav_integral_example}
+\noindent
 The example which we present below was taken from \cite{?}.
 Let the region $R$ be bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$ and $b(y)=4-y$.
-This region is depicted in Fig.~\ref{fig:caval2}.\\
-%\begin{figure}[htb]
-%\centering
-%\includegraphics[width=0.3\textwidth]{fig12}
-%\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$. Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
-%\label{fig:ex1}
-%\end{figure}
-%\begin{figure}[htb]
-%\centering
-%\includegraphics[width=0.75\textwidth]{fig13.pdf}
-%\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$.
+This region is depicted in Figure~\ref{fig:caval2}.\\
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.75\textwidth]{fig13.pdf}
+\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$.
 In the case of $R$: $a=1$, $b=4$, $a'=\frac{1}{2}$ and $b'=2$.
@@
 Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
-%\label{fig:caval2}
-%\end{figure}
+\label{fig:caval2}
+\end{figure}
 
@@
 
+\noindent
 We can approximate the area of $R$ by using rectangular integration strips.
 It, however, seems much more straightforward to approximate the area of $R$ via non-overlapping non-rectangular integration strips that toghether inscribe $R$.
-Moreover, the sides of the aforementioned integration strips need to be tranlsations of the function $a(y)$.
+This can only be accomplished if the sides of the aforementioned integration strips are tranlsations of the function $a(y)$.\\
 
+\noindent
 Let us express this idea more formally.
@@
 \end{equation}
-The partition points $(x_i^2)_{i=0}^{n}$ are depicted in Fig.~\ref{fig:caval2}.
+The partition points $(x_i^2)_{i=0}^{n}$ are depicted in Figure~\ref{fig:caval2}.
 Cavalieri's principle tells us that the area of integration strip $i$ is equal to $f(x_i^2)\Delta x_i^1$.
 Equation.~\eqref{eq:cav_sum}, therefore, approximates the area of $R$.
-In the limit Eq.~\eqref{eq:cav_sum} approaches
+In the limit equation~\eqref{eq:cav_sum} approaches
 the Cavalieri integral (see Definition~\ref{def:cav_integral}):
@@
 \end{equation}
-It is, however, quite hard to evaluate the above integral directly. Fortunately, it is easy to convert a Cavalieri integral into an equivalent Riemann or Riemann-Stieltjes 
-integral by using the functions $h$ and $g$ (see Theorem~\ref{t:conv}). Expressed mathematically:
+If we evaluate the above integral we obtain the area of $R$.
+It is, however, quite hard to evaluate the above integral in its present form.
+Fortunately, it is easy to convert a Cavalieri integral into an equivalent Riemann or Riemann-Stieltjes
+integral by using the functions $h$ and $g$ (see equation~\ref{eq:g_def} and equation~\ref{eq:h_def}). Expressed mathematically (see Theorem~\ref{t:conv}):
 \begin{equation}
@@
 \end{equation}
-We can calculate $g$ as follows (Definition~\ref{def:g}):
-\begin{equation}
-g(x) = x - a\circ f(x) + a.
-\end{equation}
-Moreover, $h=g^{-1}$ (Theorem~\ref{t:inv}). We can now evaluate in one of two ways:
+We can, therefore, evaluate equation~\ref{eq:main_cav} in one of two ways:
 \begin{equation}
@@
 \end{equation}
-Note, that in the above two equations: $h(x) = \frac{1}{2}x$ and $g(x) = 2x$.
+Note, in the above two equations: $h(x) = \frac{1}{2}x$ and $g(x) = 2x$.\\
 
-We can easily verify that the above is correct by using a more traditional route:
+\noindent
+We can easily verify that the above is correct:
 \begin{equation}
@@
 
-Recall from Section, that not every Riemann-Stieltjes integral $\int_{a'}^{b'} f(x) d\,\widetilde{g}(x)$ can directly be converted into a Cavalieri integral.
+%Recall from Section, that not every Riemann-Stieltjes integral $\int_{a'}^{b'} f(x) d\,\widetilde{g}(x)$ can directly be converted into a Cavalieri integral.
 We usually first need to convert it into an equivalent Riemann-Stieltjes integral $\int_{a'}^{b'} f(x) d\,g(x)$.
@@
 
-As an example, consider the following Riemann-Stieltjes integral:
+\noindent
+The natural question now arises, can we convert a Riemann-Stieltjes integral into a Cavalieri integral?
+As an example, can the following Riemann-Stieltjes integral be converted into a Cavalieri integral?
 \begin{equation}
@@
 \end{equation}
-
-We can now compute the following (see Section~\ref{}):
+To accomplish this task we first need to compute the following (see Section~\ref{sec:cav_integral}):
 \begin{itemize}
@@
 \section{Left-sided Riemann-Liouville Fractional Integral}
+\noindent
 For the sake of completeness, let us review the definition of the left-sided Riemann-Liouville fractional integral of order $\alpha$ (based at $a'$) \cite{laurent1884}. Let
@@
 Please note that in this paper from this point onwards our variable of integration will be $\tau$ instead of $x$.
-It is of our opinion that this notational change improves the readability of the paper (if $\tau$ is our variable of integration then it makes sense to choose $t$ as our upper integration limit).
+It is of our opinion that this notational change improves the readability of the paper (if $\tau$ is our variable of integration then it makes sense to choose $t$ as our upper integration limit).\\
+
+\noindent
 If we apply the above operator in a repetitive manner to $f$ we obtain the $n$th antiderivative of $f$ based at $a'$:
@@
 \end{equation}
-Applying Cauchy's repetitive integration formula to Eq.~\eqref{eq:n_anti} results in:
+Applying Cauchy's repetitive integration formula to equation~\eqref{eq:n_anti} results in:
 \begin{equation}
@@
 \end{equation}
-As an example if $f(t)=t$, $n=2$ and $a'=0$ then Eq.~\eqref{eq:cauchy} reduces to:
-\begin{equation}
-_{0}I_t^2\,f(t) = \int_0^t (t-\tau)\tau~d\tau = \frac{\tau^2 t}{2} - \frac{\tau^3}{3} \Bigg |_0^t = \frac{t^3}{3!}.
-\end{equation}
-The definition in Eq.~\eqref{eq:cauchy} can now be extended to an arbitrary fractional order by replacing $(n-1)!$ with the Gamma function (see Fig.~\ref{fig:gamma}):
+% As an example if $f(t)=t$, $n=2$ and $a'=0$ then equation~\eqref{eq:cauchy} reduces to:
+% \begin{equation}
+% _{0}I_t^2\,f(t) = \int_0^t (t-\tau)\tau~d\tau = \frac{\tau^2 t}{2} - \frac{\tau^3}{3} \Bigg |_0^t = \frac{t^3}{3!}.
+% \end{equation}
+The definition in equation~\eqref{eq:cauchy} can now be extended to an arbitrary fractional order by replacing $(n-1)!$ with the Gamma function (see Figure~\ref{fig:gamma}):
 \begin{equation}
@@
 \end{equation}
-Eq.~\eqref{eq:frac_integral} is known as the left-sided Riemann-Liouville fractional integral of order $\alpha$. As an example if $f(t)=t$, $\alpha=\frac{1}{2}$ and $a'=0$ then 
-Eq.~\eqref{eq:frac_integral} reduces to:
-\begin{equation}
-_0 I_t^{\frac{1}{2}}\,f(t) = \frac{1}{\Gamma(\frac{1}{2})} \int_0^t \frac{\tau}{\sqrt{t-\tau}} d\tau = \frac{1}{\sqrt{\pi}}\left [ -\frac{2}{3}\sqrt{t-\tau}(2t+\tau)\right] \Bigg |_0^t=\frac{4}{3\sqrt{\pi}}t^{\frac{3}{2}}.
-\end{equation}
+Equation~\eqref{eq:frac_integral} is known as the left-sided Riemann-Liouville fractional integral of order $\alpha$. 
+% As an example if $f(t)=t$, $\alpha=\frac{1}{2}$ and $a'=0$ then 
+% equation~\eqref{eq:frac_integral} reduces to:
+% \begin{equation}
+% _0 I_t^{\frac{1}{2}}\,f(t) = \frac{1}{\Gamma(\frac{1}{2})} \int_0^t \frac{\tau}{\sqrt{t-\tau}} d\tau = \frac{1}{\sqrt{\pi}}\left [ -\frac{2}{3}\sqrt{t-\tau}(2t+\tau)\right] \Bigg |_0^t=\frac{4}{3\sqrt{\pi}}t^{\frac{3}{2}}.
+% \end{equation}
 
@@
 \begin{equation}
+\label{eq:rl_to_rs}
 _{a'}I_t^{\alpha}\,f(t) = \frac{1}{\Gamma(\alpha)}\int_{a'}^{t}(t-\tau)^{\alpha-1}f(\tau)~d\tau = \int_{a'}^{t} f(\tau)~d\,\widetilde{g}_t^{\alpha}(\tau), 
@@
 \begin{equation}
-\widetilde{h}_t^{\alpha}(\tau) = t - \sqrt[\alpha]{t^{\alpha} - \Gamma(\alpha+1)(\tau)}.
+\widetilde{h}_t^{\alpha}(\tau) = t - \sqrt[\alpha]{t^{\alpha} - \Gamma(\alpha+1)\tau}.
 \end{equation}
-
 The function $\widetilde{g}_t^{\alpha}$ is invertable, since $\frac{d \widetilde{g}_t^{\alpha}}{d\tau}=\frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)} > 0$ for $\tau\in(-\infty,t]$.
+Let $\mathsf{A} = \{0,0.2,0.4,0.6,0.8,1\}$.
+The graphs of $\widetilde{g}_{10}^{\alpha}(\tau)$ and $\widetilde{h}_{10}^{\alpha}(\tau)$ are depicted in Figure~\ref{fig:gandh}.
 
@@
 
-\noindent
-Let $\mathsf{A} = \{0,0.2,0.4,0.6,0.8,1\}$.
-The analytic expressions of $\widetilde{g}_{10}^{\alpha}(\tau)$ and $\widetilde{h}_{10}^{\alpha}(\tau)$ are presented in Table~\ref{tab:gandh} for $\alpha\in\mathsf{A}$.
-The expressions in Table~\ref{tab:gandh} are depicted in Fig~\ref{fig:gandh}.
-
-\begin{table}[h!]
- \centering
- \caption{The analytic expressions of $\widetilde{g}_{10}^{\alpha}(\tau)$ and $\widetilde{h}_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}$.
+% \begin{table}[h!]
+%  \centering
+%  \caption{The analytic expressions of $\widetilde{g}_{10}^{\alpha}(\tau)$ and $\widetilde{h}_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}$.
 The expressions in this table are depicted in Fig~\ref{fig:gandh}.}
- \label{tab:gandh}
- \begin{tabular}{|c || c | c|} 
- \hline 
- \rule{0pt}{3ex}
- $\alpha$ &  $\widetilde{g}_{10}^{\alpha}(\tau)$ & $\widetilde{h}_{10}^{\alpha}(\tau)$ \\
- \hline\hline
- $0$ & 0 & $y=0$ \\ 
- $0.2$ & $[\Gamma\left (\frac{6}{5} \right )]^{-1}\left(\sqrt[5]{10}-\sqrt[5]{10-\tau}\right)$ & $10 - \left ( \sqrt[5]{10} -  \Gamma\left (\frac{6}{5} \right ) \tau \right )^5$  \\
- $0.4$ & $[\Gamma\left (\frac{7}{5} \right )]^{-1}\left(\sqrt[5]{10^2}-\sqrt[5]{(10-\tau)^2}\right)$ & $10 - \sqrt{\left ( \sqrt[5]{10^2} -  \Gamma\left (\frac{7}{5} \right ) \tau \right )^5}$ \\
- $0.6$ & $[\Gamma\left (\frac{8}{5} \right )]^{-1}\left(\sqrt[5]{10^3}-\sqrt[5]{(10-\tau)^3}\right)$ & $10 - \sqrt[3]{\left ( \sqrt[5]{10^3} -  \Gamma\left (\frac{8}{5} \right ) \tau \right )^5}$ \\
- $0.8$ & $[\Gamma\left (\frac{9}{5} \right )]^{-1}\left(\sqrt[5]{10^4}-\sqrt[5]{(10-\tau)^4}\right)$ & $10 - \sqrt[4]{\left ( \sqrt[5]{10^4} -  \Gamma\left (\frac{9}{5} \right ) \tau \right )^5}$ \\ [1ex]
- $1$ & $\tau$ & $\tau$ \\ [1ex] 
- \hline
- \end{tabular}
- \end{table}
+%  \label{tab:gandh}
+%  \begin{tabular}{|c || c | c|} 
+%  \hline 
+%  \rule{0pt}{3ex}
+%  $\alpha$ &  $\widetilde{g}_{10}^{\alpha}(\tau)$ & $\widetilde{h}_{10}^{\alpha}(\tau)$ \\
+%  \hline\hline
+%  $0$ & 0 & $y=0$ \\ 
+%  $0.2$ & $[\Gamma\left (\frac{6}{5} \right )]^{-1}\left(\sqrt[5]{10}-\sqrt[5]{10-\tau}\right)$ & $10 - \left ( \sqrt[5]{10} -  \Gamma\left (\frac{6}{5} \right ) \tau \right )^5$  \\
+%  $0.4$ & $[\Gamma\left (\frac{7}{5} \right )]^{-1}\left(\sqrt[5]{10^2}-\sqrt[5]{(10-\tau)^2}\right)$ & $10 - \sqrt{\left ( \sqrt[5]{10^2} -  \Gamma\left (\frac{7}{5} \right ) \tau \right )^5}$ \\
+%  $0.6$ & $[\Gamma\left (\frac{8}{5} \right )]^{-1}\left(\sqrt[5]{10^3}-\sqrt[5]{(10-\tau)^3}\right)$ & $10 - \sqrt[3]{\left ( \sqrt[5]{10^3} -  \Gamma\left (\frac{8}{5} \right ) \tau \right )^5}$ \\
+%  $0.8$ & $[\Gamma\left (\frac{9}{5} \right )]^{-1}\left(\sqrt[5]{10^4}-\sqrt[5]{(10-\tau)^4}\right)$ & $10 - \sqrt[4]{\left ( \sqrt[5]{10^4} -  \Gamma\left (\frac{9}{5} \right ) \tau \right )^5}$ \\ [1ex]
+%  $1$ & $\tau$ & $\tau$ \\ [1ex] 
+%  \hline
+%  \end{tabular}
+%  \end{table}
 
@@
 
-\section{Podlubny's Geometric Interpretation}
-Podlubny assigns a geometric meaning to the fractional integral in Eq by visualizing the equivalent Riemann-Stieltjes integral contained within the same equation.
+%\subsection{Podlubny's Geometric Interpretation}
+\noindent
+Podlubny also showed that we can assign a geometric meaning to the fractional integral in equation~\eqref{eq:rl_to_rs} by visualizing the equivalent Riemann-Stieltjes integral contained within the same equation using Bullock's geometric framework.
 Consider the axis $\tau$, $\widetilde{g}_t^{\alpha}$ and $f(\tau)$.
@@
 The ``shadow'' of this fence, i.e.
-the area under the curve which is obtained by projecting this fence onto the $\widetilde{g}f$-plane corresonds to the value which is obtained when Eq is evaluated.
-As an example, the geometric interpretation so obtained for the integrand $f(t)=\sqrt{t}$ is depicted in Figure~\ref{}.
+the area under the curve which is obtained by projecting this fence onto the $\widetilde{g}f$-plane corresonds to the value which is obtained when equation~\eqref{eq:rl_to_rs} is evaluated.
+As an example, the geometric interpretation so obtained for the integrand $f(t)=\sqrt{t}$ is depicted in Figure~\ref{fig:vis_old}.
 
@@
 }
-\label{fig:gandh}
+\label{fig:vis_old}
 \end{figure}
 
-\section{Converting into a Cavalieri integral}
+\subsection{Converting into a Cavalieri integral}
+\label{sec:rl_to_cav}
 Recall that,
@@
 \end{equation}
-Let $C\in\mathbb{R}$. Furthermore, note that (see Theorem~\ref{}):
-\begin{equation}
-\int_{a'}^{t} f(\tau)~d\,g_t^{\alpha}(\tau) = \int_{a'}^{t} f(\tau)~d\,\widetilde{g}_t^{\alpha}(\tau),  
-\end{equation}
-with $g_t^{\alpha}(\tau) = \widetilde{g}_t^{\alpha}(\tau) + C$. 
-Recall, if we wish to convert a Riemann-Stieltjes integral into a Cavalieri integral we normally first need to convert the given Riemann-Stieltjes integral into an equivalent 
-Riemann-Stieltjes integral by computing a value for $C$.
+%Furthermore, note that for all $K\in\mathbb{R}$ (see Theorem~\ref{}):
+%\begin{equation}
+%\int_{a'}^{t} f(\tau)~d\,[\widetilde{g}_t^{\alpha}(\tau)+K] = \int_{a'}^{t} f(\tau)~d%\,\widetilde{g}_t^{\alpha}(\tau),  
+%\end{equation}
+%Moreover, let $C$ be a real-valued constant so that with $g_t^{\alpha}(\tau) = \widetilde{g}_t^{\alpha}(\tau) + C$. 
+%Recall, if we wish to convert a Riemann-Stieltjes integral into a Cavalieri integral we normally first need to convert the given Riemann-Stieltjes integral into an equivalent 
+%Riemann-Stieltjes integral which we can  by computing a value for $C$.
 This latter integral can then be converted into a Cavalieri integral.
 The steps that are required to perform this conversion in the case of Eq is presented below (see Section~\ref{}):
+Let us first compute the following (see Section~\ref{sec:cav_integral}):
 \begin{itemize}
@@
  \item $C = a - \widetilde{g}_t^{\alpha}(a')$.
- \item $g_t^{\alpha} = \widetilde{g}_t^{\alpha} + C$.
+ \item $g_t^{\alpha}(\tau) = \widetilde{g}_t^{\alpha}(\tau) + C$.
  \item $b = g_t^{\alpha}(b')$ and $b_t^{\alpha}(y) = a_t^{\alpha}(y) + (b-a)$.
@@
 \begin{equation}
+\label{eq:rl_to_c}
 _{a'}I_t^{\alpha}\,f(t) =  \frac{1}{\Gamma(\alpha)}\int_{a'}^{t}(t-\tau)^{\alpha-1}f(\tau)~d\tau= \int_{a'}^{t} f(\tau)~dg_t^{\alpha}(\tau) := \int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)\,d\tau.
@@
 
-The below assertion is a direct consequence of Eq ??.
+\noindent
 Let $R_t^{\alpha}$ denote the region which is bounded by $a_t^{\alpha}(y)$, $b_t^{\alpha}(y)$, $f(t)$ and the $\tau$-axis.
 Moreover, let $A_{t}^{\alpha}$ denote the area of $R_t^{\alpha}$.
-When we evaluate $_{a'}I_t^{\alpha}\,f(t)$ we obtain $A_{t}^{\alpha}$.
+Equation~\ref{eq:rl_to_c} implies that when we evaluate $_{a'}I_t^{\alpha}\,f(t)$ we obtain $A_{t}^{\alpha}$.
+In other words, when we evaluate equation~\ref{eq:rl_to_c} we are actually summing together the area of an infinite number of non-rectangular infinitesimals inscribing $R_t^{\alpha}$.
+The aforementioned infinitesimals are, however, non-static, since their shape is a function of $\alpha$ and $t$.\\
 
@@
 
-\section{Evaluating}
 \noindent
 Let $h_t^{\alpha}(\tau)$ be equal to the inverse of $g_t^{\alpha}(\tau)$.
-Interestingly, Eq.~\eqref{eq:main_cav} implies that we can use $h_t^{\alpha}(\tau)$ to convert Eq.~\eqref{eq:cav} into the following Riemann integral:
+Interestingly, Theorem~\ref{t:conv} implies that we can use $h_t^{\alpha}(\tau)$ to convert equation~\eqref{eq:rl_to_c} into the following Riemann integral:
 \begin{equation}
-\label{eq:option2}
+\label{eq:rl_to_r}
 \int_{g_t^{\alpha}(a')}^{\frac{t^{\alpha}}{\Gamma(\alpha+1)}+C} f\circ h_{\alpha}^t (\tau) d\tau.  
 \end{equation}
-We can, therefore, evaluate Eq.~\eqref{eq:cav} in one of two ways: we can either evaluate Eq.~\eqref{eq:rs} or we can evaluate Eq.~\eqref{eq:option2}.
+We can, therefore, evaluate equation~\eqref{eq:frac_integral} in one of two ways: we can either evaluate equation~\eqref{eq:rl_to_rs} or we can evaluate equation~\eqref{eq:rl_to_r}.
 
-\section{Examples}
+\subsection{Examples}
 Consider the following fractional integral:
@@
 \end{equation}
-The function $f(t) = t$ is depicted in Fig.~\ref{fig:geo1}. We can now convert the above fractional integral into a Cavalieri integral (see Section~\ref{??}):
+The function $f(t) = t$ is depicted in Figure~\ref{fig:geo1}. We can now convert the above fractional integral into a Cavalieri integral (see Section~\ref{sec:rl_to_cav}):
 \begin{equation}
 \label{eq:ex1}
-_0I_t^{\alpha} f(t) = \int_0^t f(\tau)~d\,\widetilde{g}_t^{\alpha}(\tau)=\int_0^t f(\tau)~d\,g_t^{\alpha}(\tau)=\int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau,
+_0I_t^{\alpha} f(t) = \int_0^t f(\tau)~d\,\widetilde{g}_t^{\alpha}(\tau)=\int_0^t f(\tau)~d\,g_t^{\alpha}(\tau):=\int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau,
 \end{equation}
@@
 \includegraphics[width=0.75\textwidth]{geo_int1.pdf}
-\caption{The non-static non-rectangular sum-based geometric interpretation of Eq.~\eqref{eq:ex1_raw}.}
+\caption{The non-static non-rectangular sum-based geometric interpretation of equation~\eqref{eq:ex1_raw}.}
 \label{fig:geo1}
@@
 % \noindent
-% Since Eq.~\eqref{eq:ex1}, is a Cavalieri integral it has a known geometric interpretation (see Fig.~\ref{fig:caval2}).
+% Since equation~\eqref{eq:ex1}, is a Cavalieri integral it has a known geometric interpretation (see Figure~\ref{fig:caval2}).
 It can be interpreted as the area obtained by summing together the areas of an infinite
@@
 these infinitesimals have to be translations of $b_t^{\alpha}(y)$.
-The geometric interpretation of Eq.~\eqref{eq:ex1_raw} is, therefore, non-static as it depends on the value of $\alpha$ and $t$.
+The geometric interpretation of equation~\eqref{eq:ex1_raw} is, therefore, non-static as it depends on the value of $\alpha$ and $t$.
 % There is one thing, however, which remains unclear: in what way do $\alpha$ and $t$ affect the shape of the aforementioned infinitesimals, i.e.
@@
 %using two basic steps.
-First off, we will fix the value of $\alpha$ and $t$ in Eq.~\eqref{eq:ex1} and then depict $b_t^{\alpha}(y)$.
-We will then explore how varying the value of $\alpha$ and $t$ in Eq.~\eqref{eq:ex1} affects the shape $b_t^{\alpha}(y)$.\\
+First off, we will fix the value of $\alpha$ and $t$ in equation~\eqref{eq:ex1} and then depict $b_t^{\alpha}(y)$.
+We will then explore how varying the value of $\alpha$ and $t$ in equation~\eqref{eq:ex1} affects the shape $b_t^{\alpha}(y)$.\\
 %We know that a Cavalieri integral can be interpreted as the area which is obtained by summing together the area associated with an infinite number of non-rectangular infinitesimals whose shape 
@@
 This implies that a fractional integral of order $\alpha$ and extent $t$ can be interpeted as the area obtained by summing together the area associated with an infinite number of infinitesimals whose
-%shape is determined by $\alpha$ and $t$, i.e. the geometric interpretation of Eq.~\eqref{eq:ex1_raw} is non-static as it depends on the value of $\alpha$ and $t$.
+%shape is determined by $\alpha$ and $t$, i.e. the geometric interpretation of equation~\eqref{eq:ex1_raw} is non-static as it depends on the value of $\alpha$ and $t$.
 
-\noindent
-If we set the value of $\alpha$ to $\sfrac{4}{5}$ and the value of $t$ to 10 in Eq.~\eqref{eq:ex1} we obtain:
-\begin{equation}
-\label{eq:ex1_specific}
-_0I_{10}^{\sfrac{4}{5}} f(t) = \int_{a_{10}^{\sfrac{4}{5}}(y)}^{b_{10}^{\sfrac{4}{5}}(y)} f(\tau)~d\tau = A_{10}^{\sfrac{4}{5}}. 
-\end{equation}
-Let $R_{10}^{\sfrac{4}{5}}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{10}^{\sfrac{4}{5}}(y)$.
-The region $R_{10}^{\sfrac{4}{5}}$ is depicted in the right-most panel of Fig.~\ref{fig:geo1}.
-It is the largest of all the regions depicted in the right-most panel of Fig.~\ref{fig:geo1}.
+% \noindent
+% If we set the value of $\alpha$ to $\sfrac{4}{5}$ and the value of $t$ to 10 in equation~\eqref{eq:ex1} we obtain:
+% \begin{equation}
+% \label{eq:ex1_specific}
+% _0I_{10}^{\sfrac{4}{5}} f(t) = \int_{a_{10}^{\sfrac{4}{5}}(y)}^{b_{10}^{\sfrac{4}{5}}(y)} f(\tau)~d\tau = A_{10}^{\sfrac{4}{5}}. 
+% \end{equation}
+% Let $R_{10}^{\sfrac{4}{5}}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{10}^{\sfrac{4}{5}}(y)$.
+The region $R_{10}^{\sfrac{4}{5}}$ is depicted in the right-most panel of Figure~\ref{fig:geo1}.
+It is the largest of all the regions depicted in the right-most panel of Figure~\ref{fig:geo1}.
 Moreover, let $A_{10}^{\sfrac{4}{5}}$ denote the area of $R_{10}^{\sfrac{4}{5}}$.
-When we evaluate Equation~\ref{eq:ex1_specific} we obtain $A_{10}^{\sfrac{4}{5}}$ (see Section~\ref{??}).
+When we evaluate Equation~\ref{eq:ex1_specific} we obtain $A_{10}^{\sfrac{4}{5}}$ (see Section~\ref{sec:rl_to_cav}).
 The region $R_{10}^{\sfrac{4}{5}}$ is not bounded by $a_{10}^{\sfrac{4}{5}}(y)$, since $a'=a=0$.
-Furthermore, note that dashed grey curves in the right-most panel of Fig.~\ref{fig:geo1} are translations of $b_{10}^{\sfrac{4}{5}}(y)$.\\
+Furthermore, note that the dashed grey-tinted curves in the right-most panel of Figure~\ref{fig:geo1} are translations of $b_{10}^{\sfrac{4}{5}}(y)$.\\
 
 % We can approximate the area of $R_{10}^{\sfrac{4}{5}}$ by summing together the area of $n$ equal width non-rectangular integration strips that inscribe $R_{10}^{\sfrac{4}{5}}$, i.e. we can 
-% construct a Cavalieri sum (see Eq.~\eqref{eq:cav_sum}). Note, the sides of the non-rectangular integration strips we use in this approximation have to be translations of $b_{10}^{\sfrac{4}{5}}(y)$.
-% If we take the limit of the aforementioned sum as $n\rightarrow \infty$ we approach the Cavalieri integral in Eq.~\eqref{eq:ex1_specific}, i.e. $A_{10}^{\sfrac{4}{5}}$.  
-% Eq.~\eqref{eq:ex1_specific}, therefore, implies that the region $R_{10}^{\sfrac{4}{5}}$ is made up 
+% construct a Cavalieri sum (see equation~\eqref{eq:cav_sum}).
+Note, the sides of the non-rectangular integration strips we use in this approximation have to be translations of $b_{10}^{\sfrac{4}{5}}(y)$.
+% If we take the limit of the aforementioned sum as $n\rightarrow \infty$ we approach the Cavalieri integral in equation~\eqref{eq:ex1_specific}, i.e. $A_{10}^{\sfrac{4}{5}}$.  
+% equation~\eqref{eq:ex1_specific}, therefore, implies that the region $R_{10}^{\sfrac{4}{5}}$ is made up 
 % of an infinite number of non-rectangular infinitesimals; all of them being translations of $b_{10}^{\sfrac{4}{5}}(y)$.
-Note, the right-most curve depicted in the right-most panel of Fig.~\ref{fig:geo1} is $b_{10}^{\sfrac{4}{5}}(y)$.
-Moreover, the special case in which we approximate $A_{10}^{\sfrac{4}{5}}$ using five equal width non-rectangular integration strips is depicted in the right-most panel of Fig.~\ref{fig:geo1}.
-% The sides of the aforementioned five integration strips are depicted in Fig.~\ref{fig:geo1} using dashed lines.
+Note, the right-most curve depicted in the right-most panel of Figure~\ref{fig:geo1} is $b_{10}^{\sfrac{4}{5}}(y)$.
+Moreover, the special case in which we approximate $A_{10}^{\sfrac{4}{5}}$ using five equal width non-rectangular integration strips is depicted in the right-most panel of Figure~\ref{fig:geo1}.
+% The sides of the aforementioned five integration strips are depicted in Figure~\ref{fig:geo1} using dashed lines.
 Let, $\mathcal{B}_{\mathsf{T}}^{\sfrac{4}{5}}=\{b_{10}^{\sfrac{4}{5}}(y)-c|c\in(\mathsf{T}-2)\}$ with $\mathsf{T}=\{2,4,6,8,10\}$.\\
 
-%We have thus verified that we can employ the Cavalieri integral in Eq.~\eqref{eq:ex1_specific} to compute $A_{10}^{\sfrac{4}{5}}$ from first principles.
+%We have thus verified that we can employ the Cavalieri integral in equation~\eqref{eq:ex1_specific} to compute $A_{10}^{\sfrac{4}{5}}$ from first principles.
 %Let $\mathsf{B}_{10}^{\sfrac{4}{5}}$ denote the set containing these dashed curves.
-%We can, therefore, interpet Eq.~\eqref{}  The region $R_{10}^{\sfrac{4}{5}}$ is, therefore, made up 
+%We can, therefore, interpet equation~\eqref{}  The region $R_{10}^{\sfrac{4}{5}}$ is, therefore, made up 
 %of an infinite number of non-rectangular infinitesimals; all of them being translations of $b_{10}^{\sfrac{4}{5}}(y)$.
@@
 \noindent
-Let $\mathsf{T}=\{2,4,6,8,10\}$.
-Varying both $\alpha$ and $t$ results in Eq.~\eqref{eq:ex1}.
-In contrast with Eq.~\eqref{eq:ex1_specific}, Eq.~\eqref{eq:ex1} can be associated with more than one region.
-Let $R_{t}^{\alpha}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{t}^{\alpha}(y)$. Note that $b_{t}^{\alpha}(y)$ forms the 
+Let $\mathsf{T}=\{2,4,6,8,10\}$ and $\mathsf{A} = \{0,0.2,0.4,0.6,0.8,1\}$.
+Moreover, Let $R_{t}^{\alpha}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{t}^{\alpha}(y)$.
+Note that $b_{t}^{\alpha}(y)$ forms the
 right-most edge of $R_{t}^{\alpha}$.
@@
 Moreover, let $A_{t}^{\alpha}$ denote the area of $R_{t}^{\alpha}$ and let $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}=\{R_t^{\alpha}|t\in\mathsf{T},~\alpha\in\mathsf{A}\}$.
-When we evaluate Eq.~\eqref{eq:ex1} we obtain $A_{t}^{\alpha}$ (see Section~\ref{??}).
-The regions in the set $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}$ are depicted in Fig.~\ref{fig:geo1}.
-The regions that are depicted in each of the panels of Fig.~\ref{fig:geo1} were generated by varying $t$, whilst keeping the value of $\alpha$ fixed.
+The regions in the set $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}$ are depicted in Figure~\ref{fig:geo1}.
+The regions that are depicted in each of the panels of Figure~\ref{fig:geo1} were generated by varying $t$, whilst keeping the value of $\alpha$ fixed.
 The title of each panel indicates which $\alpha$-value was used to generate the regions depicted in each panel.
-The only difference between the regions located in each
-panel is their right edges. The right edges of the regions in each panel are depicted using varying shades of gray. The lighter the shade with which an edge is depicted, 
-the larger the $t$-value is that is associated with it.\\
+The only difference between the regions located in each panel is their right edges.
+The right edges of the regions in each panel are depicted using varying shades of gray.
+The lighter the shade with which an edge is depicted, the larger the $t$-value is that is associated with it.\\
 
 \noindent
-As mentioned in Section~\ref{}, Eq.~\eqref{eq:ex1} implies that we can assume that each of the regions depicted in Fig.~\ref{fig:geo1} are made up of an infinite number of infinitesimals.
-The infinitesimals that make up the regions in Fig.~\ref{fig:geo1} are translations of each region's right edge.
-The following observations can now be made by inspecting Fig.~\ref{fig:geo1}:
+We can interpret equation~\eqref{eq:ex1} as the value which is obtained when we sum together the area of an infinite number of non-rectangular infinitesimals inscribing $R_{t}^{\alpha}$.
+The value so obtained is $A_{t}^{\alpha}$.
+Note that, the infinitesimals that are used in the aformentioned sum are translations of $R_{t}^{\alpha}$'s right edge.
+The following observations can now be made by inspecting Figure~\ref{fig:geo1}:
 \begin{description}
- \item[Effect of $\alpha$] the gray-tinted solid curves depicted in the different panels of Fig.~\ref{fig:geo1} are not equal to one another, i.e.
+ \item[Effect of $\alpha$] the gray-tinted solid curves depicted in the different panels of Figure~\ref{fig:geo1} are not equal to one another, i.e.
 $b_{t}^{\alpha_1}(y)\neq b_{t}^{\alpha_2}(y)$ when $\alpha_1\neq\alpha_2$.
- \item[Effect of $t$] The dashed gray curves and the solid gray-tinted curves in the right-most panel are not equal to one another.
-The gray-tinted solid curves depicted in each of the panels of Fig.~\ref{fig:geo1} are, therefore, not translations of one another.
+ \item[Effect of $t$] Note that the dashed grey-tinted curves in the right-most panel of Figure~\ref{fig:geo1} are translations of $b_{10}^{\sfrac{4}{5}}(y)$.
+The dashed gray curves and the solid gray-tinted curves in the right-most panel are not equal to one another.
+The gray-tinted solid curves depicted in each of the panels of Figure~\ref{fig:geo1} are, therefore, not translations of one another.
 \end{description}
-
-The following can thus be concluded: the value of both $\alpha$ and $t$ alters the shape of the infinitesimals that make up the regions in Fig.~\ref{fig:geo1}.
-Interestingly, the effect of $\alpha$ on the shape of the infinitesimals that make up the regions depicted in Fig.~\ref{fig:geo1} is larger than the effect that $t$ has on their shape.
-The curves associated with the infinitesimals obtained by varying $t$, whilst keeping the value of $\alpha$ fixed are very similar in nature and there exists a high degree of correlation between the aforementioned curves (if their
+The following can thus be concluded: the value of both $\alpha$ and $t$ alters the shape of the aforementioned infinitesimals.
+Interestingly, their shape is more affected by $\alpha$ than by $t$.
+The curves in Figure~\ref{fig:geo1} that are associated with the infinitesimals obtained by varying $t$, whilst keeping the value of $\alpha$ fixed are very similar in nature and there exists a high degree of correlation between the aforementioned curves (if their
 sizes are ignored).
-The curves associated with the infinitesimals obtained by varying $\alpha$, whilst keeping the value of $t$ fixed are quite different from one another (the aforementioned curves are not correlated).\\
+The curves in Figure~\ref{fig:geo1} associated with the infinitesimals obtained by varying $\alpha$, whilst keeping the value of $t$ fixed are quite different from one another (the aforementioned curves are not correlated).\\
 
@@
 
-\begin{table}[h!]
-\centering
-\caption{Curves obtained by evaluating Eq.~\eqref{eq:ex1} and Eq.~\eqref{eq:ex2} for all $\alpha\in \mathsf{A}$ using either Eq.~\eqref{eq:rs} or Eq.~\eqref{eq:option2}.}
-\label{tab:eval}
-\begin{tabular}{||c|| c| c||} 
- \hline
- $\alpha$ & $\frac{1}{\Gamma(\alpha)}\int_0^t \tau(t-\tau)^{\alpha-1}~d\tau$ & $\frac{1}{\Gamma(\alpha)}\int_0^t \sqrt{\tau}(t-\tau)^{\alpha-1}~d\tau$ \\[0.5ex]
- \hline\hline
- \rule{0pt}{2.5ex}
- $0$ & $t$ & $\sqrt{t}$  \\  
- \rule{0pt}{2.5ex}
- $0.2$ & $\frac{25}{6\Gamma(\frac{1}{5})} t^{\sfrac{6}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{17}{10})} t^{\sfrac{7}{10}}$  \\ 
- \rule{0pt}{2.5ex}
- $0.4$ & $\frac{25}{14\Gamma(\frac{2}{5})} t^{\sfrac{7}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{19}{10})} t^{\sfrac{9}{10}}$  \\
- \rule{0pt}{2.5ex}
- $0.6$ & $\frac{25}{24\Gamma(\frac{3}{5})} t^{\sfrac{8}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{21}{10})} t^{\sfrac{11}{10}}$  \\ 
- \rule{0pt}{2.5ex}
- $0.8$ & $\frac{25}{36\Gamma(\frac{4}{5})} t^{\sfrac{9}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{23}{10})} t^{\sfrac{13}{10}}$  \\ 
- \rule{0pt}{2.5ex}
- $1$ & $\frac{1}{2}t^2$  & $\frac{2}{3}t^{\sfrac{3}{2}}$  \\ [1ex]
- \hline
- \end{tabular}
-\end{table}
+% \begin{table}[h!]
+% \centering
+% \caption{Curves obtained by evaluating equation~\eqref{eq:ex1} and equation~\eqref{eq:ex2} for all $\alpha\in \mathsf{A}$ using either equation~\eqref{eq:rs} or equation~\eqref{eq:option2}.}
+% \label{tab:eval}
+% \begin{tabular}{||c|| c| c||} 
+%  \hline
+%  $\alpha$ & $\frac{1}{\Gamma(\alpha)}\int_0^t \tau(t-\tau)^{\alpha-1}~d\tau$ & $\frac{1}{\Gamma(\alpha)}\int_0^t \sqrt{\tau}(t-\tau)^{\alpha-1}~d\tau$ \\[0.5ex]
+%  \hline\hline
+%  \rule{0pt}{2.5ex}
+%  $0$ & $t$ & $\sqrt{t}$  \\  
+%  \rule{0pt}{2.5ex}
+%  $0.2$ & $\frac{25}{6\Gamma(\frac{1}{5})} t^{\sfrac{6}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{17}{10})} t^{\sfrac{7}{10}}$  \\ 
+%  \rule{0pt}{2.5ex}
+%  $0.4$ & $\frac{25}{14\Gamma(\frac{2}{5})} t^{\sfrac{7}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{19}{10})} t^{\sfrac{9}{10}}$  \\
+%  \rule{0pt}{2.5ex}
+%  $0.6$ & $\frac{25}{24\Gamma(\frac{3}{5})} t^{\sfrac{8}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{21}{10})} t^{\sfrac{11}{10}}$  \\ 
+%  \rule{0pt}{2.5ex}
+%  $0.8$ & $\frac{25}{36\Gamma(\frac{4}{5})} t^{\sfrac{9}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{23}{10})} t^{\sfrac{13}{10}}$  \\ 
+%  \rule{0pt}{2.5ex}
+%  $1$ & $\frac{1}{2}t^2$  & $\frac{2}{3}t^{\sfrac{3}{2}}$  \\ [1ex]
+%  \hline
+%  \end{tabular}
+% \end{table}
 
@@
 \centering
-\includegraphics[width=0.75\textwidth]{func_eval1.eps}
-\caption{Depicts the curves which are obtained by evaluating Eq.~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ using either Eq.~\eqref{eq:rs} or Eq.~\eqref{eq:option2}.}
+\includegraphics[width=0.75\textwidth]{func_eval1.pdf}
+\caption{Depicts the curves which are obtained by evaluating equation~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ using either equation~\eqref{eq:rs} or equation~\eqref{eq:option2}.}
 \label{fig:eval1}
@@
 \noindent
-If we evaluate the integral in Eq.~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ (using either Eq.~\eqref{eq:rs} or Eq.~\eqref{eq:option2}) we obtain the curves in the 
-left-most column of Table~\ref{tab:eval}. These curves are depicted in Fig.~\ref{fig:eval1}.
-The area of the regions depicted in Fig.~\ref{fig:geo1} are also plotted in Fig.~\ref{fig:eval1} using circular markers.
-As expected, the circular markers in Fig.~\ref{fig:eval1} that correspond to the areas of the regions in Fig.~\ref{fig:eval1}
-associated with a particular choice of $\alpha$ (i.e.
-regions depicted in a particular panel of Fig.~\ref{fig:geo1}) fall on the curve in Fig.~\ref{fig:eval1}; associated with the same choice of $\alpha$.
-Moreover, note that we have adopted the
-same coloring scheme in Fig.~\ref{fig:geo1} and Fig.~\ref{fig:eval1}.
-Using the same coloring scheme in both figures makes it clear which of the area values in Fig.~\ref{fig:eval1} can be associated with which regions in Fig.~\ref{fig:geo1}.
-To summarize, Fig.~\ref{fig:geo1}, therefore, depicts a non-static non-rectangular infinitesimal-based geometric interpretation of Eq.~\eqref{eq:ex1}.
-Moreover, Fig.~\ref{fig:eval1} corroborates this geometric interpretation.\\
+If we evaluate the integral in equation~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ (using either equation~\eqref{eq:rl_to_rs} or equation~\eqref{eq:rl_to_r}) we obtain the curves depicted in in Figure~\ref{fig:eval1}.
+The area of the regions depicted in Figure~\ref{fig:geo1} are also plotted in Figure~\ref{fig:eval1} using circular markers.
+As expected, the circular markers in Figure~\ref{fig:eval1} that correspond to the areas of the regions in Figure~\ref{fig:eval1} associated with a particular choice of $\alpha$ (i.e.
+regions depicted in a particular panel of Figure~\ref{fig:geo1}) fall on the curve in Figure~\ref{fig:eval1}; associated with the same choice of $\alpha$.
+Moreover, note that we have adopted the same coloring scheme in Figure~\ref{fig:geo1} and Figure~\ref{fig:eval1}.
+Using the same coloring scheme in both figures makes it clear which of the area values in Figure~\ref{fig:eval1} can be associated with which regions in Figure~\ref{fig:geo1}.\\
+%To summarize, Figure~\ref{fig:geo1}, therefore, depicts a non-static non-rectangular infinitesimal-based geometric interpretation of equation~\eqref{eq:ex1}.
+Moreover, Figure~\ref{fig:eval1} corroborates this geometric interpretation.\\
 
@@
 \end{equation}
-We can now convert the above fractional integral into a Cavalieri integral (see Section~\ref{}):
+We can now convert the above fractional integral into a Cavalieri integral (see Section~\ref{sec:rl_to_cav}):
 \begin{equation}
@@
 Note, that for this example $a'=a=0$.
-The non-static non-rectangular infinitesimal-based geometric interpretation associated with Eq.~\eqref{eq:ex1}, which we construct vby employing Eq, is depicted in Fig.~\ref{fig:geo2}.
-If we evaluate the integral in Eq.~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ we obtain the curves in the right-most column of Table~\ref{tab:eval}.
-These curves are depicted in Fig~\ref{fig:eval2}.
-The validity of the non-static non-rectangular infinitesimal-based geometric interpretation depicted in Fig.~\ref{fig:geo2} is corroborated by Fig.~\ref{fig:eval2}.
+The visualization of equation~\eqref{eq:ex2_cav} is depicted in Figure~\ref{fig:geo2}.
+If we evaluate the integral in equation~\eqref{eq:ex2} for all $\alpha\in \mathsf{A}$ we obtain the curves depicted in Figure~\ref{fig:eval2}.
+The validity of the geometric interpretation depicted in Figure~\ref{fig:geo2} is corroborated by Figure~\ref{fig:eval2}.
 
@@
 \centering
-\includegraphics[width=0.75\textwidth]{geo_int2.eps}
-\caption{The non-static non-rectangular sum-based geometric interpretation of Eq.~\eqref{eq:ex2}.}
+\includegraphics[width=0.75\textwidth]{geo_int2.pdf}
+\caption{The non-static non-rectangular sum-based geometric interpretation of equation~\eqref{eq:ex2}.}
 \label{fig:geo2}
@@
 \centering
-\includegraphics[width=0.75\textwidth]{func_eval2.eps}
-\caption{Depicts the curves which are obtained by evaluating Eq.~\eqref{eq:ex2} for all $\alpha\in \mathsf{A}$ using either Eq.~\eqref{eq:rs} or Eq.~\eqref{eq:option2}.}
+\includegraphics[width=0.75\textwidth]{func_eval2.pdf}
+\caption{Depicts the curves which are obtained by evaluating equation~\eqref{eq:ex2} for all $\alpha\in \mathsf{A}$ using either equation~\eqref{eq:rs} or equation~\eqref{eq:option2}.}
 \label{fig:eval2}
@@
 \end{theorem}
-
-\noindent
-Furthermore, Grobler showed that it is trivial to convert a Riemann-Stieltjes integral into a Cavalieri integral \cite{ackermann12,grobler19} (see Fig.~\ref{fig:caval2} and the Cavalieri section of this paper if more details are required).
-If we apply Grobler's conversion method to Eq.~\eqref{eq:rs} we obtain:
-\begin{equation}
-\label{eq:cav}
-\int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau, 
-\end{equation}
-with
-\begin{equation}
-\label{eq:cav_a}
-a_t^{\alpha}(y) = f^{-1}(y) - \frac{t^{\alpha}-(t-f^{-1}(y))^{\alpha}}{\Gamma(\alpha+1)}.
-\end{equation}
-Eq.~\eqref{eq:cav_a} is obtained by substituting Eq.~\eqref{eq:g_rl} into Eq.~\eqref{eq:a_y}. Note, $b_t^{\alpha}(y) = a_t^{\alpha}(y) + \frac{t^{\alpha}}{\Gamma(\alpha+1)}$.
-
-\noindent
-We can now assign a geometric interpretation to Eq.~\eqref{eq:cav}, since it is a Cavalieri integral (see Fig.~\ref{fig:caval2} and the Cavalieri section of this paper).
-The fractional integral in Eq.~\eqref{eq:RL_frac_int} can, therefore, be interpreted as the area obtained
-by summing together the area of an infinite number of infinitesimally small non-rectangular integration strips whose shape is determined by $\alpha$ and $t$.
-If $\alpha$ is equal to one, however, then the integral reduces to a normal Riemann integral as the integration strips become rectangular for this particular choice of $\alpha$ (its shape becomes independent of $t$).\\
-
-\noindent
-Interestingly, Eq.~\eqref{eq:main_cav} implies that we can use $h_t^{\alpha}(\tau)$ to convert Eq.~\eqref{eq:cav} into the following Riemann integral:
-\begin{equation}
-\label{eq:option2}
-\int_0^{\frac{t^{\alpha}}{\Gamma(\alpha+1)}} f\circ h_{\alpha}^t (\tau) d\tau.  
-\end{equation}
-We can, therefore, evaluate Eq.~\eqref{eq:cav} in one of two ways: we can either evaluate Eq.~\eqref{eq:rs} or we can evaluate Eq.~\eqref{eq:option2}.
 

### 2019-10-18 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
newest version

@@
  \item[Effect of $t$] Note that the dashed grey-tinted curves in the right-most panel of Figure~\ref{fig:geo1} are translations of $b_{10}^{\sfrac{4}{5}}(y)$.
-The dashed gray curves and the solid gray-tinted curves in the right-most panel are not equal to one another.
+The dashed gray-tinted curves and the solid gray-tinted curves in the right-most panel are not equal to one another.
 The gray-tinted solid curves depicted in each of the panels of Figure~\ref{fig:geo1} are, therefore, not translations of one another.
@@
 
-\begin{theorem}
-Let $\widetilde{g}_t^{\alpha}=\frac{\left \{t^{\alpha} - (t-\tau)^{\alpha} \right \}}{\Gamma(\alpha+1)}$ and $a(y)_{t}^{\alpha} = f^{-1}(y) - \widetilde{g}_t^{\alpha}\circ f^{-1}(y) + \widetilde{g}_t^{\alpha}(a')$.
-If $a(y)_t^{\alpha}$ and $a(0)$ exists then
-there exists a $C\in \mathbb{R}$ such that the following integrals are geometrically equivalent:
-\begin{equation}
-\int_{a'}^{b'} f(x)\,dg_t^{\alpha}(x)~\textrm{and}~\int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(x)\,dx. 
-\end{equation}
-\end{theorem}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-10-24 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
newest edit

@@
 In this article we specifically focus on the geometric interpretation of fractional integrals.
-To be more specific, we present a novel geometric interpretation of the left-sided Riemann-Liouville fractional integral based at $a'$ \cite{laurent1884}.
-As we mentioned earlier, Riemann and Liouville played an important role in the development of fractional calculus. Their work was crucial in defining what is now known as 
-the Riemann-Liouville fractional integral \cite{laurent1884}.
+To be more specific, we present a novel geometric interpretation of the left-sided Riemann-Liouville fractional integral based at $a'$ \cite{laurent1884} by extending the geometric framework proposed by Podlubny \cite{podlubny02}.
+%As we mentioned earlier, Riemann and Liouville played an important role in the development of fractional calculus. Their work was crucial in defining what is now known as 
+%the Riemann-Liouville fractional integral \cite{laurent1884}.
 At this point in time the reader should be made aware of the fact that there exists many other accepted fractional integral definitions in the literature.
-We, however, deem these definitions to be beyond the scope of the current article and as such we do not discuss them any further in this work. Furthermore, the geometric interpretation 
-we present here is an extension of the geometric interpretation presented by Podlubny \cite{podlubny02}. Podlubny showed that a Riemann-Liouville fractional integral 
-can be converted into a Riemann-Stieltjes integral. Moreover, Grobler showed that a Riemann-Stieltjes integral can be interpreted as the area which is obtained by summing together 
-the area of an infinite number of non-rectangular infinitesimals, i.e.
+%We, however, deem these definitions to be beyond the scope of the current article and as such we do not discuss them any further in this work. 
+%The geometric interpretation that we present in this paper here is an extension of the geometric interpretation presented by Podlubny  
+Podlubny showed that a Riemann-Liouville fractional integral can be converted into a Riemann-Stieltjes integral.
+The Riemann-Stieltjes integral so obtained can then be visualized using Bullock's geometric framework.
+Moreover, Grobler showed that a Riemann-Stieltjes integral can be interpreted as the area which is obtained by summing together the area of an infinite number of non-rectangular infinitesimals, i.e.
 a Riemann-Stieltjes integral can be converted into a Cavalieri integral \cite{ackermann12,grobler19}.
-Combining these two ideas results in the following geometric
-interpretation: the Riemann-Liouville fractional integral can be interpreted as the area which is obtained by summing together the area of an infinite number of non-rectangular infinitesimals whose shape is determined by the order of integration $\alpha$ and the integration limit $t$.\\
+Combining these two ideas results in the following geometric interpretation: the Riemann-Liouville fractional integral can be interpreted as the area which is obtained by summing together the area of an infinite number of non-rectangular infinitesimals whose shape is determined by the order of integration $\alpha$ and the integration limit $t$.\\
 
@@
 We start the paper by reviewing the definition of the Riemann-Stieltjes integral, the Cavalieri integral and the left-sided Riemann-Liouville fractional integral.
-We then present Podlubny's original geometric framework, followed by our novel geometric framework.
+We then present Podlubny's original geometric framework, followed by our extension thereof.
 We end the paper with two examples and a conclusion.
@@
 In other words, when we evaluate equation~\ref{eq:rl_to_c} we are actually summing together the area of an infinite number of non-rectangular infinitesimals inscribing $R_t^{\alpha}$.
-The aforementioned infinitesimals are, however, non-static, since their shape is a function of $\alpha$ and $t$.\\
+The aforementioned infinitesimals are, however, non-static, since they need to be translations of $a(y)_t^{\alpha}$.
+The shape of these infitesimals are thus dependend on $\alpha$ and $t$.
+In summary, we can obtain a novel geometric interpretation of
+$_{a'}I_t^{\alpha}\,f(t)$ by first converting it into a Cavalieri integral.
+We will take the liberty in this paper to refer to the depiction of the aformentioned Cavalieri integral as the non-static non-rectangular sum-based geometric interpretation of $_{a'}I_t^{\alpha}\,f(t)$.\\
 
@@
 with $a_t^{\alpha}(y) = y - \frac{t^{\alpha}-(t-y)^{\alpha}}{\Gamma(\alpha+1)}$, $b_t^{\alpha}(y) = a_t^{\alpha}(y) + \frac{t^{\alpha}}{\Gamma(\alpha+1)}$ and $C=0$.
-Note, that for this example $a'=a=0$.\\
+Note, that for this example $a'=a=0$.
+The non-static non-rectangular sum-based geometric interpretation associated with equation~\ref{eq:ex1} is depicted in Figure~\ref{fig:geo1} (see Section~\ref{sec:rl_to_cav}).
+We elaborate on this below.\\
 
@@
 We can interpret equation~\eqref{eq:ex1} as the value which is obtained when we sum together the area of an infinite number of non-rectangular infinitesimals inscribing $R_{t}^{\alpha}$.
-The value so obtained is $A_{t}^{\alpha}$.
+The value so obtained is $A_{t}^{\alpha}$ (see Section~\ref{sec:rl_to_cav}).
 Note that, the infinitesimals that are used in the aformentioned sum are translations of $R_{t}^{\alpha}$'s right edge.
@@
 Moreover, note that we have adopted the same coloring scheme in Figure~\ref{fig:geo1} and Figure~\ref{fig:eval1}.
-Using the same coloring scheme in both figures makes it clear which of the area values in Figure~\ref{fig:eval1} can be associated with which regions in Figure~\ref{fig:geo1}.\\
+Using the same coloring scheme in both figures makes it clear which of the area values in Figure~\ref{fig:eval1} can be associated with which regions in Figure~\ref{fig:geo1}.
+The validity of the geometric interpretation depicted in Figure~\ref{fig:geo1} is, therefore, corroborated by Figure~\ref{fig:eval1}.
+\\
 %To summarize, Figure~\ref{fig:geo1}, therefore, depicts a non-static non-rectangular infinitesimal-based geometric interpretation of equation~\eqref{eq:ex1}.
@@
 Note, that for this example $a'=a=0$.
-The visualization of equation~\eqref{eq:ex2_cav} is depicted in Figure~\ref{fig:geo2}.
-If we evaluate the integral in equation~\eqref{eq:ex2} for all $\alpha\in \mathsf{A}$ we obtain the curves depicted in Figure~\ref{fig:eval2}.
-The validity of the geometric interpretation depicted in Figure~\ref{fig:geo2} is corroborated by Figure~\ref{fig:eval2}.
+The non-static non-rectangular sum-based geometric interpretation associated with equation~\ref{eq:ex2_cav} is depicted in Figure~\ref{fig:geo2} (see Section~\ref{sec:rl_to_cav}).
 
@@
 
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.75\textwidth]{func_eval2.pdf}
-\caption{Depicts the curves which are obtained by evaluating equation~\eqref{eq:ex2} for all $\alpha\in \mathsf{A}$ using either equation~\eqref{eq:rs} or equation~\eqref{eq:option2}.}
-\label{fig:eval2}
-\end{figure}
+\section{Conclusion}
+In this paper we presented a novel geometric interpretation of the left-sided 
+Riemann-Liouville fractional integral. It can be interpreted as the value which is 
+obtained by summing toghether the area of an infinite number of non-static non-rectangular infinitesimals.
+The shape of the infinitesimals used within the aforementioned sum depend on the order and the upper integration limit of the fractional integral under consideration.
+
+%\begin{figure}[htb]
+%\centering
+%\includegraphics[width=0.75\textwidth]{func_eval2.pdf}
+%\caption{Depicts the curves which are obtained by evaluating equation~\eqref{eq:ex2} %for all $\alpha\in \mathsf{A}$ using either equation~\eqref{eq:rs} or equation~\eqref{eq:option2}.}
+%\label{fig:eval2}
+%\end{figure}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Acknowledgements}
-
- The author thanks his institution for the support, under Grant No ...
+%\section*{Acknowledgements}
+
+% The author thanks his institution for the support, under Grant No ...
 

### 2019-10-25 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
added literature review

@@
  \title[VISUALIZATION OF FRACTIONAL INTEGRALS]{VISUALIZATION OF THE LEFT-SIDED RIEMANN-LIOUVILLE FRACTIONAL INTEGRAL \\ [3pt] IN ``FCAA'' JOURNAL}
- \author[\normalsize V. Kiryakova, S. Author]{\normalsize Virginia Kiryakova $^1$, Second Author $^2$}
+ \author[\normalsize T.L Grobler]{\normalsize Trienko Lups Grobler $^1$}
 
@@
 
-{\it MSC 2010\/}: Primary 26A33;
-                  Secondary 33E12, 34A08, 34K37, 35R11, 60G22, ...
+{\it MSC 2010\/}: 26A33
+                  %Secondary 33E12, 34A08, 34K37, 35R11, 60G22, ...
 
@@
 
-{\it Key Words and Phrases}: fractional calculus, Mittag-Leffler
-type functions, fractional ordinary and partial differential
-equations, ...
+{\it Key Words and Phrases}: geometric interpretation, fractional calculus, left-sided Riemann-Liouville integral, cavalieri integral.
 
@@
 In this article we specifically focus on the geometric interpretation of fractional integrals.
-To be more specific, we present a novel geometric interpretation of the left-sided Riemann-Liouville fractional integral based at $a'$ \cite{laurent1884} by extending the geometric framework proposed by Podlubny \cite{podlubny02}.
+To be more specific, we present a novel geometric interpretation of the left-sided Riemann-Liouville fractional integral based at $a'$ \cite{laurent1884}.
+We accomplish this by extending the geometric framework proposed by Podlubny \cite{podlubny02}.
 %As we mentioned earlier, Riemann and Liouville played an important role in the development of fractional calculus. Their work was crucial in defining what is now known as 
@@
 
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.75\textwidth]{gamma.pdf}
-\caption{A plot of $\Gamma(x) = \int_0^{\infty} t^{x-1} e^{-t}\,dt$ for $x\in(-5,5)$.
+% \begin{figure}[htb]
+% \centering
+% \includegraphics[width=0.7\textwidth]{gamma.pdf}
+% \caption{A plot of $\Gamma(x) = \int_0^{\infty} t^{x-1} e^{-t}\,dt$ for $x\in(-5,5)$.
 $\Gamma(x)$ is not defined for the negative integers.
 Moreover, it is a natural extension of the factorial function to the real numbers \cite{euler1738}.}
-\label{fig:gamma}
-\end{figure}
+% \label{fig:gamma}
+% \end{figure}
 
@@
 
+\bibitem{ackermann12} E.R.~Ackermann, T.L~Grobler, W.~Kleynhans,~W., J.C.~ Olivier, B.P.~Salmon, A.J.~van Zyl. Cavalieri
+Integration. \textit{Quaest. Math.} \textbf{35}, No 3 (2012), 265--296.
+
+\bibitem{adda97} F.B.~Adda, (1997). Geometric interpretation of the fractional derivative. \textit{J. of Fract. Calc.} \textbf{11}, (1997), 21--52.
+
+\bibitem{bullock88} G.L.~Bullock. A geometric interpretation of the Riemann-Stieltjes integral. \textit{Am. Math. Mon.} \textbf{95}, No 5 (1988), 448--455.
+
+%\bibitem{bartle76} R.G.~Bartle, \textit{The Elements of Real Analysis.} Wiley, New York (1976).
+
+%Physical
+%\bibitem{cioc16} Cioc, R.
+(2016).
+Physical and geometrical interpretation of Gr\"{u}nwald-Letnikov differintegrals: Measurement of path and acceleration.
+\textit{Fract.
+Calc.
+Appl.
+Anal.} 19(1): 161--172.
+
+%\bibitem{davis59} Davis,~P.~J. (1959). Leonhard Euler's Integral: A Historical Profile of the Gamma Function. \textit{Amer. Math. Monthly}. 66(10): 849--869
+
+%\bibitem{euler1738} Euler,~L. (1738). De progressionibus transcendentibus seu quarum termini generales algebraice dari nequeunt. \textit{Commentarii academiae scientiarum Petropolitanae}. 36--57.
+
+\bibitem{garcia2019} J.P.~Garc\'{i}a-Sandoval, On representation and interpretation of Fractional calculus and fractional order systems.
+\textit{Fract.
+Calc.
+Appl.
+Anal.}, \textbf{22}, No 2 (2019), 522---537.
+
+%\bibitem{gomez14} J.F~Gomez-Aguilara, R.~Razo-Hernandez, D.A.~Granados-Lieberman. Physical interpretation of fractional
+%calculus in observable terms: analysis of the fractional time constant and the transitory response. \textit{Revista Mexicana de Fisica.} \textbf{60}, (2014), 32--38.
+
+\bibitem{grobler19} T.L.~Grobler. Visualization of the Riemann-Stieltjes integral. \textit{Coll. Math. J.} \textbf{50}. No 3 (2019), 198--209.
+
+\bibitem{laurent1884} H.~Laurent, (1884). Sur le calcul des d\'{e}riv\'{e}es \`{a} indices quelconques. \textit{Nouv Annales de Mathem\'{e}matiques.} \textbf{3}, No 3 (1884), 240--252.
+
+%\bibitem{liouville1832} Liouville,~J.
+(1832).
+M\'{e}moire sur l\textquotesingle integration de l\textquotesingle \'{e}quation $(mx^2+nx+p)\frac{d^2y}{dx^2}+(qx+r)\frac{dy}{dx}+sy$ \`{a} l\textquotesingle aide des diff\'{e}rentielles \`{a} indices
+%que\textquotesingle conques. \textit{Journal d l\textquotesingle Ecole Polytechnique.} 13(21): 163--186.
+
+\bibitem{machado03} J.T.~Machado. A probabilistic interpretation of the fractionalorder differentiation. \textit{Fract. Calc. Appl. Anal.} \textbf{6}, No 1 (2003), 73--80.
+
+%\bibitem{machado14} Machado,~J.~T., Galhano,~A.~M., Trujillo,~J.~J. (2014). On development of fractional calculus during the last fifty years. \textit{Scientometrics}. 98(1): 577-582.
+
+\bibitem{machado17} J.T.~Machado, V.~Kiryakova. The chronicles of fractional calculus. \textit{Fract. Calc. Appl. Anal.} \textbf{20}, No 2 (2017), 307--336.
+
+%\bibitem{munkhammar05} Munkhammar,~J. (2005). Fractional calculus and the Taylor-Riemann series. \textit{Rose-Hulman Undergrad. Math. J.}, 6(1): 6.
+
+%physical
+\bibitem{nigmatullin92} R.R.~Nigmatullin. A fractional integral and its physical interpretation. \textit{Theor. and Math. Phys.} \textbf{90}, No 3 (1992): 242--251.
+
+\bibitem{podlubny02} Podlubny,~I. Geometric and Physical Interpretation of Fractional Integration and Fractional Differentiation, \textit{Fract. Calc. Appl. Anal.} \textbf{5}, No 4 (2002), 367--386.
+
+%\bibitem{riemann1876} Riemann,~B.~G.~F (1876). Gesammelte Werke.
+
+%\bibitem{ross77} Ross,~B. (1977). The development of fractional calculus 1695--1900. \textit{Hist. Math.} 4(1): 75--89.
+
+\bibitem{ross06} B.Ross, (Ed.).
+\textit{Fractional calculus and its applications: proceedings of the international conference held at the University of New Haven, June 1974}, \textbf{457}, Springer (1974).
+
+\bibitem{rutman95} R.S.~Rutman. On physical interpretations of fractional integration and differentiation. \textit{Theor. and Math. Phys.} \textbf{105}, No 3 (1994),1509--1519.
+
+ %Probability
+\bibitem{stanislavsky04} A.A.~Stanislavsky.  Probability interpretation of the integral of fractional order, \textit{Theor. and Math. Phys.} \textbf{138}, No 3 (2004), 418--431.
+
+%Geometric
+\bibitem{tarasov16} V.E.~Tarasov. Geometric interpretation of fractional-order derivative. \textit{Fract. Calc. Appl. Anal.} \textbf{19}, No 5 (2016), 1200--1221.
+
+%Economic
+\bibitem{tarasova17} V.V.~Tarasova, V.E.~Tarasov. Economic Interpretation of Fractional Derivatives. \textit{Prog. in Fract. Diff. and Appl.} \textbf{3}, No 1 (2017), 1--7.
+
 %%%% example for a book %%%%%%%%%%%%%
 
-\bibitem{GasRah}
- G. Gasper, M. Rahman,
- \emph{Basic Hypergeometric Series}.
- Cambridge University Press, Cambridge (1990).
+%\bibitem{GasRah}
+% G. Gasper, M. Rahman,
+% \emph{Basic Hypergeometric Series}.
+% Cambridge University Press, Cambridge (1990).
 
@@
 
-\bibitem{Kir}
- V. Kiryakova,
- A brief story about the operators of generalized
-fractional calculus.
- \emph{Fract. Calc. Appl. Anal.} \textbf{11}, No 2 (2008), 201--218; DOI: ..........
+%\bibitem{Kir}
+% V. Kiryakova,
+% A brief story about the operators of generalized
+%fractional calculus.
+% \emph{Fract. Calc. Appl. Anal.} \textbf{11}, No 2 (2008), 201--218; DOI: ..........
 
@@
 
-\bibitem{Moak}
- D.S. Moak,
- The $q$-analogue of the Laguerre polynomials.
-\emph{J. Math. Anal. Appl.} \textbf{81}, No 1 (1981), 20--47. % ; doi: ........
+%\bibitem{Moak}
+% D.S. Moak,
+% The $q$-analogue of the Laguerre polynomials.
+%\emph{J. Math. Anal. Appl.} \textbf{81}, No 1 (1981), 20--47. % ; doi: ........
 
@@
 
-\bibitem{Rosbl}
- M. Rosenblum,
- Generalized Hermite polynomials and the Bose-like oscillator
- calculus.
- In: \emph{Operator Theory: Advances and Applications},
- Birkh\"auser, Basel (1994), 369--396.
+%\bibitem{Rosbl}
+% M. Rosenblum,
+% Generalized Hermite polynomials and the Bose-like oscillator
+% calculus.
+% In: \emph{Operator Theory: Advances and Applications},
+% Birkh\"auser, Basel (1994), 369--396.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
    %(First) Author's full postal address
-$^1$ Institute of Mathematics and Informatics \\
-Bulgarian Academy of Sciences \\
-"Acad. G. Bontchev" Str., Block 8 \\
-Sofia -- 1113, BULGARIA  \\[4pt]
-  e-mail: virginia@diogenes.bg
+$^1$ Dept. of Mathematical Sciences, Stellenbosch University \\
+Private Bag X1 --- 7600 SOUTH AFRICA \\[4pt]
+  e-mail: tlgrobler@sun.ac.za
 \hfill Received: November 1, 2014 \\[12pt]
   % Second Author's address
-$^2$ Dept. of Physics, University of Bologna\\
-Via Irnerio 46, I -- 40126 Bologna, ITALY \\[4pt]
-  e-mail: .....
+%$^2$ Dept. of Physics, University of Bologna\\
+%Via Irnerio 46, I -- 40126 Bologna, ITALY \\[4pt]
+%  e-mail: .....
 

### 2019-10-25 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
added literature review

@@
 The mathematical discipline in which we study the extension of derivatives and integrals to non-integer orders is known as fractional calculus. Euler, Liouville and Riemann laid most 
-of the theoretical groundwork, which was needed to develop the field of fractional calculus \cite{davis59,euler1738,liouville1832,riemann1876,laurent1884}.
-Fractional calculus has now developed into a mature discipline \cite{machado14,machado17}.
+of the theoretical groundwork, which was needed to develop the field of fractional calculus \cite{laurent1884}. Fractional calculus has now developed into a mature discipline \cite{machado17}. 
 However, there is one aspect of the discipline which only started to develop fairly recently: its physical and geometric interpretability.
@@
 a number of papers that attempt to rectify this.
-There now exist probabilistic interpretations \cite{stanislavsky04,machado03}, geometric interpretations \cite{adda97,tarasov16,podlubny02}, physical interpretations \cite{cioc16,rutman95, nigmatullin92, gomez14} and economic
+There now exist probabilistic interpretations \cite{machado03,stanislavsky04}, geometric interpretations \cite{adda97,garcia2019,podlubny02,tarasov16}, physical interpretations \cite{rutman95, nigmatullin92} and economic
 interpretations \cite{tarasova17} of fractional order integrals and differentials.\\
@@
 Podlubny showed that a Riemann-Liouville fractional integral can be converted into a Riemann-Stieltjes integral.
-The Riemann-Stieltjes integral so obtained can then be visualized using Bullock's geometric framework.
+The Riemann-Stieltjes integral so obtained can then be visualized using Bullock's geometric framework \cite{bullock88}.
 Moreover, Grobler showed that a Riemann-Stieltjes integral can be interpreted as the area which is obtained by summing together the area of an infinite number of non-rectangular infinitesimals, i.e.
@@
 We shall suppose that both $f$ and $g$ are bounded on $[a',b']$.
-Recall that the Riemann-Stieltjes integral is defined as follows \cite{bartle76}:
+Recall that the Riemann-Stieltjes integral is defined as follows:
 \begin{equation}
@@
 \noindent
-Ackerman et al. used the notion of non-rectangular integration strips to define the so called Cavalieri integral. The area of a non-rectangular 
+Ackerman et al. used the notion of non-rectangular integration strips to define the so called Cavalieri integral \cite{ackermann12}. The area of a non-rectangular 
 integration strip is calculated using Cavalieri's principle. Cavalieri's principle is stated below without proof:
@@
 Suppose two regions in a plane are included between two parallel lines in that plane.
-If every line parallel to these two lines intersects both regions in line segments of equal length, then the two regions have equal areas \cite{??}.
+If every line parallel to these two lines intersects both regions in line segments of equal length, then the two regions have equal areas \cite{ackermann12}.
 \end{theorem}
 
+\noindent
 The definition of the Cavalieri integral is presented in Definition~\ref{def:cav_integral}.
@@
 We, therefore, encourage readers who are not familiar with the Cavalieri integral to rather first read Section~\ref{sec:cav_integral_example} instead.
-The reader who is not familiar with the Cavalieri integral should only refer back to the definitions presented in this section when things in Section~\ref{sec:cav_integral_example} become unclear.
-Moreover, the definitions presented below were taken from \cite{??}.
-Furthermore, none of the theorems in this section are proved, the proofs can be found in \cite{??}.
+The reader who is not familiar with the Cavalieri integral should, however, feel free to refer back to the definitions presented in this section when things in Section~\ref{sec:cav_integral_example} become unclear.
+Moreover, the definitions presented below were taken from \cite{ackermann12}.
+Furthermore, none of the theorems in this section are proved, the proofs can be found in \cite{ackermann12,grobler19}.
 
@@
 \noindent
-Theorem~\ref{t:conv} tells us how to convert a Cavalieri integral into an equivalent Riemann or Riemann-Stieltjes integral. It, however, tells us nothing about the reverse 
-procedure, if we are given a Riemann-Stieltjes integral how do we convert it into a Cavalieri integral?\\
+Theorem~\ref{t:conv} tells us how to convert a Cavalieri integral into an equivalent Riemann or Riemann-Stieltjes integral.
+It, however, tells us nothing about the reverse procedure, if we are given a Riemann-Stieltjes integral how do we convert it into a Cavalieri integral?\\
 
@@
 Assume that $\widetilde{g}(x)$ is a differentiable and invertable real-valued function on $[a',b']$.
-How do we go about converting $\int_{a'}^{b'} f(x)\,\widetilde{g}(x)$ into a Cavalieri integral?
+How do we go about converting $\int_{a'}^{b'} f(x)\,\widetilde{g}(x)$ into a Cavalieri integral?\\
+
+\noindent
 Note that for all $K\in\mathbb{R}$ (see equation~\ref{eq:rs_identity}):
@@
 \end{equation}
-Moreover, let $C$ be a unique real-valued constant that satisfies: $g(x) := \widetilde{g}(x)+C$.
-At first, it does not seem possible to compute $a(y)$ (perform the required conversion) given only $\widetilde{g}(x)$ as $C$ and $a$ are unknown a priori.
-However,
+Moreover, let $C$ be a unique real-valued constant that satisfies: $g(x) := \widetilde{g}(x)+C$.\\
+
+\noindent
+At first it seems impossible to compute $a(y)$ (perform the required conversion) given only $\widetilde{g}(x)$ as $C$ and $a$ are unknown a priori. However, 
 \begin{equation}
@@
 \int_{a'}^{b'} f(x)d\,\widetilde{g}(x) = \int_{a'}^{b'} f(x)d\,g(x):=\int_{a(y)}^{b(y)}f(x)dx. 
-\end{equation}
+\end{equation}\
+
+\noindent
 The above derivation implies that that not every Riemann-Stieltjes integral $\int_{a'}^{b'} f(x) d\,\widetilde{g}(x)$ can directly be converted into a Cavalieri integral.
@@
 \noindent
-The example which we present below was taken from \cite{?}.
+The example which we present below was taken from \cite{ackermann12,grobler19}.
 Let the region $R$ be bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$ and $b(y)=4-y$.
@@
 We can approximate the area of $R$ by using rectangular integration strips.
-It, however, seems much more straightforward to approximate the area of $R$ via non-overlapping non-rectangular integration strips that toghether inscribe $R$.
+It, however, seems much more straightforward to approximate the area of $R$ via non-overlapping non-rectangular integration strips that inscribe $R$.
 This can only be accomplished if the sides of the aforementioned integration strips are tranlsations of the function $a(y)$.\\
@@
 Cavalieri's principle tells us that the area of integration strip $i$ is equal to $f(x_i^2)\Delta x_i^1$.
-Equation.~\eqref{eq:cav_sum}, therefore, approximates the area of $R$.
+Equation~\eqref{eq:cav_sum}, therefore, approximates the area of $R$.
 In the limit equation~\eqref{eq:cav_sum} approaches
@@
 \end{equation}
-Note, in the above two equations: $h(x) = \frac{1}{2}x$ and $g(x) = 2x$.\\
+Note: $h(x) = \frac{1}{2}x$ and $g(x) = 2x$.\\
 
@@
 % \end{equation}
-The definition in equation~\eqref{eq:cauchy} can now be extended to an arbitrary fractional order by replacing $(n-1)!$ with the Gamma function (see Figure~\ref{fig:gamma}):
+The definition in equation~\eqref{eq:cauchy} can now be extended to an arbitrary fractional order by replacing $(n-1)!$ with the Gamma function $\Gamma(s)$:
 \begin{equation}
@@
 \end{equation}
-Equation~\eqref{eq:frac_integral} is known as the left-sided Riemann-Liouville fractional integral of order $\alpha$. 
+Recall that $\Gamma(s) := \int_0^{\infty} t^{s-1} e^{-t}\,dt$. Equation~\eqref{eq:frac_integral} is known as the left-sided Riemann-Liouville fractional integral of order $\alpha$. 
 % As an example if $f(t)=t$, $\alpha=\frac{1}{2}$ and $a'=0$ then 
@@
 \begin{equation}
+\label{eq:h}
 \widetilde{h}_t^{\alpha}(\tau) = t - \sqrt[\alpha]{t^{\alpha} - \Gamma(\alpha+1)\tau}.
@@
 Let $\mathsf{A} = \{0,0.2,0.4,0.6,0.8,1\}$.
-The graphs of $\widetilde{g}_{10}^{\alpha}(\tau)$ and $\widetilde{h}_{10}^{\alpha}(\tau)$ are depicted in Figure~\ref{fig:gandh}.
+The functions $\widetilde{g}_{10}^{\alpha}(\tau)$ and $\widetilde{h}_{10}^{\alpha}(\tau)$ are depicted in Figure~\ref{fig:gandh} for $\alpha\in\mathsf{A}$.\\
 
@@
 \noindent
-Podlubny also showed that we can assign a geometric meaning to the fractional integral in equation~\eqref{eq:rl_to_rs} by visualizing the equivalent Riemann-Stieltjes integral contained within the same equation using Bullock's geometric framework.
+Podlubny also showed that we can assign a geometric meaning to the fractional integral in equation~\eqref{eq:rl_to_rs} by visualizing the equivalent Riemann-Stieltjes integral contained within the same equation \cite{bullock88,podlubny02}.
 Consider the axis $\tau$, $\widetilde{g}_t^{\alpha}$ and $f(\tau)$.
@@
 \noindent
-Let $h_t^{\alpha}(\tau)$ be equal to the inverse of $g_t^{\alpha}(\tau)$.
+Let $h_t^{\alpha}(\tau)$ be equal to the inverse of $g_t^{\alpha}(\tau)$ (see equation~\ref{eq:h}).
 Interestingly, Theorem~\ref{t:conv} implies that we can use $h_t^{\alpha}(\tau)$ to convert equation~\eqref{eq:rl_to_c} into the following Riemann integral:
@@
 \label{eq:rl_to_r}
-\int_{g_t^{\alpha}(a')}^{\frac{t^{\alpha}}{\Gamma(\alpha+1)}+C} f\circ h_{\alpha}^t (\tau) d\tau.  
+\int_{g_t^{\alpha}(a')}^{g_t^{\alpha}(t)} f\circ h_{\alpha}^t (\tau) d\tau.  
 \end{equation}
@@
 The non-static non-rectangular sum-based geometric interpretation associated with equation~\ref{eq:ex1} is depicted in Figure~\ref{fig:geo1} (see Section~\ref{sec:rl_to_cav}).
-We elaborate on this below.\\
+We elaborate further below.\\
 
@@
 sizes are ignored).
-The curves in Figure~\ref{fig:geo1} associated with the infinitesimals obtained by varying $\alpha$, whilst keeping the value of $t$ fixed are quite different from one another (the aforementioned curves are not correlated).\\
+The curves in Figure~\ref{fig:geo1} associated with the infinitesimals obtained by varying $\alpha$, whilst keeping the value of $t$ fixed are quite different from one another (the aforementioned curves are only weakly correlated).\\
 
@@
 \includegraphics[width=0.75\textwidth]{func_eval1.pdf}
-\caption{Depicts the curves which are obtained by evaluating equation~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ using either equation~\eqref{eq:rs} or equation~\eqref{eq:option2}.}
+\caption{Depicts the curves which are obtained by evaluating equation~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ using either equation~\eqref{eq:rl_to_rs} or equation~\eqref{eq:rl_to_r}.}
 \label{fig:eval1}
@@
 \noindent
-If we evaluate the integral in equation~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ (using either equation~\eqref{eq:rl_to_rs} or equation~\eqref{eq:rl_to_r}) we obtain the curves depicted in in Figure~\ref{fig:eval1}.
+If we evaluate the integral in equation~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ (using either equation~\eqref{eq:rl_to_rs} or equation~\eqref{eq:rl_to_r}) we obtain the curves depicted in Figure~\ref{fig:eval1}.
 The area of the regions depicted in Figure~\ref{fig:geo1} are also plotted in Figure~\ref{fig:eval1} using circular markers.
@@
 Using the same coloring scheme in both figures makes it clear which of the area values in Figure~\ref{fig:eval1} can be associated with which regions in Figure~\ref{fig:geo1}.
-The validity of the geometric interpretation depicted in Figure~\ref{fig:geo1} is, therefore, corroborated by Figure~\ref{fig:eval1}.
+Figure~\ref{fig:eval1}, therefore validates the geometric interpretation depicted in Figure~\ref{fig:geo1}.
 \\
@@
 \section{Conclusion}
+\noindent
 In this paper we presented a novel geometric interpretation of the left-sided 

### 2019-10-25 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
added literature review

@@
 These additional restrictions on $f(x)$ and $g(x)$ are assumed to be true for the remainder of the paper and as such are not repeated again.
+As will become apparent later, these additional restictions reduce the number of fractional integrals we can visualize with the framework we propose in Section~\ref{sec:rl_to_cav}.
+However, this fact does not diminish the importance of the proposed framework as it allows us to gain deeper insight into the process of fractional integration.
 

### 2019-10-25 fractional/FCAA/Authors Kit (Updated)/einstein.py
added an idea around einstein

@@ -1,0 +1,37 @@
+import numpy as np
+from mpl_toolkits.mplot3d import Axes3D
+import matplotlib.pyplot as plt
+import random
+import math
+from matplotlib.collections import PolyCollection
+from matplotlib.colors import colorConverter
+from mpl_toolkits.mplot3d import Axes3D
+from mpl_toolkits.mplot3d.art3d import Poly3DCollection
+
+
+def x_t(t,v = 200):
+    x = v*t
+    return x
+
+def a_x(x,c=3e8,v = 200):
+    l = np.sqrt(1 - v**2/c**2)
+    a = v**(-1)*x - (v**(-1)*x)/l
+    return a
+
+t = np.linspace(0,1,200)
+
+
+
+
+xt = x_t(t,v=2.999999e8)
+
+x = np.linspace(0,xt[-1],1000)
+
+a = a_x(x,v=2.999999e8)
+
+plt.plot(t,xt)
+
+print(a)
+plt.plot(a,x)
+
+plt.show()

### 2019-10-25 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
final fixes

@@
 
-{\it MSC 2010\/}: 26A33
-                  %Secondary 33E12, 34A08, 34K37, 35R11, 60G22, ...
+{\it MSC 2010\/}: 26A33 and 26A42.%, 34A08, 34K37, 35R11, 60G22, ...
 
@@
 
-{\it Key Words and Phrases}: geometric interpretation, fractional calculus, left-sided Riemann-Liouville integral, cavalieri integral.
+{\it Key Words and Phrases}: fractional calculus, Cavalieri integral, geometric interpretation, left-sided Riemann-Liouville fractional integral and Riemann-Stieltjes integral.
 
@@
 In this article we specifically focus on the geometric interpretation of fractional integrals.
-To be more specific, we present a novel geometric interpretation of the left-sided Riemann-Liouville fractional integral based at $a'$ \cite{laurent1884}.
+To be more specific, we present a novel geometric interpretation of the left-sided Riemann-Liouville fractional integral $_{a'}I_t^{\alpha} f(t)$ based at $a'$ (see Section~\ref{sec:ls}) \cite{laurent1884}.
 We accomplish this by extending the geometric framework proposed by Podlubny \cite{podlubny02}.
@@
 \label{t:inv}
-The function $g(x)$ is equal to $h^{-1}(x)$.
+The mapping $g(x)$ is a strictly monotone continuous function and it is equal to $h^{-1}(x)$.
 \end{theorem}
@@
 \noindent
-Note that for all $K\in\mathbb{R}$ (see equation~\ref{eq:rs_identity}):
+Note that for all $K\in\mathbb{R}$ (see equation~\eqref{eq:rs_identity}):
 \begin{equation}
@@
 \end{equation}
-Substituting Equation~\eqref{eq:implies} into Equation~\eqref{eq:g_definition} eliminates both $a$ and $C$ from it. If we then solve for $a(y)$ we obtain:
+Substituting equation~\eqref{eq:implies} into equation~\eqref{eq:g_definition} eliminates both $a$ and $C$ from it. If we then solve for $a(y)$ we obtain:
 \begin{equation}
@@
 \item Compute $g(x) = \widetilde{g}(x) + C$.
-\item Compute $h(x) = g^{-1}(x)$.
 \item Compute $b = g(b')$ and $b(y) = a(y) + (b-a)$.
@@
 \noindent
-The above derivation implies that that not every Riemann-Stieltjes integral $\int_{a'}^{b'} f(x) d\,\widetilde{g}(x)$ can directly be converted into a Cavalieri integral.
+The above derivation was taken from \cite{grobler19} and implies that that not every Riemann-Stieltjes integral $\int_{a'}^{b'} f(x) d\,\widetilde{g}(x)$ can be converted into a Cavalieri integral.
 We normally need to first convert it into an equivalent Riemann-Stieltjes integral $\int_{a'}^{b'} f(x) d\,g(x)$.
@@
 The former conversion is achieved by computing the real-valued constant $C$.
-Once, $C$ is known the latter conversion follows trivially.
+Once $C$ is known the latter conversion follows trivially.
 The above steps should be clearer to the reader once they have worked through the example presented in Section~\ref{sec:cav_integral_example}.\\
@@
 Let the region $R$ be bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$ and $b(y)=4-y$.
-This region is depicted in Figure~\ref{fig:caval2}.\\
+This region is depicted in Figure~\ref{fig:caval2}.
+Note that in the case of $R$: $a=1$, $b=4$, $a'=\frac{1}{2}$ and $b'=2$.\\
 
@@
 \centering
-\includegraphics[width=0.75\textwidth]{fig13.pdf}
+\includegraphics[width=0.8\textwidth]{fig13.pdf}
 \caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$.
 In the case of $R$: $a=1$, $b=4$, $a'=\frac{1}{2}$ and $b'=2$.
-The figure also depicts the partition points $x_i^2$ as used in the Cavalieri sum (see Equation~\eqref{eq:cav_sum}).
+The figure also depicts the partition points $x_i^2$ as used in the Cavalieri sum (see equation~\eqref{eq:cav_sum}).
 Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
@@
 Let $(x_i^1)_{i=0}^{n}$ denote a partition on the $x$-axis, such that $a = x_0^1 < x_1^1 < \cdots < x_n^1 = b$, and $\Delta x_i^1 = x_{i+1}^1 - x_i^1$.
-We are now able to construct the following lower Cavalieri sum (see Equation~\ref{eq:c_low}):
+Consider the following lower Cavalieri sum (see equation~\ref{eq:c_low}):
 \begin{equation}
@@
 \end{equation}
-The partition points $(x_i^2)_{i=0}^{n}$ are depicted in Figure~\ref{fig:caval2}.
+The partition points $(x_i^1)_{i=0}^{n}$ and $(x_i^2)_{i=0}^{n}$ are depicted in Figure~\ref{fig:caval2}.
 Cavalieri's principle tells us that the area of integration strip $i$ is equal to $f(x_i^2)\Delta x_i^1$.
@@
 Fortunately, it is easy to convert a Cavalieri integral into an equivalent Riemann or Riemann-Stieltjes
-integral by using the functions $h$ and $g$ (see equation~\ref{eq:g_def} and equation~\ref{eq:h_def}). Expressed mathematically (see Theorem~\ref{t:conv}):
+integral by using the functions $h$ and $g$ (see equation~\eqref{eq:g_def} and equation~\eqref{eq:h_def}). Expressed mathematically (see Theorem~\ref{t:conv}):
 \begin{equation}
@@
 \end{equation}
-We can, therefore, evaluate equation~\ref{eq:main_cav} in one of two ways:
+We can, therefore, evaluate equation~\eqref{eq:main_cav} in one of two ways:
 \begin{equation}
@@
 \section{Left-sided Riemann-Liouville Fractional Integral}
-\noindent
-For the sake of completeness, let us review the definition of the left-sided Riemann-Liouville fractional integral of order $\alpha$ (based at $a'$) \cite{laurent1884}. Let
+\label{sec:ls}
+\noindent
+For the sake of completeness, let us review the definition of the left-sided Riemann-Liouville fractional integral of order $\alpha$ based at $a'$ \cite{laurent1884}. Let
 \begin{equation}
@@
 \end{equation}
-Please note that in this paper from this point onwards our variable of integration will be $\tau$ instead of $x$.
+Please note that from this point onwards our variable of integration will be $\tau$ instead of $x$.
 It is of our opinion that this notational change improves the readability of the paper (if $\tau$ is our variable of integration then it makes sense to choose $t$ as our upper integration limit).\\
@@
 % \end{equation}
-The definition in equation~\eqref{eq:cauchy} can now be extended to an arbitrary fractional order by replacing $(n-1)!$ with the Gamma function $\Gamma(s)$:
+The definition in equation~\eqref{eq:cauchy} can now be extended to an arbitrary fractional order by replacing $(n-1)!$ with the Gamma function $\Gamma(\alpha)$:
 \begin{equation}
@@
 \end{equation}
-Recall that $\Gamma(s) := \int_0^{\infty} t^{s-1} e^{-t}\,dt$. Equation~\eqref{eq:frac_integral} is known as the left-sided Riemann-Liouville fractional integral of order $\alpha$. 
+Recall that $\Gamma(\alpha) := \int_0^{\infty} k^{\alpha-1} e^{-k}\,dk$. Equation~\eqref{eq:frac_integral} is known as the left-sided Riemann-Liouville fractional integral of order $\alpha$. 
 % As an example if $f(t)=t$, $\alpha=\frac{1}{2}$ and $a'=0$ then 
@@
 As is indicated in the figure, the graphs contained in each row of the subfigure-grid are obtained by varying $\alpha$, while the graphs contained in each column of the subfigure-grid are obtained by varying $t$.
-The fence itstelf is depicted in green.
+The fence in each subfigure is depicted in green.
 The areas depicted in red (the shadow of the fence) correspond to the value obtained when $\frac{1}{\Gamma(\alpha)}\int_{0}^{t}(t-\tau)^{\alpha-1}\sqrt{\tau}~d\tau$ is evaluated.
-The surface which is obtained by extending the curve $f(\tau)$ and $\widetilde{g}_t^{\alpha}(\tau)$ along the $\widetilde{g}$ and $f$ direction is depicted in cyan and blue, respectively.
-The intersection between the blue and cyan
-surfaces represents the curve that determines the height of the aforementioned fence (and is depicted as a dashed curve).   
+The surface which is obtained by extending the curve $f(\tau)$ and $\widetilde{g}_t^{\alpha}(\tau)$ along the $\widetilde{g}$ and $f$ direction is depicted in cyan and blue, respectively (in each subfigure).
+The intersection between the blue and cyan surfaces in each subfigure represents the curve that determines the height of the fence in each subfigure (it is depicted as a dashed curve).
 }
@@
 \noindent
-Let $R_t^{\alpha}$ denote the region which is bounded by $a_t^{\alpha}(y)$, $b_t^{\alpha}(y)$, $f(t)$ and the $\tau$-axis.
+Let $R_t^{\alpha}$ denote the region which is bounded by $a_t^{\alpha}(y)$, $b_t^{\alpha}(y)$, $f(\tau)$ and the $\tau$-axis.
 Moreover, let $A_{t}^{\alpha}$ denote the area of $R_t^{\alpha}$.
 Equation~\ref{eq:rl_to_c} implies that when we evaluate $_{a'}I_t^{\alpha}\,f(t)$ we obtain $A_{t}^{\alpha}$.
-In other words, when we evaluate equation~\ref{eq:rl_to_c} we are actually summing together the area of an infinite number of non-rectangular infinitesimals inscribing $R_t^{\alpha}$.
-The aforementioned infinitesimals are, however, non-static, since they need to be translations of $a(y)_t^{\alpha}$.
+In other words, when we evaluate equation~\eqref{eq:rl_to_c} we are actually summing together the area of an infinite number of non-rectangular infinitesimals inscribing $R_t^{\alpha}$.
+The aforementioned infinitesimals are, however, non-static, since they need to be translations of $a_t^{\alpha}(y)$.
 The shape of these infitesimals are thus dependend on $\alpha$ and $t$.
@@
 \noindent
-Let $h_t^{\alpha}(\tau)$ be equal to the inverse of $g_t^{\alpha}(\tau)$ (see equation~\ref{eq:h}).
+Let $h_t^{\alpha}(\tau)$ be equal to the inverse of $g_t^{\alpha}(\tau)$ (see equation~\eqref{eq:h}).
 Interestingly, Theorem~\ref{t:conv} implies that we can use $h_t^{\alpha}(\tau)$ to convert equation~\eqref{eq:rl_to_c} into the following Riemann integral:
@@
 \end{equation}
-The function $f(t) = t$ is depicted in Figure~\ref{fig:geo1}. We can now convert the above fractional integral into a Cavalieri integral (see Section~\ref{sec:rl_to_cav}):
+We can now convert the above fractional integral into a Cavalieri integral (see Section~\ref{sec:rl_to_cav}):
 \begin{equation}
@@
 Note, that for this example $a'=a=0$.
-The non-static non-rectangular sum-based geometric interpretation associated with equation~\ref{eq:ex1} is depicted in Figure~\ref{fig:geo1} (see Section~\ref{sec:rl_to_cav}).
+The non-static non-rectangular sum-based geometric interpretation associated with equation~\eqref{eq:ex1} is depicted in Figure~\ref{fig:geo1} (see Section~\ref{sec:rl_to_cav}).
 We elaborate further below.\\
@@
 \noindent
-Let $\mathsf{T}=\{2,4,6,8,10\}$ and $\mathsf{A} = \{0,0.2,0.4,0.6,0.8,1\}$.
-Moreover, Let $R_{t}^{\alpha}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{t}^{\alpha}(y)$.
+Let $\mathsf{T}=\{2,4,6,8,10\}$ and $\mathsf{A} = \{0.2,0.4,0.6,0.8\}$.
+Moreover, let $R_{t}^{\alpha}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{t}^{\alpha}(y)$.
 Note that $b_{t}^{\alpha}(y)$ forms the
@@
 Interestingly, their shape is more affected by $\alpha$ than by $t$.
-The curves in Figure~\ref{fig:geo1} that are associated with the infinitesimals obtained by varying $t$, whilst keeping the value of $\alpha$ fixed are very similar in nature and there exists a high degree of correlation between the aforementioned curves (if their
-sizes are ignored).
-The curves in Figure~\ref{fig:geo1} associated with the infinitesimals obtained by varying $\alpha$, whilst keeping the value of $t$ fixed are quite different from one another (the aforementioned curves are only weakly correlated).\\
+The curves in Figure~\ref{fig:geo1} that are associated with the infinitesimals obtained by varying $t$, whilst keeping the value of $\alpha$ fixed are very similar in nature (if their
+sizes are ignored). The curves in Figure~\ref{fig:geo1} associated with the infinitesimals obtained by varying $\alpha$, whilst keeping the value of $t$ fixed are quite different from one another.\\
 
@@
 \includegraphics[width=0.75\textwidth]{func_eval1.pdf}
-\caption{Depicts the curves which are obtained by evaluating equation~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ using either equation~\eqref{eq:rl_to_rs} or equation~\eqref{eq:rl_to_r}.}
+\caption{Depicts the curves which are obtained by evaluating equation~\eqref{eq:ex1_raw} for all $\alpha\in \mathsf{A}$ using either equation~\eqref{eq:rl_to_rs} or equation~\eqref{eq:rl_to_r}.}
 \label{fig:eval1}
@@
 \noindent
-If we evaluate the integral in equation~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ (using either equation~\eqref{eq:rl_to_rs} or equation~\eqref{eq:rl_to_r}) we obtain the curves depicted in Figure~\ref{fig:eval1}.
+If we evaluate the integral in equation~\eqref{eq:ex1_raw} for all $\alpha\in \mathsf{A}$ (using either equation~\eqref{eq:rl_to_rs} or equation~\eqref{eq:rl_to_r}) we obtain the curves depicted in Figure~\ref{fig:eval1}.
 The area of the regions depicted in Figure~\ref{fig:geo1} are also plotted in Figure~\ref{fig:eval1} using circular markers.
@@
 Note, that for this example $a'=a=0$.
-The non-static non-rectangular sum-based geometric interpretation associated with equation~\ref{eq:ex2_cav} is depicted in Figure~\ref{fig:geo2} (see Section~\ref{sec:rl_to_cav}).
+The non-static non-rectangular sum-based geometric interpretation associated with equation~\eqref{eq:ex2_cav} is depicted in Figure~\ref{fig:geo2} (see Section~\ref{sec:rl_to_cav}).
 
@@
 obtained by summing toghether the area of an infinite number of non-static non-rectangular infinitesimals.
-The shape of the infinitesimals used within the aforementioned sum depend on the order and the upper integration limit of the fractional integral under consideration.
+The shape of the infinitesimals used within the aforementioned sum depend on the order of integration and the upper integration limit of the fractional integral under consideration.
 

### 2019-10-28 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
added minor fixes

@@
  \begin{abstract}In this paper we present a novel geometric interpretation of the left-sided Riemann-Liouville fractional integral.
-We found that a Riemann-Liouville integral can be thought of as the area obtained by summing together the area of an infinite number of non-rectangular infinitesimals whose shape is determined by the integral's order of integration and its upper integration limit.
-This geometric interpretation is quite useful from a pedagogical perspective as it is very similar
-in nature to the geometric interpretation of the Riemann integral.
+We found that a Riemann-Liouville fractional integral can be thought of as the area which is obtained by summing together the area of an infinite number of non-rectangular infinitesimals.
+The shape of the aforementioned infinitesimals depend on the order of integration and the upper integration limit of the fractional integral that is being evaluated.
+This geometric interpretation is quite useful, pedagogically speaking, as it is very similar in nature to the geometric interpretation of the Riemann integral.
 
@@
 The mathematical discipline in which we study the extension of derivatives and integrals to non-integer orders is known as fractional calculus. Euler, Liouville and Riemann laid most 
-of the theoretical groundwork, which was needed to develop the field of fractional calculus \cite{laurent1884}. Fractional calculus has now developed into a mature discipline \cite{machado17}. 
+of the theoretical groundwork, which was needed to develop the field of fractional calculus \cite{laurent1884}. Fractional calculus is now a mature discipline \cite{machado17}. 
 However, there is one aspect of the discipline which only started to develop fairly recently: its physical and geometric interpretability.
@@
 a Riemann-Stieltjes integral can be converted into a Cavalieri integral \cite{ackermann12,grobler19}.
-Combining these two ideas results in the following geometric interpretation: the Riemann-Liouville fractional integral can be interpreted as the area which is obtained by summing together the area of an infinite number of non-rectangular infinitesimals whose shape is determined by the order of integration $\alpha$ and the integration limit $t$.\\
+Combining these two ideas results in the following geometric interpretation: the Riemann-Liouville fractional integral $_{a'}I_t^{\alpha} f(t)$ can be interpreted as the area which is obtained by summing together the area of an infinite number of non-rectangular infinitesimals.
+The shape
+of the aforementioned infinitesimals is determined by the order of integration $\alpha$ and the integration limit $t$ of the fractional integral under consideration.\\
 
@@
 \end{equation}
-with $(x_i)_{i=0}^n$ being arbitrary partition points on the $x$-axis. 
+with $(x_i)_{i=0}^n$ being arbitrary partition points on the $x$-axis (such that $a' = x_0 \leq x_1 \leq \cdots \leq x_n = b'$).
 The function $g$ is known as the integrator and if it is monotone increasing then it maps points in the interval $[a',b,]$ to the interval $[a,b]$, with $a = g(a')$ and $b = g(b')$.
@@
 \noindent
-The above derivation was taken from \cite{grobler19} and implies that that not every Riemann-Stieltjes integral $\int_{a'}^{b'} f(x) d\,\widetilde{g}(x)$ can be converted into a Cavalieri integral.
+The above derivation was taken from \cite{grobler19} and implies that not every Riemann-Stieltjes integral $\int_{a'}^{b'} f(x) d\,\widetilde{g}(x)$ can be converted into a Cavalieri integral.
 We normally need to first convert it into an equivalent Riemann-Stieltjes integral $\int_{a'}^{b'} f(x) d\,g(x)$.
@@
 In the case of $R$: $a=1$, $b=4$, $a'=\frac{1}{2}$ and $b'=2$.
-The figure also depicts the partition points $x_i^2$ as used in the Cavalieri sum (see equation~\eqref{eq:cav_sum}).
+The figure also depicts the partition points $(x_i^1)_{i=0}^{n}$ and $(x_i^2)_{i=0}^{n}$ as used in the Cavalieri sum (see equation~\eqref{eq:cav_sum}).
 Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
@@
 Moreover, let $A_{t}^{\alpha}$ denote the area of $R_t^{\alpha}$.
-Equation~\ref{eq:rl_to_c} implies that when we evaluate $_{a'}I_t^{\alpha}\,f(t)$ we obtain $A_{t}^{\alpha}$.
+Equation~\eqref{eq:rl_to_c} implies that when we evaluate $_{a'}I_t^{\alpha}\,f(t)$ we obtain $A_{t}^{\alpha}$.
 In other words, when we evaluate equation~\eqref{eq:rl_to_c} we are actually summing together the area of an infinite number of non-rectangular infinitesimals inscribing $R_t^{\alpha}$.
@@
 \end{equation}
-We can, therefore, evaluate equation~\eqref{eq:frac_integral} in one of two ways: we can either evaluate equation~\eqref{eq:rl_to_rs} or we can evaluate equation~\eqref{eq:rl_to_r}.
-
-\subsection{Examples}
+We can, therefore, evaluate equation~\eqref{eq:frac_integral} in one of two ways: we can either evaluate equation~\eqref{eq:rl_to_rs} or we can evaluate equation~\eqref{eq:rl_to_r}.\\
+
+%\subsection{Examples}
+\noindent
 Consider the following fractional integral:
@@
 obtained by summing toghether the area of an infinite number of non-static non-rectangular infinitesimals.
-The shape of the infinitesimals used within the aforementioned sum depend on the order of integration and the upper integration limit of the fractional integral under consideration.
+The shape of the infinitesimals used within the aforementioned sum depend on the order of integration and the upper integration limit of the fractional integral being evaluated.
 

### 2019-10-28 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
spelling mistakes

@@
 \begin{theorem}
-The mapping $h(x)$ is a strictly monotone continuous function. The function $h(x)$ is, therefore, invertable.
+The mapping $h(x)$ is a strictly monotone continuous function. The function $h(x)$ is, therefore, invertible.
 \end{theorem}
@@
 \noindent
-The theorems and definitions presented in this section impose much greater restrictions on $g(x)$ and $f(x)$ than that mentioned in the begining of Section~\ref{sec:rs}.
-The functions $g(x)$ and $f(x)$ now also need to be differentiable and invertable.
+The theorems and definitions presented in this section impose much greater restrictions on $g(x)$ and $f(x)$ than that mentioned in the beginning of Section~\ref{sec:rs}.
+The functions $g(x)$ and $f(x)$ now also need to be differentiable and invertible.
 Moreover, $a(0)$ must exist.
 These additional restrictions on $f(x)$ and $g(x)$ are assumed to be true for the remainder of the paper and as such are not repeated again.
-As will become apparent later, these additional restictions reduce the number of fractional integrals we can visualize with the framework we propose in Section~\ref{sec:rl_to_cav}.
+As will become apparent later, these additional restrictions reduce the number of fractional integrals we can visualize with the framework we propose in Section~\ref{sec:rl_to_cav}.
 However, this fact does not diminish the importance of the proposed framework as it allows us to gain deeper insight into the process of fractional integration.
@@
 It, however, seems much more straightforward to approximate the area of $R$ via non-overlapping non-rectangular integration strips that inscribe $R$.
-This can only be accomplished if the sides of the aforementioned integration strips are tranlsations of the function $a(y)$.\\
+This can only be accomplished if the sides of the aforementioned integration strips are translations of the function $a(y)$.\\
 
@@
 \end{equation}
-Moreover, the function $\widetilde{g}_t^{\alpha}(\tau)$ is invertable. Its inverse is:
+Moreover, the function $\widetilde{g}_t^{\alpha}(\tau)$ is invertible. Its inverse is:
 \begin{equation}
@@
 \end{equation}
-The function $\widetilde{g}_t^{\alpha}$ is invertable, since $\frac{d \widetilde{g}_t^{\alpha}}{d\tau}=\frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)} > 0$ for $\tau\in(-\infty,t]$.
+The function $\widetilde{g}_t^{\alpha}$ is invertible, since $\frac{d \widetilde{g}_t^{\alpha}}{d\tau}=\frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)} > 0$ for $\tau\in(-\infty,t]$.
 Let $\mathsf{A} = \{0,0.2,0.4,0.6,0.8,1\}$.
@@
 The ``shadow'' of this fence, i.e.
-the area under the curve which is obtained by projecting this fence onto the $\widetilde{g}f$-plane corresonds to the value which is obtained when equation~\eqref{eq:rl_to_rs} is evaluated.
+the area under the curve which is obtained by projecting this fence onto the $\widetilde{g}f$-plane corresponds to the value which is obtained when equation~\eqref{eq:rl_to_rs} is evaluated.
 As an example, the geometric interpretation so obtained for the integrand $f(t)=\sqrt{t}$ is depicted in Figure~\ref{fig:vis_old}.
@@
 The fence in each subfigure is depicted in green.
-The areas depicted in red (the shadow of the fence) correspond to the value obtained when $\frac{1}{\Gamma(\alpha)}\int_{0}^{t}(t-\tau)^{\alpha-1}\sqrt{\tau}~d\tau$ is evaluated.
+The areas depicted in red (the shadows of the fences) correspond to the value obtained when $\frac{1}{\Gamma(\alpha)}\int_{0}^{t}(t-\tau)^{\alpha-1}\sqrt{\tau}~d\tau$ is evaluated.
 The surface which is obtained by extending the curve $f(\tau)$ and $\widetilde{g}_t^{\alpha}(\tau)$ along the $\widetilde{g}$ and $f$ direction is depicted in cyan and blue, respectively (in each subfigure).
@@
 The aforementioned infinitesimals are, however, non-static, since they need to be translations of $a_t^{\alpha}(y)$.
-The shape of these infitesimals are thus dependend on $\alpha$ and $t$.
+The shape of these infinitesimals are thus dependent on $\alpha$ and $t$.
 In summary, we can obtain a novel geometric interpretation of
 $_{a'}I_t^{\alpha}\,f(t)$ by first converting it into a Cavalieri integral.
-We will take the liberty in this paper to refer to the depiction of the aformentioned Cavalieri integral as the non-static non-rectangular sum-based geometric interpretation of $_{a'}I_t^{\alpha}\,f(t)$.\\
+We will take the liberty in this paper to refer to the depiction of the aforementioned Cavalieri integral as the non-static non-rectangular sum-based geometric interpretation of $_{a'}I_t^{\alpha}\,f(t)$.\\
 
@@
 The value so obtained is $A_{t}^{\alpha}$ (see Section~\ref{sec:rl_to_cav}).
-Note that, the infinitesimals that are used in the aformentioned sum are translations of $R_{t}^{\alpha}$'s right edge.
+Note that, the infinitesimals that are used in the aforementioned sum are translations of $R_{t}^{\alpha}$'s right edge.
 The following observations can now be made by inspecting Figure~\ref{fig:geo1}:
@@
 Riemann-Liouville fractional integral. It can be interpreted as the value which is 
-obtained by summing toghether the area of an infinite number of non-static non-rectangular infinitesimals.
+obtained by summing together the area of an infinite number of non-static non-rectangular infinitesimals.
 The shape of the infinitesimals used within the aforementioned sum depend on the order of integration and the upper integration limit of the fractional integral being evaluated.

### 2019-10-30 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
worked in suggestions from CMJ

@@
 In this article we specifically focus on the geometric interpretation of fractional integrals.
-To be more specific, we present a novel geometric interpretation of the left-sided Riemann-Liouville fractional integral $_{a'}I_t^{\alpha} f(t)$ based at $a'$ (see Section~\ref{sec:ls}) \cite{laurent1884}.
+To be more specific, we present a novel geometric interpretation of the left-sided Riemann-Liouville fractional integral based at $a'$ (see Section~\ref{sec:ls}) \cite{laurent1884}.
 We accomplish this by extending the geometric framework proposed by Podlubny \cite{podlubny02}.
@@
 a Riemann-Stieltjes integral can be converted into a Cavalieri integral \cite{ackermann12,grobler19}.
-Combining these two ideas results in the following geometric interpretation: the Riemann-Liouville fractional integral $_{a'}I_t^{\alpha} f(t)$ can be interpreted as the area which is obtained by summing together the area of an infinite number of non-rectangular infinitesimals.
+Combining these two ideas results in the following geometric interpretation: the Riemann-Liouville fractional integral $_{a'}I_t^{\alpha} f(t)$ (see Section~\ref{sec:ls}) can be interpreted as the area which is obtained by summing together the area of an infinite number of non-rectangular infinitesimals.
 The shape
-of the aforementioned infinitesimals is determined by the order of integration $\alpha$ and the integration limit $t$ of the fractional integral under consideration.\\
+of the aforementioned infinitesimals is determined by the order of integration $\alpha$ and the integration limit $t$ of the fractional integral being evaluated.\\
 
@@
 \end{equation}
-with $(x_i)_{i=0}^n$ being arbitrary partition points on the $x$-axis (such that $a' = x_0 \leq x_1 \leq \cdots \leq x_n = b'$).
-The function $g$ is known as the integrator and if it is monotone increasing then it maps points in the interval $[a',b,]$ to the interval $[a,b]$, with $a = g(a')$ and $b = g(b')$.
+with $(x_i)_{i=0}^n$ being an arbitrary partition of $[a',b']$.
+The function $g$ is known as the integrator and if it is monotone increasing then it maps points in the interval $[a',b']$ to the interval $[a,b]$, with $a = g(a')$ and $b = g(b')$.
 The integral in equation~\eqref{eq:g_int2} is hard to evaluate in its present form.
@@
 The definition of the Cavalieri integral is presented in Definition~\ref{def:cav_integral}.
-It is, however, our experience that Definition~\ref{def:cav_integral} is hard to assimilate if it is encounterd by a reader for the first time.
-We, therefore, encourage readers who are not familiar with the Cavalieri integral to rather first read Section~\ref{sec:cav_integral_example} instead.
-The reader who is not familiar with the Cavalieri integral should, however, feel free to refer back to the definitions presented in this section when things in Section~\ref{sec:cav_integral_example} become unclear.
+It is, however, our experience that Definition~\ref{def:cav_integral} is hard to assimilate if it is encountered by a reader for the first time.
+We, therefore, encourage readers who are not familiar with the Cavalieri integral to rather first read Section~\ref{sec:cav_integral_example} before continuing to read the current section.
+The reader who is unfamiliar with the Cavalieri integral should, however, refer back to the definitions presented in this section when things in Section~\ref{sec:cav_integral_example} become unclear.
 Moreover, the definitions presented below were taken from \cite{ackermann12}.
@@
 \noindent
+The symbol $\circ$ denotes function composition.
 Let $a(y)$ be a translational function with respect to a function $f(x)$ on the interval $[a,b]$.
@@
 The mapping $h : [a, b] \rightarrow [a',b']$, which maps $x_i^1 \in [a, b]$ to $x_i^2 \in [a',b']$, is defined as
-$h(x_i^1) =$ $\{x_i^2 \in [a' ,b'] | a\circ f(x_i^2) + [x_i^1 - a] = x_i^2$ , $a = a(0)\}$
+$h(x_i^1) :=$ $\{x_i^2 \in [a' ,b'] | a\circ f(x_i^2) + [x_i^1 - a] = x_i^2$ , $a = a(0)\}$
 \end{definition}
@@
 The mapping $g:[a', b'] \rightarrow [a, b]$, which maps $x_i^2 \in [a' , b']$ to $x_i^1\in [a, b]$,
-is defined as $g(x_i^2) = x_i^2 - a \circ f (x_i^2) + a$.
+is defined as $g(x_i^2) := x_i^2 - a \circ f (x_i^2) + a$.
 \end{definition}
@@
 \noindent
-The functions $h(x)$ and $g(x)$ are known as the transformation function and the inverse transformation function, respectively. Furthermore,
+The notation $(\cdot)^{-1}$ denotes the functional inverse. The functions $h(x)$ and $g(x)$ are known as the transformation function and the inverse transformation function, respectively. Furthermore,
+\begin{equation}
+\label{eq:h_def}
+h(x) = g^{-1}(x). 
+\end{equation}
+and
 \begin{equation}
@@
 g(x) = x - a\circ f(x) + a 
-\end{equation}
-and
-\begin{equation}
-\label{eq:h_def}
-h(x) = g^{-1}(x). 
 \end{equation}
@@
 If the transformation function $h$ is strictly increasing,
-the application of $h$ to the partition $\mathcal{P}_1$ induces a new partition $\mathcal{P}_2 = \{x_0^2, x_1^2,\cdots, x_n^2\}$.
+the application of $h$ to the partition $\mathcal{P}_1$ induces a new partition $\mathcal{P}_2 = \{x_0^2, x_1^2,\cdots, x_n^2\}$,  
+where $a' = x_0^2 \leq x_1^2 \leq \cdots \leq x_n^2 = b'$.
 Otherwise, if $h$ is strictly decreasing, the application of $h$ induces a reversed partition $\mathcal{P}_2 = \{x_n^2, \cdots, x_1^2,x_0^2\}$. It
@@
 \end{equation}
-Furthermore, recall that
+Furthermore, recall that (see equation~\ref{eq:g_def}):
 \begin{equation}
@@
 \end{equation}
-Moreover, let $C$ be a unique real-valued constant that satisfies: $g(x) := \widetilde{g}(x)+C$.\\
+Moreover, let $C$ be a real-valued constant that satisfies: $g(x) := \widetilde{g}(x)+C$.\\
 
@@
 This region is depicted in Figure~\ref{fig:caval2}.
-Note that in the case of $R$: $a=1$, $b=4$, $a'=\frac{1}{2}$ and $b'=2$.\\
+Let $a=1$, $b=4$, $a'=\frac{1}{2}$ and $b'=2$.
+Note that $a(y)$ is a translational function with respect to $f(x)$ on $[a,b]$.
+Moreover $a(y)$ and $b(y)$ intersect $f(x)$ at $a'$ and $b'$, respectively (see Definition~\ref{def:trans}).\\
 
@@
 Let $(x_i^1)_{i=0}^{n}$ denote a partition on the $x$-axis, such that $a = x_0^1 < x_1^1 < \cdots < x_n^1 = b$, and $\Delta x_i^1 = x_{i+1}^1 - x_i^1$.
-Consider the following lower Cavalieri sum (see equation~\ref{eq:c_low}):
+Furthermore, consider the following lower Cavalieri sum (see Definition~\ref{def:cav_integral} and equation~\ref{eq:c_low}):
 \begin{equation}
@@
 \end{equation}
-The partition points $(x_i^1)_{i=0}^{n}$ and $(x_i^2)_{i=0}^{n}$ are depicted in Figure~\ref{fig:caval2}.
+The partition points $(x_i^1)_{i=0}^{n}$ and $(x_i^2)_{i=0}^{n}$ are depicted in the left panel of Figure~\ref{fig:caval2} (if $n$ is set to 3).
 Cavalieri's principle tells us that the area of integration strip $i$ is equal to $f(x_i^2)\Delta x_i^1$.

### 2019-10-30 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
worked in suggestions from CMJ

@@
 \label{eq:h_def}
-h(x) = g^{-1}(x). 
+h(x) = g^{-1}(x) 
 \end{equation}
@@
 \centering
-\includegraphics[width=0.8\textwidth]{fig13.pdf}
+\includegraphics[width=0.75\textwidth]{fig13.pdf}
 \caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$.
@@
 \end{equation}
-The partition points $(x_i^1)_{i=0}^{n}$ and $(x_i^2)_{i=0}^{n}$ are depicted in the left panel of Figure~\ref{fig:caval2} (if $n$ is set to 3).
-Cavalieri's principle tells us that the area of integration strip $i$ is equal to $f(x_i^2)\Delta x_i^1$.
+The partition points $(x_i^1)_{i=0}^{n}$ and $(x_i^2)_{i=0}^{n}$ are depicted in the left panel of Figure~\ref{fig:caval2} (for the case when $n$ is set to 3).
+Note that $\Delta x_i^1$ represents the width, $f(x_i^2)$ the height and $f(x_i^2)\Delta x_i^1$ the area of the $i^{\textrm{th}}$ non-rectangular integration strip depicted in Figure~\ref{fig:caval2} (due to Cavalieri's principle).
 Equation~\eqref{eq:cav_sum}, therefore, approximates the area of $R$.
@@
 The natural question now arises, can we convert a Riemann-Stieltjes integral into a Cavalieri integral?
-As an example, can the following Riemann-Stieltjes integral be converted into a Cavalieri integral?
-\begin{equation}
-\int_{a'}^{b'} \,d\,\widetilde{g}(x) = \int_{\frac{1}{2}}^2 x\,d[2x+1].
-\end{equation}
+As an example, can $\int_{a'}^{b'} f(x)\,d\,\widetilde{g}(x) = \int_{\frac{1}{2}}^2 x\,d[2x+1]$ be converted into a Cavalieri integral?
+Note: $f(x) = x$ and $\widetilde{g}(x) = 2x+1$.
 To accomplish this task we first need to compute the following (see Section~\ref{sec:cav_integral}):
@@
  \item $a(y) = f^{-1}(y) - \widetilde{g}\circ f^{-1}(y)+ \widetilde{g}(a') = 1-y$.
- \item $a = a(0) = 1$.
- \item $C = a - \widetilde{g}(a') = -1$.
+ \item $a = a(0) = 1$ and $C = a - \widetilde{g}(a') = -1$.
  \item $g(x) = \widetilde{g}(x) + C = 2x$.
@@
 % \end{equation}
-The definition in equation~\eqref{eq:cauchy} can now be extended to an arbitrary fractional order by replacing $(n-1)!$ with the Gamma function $\Gamma(\alpha)$:
+The definition in equation~\eqref{eq:cauchy} can now be extended to an arbitrary fractional order by replacing $n$ with the real value $\alpha$ and $(n-1)!$ with the Gamma function $\Gamma(\alpha)$:
 \begin{equation}
@@
 
-\section{Geometric Interpretation of the Left-sided Riemann-Liouville Fractional Integral}
-
-\subsection{Converting into a Riemann-Stieltjes integral}
+\section{Converting into a Riemann-Stieltjes integral}
 Podlubny showed that the Left-sided Riemann-Liouville fractional integral can be converted into a Riemann-Stieltjes integral \cite{podlubny02}:
@@
 The function $\widetilde{g}_t^{\alpha}$ is invertible, since $\frac{d \widetilde{g}_t^{\alpha}}{d\tau}=\frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)} > 0$ for $\tau\in(-\infty,t]$.
-Let $\mathsf{A} = \{0,0.2,0.4,0.6,0.8,1\}$.
-The functions $\widetilde{g}_{10}^{\alpha}(\tau)$ and $\widetilde{h}_{10}^{\alpha}(\tau)$ are depicted in Figure~\ref{fig:gandh} for $\alpha\in\mathsf{A}$.\\
+Let $\mathsf{A} = \{0.2,0.4,0.6,0.8\}$.
+The functions $\widetilde{g}_{10}^{\alpha}(\tau)$ and $\widetilde{h}_{10}^{\alpha}(\tau)$ are depicted in Figure~\ref{fig:gandh} for $\alpha\in\mathsf{A}\cup\{0,1\}$.\\
 
@@
 \centering
-\includegraphics[width=0.75\textwidth]{gh.pdf}
-\caption{This figure depicts the curves of $\widetilde{g}_{10}^{\alpha}(\tau)$ and $\widetilde{h}_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}$.
+\includegraphics[width=0.7\textwidth]{gh.pdf}
+\caption{This figure depicts the curves of $\widetilde{g}_{10}^{\alpha}(\tau)$ and $\widetilde{h}_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}\cup\{0,1\}$.
 The curves associated with $\widetilde{g}$ are plotted using solid lines, while the curves plotted using dashed lines are associated with $\widetilde{h}$.
@@
 \centering
-\includegraphics[width=1.0\textwidth]{vis_old.pdf}
+\includegraphics[width=0.9\textwidth]{vis_old.pdf}
 \caption{This figure depicts the visualization of $\frac{1}{\Gamma(\alpha)}\int_{0}^{t}(t-\tau)^{\alpha-1}\sqrt{\tau}~d\tau$ using the geometric framework proposed by Podlubny.
@@
 
-\subsection{Converting into a Cavalieri integral}
+\section{Converting into a Cavalieri integral}
 \label{sec:rl_to_cav}
-Recall that,
+Recall that:
 \begin{equation}
@@
  \item $g_t^{\alpha}(\tau) = \widetilde{g}_t^{\alpha}(\tau) + C$.
- \item $b = g_t^{\alpha}(b')$ and $b_t^{\alpha}(y) = a_t^{\alpha}(y) + (b-a)$.
+ \item $b = g_t^{\alpha}(t)$ and $b_t^{\alpha}(y) = a_t^{\alpha}(y) + (b-a)$.
 \end{itemize}
@@
 \noindent
-Let $h_t^{\alpha}(\tau)$ be equal to the inverse of $g_t^{\alpha}(\tau)$ (see equation~\eqref{eq:h}).
+Let $h_t^{\alpha}(\tau)$ be equal to the functional inverse of $g_t^{\alpha}(\tau)$ (see equation~\eqref{eq:h}).
 Interestingly, Theorem~\ref{t:conv} implies that we can use $h_t^{\alpha}(\tau)$ to convert equation~\eqref{eq:rl_to_c} into the following Riemann integral:
@@
 \end{equation}
-We can, therefore, evaluate equation~\eqref{eq:frac_integral} in one of two ways: we can either evaluate equation~\eqref{eq:rl_to_rs} or we can evaluate equation~\eqref{eq:rl_to_r}.\\
-
-%\subsection{Examples}
+We can, therefore, evaluate equation~\eqref{eq:frac_integral} in one of two ways: we can either evaluate equation~\eqref{eq:rl_to_rs} or we can evaluate equation~\eqref{eq:rl_to_r}.
+
+\section{Examples}
 \noindent
@@
 \centering
-\includegraphics[width=0.75\textwidth]{geo_int1.pdf}
+\includegraphics[width=0.7\textwidth]{geo_int1.pdf}
 \caption{The non-static non-rectangular sum-based geometric interpretation of equation~\eqref{eq:ex1_raw}.}
@@
 right-most edge of $R_{t}^{\alpha}$.
-The region $R_{t}^{\alpha}$ is not bounded by $a_{t}^{\alpha}(y)$, since $a'=a=0$.
 Moreover, let $A_{t}^{\alpha}$ denote the area of $R_{t}^{\alpha}$ and let $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}=\{R_t^{\alpha}|t\in\mathsf{T},~\alpha\in\mathsf{A}\}$.
@@
 The value so obtained is $A_{t}^{\alpha}$ (see Section~\ref{sec:rl_to_cav}).
-Note that, the infinitesimals that are used in the aforementioned sum are translations of $R_{t}^{\alpha}$'s right edge.
+Note that, the region $R_{t}^{\alpha}$ is not bounded by $a_{t}^{\alpha}(y)$, since $a'=a=0$.
+Furthermore, the infinitesimals that are used in the aforementioned sum are translations of $R_{t}^{\alpha}$'s right edge.
 The following observations can now be made by inspecting Figure~\ref{fig:geo1}:
@@
 \centering
-\includegraphics[width=0.75\textwidth]{func_eval1.pdf}
+\includegraphics[width=0.7\textwidth]{func_eval1.pdf}
 \caption{Depicts the curves which are obtained by evaluating equation~\eqref{eq:ex1_raw} for all $\alpha\in \mathsf{A}$ using either equation~\eqref{eq:rl_to_rs} or equation~\eqref{eq:rl_to_r}.}
@@
 \centering
-\includegraphics[width=0.75\textwidth]{geo_int2.pdf}
+\includegraphics[width=0.7\textwidth]{geo_int2.pdf}
 \caption{The non-static non-rectangular sum-based geometric interpretation of equation~\eqref{eq:ex2}.}
@@
 
-\bibitem{podlubny02} Podlubny,~I. Geometric and Physical Interpretation of Fractional Integration and Fractional Differentiation, \textit{Fract. Calc. Appl. Anal.} \textbf{5}, No 4 (2002), 367--386.
+\bibitem{podlubny02} I.~Podlubny, Geometric and Physical Interpretation of Fractional Integration and Fractional Differentiation, \textit{Fract. Calc. Appl. Anal.} \textbf{5}, No 4 (2002), 367--386.
 

### 2019-10-30 fractional/FCAA/Authors Kit (Updated)/wire3d_demo.py
code as well

@@ -113,7 +113,7 @@ for i in range(3):
 
         if counter == 2:
            ax.set_xlabel(r'$\tau$',labelpad=10)
-	   ax.set_ylabel(r'$g_t^{\alpha}(\tau)$',labelpad=18)
+	   ax.set_ylabel(r'$\widetilde{g}_t^{\alpha}(\tau)$',labelpad=18)
 	   ax.set_zlabel(r'$f(\tau)$')
 
         if counter <=3:

### 2019-10-31 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
final version of paper

@@
 The mathematical discipline in which we study the extension of derivatives and integrals to non-integer orders is known as fractional calculus. Euler, Liouville and Riemann laid most 
-of the theoretical groundwork, which was needed to develop the field of fractional calculus \cite{laurent1884}. Fractional calculus is now a mature discipline \cite{machado17}. 
-However, there is one aspect of the discipline which only started to develop fairly recently: its physical and geometric interpretability.
+of the theoretical groundwork, which was needed to develop the field of fractional calculus \cite{laurent1884}.
+Fractional calculus is over 300 years old \cite{machado17}.
+Interestingly, there is one aspect of the discipline which only started to develop fairly recently: its physical and geometric interpretability.
 At the first international conference on fractional calculus in
@@
 In this article we specifically focus on the geometric interpretation of fractional integrals.
-To be more specific, we present a novel geometric interpretation of the left-sided Riemann-Liouville fractional integral based at $a'$ (see Section~\ref{sec:ls}) \cite{laurent1884}.
+To be more specific, we present a novel geometric interpretation of the left-sided Riemann-Liouville fractional integral \cite{laurent1884}.
 We accomplish this by extending the geometric framework proposed by Podlubny \cite{podlubny02}.
@@
 a Riemann-Stieltjes integral can be converted into a Cavalieri integral \cite{ackermann12,grobler19}.
-Combining these two ideas results in the following geometric interpretation: the Riemann-Liouville fractional integral $_{a'}I_t^{\alpha} f(t)$ (see Section~\ref{sec:ls}) can be interpreted as the area which is obtained by summing together the area of an infinite number of non-rectangular infinitesimals.
+Combining these two ideas results in the following geometric interpretation: the Riemann-Liouville fractional integral $_{a'}I_t^{\alpha} f(t)$  based at $a'$ (see Section~\ref{sec:ls}) can be interpreted as the area which is obtained by summing together the area of an infinite number of non-rectangular infinitesimals.
 The shape
@@
 \label{eq:g_def}
-g(x) = x - a\circ f(x) + a 
+g(x) = x - a\circ f(x) + a. 
 \end{equation}
@@
 \begin{itemize}
-\item Compute $a = a(0)$.
-\item Compute $C = a - \widetilde{g}(a')$.
+\item Compute $a = a(0)$ and $C = a - \widetilde{g}(a')$.
 \item Compute $g(x) = \widetilde{g}(x) + C$.
@@
 \label{eq:main_cav}
-\int_{a(y)}^{b(y)}f(x)\,dx =\int_a^b f \circ h (x)\, dx = \int_{a'}^{b'} f(x) dg(x),
+\int_{a(y)}^{b(y)}f(x)\,dx =\int_a^b f \circ h (x)\, dx = \int_{a'}^{b'} f(x) dg(x).
 \end{equation}
@@
 \end{equation}
-Recall that $\Gamma(\alpha) := \int_0^{\infty} k^{\alpha-1} e^{-k}\,dk$. Equation~\eqref{eq:frac_integral} is known as the left-sided Riemann-Liouville fractional integral of order $\alpha$. 
+Recall that $\Gamma(\alpha) := \int_0^{\infty} k^{\alpha-1} e^{-k}\,dk$.
+Equation~\eqref{eq:frac_integral} is known as the left-sided Riemann-Liouville fractional integral of order $\alpha$ based at $a'$.
 % As an example if $f(t)=t$, $\alpha=\frac{1}{2}$ and $a'=0$ then 
@@
 \centering
-\includegraphics[width=0.7\textwidth]{gh.pdf}
+\includegraphics[width=0.75\textwidth]{gh.pdf}
 \caption{This figure depicts the curves of $\widetilde{g}_{10}^{\alpha}(\tau)$ and $\widetilde{h}_{10}^{\alpha}(\tau)$ for $\alpha\in\mathsf{A}\cup\{0,1\}$.
@@
 \centering
-\includegraphics[width=0.9\textwidth]{vis_old.pdf}
+\includegraphics[width=1.0\textwidth]{vis_old.pdf}
 \caption{This figure depicts the visualization of $\frac{1}{\Gamma(\alpha)}\int_{0}^{t}(t-\tau)^{\alpha-1}\sqrt{\tau}~d\tau$ using the geometric framework proposed by Podlubny.
@@
  \item $a_t^{\alpha}(y) = f^{-1}(y) - \widetilde{g}_t^{\alpha}\circ f^{-1}(y)+ \widetilde{g}_t^{\alpha}(a')$.
- \item $a = a_t^{\alpha}(0)$.
- \item $C = a - \widetilde{g}_t^{\alpha}(a')$.
+ \item $a = a_t^{\alpha}(0)$ and $C = a - \widetilde{g}_t^{\alpha}(a')$.
  \item $g_t^{\alpha}(\tau) = \widetilde{g}_t^{\alpha}(\tau) + C$.
@@
 \centering
-\includegraphics[width=0.7\textwidth]{geo_int1.pdf}
+\includegraphics[width=0.75\textwidth]{geo_int1.pdf}
 \caption{The non-static non-rectangular sum-based geometric interpretation of equation~\eqref{eq:ex1_raw}.}
@@
 \centering
-\includegraphics[width=0.7\textwidth]{func_eval1.pdf}
+\includegraphics[width=0.75\textwidth]{func_eval1.pdf}
 \caption{Depicts the curves which are obtained by evaluating equation~\eqref{eq:ex1_raw} for all $\alpha\in \mathsf{A}$ using either equation~\eqref{eq:rl_to_rs} or equation~\eqref{eq:rl_to_r}.}
@@
 \centering
-\includegraphics[width=0.7\textwidth]{geo_int2.pdf}
+\includegraphics[width=0.75\textwidth]{geo_int2.pdf}
 \caption{The non-static non-rectangular sum-based geometric interpretation of equation~\eqref{eq:ex2}.}

### 2019-11-01 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
fixed bibliography

@@
 Consider the Riemann-Stieltjes integral $\int_{a'}^{b'} f(x)\,\widetilde{g}(x)$.
-Assume that $\widetilde{g}(x)$ is a differentiable and invertable real-valued function on $[a',b']$.
+Assume that $\widetilde{g}(x)$ is a differentiable and invertible real-valued function on $[a',b']$.
 How do we go about converting $\int_{a'}^{b'} f(x)\,\widetilde{g}(x)$ into a Cavalieri integral?\\
@@
 
-\bibitem{laurent1884} H.~Laurent, (1884). Sur le calcul des d\'{e}riv\'{e}es \`{a} indices quelconques. \textit{Nouv Annales de Mathem\'{e}matiques.} \textbf{3}, No 3 (1884), 240--252.
+\bibitem{laurent1884} H.~Laurent. Sur le calcul des d\'{e}riv\'{e}es \`{a} indices quelconques. \textit{Nouv Annales de Mathem\'{e}matiques.} \textbf{3}, No 3 (1884), 240--252.
 
@@
 %physical
-\bibitem{nigmatullin92} R.R.~Nigmatullin. A fractional integral and its physical interpretation. \textit{Theor. and Math. Phys.} \textbf{90}, No 3 (1992): 242--251.
+\bibitem{nigmatullin92} R.R.~Nigmatullin. A fractional integral and its physical interpretation. \textit{Theor. and Math. Phys.} \textbf{90}, No 3 (1992), 242--251.
 
@@
 \bibitem{ross06} B.Ross, (Ed.).
-\textit{Fractional calculus and its applications: proceedings of the international conference held at the University of New Haven, June 1974}, \textbf{457}, Springer (1974).
+\textit{Fractional calculus and its applications: proceedings of the international conference held at the University of New Haven, June 1974}.
+\textbf{457}, Springer (1974).
 
